### 2020-09-25 expose/main.tex
initial commit

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber,style=alphabetic,sorting=ynt]{biblatex}
\addbibresource{bibliography.bib}

\title{Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.1}
\author{Jonas Gann}
\date{25 September 2020}

\begin{document}

\maketitle

\section{Context}

As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
Many shops were closed due to government measurements. Customers therefore had to use respective web
presences. CSS is a useful method to handle support for a high number of customers.

\section{Problem Statements}

Most enterprise systems such as CSS need to be integrated into existing enterprise architectures (EA).
This can be done via a business connector dedicated to providing CSS.

Resources and especially time are scarce. Integration therefore has to be as simple and fast as possible.
Simple means e.g. that existing systems do not need to be modified for integration or, 
that integration systems do not differ fundamentally between heterogenious landscapes.

Of course, besides being simple and fast, it also has to satisfy requirements of the connector 
and provide its CSS functionalities towards the EA. Typical integration challanges have to be adressed: 
Networks are slow and unreliable, applications have different interfacing requirements or are not 
built to be interfaced at all and possible changes of applications have to be considered.

\section{Objectives and Planned Approaches}

The bachelor thesis defines a messaging architecture for integration of CSS systems into existing enterprise
architectures.

In order to describe, what CSS is in practice, the bachelor thesis compiles CSS scenarios from multiple
resources. A scenario might e.g. be: \textit{New Address: User has a new home address and wants to change it in his profile}.

Enterprise architecture patterns (EAP) described by \cite{architecturePatterns} are used as model for
real life architectures. An EAP describes a common solution for reoccuring architectural problems in a 
generic way. It contains business processes, data objects and architecture bricks relevant for each pattern.
Architecture bricks are in the context of EAPs "the smallest element that everything is built of" 
\cite[Page 21]{architecturePatterns}. They can e.g. be a web-server or a database. Implementations of 
architecture bricks are called solution bricks and can e.g. be the Apache web-server or PostgreSQL.

For each CSS scenario, relevant business processes of the EAPs get selected. A pattern might already
provide business processes which are part of or related to a CSS scenario.
This can e.g. be: \textit{Change Address: Login, Edit Profile, Change Address, Save Changes}

EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
bricks and data objects.

An integration architecture gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Architecture bricks and data objects 
used in the final form of the integration architecture can be seen as its requirements towards the existing EA.

The integration architecture takes a message based approach by using enterprise integration patterns described
by \cite{integrationPatterns}. This approach aims to solve the previously described challenges in the 
"Problem Statements" section.

The integration architecture gets documented as a component diagram
containing architecture bricks, integration patterns and business connector along with communication 
channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
For each CSS business process, relevant data and instruction flows inside the integration architecture 
are visualized as a sequence diagram.

An operation manual, 
amongst other things, guides the requirement analysis in respect to existing architecture bricks and data 
objects of the EA and helps with theoretical and practical deployment of the integration architecture.

The results of the bachelor thesis are validated through application on customer examples. For given 
EA, business processes and customer specific requirments, the integration architecture will be 
deployed (in theory) by usage of the operation manual.
The quality of the integration architecture is measured by ease of deployment (e.g. used time) and 
statisfaction of customer requirements.

\section{Realted Work}

\begin{itemize}
    \item Business Connecor: The business connector of IDAS providing CSS functionalities
    \item Architecture Patterns described in the book by \cite{architecturePatterns}
    \item Integration Patterns described in the book by \cite{integrationPatterns}
\end{itemize}

\section{Milestones}

\begin{enumerate}
    \item Compilation CSS scenarios: October
    \item Relevant business processes and patterns: October / November
    \item Relevant architecture bricks and data objects: October / November
    \item Integration architecture: November / December
    \item Operation manual: December / January
    \item Validation: December / January
\end{enumerate}

\printbibliography

\end{document}

### 2020-09-27 expose/main.tex
add info about business connector

@@
 
-Of course, besides being simple and fast, it also has to satisfy requirements of the connector 
-and provide its CSS functionalities towards the EA. Typical integration challanges have to be adressed: 
-Networks are slow and unreliable, applications have different interfacing requirements or are not 
-built to be interfaced at all and possible changes of applications have to be considered.
+Of course, besides being simple and fast, it also has to enable EA and business connector to access each others 
+functionalities according to their requirements.
 
@@
 EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
-bricks and data objects.
+bricks and data objects, which will make up the enterprise architecture. The requirements of the EA 
+regarding the consumption of CSS services will be analyzed. One requirement could e.g. be, that access to 
+the \textit{New Address} CSS scenario is required via a web server architecture brick.
+
+CSS scenarios will be used to construct the business connector as a black box of requirements regarding 
+access to EA systems and data objects. The black box will also contain interfaces, which provide the CSS 
+scenarios. It will not be included, how the business 
+connector processes the recieved data, triggers instructions to the EA or implements a service.
+The business connector could e.g. consist of the requirements: \textit{access to identities, access to idendity validation, 
+access to profile data} and of the interface: \textit{changeIdendityProfileProperty}
 
 An integration architecture gets defined, which utilizes the selected business processes, architecture 
-bricks and data objects in order to integrate the business connector. Architecture bricks and data objects 
-used in the final form of the integration architecture can be seen as its requirements towards the existing EA.
+bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
+the EA and business connector to access each others functionalities according to their requirements considering 
+the rigid and heterogenious nature of the EA. Rather technological requirements like scalability and fail safety 
+and possible solutions will be evaluated while creating the integration architecture.
+Architecture bricks and data objects used in the final form of the 
+integration architecture can be seen as its requirements towards the existing EA.
 
 The integration architecture takes a message based approach by using enterprise integration patterns described
-by \cite{integrationPatterns}. This approach aims to solve the previously described challenges in the 
-"Problem Statements" section.
-
+by \cite{integrationPatterns}.
 The integration architecture gets documented as a component diagram

### 2020-09-28 expose/main.tex
add info on how problems are solved

@@
 
-Resources and especially time are scarce. Integration therefore has to be as simple and fast as possible.
-Simple means e.g. that existing systems do not need to be modified for integration or, 
-that integration systems do not differ fundamentally between heterogenious landscapes.
-
-Of course, besides being simple and fast, it also has to enable EA and business connector to access each others 
-functionalities according to their requirements.
+Resources and especially time are scarce. Integration therefore needs to be as simple and fast as possible and 
+function with little support, failure and modification over time. The variety of heterogenious landscapes and their constant 
+development make this challenging. The integration has to interface with an EA without the need of changing it but also be able to 
+adabt to its modifications.
+Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector, which 
+the bachelor thesis evaluates.
+As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
+relating to reliability e.g. sclability, failure safety have to be considered.
 
@@
 
-The bachelor thesis defines a messaging architecture for integration of CSS systems into existing enterprise
-architectures.
+In order to simplify integration, the bachelor thesis defines a messaging architecture for integration of a CSS connector 
+into enterprise
+architectures. The integration architecture simplifies integration by providing a integration solution reusable in many different 
+scenarios. It uses a messaging approach to be applicaple to heterogenious landscapes through loosely coupling. 
+Loose coupling allows integrated systems to not make assumptions about each other and use a send-and-forget approach, 
+simplifying their integration.
+Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.
+If the integration system satisifes requirements of the EA and business connector will be validated on a real life example.
+An operation manual presented by the thesis aims to further reduce deployment time and complexity and is used in the evaluation.
+
+The following describes the planned approaches:
 
@@
 bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
-the EA and business connector to access each others functionalities according to their requirements considering 
-the rigid and heterogenious nature of the EA. Rather technological requirements like scalability and fail safety 
-and possible solutions will be evaluated while creating the integration architecture.
+the EA and business connector to access each others functionalities according to their requirements.
+Requirements relating to the internal data and instruction delivery like e.g. scalability and fail safety will be considered.
 Architecture bricks and data objects used in the final form of the 

### 2020-09-28 expose/main.tex
fix spelling

@@
 
-\title{Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.1}
+\title{Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.2}
 \author{Jonas Gann}
-\date{25 September 2020}
+\date{28 September 2020}
 
@@
 \section{Context}
-
 As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
@@
 Resources and especially time are scarce. Integration therefore needs to be as simple and fast as possible and 
-function with little support, failure and modification over time. The variety of heterogenious landscapes and their constant 
+function with little support, failure and modification over time. The variety of heterogeneous landscapes and their constant 
 development make this challenging. The integration has to interface with an EA without the need of changing it but also be able to 
-adabt to its modifications.
+adapt to its modifications.
 Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector, which 
@@
 As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
-relating to reliability e.g. sclability, failure safety have to be considered.
+relating to reliability e.g. scalability, failure safety have to be considered.
 
@@
 architectures. The integration architecture simplifies integration by providing a integration solution reusable in many different 
-scenarios. It uses a messaging approach to be applicaple to heterogenious landscapes through loosely coupling. 
+scenarios. It uses a messaging approach to be applicable to heterogeneous landscapes through loosely coupling. 
 Loose coupling allows integrated systems to not make assumptions about each other and use a send-and-forget approach, 
@@
 Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.
-If the integration system satisifes requirements of the EA and business connector will be validated on a real life example.
+If the integration system satisfies requirements of the EA and business connector will be validated on a real life example.
 An operation manual presented by the thesis aims to further reduce deployment time and complexity and is used in the evaluation.
@@
 Enterprise architecture patterns (EAP) described by \cite{architecturePatterns} are used as model for
-real life architectures. An EAP describes a common solution for reoccuring architectural problems in a 
+real life architectures. An EAP describes a common solution for reoccurring architectural problems in a 
 generic way. It contains business processes, data objects and architecture bricks relevant for each pattern.
@@
 CSS scenarios will be used to construct the business connector as a black box of requirements regarding 
-access to EA systems and data objects. The black box will also contain interfaces, which provide the CSS 
+access to EA systems and data objects. The black box will also contain interfaces, which provide functionalities for CSS 
 scenarios. It will not be included, how the business 
-connector processes the recieved data, triggers instructions to the EA or implements a service.
-The business connector could e.g. consist of the requirements: \textit{access to identities, access to idendity validation, 
-access to profile data} and of the interface: \textit{changeIdendityProfileProperty}
+connector processes the received data, triggers instructions to the EA or implements a service.
+The business connector could e.g. consist of the requirements: \textit{access to identities, access to identity validation, 
+access to profile data} and of the interface: \textit{changeIdentityProfileProperty}
 
@@
 channels and respective message layouts \cite[cf. 16 ff.]{integrationPatterns}.
-For each CSS business process, relevant data and instruction flows inside the integration architecture 
+For each CSS scenario, relevant data and instruction flows inside the integration architecture 
 are visualized as a sequence diagram.
 
-An operation manual, 
-amongst other things, guides the requirement analysis in respect to existing architecture bricks and data 
+With the integration architecture finished, technologies which can be used for implementation get evaluated.
+These can e.g. be different message oriented middlewares used for implementing messaging systems in general.
+
+An operation manual guides the requirement analysis in respect to existing architecture bricks and data 
 objects of the EA and helps with theoretical and practical deployment of the integration architecture.
+It might e.g. help finding architecture bricks required by the integration architecture inside the EA 
+and instruct on how to implement the integration architecture in practice.
 
 The results of the bachelor thesis are validated through application on customer examples. For given 
-EA, business processes and customer specific requirments, the integration architecture will be 
+EA, business processes and customer specific requirements, the integration architecture will be 
 deployed (in theory) by usage of the operation manual.
 The quality of the integration architecture is measured by ease of deployment (e.g. used time) and 
-statisfaction of customer requirements.
+satisfaction of customer requirements.
 
-\section{Realted Work}
+\section{Related Work}
 
 \begin{itemize}
-    \item Business Connecor: The business connector of IDAS providing CSS functionalities
     \item Architecture Patterns described in the book by \cite{architecturePatterns}

### 2020-09-28 expose/main.tex
improved formulations and formatting

@@
 
-\title{Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.2}
+\title{Messaging Architecture for Integration of Customer Self Services \\ Version 0.2}
 \author{Jonas Gann}
@@
 As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
-Many shops were closed due to government measurements. Customers therefore had to use respective web
-presences. CSS is a useful method to handle support for a high number of customers.
+Many shops were closed due to government measurements. Customers therefore had to use their web
+presences. CSS is a useful method to handle support for an increasing number of online customers. It enables them to search 
+for contract data, change profile information, track shipment and much more without the need of human to human interaction.
+This reduces cost and increases customer performance.
 
@@
 Most enterprise systems such as CSS need to be integrated into existing enterprise architectures (EA).
-This can be done via a business connector dedicated to providing CSS.
+This can be done via a business connector dedicated to providing an interface for CSS.
 
 Resources and especially time are scarce. Integration therefore needs to be as simple and fast as possible and 
-function with little support, failure and modification over time. The variety of heterogeneous landscapes and their constant 
+function with little maintenance and failure. The variety of heterogeneous landscapes and their constant 
 development make this challenging. The integration has to interface with an EA without the need of changing it but also be able to 
-adapt to its modifications.
-Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector, which 
-the bachelor thesis evaluates.
+adapt to future modifications.
+
+Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector.
+
 As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
@@
 In order to simplify integration, the bachelor thesis defines a messaging architecture for integration of a CSS connector 
-into enterprise
-architectures. The integration architecture simplifies integration by providing a integration solution reusable in many different 
-scenarios. It uses a messaging approach to be applicable to heterogeneous landscapes through loosely coupling. 
-Loose coupling allows integrated systems to not make assumptions about each other and use a send-and-forget approach, 
-simplifying their integration.
+into enterprise architectures. The integration architecture simplifies integration by providing a solution for integration 
+reusable in many different scenarios. It uses a messaging approach to be applicable to heterogeneous landscapes through 
+loose coupling. Loose coupling allows integrated systems to not make assumptions about each other and use a 
+send-and-forget approach, simplifying their integration.
+
 Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.
-If the integration system satisfies requirements of the EA and business connector will be validated on a real life example.
-An operation manual presented by the thesis aims to further reduce deployment time and complexity and is used in the evaluation.
 
-The following describes the planned approaches:
+Through a real life example, it is validated, if the integration system satisfies requirements of the EA and business connector.
+
+An operation manual presented by the thesis aims to further reduce deployment time and complexity and is used during the evaluation.
+
+The following approaches are planned:
 
 In order to describe, what CSS is in practice, the bachelor thesis compiles CSS scenarios from multiple
-resources. A scenario might e.g. be: \textit{New Address: User has a new home address and wants to change it in his profile}.
+resources. A scenario might e.g. be "New Address": User wants to change new address in his profile.
 
-Enterprise architecture patterns (EAP) described by \cite{architecturePatterns} are used as model for
+Enterprise architecture patterns (EAP) described by \cite{architecturePatterns} are used to abstract
 real life architectures. An EAP describes a common solution for reoccurring architectural problems in a 
@@
 
-For each CSS scenario, relevant business processes of the EAPs get selected. A pattern might already
-provide business processes which are part of or related to a CSS scenario.
-This can e.g. be: \textit{Change Address: Login, Edit Profile, Change Address, Save Changes}
+For each CSS scenario, relevant business processes from EAPs get selected. A pattern might 
+provide business processes which are part of or related to CSS scenarios.
+This can e.g. be "Change Address": Login, Edit Profile, Change Address, Save Changes
 
 EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
-bricks and data objects, which will make up the enterprise architecture. The requirements of the EA 
-regarding the consumption of CSS services will be analyzed. One requirement could e.g. be, that access to 
-the \textit{New Address} CSS scenario is required via a web server architecture brick.
+bricks and data objects. These make up the enterprise architecture. The requirements of the EA 
+regarding the consumption of CSS services get analyzed. One requirement could e.g. be, that access to 
+the "New Address" CSS scenario is required via a web server architecture brick. Another requirement might be, 
+that data has to arrive in the correct order.
 
-CSS scenarios will be used to construct the business connector as a black box of requirements regarding 
-access to EA systems and data objects. The black box will also contain interfaces, which provide functionalities for CSS 
-scenarios. It will not be included, how the business 
-connector processes the received data, triggers instructions to the EA or implements a service.
-The business connector could e.g. consist of the requirements: \textit{access to identities, access to identity validation, 
-access to profile data} and of the interface: \textit{changeIdentityProfileProperty}
+CSS scenarios are used to construct the business connector as a black box of requirements regarding 
+access to EA systems and data objects. The black box also contains interfaces, which provide functionalities for CSS 
+scenarios. It is not be included, how the business 
+connector processes received data, triggers instructions to the EA or implements a service.
+The business connector could e.g. consist of the requirements: access to identities, access to identity validation, 
+access to profile data and of the interface "changeIdentityProfileProperty"
 
@@
 the EA and business connector to access each others functionalities according to their requirements.
-Requirements relating to the internal data and instruction delivery like e.g. scalability and fail safety will be considered.
+Requirements relating to the internal data and instruction delivery of the integration architecture 
+like e.g. scalability and fail safety get considered in addition.
 Architecture bricks and data objects used in the final form of the 
-integration architecture can be seen as its requirements towards the existing EA.
+integration architecture can be seen as its requirements towards an existing EA.
 
 The integration architecture takes a message based approach by using enterprise integration patterns described
-by \cite{integrationPatterns}.
+by \textcite{integrationPatterns}.
 The integration architecture gets documented as a component diagram
@@
 The results of the bachelor thesis are validated through application on customer examples. For given 
-EA, business processes and customer specific requirements, the integration architecture will be 
+EA, business processes, business connector and customer specific requirements, the integration architecture gets 
 deployed (in theory) by usage of the operation manual.
 The quality of the integration architecture is measured by ease of deployment (e.g. used time) and 
-satisfaction of customer requirements.
+satisfaction of requirements.
 
@@
 \begin{itemize}
-    \item Architecture Patterns described in the book by \cite{architecturePatterns}
-    \item Integration Patterns described in the book by \cite{integrationPatterns}
+    \item "Enterprise Architecture Patterns" \cite{architecturePatterns}: This book presents how to construct and use so 
+    called enterprise architecture patterns (EAP) and documents 13 common examples. 
+    \item "Enterprise Integration Patterns" \cite{integrationPatterns}: This book documents fundamental messaging patterns, 
+    which can be used for integration purposes.
 \end{itemize}
@@
 
+The bachelor thesis is planned to be officially registered in November and finished in February.
+Parallel to the execution of the described approaches, the relating chapters of the bachelor thesis will be written.
+
 \begin{enumerate}
-    \item Compilation CSS scenarios: October
-    \item Relevant business processes and patterns: October / November
+    \item CSS scenarios: October
+    \item Relevant business processes and patterns: October
     \item Relevant architecture bricks and data objects: October / November
+    \item Business connector: October / November
     \item Integration architecture: November / December
@@
     \item Validation: December / January
+    \item Finishing writing and presentation: February
 \end{enumerate}

### 2020-09-28 expose/main.tex
add big font on beginning of chapter

@@
 As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
-Many shops were closed due to government measurements. Customers therefore had to use their web
+Many shops were closed due to government measurements and customers had to use their web
 presences. CSS is a useful method to handle support for an increasing number of online customers. It enables them to search 
@@
 
-\section{Objectives and Planned Approaches}
+\section{Objectives}
 
-In order to simplify integration, the bachelor thesis defines a messaging architecture for integration of a CSS connector 
-into enterprise architectures. The integration architecture simplifies integration by providing a solution for integration 
-reusable in many different scenarios. It uses a messaging approach to be applicable to heterogeneous landscapes through 
+The bachelor thesis defines a messaging architecture for integration of a CSS connector 
+into enterprise architectures. This simplifies and speeds up integration by providing a solution reusable in many 
+different scenarios. A messaging approach enables deployment on different heterogeneous landscapes through 
 loose coupling. Loose coupling allows integrated systems to not make assumptions about each other and use a 
@@
 
-Through a real life example, it is validated, if the integration system satisfies requirements of the EA and business connector.
+Through a real life example, it is validated, if the integration architecture satisfies requirements of the EA and 
+business connector.
 
@@
 
-The following approaches are planned:
+\section{Planned Approaches}
 
-In order to describe, what CSS is in practice, the bachelor thesis compiles CSS scenarios from multiple
-resources. A scenario might e.g. be "New Address": User wants to change new address in his profile.
+\textbf{CSS scenarios} get compiled from multiple resources in order to describe, what CSS looks like in practice.
+A scenario might e.g. be "New Address": User wants to change the address in his profile.
 
-Enterprise architecture patterns (EAP) described by \cite{architecturePatterns} are used to abstract
+\textbf{Enterprise architecture patterns (EAP)} described by \textcite{architecturePatterns} are used to abstract
 real life architectures. An EAP describes a common solution for reoccurring architectural problems in a 
@@
 
-For each CSS scenario, relevant business processes from EAPs get selected. A pattern might 
-provide business processes which are part of or related to CSS scenarios.
+\textbf{Business processes} relevant for the CSS scenarios get selected from EAPs. Relevance means, that the process 
+is part of or related to the scenario.
 This can e.g. be "Change Address": Login, Edit Profile, Change Address, Save Changes
 
-EAPs, which contain the selected business processes, are evaluated in respect to relevant architecture 
-bricks and data objects. These make up the enterprise architecture. The requirements of the EA 
-regarding the consumption of CSS services get analyzed. One requirement could e.g. be, that access to 
+\textbf{Architecture bricks and data objects} contained by EAPs of selected business processes are evaluated in respect to their necessity 
+for the process. They make up the enterprise architecture. Requirements of the EA 
+regarding the consumption of CSS get analyzed. One requirement could e.g. be, that access to 
 the "New Address" CSS scenario is required via a web server architecture brick. Another requirement might be, 
@@
 
-CSS scenarios are used to construct the business connector as a black box of requirements regarding 
-access to EA systems and data objects. The black box also contains interfaces, which provide functionalities for CSS 
+\textbf{The business connector} is constructed - based on CSS scenarios - as a black box of requirements regarding 
+the access to EA systems and data objects. The black box also contains interfaces, which provide functionalities for CSS 
 scenarios. It is not be included, how the business 
@@
 
-An integration architecture gets defined, which utilizes the selected business processes, architecture 
+\textbf{An integration architecture} gets defined, which utilizes the selected business processes, architecture 
 bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
@@
 
-The integration architecture takes a message based approach by using enterprise integration patterns described
-by \textcite{integrationPatterns}.
-The integration architecture gets documented as a component diagram
+\textbf{A messaging approach} based on enterprise integration patterns described
+by \textcite{integrationPatterns} is used for the integration architecture.
+It gets documented as a component diagram
 containing architecture bricks, integration patterns and business connector along with communication 
@@
 
-With the integration architecture finished, technologies which can be used for implementation get evaluated.
+\textbf{Technologies} which can be used for implementation get evaluated for the final form of the integration architecture.
 These can e.g. be different message oriented middlewares used for implementing messaging systems in general.
 
-An operation manual guides the requirement analysis in respect to existing architecture bricks and data 
-objects of the EA and helps with theoretical and practical deployment of the integration architecture.
+\textbf{An operation manual} with the purpose of guiding the requirement analysis in respect to existing architecture bricks and data 
+objects of the EA and helping with theoretical and practical deployment of the integration architecture gets constructed.
 It might e.g. help finding architecture bricks required by the integration architecture inside the EA 
@@
 
-The results of the bachelor thesis are validated through application on customer examples. For given 
+\textbf{A validation} of results is done through a customer example. For given 
 EA, business processes, business connector and customer specific requirements, the integration architecture gets 
@@
     \item "Enterprise Architecture Patterns" \cite{architecturePatterns}: This book presents how to construct and use so 
-    called enterprise architecture patterns (EAP) and documents 13 common examples. 
+    called enterprise architecture patterns and documents 13 common examples. 
     \item "Enterprise Integration Patterns" \cite{integrationPatterns}: This book documents fundamental messaging patterns, 
@@
 The bachelor thesis is planned to be officially registered in November and finished in February.
-Parallel to the execution of the described approaches, the relating chapters of the bachelor thesis will be written.
+Parallel to the execution of described approaches, relating chapters of the bachelor thesis will be written.
 

### 2020-10-08 thesis/msc-thesis.tex
add sections

% This template was initially provided by Dulip Withanage.
% Modifications for the database systems research group
% were made by Conny Junghans,  Jannik Strötgen and Michael Gertz

\documentclass[
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
%     liststotoc,   % table listing in toc
%     bibtotoc,     % bibliography in toc
%     idxtotoc,     % index in toc
%     parskip       % paragraph skip instad of paragraph indent
     ]{scrreprt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES:

% Use German :
\usepackage[english]{babel}
% Input and font encoding
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
% Index-generation
\usepackage{makeidx}
% Einbinden von URLs:
\usepackage{url}
% Special \LaTex symbols (e.g. \BibTeX):
%\usepackage{doc}
% Include Graphic-files:
\usepackage{graphicx}
% Include doc++ generated tex-files:
%\usepackage{docxx}
% Include PDF links
%\usepackage[pdftex, bookmarks=true]{hyperref}

% Fuer anderthalbzeiligen Textsatz
\usepackage{setspace}

% hyperrefs in the documents
\usepackage[bookmarks=true,colorlinks,pdfpagelabels,pdfstartview = FitH,bookmarksopen = true,bookmarksnumbered = true,linkcolor = black,plainpages = false,hypertexnames = false,citecolor = black,urlcolor=black]{hyperref} 
%\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% OTHER SETTINGS:

% Pagestyle:
\pagestyle{headings}

% Choose language
\newcommand{\setlang}[1]{\selectlanguage{#1}\nonfrenchspacing}

\begin{document}

% TITLE:
\pagenumbering{roman}
\begin{titlepage}
     \vspace*{1cm}
     \begin{center}
          \vspace*{3cm}
          \textbf
          {
               \Large University of Heidelberg\\
               \smallskip
               \Large Institute for Computer Science\\
               \smallskip
               \Large Working group database systems\\
               \smallskip
          }

          \vspace{3cm}

          \textbf{\large Bachelor thesis}

          \vspace{0.5\baselineskip}
          {
               \huge
               \textbf{Messaging Architecture for Integration of Customer Self-Services}
          }

     \end{center}

     \vfill
     {
          \large
          \begin{tabular}[l]{ll}
               Name:                 & Jonas Gann              \\
               Matriculation number: & 3367576                 \\
               Supervisor:           & Prof. Dr. Michael Gertz \\
               Date of submission:   & \today
          \end{tabular}
     }

\end{titlepage}

\onehalfspacing

\thispagestyle{empty}

\vspace*{100pt}
\noindent
I assure that I have written this bachelor thesis on my own and only used the specified sources and
resources and that I followed the principles and recommendations "Responsibility in Science" of the
University of Heidelberg.

\vspace*{50pt}
\noindent

\underline{\phantom{mmmmmmmmmmmmmmmmmmmm}}

\medskip
\noindent
Date of Submission: \today
\newpage

\chapter*{Zusammenfassung}

\newpage

\chapter*{Abstract}

\newpage

% MAIN PART:
% Table of contents (Inhaltsverzeichnis)
\tableofcontents
\cleardoublepage
\pagenumbering{arabic}

% List of figures (Abbildungsverzeichnis):
%\listoffigures
% List of tables (Tabellenverzeichnis):
%\listoftables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}\label{intro}

\section{Motivation}

\subsection{Example(s) of CSS Problems Today}
\begin{enumerate}
     \item CSS incomplete in governmental administration
           \begin{enumerate}
                \item identity card renewal
                \item change of home address
                \item change of residency status
           \end{enumerate}

     \item CSS incomplete in universities
           \begin{enumerate}
                \item transfer of profile: grades, certificates, etc. between universities
                \item applications in general (study place, semester abroad, ...)
           \end{enumerate}

     \item CSS different for each enterprise / organization
           \begin{enumerate}
                \item multiple identities
                \item multiple profiles => addresses, phone numbers, mail address
                \item time consuming to manage same information in all systems
           \end{enumerate}
\end{enumerate}

\subsection{Solution for CSS Problems}
\begin{enumerate}
     \item One CSS providing company, which integrates multiple / all EA
     \item One identity, profile, address, phone number, location, ...
     \item Easy management of identity used by multiple enterprises / organizations
\end{enumerate}

\subsection{Integration necessity}
\begin{enumerate}
     \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
     \item The CSS providing company needs to manage those systems / data of each enterprise / organization
     \item Enterprise Integration solves this Problem
\end{enumerate}

\section{Goals of the work}

\subsection{Integration Challenges}
\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}

     \item Different (proprietary) data models within and between Enterprises and Organizations
           \begin{enumerate}
                \item Different (property)name for same data objects (syntactic integration)
                \item Different meanings for same (property)name (semantic integration)
           \end{enumerate}

     \item Stability of Integration
           \begin{enumerate}
                \item Future Changes of EA
                \item Scalability
                \item Failure of EA or Integration Components
           \end{enumerate}

     \item Scarce Resources
           \begin{enumerate}
                \item Integration Development Speed
                      \begin{enumerate}
                           \item Necessary Development <=> Reuse of existing Technology
                           \item Complexity / Size of Integration
                      \end{enumerate}

                \item Maintenance of finished Integration

                \item Hardware / Software Costs of Integration
                      \begin{enumerate}
                           \item Licenses for Software
                           \item Scalability of Integration => Necessary Computing Power
                      \end{enumerate}

           \end{enumerate}

\end{enumerate}

\subsection{Presented Solutions}
\begin{enumerate}
     \item Messaging Integration
           \begin{enumerate}
                \item Loose Coupling
                      \begin{enumerate}
                           \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                           \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                           \item Loose Coupling allows Reuse of "Modules" => faster development
                      \end{enumerate}

                \item Messaging enables communication with many systems through Adapters

                \item Messaging provides mechanisms for Stability
                      \begin{enumerate}
                           \item Store-and-Forward
                           \item Load Balancing
                      \end{enumerate}

           \end{enumerate}

     \item Integration Patterns
           \begin{enumerate}
                \item Patterns speed up construction of Integration Architecture
                \item Patterns are proven solutions
                \item Patterns abstract from concrete technologies
                      \begin{enumerate}
                           \item Simplifies understanding of integration concept
                           \item Allows implementation with different technologies
                      \end{enumerate}

           \end{enumerate}

\end{enumerate}

\section{Structure of the work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\chapter{Foundation and related work}

\section{Customer Self-Service}

\subsection{Definition}
\begin{enumerate}
     \item Definition in the context of the thesis
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How can CSS-Scenarios be documented?
\end{enumerate}

\subsection{List of Scenarios}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Finding relevant EAPs
     \item Requirement analysis of business Connector
     \item Interface definition of business connector
\end{enumerate}

\section{Architecture Patterns}
\subsection{Definition}
\begin{enumerate}
     \item Definition
     \item Metadata
     \item Views
     \item Architecture bricks
     \item Data bricks
     \item Business processes
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Basis for real-life enterprise architectures
     \item Provides architecture and data bricks the integration can build up on
\end{enumerate}

\subsection{Architecture- and Data bricks}
\begin{enumerate}
     \item Description of EAPs used in the thesis
     \item Reasons why each EAP is relevant for CSS
           \begin{enumerate}
                \item Derived by comparing CSS-Scenarios with business processes
           \end{enumerate}
     \item Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
     \item Documentation of resulting Architecture and data bricks
\end{enumerate}

\subsection{Requirements of Enterprise Architecture}
\begin{enumerate}
     \item List of requirements towards the integration Architecture
           \begin{enumerate}
                \item Adapters for systems
                \item Required Format of incoming data
           \end{enumerate}
\end{enumerate}

\section{Business Connector}

\subsection{Definition}
\begin{enumerate}
     \item Provides functionality of "external" service provider
     \item Purpose is to simplify integration
     \item Can be assumed to provide sufficient interfaces
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Provides interface for CSS functionalities
     \item Should be integrated in architecture and data bricks
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How to document the business Connector in this context

     \item List of provided functionalities along with their interfaces
           \begin{enumerate}
                \item Derived from CSS-Scenarios
                \item Derived from IDAS Connector
           \end{enumerate}

     \item List of requirements regarding the EA
           \begin{enumerate}
                \item Access to architecture and data bricks
           \end{enumerate}

     \item List of requirements regarding the integration Architecture
           \begin{enumerate}
                \item Format of data
                \item Order of delivery
                \item Time relevance of data
                \item Guaranteed delivery of data
           \end{enumerate}

\end{enumerate}

\section{Integration Patterns}

\subsection{Definition}
\begin{enumerate}
     \item Messaging Methodology
     \item Patterns describe often solved messaging problems
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Already explained in Motivation?
\end{enumerate}

\subsection{Patterns used in Thesis}
\begin{enumerate}
     \item Description of Patterns later used in the integration architecture
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\chapter{My contribution}

\section{Overview}

\section{Requirements}

\subsection{Requirements of Enterprise Architecture}

\subsection{Requirements of Business Connector}

\subsection{Requirements of Integration System}

\section{Scenario Integrations}
\begin{enumerate}
     \item Look at integration architecture for each CSS-Scenario
\end{enumerate}

\subsection{Integration Architecture Documentation Method}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsection{Scenario1}
\begin{enumerate}
     \item Description of Scenario
\end{enumerate}

\subsubsection{Scenario1 Integration Architecture}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsubsection{System Integration}
\begin{enumerate}
     \item Explanation how the systems are integrated
     \item Why was each pattern used?
     \item How are requirements met?
\end{enumerate}

\subsubsection{Data Integration}
\begin{enumerate}
     \item Explanation how the data objects are integrated
     \item Why was data transformed / mapped?
     \item How are requirements met
\end{enumerate}

\subsection{Scenario2}

\subsubsection{Scenario2 Integration Architecture}

\subsubsection{System Integration}

\subsubsection{Data Integration}

\section{Operating Manual}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental evaluation}

\section{Customer Landscape}

\section{Customer Requirements}

\section{Integration}

\subsection{Using the Operating Manual}

\subsection{Relevant Bricks}

\subsubsection{Data Bricks}

\subsubsection{Architecture Bricks}

\subsection{Resulting Integration}

\subsubsection{Integration Documentation}

\subsubsection{System Integration}

\subsubsection{Data Integration}

\section{Evaluation}

\subsection{Satisfaction of Requirements}

\subsubsection{Enterprise Architecture Requirements}

\subsubsection{Customer Requirements}

\subsubsection{Business Connector Requirements}

\subsubsection{Integration Architecture Requirements}

\subsection{Resource-Heaviness}

\subsubsection{Required time for application}

\subsubsection{Size of Resulting System}

\subsubsection{Increasing cost due to scaling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Summary and outlook}

% References (Literaturverzeichnis):
% a) Style (with abbreviations: use alpha):
% see
% https://de.wikibooks.org/wiki/LaTeX-W%C3%B6rterbuch:_bibliographystyle
% for the different formats and styles

\bibliographystyle{apalike}
% b) The File:
\bibliography{references}

\end{document}

### 2020-10-12 thesis/msc-thesis.tex
Verbesserungen vorgeschlagen von Thomas

@@
 
-\subsection{Example(s) of CSS Problems Today}
+\subsection{Evolution of digital Customer Self-Service}
 \begin{enumerate}
-     \item CSS incomplete in governmental administration
+     \item Increasing consumer standards
            \begin{enumerate}
-                \item identity card renewal
-                \item change of home address
-                \item change of residency status
+                \item Passwordless sign in
+                \item instant updates
            \end{enumerate}
 
-     \item CSS incomplete in universities
+     \item New regulations
            \begin{enumerate}
-                \item transfer of profile: grades, certificates, etc. between universities
-                \item applications in general (study place, semester abroad, ...)
+                \item DSGVO
+                \item Onlinezugangsgesetz
+                \item DVG (eAU, eRezept)
+                \item psd2
            \end{enumerate}
 
-     \item CSS different for each enterprise / organization
-           \begin{enumerate}
-                \item multiple identities
-                \item multiple profiles => addresses, phone numbers, mail address
-                \item time consuming to manage same information in all systems
-           \end{enumerate}
 \end{enumerate}
 
-\subsection{Solution for CSS Problems}
+\subsection{CSS as a Service}
 \begin{enumerate}
-     \item One CSS providing company, which integrates multiple / all EA
-     \item One identity, profile, address, phone number, location, ...
-     \item Easy management of identity used by multiple enterprises / organizations
+     \item Enterprises can offer CSS service, satisfying modern requirements and regulations
 \end{enumerate}
 
-\subsection{Integration necessity}
+\subsection{Service Integration}
 \begin{enumerate}
-     \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
-     \item The CSS providing company needs to manage those systems / data of each enterprise / organization
-     \item Enterprise Integration solves this Problem
+     \item The provided CSS service has to be integrated into existing enterprise architecture
 \end{enumerate}
@@
 
-\subsection{Integration Challenges}
+Solution for integration challenges
 \begin{enumerate}
@@
 
-\subsection{Presented Solutions}
-\begin{enumerate}
-     \item Messaging Integration
-           \begin{enumerate}
-                \item Loose Coupling
-                      \begin{enumerate}
-                           \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
-                           \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
-                           \item Loose Coupling allows Reuse of "Modules" => faster development
-                      \end{enumerate}
-
-                \item Messaging enables communication with many systems through Adapters
-
-                \item Messaging provides mechanisms for Stability
-                      \begin{enumerate}
-                           \item Store-and-Forward
-                           \item Load Balancing
-                      \end{enumerate}
-
-           \end{enumerate}
-
-     \item Integration Patterns
-           \begin{enumerate}
-                \item Patterns speed up construction of Integration Architecture
-                \item Patterns are proven solutions
-                \item Patterns abstract from concrete technologies
-                      \begin{enumerate}
-                           \item Simplifies understanding of integration concept
-                           \item Allows implementation with different technologies
-                      \end{enumerate}
-
-           \end{enumerate}
-
-\end{enumerate}
-
 \section{Structure of the work}
@@
 \section{Customer Self-Service}
-
-\subsection{Definition}
 \begin{enumerate}
      \item Definition in the context of the thesis
-\end{enumerate}
-
-\subsection{Documentation}
-\begin{enumerate}
-     \item How can CSS-Scenarios be documented?
-\end{enumerate}
-
-\subsection{List of Scenarios}
-
-\subsection{Purpose in Thesis}
-\begin{enumerate}
-     \item Finding relevant EAPs
-     \item Requirement analysis of business Connector
-     \item Interface definition of business connector
+     \item Purpose in Thesis
+     \item Overview of CSS-Scenarios found in literature
 \end{enumerate}
@@
 \section{Architecture Patterns}
-\subsection{Definition}
 \begin{enumerate}
      \item Definition
-     \item Metadata
-     \item Views
-     \item Architecture bricks
-     \item Data bricks
-     \item Business processes
+     \item Purpose in Thesis
+     \item Explanation of used Patterns
 \end{enumerate}
 
-\subsection{Purpose in Thesis}
+\subsection{Business Connector}
 \begin{enumerate}
-     \item Basis for real-life enterprise architectures
-     \item Provides architecture and data bricks the integration can build up on
+     \item Definition in context of the thesis
+     \item Purpose in Thesis
 \end{enumerate}
 
-\subsection{Architecture- and Data bricks}
+\section{Messaging Patterns}
 \begin{enumerate}
-     \item Description of EAPs used in the thesis
-     \item Reasons why each EAP is relevant for CSS
+     \item Definition
+     \item Messaging
+           \begin{enumerate}
+                \item Answer: Why is messaging used?
+           \end{enumerate}
+     \item Patterns
+           \begin{enumerate}
+                \item Answer: Why are patterns used?
+           \end{enumerate}
+     \item Explanation of used patterns
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\chapter{Groundwork}
+
+\subsection{CSS-Scenarios}
+\begin{enumerate}
+     \item Categorization of Scenarios
+     \item Combining similar scenarios (into a more general one)
+     \item Prioritization
+     \item ToDo: How to document?
+     \item Documentation of final list
+\end{enumerate}
+
+\subsection{Enterprise Architecture}
+\begin{enumerate}
+     \item Architecture- and Data bricks
+           \begin{enumerate}
+                \item Selection of EAPs relevant for CSS
                       \begin{enumerate}
@@
                       \end{enumerate}
-     \item Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
+                \item Evaluation of Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
                 \item Documentation of resulting Architecture and data bricks
@@
 
-\subsection{Requirements of Enterprise Architecture}
+     \item Requirements of Enterprise Architecture
            \begin{enumerate}
@@
            \end{enumerate}
+\end{enumerate}
 
 \section{Business Connector}
-
-\subsection{Definition}
 \begin{enumerate}
-     \item Provides functionality of "external" service provider
-     \item Purpose is to simplify integration
-     \item Can be assumed to provide sufficient interfaces
-\end{enumerate}
-
-\subsection{Purpose in Thesis}
-\begin{enumerate}
-     \item Provides interface for CSS functionalities
-     \item Should be integrated in architecture and data bricks
-\end{enumerate}
-
-\subsection{Documentation}
-\begin{enumerate}
-     \item How to document the business Connector in this context
-
+     \item How to document the business Connector
      \item List of provided functionalities along with their interfaces
@@
 
-\section{Integration Patterns}
-
-\subsection{Definition}
-\begin{enumerate}
-     \item Messaging Methodology
-     \item Patterns describe often solved messaging problems
-\end{enumerate}
-
-\subsection{Purpose in Thesis}
-\begin{enumerate}
-     \item Already explained in Motivation?
-\end{enumerate}
-
-\subsection{Patterns used in Thesis}
-\begin{enumerate}
-     \item Description of Patterns later used in the integration architecture
-\end{enumerate}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\chapter{My contribution}
+\chapter{Integration Architecture}
 
@@
 \section{Requirements}
+
+\begin{enumerate}
+     \item Requirements of Enterprise Architecture
+     \item Requirements of Business Connector
+     \item Requirements of Integration System
+\end{enumerate}
 
@@
 
-\section{Operating Manual}
+\chapter{Evaluation}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Experimental evaluation}
+\section{Technological Evaluation}
 
-\section{Customer Landscape}
+\subsection{Available Messaging Technologies}
 
-\section{Customer Requirements}
+\subsection{Implementation of Integration Architecture}
 
-\section{Integration}
+\subsection{Evaluation of result}
 
-\subsection{Using the Operating Manual}
+\section{Experimental Evaluation}
 
-\subsection{Relevant Bricks}
+\subsection{Customer Example}
 
-\subsubsection{Data Bricks}
+\subsection{Application of Integration Architecture}
 
-\subsubsection{Architecture Bricks}
+\subsection{Evaluation of result}
 
-\subsection{Resulting Integration}
-
-\subsubsection{Integration Documentation}
-
-\subsubsection{System Integration}
-
-\subsubsection{Data Integration}
-
-\section{Evaluation}
-
-\subsection{Satisfaction of Requirements}
-
-\subsubsection{Enterprise Architecture Requirements}
-
-\subsubsection{Customer Requirements}
-
-\subsubsection{Business Connector Requirements}
-
-\subsubsection{Integration Architecture Requirements}
-
-\subsection{Resource-Heaviness}
-
-\subsubsection{Required time for application}
-
-\subsubsection{Size of Resulting System}
-
-\subsubsection{Increasing cost due to scaling}
+\section{Operation Manual}
+\begin{enumerate}
+     \item Guide on how to implement and deploy the integration architecture
+     \item incorporates results of previous evaluations
+\end{enumerate}
 

### 2020-10-15 thesis/msc-thesis.tex
new table of content

@@
 
-% MAIN PART:
-% Table of contents (Inhaltsverzeichnis)
 \tableofcontents
@@
 
-% List of figures (Abbildungsverzeichnis):
-%\listoffigures
-% List of tables (Tabellenverzeichnis):
-%\listoftables
+\chapter{Context}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The german ministry of economy and energy recognizes that "we have long since arrived in a digitized world". This realization 
+of the german government comes along with important federal and european legislation. Most prominent are DSGVO, OZG and DVG, 
+modernizing data protection, governmental administration and health care.
 
-\chapter{Introduction}\label{intro}
+Enterprises, organizations and authorities are required to provide additional digital services for its customers and users.
+Those include for example the deletion of non-mandatory data and the digital application for unemployment benefit.
 
-\section{Motivation}
+Working with existing system- and data architectures, integration of new solutions is necessary.
 
-\subsection{Evolution of digital Customer Self-Service}
+\chapter{Objectives}
+
+This bachelor thesis describes digital self-service as a solution for the additional requirements. It explains the basis of what 
+customer self-service (CSS) is, what relevant legislation is about and how CSS providers can help in the digital transformation.
+
+The technological challenge of integrating CSS providers into existing system architectures is focus of this bachelor thesis.
+An integration architecture is presented, which provides solutions for the following questions (ToDo: In Textform schreiben):
+
 \begin{enumerate}
-     \item Increasing consumer standards
-           \begin{enumerate}
-                \item Passwordless sign in
-                \item instant updates
+     \item How can services of a CSS provider be accessed by the enterprise architecture?
+     \item Which systems of a typical enterprise architecture are required?
+     \item Which data objects of a typical enterprise architecture are required?
+     \item Which additional systems and data objects are required?
+     \item How can heterogeneous enterprise architectures be integrated the same way?
+     \item How can the integration be non-invasive?
+     \item How can the speed of integration development be increased?
+     \item How can the speed of integration deployment be increased?
+     \item How can the integration system be reliable and maintainable?
 \end{enumerate}
 
-     \item New regulations
-           \begin{enumerate}
-                \item DSGVO
-                \item Onlinezugangsgesetz
-                \item DVG (eAU, eRezept)
-                \item psd2
-           \end{enumerate}
+The architecture is evaluated in respect to technological feasibility and real-life applicability. The results are incorporated into 
+an operating manual, providing guidance in developing and deploying the presented integration architecture.
 
-\end{enumerate}
+\chapter{Structure of Work}
 
-\subsection{CSS as a Service}
-\begin{enumerate}
-     \item Enterprises can offer CSS service, satisfying modern requirements and regulations
-\end{enumerate}
+\chapter{Customer Self-Service (CSS)}
 
-\subsection{Service Integration}
-\begin{enumerate}
-     \item The provided CSS service has to be integrated into existing enterprise architecture
-\end{enumerate}
+\section{Definition}
 
-\section{Goals of the work}
+\section{Description}
 
-Solution for integration challenges
-\begin{enumerate}
-     \item Heterogeneous Enterprise Architecture Systems
-           \begin{enumerate}
-                \item Different Applications
-                \item Different Application Vendors
-                \item Different / No Application Interfaces
-                \item Legacy Systems
-           \end{enumerate}
+\section{Benefits}
 
-     \item Different (proprietary) data models within and between Enterprises and Organizations
-           \begin{enumerate}
-                \item Different (property)name for same data objects (syntactic integration)
-                \item Different meanings for same (property)name (semantic integration)
-           \end{enumerate}
+\subsection{Customer}
 
-     \item Stability of Integration
-           \begin{enumerate}
-                \item Future Changes of EA
-                \item Scalability
-                \item Failure of EA or Integration Components
-           \end{enumerate}
+\subsection{Organization}
 
-     \item Scarce Resources
-           \begin{enumerate}
-                \item Integration Development Speed
-                      \begin{enumerate}
-                           \item Necessary Development <=> Reuse of existing Technology
-                           \item Complexity / Size of Integration
-                      \end{enumerate}
+\section{Examples}
 
-                \item Maintenance of finished Integration
+\chapter{Governmental Regulations}
 
-                \item Hardware / Software Costs of Integration
-                      \begin{enumerate}
-                           \item Licenses for Software
-                           \item Scalability of Integration => Necessary Computing Power
-                      \end{enumerate}
+\section{Purpose}
 
-           \end{enumerate}
+\section{Importance for Organizations}
 
-\end{enumerate}
+\section{DSGVO}
 
-\section{Structure of the work}
+\section{OZG}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\section{DVG}
 
-\chapter{Foundation and related work}
+\section{Challenges for Organizations}
 
-\section{Customer Self-Service}
-\begin{enumerate}
-     \item Definition in the context of the thesis
-     \item Purpose in Thesis
-     \item Overview of CSS-Scenarios found in literature
-\end{enumerate}
+\chapter{Compliance through CSS}
 
-\section{Architecture Patterns}
-\begin{enumerate}
-     \item Definition
-     \item Purpose in Thesis
-     \item Explanation of used Patterns
-\end{enumerate}
+\section{Description}
 
-\subsection{Business Connector}
-\begin{enumerate}
-     \item Definition in context of the thesis
-     \item Purpose in Thesis
-\end{enumerate}
+\section{CSS-Scenarios}
 
-\section{Messaging Patterns}
-\begin{enumerate}
-     \item Definition
-     \item Messaging
-           \begin{enumerate}
-                \item Answer: Why is messaging used?
-           \end{enumerate}
-     \item Patterns
-           \begin{enumerate}
-                \item Answer: Why are patterns used?
-           \end{enumerate}
-     \item Explanation of used patterns
-\end{enumerate}
+\section{Requirements}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\chapter{CSS Providers}
 
-\chapter{Groundwork}
+\section{Description}
 
-\subsection{CSS-Scenarios}
-\begin{enumerate}
-     \item Categorization of Scenarios
-     \item Combining similar scenarios (into a more general one)
-     \item Prioritization
-     \item ToDo: How to document?
-     \item Documentation of final list
-\end{enumerate}
-
-\subsection{Enterprise Architecture}
-\begin{enumerate}
-     \item Architecture- and Data bricks
-           \begin{enumerate}
-                \item Selection of EAPs relevant for CSS
-                      \begin{enumerate}
-                           \item Derived by comparing CSS-Scenarios with business processes
-                      \end{enumerate}
-                \item Evaluation of Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
-                \item Documentation of resulting Architecture and data bricks
-           \end{enumerate}
-
-     \item Requirements of Enterprise Architecture
-           \begin{enumerate}
-                \item List of requirements towards the integration Architecture
-                      \begin{enumerate}
-                           \item Adapters for systems
-                           \item Required Format of incoming data
-                      \end{enumerate}
-           \end{enumerate}
-\end{enumerate}
+\section{CSS Solutions}
 
 \section{Business Connector}
-\begin{enumerate}
-     \item How to document the business Connector
-     \item List of provided functionalities along with their interfaces
-           \begin{enumerate}
-                \item Derived from CSS-Scenarios
-                \item Derived from IDAS Connector
-           \end{enumerate}
 
-     \item List of requirements regarding the EA
-           \begin{enumerate}
-                \item Access to architecture and data bricks
-           \end{enumerate}
+\chapter{Enterprise Architectures}
 
-     \item List of requirements regarding the integration Architecture
-           \begin{enumerate}
-                \item Format of data
-                \item Order of delivery
-                \item Time relevance of data
-                \item Guaranteed delivery of data
-           \end{enumerate}
+\section{Modeling of the real world}
 
-\end{enumerate}
+\section{Modeling Challenges}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\section{Enterprise Architecture Patterns (EAP)}
+
+\chapter{Relevant Systems and Data}
+
+\section{EAPs}
+
+\section{Architecture Bricks}
+
+\section{Data Bricks}
+
+\section{Integration Requirements}
+
+\subsection{Regarding Integration Architecture}
+
+\subsection{Regarding Business Connector}
+
+\chapter{Integration}
+
+\section{Definition}
+
+\section{Requirements}
+
+\subsection{Loose Coupling}
+
+\subsection{Homogeneous Landscapes}
+
+\section{Enterprise Integration Patterns (EIP)}
+
+\subsection{Pattern 1}
+
+\subsection{Pattern 2}
+
+\chapter{Business Connector}
+
+\section{Functionalities and Interfaces}
+
+\section{Integration Requirements}
+
+\subsection{Regarding Enterprise Architecture}
+
+\subsection{Regarding Integration Architecture}
+
+\section{Documentation}
+
+\subsection{Connector as Architecture Brick}
 
@@
 
-\section{Overview}
+\section{Scenario 1}
 
-\section{Requirements}
+\subsection{Integration Documentation}
 
-\begin{enumerate}
-     \item Requirements of Enterprise Architecture
-     \item Requirements of Business Connector
-     \item Requirements of Integration System
-\end{enumerate}
+\subsection{System Integration}
 
-\subsection{Requirements of Enterprise Architecture}
+\subsection{Data Integration}
 
-\subsection{Requirements of Business Connector}
+\section{Scenario 2}
 
-\subsection{Requirements of Integration System}
+\subsection{Integration Documentation}
 
-\section{Scenario Integrations}
-\begin{enumerate}
-     \item Look at integration architecture for each CSS-Scenario
-\end{enumerate}
+\subsection{System Integration}
 
-\subsection{Integration Architecture Documentation Method}
-\begin{enumerate}
-     \item Entity Diagram(s)
-     \item Flow Diagram(s)
-     \item etc.
-\end{enumerate}
+\subsection{Data Integration}
 
-\subsection{Scenario1}
-\begin{enumerate}
-     \item Description of Scenario
-\end{enumerate}
+\chapter{Integration Architecture Evaluation}
 
-\subsubsection{Scenario1 Integration Architecture}
-\begin{enumerate}
-     \item Entity Diagram(s)
-     \item Flow Diagram(s)
-     \item etc.
-\end{enumerate}
+\section{Technology}
 
-\subsubsection{System Integration}
-\begin{enumerate}
-     \item Explanation how the systems are integrated
-     \item Why was each pattern used?
-     \item How are requirements met?
-\end{enumerate}
+\section{Customer Example}
 
-\subsubsection{Data Integration}
-\begin{enumerate}
-     \item Explanation how the data objects are integrated
-     \item Why was data transformed / mapped?
-     \item How are requirements met
-\end{enumerate}
-
-\subsection{Scenario2}
-
-\subsubsection{Scenario2 Integration Architecture}
-
-\subsubsection{System Integration}
-
-\subsubsection{Data Integration}
-
-\chapter{Evaluation}
-
-\section{Technological Evaluation}
-
-\subsection{Available Messaging Technologies}
-
-\subsection{Implementation of Integration Architecture}
-
-\subsection{Evaluation of result}
-
-\section{Experimental Evaluation}
-
-\subsection{Customer Example}
-
-\subsection{Application of Integration Architecture}
-
-\subsection{Evaluation of result}
-
-\section{Operation Manual}
-\begin{enumerate}
-     \item Guide on how to implement and deploy the integration architecture
-     \item incorporates results of previous evaluations
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Summary and outlook}
-
-% References (Literaturverzeichnis):
-% a) Style (with abbreviations: use alpha):
-% see
-% https://de.wikibooks.org/wiki/LaTeX-W%C3%B6rterbuch:_bibliographystyle
-% for the different formats and styles
+\section{Operating Manual}
 
 \bibliographystyle{apalike}
-% b) The File:
 \bibliography{references}

### 2020-10-24 thesis/msc-thesis.tex
minor changes

@@
 % Modifications for the database systems research group
-% were made by Conny Junghans,  Jannik Strötgen and Michael Gertz
+% were made by Conny Junghans,  Jannik Strï¿½tgen and Michael Gertz
 
@@
 
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+
+\usepackage{color,soul}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{document}
+
+\listoftodos
 
@@
 \chapter{Context}
+\todo[inline, caption={Expand Context Chapter}]{Add more content to this chapter}
 
-The german ministry of economy and energy recognizes that "we have long since arrived in a digitized world". This realization 
-of the german government comes along with important federal and european legislation. Most prominent are DSGVO, OZG and DVG, 
-modernizing data protection, governmental administration and health care.
+Digital customer self-service (DCSS) is a great tool for improving customer experience and reducing cost. Many enterprises therefore heavily
+rely on it for main business services. Especially recent governmental regulations like "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung"
+(DSGVO) and "Digitale Versorgung Gesetz" (DVG) have increased requirements for DCSS capabilities.
 
-Enterprises, organizations and authorities are required to provide additional digital services for its customers and users.
-Those include for example the deletion of non-mandatory data and the digital application for unemployment benefit.
+DCSS is made available through DCSS providers. They can consist of websites and applications developed in self-work or be 
+services provided by separate companies.
 
-Working with existing system- and data architectures, integration of new solutions is necessary.
+Adding DCSS to a system architecture is a common task. It usually involves integration of new DCSS components
+into an existing system architecture. Due to the complicated nature of system architectures, integration proves to be a difficult
+task.
 
-\chapter{Objectives}
+\chapter{Objective}
 
-This bachelor thesis describes digital self-service as a solution for the additional requirements. It explains the basis of what 
-customer self-service (CSS) is, what relevant legislation is about and how CSS providers can help in the digital transformation.
+\todo[inline, caption={Expand Objectives Chapter}]{Add more content to this chapter}
 
-The technological challenge of integrating CSS providers into existing system architectures is focus of this bachelor thesis.
-An integration architecture is presented, which provides solutions for the following questions (ToDo: In Textform schreiben):
+The objective of this bachelor thesis is to improve the capability of enterprises and organizations to integrate DCSS providers.
+The thesis explains the basis of what DCSS and its providers are, which relevant scenarios exist and how DCSS providers can help
+in the digital transformation.
 
-\begin{enumerate}
-     \item How can services of a CSS provider be accessed by the enterprise architecture?
-     \item Which systems of a typical enterprise architecture are required?
-     \item Which data objects of a typical enterprise architecture are required?
-     \item Which additional systems and data objects are required?
-     \item How can heterogeneous enterprise architectures be integrated the same way?
-     \item How can the integration be non-invasive?
-     \item How can the speed of integration development be increased?
-     \item How can the speed of integration deployment be increased?
-     \item How can the integration system be reliable and maintainable?
-\end{enumerate}
+The technological challenge of integrating DCSS providers into existing system architectures is focus of this bachelor thesis.
 
-The architecture is evaluated in respect to technological feasibility and real-life applicability. The results are incorporated into 
-an operating manual, providing guidance in developing and deploying the presented integration architecture.
+Based on scenarios resulting from governmental regulations (due to their current relevance), an integration architecture is presented, which describes
+their integration. It provides information on which type of systems and data objects an existing
+architecture requires. It models how CSS providers and system architectures can communicate -
+deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
+heterogeneous system architectures, be non-invasive and reliable.
+
+The integration architecture is evaluated in respect to technological feasibility and real-life applicability. The results are
+incorporated into an operating manual, providing guidance in developing and deploying the presented integration architecture.
 
@@
 
-\chapter{Customer Self-Service (CSS)}
+\todo[inline, caption={Write Structure of Work Chapter}]{Briefly explain each chapter and their relationships}
 
-\section{Definition}
+\chapter{Digital Customer Self-Service (DCSS)}
 
-\section{Description}
+\todo[inline, caption={Expand DCSS Chapter}]{Add more content to this chapter}
 
-\section{Benefits}
+This chapter introduces the concept of digital customer self-service. It defines DCSS, describes what it is by usage of examples and mentions benefits such as challenges.
 
-\subsection{Customer}
+\textbf{Definition}: Digital self-service is the consumption of services provided by an enterprise over the internet without human to human interaction.
 
-\subsection{Organization}
+It is important to distinguish between "service" and "self-service". The difference is shown through two examples:
 
-\section{Examples}
+\textbf{Example 1}: A service is the availability to purchase items whereas digital self-service is the order placement over a website.
+
+\textbf{Example 2}: A service is the availability of video on demand whereas digital self-service is the access of video files over a website.
+
+Digital self-service is one of many possible ways to access a service: An order placement could also be done through email
+or phone call and access to videos could be granted through same-day-delivery of DVDs.
+
+Customers are able to do self-service because companies provide them with self-service tools. Creating them is not trivial
+and is the main business model of many companies. Video on demand websites for example do not only flourish as a result of providing access to
+videos (this business model existed long before them) but as a result of the digital self-service tools they provide.
+
+Reasons for the widespread usage of digital self-service are significant benefits in ease of service usability for customers and cost reduction for enterprises.
+Customers can self-service from almost every place, easily manage customer data like phone number and address, configure services like subscription plans and
+access lots of information on available products or trouble shooting steps in an immediate way.
+Digital customer self-service improves usability, saves time, increases availability, saves money and therefore increases customer experience
+\cite[cf. 243]{CSSInternetAge}.
+Enterprises, especially in progressive countries, aim to keep employment at a minimum, as it is a big cost factor. Digital self-service turns customers into
+unpaid employees \cite{served}.
+
+Decreasing employment cost while increasing customer experience sounds like a win-win situation. Sadly, digital self-service does have its downsides.
+One downside is most immediate to the elderly. In order to use DCSS, computers have to be available and one has to be experienced in their usage.
+Technological complexity, however, is not only a problem for customers but also for enterprises providing DCSS. Based on existing system architectures,
+adding DCSS functionalities can turn out to be a difficult task. Some form of integration is often necessary. With increased system complexity and business
+dependability come additional maintenance cost.
+
+As tody most large enterprises provide DCSS, it can be assumed, that at a given size of an enterprise (measured in number of customers), the benefits of DCSS
+surpass its disadvantages.
+
+Governments see digitalization as a chance for improvements in many important social and economical areas\todo{references}. The process of digitalization can in
+some cases be described as reinventing existing solutions for usability with computers. One of the goals is to make solutions more easily accessible for users and as a 
+method, provide digital self-service. Governmental regulations relating to digitalization therefore often encourage or demand enterprises and organizations to 
+provide DCSS.
 
@@
 
-\section{Purpose}
-
-\section{Importance for Organizations}
+\todo[inline, caption={Research Governmental Regulations Chapter}]{Explain the three regulations in general, what their purpose is what their challenges are}
 
@@
 
-\section{Challenges for Organizations}
+\chapter{DCSS Providers}
 
-\chapter{Compliance through CSS}
-
-\section{Description}
-
-\section{CSS-Scenarios}
-
-\section{Requirements}
-
-\chapter{CSS Providers}
+\todo[inline, caption={Write CSS Providers Chapter}]{Explain what CSS Providers are (what services they can provide -> what IDAS does) and how they can help creating DCSS.
+     Also explain the concept of a business connector as technological communication point of the CSS provider}
 
@@
 
+\chapter{DCSS Scenarios}
+
+\todo[inline, caption={Research DCSS Scenarios Chapter}]{
+     \begin{enumerate}
+          \item Should governmental regulations be the focus of scenarios? => good resources for OZG
+     \end{enumerate}
+}
+
+Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
+\cite{ozgScenarios}), DSGVO scenarios (textual description available \cite{dsgvo}) and DVG scenarios
+(textual desciption available \cite{gematik-e-rezept})
+\\\\
+The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
+and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:
+
+\begin{enumerate}
+     \item What part of a scenario is digital?
+     \item What part of a scenario can be done through a DCSS provider / is relevant for DCSS?
+     \item What part of a scenario is done through \textbf{existing} business systems?
+           \begin{enumerate}
+                \item new necessary business logic part of (configurable) integration? => non invasive
+           \end{enumerate}
+     \item What part of a scenario should be done by the integration architecture?
+     \item What are commonalities of scenarios?
+           \begin{enumerate}
+                \item OZG scenarios often describe digital handling of applications
+                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system architecture with the problem of distributed
+                      data and functionality which the integration architecture would solve.
+           \end{enumerate}
+\end{enumerate}
+
+\section{OZG}
+
+\subsection{Unemployment Benefit (AG2)}
+\textbf{Available Resources}
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\subsection{Training Promotion (BAfï¿½G)}
+\textbf{Available Resources}
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\subsection{Drivers License}
+\textbf{Available Resources}
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\subsection{Company Registration and Approval}
+\textbf{Available Resources}
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\subsection{Visa Issuance}
+\textbf{Available Resources}
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+\end{itemize}
+
+\section{DSGVO}
+
+The DSGVO influences DCSS by regulating how digitally collected personal information (which is common in DCSS) has to be managed. This means, DCSS providers have to 
+keep this regulation in mind when designing their solutions. It has implications on integration in that DSGVO compliance requires special management of data, 
+which an integration system has to make possible (DCSS providers use it).
+
+It has to be analyzed in regard to:
+\begin{enumerate}
+     \item Which parts of the regulation describe requirements for features of DCSS providers
+     \item Which parts of the regulation describe requirements for integrations
+\end{enumerate}
+
+\subsection{Transparent Accessability}
+The enterprise or organization can have the duty to make information about personal data accessible in transparent and understandable ways
+
+\subsection{Deletion of Personal Data}
+The user can have the right of removal of personal data
+
+\subsection{Correction of Personal Data}
+The user can have the right of modification of personal data.
+
+\subsection{Information about collected Personal Data}
+The user can have the right to be informed about various information of collected and stored personal data such as usage, duration of storage, ...
+
+\subsection{Restriction of Processing}
+The user can have the right to restrict the way in which personal data is processed
+
+\subsection{Availability of Transferral of Personal Data}
+The user can have the right to transfer personal data to himself or separate entities (company, organization).
+
+\section{DVG}
+
+\subsection{e-Prescription}
+Reference can be found in the "Ärzteblatt" \cite{Ärzteblatt}.
+\\\\
+The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
+which can digitally be used in pharmacies also without physically being there.
+\\\\
+Regulation: "Gesetz für mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
+\\\\
+e-Prescription processes \cite{gematik-e-rezept}
+\begin{enumerate}
+     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
+     \item Prescription is saved on "Telematikinfrastruktur"
+     \item Doctor displays a QR-Code (prescription-token)
+     \item Patient can receive QR-Code in App (or get a printout)
+     \item Patient can check availability of drug in pharmacies via the app
+     \item Patient can "apply" the prescription to a pharmacy via the app
+     \item prescription is now irrevocably bound to the pharmacy and gets reserved
+     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
+     \item pharmacy notifies patient if or when the drug is available
+     \item drug can be picked up by patient or be delivered
+     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
+     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
+     \item pharmacy gives drug if validated
+\end{enumerate}
+~\\
+Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
+\\\\
+What are services and what are self-services in this scenario:
+\begin{itemize}
+     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
+     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
+           to pharmacy and digital instruction of delivery of drug
+\end{itemize}
+
+\section{PSD2}
+
+The regulation is about how digital payment self-service providers have to function. This includes their communication / integration\cite{psd2Summary}.
+\\\\
+Full law at \cite{psd2}
+\\\\
+Regulation: "Payment Services Directive 2" (PSD2) (European law)
+\\\\
+What are services and what are self-services in this scenario:
+\begin{itemize}
+     \item Service: Payments and transfers. Self-service: Payment services are DCSS providers and offer digital execution of payments and transfers
+\end{itemize}
+~\\
+The regulation has to be analyzed regarding:
+\begin{enumerate}
+     \item Which parts of the regulation describe required features of the self-service provider
+     \item Which parts of the regulation describe requirements for integration
+\end{enumerate}
+
+\section{Requirements}
+
 \chapter{Enterprise Architectures}
+
+\todo[inline, caption={Write Enterprise Architectures Chapter}]{Introduce Enterprise Architectures and challenges such as heterogeneous systems when trying to model them}
+
+\begin{enumerate}
+     \item Heterogeneous Enterprise Architecture Systems
+           \begin{enumerate}
+                \item Different Applications
+                \item Different Application Vendors
+                \item Different / No Application Interfaces
+                \item Legacy Systems
+           \end{enumerate}
+     \item Different (proprietary) data models within and between Enterprises and Organizations
+           \begin{enumerate}
+                \item Different (property)name for same data objects (syntactic integration)
+                \item Different meanings for same (property)name (semantic integration)
+           \end{enumerate}
+\end{enumerate}
 
@@
 \chapter{Relevant Systems and Data}
+
+\todo[inline, caption={Research Relevant Systems and Data Chapter}]{Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs.
+     Analyze which system and data bricks of the system architecture could be necessarry for DCSS}
 
@@
 \chapter{Integration}
+
+\todo[inline, caption={Write Integration Chapter}]{Introduce the concept of integration. What are challenges in general and what would be an ideal integration.
+     Also explain the approach towards integration used (messaging, patterns)}
+
+\begin{enumerate}
+     \item Scarce Resources
+           \begin{enumerate}
+                \item Integration Development Speed
+                      \begin{enumerate}
+                           \item Necessary Development <=> Reuse of existing Technology
+                           \item Complexity / Size of Integration
+                      \end{enumerate}
+                \item Maintenance of finished Integration
+                \item Hardware / Software Costs of Integration
+                      \begin{enumerate}
+                           \item Licenses for Software
+                           \item Scalability of Integration => Necessary Computing Power
+                      \end{enumerate}
+                \item Messaging Integration
+                      \begin{enumerate}
+                           \item Loose Coupling
+                                 \begin{enumerate}
+                                      \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
+                                      \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
+                                      \item Loose Coupling allows Reuse of "Modules" => faster development
+                                 \end{enumerate}
+                           \item Messaging enables communication with many systems through Adapters
+                           \item Stability of Integration
+                                 \begin{enumerate}
+                                      \item Future Changes of EA
+                                      \item Scalability
+                                      \item Failure of EA or Integration Components
+                                 \end{enumerate}
+                           \item Messaging provides mechanisms for Stability
+                                 \begin{enumerate}
+                                      \item Store-and-Forward
+                                      \item Load Balancing
+                                 \end{enumerate}
+                      \end{enumerate}
+                \item Integration Patterns
+                      \begin{enumerate}
+                           \item Patterns speed up construction of Integration Architecture
+                           \item Patterns are proven solutions
+                           \item Patterns abstract from concrete technologies
+                                 \begin{enumerate}
+                                      \item Simplifies understanding of integration concept
+                                      \item Allows implementation with different technologies
+                                 \end{enumerate}
+                      \end{enumerate}
+           \end{enumerate}
+\end{enumerate}
 
@@
 
+\todo[inline, caption={Research Business Connector Chapter}]{Construct the model of the business connector}
+
 \section{Functionalities and Interfaces}
@@
 
+\todo[inline, caption={Integration Architecture Chapter}]{Create the integration architecture}
+
 \section{Scenario 1}
@@
 \subsection{Integration Documentation}
+
+\subsection{Required System and Data Bricks}
 

### 2020-10-25 thesis/msc-thesis.tex
codespaces

@@
 %     idxtotoc,     % index in toc
-%     parskip       % paragraph skip instad of paragraph indent
+%     parskip       % p
+aragraph skip instad of paragraph indent
      ]{scrreprt}
@@
 
-\subsection{Training Promotion (BAfï¿½G)}
+\subsection{Training Promotion (BAföG)}
 \textbf{Available Resources}
@@
 \subsection{e-Prescription}
-Reference can be found in the "Ärzteblatt" \cite{Ärzteblatt}.
+Reference can be found in the "rzteblatt" \cite{Ärzteblatt}.
 \\\\
@@
 \\\\
-Regulation: "Gesetz für mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
+Regulation: "Gesetz fï¿½r mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
 \\\\

### 2020-10-26 thesis/__latexindent_temp.tex
Update index

--- 2020-10-25 thesis/msc-thesis.tex
@@
 
-\chapter{Digital Customer Self-Service (DCSS)}
+\chapter{Basis}
+
+\section{Digital Customer Self-Service (DCSS)}
 
@@
 
-\chapter{Governmental Regulations}
+\section{OZG}
 
@@
 
-\section{DSGVO}
-
-\section{OZG}
-
-\section{DVG}
-
-\chapter{DCSS Providers}
+\section{DCSS Provider}
 
@@
 
-\section{Description}
+\subsection{Description}
 
-\section{CSS Solutions}
+\subsection{CSS Solutions}
 
-\section{Business Connector}
+\subsection{Business Connector}
 
-\chapter{DCSS Scenarios}
-
-\todo[inline, caption={Research DCSS Scenarios Chapter}]{
-     \begin{enumerate}
-          \item Should governmental regulations be the focus of scenarios? => good resources for OZG
-     \end{enumerate}
-}
-
-Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
-\cite{ozgScenarios}), DSGVO scenarios (textual description available \cite{dsgvo}) and DVG scenarios
-(textual desciption available \cite{gematik-e-rezept})
-\\\\
-The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
-and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:
-
-\begin{enumerate}
-     \item What part of a scenario is digital?
-     \item What part of a scenario can be done through a DCSS provider / is relevant for DCSS?
-     \item What part of a scenario is done through \textbf{existing} business systems?
-           \begin{enumerate}
-                \item new necessary business logic part of (configurable) integration? => non invasive
-           \end{enumerate}
-     \item What part of a scenario should be done by the integration architecture?
-     \item What are commonalities of scenarios?
-           \begin{enumerate}
-                \item OZG scenarios often describe digital handling of applications
-                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system architecture with the problem of distributed
-                      data and functionality which the integration architecture would solve.
-           \end{enumerate}
-\end{enumerate}
-
-\section{OZG}
-
-\subsection{Unemployment Benefit (AG2)}
-\textbf{Available Resources}
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Process Diagram of Application
-     \item Click-Dummy
-\end{itemize}
-
-\subsection{Training Promotion (BAföG)}
-\textbf{Available Resources}
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Click-Dummy
-\end{itemize}
-
-\subsection{Drivers License}
-\textbf{Available Resources}
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Process Diagram of Application
-     \item Click-Dummy
-\end{itemize}
-
-\subsection{Company Registration and Approval}
-\textbf{Available Resources}
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Click-Dummy
-\end{itemize}
-
-\subsection{Visa Issuance}
-\textbf{Available Resources}
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-\end{itemize}
-
-\section{DSGVO}
-
-The DSGVO influences DCSS by regulating how digitally collected personal information (which is common in DCSS) has to be managed. This means, DCSS providers have to 
-keep this regulation in mind when designing their solutions. It has implications on integration in that DSGVO compliance requires special management of data, 
-which an integration system has to make possible (DCSS providers use it).
-
-It has to be analyzed in regard to:
-\begin{enumerate}
-     \item Which parts of the regulation describe requirements for features of DCSS providers
-     \item Which parts of the regulation describe requirements for integrations
-\end{enumerate}
-
-\subsection{Transparent Accessability}
-The enterprise or organization can have the duty to make information about personal data accessible in transparent and understandable ways
-
-\subsection{Deletion of Personal Data}
-The user can have the right of removal of personal data
-
-\subsection{Correction of Personal Data}
-The user can have the right of modification of personal data.
-
-\subsection{Information about collected Personal Data}
-The user can have the right to be informed about various information of collected and stored personal data such as usage, duration of storage, ...
-
-\subsection{Restriction of Processing}
-The user can have the right to restrict the way in which personal data is processed
-
-\subsection{Availability of Transferral of Personal Data}
-The user can have the right to transfer personal data to himself or separate entities (company, organization).
-
-\section{DVG}
-
-\subsection{e-Prescription}
-Reference can be found in the "rzteblatt" \cite{Ärzteblatt}.
-\\\\
-The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
-which can digitally be used in pharmacies also without physically being there.
-\\\\
-Regulation: "Gesetz fï¿½r mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
-\\\\
-e-Prescription processes \cite{gematik-e-rezept}
-\begin{enumerate}
-     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
-     \item Prescription is saved on "Telematikinfrastruktur"
-     \item Doctor displays a QR-Code (prescription-token)
-     \item Patient can receive QR-Code in App (or get a printout)
-     \item Patient can check availability of drug in pharmacies via the app
-     \item Patient can "apply" the prescription to a pharmacy via the app
-     \item prescription is now irrevocably bound to the pharmacy and gets reserved
-     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
-     \item pharmacy notifies patient if or when the drug is available
-     \item drug can be picked up by patient or be delivered
-     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
-     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
-     \item pharmacy gives drug if validated
-\end{enumerate}
-~\\
-Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
-\\\\
-What are services and what are self-services in this scenario:
-\begin{itemize}
-     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
-     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
-           to pharmacy and digital instruction of delivery of drug
-\end{itemize}
-
-\section{PSD2}
-
-The regulation is about how digital payment self-service providers have to function. This includes their communication / integration\cite{psd2Summary}.
-\\\\
-Full law at \cite{psd2}
-\\\\
-Regulation: "Payment Services Directive 2" (PSD2) (European law)
-\\\\
-What are services and what are self-services in this scenario:
-\begin{itemize}
-     \item Service: Payments and transfers. Self-service: Payment services are DCSS providers and offer digital execution of payments and transfers
-\end{itemize}
-~\\
-The regulation has to be analyzed regarding:
-\begin{enumerate}
-     \item Which parts of the regulation describe required features of the self-service provider
-     \item Which parts of the regulation describe requirements for integration
-\end{enumerate}
-
-\section{Requirements}
-
-\chapter{Enterprise Architectures}
+\section{Enterprise Architecture}
 
@@
 
-\section{Modeling of the real world}
+\subsection{Modeling of the real world}
 
-\section{Modeling Challenges}
+\subsection{Modeling Challenges}
 
-\section{Enterprise Architecture Patterns (EAP)}
+\subsection{Enterprise Architecture Patterns (EAP)}
 
-\chapter{Relevant Systems and Data}
-
-\todo[inline, caption={Research Relevant Systems and Data Chapter}]{Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs.
-     Analyze which system and data bricks of the system architecture could be necessarry for DCSS}
-
-\section{EAPs}
-
-\section{Architecture Bricks}
-
-\section{Data Bricks}
-
-\section{Integration Requirements}
-
-\subsection{Regarding Integration Architecture}
-
-\subsection{Regarding Business Connector}
-
-\chapter{Integration}
+\section{Integration}
 
@@
 
-\section{Definition}
+\subsection{Definition}
 
-\section{Requirements}
+\subsection{Requirements}
 
-\subsection{Loose Coupling}
+\subsubsection{Loose Coupling}
 
-\subsection{Homogeneous Landscapes}
+\subsubsection{Homogeneous Landscapes}
 
-\section{Enterprise Integration Patterns (EIP)}
+\chapter{Preparatory Work}
 
-\subsection{Pattern 1}
+\section{OZG Scenarios}
 
-\subsection{Pattern 2}
+\todo[inline, caption={Research DCSS Scenarios Chapter}]{
+     \begin{enumerate}
+          \item Should governmental regulations be the focus of scenarios? => good resources for OZG
+     \end{enumerate}
+}
 
-\chapter{Business Connector}
+Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
+\cite{ozgScenarios}), DSGVO scenarios (textual description available \cite{dsgvo}) and DVG scenarios
+(textual desciption available \cite{gematik-e-rezept})
+\\\\
+The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
+and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:
+
+\begin{enumerate}
+     \item What part of a scenario is digital?
+     \item What part of a scenario can be done through a DCSS provider / is relevant for DCSS?
+     \item What part of a scenario is done through \textbf{existing} business systems?
+           \begin{enumerate}
+                \item new necessary business logic part of (configurable) integration? => non invasive
+           \end{enumerate}
+     \item What part of a scenario should be done by the integration architecture?
+     \item What are commonalities of scenarios?
+           \begin{enumerate}
+                \item OZG scenarios often describe digital handling of applications
+                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system architecture with the problem of distributed
+                      data and functionality which the integration architecture would solve.
+           \end{enumerate}
+\end{enumerate}
+
+\begin{itemize}
+     \item Unemployment Benefit (AG2)
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\item Training Promotion (BAföG)
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\item Drivers License
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\item Company Registration and Approval
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\item Visa Issuance
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+\end{itemize}
+
+\end{itemize}
+
+\section{Relevant Systems and Data}
+
+\todo[inline, caption={Research Relevant Systems and Data Chapter}]{Explain the approach of modeling enterprise architectures by EAPs and explain the used EAPs.
+     Analyze which system and data bricks of the system architecture could be necessarry for DCSS}
+
+\subsection{EAPs}
+
+\subsection{Architecture Bricks}
+
+\subsection{Data Bricks}
+
+\subsection{Integration Requirements}
+
+\subsubsection{Regarding Integration Architecture}
+
+\subsubsection{Regarding Business Connector}
+
+\section{Business Connector}
 
@@
 
-\section{Functionalities and Interfaces}
+\subsection{Functionalities and Interfaces}
 
-\section{Integration Requirements}
+\subsection{Integration Requirements}
 
-\subsection{Regarding Enterprise Architecture}
+\subsubsection{Regarding Enterprise Architecture}
 
-\subsection{Regarding Integration Architecture}
+\subsubsection{Regarding Integration Architecture}
 
-\section{Documentation}
+\subsection{Documentation}
 
-\subsection{Connector as Architecture Brick}
+\subsubsection{Connector as Architecture Brick}
 

### 2020-11-10 expose/main.tex
Add Whitepaper and resources

@@
 
-\title{Messaging Architecture for Integration of Customer Self Services \\ Version 0.2}
+\title{Messaging Architecture for Integration of Customer Self-Services}
 \author{Jonas Gann}
-\date{28 September 2020}
+\date{29 September 2020}
 
@@
 \section{Context}
-As a result of the 2020 pandemic, customer self-service (CSS) technologies reached a new level of importance \cite{covid}.
+As a result of the 2020 COVID-19 pandemic, customer self-service (CSS) technologies reached a new level of importance.
 Many shops were closed due to government measurements and customers had to use their web
-presences. CSS is a useful method to handle support for an increasing number of online customers. It enables them to search 
-for contract data, change profile information, track shipment and much more without the need of human to human interaction.
-This reduces cost and increases customer performance.
+presences. CSS is a useful method to handle support for an increasing number of online customers. It enables searching
+for contract data, changing profile information, tracking shipment and much more without the need of human to human interaction.
+This reduces cost and increases customer performance \cite{covid}.
 
@@
 
-Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector.
+The integration also has to perform according to requirements of both the EA and the CSS business connector.
 
 As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
-relating to reliability e.g. scalability, failure safety have to be considered.
+relating to reliability like scalability and failure safety have to be considered.
 
@@
 
-The bachelor thesis defines a messaging architecture for integration of a CSS connector 
+The bachelor thesis defines a messaging architecture for integration of a business connector, providing an interface for CSS,  
 into enterprise architectures. This simplifies and speeds up integration by providing a solution reusable in many 
-different scenarios. A messaging approach enables deployment on different heterogeneous landscapes through 
+different scenarios.
+
+A messaging approach enables deployment on different heterogeneous landscapes through 
 loose coupling. Loose coupling allows integrated systems to not make assumptions about each other and use a 
@@
 
-Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.
+Mechanisms increasing reliability of message communication through for example load balancing and store-and-forward are part of the 
+messaging approach.
 
@@
 \textbf{CSS scenarios} get compiled from multiple resources in order to describe, what CSS looks like in practice.
-A scenario might e.g. be "New Address": User wants to change the address in his profile.
+A scenario might be "New Address: User wants to change the address in his profile".
 
@@
 
-\textbf{Business processes} relevant for the CSS scenarios get selected from EAPs. Relevance means, that the process 
-is part of or related to the scenario.
-This can e.g. be "Change Address": Login, Edit Profile, Change Address, Save Changes
+\textbf{Business processes} relevant for the CSS scenarios get selected from EAPs. A process is relevant if he
+is part of or related to a scenario and can be "Change Address: Login, Edit Profile, Change Address, Save Changes"
 
@@
 for the process. They make up the enterprise architecture. Requirements of the EA 
-regarding the consumption of CSS get analyzed. One requirement could e.g. be, that access to 
+regarding the consumption of CSS get analyzed. One requirement could be, that access to 
 the "New Address" CSS scenario is required via a web server architecture brick. Another requirement might be, 
@@
 
-\textbf{The business connector} is constructed - based on CSS scenarios - as a black box of requirements regarding 
-the access to EA systems and data objects. The black box also contains interfaces, which provide functionalities for CSS 
-scenarios. It is not be included, how the business 
+The \textbf{business connector} is constructed - based on CSS scenarios - as a black box of requirements regarding 
+the access to EA systems and data objects. The black box also contains interfaces which provide functionalities for CSS 
+scenarios. It is not included, how the business 
 connector processes received data, triggers instructions to the EA or implements a service.
-The business connector could e.g. consist of the requirements: access to identities, access to identity validation, 
+The business connector could consist of the requirements: access to identities, access to identity validation, 
 access to profile data and of the interface "changeIdentityProfileProperty"
 
-\textbf{An integration architecture} gets defined, which utilizes the selected business processes, architecture 
+An \textbf{integration architecture} gets defined which utilizes the selected business processes, architecture 
 bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
@@
 Requirements relating to the internal data and instruction delivery of the integration architecture 
-like e.g. scalability and fail safety get considered in addition.
+like scalability and fail safety get considered in addition.
 Architecture bricks and data objects used in the final form of the 
@@
 
-\textbf{A messaging approach} based on enterprise integration patterns described
+A \textbf{messaging approach} based on enterprise integration patterns described
 by \textcite{integrationPatterns} is used for the integration architecture.
@@
 \textbf{Technologies} which can be used for implementation get evaluated for the final form of the integration architecture.
-These can e.g. be different message oriented middlewares used for implementing messaging systems in general.
+These can be different message oriented middlewares used for implementing messaging systems in general.
 
-\textbf{An operation manual} with the purpose of guiding the requirement analysis in respect to existing architecture bricks and data 
+An \textbf{operation manual} with the purpose of guiding the requirement analysis in respect to existing architecture bricks and data 
 objects of the EA and helping with theoretical and practical deployment of the integration architecture gets constructed.
-It might e.g. help finding architecture bricks required by the integration architecture inside the EA 
+It might help finding architecture bricks required by the integration architecture inside the EA 
 and instruct on how to implement the integration architecture in practice.
 
-\textbf{A validation} of results is done through a customer example. For given 
+A \textbf{validation} of results is done through a real life example. For given 
 EA, business processes, business connector and customer specific requirements, the integration architecture gets 
@@
 
-\section{Related Work}
-
-\begin{itemize}
-    \item "Enterprise Architecture Patterns" \cite{architecturePatterns}: This book presents how to construct and use so 
-    called enterprise architecture patterns and documents 13 common examples. 
-    \item "Enterprise Integration Patterns" \cite{integrationPatterns}: This book documents fundamental messaging patterns, 
-    which can be used for integration purposes.
-\end{itemize}
-
 \section{Milestones}
 
-The bachelor thesis is planned to be officially registered in November and finished in February.
+The bachelor thesis is planned to be officially registered at the beginning of November and finished at the end of February.
 Parallel to the execution of described approaches, relating chapters of the bachelor thesis will be written.

### 2020-11-24 thesis/msc-thesis.tex
Inserted content from Whitepaper OZG

--- 2020-10-15 thesis/msc-thesis.tex
@@
 % Modifications for the database systems research group
-% were made by Conny Junghans,  Jannik Strötgen and Michael Gertz
+% were made by Conny Junghans,  Jannik Strtgen and Michael Gertz
 
@@
      a4paper,      % paper format
-     BCOR10mm,     % binding correction
-     DIV14,        % stripe size for margin calculation
+     BCOR=10mm,version=first,     % binding correction
+     DIV=14,version=first,        % stripe size for margin calculation
 %     liststotoc,   % table listing in toc
@@
 %\usepackage[pdftex, bookmarks=true]{hyperref}
+\usepackage{csquotes}
 
@@
 \newcommand{\setlang}[1]{\selectlanguage{#1}\nonfrenchspacing}
+
+\usepackage{biblatex}
+\addbibresource{references.bib}
 
@@
 \noindent
-I assure that I have written this bachelor thesis on my own and only used the specified sources and
-resources and that I followed the principles and recommendations "Responsibility in Science" of the
-University of Heidelberg.
+I assure that I have written this bachelor thesis on my own and only used the specified sources and resources and that I followed the principles and recommendations "Responsibility in Science" of the University of Heidelberg.
 
@@
 
-The german ministry of economy and energy recognizes that "we have long since arrived in a digitized world". This realization 
-of the german government comes along with important federal and european legislation. Most prominent are DSGVO, OZG and DVG, 
-modernizing data protection, governmental administration and health care.
+Many enterprises provide digital tools which improve service usability for their customers.
+For example: If somebody wants to watch a movie, he does not drive to the nearest store to buy a DVD but instead uses websites providing video on demand (VoD).
+The reason is: VoD enterprises provide tools for digital customer self-service (DCSS).
+A customer can easily access the video over a website on his own.
+Technologies for DCSS becomes increasingly relevant, as the German government introduced requirements for DCSS in recent regulations.
+Most prominent are  "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung" (DSGVO) and "Digitale Versorgung Gesetz" (DVG).
 
-Enterprises, organizations and authorities are required to provide additional digital services for its customers and users.
-Those include for example the deletion of non-mandatory data and the digital application for unemployment benefit.
+DCSS is made available through DCSS providers.
+They can consist of websites and applications developed in self-work or be services provided by separate companies.
+Adding DCSS providers to a system architecture is a common task.
+It usually involves integration of new DCSS components into an existing system architecture.
+Due to the complicated nature of system architectures, integration proves to be a difficult task.
 
-Working with existing system- and data architectures, integration of new solutions is necessary.
+\chapter{Objective}
 
-\chapter{Objectives}
-
-This bachelor thesis describes digital self-service as a solution for the additional requirements. It explains the basis of what 
-customer self-service (CSS) is, what relevant legislation is about and how CSS providers can help in the digital transformation.
-
-The technological challenge of integrating CSS providers into existing system architectures is focus of this bachelor thesis.
-An integration architecture is presented, which provides solutions for the following questions (ToDo: In Textform schreiben):
-
-\begin{enumerate}
-     \item How can services of a CSS provider be accessed by the enterprise architecture?
-     \item Which systems of a typical enterprise architecture are required?
-     \item Which data objects of a typical enterprise architecture are required?
-     \item Which additional systems and data objects are required?
-     \item How can heterogeneous enterprise architectures be integrated the same way?
-     \item How can the integration be non-invasive?
-     \item How can the speed of integration development be increased?
-     \item How can the speed of integration deployment be increased?
-     \item How can the integration system be reliable and maintainable?
-\end{enumerate}
-
-The architecture is evaluated in respect to technological feasibility and real-life applicability. The results are incorporated into 
-an operating manual, providing guidance in developing and deploying the presented integration architecture.
+The objective of this bachelor thesis is to improve the capability of enterprises and institutions to integrate DCSS providers.
+The execution of the German "Online Access Law (OZG)" is a good example for modernization efforts through usage of DCSS.
+Due to an incoming deadline of the OZG, integration of DCSS technology in this context gets increasingly relevant.
+The bachelor thesis therefore focuses on the integration of DCSS providers into the technological OZG ecosystem.
+A message based integration architecture is presented which enables system architectures relevant for the OZG to utilize services of DCSS providers.
+However, the integration architecture is constructed to also be applicable in cases not related to the OZG and to be expandable according to requirements of future use cases.
+The integration architecture is evaluated in respect to technological feasibility and real-life applicability.
+The results are incorporated into an operating manual, providing guidance in developing and deploying the presented integration architecture.
 
@@
 
-\chapter{Customer Self-Service (CSS)}
+The first chapter explains what DCSS and its providers are, what system architectures are and how they can be modeled, what the content of the OZG is, how its implementation is planned and how DCSS providers can be utilized and what integration is, why it is necessary and why a message based approach is used.
+The second chapter ...
 
-\section{Definition}
+\chapter{Fundamentals}
 
-\section{Description}
+\section{Digital Customer Self-Service}
+This chapter introduces the concept of digital customer self-service. It defines DCSS, describes what it is by usage of examples and mentions benefits such as challenges.
 
-\section{Benefits}
+\textbf{Definition}: Digital self-service is the consumption of services provided by an enterprise over the internet without human to human interaction.
 
-\subsection{Customer}
+It is important to distinguish between "service" and "self-service". The difference is shown through two examples:
 
-\subsection{Organization}
+\textbf{Example 1}: A service is the availability to purchase items whereas digital self-service is the placement of orders over a website.
 
-\section{Examples}
+\textbf{Example 2}: A service is the availability of video on demand whereas digital self-service is the access of video files over a website.
 
-\chapter{Governmental Regulations}
+Digital self-service is one of many possible ways to access a service: An order placement could also be done through email or phone call and access to videos could be granted through same-day-delivery of DVDs.
 
-\section{Purpose}
+Customers are able to do self-service because companies provide them with self-service tools.
+Creating them is not trivial and is the main business model of many companies.
+Video on demand websites for example do not only flourish as a result of providing access to videos (this business model existed long before them) but as a result of the digital self-service tools they provide.
 
-\section{Importance for Organizations}
+Reasons for the widespread usage of digital self-service are significant benefits in ease of service usability for customers and cost reduction for enterprises.
+Customers can self-service from almost every place, easily manage customer data like phone number and address, configure services like subscription plans and access lots of information on available products or trouble shooting steps in an immediate way.
+Digital customer self-service improves usability, saves time, increases availability, saves money and therefore increases customer experience.
+Enterprises, especially in progressive countries, aim to keep employment at a minimum, as it is a big cost factor. Digital self-service turns customers into unpaid employees.
 
-\section{DSGVO}
+Decreasing employment cost while increasing customer experience sounds like a win-win situation.
+Sadly, digital self-service does have its downsides.
+One downside is most immediate to the elderly.
+In order to use DCSS, computers have to be available and one has to be experienced in their usage.
+Technological complexity, however, is not only a problem for customers but also for enterprises providing DCSS.
+Based on existing system architectures, adding DCSS functionalities can turn out to be a difficult task.
+Some form of integration is often necessary.
+With increased system complexity and business dependability come additional maintenance cost.
+
+As today most large enterprises provide DCSS, it can be assumed, that at a given size of an enterprise (measured in number of customers), the benefits of DCSS surpass its disadvantages.
+
+Governments see digitalization as a chance for improvements in many important social and economical areas.
+The process of digitalization can in some cases be described as reinventing existing solutions for usability with computers.
+One of the goals is to make solutions more easily accessible for users and as a method, provide digital self-service.
+Governmental regulations relating to digitalization therefore often encourage or demand enterprises and organizations to provide DCSS.
+
+\section{Enterprise Architecture}
+
+\subsection{Modeling of the real world}
+
+\subsection{Modeling Challenges}
+
+\subsection{Enterprise Architecture Patterns (EAP)}
+
+\section{Integration}
+
+\subsection{Definition}
+
+\subsection{Requirements}
+
+\subsubsection{Loose Coupling}
+
+\subsubsection{Homogeneous Landscapes}
+
+\section{DCSS Provider}
+
+This chapter introduces digital customer self-service providers. It explains what they are, why they are useful, what services they can provide and what integration challenges can be.
+
+\subsection{Motivation}
+
+As described in the previous chapter, digital customer self-service is a widely used method on the free market to increase customer experience.
+In order for customers to use self-service, respective companies or institutions have to provide necessary tools.
+Depending on the business case, different self-service tools might be used: The local grocery store might simply provide tools for customers to inform themselves about opening hours and available products while e-commerce companies would want to enable users to buy products online.
+Depending on the use case, complexity of technology providing DCSS can be very high.
+Besides enabling DCSS functionality, used technology also needs to adhere to security and data protection standards which can change regularly and between countries.
+As a result, individual companies or institutions would have to invest many resources for development and maintenance of DCSS solutions.
+They could therefore decide to hire DCSS solutions from companies which have specialised in this area.
+
+\subsectio{Description}
+
+- Areas of DCSS: identity, profile, relations, forms, messages, inbox, applications,
+
+\subsectio{Integration}
 
@@
 
-\section{DVG}
+This section introduces the law for improvement of online access of administrative services (Online Access Law - OZG), its origin, purpose and planned realization.
+It explains the relevance of DCSS providers for the implementation of the OZG and where integration is necessary.
 
-\section{Challenges for Organizations}
+\subsection{Context}
 
-\chapter{Compliance through CSS}
+The Federal Ministry of the Interior, Building and Community is, amongst other things, responsible for modernizing public administration \cite{BMI:Moderne_Verwaltung}.
+Current modernization efforts lie in the construction of an E-Government \cite{BMI:Behoerdengaenge}.
+The E-Government-Law in 2013 was an early step increasing internal usage of digital systems in governmental administration.
+This includes for example the usage of digital personal files and scanning of documents for replacement \cite{BMI:E-Government_Gesetz}.
+In 2017 the German government passed the law for improvement of online access to administrative services (OZG) which focuses on usage of administration services by the people \cite{BMI:Onlinezugangsgesetz}.
+Modernization of the administration, however, is not exclusive to Germany as in 2018 the European Parliament and Council decided on a Single Digital Gateway (SDG) providing uniform access to digital administrative governmental services of every European country \cite{BMI:Single_Digital_Gateway}.
 
-\section{Description}
+\subsection{Motivation}
 
-\section{CSS-Scenarios}
+Customers on the free market are used to One-Stop-Shops providing access to services of companies in one digital place.
+Many self-service methods improve the user experience: Customers of e-commerce companies can put products in a digital shopping card, pay with digital money and select a location for delivery.
+In most cases, no direct human to human interaction is required.
+Customers complete the process of ordering in self-service.
+The progress of online self-service usage on the free market is a result of the ongoing digitalization of the world and the competitiveness of the market.
+Today, many customers own personal computers or smartphones and companies providing easy access to their services via online self-service have an advantage in the market.
+Governmental institutions provide administrative services for customers.
+This can for example be an application for child benefit or a new ID card.
+In contrast to the free market, access to administrative services is, in most cases, not available through online self-service.
+Reasons are, that digitalization is expensive and governmental institutions do not have competitors.
+Digitalization of governmental administration could for example enable users to inform themselves about available administrative services and access them over the internet.
+The need to personally appear in offices of an administration would be reduced.
+Communication about questions or required documents could also happen faster, more immediate, and more reliable over the internet than over mail.
+Governmental institutions could reduce bureaucracy through modernization of registries and the once-only principle.
+The German government recognizes the possible improvements and presents, amongst other things, the OZG as a solution. \cite{IT-Planungsrat:Herausforderung}
 
-\section{Requirements}
+\subsection{The OZG}
 
-\chapter{CSS Providers}
+The law for improvement of online access of administrative services (Online Access Law - OZG) passed in 2017 and requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
+\begin{enumerate}
+    \item \textbf{Digital availability of administrative services} \\
+    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.
+As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
+The OZG requires these services to be digitally available.
+As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
+    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
+    Federal republic, each member state and each commune must provide an administration portal.
+Portals of communes must be linked to the portal of the corresponding member state.
+Portals of federal republic and member states must be connected through a portal network.
+\cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.
+    \item \textbf{Interoperable user profiles for accessing administrative services} \\
+    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
+The user profiles must be interoperable for every administration portal of the portal network.
+\end{enumerate}
 
-\section{Description}
+\subsection{OZG Execution}
 
-\section{CSS Solutions}
+Execution of the OZG can be separate into two main projects: Digitalization and Networking.
+The digitalization focuses on transformation of existing processes and services to be using modern technologies.
+This includes most importantly the digitalization of governmental administrative services.
+The networking focuses on connecting existing and future governmental systems to make digitalization universally usable.
+This includes most importantly the construction of administration portals which are connected in a portal network.
+
+\subsubsection{Administrative Service Digitalization}
+
+The OZG requires administrative services to be available through a portal network. As a result of that, many services, which are still bound to paper must be digitalized.
+In total, the BMI lists 575 relevant services.
+Some of them are provided by the federal republic, some by the member states and yet other by the communes.
+Respective to these responsibilities, the task of digitalization is distributed between federal republic and member states, where each member state is assigned to take the lead for specific areas.
+\cite{BMI:Onlinezugangsgesetz}
+Weiter Digitalisierung erklären
+Results of the digitalization are documented on the "OZG-Informationsplattform" \cite{BMI:Informatiosplattform} as process diagrams and data schemata.
+
+\subsubsection{Portal Network}
+
+Following information describes the currently planned creation of a portal network:
+Administration portals are be provided by federal republic, each member state and each commune.
+Each commune integrates its portal with its corresponding member state. This is be done by ... 
+Federal republic and member states connect their administration portals to a portal network.
+This is done through an "Online-Gateway" which enables any administration portal to retrieve information about administration services provided on every other administration portal.
+The portal network is also characterized by interoperable user profiles.
+Federal republic and member states each provide their own user profile, which can be used on every administration portal of the portal network \cite{Cotar:Drucksache_19/12775}.
+Administration portals and user profiles of member states and federal republic are partly available.
+They are, however, not yet connected to a portal network.
+As the implementations of the federal republic can be seen as a guideline for member states on how administration portals and user profiles should work, the rest of the chapter will focus on systems developed by the BMI for usage by federal institutions.
+Those systems are:
+\begin{enumerate}
+    \item federal administration portal: "Verwaltungsportal Bund" \cite{BMI:Verwaltungsportal_Bund}
+    \item federal user profile: "Nutzerkonto Bund" \cite{BMI:Nutzerkonto_Bund}
+\end{enumerate}
+Administration portals of the portal network are supposed to provide the following functionalities.
+
+\textbf{Service Execution Functionality}: 
+Each administration portal provides information and access to a fixed (but expandable) list of administration services.
+Usually the administration services on this list consists of services the operator of the site is responsible for.
+However, it is also possible (and encouraged by the IT-Planungsrat) that a method called "one for all" is used:
+\begin{enumerate}
+    \item Federal republic or one member state develop the digitalization for a group of services
+    \item After development, federal republic or the member state provide the service on its portal
+    \item Every user requiring access to these services visits this portal
+    \item Federal republic or one member state is selected to be responsible for processing these services
+\end{enumerate}
+This method is recommended in order to minimize the amount of duplicate administration services.
+It, however, cannot be used in cases where the requirements for the "same" administration service differentiate a lot.
+A given administrative service of a portal can be accessed in three different ways \cite{BMI:Integrationsleitfaden_Bund}:
+\begin{itemize}
+    \item Fully integrated:	Full availability of the service through the portal
+    \item Web-Component:	Display of separate website providing the service inside the portal
+    \item Linking:			Link to separate website providing the service
+\end{itemize}
+In the long run, fully integrated administrative services are the goal, the following will therefore focus on this case. 
+Access to an administrative service is typically done through a form a user can fill- and hand in via self-service tools provided by the website.
+The acquired data can be made available to institutions through a special website and through methods like REST and SOAP for further automated processing by IT-systems.
+Governmental institutions responsible for an administrative service provide the corresponding operator of the portal with necessary data \cite[88]{BMI:Integrationsleitfaden_Bund}):
+\begin{itemize}
+    \item General information about the service, like name, description, and laws
+    \item Layout of the form, like required fields, optional fields, click-dummy
+    \item Communication method for acquired data through form, like JSON over REST or XML over SOAP
+\end{itemize}
+
+\textbf{Service Search Functionality}: 
+As explained above, each administration portal provides its own list of administrative services.
+As required by the OZG, any administration portal should also be able to search and find administration services provided by other portals.
+This requires administration portals to share information about who provides which services which is done through an "Online-Gateway".
+\cite{BMI:Gateway}
+If a user searches for an administration service on a portal which does not provide it, he will see a list of search entries related to the search term.
+Selecting the service will forward the user to the corresponding portal.
+
+\textbf{Profile Functionality}:
+Profiles enable users to save reusable personal data according to the once-only principle and authenticate for usage of administrative services.
+A user profile can be created and accessed by using multiple identification methods.
+Three different levels of identification methods exist:
+\begin{enumerate}
+    \item Low trust level
+    \item Substantial trust level
+    \item High trust level
+\end{enumerate}
+A low trust level is for example the usage of a username and password combination. A high trust level is for example the usage of the eID feature of the German ID card.
+Depending on the administrative service a profile tries to access, a different level of identification is required.
+This is necessary to validate that the correct person is using the profile.
+As a result, for example, profiles created only by specifying a random username and password do not suffice for accessing important administrative services.
+An additional identification through the eID would be necessary.
+The user profile saves personal data like name, address, birth date, nationality and more. This information can be used to prefill forms for the user. \cite{BMI:Nutzerkonto_Bund}
+
+\textbf{Inbox Functionality}:
+This functionality is strongly connected to user profiles.
+The Inbox enables users and authorities to communicate directly if for example additional documents are necessary for a request or if the user has some general questions and more.
+The user can provide an E-Mail address to be notified of received messages.
+Depending on the security relevance of the message, different identification methods are necessary to view it.
+\cite{BMI:Nutzerkonto_Bund}
+
+\chapter{Preparatory Work}
+
+\section{OZG Scenarios}
+
+Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
+\\\\
+The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
+and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:
+
+\begin{enumerate}
+     \item What part of a scenario is digital?
+     \item What part of a scenario can be done through a DCSS provider / is relevant for DCSS?
+     \item What part of a scenario is done through \textbf{existing} business systems?
+           \begin{enumerate}
+                \item new necessary business logic part of (configurable) integration? => non invasive
+           \end{enumerate}
+     \item What part of a scenario should be done by the integration architecture?
+     \item What are commonalities of scenarios?
+           \begin{enumerate}
+                \item OZG scenarios often describe digital handling of applications
+                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system architecture with the problem of distributed
+                      data and functionality which the integration architecture would solve.
+           \end{enumerate}
+\end{enumerate}
+
+\begin{itemize}
+     \item Unemployment Benefit (AG2)
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\item Training Promotion (BAföG)
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\item Drivers License
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Process Diagram of Application
+     \item Click-Dummy
+\end{itemize}
+
+\item Company Registration and Approval
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+     \item Click-Dummy
+\end{itemize}
+
+\item Visa Issuance
+\begin{itemize}
+     \item Data Schema
+     \item Process Diagram
+\end{itemize}
+
+\end{itemize}
+
+\section{Relevant Systems and Data}
+
+\subsection{EAPs}
+
+\subsection{Architecture Bricks}
+
+\subsection{Data Bricks}
+
+\subsection{Integration Requirements}
+
+\subsubsection{Regarding Integration Architecture}
+
+\subsubsection{Regarding Business Connector}
 
@@
 
-\chapter{Enterprise Architectures}
+\subsection{Functionalities and Interfaces}
 
-\section{Modeling of the real world}
+\subsection{Integration Requirements}
 
-\section{Modeling Challenges}
+\subsubsection{Regarding Enterprise Architecture}
 
-\section{Enterprise Architecture Patterns (EAP)}
+\subsubsection{Regarding Integration Architecture}
 
-\chapter{Relevant Systems and Data}
+\subsection{Documentation}
 
-\section{EAPs}
-
-\section{Architecture Bricks}
-
-\section{Data Bricks}
-
-\section{Integration Requirements}
-
-\subsection{Regarding Integration Architecture}
-
-\subsection{Regarding Business Connector}
-
-\chapter{Integration}
-
-\section{Definition}
-
-\section{Requirements}
-
-\subsection{Loose Coupling}
-
-\subsection{Homogeneous Landscapes}
-
-\section{Enterprise Integration Patterns (EIP)}
-
-\subsection{Pattern 1}
-
-\subsection{Pattern 2}
-
-\chapter{Business Connector}
-
-\section{Functionalities and Interfaces}
-
-\section{Integration Requirements}
-
-\subsection{Regarding Enterprise Architecture}
-
-\subsection{Regarding Integration Architecture}
-
-\section{Documentation}
-
-\subsection{Connector as Architecture Brick}
+\subsubsection{Connector as Architecture Brick}
 
@@
 
-\bibliographystyle{apalike}
-\bibliography{references}
+\chapter{Outlook}
+
+\begin{itemize}
+     \item Expanding integration architecture with capabilities for DCSS scenarios of different areas than online administration self-service
+     \begin{itemize}
+          \item online payment self-service (PayPal, psd2)
+          \item online shopping self-service (Amazon)
+          \item online health care self-service (DVG)
+          \item online entertainment self-service (Netflix, YouTube, Spotify)
+          \item online information / support self-service (StackOverflow)
+     \end{itemize}
+\end{itemize}
+
+\printbibliography
 

### 2020-12-09 msc-thesis.tex
Large update

--- 2020-11-24 thesis/msc-thesis.tex
@@
 
-Many enterprises provide digital tools which improve service usability for their customers.
-For example: If somebody wants to watch a movie, he does not drive to the nearest store to buy a DVD but instead uses websites providing video on demand (VoD).
-The reason is: VoD enterprises provide tools for digital customer self-service (DCSS).
-A customer can easily access the video over a website on his own.
-Technologies for DCSS becomes increasingly relevant, as the German government introduced requirements for DCSS in recent regulations.
-Most prominent are  "Onlinezugangsgesetz" (OZG), "Datenschutzgrundverordnung" (DSGVO) and "Digitale Versorgung Gesetz" (DVG).
+Since invention of the World Wide Web, the number of its users increased rapidly.
+Today, more than 90 percent of the German population use the Internet \cite{Onlinestudie}.
+Enterprises recognised this potential to inform and interact with a large number of people.
+Today, an often used method can be called "digital customer self-service" (DCSS).
+Specialized software tools enable customers to use services of an enterprise through the internet without direct human interaction.
 
-DCSS is made available through DCSS providers.
-They can consist of websites and applications developed in self-work or be services provided by separate companies.
-Adding DCSS providers to a system architecture is a common task.
-It usually involves integration of new DCSS components into an existing system architecture.
-Due to the complicated nature of system architectures, integration proves to be a difficult task.
+Developing and maintaining these tools and the underlying architecture can be a difficult and expensive task.
+Required software solutions can therefore be accessed from commercial DCSS providers.
+In order to use their tools, enterprises will have to integrate them into existing system architectures.
+Depending on for example the complexity of the tools, different integration approaches can be applied.
+
+Many tools require user profiles if authentication, communication or access to personal information is necessary.
+Systems providing profiles therefore are part of numerous enterprise architectures.
+This leads online customers to create multiple user profiles - one for each enterprise.
+It is then his responsibility to keep his profiles synchronised and up to date.
+Increasing numbers of user profiles lead to a variety issues: Frequent changes of credentials become unrealistic and modification of an E-Mail address becomes a major inconvenience.
+
+An evolutionary step in customer profile management is the usage of self-sovereign identities (SSI): instead of each enterprise, the customer provides a user profile.
+This profile can be managed by a trusted DCSS provider for SSI.
+In order for this concept to work, each enterprise will have to integrate the provider into their existing user profile systems.
+The result would be one user profile for one person which identifies him as a customer for multiple integrated enterprises.
+
+A currently relevant example for usage of DCSS with particular interesting requirements for user profiles is the "Online Access Law" (OZG).
+It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
+The current plan is to make the profile only available for usage in context of the OZG.
+From a user perspective, this would be yet another profile to manage.
 
@@
 
-The objective of this bachelor thesis is to improve the capability of enterprises and institutions to integrate DCSS providers.
-The execution of the German "Online Access Law (OZG)" is a good example for modernization efforts through usage of DCSS.
-Due to an incoming deadline of the OZG, integration of DCSS technology in this context gets increasingly relevant.
-The bachelor thesis therefore focuses on the integration of DCSS providers into the technological OZG ecosystem.
-A message based integration architecture is presented which enables system architectures relevant for the OZG to utilize services of DCSS providers.
-However, the integration architecture is constructed to also be applicable in cases not related to the OZG and to be expandable according to requirements of future use cases.
-The integration architecture is evaluated in respect to technological feasibility and real-life applicability.
-The results are incorporated into an operating manual, providing guidance in developing and deploying the presented integration architecture.
+Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures with existing user profiles to accept SSI through its providers.
 
-\chapter{Structure of Work}
+In the beginning, the terms DCSS, DCSS provider, SSI, SSI provider, SSI connector and OZG are defined and the underlying concept is explained.
 
-The first chapter explains what DCSS and its providers are, what system architectures are and how they can be modeled, what the content of the OZG is, how its implementation is planned and how DCSS providers can be utilized and what integration is, why it is necessary and why a message based approach is used.
-The second chapter ...
+Then, preparatory work relevant for the integration architecture is presented.
+Based on process diagrams of digitalized administration services, several use cases of DCSS are listed and evaluated for their relevance.
+They provide important information on which functionalities the SSI provider is expected to have and the integration architecture is required to integrate.
+
+As an integration approach through a connector is used, concrete functionalities and interfaces of a possible connector are specified for usage by the integration architecture.
+
+Based on documentation of system architectures of several member states, relevant components of the architecture relevant for the OZG are selected.
+Each component is explained in detail along with the functionalities it provides for usage by the integration architecture.
+
+The integration architecture integrates previously documented connector and components of the system architecture in order to make the selected use cases available through the SSI provider.
+Integration patterns are used to formulate the integration architecture.
+In order to save investments the integration reuses as many systems as possible and modifies as few systems as necessary.
+
+The integration architecture is presented iteratively.
+Each iteration contains increasingly demanding requirements along with the documentation of the increasingly complex integration architecture.
+Each documentation is done through textual explanations, multiple flow diagrams and one messaging architecture.
+
+In order to validate the integration architecture, the execution of one administration service through the SSI provider is evaluated in theory.
 
@@
 \textbf{Definition}: Digital self-service is the consumption of services provided by an enterprise over the internet without human to human interaction.
-
-It is important to distinguish between "service" and "self-service". The difference is shown through two examples:
+It is important to distinguish between "service" and "self-service".
+The difference is shown through two examples:
 
@@
 
-Customers are able to do self-service because companies provide them with self-service tools.
-Creating them is not trivial and is the main business model of many companies.
+Customers are able to do digital self-service because they are provided with digital self-service tools.
+Creating those is not trivial and is the main business model of many companies.
 Video on demand websites for example do not only flourish as a result of providing access to videos (this business model existed long before them) but as a result of the digital self-service tools they provide.
+
+There exist a lot of different use cases of DCSS. Many can be differentiated into two categories: DCSS for information and DCSS for transaction.
+The category DCSS for information contains use cases where DCSS enables users to \textbf{retrieve} information relevant for them.
+The category DCSS for transaction contains use cases where DCSS enables users to permanently \textbf{add} information to a system, usually in order to trigger some process.
+
+A use case for retrieving information through DCSS are so called "WiKi" pages.
+Similar to the famous website "Wikipedia", information about for example the usage of a product can be made accessible to customers.
+In this case, it is not necessary any more to call a support hot-line or visit a shop.
+Another example are online learning platforms which provide customers with necessary information to for example learn a language.
+In this case, it is not necessary any more to meet teachers.
+Online job hunting websites enable its users to find information about job offers which fit their requirements.
+In this case it is not necessary any more to go to employment bureaus.
+
+A common use case for transaction through DCSS are online retailers which enable users to start payment and delivery processes by providing the necessary information.
+They are often accompanied by DCSS for information in order to find and select products.
+In this case it is not necessary any more to go to the local shopping mall.
+Another use case is the management of user identities where DCSS enables users to authenticate themselves and manage personal information.
+In this case it is not necessary any more to show up in person at for example a store in order to identify ones identity and give personal information about e.g.
+the living address.
 
@@
 
-\section{Enterprise Architecture}
+\subsection{DCSS Provider}
+As described in the previous section, digital customer self-service is a widely used method on the free market to increase customer experience.
+In order for customers to use self-service, companies and institutions have to provide necessary tools.
+Depending on the business case, different categories of DCSS are relevant.
+Depending on the use case, DCSS is enabled through a variety of software tools.
 
-\subsection{Modeling of the real world}
+A chain of stores, for example, might provide DCSS tools for information which enable users to inform themselves about available products and opening hours.
+One tool could for example provide a search functionality for stores in the local area.
+Another tool could provide a catalogue of available products when a store is selected.
+The catalogue could also enable users to filter for relevant products.
 
-\subsection{Modeling Challenges}
+Online retailers however will additionally require DCSS tools for transaction.
+This can be for example be tools for management of user profiles in order for users to authenticate and manage personal information like payment and delivery details.
 
-\subsection{Enterprise Architecture Patterns (EAP)}
+As just shown, depending on the use case, complexity of technology providing DCSS can be very high.
+Besides enabling DCSS functionality, technology in use also needs to be maintained in order to adhere to most recent security and data protection standards.
+Those can also differ between countries.
+Therefore, in an effort to save costs or to improve functionality companies and organizations could decide to use DCSS software solutions from companies which have specialised in this area: DCSS providers.
 
-\section{Integration}
+As there exist many use cases for DCSS, different software solutions from DCSS providers are possible. The bachelor thesis focuses on DCSS providers for management of identities.
 
-\subsection{Definition}
+Identity management is important for many businesses and organizations.
+In order to provide services to individual persons it is necessary to verify their identity, access and update related information and be able to interact.
+Interaction and verification of identities is straight forward if somebody shows up in person.
+Personal information of a customer can be managed trough paper files.
 
-\subsection{Requirements}
+DCSS providers for identity management can improve this process for customers and businesses.
+The following is a possible solution for identity management through DCSS providers, the bachelor thesis will assume.
 
-\subsubsection{Loose Coupling}
-
-\subsubsection{Homogeneous Landscapes}
-
-\section{DCSS Provider}
-
-This chapter introduces digital customer self-service providers. It explains what they are, why they are useful, what services they can provide and what integration challenges can be.
-
-\subsection{Motivation}
-
-As described in the previous chapter, digital customer self-service is a widely used method on the free market to increase customer experience.
-In order for customers to use self-service, respective companies or institutions have to provide necessary tools.
-Depending on the business case, different self-service tools might be used: The local grocery store might simply provide tools for customers to inform themselves about opening hours and available products while e-commerce companies would want to enable users to buy products online.
-Depending on the use case, complexity of technology providing DCSS can be very high.
-Besides enabling DCSS functionality, used technology also needs to adhere to security and data protection standards which can change regularly and between countries.
-As a result, individual companies or institutions would have to invest many resources for development and maintenance of DCSS solutions.
-They could therefore decide to hire DCSS solutions from companies which have specialised in this area.
-
-\subsectio{Description}
+Description of IDAS ...
 
@@
 
-\subsectio{Integration}
+- relations, relationship template, app, server, ....
+
+\section{SSI}
+
+\section{SSI Connector}
+seperat wegen bedeutung für Arbeit
 
@@
 This section introduces the law for improvement of online access of administrative services (Online Access Law - OZG), its origin, purpose and planned realization.
-It explains the relevance of DCSS providers for the implementation of the OZG and where integration is necessary.
 
@@
 
-Execution of the OZG can be separate into two main projects: Digitalization and Networking.
-The digitalization focuses on transformation of existing processes and services to be using modern technologies.
+Execution of the OZG can be separated into two projects: Digitalization and Networking.
+Digitalization focuses on transformation of existing processes and services to be using modern technologies.
 This includes most importantly the digitalization of governmental administrative services.
@@
 
-\subsubsection{Administrative Service Digitalization}
-
-The OZG requires administrative services to be available through a portal network. As a result of that, many services, which are still bound to paper must be digitalized.
+Many services, which are still bound to paper must be digitalized.
 In total, the BMI lists 575 relevant services.
@@
 Respective to these responsibilities, the task of digitalization is distributed between federal republic and member states, where each member state is assigned to take the lead for specific areas.
-\cite{BMI:Onlinezugangsgesetz}
-Weiter Digitalisierung erklären
-Results of the digitalization are documented on the "OZG-Informationsplattform" \cite{BMI:Informatiosplattform} as process diagrams and data schemata.
+\cite{BMI:Onlinezugangsgesetz} Results of the digitalization are documented on the "OZG-Informationsplattform" \cite{BMI:Informatiosplattform} as process diagrams and data schemata.
 
-\subsubsection{Portal Network}
+Administrative services are made available through administrative portals which are be provided by federal republic, each member state and each commune.
+Communes integrate their portals with corresponding member states.
+The portals are connected through an "Online-Gateway" and form a portal network.
 
-Following information describes the currently planned creation of a portal network:
-Administration portals are be provided by federal republic, each member state and each commune.
-Each commune integrates its portal with its corresponding member state. This is be done by ... 
-Federal republic and member states connect their administration portals to a portal network.
-This is done through an "Online-Gateway" which enables any administration portal to retrieve information about administration services provided on every other administration portal.
-The portal network is also characterized by interoperable user profiles.
-Federal republic and member states each provide their own user profile, which can be used on every administration portal of the portal network \cite{Cotar:Drucksache_19/12775}.
-Administration portals and user profiles of member states and federal republic are partly available.
-They are, however, not yet connected to a portal network.
-As the implementations of the federal republic can be seen as a guideline for member states on how administration portals and user profiles should work, the rest of the chapter will focus on systems developed by the BMI for usage by federal institutions.
-Those systems are:
-\begin{enumerate}
-    \item federal administration portal: "Verwaltungsportal Bund" \cite{BMI:Verwaltungsportal_Bund}
-    \item federal user profile: "Nutzerkonto Bund" \cite{BMI:Nutzerkonto_Bund}
-\end{enumerate}
-Administration portals of the portal network are supposed to provide the following functionalities.
+Federal republic and each member state provide digital access to administrative services.
+An important method is called "one for all": One member state manages the digitalization of a category of administrative services and makes them digitally accessible for every other member state.
+Every administrative service can be found through a search function provided by every portal of the network.
 
-\textbf{Service Execution Functionality}: 
-Each administration portal provides information and access to a fixed (but expandable) list of administration services.
-Usually the administration services on this list consists of services the operator of the site is responsible for.
-However, it is also possible (and encouraged by the IT-Planungsrat) that a method called "one for all" is used:
-\begin{enumerate}
-    \item Federal republic or one member state develop the digitalization for a group of services
-    \item After development, federal republic or the member state provide the service on its portal
-    \item Every user requiring access to these services visits this portal
-    \item Federal republic or one member state is selected to be responsible for processing these services
-\end{enumerate}
-This method is recommended in order to minimize the amount of duplicate administration services.
-It, however, cannot be used in cases where the requirements for the "same" administration service differentiate a lot.
-A given administrative service of a portal can be accessed in three different ways \cite{BMI:Integrationsleitfaden_Bund}:
-\begin{itemize}
-    \item Fully integrated:	Full availability of the service through the portal
-    \item Web-Component:	Display of separate website providing the service inside the portal
-    \item Linking:			Link to separate website providing the service
-\end{itemize}
-In the long run, fully integrated administrative services are the goal, the following will therefore focus on this case. 
-Access to an administrative service is typically done through a form a user can fill- and hand in via self-service tools provided by the website.
-The acquired data can be made available to institutions through a special website and through methods like REST and SOAP for further automated processing by IT-systems.
-Governmental institutions responsible for an administrative service provide the corresponding operator of the portal with necessary data \cite[88]{BMI:Integrationsleitfaden_Bund}):
-\begin{itemize}
-    \item General information about the service, like name, description, and laws
-    \item Layout of the form, like required fields, optional fields, click-dummy
-    \item Communication method for acquired data through form, like JSON over REST or XML over SOAP
-\end{itemize}
+Depending on the administrative service, a user profile is required to verify ones identity.
+As federal republic and most member states already provide their own user profiles, the "IT-Planungsrat" decided to save investments by connecting them to an interoperable user profile.
 
-\textbf{Service Search Functionality}: 
-As explained above, each administration portal provides its own list of administrative services.
-As required by the OZG, any administration portal should also be able to search and find administration services provided by other portals.
-This requires administration portals to share information about who provides which services which is done through an "Online-Gateway".
-\cite{BMI:Gateway}
-If a user searches for an administration service on a portal which does not provide it, he will see a list of search entries related to the search term.
-Selecting the service will forward the user to the corresponding portal.
+There exists a low, substantial and high level of authentication security when logging in to a user profile or when creating one.
+A low trust level is for example the usage of a username and password combination, a high trust level is for example the usage of the eID feature of the German ID card.
+Depending on the administrative service a profile tries to access, a different trust level is required.
 
-\textbf{Profile Functionality}:
-Profiles enable users to save reusable personal data according to the once-only principle and authenticate for usage of administrative services.
-A user profile can be created and accessed by using multiple identification methods.
-Three different levels of identification methods exist:
-\begin{enumerate}
-    \item Low trust level
-    \item Substantial trust level
-    \item High trust level
-\end{enumerate}
-A low trust level is for example the usage of a username and password combination. A high trust level is for example the usage of the eID feature of the German ID card.
-Depending on the administrative service a profile tries to access, a different level of identification is required.
-This is necessary to validate that the correct person is using the profile.
-As a result, for example, profiles created only by specifying a random username and password do not suffice for accessing important administrative services.
-An additional identification through the eID would be necessary.
-The user profile saves personal data like name, address, birth date, nationality and more. This information can be used to prefill forms for the user. \cite{BMI:Nutzerkonto_Bund}
-
-\textbf{Inbox Functionality}:
-This functionality is strongly connected to user profiles.
-The Inbox enables users and authorities to communicate directly if for example additional documents are necessary for a request or if the user has some general questions and more.
-The user can provide an E-Mail address to be notified of received messages.
-Depending on the security relevance of the message, different identification methods are necessary to view it.
-\cite{BMI:Nutzerkonto_Bund}
+Profiles also enable users to save personal data in a data wallet and to communicate with institutions through an inbox.
 
@@
 
-\section{OZG Scenarios}
+\section{OZG DCSS Scenarios}
 
-Usage of DCSS OZG scenarios (\textbf{process diagrams and data schemas available}
-\\\\
-The scenarios include more than just CSS and are partly non-digital. Therefore processes relevant for DCSS have to be selected
-and it has to be defined which processes are part of a CSS provider, the business systems or the integration architecture:
+The information platform of the OZG contains information about many administration services in form of process diagrams \cite{BMI:Ergebnisse}.
+They serve as a resource to identify important DCSS scenarios of administration processes.
+The following scenarios were identified:
 
-\begin{enumerate}
-     \item What part of a scenario is digital?
-     \item What part of a scenario can be done through a DCSS provider / is relevant for DCSS?
-     \item What part of a scenario is done through \textbf{existing} business systems?
-           \begin{enumerate}
-                \item new necessary business logic part of (configurable) integration? => non invasive
-           \end{enumerate}
-     \item What part of a scenario should be done by the integration architecture?
-     \item What are commonalities of scenarios?
-           \begin{enumerate}
-                \item OZG scenarios often describe digital handling of applications
-                \item In OZG scenarios, often multiple governmental institutions are involved. This could be modeled as one system architecture with the problem of distributed
-                      data and functionality which the integration architecture would solve.
-           \end{enumerate}
-\end{enumerate}
+\subsection{Identity Management}
 
+\subsubsection{Scenario Profile Management}
 \begin{itemize}
-     \item Unemployment Benefit (AG2)
-\begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Process Diagram of Application
-     \item Click-Dummy
+    \item Create a user profile
+    \item Delete a user profile
+    \item Check existence of a user profile
 \end{itemize}
 
-\item Training Promotion (BAföG)
+\subsubsection{Scenario Identity verification}
 \begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Click-Dummy
+    \item Login to a user profile
+    \item Provide multiple levels of security for identity verification
+    \item Usage of a guest profile
 \end{itemize}
 
-\item Drivers License
+\subsection{Request Management}
+
+\subsubsection{Scenario Request Preparation}
 \begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Process Diagram of Application
-     \item Click-Dummy
+    \item Search for administration services
+    \item Check necessity of a profile
+    \item Check required level of identity verification
+    \item Selection of institution responsible for processing the request (Specification of current location)
 \end{itemize}
 
-\item Company Registration and Approval
+\subsubsection{Scenario Request Creation}
 \begin{itemize}
-     \item Data Schema
-     \item Process Diagram
-     \item Click-Dummy
+    \item Filling in a form for an application
+    \item Automated filling in of form with saved personal data
+    \item Collaboration on application by multiple identities
 \end{itemize}
 
-\item Visa Issuance
+\subsubsection{Scenario Request Delivery}
 \begin{itemize}
-     \item Data Schema
-     \item Process Diagram
+    \item Transmission of an application to responsible institution
 \end{itemize}
 
+\subsubsection{Scenario Request Processing}
+\begin{itemize}
+    \item Period of validity of applications
+    \item Notification of user about missing information or documents
+    \item Transmission of missing information
+    \item Notification of user about required preliminary administration services
+    \item Communication through E-Mail
+    \item Cancel an application
+    \item Approvals of user to e.g. data protection or information transfer
+    \item Modification request of application after transmission
+    \item Notification of received application by institution
+    \item Request status update by user
+    \item Sending notification to confirm the reading of a message
+    \item Notification of certain events to separate person e.g. parents
+    \item Request of institution about explicit document
 \end{itemize}
 
-\section{Relevant Systems and Data}
+\subsubsection{Scenario Request Finalization}
+\begin{itemize}
+    \item Notification of outcome of process / application
+    \item Objection of user to result of the process
+    \item Access to signed digital formula of result of process
+    \item Definition of dates for evens
+\end{itemize}
 
-\subsection{EAPs}
+\subsection{Data Management}
 
-\subsection{Architecture Bricks}
+\subsubsection{Scenario Access Management}
+\begin{itemize}
+    \item Access to an application by multiple separate identities
+    \item Sharing of documents saved in a wallet
+\end{itemize}
 
-\subsection{Data Bricks}
+\subsubsection{Scenario Data Consistency}
+\begin{itemize}
+    \item Period of validity of documents
+    \item Profile data discrepancies between involved user profiles
+\end{itemize}
 
-\subsection{Integration Requirements}
+\subsubsection{Scenario Data Accessibility}
+\begin{itemize}
+    \item Upload of e.g. documents and certificates
+    \item Saving personal data entered in a form to the user profile
+    \item Protocol of all processes accessible with information about interactions
+\end{itemize}
 
-\subsubsection{Regarding Integration Architecture}
+\section{DCSS Connector}
 
-\subsubsection{Regarding Business Connector}
+\section{OZG System Architecture}
+This section describes the system architecture of a member state relevant for the execution of the OZG an integration of a DCSS provider.
+Due to a lack of detailed information, the system architecture is described by components responsible for a category of tasks.
+Each component is associated to data objects it processes.
+The definition of components and data objects are based on research about planned system architectures of member states.
 
-\section{Business Connector}
+\subsection{User Profile}
+Each member state provides its own user profile which manages the identity of a user.
+It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.
 
-\subsection{Functionalities and Interfaces}
+\subsection{Administration Portal}
+The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.
 
-\subsection{Integration Requirements}
+\subsection{Application Platform}
+The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions.
+It is possible to prefill the form with personal data stored inside the user profile.
 
-\subsubsection{Regarding Enterprise Architecture}
-
-\subsubsection{Regarding Integration Architecture}
-
-\subsection{Documentation}
-
-\subsubsection{Connector as Architecture Brick}
+\subsection{Institution}
+Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.
 
@@
 
-\section{Scenario 1}
+This chapter presents a message based integration architecture which enables access to DCSS features of member states through a DCSS provider.
+Multiple versions of an integration architecture are presented which fulfill increasingly complex requirements.
+Requirements are formulated as user scenarios which should be accomplishable through the DCSS provider.
+Each version is presented in the form of multiple flow charts, each describing sequential steps while carrying out a required scenario and a corresponding messaging infrastructure.
 
-\subsection{Integration Documentation}
+\section{Basic}
 
-\subsection{Required System and Data Bricks}
+\subsection{Requirements}
+In the first version of the integration architecture, users of the DCSS provider should be able to
+\begin{itemize}
+    \item fill in an application
+    \item authenticate
+    \item receive and send messages
+\end{itemize}
 
-\subsection{System Integration}
+\subsection{Flow Charts}
 
-\subsection{Data Integration}
+\includegraphics[width=\textwidth]{Basic Integration Application.png}
 
-\section{Scenario 2}
+\includegraphics[width=\textwidth]{Basic Integration Onboarding.png}
 
-\subsection{Integration Documentation}
+\subsection{Messaging Integration}
 
-\subsection{Required System and Data Bricks}
+\section{Advanced}
 
-\subsection{System Integration}
+\subsection{Requirements}
 
-\subsection{Data Integration}
+\subsection{Flow Charts}
+
+\subsection{Messaging Integration}
 

### 2020-12-10 msc-thesis.tex
New Introduction

@@
 \chapter{Context}
-
 Since invention of the World Wide Web, the number of its users increased rapidly.
 Today, more than 90 percent of the German population use the Internet \cite{Onlinestudie}.
-Enterprises recognised this potential to inform and interact with a large number of people.
-Today, an often used method can be called "digital customer self-service" (DCSS).
-Specialized software tools enable customers to use services of an enterprise through the internet without direct human interaction.
+Enterprises and organizations recognised this potential to inform and interact with a large number of people.
+A frequently used method is "online self-service" (OSS).
+Specialized software tools enable customers to use services through the internet without direct human interaction.
 
 Developing and maintaining these tools and the underlying architecture can be a difficult and expensive task.
-Required software solutions can therefore be accessed from commercial DCSS providers.
+Required software solutions can therefore be accessed from commercial OSS providers.
 In order to use their tools, enterprises will have to integrate them into existing system architectures.
@@
 An evolutionary step in customer profile management is the usage of self-sovereign identities (SSI): instead of each enterprise, the customer provides a user profile.
-This profile can be managed by a trusted DCSS provider for SSI.
+This profile can be managed by a trusted OSS provider for SSI.
+
 In order for this concept to work, each enterprise will have to integrate the provider into their existing user profile systems.
@@
 
-A currently relevant example for usage of DCSS with particular interesting requirements for user profiles is the "Online Access Law" (OZG).
+A currently relevant example for usage of OSS with particular interesting requirements for user profiles is the "Online Access Law" (OZG).
 It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
@@
 \chapter{Objective}
+Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures with existing user profiles to accept SSI through its providers.
+The goal of the integration architecture in the example is to make important OZG scenarios accessible with usage of self-sovereign identities instead of the existing user profiles.
+The two points of integration are on one hand-side the system architecture relevant for the OZG in form of a list of system components and on the other hand-side the SSI provider in form of a connector.
+Integration patterns are used to formulate the integration architecture which enables to use a combination of established and tested messaging solutions.
+In order to save investments the integration reuses as many system components as possible and modifies as few system components as necessary.
 
-Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures with existing user profiles to accept SSI through its providers.
+\chapter{Structure of Work}
 
-In the beginning, the terms DCSS, DCSS provider, SSI, SSI provider, SSI connector and OZG are defined and the underlying concept is explained.
+In the beginning, the terms OSS, OSS provider, SSI, SSI provider, SSI connector and OZG are defined and the underlying concept is explained.
 
 Then, preparatory work relevant for the integration architecture is presented.
-Based on process diagrams of digitalized administration services, several use cases of DCSS are listed and evaluated for their relevance.
+Based on process diagrams of digitalized administration services, several use cases of OSS are listed and evaluated for their relevance.
 They provide important information on which functionalities the SSI provider is expected to have and the integration architecture is required to integrate.
 
-As an integration approach through a connector is used, concrete functionalities and interfaces of a possible connector are specified for usage by the integration architecture.
+An integration approach through a connector is used. Concrete functionalities and interfaces of a possible connector are specified for usage by the integration architecture.
 
@@
 The integration architecture integrates previously documented connector and components of the system architecture in order to make the selected use cases available through the SSI provider.
-Integration patterns are used to formulate the integration architecture.
-In order to save investments the integration reuses as many systems as possible and modifies as few systems as necessary.
-
-The integration architecture is presented iteratively.
+The architecture is presented iteratively.
 Each iteration contains increasingly demanding requirements along with the documentation of the increasingly complex integration architecture.
@@
 \chapter{Fundamentals}
+The goal of this chapter is to define terminology and to explain basic concepts for better understanding of context and objective of the bachelor thesis.
 
-\section{Digital Customer Self-Service}
-This chapter introduces the concept of digital customer self-service. It defines DCSS, describes what it is by usage of examples and mentions benefits such as challenges.
+\section{Online Self-Service}
+Self-service has existed for a long time.
+It generally means the consumption of some service without human interaction but rather in a self-reliant way.
+One example which is still relevant today are restaurants offering buffets.
+Instead of a waiter, customers take food for themselves - in self-service.
+In spring, some farmers allow people to pick flowers from the acre in exchange for a small fee.
 
-\textbf{Definition}: Digital self-service is the consumption of services provided by an enterprise over the internet without human to human interaction.
-It is important to distinguish between "service" and "self-service".
-The difference is shown through two examples:
+In recent decades technology made advanced methods of digital self-service possible.
+Money can be withdrawn from local ATMs and train tickets can be bought from ticket machines.
+Technological advancements, at least directed to the average consumer, can be seen as advancements in self-service capabilities.
+Consumers buy technology which makes them independent from the help of other people.
 
-\textbf{Example 1}: A service is the availability to purchase items whereas digital self-service is the placement of orders over a website.
+Since the internet enabled the connection of a very large amount of people, especially the world wide web made it accessible to the general public.
+The world wide web enables any user to access and interact with technological systems all over the world through a user friendly visual interface.
+Today, many of those systems are provided by enterprises and other organizations for customers and users to access their services - they enable customers online self-service (OSS).
 
-\textbf{Example 2}: A service is the availability of video on demand whereas digital self-service is the access of video files over a website.
+Online self-service is defined as: self-reliant consumption of services over the internet without human to human interaction.
 
-Digital self-service is one of many possible ways to access a service: An order placement could also be done through email or phone call and access to videos could be granted through same-day-delivery of DVDs.
+Depending on the reasoning most websites on the WWW can be described as providing online self-service. OSS therefore rather describes a perspective on the WWW than a use case.
 
-Customers are able to do digital self-service because they are provided with digital self-service tools.
-Creating those is not trivial and is the main business model of many companies.
-Video on demand websites for example do not only flourish as a result of providing access to videos (this business model existed long before them) but as a result of the digital self-service tools they provide.
+Tow categories of OSS can be differentiated: The information category contains cases where users are enabled to retrieve relevant information.
+The transaction category contains cases where users modify the systems they interacts with to for example save data or trigger some internal business process.
 
-There exist a lot of different use cases of DCSS. Many can be differentiated into two categories: DCSS for information and DCSS for transaction.
-The category DCSS for information contains use cases where DCSS enables users to \textbf{retrieve} information relevant for them.
-The category DCSS for transaction contains use cases where DCSS enables users to permanently \textbf{add} information to a system, usually in order to trigger some process.
+An example for retrieving information through OSS are so called "WiKi" pages.
+Similar to the famous website "Wikipedia", information about for example the usage of a product can be made accessible to customers.
+In this case, it is not necessary any more to call a support hot-line.
+Another example are online learning platforms which provide customers with necessary information to for example learn a language. In this case, it is not necessary any more to meet teachers.
+Online job hunting websites enable its users to find information about job offers which fit their requirements. In this case it is not necessary any more to visit employment bureaus.
 
-A use case for retrieving information through DCSS are so called "WiKi" pages.
-Similar to the famous website "Wikipedia", information about for example the usage of a product can be made accessible to customers.
-In this case, it is not necessary any more to call a support hot-line or visit a shop.
-Another example are online learning platforms which provide customers with necessary information to for example learn a language.
-In this case, it is not necessary any more to meet teachers.
-Online job hunting websites enable its users to find information about job offers which fit their requirements.
-In this case it is not necessary any more to go to employment bureaus.
+A common use case for transaction through OSS are online retailers which enable users to start payment and delivery processes.
+They are often accompanied by OSS for information in order to find and select products.
+In this case it is not necessary any more to go to the local shopping mall.
+Another use case is the management of user identities which enables users to authenticate themselves and manage personal information.
+In this case it is not necessary any more to show up in person at for example a store in order to identify ones identity and give personal information about for example the living address.
 
-A common use case for transaction through DCSS are online retailers which enable users to start payment and delivery processes by providing the necessary information.
-They are often accompanied by DCSS for information in order to find and select products.
-In this case it is not necessary any more to go to the local shopping mall.
-Another use case is the management of user identities where DCSS enables users to authenticate themselves and manage personal information.
-In this case it is not necessary any more to show up in person at for example a store in order to identify ones identity and give personal information about e.g.
-the living address.
+Reasons for the widespread usage of online self-service are significant benefits in ease of service usability for customers and cost reduction for enterprises.
+Customers can self-service from almost every place, easily manage customer data like phone number and address, configure services like subscription plans and access lots of information on available products or trouble shooting steps in an immediate way.
+Online customer self-service improves usability, saves time, increases availability, saves money and therefore increases customer experience.
+Enterprises, especially in progressive countries, aim to keep employment at a minimum, as it is a big cost factor.
 
-Reasons for the widespread usage of digital self-service are significant benefits in ease of service usability for customers and cost reduction for enterprises.
-Customers can self-service from almost every place, easily manage customer data like phone number and address, configure services like subscription plans and access lots of information on available products or trouble shooting steps in an immediate way.
-Digital customer self-service improves usability, saves time, increases availability, saves money and therefore increases customer experience.
-Enterprises, especially in progressive countries, aim to keep employment at a minimum, as it is a big cost factor. Digital self-service turns customers into unpaid employees.
+Digital self-service turns customers into unpaid employees.
 
-Decreasing employment cost while increasing customer experience sounds like a win-win situation.
-Sadly, digital self-service does have its downsides.
-One downside is most immediate to the elderly.
-In order to use DCSS, computers have to be available and one has to be experienced in their usage.
-Technological complexity, however, is not only a problem for customers but also for enterprises providing DCSS.
-Based on existing system architectures, adding DCSS functionalities can turn out to be a difficult task.
-Some form of integration is often necessary.
-With increased system complexity and business dependability come additional maintenance cost.
+\subsection{OSS Provider}
+In order for customers to use online self-service, companies and institutions have to provide the necessary software tools. Depending on category and use case of OSS, different software tools exist.
 
-As today most large enterprises provide DCSS, it can be assumed, that at a given size of an enterprise (measured in number of customers), the benefits of DCSS surpass its disadvantages.
+A chain of stores might provide tools which enables the users to inform themselves about available products and opening hours.
+This could for example be a search functionality for stores in the local area and a catalogue of available products of a selected store.
+Online retailers however will require additional tools which for example enable management of user profiles to authenticate and communicate with customers.
 
-Governments see digitalization as a chance for improvements in many important social and economical areas.
-The process of digitalization can in some cases be described as reinventing existing solutions for usability with computers.
-One of the goals is to make solutions more easily accessible for users and as a method, provide digital self-service.
-Governmental regulations relating to digitalization therefore often encourage or demand enterprises and organizations to provide DCSS.
+OSS providers are defined as: enterprises which develop and maintain solutions for OSS and make them accessible to system architectures of customers.
 
-\subsection{DCSS Provider}
-As described in the previous section, digital customer self-service is a widely used method on the free market to increase customer experience.
-In order for customers to use self-service, companies and institutions have to provide necessary tools.
-Depending on the business case, different categories of DCSS are relevant.
-Depending on the use case, DCSS is enabled through a variety of software tools.
-
-A chain of stores, for example, might provide DCSS tools for information which enable users to inform themselves about available products and opening hours.
-One tool could for example provide a search functionality for stores in the local area.
-Another tool could provide a catalogue of available products when a store is selected.
-The catalogue could also enable users to filter for relevant products.
-
-Online retailers however will additionally require DCSS tools for transaction.
-This can be for example be tools for management of user profiles in order for users to authenticate and manage personal information like payment and delivery details.
-
-As just shown, depending on the use case, complexity of technology providing DCSS can be very high.
-Besides enabling DCSS functionality, technology in use also needs to be maintained in order to adhere to most recent security and data protection standards.
-Those can also differ between countries.
-Therefore, in an effort to save costs or to improve functionality companies and organizations could decide to use DCSS software solutions from companies which have specialised in this area: DCSS providers.
-
-As there exist many use cases for DCSS, different software solutions from DCSS providers are possible. The bachelor thesis focuses on DCSS providers for management of identities.
-
-Identity management is important for many businesses and organizations.
-In order to provide services to individual persons it is necessary to verify their identity, access and update related information and be able to interact.
-Interaction and verification of identities is straight forward if somebody shows up in person.
-Personal information of a customer can be managed trough paper files.
-
-DCSS providers for identity management can improve this process for customers and businesses.
-The following is a possible solution for identity management through DCSS providers, the bachelor thesis will assume.
-
-Description of IDAS ...
-
-- Areas of DCSS: identity, profile, relations, forms, messages, inbox, applications,
-
-- relations, relationship template, app, server, ....
+Depending on the complexity of the solution, different methods of access are possible.
+One possibility would be to provide a self-contained software, the customer can deploy in his system architecture.
+This can be done for example in the case of solutions for WiKi-pages where the customer installs respective software in his web server.
+Another possibility would be, for the OSS provider to host the solution himself and provide system architectures of customers access.
+This can be done for example in the case of retailers which contain systems only for managing a catalogue of available products and processing incoming orders.
+They could integrate an online shop solution hosted by a OSS provider through using a business connector.
 
@@
 \section{SSI Connector}
-seperat wegen bedeutung für Arbeit
 
@@
 
-\section{OZG DCSS Scenarios}
+\section{OZG OSS Scenarios}
 
 The information platform of the OZG contains information about many administration services in form of process diagrams \cite{BMI:Ergebnisse}.
-They serve as a resource to identify important DCSS scenarios of administration processes.
+They serve as a resource to identify important OSS scenarios of administration processes.
 The following scenarios were identified:
@@
 
-\section{DCSS Connector}
+\section{OSS Connector}
 
 \section{OZG System Architecture}
-This section describes the system architecture of a member state relevant for the execution of the OZG an integration of a DCSS provider.
+This section describes the system architecture of a member state relevant for the execution of the OZG an integration of a OSS provider.
 Due to a lack of detailed information, the system architecture is described by components responsible for a category of tasks.
@@
 
-This chapter presents a message based integration architecture which enables access to DCSS features of member states through a DCSS provider.
+This chapter presents a message based integration architecture which enables access to OSS features of member states through a OSS provider.
 Multiple versions of an integration architecture are presented which fulfill increasingly complex requirements.
-Requirements are formulated as user scenarios which should be accomplishable through the DCSS provider.
+Requirements are formulated as user scenarios which should be accomplishable through the OSS provider.
 Each version is presented in the form of multiple flow charts, each describing sequential steps while carrying out a required scenario and a corresponding messaging infrastructure.
@@
 \subsection{Requirements}
-In the first version of the integration architecture, users of the DCSS provider should be able to
+In the first version of the integration architecture, users of the OSS provider should be able to
 \begin{itemize}
@@
 \begin{itemize}
-     \item Expanding integration architecture with capabilities for DCSS scenarios of different areas than online administration self-service
+     \item Expanding integration architecture with capabilities for OSS scenarios of different areas than online administration self-service
      \begin{itemize}

### 2020-12-15 msc-thesis.tex
new introduction

@@
 Since invention of the World Wide Web, the number of its users increased rapidly.
-Today, more than 90 percent of the German population use the Internet \cite{Onlinestudie}.
-Enterprises and organizations recognised this potential to inform and interact with a large number of people.
-A frequently used method is "online self-service" (OSS).
+Today, more than 90 percent of the German population use the internet \cite{Onlinestudie}.
+Enterprises and organizations, recognised this potential to provide their services to a large number of people as Service Providers (SP).
+A frequently used method of SPs is "online self-service" (OSS).
 Specialized software tools enable customers to use services through the internet without direct human interaction.
 
-Developing and maintaining these tools and the underlying architecture can be a difficult and expensive task.
-Required software solutions can therefore be accessed from commercial OSS providers.
-In order to use their tools, enterprises will have to integrate them into existing system architectures.
-Depending on for example the complexity of the tools, different integration approaches can be applied.
+Many tools require identification of a user in case interactions or initiated business processes have to be associated with him.
+An identity provider (IdP) who stores partial identities of users therefore is part of numerous system architectures.
+This leads to customers of SPs to be associated with multiple partial identities - one for each SP.
+Service Providers usually enable users to manage their partial identities using online self-service through so called User Profiles.
 
-Many tools require user profiles if authentication, communication or access to personal information is necessary.
-Systems providing profiles therefore are part of numerous enterprise architectures.
-This leads online customers to create multiple user profiles - one for each enterprise.
-It is then his responsibility to keep his profiles synchronised and up to date.
-Increasing numbers of user profiles lead to a variety issues: Frequent changes of credentials become unrealistic and modification of an E-Mail address becomes a major inconvenience.
+The issues of this approach becomes clear for a large amount of partial identities.
+The more Service Providers a person is customer of, the more partial identities he will have to manage through user profiles.
+Changing the home address in each profile becomes a major inconvenience.
+More serious problems occur for example through the increased risk of data breaches.
 
-An evolutionary step in customer profile management is the usage of self-sovereign identities (SSI): instead of each enterprise, the customer provides a user profile.
-This profile can be managed by a trusted OSS provider for SSI.
+An improved model for identity management is necessary.
+In recent years, multiple new models have been invented.
+One model called Social Login became popular.
+It enables customers to leverage existing User Profiles of social networks like Facebook to create new User Profiles for Service Providers.
+This improves identity management by enabling SPs to rely on the identity information they are provided by the external profile.
+Users can manage identity related information through their Social Profile and each change would then be propagated to User Profiles of connected SPs.
 
-In order for this concept to work, each enterprise will have to integrate the provider into their existing user profile systems.
-The result would be one user profile for one person which identifies him as a customer for multiple integrated enterprises.
+This approach, however, still leaves the requirement of User Profiles for each SP because depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
+This includes for example subscriptions or contracts.
 
-A currently relevant example for usage of OSS with particular interesting requirements for user profiles is the "Online Access Law" (OZG).
+The solution to this problem is an Identity Management System (IMS) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles of SPs.
+To replace User Profiles of SPs, the IMS can not only rely on systems for registration, authentication, authorisation and provisioning.
+Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
+
+In order for an SP to use identities and services of an IMS, an integration into the system architecture of the SP has to take place.
+Due to the complex nature of system architectures and identity management, this is a difficult task.
+
+A currently relevant example for usage of online self-service with particular interesting requirements for identities is the "Online Access Law" (OZG).
 It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
-The current plan is to make the profile only available for usage in context of the OZG.
-From a user perspective, this would be yet another profile to manage.
+The current plan is to make the profiles only available for usage in context of the OZG.
+From a user perspective, this would be yet another partial identity and user profile to manage.
 
 \chapter{Objective}
-Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures with existing user profiles to accept SSI through its providers.
-The goal of the integration architecture in the example is to make important OZG scenarios accessible with usage of self-sovereign identities instead of the existing user profiles.
-The two points of integration are on one hand-side the system architecture relevant for the OZG in form of a list of system components and on the other hand-side the SSI provider in form of a connector.
-Integration patterns are used to formulate the integration architecture which enables to use a combination of established and tested messaging solutions.
+Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of SPs with existing user profiles to make their services accessible through an Identity Management System.
+In the example of the OZG, the integration architecture should enable users to access administrative services of a member state through usage of an IMS instead of a User Profile.
+The two points of integration are on one hand-side the system architecture relevant for the OZG in form of a list of system components and on the other hand-side a connector provided by the IMS.
+Integration patterns are used to formulate the integration architecture in order to utilize a combination of established and tested messaging solutions.
 In order to save investments the integration reuses as many system components as possible and modifies as few system components as necessary.
@@
 
-In the beginning, the terms OSS, OSS provider, SSI, SSI provider, SSI connector and OZG are defined and the underlying concept is explained.
+In the beginning of the thesis, basic concepts and terminology is explained on which the following chapters will rely.
 
@@
 Based on process diagrams of digitalized administration services, several use cases of OSS are listed and evaluated for their relevance.
-They provide important information on which functionalities the SSI provider is expected to have and the integration architecture is required to integrate.
+They provide important information on which functionalities the IMS is required to have and the integration architecture is required to integrate.
 
@@
 
-The integration architecture integrates previously documented connector and components of the system architecture in order to make the selected use cases available through the SSI provider.
+The integration architecture integrates previously documented connector and components of the system architecture in order to make the selected OSS cases usable with the IMS.
 The architecture is presented iteratively.
@@
 
-In order to validate the integration architecture, the execution of one administration service through the SSI provider is evaluated in theory.
+In order to validate the integration architecture, the execution of one administration service with usage of the IMS is evaluated in theory.
 
 \chapter{Fundamentals}
-The goal of this chapter is to define terminology and to explain basic concepts for better understanding of context and objective of the bachelor thesis.
+
+\section{Service Provider}
+Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.
+
+\section{Online Self-Service}
+Online self-service (OSS) describes a method used by service providers to make their services available to the user.
+The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way.
+The user can be supported by a variety of software solutions.
+
+\section{Self-Service Tools}
+Self-service tools are software solutions for customers to enable a online self-service experience.
+Depending on the use case, the tools can be transactional or informing.
+Informing tools help users to receive relevant information, often replacing human customer support.
+Transactional tools help users to interact with services in a persistent way to for example save data or trigger business processes.
+
+Information tools can be for example so called "WiKi" pages or search fields which assist the user in his process of finding information.
+Transactional tools can be for example online forms which assist the user in his process of initiating an ordering business process.
+
+In contrast to information tools, transactional tools often require identification of users in order to associate them with changes they made to the system: If a user triggers the business process of ordering a product, the SP requires identification of the user.
+
+\section{Identity}
+
+Identities are managed by the system architecture of SPs through identity providers (Idp).
+
+- Problem multiple identities
+
+- Modern Identity models
+
+-
+
+\section{User Profile}
+
+- self service for identities
+
+- problem multiple user profiles
+
+\section{}
+
+\section{OSS Profile Provider}
+
+\section{Connector}
 
@@
 Since the internet enabled the connection of a very large amount of people, especially the world wide web made it accessible to the general public.
-The world wide web enables any user to access and interact with technological systems all over the world through a user friendly visual interface.
-Today, many of those systems are provided by enterprises and other organizations for customers and users to access their services - they enable customers online self-service (OSS).
+It enables any user to access and interact with technological systems all over the world through a user friendly visual interface.
+Today, many of those systems are provided by enterprises and other organizations for customers and users to access their services.
+
+- they enable customers online self-service (OSS).
 
@@
 They could integrate an online shop solution hosted by a OSS provider through using a business connector.
-
-\section{SSI}
-
-\section{SSI Connector}
 

### 2020-12-15 msc-thesis.tex
improved objective

@@
 % Input and font encoding
-\usepackage[latin1]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
@@
                \huge
-               \textbf{Messaging Architecture for Integration of Customer Self-Services}
+               \textbf{Messaging Architecture for Integration of Identity Management Systems}
           }
@@
 
-The solution to this problem is an Identity Management System (IMS) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles of SPs.
-To replace User Profiles of SPs, the IMS can not only rely on systems for registration, authentication, authorisation and provisioning.
+The solution to this problem is an Identity Management System (IMS) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles.
+The system itself is provided and hosted by a SP for consumption by other SPs.
+To replace existing User Profiles, the IMS can not only rely on systems for registration, authentication, authorisation and provisioning.
 Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
@@
 \chapter{Objective}
-Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of SPs with existing user profiles to make their services accessible through an Identity Management System.
-In the example of the OZG, the integration architecture should enable users to access administrative services of a member state through usage of an IMS instead of a User Profile.
-The two points of integration are on one hand-side the system architecture relevant for the OZG in form of a list of system components and on the other hand-side a connector provided by the IMS.
-Integration patterns are used to formulate the integration architecture in order to utilize a combination of established and tested messaging solutions.
-In order to save investments the integration reuses as many system components as possible and modifies as few system components as necessary.
+Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management System.
+In order to make the integration architecture suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
+The integration architecture is however not only applicable in cases relevant for OZG but also for other Service Providers with similar requirements.
+As requirements of SPs are not guaranteed to be similar to those of the OZG, the integration architecture is built to be expendable.
+
+The \textbf{integration architecture} for the OZG enables the \textbf{IMS functionalities} to be usable for selected \textbf{OZG scenarios} by integrating a \textbf{connector} in the \textbf{system architecture} of a member state.
+
+\begin{itemize}
+    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example be the application for an administrative service or the communication with a governmental institution.
+    \item The system architecture is based on documentation about architecture plans of member states.
+    \item The functionalities of the IMS are based on a requirements analysis of OZG scenarios and additional research.
+    \item The connector is defined based on functionalities the integration architecture requires from the IMS.
+    \item The integration architecture is the main scientific contribution of this bachelor thesis.
+It is based on messaging patterns in order to utilize a combination of established and tested messaging solutions.
+In order to save investments it also reuses as many system components as possible and modifies as few system components as necessary.
+\end{itemize}
 
 \chapter{Structure of Work}
-
 In the beginning of the thesis, basic concepts and terminology is explained on which the following chapters will rely.
@@
 
+This chapter defines many of the terms which were used in the previous introduction and further elaborates the underlying concepts and relevance for the objective of the bachelor thesis.
+
 \section{Service Provider}
@@
 \section{Online Self-Service}
-Online self-service (OSS) describes a method used by service providers to make their services available to the user.
+Online self-service (OSS) describes a method used by Service Providers to make their services available to the user.
 The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way.
-The user can be supported by a variety of software solutions.
+The user is usually supported by a variety of software solutions.
 
@@
 Depending on the use case, the tools can be transactional or informing.
-Informing tools help users to receive relevant information, often replacing human customer support.
-Transactional tools help users to interact with services in a persistent way to for example save data or trigger business processes.
+Informing tools help users to retrieve relevant information, often replacing human customer support.
+Transactional tools help users to interact with services in a persistent way to for example save personal data or trigger business processes.
 
 Information tools can be for example so called "WiKi" pages or search fields which assist the user in his process of finding information.
-Transactional tools can be for example online forms which assist the user in his process of initiating an ordering business process.
+Transactional tools can be for example online forms which assist the user in his process of triggering an order placement business process.
 
@@
 
-Identities are managed by the system architecture of SPs through identity providers (Idp).
-
-- Problem multiple identities
-
-- Modern Identity models
-
--
-
 \section{User Profile}
 
-- self service for identities
-
-- problem multiple user profiles
-
-\section{}
-
-\section{OSS Profile Provider}
-
-\section{Connector}
-
-\section{Online Self-Service}
-Self-service has existed for a long time.
-It generally means the consumption of some service without human interaction but rather in a self-reliant way.
-One example which is still relevant today are restaurants offering buffets.
-Instead of a waiter, customers take food for themselves - in self-service.
-In spring, some farmers allow people to pick flowers from the acre in exchange for a small fee.
-
-In recent decades technology made advanced methods of digital self-service possible.
-Money can be withdrawn from local ATMs and train tickets can be bought from ticket machines.
-Technological advancements, at least directed to the average consumer, can be seen as advancements in self-service capabilities.
-Consumers buy technology which makes them independent from the help of other people.
-
-Since the internet enabled the connection of a very large amount of people, especially the world wide web made it accessible to the general public.
-It enables any user to access and interact with technological systems all over the world through a user friendly visual interface.
-Today, many of those systems are provided by enterprises and other organizations for customers and users to access their services.
-
-- they enable customers online self-service (OSS).
-
-Online self-service is defined as: self-reliant consumption of services over the internet without human to human interaction.
-
-Depending on the reasoning most websites on the WWW can be described as providing online self-service. OSS therefore rather describes a perspective on the WWW than a use case.
-
-Tow categories of OSS can be differentiated: The information category contains cases where users are enabled to retrieve relevant information.
-The transaction category contains cases where users modify the systems they interacts with to for example save data or trigger some internal business process.
-
-An example for retrieving information through OSS are so called "WiKi" pages.
-Similar to the famous website "Wikipedia", information about for example the usage of a product can be made accessible to customers.
-In this case, it is not necessary any more to call a support hot-line.
-Another example are online learning platforms which provide customers with necessary information to for example learn a language. In this case, it is not necessary any more to meet teachers.
-Online job hunting websites enable its users to find information about job offers which fit their requirements. In this case it is not necessary any more to visit employment bureaus.
-
-A common use case for transaction through OSS are online retailers which enable users to start payment and delivery processes.
-They are often accompanied by OSS for information in order to find and select products.
-In this case it is not necessary any more to go to the local shopping mall.
-Another use case is the management of user identities which enables users to authenticate themselves and manage personal information.
-In this case it is not necessary any more to show up in person at for example a store in order to identify ones identity and give personal information about for example the living address.
-
-Reasons for the widespread usage of online self-service are significant benefits in ease of service usability for customers and cost reduction for enterprises.
-Customers can self-service from almost every place, easily manage customer data like phone number and address, configure services like subscription plans and access lots of information on available products or trouble shooting steps in an immediate way.
-Online customer self-service improves usability, saves time, increases availability, saves money and therefore increases customer experience.
-Enterprises, especially in progressive countries, aim to keep employment at a minimum, as it is a big cost factor.
-
-Digital self-service turns customers into unpaid employees.
-
-\subsection{OSS Provider}
-In order for customers to use online self-service, companies and institutions have to provide the necessary software tools. Depending on category and use case of OSS, different software tools exist.
-
-A chain of stores might provide tools which enables the users to inform themselves about available products and opening hours.
-This could for example be a search functionality for stores in the local area and a catalogue of available products of a selected store.
-Online retailers however will require additional tools which for example enable management of user profiles to authenticate and communicate with customers.
-
-OSS providers are defined as: enterprises which develop and maintain solutions for OSS and make them accessible to system architectures of customers.
-
-Depending on the complexity of the solution, different methods of access are possible.
-One possibility would be to provide a self-contained software, the customer can deploy in his system architecture.
-This can be done for example in the case of solutions for WiKi-pages where the customer installs respective software in his web server.
-Another possibility would be, for the OSS provider to host the solution himself and provide system architectures of customers access.
-This can be done for example in the case of retailers which contain systems only for managing a catalogue of available products and processing incoming orders.
-They could integrate an online shop solution hosted by a OSS provider through using a business connector.
+\section{Identity Management System}
 

### 2020-12-18 msc-thesis.tex
Introduction

@@
 Many tools require identification of a user in case interactions or initiated business processes have to be associated with him.
-An identity provider (IdP) who stores partial identities of users therefore is part of numerous system architectures.
-This leads to customers of SPs to be associated with multiple partial identities - one for each SP.
+A system for management of identities of users therefore is part of numerous system architectures.
 Service Providers usually enable users to manage their partial identities using online self-service through so called User Profiles.
+Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP
 
-The issues of this approach becomes clear for a large amount of partial identities.
-The more Service Providers a person is customer of, the more partial identities he will have to manage through user profiles.
-Changing the home address in each profile becomes a major inconvenience.
-More serious problems occur for example through the increased risk of data breaches.
+The result is a digital identity crisis \cite{IdentityCrisis}:
+\begin{itemize}
+    \item Multiple SPs collect, use and share parts of identities which leads to a distributed and fragmented identity.
+    \item As a result of the distributed identity, risk of data breaches increases.
+    \item Managing multiple use profiles is very inconvenient for users.
+    \item It is often unclear who stores which data and for what purpose.
+    \item SPs have an incentive to collect and share more user data than they need, to provide their service.
+\end{itemize}
 
@@
 One model called Social Login became popular.
-It enables customers to leverage existing User Profiles of social networks like Facebook to create new User Profiles for Service Providers.
-This improves identity management by enabling SPs to rely on the identity information they are provided by the external profile.
-Users can manage identity related information through their Social Profile and each change would then be propagated to User Profiles of connected SPs.
+It enables customers to create User Profiles for SPs through existing User Profile of Social Networks like Facebook.
+This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes.
+Users can therefore manage identity related information through their Social Profile which is accessed by the SP.
 
-This approach, however, still leaves the requirement of User Profiles for each SP because depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
-This includes for example subscriptions or contracts.
+This approach, however, still leaves the requirement of User Profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
+SPs also might require additional online self-service tools the social network does not provide.
 
-The solution to this problem is an Identity Management System (IMS) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles.
+The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles.
 The system itself is provided and hosted by a SP for consumption by other SPs.
-To replace existing User Profiles, the IMS can not only rely on systems for registration, authentication, authorisation and provisioning.
+To replace existing User Profiles, the IMP can not only rely on systems for registration, authentication, authorisation and provisioning.
 Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
 
-In order for an SP to use identities and services of an IMS, an integration into the system architecture of the SP has to take place.
+In order for an SP to use identities and services of an IMP, an integration into the system architecture of the SP has to take place.
 Due to the complex nature of system architectures and identity management, this is a difficult task.
 
-A currently relevant example for usage of online self-service with particular interesting requirements for identities is the "Online Access Law" (OZG).
+A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG).
 It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
@@
 \chapter{Objective}
-Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management System.
+Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management Provider.
 In order to make the integration architecture suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
@@
 
-The \textbf{integration architecture} for the OZG enables the \textbf{IMS functionalities} to be usable for selected \textbf{OZG scenarios} by integrating a \textbf{connector} in the \textbf{system architecture} of a member state.
+The \textbf{integration architecture} for the OZG enables \textbf{IMP functionalities} to be usable for selected \textbf{OZG scenarios} by integrating a \textbf{connector} in the \textbf{system architecture} of a member state.
 
@@
     \item The system architecture is based on documentation about architecture plans of member states.
-    \item The functionalities of the IMS are based on a requirements analysis of OZG scenarios and additional research.
-    \item The connector is defined based on functionalities the integration architecture requires from the IMS.
+    \item The functionalities of the IMP are based on a requirements analysis of OZG scenarios and additional research.
+    \item The connector is defined based on functionalities the integration architecture requires from the IMP.
     \item The integration architecture is the main scientific contribution of this bachelor thesis.
@@
 \chapter{Structure of Work}
-In the beginning of the thesis, basic concepts and terminology is explained on which the following chapters will rely.
+In the beginning of the thesis, terminology and basic concepts are explained.
+This includes definitions of terms like Online Self-Service, Identity and Identity Management.
+The concept of Identity Management Providers and the Online Access Law are explained.
+The special relevance for integration of IMPs and OZG are described.
 
 Then, preparatory work relevant for the integration architecture is presented.
-Based on process diagrams of digitalized administration services, several use cases of OSS are listed and evaluated for their relevance.
-They provide important information on which functionalities the IMS is required to have and the integration architecture is required to integrate.
-
-An integration approach through a connector is used. Concrete functionalities and interfaces of a possible connector are specified for usage by the integration architecture.
-
+Relevant OZG scenarios based on digitisation documentations of administrative services are analyzed in order to define important features the IMP is required to have.
+The connector which makes the IMP accessible towards the integration architecture is documented.
 Based on documentation of system architectures of several member states, relevant components of the architecture relevant for the OZG are selected.
@@
 
-The integration architecture integrates previously documented connector and components of the system architecture in order to make the selected OSS cases usable with the IMS.
-The architecture is presented iteratively.
+The integration architecture integrates previously documented connector and components of the system architecture in order to make selected OZG scenarios usable with the IMP.
+The architecture is presented iterative.
 Each iteration contains increasingly demanding requirements along with the documentation of the increasingly complex integration architecture.
@@
 
-In order to validate the integration architecture, the execution of one administration service with usage of the IMS is evaluated in theory.
+In order to validate the integration architecture, the execution of one administration service with usage of the IMP is evaluated in theory.
 
@@
 
-This chapter defines many of the terms which were used in the previous introduction and further elaborates the underlying concepts and relevance for the objective of the bachelor thesis.
+\section{Terminology}
 
-\section{Service Provider}
+\subsection{Service Provider}
 Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.
 
-\section{Online Self-Service}
+\subsection{Online Self-Service}
 Online self-service (OSS) describes a method used by Service Providers to make their services available to the user.
@@
 
-\section{Self-Service Tools}
+\subsection{Self-Service Tools}
 Self-service tools are software solutions for customers to enable a online self-service experience.
@@
 
-\section{Identity}
+\subsection{Digital Identity}
+The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information.
+This includes a set of identifiers which are pieces of information that can uniquely identify an entity and attributes which describe properties of an entity but do not uniquely identify it.
+It is also possible to use an aggregation of attributes as identifier.
 
-\section{User Profile}
+Identifiers which are commonly used by SPs are the phone number and E-Mail address.
+Attributes are for example nicknames, hobbies, interests or education.
+The full name of a person is often not sufficient unique identification, the aggregation of name, age and home address can therefore be used as identifier.
 
-\section{Identity Management System}
+\subsection{Partial Digital Identity}
+A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.
 
-\section{OZG}
+\subsection{Identity Management}
+Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities.
+The possible utilization of identities depends on the system for management of identities.
+It could be for example authorization for a service or communication through an inbox.
 
-This section introduces the law for improvement of online access of administrative services (Online Access Law - OZG), its origin, purpose and planned realization.
+\subsection{Identity Management System}
+Identity management systems are solutions which enable SPs and customers to manage identities.
 
-\subsection{Context}
+\subsection{User Profile}
+User profiles are one method for identity management.
+They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.
 
+\section{Digital Identity Crisis}
+The current situation of digital identities has the following core issues:
+\begin{itemize}
+    \item aktuelle übersicht über identitiy management
+    \begin{itemize}
+        \begin{itemize}
+            \item oAuth
+            \item saml
+        \end{itemize}
+        \item Social Login
+        \item central idps
+        \item idendity federation (SOcial login, Single sign on)
+        \item device identity kopplung
+        \item SSI
+    \end{itemize}
+\end{itemize}
+
+\section{Identity Management Provider}
+Identity management providers (IMP) are a method for identity management which aims to solve the digital identity crisis.
+They are characterized by giving SPs access to customer identities for which they provide one-stop online self-service.
+The important aspect of IMP is, that the identity is stored and managed in one place and its utilization is enabled through integration with system architectures of multiple SPs.
+
+\subsection{Objective}
+The IMP method can solve the identity issues the following way:
+
+\subsection{IMP System}
+A system for IMP can work as follows:
+
+Additional requirements for IMP systems can exist and are analyzed as part of the preparatory work.
+
+\subsection{Integration}
+The IMP system has to be integrated. A connector is used:
+
+\subsection{Challenges}
+The IMP system has the following problems / open questions regarding integration:
+\begin{itemize}
+    \item which personal information resides at SP systems an which at IMP systems? => data the user personally manages resides at IMP systems, derived data etc. at SP systems
+    \item should data be mirrored at the SP and just a synchronisation functionality exist
+\end{itemize}
+
+\section{Online Access Law}
 The Federal Ministry of the Interior, Building and Community is, amongst other things, responsible for modernizing public administration \cite{BMI:Moderne_Verwaltung}.
@@
 Modernization of the administration, however, is not exclusive to Germany as in 2018 the European Parliament and Council decided on a Single Digital Gateway (SDG) providing uniform access to digital administrative governmental services of every European country \cite{BMI:Single_Digital_Gateway}.
-
-\subsection{Motivation}
 
@@
 The German government recognizes the possible improvements and presents, amongst other things, the OZG as a solution. \cite{IT-Planungsrat:Herausforderung}
-
-\subsection{The OZG}
 
@@
 
-\subsection{OZG Execution}
-
 Execution of the OZG can be separated into two projects: Digitalization and Networking.
@@
 
-Many services, which are still bound to paper must be digitalized.
+Many services, which are still bound to paper must be digitized.
 In total, the BMI lists 575 relevant services.
@@
 
+The OZG is a fitting example for integration of IMP solutions and could benefit from it because:
+
 \chapter{Preparatory Work}
 
-\section{OZG OSS Scenarios}
+\section{OZG Processes}
+
+\begin{itemize}
+    \item selecting important processes (priority 1)
+    \item describing processes: purpose, result, etc
+    \item process diagram visualizing
+    \item 
+\end{itemize}
+
+\section{OZG Scenarios}
+
+\begin{itemize}
+    \item structuring parts of upper processes into clusters
+    \item 
+\end{itemize}
 
 The information platform of the OZG contains information about many administration services in form of process diagrams \cite{BMI:Ergebnisse}.
-They serve as a resource to identify important OSS scenarios of administration processes.
+They serve as a resource to identify important OZG scenarios of administration processes.
 The following scenarios were identified:
@@
 
-\section{OSS Connector}
-
 \section{OZG System Architecture}
-This section describes the system architecture of a member state relevant for the execution of the OZG an integration of a OSS provider.
+This section describes the system architecture of a member state relevant for the execution of the OZG and integration of an IMP.
 Due to a lack of detailed information, the system architecture is described by components responsible for a category of tasks.
@@
 
+\section{IMP System}
+List of functionalities of the IMP System based on research and analysis of the OZG scenarios:
+
+\section{IMP Connector}
+Interfaces of the connector for usage by the integration architecture:
+
+\section{Integration Thoughts}
+
+\subsection{OZG}
+
+\subsection{IMP}
+
 \chapter{Integration Architecture}
 
-This chapter presents a message based integration architecture which enables access to OSS features of member states through a OSS provider.
+This chapter presents a message based integration architecture which enables access to OZG features of member states through an IMP.
 Multiple versions of an integration architecture are presented which fulfill increasingly complex requirements.
-Requirements are formulated as user scenarios which should be accomplishable through the OSS provider.
+Requirements are formulated as user scenarios which should be achievable through the IMP.
 Each version is presented in the form of multiple flow charts, each describing sequential steps while carrying out a required scenario and a corresponding messaging infrastructure.

### 2020-12-22 msc-thesis.tex
New structure

@@
                \huge
-               \textbf{Messaging Architecture for Integration of Identity Management Systems}
+               \textbf{Integrating Identity Management Providers based on Online Zugangs Gesetz}
           }
@@
 
-The result is a digital identity crisis \cite{IdentityCrisis}:
+The result is variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
 \begin{itemize}
-    \item Multiple SPs collect, use and share parts of identities which leads to a distributed and fragmented identity.
-    \item As a result of the distributed identity, risk of data breaches increases.
+    \item Multiple SPs collect, use and share parts of identities which leads to distributed and fragmented identities.
+    \item As a result of the distributed identities, risk of data breaches increases.
     \item Managing multiple use profiles is very inconvenient for users.
     \item It is often unclear who stores which data and for what purpose.
-    \item SPs have an incentive to collect and share more user data than they need, to provide their service.
+    \item SPs have an incentive to collect and share more user data than they need.
 \end{itemize}
@@
 \begin{itemize}
-    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example be the application for an administrative service or the communication with a governmental institution.
+    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example the application for an administrative service or the communication with a governmental institution.
     \item The system architecture is based on documentation about architecture plans of member states.
@@
 
+The integration architecture ...
+
 \chapter{Structure of Work}
-In the beginning of the thesis, terminology and basic concepts are explained.
-This includes definitions of terms like Online Self-Service, Identity and Identity Management.
-The concept of Identity Management Providers and the Online Access Law are explained.
-The special relevance for integration of IMPs and OZG are described.
+The "Fundamentals" chapter explains terminology and basic concepts.
 
-Then, preparatory work relevant for the integration architecture is presented.
-Relevant OZG scenarios based on digitisation documentations of administrative services are analyzed in order to define important features the IMP is required to have.
-The connector which makes the IMP accessible towards the integration architecture is documented.
-Based on documentation of system architectures of several member states, relevant components of the architecture relevant for the OZG are selected.
-Each component is explained in detail along with the functionalities it provides for usage by the integration architecture.
+In the following chapter called "Identity Management System" the thesis analyzes requirements for identity management through the perspective of the user and through the perspective of service providers for the OZG.
+It is presented, how an identity management provider could solve current identity management problems and which challenges for an integration exist.
 
-The integration architecture integrates previously documented connector and components of the system architecture in order to make selected OZG scenarios usable with the IMP.
-The architecture is presented iterative.
-Each iteration contains increasingly demanding requirements along with the documentation of the increasingly complex integration architecture.
-Each documentation is done through textual explanations, multiple flow diagrams and one messaging architecture.
+The chapter "Integration Proposal" first documents a possible IMP system and connector, based on the requirement analysis of the previous chapter.
+It then presents the integration architecture with iteratively increasing requirements through textual description, multiple flow diagrams and messaging architectures.
 
-In order to validate the integration architecture, the execution of one administration service with usage of the IMP is evaluated in theory.
+A "Solution Evaluation" analyzes benefits and problems of the proposed solution.
+
+The "Outlook" will conclude the thesis by presenting possibilities for advanced integration architectures.
 
@@
 
-\subsection{Service Provider}
+\paragraph{Service Provider}
 Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.
 
-\subsection{Online Self-Service}
+\paragraph{Online Self-Service}
 Online self-service (OSS) describes a method used by Service Providers to make their services available to the user.
@@
 
-\subsection{Self-Service Tools}
+\paragraph{Self-Service Tools}
 Self-service tools are software solutions for customers to enable a online self-service experience.
@@
 
-\subsection{Digital Identity}
+\paragraph{Digital Identity}
 The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information.
-This includes a set of identifiers which are pieces of information that can uniquely identify an entity and attributes which describe properties of an entity but do not uniquely identify it.
+Each piece of personal information is an attribute.
+Attributes can be identifiers which are able uniquely identify an entity.
 It is also possible to use an aggregation of attributes as identifier.
@@
 
-\subsection{Partial Digital Identity}
+\paragraph{Partial Digital Identity}
 A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.
 
-\subsection{Identity Management}
+\paragraph{Identity Management}
 Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities.
@@
 
-\subsection{Identity Management System}
-Identity management systems are solutions which enable SPs and customers to manage identities.
+\paragraph{Identity Management System}
+Identity management systems are solutions which enable SPs and customers to manage identities or partial identities.
+They usually provide the following functionalities an properties:
+\begin{itemize}
+    \item 
+\end{itemize}
 
-\subsection{User Profile}
+\paragraph{User Profile}
 User profiles are one method for identity management.
@@
 
-\section{Digital Identity Crisis}
-The current situation of digital identities has the following core issues:
-\begin{itemize}
-    \item aktuelle übersicht über identitiy management
-    \begin{itemize}
-        \begin{itemize}
-            \item oAuth
-            \item saml
-        \end{itemize}
-        \item Social Login
-        \item central idps
-        \item idendity federation (SOcial login, Single sign on)
-        \item device identity kopplung
-        \item SSI
-    \end{itemize}
-\end{itemize}
+\section{Identity Management Provisioning (IMP)}
+Identity management provisioning (IMP) is a method for identity management which is characterized by an identity management provider hosting an identity management system for "non-partial" identities.
+The identity management system provides one-stop online self-service for users and manages the storage of identities.
+SPs are provided access to the identities of the identity management system.
 
-\section{Identity Management Provider}
-Identity management providers (IMP) are a method for identity management which aims to solve the digital identity crisis.
-They are characterized by giving SPs access to customer identities for which they provide one-stop online self-service.
-The important aspect of IMP is, that the identity is stored and managed in one place and its utilization is enabled through integration with system architectures of multiple SPs.
+The following are functionalities of an IMP system in addition to those of conventional identity management systems:
 
-\subsection{Objective}
-The IMP method can solve the identity issues the following way:
+\paragraph{Attribute Management}
+It is common for identity management systems to enable users to manage a predetermined set of attributes.
+IMP systems however do not just manage partial identities and therefore enable users to manage any possible attribute of their identity.
+Users therefore can add, remove and modify any attribute.
 
-\subsection{IMP System}
-A system for IMP can work as follows:
+As often, attributes of a digital identity are defined by service providers, they are also able to create new attributes or delete and modify existing ones, if approved by the user.
 
-Additional requirements for IMP systems can exist and are analyzed as part of the preparatory work.
+\paragraph{Online Self-Service}
+Many attributes, especially those created by SPs, do not make sense to the user without context and my be heavily dependant on systems of a SP.
+Therefore, the IMP provides solutions for online self-service which supports the management of attributes.
 
-\subsection{Integration}
-The IMP system has to be integrated. A connector is used:
+\paragraph{Integration}
+Service providers which use IMP systems as solution for identity management require access to its services and have to make their existing systems work with them.
+The IMP solution therefore provides interfaces which enable the SP to access services.
+As it is in the best interest of the IMP solution to integrate SPs, advanced integration methods reducing the integration effort for SPs can be provided.
 
-\subsection{Challenges}
-The IMP system has the following problems / open questions regarding integration:
-\begin{itemize}
-    \item which personal information resides at SP systems an which at IMP systems? => data the user personally manages resides at IMP systems, derived data etc. at SP systems
-    \item should data be mirrored at the SP and just a synchronisation functionality exist
-\end{itemize}
-
-\section{Online Access Law}
-The Federal Ministry of the Interior, Building and Community is, amongst other things, responsible for modernizing public administration \cite{BMI:Moderne_Verwaltung}.
-Current modernization efforts lie in the construction of an E-Government \cite{BMI:Behoerdengaenge}.
-The E-Government-Law in 2013 was an early step increasing internal usage of digital systems in governmental administration.
-This includes for example the usage of digital personal files and scanning of documents for replacement \cite{BMI:E-Government_Gesetz}.
-In 2017 the German government passed the law for improvement of online access to administrative services (OZG) which focuses on usage of administration services by the people \cite{BMI:Onlinezugangsgesetz}.
-Modernization of the administration, however, is not exclusive to Germany as in 2018 the European Parliament and Council decided on a Single Digital Gateway (SDG) providing uniform access to digital administrative governmental services of every European country \cite{BMI:Single_Digital_Gateway}.
-
-Customers on the free market are used to One-Stop-Shops providing access to services of companies in one digital place.
-Many self-service methods improve the user experience: Customers of e-commerce companies can put products in a digital shopping card, pay with digital money and select a location for delivery.
-In most cases, no direct human to human interaction is required.
-Customers complete the process of ordering in self-service.
-The progress of online self-service usage on the free market is a result of the ongoing digitalization of the world and the competitiveness of the market.
-Today, many customers own personal computers or smartphones and companies providing easy access to their services via online self-service have an advantage in the market.
-Governmental institutions provide administrative services for customers.
-This can for example be an application for child benefit or a new ID card.
-In contrast to the free market, access to administrative services is, in most cases, not available through online self-service.
-Reasons are, that digitalization is expensive and governmental institutions do not have competitors.
-Digitalization of governmental administration could for example enable users to inform themselves about available administrative services and access them over the internet.
-The need to personally appear in offices of an administration would be reduced.
-Communication about questions or required documents could also happen faster, more immediate, and more reliable over the internet than over mail.
-Governmental institutions could reduce bureaucracy through modernization of registries and the once-only principle.
-The German government recognizes the possible improvements and presents, amongst other things, the OZG as a solution. \cite{IT-Planungsrat:Herausforderung}
-
-The law for improvement of online access of administrative services (Online Access Law - OZG) passed in 2017 and requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
+\section{Online Access Law (OZG)}
+In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
 \begin{enumerate}
@@
 
-Execution of the OZG can be separated into two projects: Digitalization and Networking.
-Digitalization focuses on transformation of existing processes and services to be using modern technologies.
-This includes most importantly the digitalization of governmental administrative services.
-The networking focuses on connecting existing and future governmental systems to make digitalization universally usable.
-This includes most importantly the construction of administration portals which are connected in a portal network.
+Execution of the OZG can be separated into two projects:
 
-Many services, which are still bound to paper must be digitized.
-In total, the BMI lists 575 relevant services.
-Some of them are provided by the federal republic, some by the member states and yet other by the communes.
-Respective to these responsibilities, the task of digitalization is distributed between federal republic and member states, where each member state is assigned to take the lead for specific areas.
-\cite{BMI:Onlinezugangsgesetz} Results of the digitalization are documented on the "OZG-Informationsplattform" \cite{BMI:Informatiosplattform} as process diagrams and data schemata.
+\paragraph{Digitalization}
+Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions.
+The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:
 
-Administrative services are made available through administrative portals which are be provided by federal republic, each member state and each commune.
-Communes integrate their portals with corresponding member states.
-The portals are connected through an "Online-Gateway" and form a portal network.
+A digitized administrative service can be accessed by a user through a website.
+The website is hosted either by the federal republic or a member state and is called "Administration Portal".
+Access is usually provided through an application form.
+The administrative service can be managed through a user profile which is provided by the federal republic or the member state.
+Management of an administrative service usually includes starting the service by sending in a form, communicating with responsible institutions through the inbox of the profile and receiving a result.
+The user profile can also enable users to upload documents to a data wallet and to save personal information for automatically filling in forms.
 
-Federal republic and each member state provide digital access to administrative services.
-An important method is called "one for all": One member state manages the digitalization of a category of administrative services and makes them digitally accessible for every other member state.
-Every administrative service can be found through a search function provided by every portal of the network.
+Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal.
+In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and yet other by the communes \cite{BMI:Onlinezugangsgesetz}.
 
-Depending on the administrative service, a user profile is required to verify ones identity.
-As federal republic and most member states already provide their own user profiles, the "IT-Planungsrat" decided to save investments by connecting them to an interoperable user profile.
+\paragraph{Networking}
+The networking focuses on connecting governmental systems to make all digitized administrative services available for every user.
+This includes most importantly the connection of administration portals to a portal network through an online gateway and the interoperability of user profiles.
 
-There exists a low, substantial and high level of authentication security when logging in to a user profile or when creating one.
-A low trust level is for example the usage of a username and password combination, a high trust level is for example the usage of the eID feature of the German ID card.
-Depending on the administrative service a profile tries to access, a different trust level is required.
+In order to save investments a method called "one for all" is used when hosting administrative services.
+One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood".
+As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal.
+Interoperable user profiles enable usage of each profile for management of administrative services on all portals.
 
-Profiles also enable users to save personal data in a data wallet and to communicate with institutions through an inbox.
+\subsection{Administrative Service}
+Unemployment benefit (Arbeitslosengeld II: AGII) is selected as an example for a digitized administrative service, because it has a high priority according to the "OZG-Informationsplattform" and is well documented.
 
-The OZG is a fitting example for integration of IMP solutions and could benefit from it because:
+The AGII is accessible through the "one for all" method through the administration portal of the federal republic.
+The digitalization of the service was done by the member state Nordrhein-Westfalen.
+The purpose of this service is to enable application for unemployment benefit and the result is an approval or denial by the responsible institution of the commune.
+The digitized process of this service enhances it to be manageable on an administration portal trough a user profile in the following way:
 
-\chapter{Preparatory Work}
+In order to access the service, a user must authenticate for an existing user profile or create one.
 
-\section{OZG Processes}
+\subsection{System Architecture}
+This subsection describes the system architecture of a member state relevant for the execution of the OZG.
 
-\begin{itemize}
-    \item selecting important processes (priority 1)
-    \item describing processes: purpose, result, etc
-    \item process diagram visualizing
-    \item 
-\end{itemize}
+\subsubsection{System Components}
+The system architecture consists of the following system components where each component is responsible for processing a certain group of tasks:
 
-\section{OZG Scenarios}
+\paragraph{User Profile}
+Each member state provides its own user profile which manages the identity of a user.
+It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.
 
-\begin{itemize}
-    \item structuring parts of upper processes into clusters
-    \item 
-\end{itemize}
+\paragraph{Administration Portal}
+The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.
+
+\paragraph{Application Platform}
+The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions.
+It is possible to prefill the form with personal data stored inside the user profile.
+
+\paragraph{Institution}
+Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.
+
+\subsubsection{Data Objects}
+The system architecture processes the following data objects which are associated to certain system components:
+
+\chapter{Problem Analysis}
+
+\section{Requirement Analysis}
+
+\subsection{User Requirements}
+
+\subsection{OZG Requirements}
 
@@
 
-\subsection{Identity Management}
+\subsubsection{Identity Management}
 
-\subsubsection{Scenario Profile Management}
+\textbf{Scenario Profile Management}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Identity verification}
+\textbf{Scenario Identity verification}
 \begin{itemize}
@@
 
-\subsection{Request Management}
+\subsubsection{Request Management}
 
-\subsubsection{Scenario Request Preparation}
+\textbf{Scenario Request Preparation}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Request Creation}
+\textbf{Scenario Request Creation}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Request Delivery}
+\textbf{Scenario Request Delivery}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Request Processing}
+\textbf{Scenario Request Processing}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Request Finalization}
+\textbf{Scenario Request Finalization}
 \begin{itemize}
@@
 
-\subsection{Data Management}
+\subsubsection{Data Management}
 
-\subsubsection{Scenario Access Management}
+\textbf{Scenario Access Management}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Data Consistency}
+\textbf{Scenario Data Consistency}
 \begin{itemize}
@@
 
-\subsubsection{Scenario Data Accessibility}
+\textbf{Scenario Data Accessibility}
 \begin{itemize}
@@
 
-\section{OZG System Architecture}
-This section describes the system architecture of a member state relevant for the execution of the OZG and integration of an IMP.
-Due to a lack of detailed information, the system architecture is described by components responsible for a category of tasks.
-Each component is associated to data objects it processes.
-The definition of components and data objects are based on research about planned system architectures of member states.
+\section{Solution with IMP}
 
-\subsection{User Profile}
-Each member state provides its own user profile which manages the identity of a user.
-It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.
+\section{Integration Challenges}
+The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems.
+The origin of the challenges is the interoperability of the IMP identity with multiple SPs.
+It is the purpose of the integration architecture to solve as many of these challenges as possible.
 
-\subsection{Administration Portal}
-The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.
+\paragraph{Data Mapping}
+If multiple SPs and the user are able to add new attributes, there is the possibility of duplicate attributes with the same meaning but different name.
+It is also possible for SPs to utilize the same attribute but interpreting its meaning differently.
 
-\subsection{Application Platform}
-The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions.
-It is possible to prefill the form with personal data stored inside the user profile.
+\paragraph{Identity Attributes}
+Service providers are able to add attributes to an identity.
+It, however, is not clear which information should be added to an IMP system as part of an identity and which information should be stored by the individual SPs.
+One reason is, that service providers exist for which creation and utilization of personal information is a business model.
+For those SPs, the secrecy of certain types of personal information is important.
+One example would be information about product preferences of customers acquired by online retailers for usage with recommender systems.
+A guideline could be, to only add attributes to the IMP system, which should be directly managed by users.
 
-\subsection{Institution}
-Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.
+\paragraph{Online Self-Service}
+SPs might add attributes to the identity of an IMP system which have very special meanings which are not self-explanatory.
+The attribute might also adhere to a special data format or be conditioned by other attributes of the identity.
+The modification of the attributes might also require interaction with the system architecture of an SP.
+In order for the attributes to stay valid, management through online self-service tools which are provided by the system architecture of an SP might be required.
+
+In this case, the self-service tools should be accessible through the IMP systems in a user friendly way.
+
+\paragraph{Attribute Access}
+Attributes which were added by a SP might require restrictions towards the user.
+If for example a subscription status is saved as an attribute, the user should not be able to modify it without permission of the SP.
+
+\chapter{Integration Proposal}
+The bachelor thesis proposes an integration using a connector because:
 
@@
 
-\section{Integration Thoughts}
+\section{Basic Integration Architecture}
 
-\subsection{OZG}
+\subsection{Version 1}
 
-\subsection{IMP}
+\subsubsection{Requirements}
 
-\chapter{Integration Architecture}
+\subsubsection{Flow Diagrams}
 
-This chapter presents a message based integration architecture which enables access to OZG features of member states through an IMP.
-Multiple versions of an integration architecture are presented which fulfill increasingly complex requirements.
-Requirements are formulated as user scenarios which should be achievable through the IMP.
-Each version is presented in the form of multiple flow charts, each describing sequential steps while carrying out a required scenario and a corresponding messaging infrastructure.
+\includegraphics[width=15cm]{Basic Integration Onboarding.png}
 
-\section{Basic}
+\includegraphics[width=15cm]{Basic Integration Application.png}
 
-\subsection{Requirements}
-In the first version of the integration architecture, users of the OSS provider should be able to
-\begin{itemize}
-    \item fill in an application
-    \item authenticate
-    \item receive and send messages
-\end{itemize}
+\subsubsection{Messaging Architecture}
 
-\subsection{Flow Charts}
+\subsection{Version 2}
 
-\includegraphics[width=\textwidth]{Basic Integration Application.png}
+\subsubsection{Requirements}
 
-\includegraphics[width=\textwidth]{Basic Integration Onboarding.png}
+\subsubsection{Flow Diagrams}
 
-\subsection{Messaging Integration}
+\subsubsection{Messaging Architecture}
 
-\section{Advanced}
+\chapter{Solution Evaluation}
 
-\subsection{Requirements}
-
-\subsection{Flow Charts}
-
-\subsection{Messaging Integration}
-
-\chapter{Integration Architecture Evaluation}
-
-\section{Technology}
-
-\section{Customer Example}
-
-\section{Operating Manual}
+\section{Conclusion}
 
@@
 
-\begin{itemize}
-     \item Expanding integration architecture with capabilities for OSS scenarios of different areas than online administration self-service
-     \begin{itemize}
-          \item online payment self-service (PayPal, psd2)
-          \item online shopping self-service (Amazon)
-          \item online health care self-service (DVG)
-          \item online entertainment self-service (Netflix, YouTube, Spotify)
-          \item online information / support self-service (StackOverflow)
-     \end{itemize}
-\end{itemize}
+\section{Advanced Integration Architecture}
 

### 2020-12-22 msc-thesis.tex
Changed structure and added info about ozg basic use case

@@
 
-\subsection{Administrative Service}
-Unemployment benefit (Arbeitslosengeld II: AGII) is selected as an example for a digitized administrative service, because it has a high priority according to the "OZG-Informationsplattform" and is well documented.
+\subsection{Basic Use Case}
+The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}.
+Each process consists of multiple sub-processes.
+When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements.
+Those arrangements can be called the basic use case of OZG services.
 
-The AGII is accessible through the "one for all" method through the administration portal of the federal republic.
-The digitalization of the service was done by the member state Nordrhein-Westfalen.
-The purpose of this service is to enable application for unemployment benefit and the result is an approval or denial by the responsible institution of the commune.
-The digitized process of this service enhances it to be manageable on an administration portal trough a user profile in the following way:
+The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:
 
-In order to access the service, a user must authenticate for an existing user profile or create one.
+\paragraph{1. Selection of Application Form}
+The user visits any administration portal of the portal network and types a search term in the corresponding search field.
+The user is then presented with a list of search results consisting of administrative services.
+If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service.
+This page provides information about the administration service along with instructions on how to access the form for application.
+The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.
+
+\paragraph{2. Login to User Profile}
+Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
+The user has to finish authentication steps, which can consist for example of a username and password.
+Depending on the authentication method, a trust level of the current session is determined.
+With approval from the user, personal information from his profile is provided towards the form-server.
+
+\paragraph{3. Filling in of Application}
+Personal information from the user profile is used to by the form-server to fill as many fields of the form as possible.
+The form with prefilled information is then presented to the user.
+The interactive form can then be modified by the user.
+Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.
+
+\paragraph{4. Uploading Attachments}
+The user can upload documents to his user profile and reference them from the form.
+
+\paragraph{5. Submission of Application}
+The user again authenticates for his user profile and authorises the form-server to submit the application.
+The form-server saves the application until he is notified to delete it.
+The form-server submits the application to the administration portal which hosts the administrative service.
+
+\paragraph{6. Reception of Application by Administration Portal}
+The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.
+
+\paragraph{7. Submission of Application to Data-Exchange Platform}
+The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.
+
+\paragraph{8. Sending of Acknowledgment}
+The data-exchange platform notifies the user through the inbox functionality of the user profile if the application was submitted successfully.
 
@@
 \subsubsection{System Components}
-The system architecture consists of the following system components where each component is responsible for processing a certain group of tasks:
+The system architecture consists of the following system components where each component is responsible for providing a certain set of services:
 
@@
 
-\chapter{Problem Analysis}
+\chapter{Identity Management}
 
@@
 
-\subsection{User Requirements}
+\subsection{User Perspective}
 
-\subsection{OZG Requirements}
+\subsection{OZG Perspective}
 
-The information platform of the OZG contains information about many administration services in form of process diagrams \cite{BMI:Ergebnisse}.
-They serve as a resource to identify important OZG scenarios of administration processes.
-The following scenarios were identified:
+\section{IMP Solution Proposal}
 
-\subsubsection{Identity Management}
+\chapter{IMP Integration Architecture}
 
-\textbf{Scenario Profile Management}
-\begin{itemize}
-    \item Create a user profile
-    \item Delete a user profile
-    \item Check existence of a user profile
-\end{itemize}
+\section{Requirement Analysis}
 
-\textbf{Scenario Identity verification}
-\begin{itemize}
-    \item Login to a user profile
-    \item Provide multiple levels of security for identity verification
-    \item Usage of a guest profile
-\end{itemize}
+\subsection{Integration Challenges}
 
-\subsubsection{Request Management}
-
-\textbf{Scenario Request Preparation}
-\begin{itemize}
-    \item Search for administration services
-    \item Check necessity of a profile
-    \item Check required level of identity verification
-    \item Selection of institution responsible for processing the request (Specification of current location)
-\end{itemize}
-
-\textbf{Scenario Request Creation}
-\begin{itemize}
-    \item Filling in a form for an application
-    \item Automated filling in of form with saved personal data
-    \item Collaboration on application by multiple identities
-\end{itemize}
-
-\textbf{Scenario Request Delivery}
-\begin{itemize}
-    \item Transmission of an application to responsible institution
-\end{itemize}
-
-\textbf{Scenario Request Processing}
-\begin{itemize}
-    \item Period of validity of applications
-    \item Notification of user about missing information or documents
-    \item Transmission of missing information
-    \item Notification of user about required preliminary administration services
-    \item Communication through E-Mail
-    \item Cancel an application
-    \item Approvals of user to e.g. data protection or information transfer
-    \item Modification request of application after transmission
-    \item Notification of received application by institution
-    \item Request status update by user
-    \item Sending notification to confirm the reading of a message
-    \item Notification of certain events to separate person e.g. parents
-    \item Request of institution about explicit document
-\end{itemize}
-
-\textbf{Scenario Request Finalization}
-\begin{itemize}
-    \item Notification of outcome of process / application
-    \item Objection of user to result of the process
-    \item Access to signed digital formula of result of process
-    \item Definition of dates for evens
-\end{itemize}
-
-\subsubsection{Data Management}
-
-\textbf{Scenario Access Management}
-\begin{itemize}
-    \item Access to an application by multiple separate identities
-    \item Sharing of documents saved in a wallet
-\end{itemize}
-
-\textbf{Scenario Data Consistency}
-\begin{itemize}
-    \item Period of validity of documents
-    \item Profile data discrepancies between involved user profiles
-\end{itemize}
-
-\textbf{Scenario Data Accessibility}
-\begin{itemize}
-    \item Upload of e.g. documents and certificates
-    \item Saving personal data entered in a form to the user profile
-    \item Protocol of all processes accessible with information about interactions
-\end{itemize}
-
-\section{Solution with IMP}
-
-\section{Integration Challenges}
 The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems.
@@
 
-\chapter{Integration Proposal}
-The bachelor thesis proposes an integration using a connector because:
+\subsection{Basic Use Case}
 
-\section{IMP System}
-List of functionalities of the IMP System based on research and analysis of the OZG scenarios:
+\subsection{Extensions}
 
-\section{IMP Connector}
-Interfaces of the connector for usage by the integration architecture:
+\section{Integration Proposal}
 
-\section{Basic Integration Architecture}
+\subsection{IMP Connector}
 
-\subsection{Version 1}
+\subsection{Messaging}
 
-\subsubsection{Requirements}
+\section{Basic Use Case}
 
-\subsubsection{Flow Diagrams}
+\subsection{Process Integration}
 
-\includegraphics[width=15cm]{Basic Integration Onboarding.png}
+\subsection{Messaging Integration}
 
-\includegraphics[width=15cm]{Basic Integration Application.png}
+\section{Extension: Inbox}
 
-\subsubsection{Messaging Architecture}
-
-\subsection{Version 2}
-
-\subsubsection{Requirements}
-
-\subsubsection{Flow Diagrams}
-
-\subsubsection{Messaging Architecture}
+\section{Extension: Collaboration}
 
@@
 
-\chapter{Outlook}
-
-\section{Advanced Integration Architecture}
+\chapter{Outlook: Advanced IMP Integration}
 

### 2021-01-01 msc-thesis.tex
System architecture definition

@@
 
-\chapter{Context}
+\chapter{Introduction}
+
+\section{Context}
 Since invention of the World Wide Web, the number of its users increased rapidly.
@@
 
-\chapter{Objective}
+\section{Objective}
 Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management Provider.
@@
 
-\chapter{Structure of Work}
+\section{Structure of Work}
 The "Fundamentals" chapter explains terminology and basic concepts.
@@
 
-\chapter{Fundamentals}
+\chapter{Background and Related Work}
 
@@
 
-\paragraph{1. Selection of Application Form}
+\paragraph{1. Selection of Administrative Service}
 The user visits any administration portal of the portal network and types a search term in the corresponding search field.
@@
 
-\paragraph{3. Filling in of Application}
-Personal information from the user profile is used to by the form-server to fill as many fields of the form as possible.
+\paragraph{3. Filling in Application}
+Personal information from the user profile is used by the form-server to fill as many fields of the form as possible.
 The form with prefilled information is then presented to the user.
@@
 \paragraph{4. Uploading Attachments}
-The user can upload documents to his user profile and reference them from the form.
+The user can upload documents to his user profile and reference them in the form.
 
@@
 \subsection{System Architecture}
-This subsection describes the system architecture of a member state relevant for the execution of the OZG.
+This subsection describes the system architecture of a member state relevant for the execution the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen.
+Systems, which are responsible for coordination of OZG execution between member states and the federal republic are not the focus.
 
 \subsubsection{System Components}
-The system architecture consists of the following system components where each component is responsible for providing a certain set of services:
+The system architecture consists of the following system components.
+Each component consists of a list of services it provides either to the user or to other components.
+Components are defined based on strongly connected categories of services \cite{NRW:Umsetzung}:
+
+\paragraph{Administration Portal}
+The administration portal provides the user with a web-interface and implements user flows of digitized administrative processes by interacting with other system components.
+The main services are \cite{NRW:Umsetzung}:
+
+\begin{itemize}
+    \item \textbf{Search and find a form}
+
+    Due to the distributed responsibility for provisioning administrative services through for example the "one for all" method, it is not clear to the user, which member state provides which administrative service on his portal.
+Therefore, each administration portal provides a "Search and Find" functionality, which enables the user to find the correct administration portal and page, where the service is provided.
+In order for the administration portals to provide the "Search and Find" feature, an "Online Gateway" makes information about the location of administrative services accessible through a central data storage \cite{Capgemini:OnlineGateway}.
+
+    \item \textbf{Selection of administrative service}
+
+    In combination with the "Search and Find" feature, the user can select an entry of the search result and is forwarded to the corresponding web-page.
+Depending on the administrative service, the web-page can be hosted on the current or a different portal.
+It shows information about the selected service like a service description, requirements and possible outcomes and enables the user to open the corresponding form hosted by a form-server.
+
+    \item \textbf{Opening a form through a form-server}
+
+    The web-page of an administration portal describing the administrative service can integrate a form-server in multiple ways.
+The maybe easiest way is to add an URL which forwards the user to a web-page provided by the form-server.
+More advanced integration methods are possible where the form is rendered inside the web-page of the portal.
+
+    \item \textbf{Request of personal information from user profile}
+
+    Each member state and the federal republic provide interoperable user profiles.
+The administration portal is able to access the services of every user profile, which includes retrieval of personal information stored in the user profile.
+This requires a user to be logged into his user profile with a sufficiently high trust level.
+
+    \item \textbf{Transfer of personal data to the form-server}
+
+    If the administration portal was able to retrieve personal information from a currently active user profile, it can, with approval of the user, transmit it to the form-server which provides the form corresponding to the selected administrative service.
+
+    \item \textbf{Reception of applications from form-server}
+
+    The administration portal can request the application data from the form-server after it was notified of its "submission".
+
+    \item \textbf{Feedback to form-server}
+
+    The administration portal notifies the form-server, that it no longer has to store a certain application.
+
+    \item \textbf{Determination of receiving institution}
+
+    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender.
+It is the responsibility of the administration portal to determine which institution receives which application.
+
+    \item \textbf{Transfer to data-exchange platform}
+
+    The administration portal transfers the application to the data-exchange platform which is responsible for delivering it to the institution.
+\end{itemize}
+
+\paragraph{Form-Server}
+The from-server provides digital forms associated to administrative services.
+They can be accessed by a user profile through online self-service and submitted as applications to administrative institutions.
+The main services are \cite{dNRW:Standardisierungskonzeptzur}
+
+\begin{itemize}
+    \item \textbf{Retrieval of a digital form}
+
+    There exist many administrative services and depending on the member state or commune, the required layout of the application can be different.
+Therefore, a system called federal information management (Föderales Informationsmanagement: FIM) is used to standardize administrative services.
+FIM consists of three categories of building blocks.
+
+    \textit{Service blocks} contain human readable descriptions about a administrative service.
+
+    \textit{Data field blocks} contain the standardized description of data fields required for the application of administrative services.
+
+    \textit{Process blocks} contain standardized descriptions about the process of an administrative service.
+
+    Relevant for the form-server are data field blocks. A data field block can contain one element of five categories.
+
+    \textit{Data fields} are the "smallest entity" of a data field block and describes one standardized piece of information.
+Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.
+
+    \textit{Data field groups} consist of multiple data fields and other data field groups, relating to a category of information. A data field group can for example be "person" or "company".
+
+    \textit{Rules} describe all kinds of logical conditions of and between data fields.
+This includes for example the automatic validation of the correctness of an entered value or the activation and deactivation of data fields depending on an entered value.
+
+    \textit{Code lists} are lists of predefined values the user can select. This can for example be a list of all countries.
+
+    \textit{Data field schemata} is the combination of entities from all previously described categories and describes the structure of a form.
+
+    The building blocks are centrally managed by federal republic, member states and communes.
+This simplifies the creation of for example a new form by reusing existing data schema blocks and adding additional required data fields to a new data field schema.
+
+    Each data field block can be uniquely identified through an ID.
+Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data filed block from the central storage.
+
+    \item \textbf{Initiation of application}
+
+    The from-server can be requested to initiate an application using a certain form based on a FIM ID of a data field schemata.
+Along with the request, an identification and authorisation of a user profile has to be passed.
+Additional personal information of the user profile can be passed for automated filling in of the form.
+
+    \item \textbf{Status update to portal}
+
+    The form-server sends updates to the administration portal regarding the current status of the application. The possible status updates are listed in the interface section.
+
+    \item \textbf{Automatic filling in of form}
+
+    If the administration portal submitted personal data to the form-server, the form can automatically be filled in.
+This can be done because both the user profile and the form-server use the same data fields defined through FIM.
+
+    \item \textbf{Presentation of form}
+
+    The form can be integrated into the administration portal through for example an URL or Web-Component.
+
+    \item \textbf{Application interruption}
+
+    The application can be interrupted or aborted.
+Interruption may occur if the user stays inactive for a certain period of time while filling in the form.
+The user can also manually interrupt the editing process.
+If the application is interrupted, the form-server stores the unfinished application for a certain amount of time.
+The user can then access the application at a later time.
+
+    If the user decides to cancel editing the form, the application is deleted from the from-server.
+
+    Depending on the actions of the user, the status of the application changes accordingly and the administration portal is notified through a status update.
+
+    \item \textbf{Storage of application}
+
+    The form-server stores applications for a specified period of time if they were interrupted or submitted.
+In case of submission, the administration portal notifies the form server, if the application can be deleted.
+
+    \item \textbf{Provisioning stored applications}
+
+    The administration portal submits JWT to the form-server which corresponds to a user profile.
+Based on this information, the form-server searches all stored applications which belong to the user profile and sends back to the portal a list of URLs, through which the user can access them.
+
+    \item \textbf{Deletion of stored application}
+
+    If requested by the administration portal, the form-server can delete stored applications. This is usually the case after an application was submitted to the administration portal.
+
+    \item \textbf{Manually filling in data fields}
+
+    When the form is presented to the user, it can happen, that not all information could be automatically filled in. In this case, the form can be interactively filled in by the user.
+
+    \item \textbf{Uploading documents}
+
+    The user can add documents as attachments to an application. Uploaded documents are scanned for viruses.
+
+    \item \textbf{Authentication of user profile}
+
+    JSON web token from administration portal.
+
+    \item \textbf{Submission of application}
+
+    When the user submits the application by for example pressing a "submit" button, the form-server notifies the administration portal through a status update.
+The administration portal can then continue processing the application by requesting the application data from the form server.
+The portal does this by sending the form-server a FMS-ID it was sent by the form-server with the first status update.
+
+\end{itemize}
 
 \paragraph{User Profile}
-Each member state provides its own user profile which manages the identity of a user.
-It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.
+Each member state provides its own user profile for identity management. The main services are \cite{NRW:Umsetzung}:
 
-\paragraph{Administration Portal}
-The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.
+\begin{itemize}
+    \item \textbf{Identification and Authentification} \cite{dNRW:Anbindungsleitfaden}
 
-\paragraph{Application Platform}
-The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions.
-It is possible to prefill the form with personal data stored inside the user profile.
+    The user profile can be used for identification by transmitting personal information like name and address after successfully authentification.
+Authentification is the verification of an authentication.
+Users can authenticate for the user profile for example through a username / password combination.
+
+    \item \textbf{Determination Trust Level} \cite{dNRW:Anbindungsleitfaden}
+
+    The trust level of a logged in user profile is determined while registration and usage.
+The user can register and login to the user profile using a username / password combination or the German ID card.
+The trust level "High" is only granted, if the user registered using the German ID card \textbf{AND} logs in using the German ID card.
+All other combinations of registration and login result in a "normal" trust level.
+
+    \item \textbf{Management Personal Information} \cite{dNRW:Anbindungsleitfaden}
+
+    Personal information of the user profile can be managed through the administration portal after successful authentication.
+
+    \item \textbf{Provisioning Personal Information to Form-Server} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}
+
+    If a user selects to open the form of an administrative service which is integrated in the administration portal, the portal asks the user for permission to transmit personal information to the form-server.
+If the user is logged in and accepts, the administration portal retrieves the necessary personal information from the user profile and forwards it to the form-server.
+
+\end{itemize}
 
 \paragraph{Institution}
-Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.
+Institutions are the entities which eventually process the incoming applications and provide the users with solutions.
+They receive a digital application through the data-exchange platform.
+Institution are provided a special website on the administration portal, where they can interact with the user of an application through for example messages, status updates or requests for additional documents.
+Those interactions are done manually by an employee through the user interface of the website but can, to some degree, be automated.
+
+\paragraph{Data-Exchange Platform}
+The data-exchange platform delivers applications from the administration portal to the correct administrative institution.
+
+\subsubsection{Interfaces}
+The following interfaces of system components are relevant:
+
+\paragraph{Administration Portal and Form-Server}
+    \begin{itemize}
+        \item \textbf{Initiation of an application}
+
+            When the user selects to fill in a certain form on an administration portal, the portal submits the following data to the form-server through an interface:
+
+            \textbf{JSON Web Token}: 
+            If the user authenticated for a user profile on the administration portal, a JWT is created.
+This token authorizes its owner to automatically access services or resources as the corresponding user profile without the need of additional authentication.
+In order for the form-server to verify, that the current user is authenticated for the user profile, the portal submits a JWT token to it.
+
+            \textbf{User Profile ID}: 
+            Each user profile contains a unique identifier. This identifier is submitted to the form server in order to associate the application with a user.
+
+            \textbf{Personal Information}: 
+            The portal submits personal information to the form-server, so that the form can be automatically filled in.
+The user is asked if the data should be transmitted beforehand.
+This is therefore optional.
+
+            \textbf{Personal Information Schema ID}: 
+            The portal is aware of the currently selected administration service by the user and knows which the corresponding form is.
+It therefore sends the correct ID of a FIM data field schemata to the form-server.
+Based on this ID, the form-server knows which form to present to the user.
+
+        \item \textbf{Status Update}
+
+            When an application was initiated, it is associated with a status.
+If the status changes, the administration portal gets notified of the new status along with a FMS-ID.
+The FMS-ID is created by the form server and uniquely identifies the application.
+The application can have the following states:
+
+            \textbf{null}: The application and the corresponding form was successfully created
+
+            \textbf{submitted}: The form was filled in and the application is ready to be requested by the administration portal.
+
+            \textbf{filed}: The form was transmitted to the administration portal but the portal did not yet verify.
+
+            \textbf{confirmed}: The administration portal confirmed the successful reception of the application
+
+            \textbf{deleted}: The application was deleted by the form-server.
+
+        \item \textbf{Submission of application}
+
+            If the user presses a "submit" button on the interactive form, the status of the application changes to submitted and the administration portal is notified.
+The portal can then request the application data from the from-server through an interface by sending the FMS-ID and receives the following results:
+
+            \textbf{FMS-ID}:
+
+            \textbf{JSON Web Token}:
+
+            \textbf{User Profile ID}:
+
+            \textbf{XML File}:
+
+            This file consists of the personal information the form was filled in with
+
+            \textbf{Print version}:
+
+            The form-server can optionally sent a printable version of the filled in form
+
+            \textbf{Protocol Virus Scan}:
+
+            \textbf{Protocol Signature Check}:
+
+    \paragraph{Administration Portal and User Profile}
+
+    \begin{itemize}
+        \item \textbf{}
+    \end{itemize}
+
+    \end{itemize}
 
@@
 The system architecture processes the following data objects which are associated to certain system components:
+
+\subsection{Basic Use Case Flow Diagram}
 
@@
 
+\begin{itemize}
+    \item user wants to manage his data only on one platform
+    \item user wants to know who he provisions his personal information
+    \item user wants to communicate
+    \item user wants to know the reason each time his personal information is requested
+\end{itemize}
+
 \subsection{OZG Perspective}
@@
 \section{IMP Solution Proposal}
+
+\begin{itemize}
+    \item The administration portal / form-server sends the user/app the content of a form.
+The app will display the form and ask the user to fill it in.
+The interaction is displayed under a relation between the user and the requesting portal.
+When submitting, the app sends the data back to the portal and logs that the user transmitted the list of personal data.
+No authentication is necessary?
+The content is encrypted and the connector knows the pub.
+key?
+
+    Or relation is made with the responsible administrative institution.
+The administration portal determines the corresponding institution beforehand.
+In this case, the communication can also be done through the same relation and the personal data is provisioned to only the institution which needs it, not the whole member state or commune.
+
+    The IMP solution has to allow the inititation of relations and after that the request of information for new usage (Verwendungszweck) where the new usage is the application for a administrative service.
+\end{itemize}
 
@@
 
+\includegraphics[width=15cm]{Basic Integration Application.png}
+
 \subsection{Messaging Integration}

### 2021-01-06 msc-thesis.tex
Sequence Diagrams

@@
 \usepackage{csquotes}
-
+\usepackage{color, colortbl, tabularx, ragged2e}
+\definecolor{LightCyan}{rgb}{0.88,1,1}
+\newcolumntype{C}{>{\raggedright\arraybackslash}X} % centered "X" column
 % Fuer anderthalbzeiligen Textsatz
@@
 
+\paragraph{Data Wallet}
+
+\paragraph{Inbox}
+
 \subsubsection{Interfaces}
-The following interfaces of system components are relevant:
+In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards.
 
-\paragraph{Administration Portal and Form-Server}
+\begin{center}
+    \includegraphics[width=8cm]{Interaction Diagram.png}
+\end{center}
+
+\begin{enumerate}
+    \item The user interacts with the system architecture relevant for OZG only through the administration portal.
+The user is provided with a website as an interface with multiple online self-service functionalities.
+    \item Administration portal and form-server interact through a REST API. The API provides the following interfaces:
     \begin{itemize}
-        \item \textbf{Initiation of an application}
+        \item \textbf{Application initiation interface provided by form-server and used by administration portal}
 
-            When the user selects to fill in a certain form on an administration portal, the portal submits the following data to the form-server through an interface:
+        On the page of an administrative service on the administration portal, the user can press a button "to online application".
+Upon pressing the button, the portal interacts with the form server by transmitting data through an interface and receiving a response, see table \ref{table:interface_form_initialization}.
 
-            \textbf{JSON Web Token}: 
-            If the user authenticated for a user profile on the administration portal, a JWT is created.
-This token authorizes its owner to automatically access services or resources as the corresponding user profile without the need of additional authentication.
-In order for the form-server to verify, that the current user is authenticated for the user profile, the portal submits a JWT token to it.
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
 
-            \textbf{User Profile ID}: 
-            Each user profile contains a unique identifier. This identifier is submitted to the form server in order to associate the application with a user.
+            JSON Web Token & The portal received this JWT as a result of the login process with the user profile component.
+This token enables the form-server to verify the authentication of the user.
+& User Profile \\
 
-            \textbf{Personal Information}: 
-            The portal submits personal information to the form-server, so that the form can be automatically filled in.
-The user is asked if the data should be transmitted beforehand.
-This is therefore optional.
+            \hline
 
-            \textbf{Personal Information Schema ID}: 
-            The portal is aware of the currently selected administration service by the user and knows which the corresponding form is.
-It therefore sends the correct ID of a FIM data field schemata to the form-server.
-Based on this ID, the form-server knows which form to present to the user.
+            User Profile ID & This ID is a unique identifier of a user profile and is used by the form server to associate the initiated application with a user profile. & User Profile \\
 
-        \item \textbf{Status Update}
+            \hline
 
-            When an application was initiated, it is associated with a status.
-If the status changes, the administration portal gets notified of the new status along with a FMS-ID.
-The FMS-ID is created by the form server and uniquely identifies the application.
-The application can have the following states:
+            Personal Data & If the user approves, the administration portal submits personal data, the form-server can use to automatically fill in the form. & User Profile \\
 
-            \textbf{null}: The application and the corresponding form was successfully created
+            \hline
 
-            \textbf{submitted}: The form was filled in and the application is ready to be requested by the administration portal.
+            FIM Schema ID & The administration portal stores a hard coded FIM-ID for every administration service.
+This FIM-ID corresponds to the correct data field schemata, the form-server can display & Hard Coded in Portal \\
 
-            \textbf{filed}: The form was transmitted to the administration portal but the portal did not yet verify.
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Output} \\
+            \hline
 
-            \textbf{confirmed}: The administration portal confirmed the successful reception of the application
+            Status & The form-server answers with the status of the initiated application. & From Server \\
 
-            \textbf{deleted}: The application was deleted by the form-server.
+            \hline
 
-        \item \textbf{Submission of application}
+            FMS-ID & While initializing the application, the form-server creates an ID, which uniquely identifies the application.
+This FMS-ID is sent back to the portal so that it can request information about the application at a later time.
+& Form Server \\
 
-            If the user presses a "submit" button on the interactive form, the status of the application changes to submitted and the administration portal is notified.
-The portal can then request the application data from the from-server through an interface by sending the FMS-ID and receives the following results:
+            \hline
+            \end{tabularx}
+            \caption{Interface of the form-server for initialization of an application}
+            \label{table:interface_form_initialization}
+        \end{table}
+        \item \textbf{Status updates from from-server to administration portal}
 
-            \textbf{FMS-ID}:
+        The form-server notifies the administration portal of changes in the status of the application through an interface, see table \ref{table:interface_status}.
 
-            \textbf{JSON Web Token}:
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
 
-            \textbf{User Profile ID}:
+            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal.
+Each status update includes this ID in order for the portal to associate the update with an application.
+& Form Server \\
 
-            \textbf{XML File}:
+            \hline
 
-            This file consists of the personal information the form was filled in with
-
-            \textbf{Print version}:
-
-            The form-server can optionally sent a printable version of the filled in form
-
-            \textbf{Protocol Virus Scan}:
-
-            \textbf{Protocol Signature Check}:
-
-    \paragraph{Administration Portal and User Profile}
+            Status & The status provides information about interactions of the user or the form-server with the application. The possible states are:
 
             \begin{itemize}
-        \item \textbf{}
+                \item \textbf{null}: This application has this status right after initialisation.
+                \item \textbf{submitted}: The application has this status after the user triggered the submit functionality of the form-server.
+Usually the form is now locked for further modification by the user.
+                \item \textbf{filed}: The form-server submitted the application to the portal but did not yet receive a confirmation.
+                \item \textbf{confirmed}: The form-server received a confirmation from the portal.
+                \item \textbf{deleted}: The form-server deleted the application.
             \end{itemize}
 
+            & Form Server \\
+            \hline
+            \end{tabularx}
+            \caption{Interface of the administration portal for receiving status updates by the form-server}
+            \label{table:interface_status}
+        \end{table}
+
+        \item \textbf{Submission of the application from the form-server to the administration portal}
+
+        After the administration portal received the status update "submitted", it requests the form-server to transfer the application data through an interface, see table \ref{table:interface_application_data}.
+
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
+
+            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal along with the status update of the submission.
+The administration portal sends this ID in order for the form-server to know which application data to transfer.
+& Form Server \\
+
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Output} \\
+            \hline
+
+            FMS-ID & The FMS-ID is transmitted in order for the portal to associate the response with an application. & Form Server \\
+
+            \hline
+
+            JSON Web Token & The JWT which was initially sent from the portal to the form-server is now transmitted back again, in order for the portal to verify, that the form-server is authorized to submit an application for the user.
+& User Profile \\
+
+            \hline
+
+            User Profile ID & The user profile ID was initially transmitted to the form-server by the portal and is now transmitted back in order for the portal to associate the application with a user profile.
+& User Profile \\
+
+            \hline
+
+            XML File & The XML file contains the personal data retrieved through the form. & Form Server \\
+
+            \hline
+            \end{tabularx}
+            \caption{Interface of the form-server for requesting application data by the administration portal.}
+            \label{table:interface_application_data}
+        \end{table}
     \end{itemize}
+
+    \item The administration portal interacts with the user profile to provide online self-service for profile management and to identify the user and to request authentication and authorisation.
+
+    \item The administration portal interacts with the data exchange platform to transfer an application which the data exchange platform submits to the correct institution.
+
+    \item
+
+    \item
+
+    \item
+
+\end{enumerate}
 
@@
 
-\subsection{Basic Use Case Flow Diagram}
+\subsection{Basic Use Case Sequence Diagram}
+
+\includegraphics[width=15cm]{Basic Use Case.png}
 
@@
 
-\section{Requirement Analysis}
+\section{Functional Requirement Analysis}
 
@@
 \begin{itemize}
-    \item user wants to manage his data only on one platform
-    \item user wants to know who he provisions his personal information
-    \item user wants to communicate
-    \item user wants to know the reason each time his personal information is requested
+    \item The user wants to manage his personal information in one place
+    \begin{itemize}
+        \item The user wants to CRUD attributes
+        \item The user wants SPs to CRUD his attributes
+        \item The user wants a user friendly interface where he can CRUD his attributes
+        \item In case the user cannot understand an attribute or its possible values, he needs OSS tools which enables him to enter the correct value
+        \item The user wants to enter personal information only once (=> SPs should reuse existing attributes)
+        \item The user wants a new or modified attributes to be instantly used everywhere
+        \item The user wants a deleted attribute to be instantly deleted everywhere
+        \item The user wants to have a list of often used attributes, in order to prefill them
+    \end{itemize}
+    \item The user wants to manage authentication in one place
+    \begin{itemize}
+        \item The user does not want to authenticate
+        \item The user wants that only he has access to the identity
+    \end{itemize}
+    \item The user wants to manage authorisation in one place
+    \begin{itemize}
+        \item The user wants to manage who can perform which actions in his name (f.e CRUD attributes, place order, cancel subscription)
+        \item The user wants an authorisation to only be granted if he manually approves
+        \item The user wants an authorisation to be associated with a single entity, a reason, which actions can be performed and duration of the authorisation
+        \item The user wants to communicate with the authorised entity
+        \item The user wants to have much information about the authorised entity
+        \item The user wants to be able to revoke an authorisation
+        \item The user wants to save the history of authorisations
+    \end{itemize}
+    \item The user wants to use all OSS tools in one place
+    \begin{itemize}
+        \item Communication through inbox
+        \item Subscribe for a service of an SP
+        \item Place order in a shop of an SP
+        \item ...
+    \end{itemize}
+    \item The user wants
+
+\end{itemize}
+
+\subsection{Service Provider Perspective}
+
+\begin{itemize}
+    \item SPs want to manage personal information of users
+    \begin{itemize}
+        \item SPs want to CRUD attributes of the user
+        \item In case modification of an attribute has strong implications on the operation of a system, the modification of an attribute needs to be limited
+        \item SPs want to access personal information already collected by other SPs
+        \item SPs want 
+    \end{itemize}
+    \item identification
+    \item authentication
+    \item authorisation
+    \item 
 \end{itemize}
@@
 
-\begin{itemize}
-    \item The administration portal / form-server sends the user/app the content of a form.
-The app will display the form and ask the user to fill it in.
-The interaction is displayed under a relation between the user and the requesting portal.
-When submitting, the app sends the data back to the portal and logs that the user transmitted the list of personal data.
-No authentication is necessary?
-The content is encrypted and the connector knows the pub.
-key?
+\subsection{IMP Functionalities}
 
-    Or relation is made with the responsible administrative institution.
-The administration portal determines the corresponding institution beforehand.
-In this case, the communication can also be done through the same relation and the personal data is provisioned to only the institution which needs it, not the whole member state or commune.
+The IMP solution aims to replace existing user profiles by enabling users to manage their identity through IMP clients and by integration with service providers.
 
-    The IMP solution has to allow the inititation of relations and after that the request of information for new usage (Verwendungszweck) where the new usage is the application for a administrative service.
-\end{itemize}
+\subsection{Basic Use Case}
+
+The following diagram describes the concept of how IMP fits within the basic use case of the OZG.
+It contains some of the previously explained OZG components and an additional component: the IMP client.
+The IMP client is part of the system architecture and is responsible for identity management.
+Components related to integration and implementation of IMP are left out in this diagram and are focus of the Integration chapter.
+
+\includegraphics[width=15cm]{Basic Use Case IMP.png}
+
+The selection of an administrative service is online self-service which is not part of identity management an is therefore left to be done through the websites of the administration portal.
+
+One focus of IMP is to enable the user to be in full control of his identity.
+It therefore is the goal to execute the basic use case while sharing as little personal information as necessary and sharing personal information only with the components which require it.
+The main issue of the official execution of the basic use case in this regard is, that the administration portal collects personal information with the purpose of forwarding it to responsible institutions.
+It is not in the best interest of the user to share all information of an application with the administration portal of a member state when the application is eventually processed by an institution.
+It would be in the interest of the user to share personal information regarding the application with the institution directly.
+This way, the user has more differentiated control of which institutions access which personal information.
+The IMP client in the proposed solution therefore shares personal information directly with the institutions instead of the administration portal.
+
+The result of the application is sent to the IMP client as it contributes to personal information of his identity.
 
@@
 
-\subsection{Process Integration}
+\subsection{Sequence Diagrams}
 
-\includegraphics[width=15cm]{Basic Integration Application.png}
+Hier eine grobe Beschreibung des Basis Anwendungsfalls aufgeteilt in mehrere Bilder.
 
-\subsection{Messaging Integration}
+\includegraphics[width=15cm]{Selection Administrative Service.png}
+
+\includegraphics[width=15cm]{Institution Determination.png}
+
+\includegraphics[width=15cm]{Notify Institution.png}
+
+\includegraphics[width=15cm]{Institution Request.png}
+
+\includegraphics[width=15cm]{Submit Result.png}
+
+Hier der Anfang einer detaillierteren Beschreibung des Basis Anwendungsfalls basierend auf dem Klassen Diagramm weiter unten.
+
+\includegraphics[width=15cm]{Sequence Diagram.png}
+
+\subsection{Class Diagram}
+
+\includegraphics[width=15cm]{Data Model.png}
+
+\subsection{Messaging Diagram}
 

### 2021-01-08 msc-thesis.tex
new diagrams
change Diagrams

@@
 
-Hier eine grobe Beschreibung des Basis Anwendungsfalls aufgeteilt in mehrere Bilder.
-
-\includegraphics[width=15cm]{Selection Administrative Service.png}
-
-\includegraphics[width=15cm]{Institution Determination.png}
-
-\includegraphics[width=15cm]{Notify Institution.png}
-
-\includegraphics[width=15cm]{Institution Request.png}
-
-\includegraphics[width=15cm]{Submit Result.png}
-
 Hier der Anfang einer detaillierteren Beschreibung des Basis Anwendungsfalls basierend auf dem Klassen Diagramm weiter unten.
 
-\includegraphics[width=15cm]{Sequence Diagram.png}
+\includegraphics[width=15cm]{Diagrams/out/Sequence Diagram/Sequence Diagram.png}
 
@@
 
-\includegraphics[width=15cm]{Data Model.png}
+\includegraphics[width=15cm]{Diagrams/out/Class Diagram/Class Diagram.png}
 

### 2021-01-11 msc-thesis.tex
.

@@
 
-    \item \textbf{Status update to portal}
+    \item \textbf{Status update}
 
-    The form-server sends updates to the administration portal regarding the current status of the application. The possible status updates are listed in the interface section.
+    The form-server sends updates regarding the current status of the application.
 
@@
 
-    If the administration portal submitted personal data to the form-server, the form can automatically be filled in.
-This can be done because both the user profile and the form-server use the same data fields defined through FIM.
+    If the form server was provided with personal information during the initiation request for an application, it can automatically fill in the form.
 
@@
 
-    The form can be integrated into the administration portal through for example an URL or Web-Component.
+    The form server can host a website where it displays an interactive form. The user can access this website either through an URL or through a web component.
 
@@
 
-    Depending on the actions of the user, the status of the application changes accordingly and the administration portal is notified through a status update.
+    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.
 
     \item \textbf{Storage of application}
-
     The form-server stores applications for a specified period of time if they were interrupted or submitted.
-In case of submission, the administration portal notifies the form server, if the application can be deleted.
 
@@
 
-    The administration portal submits JWT to the form-server which corresponds to a user profile.
-Based on this information, the form-server searches all stored applications which belong to the user profile and sends back to the portal a list of URLs, through which the user can access them.
+    If the form server is provided an identification and authorisation of a user, it searches all stored applications which belong to the user and sends back a list of URLs, through which the user can access them.
 
@@
 
-    If requested by the administration portal, the form-server can delete stored applications. This is usually the case after an application was submitted to the administration portal.
+    If the form server is provided an identification and authorisation of a user and an identification of an application, it can delete the stored application.
 
@@
 
-    The user can add documents as attachments to an application. Uploaded documents are scanned for viruses.
-
-    \item \textbf{Authentication of user profile}
-
-    JSON web token from administration portal.
+    The user can add documents as attachments to an application. The documents can either be uploaded from the local machine or the data wallet of the user profile.
 
@@
 
-    When the user submits the application by for example pressing a "submit" button, the form-server notifies the administration portal through a status update.
-The administration portal can then continue processing the application by requesting the application data from the form server.
-The portal does this by sending the form-server a FMS-ID it was sent by the form-server with the first status update.
+    When the user submits the application by for example pressing a "submit" button, the form-server sends a status update. The finished application can now be transmitted to a requesting system.
 
@@
 
-    Personal information of the user profile can be managed through the administration portal after successful authentication.
+    Personal information of the user profile can be managed through the administration portal after successful authentification.
 
-    \item \textbf{Provisioning Personal Information to Form-Server} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}
+    \item \textbf{Provisioning Personal Information} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}
 
-    If a user selects to open the form of an administrative service which is integrated in the administration portal, the portal asks the user for permission to transmit personal information to the form-server.
-If the user is logged in and accepts, the administration portal retrieves the necessary personal information from the user profile and forwards it to the form-server.
+    The user profile can be requested to send personal information to a specified URL. This requires the user to authenticate.
 
@@
 \paragraph{Data Wallet}
+The data wallet is a sub-component of the user profile and enables the user to manage documents for his user profile. The main services are:
+
+\begin{itemize}
+
+    \item \textbf{Upload of document}
+
+    The user can upload a document from his local machine to the data wallet.
+
+    \item \textbf{Show documents}
+
+    The user can list all documents which are stored in the data wallet.
+
+    \item \textbf{Delete documents}
+
+    The user can delete documents from the data wallet.
+
+    \item \textbf{Attach documents to application}
+
+    The user can attach a copy of a document stored in his data wallet to an application on a from server.
+
+\end{itemize}
 
 \paragraph{Inbox}
+The inbox is a sub-component of the user profile and enables the user to send messages through his user profile. The main services are:
+
+\begin{itemize}
+
+    \item \textbf{Send a message}
+
+    The user can send a message to authorities. This can be for example an institution which processes an application.
+
+    \item \textbf{Receive a message}
+
+    The user can receive messages from authorities for example to update the status of an application.
+
+    \item \textbf{List messages}
+
+    The user can see the messages he received by logging in to his user profile on the administration portal.
+
+    \item \textbf{Notification through E-Mail}
+
+    The user can be notified of a new message through E-Mail.
+
+\end{itemize}
 
 \subsubsection{Interfaces}
-In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards.
+In order to implement the basic use case, the components have to interact with each.
+The following diagram visualizes, which components interact.
+Each interaction is described afterwards.
+The arrows describe the main direction of information flow in an interaction.
 
@@
 \begin{enumerate}
+
+    \item The form-server provides the service "Initiation of application" which can be requested by the administration portal.
+The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID.
+In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata.
+In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.
+
     \item The user interacts with the system architecture relevant for OZG only through the administration portal.
@@
 
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            JSON Web Token & The portal received this JWT as a result of the login process with the user profile component.
-This token enables the form-server to verify the authentication of the user.
-& User Profile \\
-
-            \hline
-
-            User Profile ID & This ID is a unique identifier of a user profile and is used by the form server to associate the initiated application with a user profile. & User Profile \\
-
-            \hline
-
-            Personal Data & If the user approves, the administration portal submits personal data, the form-server can use to automatically fill in the form. & User Profile \\
-
-            \hline
-
-            FIM Schema ID & The administration portal stores a hard coded FIM-ID for every administration service.
-This FIM-ID corresponds to the correct data field schemata, the form-server can display & Hard Coded in Portal \\
-
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Output} \\
-            \hline
-
-            Status & The form-server answers with the status of the initiated application. & From Server \\
-
-            \hline
-
-            FMS-ID & While initializing the application, the form-server creates an ID, which uniquely identifies the application.
-This FMS-ID is sent back to the portal so that it can request information about the application at a later time.
-& Form Server \\
-
-            \hline
-            \end{tabularx}
-            \caption{Interface of the form-server for initialization of an application}
-            \label{table:interface_form_initialization}
-        \end{table}
         \item \textbf{Status updates from from-server to administration portal}
@@
         The form-server notifies the administration portal of changes in the status of the application through an interface, see table \ref{table:interface_status}.
-
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal.
-Each status update includes this ID in order for the portal to associate the update with an application.
-& Form Server \\
-
-            \hline
-
-            Status & The status provides information about interactions of the user or the form-server with the application. The possible states are:
-
-            \begin{itemize}
-                \item \textbf{null}: This application has this status right after initialisation.
-                \item \textbf{submitted}: The application has this status after the user triggered the submit functionality of the form-server.
-Usually the form is now locked for further modification by the user.
-                \item \textbf{filed}: The form-server submitted the application to the portal but did not yet receive a confirmation.
-                \item \textbf{confirmed}: The form-server received a confirmation from the portal.
-                \item \textbf{deleted}: The form-server deleted the application.
-            \end{itemize}
-
-            & Form Server \\
-            \hline
-            \end{tabularx}
-            \caption{Interface of the administration portal for receiving status updates by the form-server}
-            \label{table:interface_status}
-        \end{table}
 
@@
 
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal along with the status update of the submission.
-The administration portal sends this ID in order for the form-server to know which application data to transfer.
-& Form Server \\
-
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Output} \\
-            \hline
-
-            FMS-ID & The FMS-ID is transmitted in order for the portal to associate the response with an application. & Form Server \\
-
-            \hline
-
-            JSON Web Token & The JWT which was initially sent from the portal to the form-server is now transmitted back again, in order for the portal to verify, that the form-server is authorized to submit an application for the user.
-& User Profile \\
-
-            \hline
-
-            User Profile ID & The user profile ID was initially transmitted to the form-server by the portal and is now transmitted back in order for the portal to associate the application with a user profile.
-& User Profile \\
-
-            \hline
-
-            XML File & The XML file contains the personal data retrieved through the form. & Form Server \\
-
-            \hline
-            \end{tabularx}
-            \caption{Interface of the form-server for requesting application data by the administration portal.}
-            \label{table:interface_application_data}
-        \end{table}
     \end{itemize}
@@
 
+\chapter{Tables}
+
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
+
+            JSON Web Token & The portal received this JWT as a result of the login process with the user profile component.
+This token enables the form-server to verify the authentication of the user.
+& User Profile \\
+
+            \hline
+
+            User Profile ID & This ID is a unique identifier of a user profile and is used by the form server to associate the initiated application with a user profile. & User Profile \\
+
+            \hline
+
+            Personal Data & If the user approves, the administration portal submits personal data, the form-server can use to automatically fill in the form. & User Profile \\
+
+            \hline
+
+            FIM Schema ID & The administration portal stores a hard coded FIM-ID for every administration service.
+This FIM-ID corresponds to the correct data field schemata, the form-server can display & Hard Coded in Portal \\
+
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Output} \\
+            \hline
+
+            Status & The form-server answers with the status of the initiated application. & From Server \\
+
+            \hline
+
+            FMS-ID & While initializing the application, the form-server creates an ID, which uniquely identifies the application.
+This FMS-ID is sent back to the portal so that it can request information about the application at a later time.
+& Form Server \\
+
+            \hline
+            \end{tabularx}
+            \caption{Interface of the form-server for initialization of an application}
+            \label{table:interface_form_initialization}
+        \end{table}
+
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
+
+            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal.
+Each status update includes this ID in order for the portal to associate the update with an application.
+& Form Server \\
+
+            \hline
+
+            Status & The status provides information about interactions of the user or the form-server with the application. The possible states are:
+
+            \begin{itemize}
+                \item \textbf{null}: This application has this status right after initialisation.
+                \item \textbf{submitted}: The application has this status after the user triggered the submit functionality of the form-server.
+Usually the form is now locked for further modification by the user.
+                \item \textbf{filed}: The form-server submitted the application to the portal but did not yet receive a confirmation.
+                \item \textbf{confirmed}: The form-server received a confirmation from the portal.
+                \item \textbf{deleted}: The form-server deleted the application.
+            \end{itemize}
+
+            & Form Server \\
+            \hline
+            \end{tabularx}
+            \caption{Interface of the administration portal for receiving status updates by the form-server}
+            \label{table:interface_status}
+        \end{table}
+
+        \begin{table}[!h]
+            \begin{tabularx}{\textwidth}{|l|C|l|}
+            \hline
+            Property & Description & Data Source \\
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Input} \\
+            \hline
+
+            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal along with the status update of the submission.
+The administration portal sends this ID in order for the form-server to know which application data to transfer.
+& Form Server \\
+
+            \hline
+            \rowcolor{LightCyan}
+            \multicolumn{3}{|l|}{Output} \\
+            \hline
+
+            FMS-ID & The FMS-ID is transmitted in order for the portal to associate the response with an application. & Form Server \\
+
+            \hline
+
+            JSON Web Token & The JWT which was initially sent from the portal to the form-server is now transmitted back again, in order for the portal to verify, that the form-server is authorized to submit an application for the user.
+& User Profile \\
+
+            \hline
+
+            User Profile ID & The user profile ID was initially transmitted to the form-server by the portal and is now transmitted back in order for the portal to associate the application with a user profile.
+& User Profile \\
+
+            \hline
+
+            XML File & The XML file contains the personal data retrieved through the form. & Form Server \\
+
+            \hline
+            \end{tabularx}
+            \caption{Interface of the form-server for requesting application data by the administration portal.}
+            \label{table:interface_application_data}
+        \end{table}
+
 \printbibliography

### 2021-01-13 msc-thesis.tex
integration 1

@@
 \usepackage{setspace}
+\usepackage{multirow}
+\usepackage{longtable}
+\usepackage{float}
 
@@
 
-\paragraph{Administration Portal}
-The administration portal provides the user with a web-interface and implements user flows of digitized administrative processes by interacting with other system components.
-The main services are \cite{NRW:Umsetzung}:
-
-\begin{itemize}
-    \item \textbf{Search and find a form}
-
-    Due to the distributed responsibility for provisioning administrative services through for example the "one for all" method, it is not clear to the user, which member state provides which administrative service on his portal.
-Therefore, each administration portal provides a "Search and Find" functionality, which enables the user to find the correct administration portal and page, where the service is provided.
-In order for the administration portals to provide the "Search and Find" feature, an "Online Gateway" makes information about the location of administrative services accessible through a central data storage \cite{Capgemini:OnlineGateway}.
-
-    \item \textbf{Selection of administrative service}
-
-    In combination with the "Search and Find" feature, the user can select an entry of the search result and is forwarded to the corresponding web-page.
-Depending on the administrative service, the web-page can be hosted on the current or a different portal.
-It shows information about the selected service like a service description, requirements and possible outcomes and enables the user to open the corresponding form hosted by a form-server.
-
-    \item \textbf{Opening a form through a form-server}
-
-    The web-page of an administration portal describing the administrative service can integrate a form-server in multiple ways.
-The maybe easiest way is to add an URL which forwards the user to a web-page provided by the form-server.
-More advanced integration methods are possible where the form is rendered inside the web-page of the portal.
-
-    \item \textbf{Request of personal information from user profile}
-
-    Each member state and the federal republic provide interoperable user profiles.
-The administration portal is able to access the services of every user profile, which includes retrieval of personal information stored in the user profile.
-This requires a user to be logged into his user profile with a sufficiently high trust level.
-
-    \item \textbf{Transfer of personal data to the form-server}
-
-    If the administration portal was able to retrieve personal information from a currently active user profile, it can, with approval of the user, transmit it to the form-server which provides the form corresponding to the selected administrative service.
-
-    \item \textbf{Reception of applications from form-server}
-
-    The administration portal can request the application data from the form-server after it was notified of its "submission".
-
-    \item \textbf{Feedback to form-server}
-
-    The administration portal notifies the form-server, that it no longer has to store a certain application.
-
-    \item \textbf{Determination of receiving institution}
-
-    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender.
-It is the responsibility of the administration portal to determine which institution receives which application.
-
-    \item \textbf{Transfer to data-exchange platform}
-
-    The administration portal transfers the application to the data-exchange platform which is responsible for delivering it to the institution.
-\end{itemize}
-
 \paragraph{Form-Server}
@@
 
-    Personal information of the user profile can be managed through the administration portal after successful authentification.
+    Personal information of the user profile can be modified.
+This requires the user to authenticate.
+In case the user profile is connected with an online identity card, some attributes like name and age can not be changed.
 
@@
 Institutions are the entities which eventually process the incoming applications and provide the users with solutions.
-They receive a digital application through the data-exchange platform.
-Institution are provided a special website on the administration portal, where they can interact with the user of an application through for example messages, status updates or requests for additional documents.
-Those interactions are done manually by an employee through the user interface of the website but can, to some degree, be automated.
+They receive a digital application through the data-exchange platform and send back the result as a message through the inbox.
 
@@
     The user can be notified of a new message through E-Mail.
+
+\end{itemize}
+
+\paragraph{Administration Portal}
+The administration portal provides the user access to various OZG services of other system components:
+
+\begin{itemize}
+
+    \item \textbf{Application for administrative service}
+    The administration portal provides access to services for creation and submission of applications for administration services.
+The portal hosts a web page for each administration service which enables the user to get information about the service and start the application process.
+After starting the process, the portal interacts with multiple system components to guide the user through the application.
+
+    \item \textbf{Management of user profile}
+    The administration portal provides access to the personal information stored in the user profile by interacting with the user profile system component.
+It enables the user to add, remove and update a set of attributes.
+
+    \item \textbf{Management of inbox}
+    The administration portal provides access to the inbox of the user profile. It enables the user to send new messages and display received messages.
+
+    \item \textbf{Management of data wallet}
+    The administration portal provides access to the data wallet of the user profile. It enables the user to upload and download documents and to attach copies of documents to applications.
+
+\end{itemize}
+
+The administration portal provides additional services:
+
+\begin{itemize}
+    \item \textbf{Determination of responsible institution}
+
+    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender.
+It is the responsibility of the administration portal to determine which institution receives which application.
+
+    \item \textbf{Search and find Administrative Service}
+
+    The administration portal provides a search and find service which enables the user to find the web page of all administrative services which relate to the entered search term.
 
@@
 \begin{center}
-    \includegraphics[width=8cm]{Interaction Diagram.png}
+    \includegraphics[width=8cm]{Diagrams/Interaction Diagram.png}
 \end{center}
@@
 
-    \item The form-server provides the service "Initiation of application" which can be requested by the administration portal.
+    \item The web browser of the user displays the web pages hosted by the administration portal.
+
+    \item The form-server can initiate the application if requested by the administration portal.
 The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID.
@@
 
-    \item The user interacts with the system architecture relevant for OZG only through the administration portal.
-The user is provided with a website as an interface with multiple online self-service functionalities.
-    \item Administration portal and form-server interact through a REST API. The API provides the following interfaces:
-    \begin{itemize}
-        \item \textbf{Application initiation interface provided by form-server and used by administration portal}
-
-        On the page of an administrative service on the administration portal, the user can press a button "to online application".
-Upon pressing the button, the portal interacts with the form server by transmitting data through an interface and receiving a response, see table \ref{table:interface_form_initialization}.
-
-        \item \textbf{Status updates from from-server to administration portal}
-
-        The form-server notifies the administration portal of changes in the status of the application through an interface, see table \ref{table:interface_status}.
-
-        \item \textbf{Submission of the application from the form-server to the administration portal}
-
-        After the administration portal received the status update "submitted", it requests the form-server to transfer the application data through an interface, see table \ref{table:interface_application_data}.
-
-    \end{itemize}
-
-    \item The administration portal interacts with the user profile to provide online self-service for profile management and to identify the user and to request authentication and authorisation.
-
-    \item The administration portal interacts with the data exchange platform to transfer an application which the data exchange platform submits to the correct institution.
-
-    \item
-
-    \item
-
-    \item
+    \item The form server provides the user a web page which displays an interactive form.
+
+    \item The form server notifies the administration portal of changes in the status of applications.
+If the administration portal is notified of a submitted application, it requests the form server to transmit the application data.
+
+    \item The administration portal requests the user profile for identification and authentication to login a user on the web page of the portal.
+The portal also requests authorisation from the user profile to for example access certain personal information.
+
+    \item The administration portal enables the user to manage services of the user profile.
+It provides OSS tools for managing attributes stored in the user profile, to send new messages and to manage documents in the data wallet.
+
+    \item The administration platform submits application data to the data exchange platform for delivery to the responsible institution.
+
+    \item The data exchange platform notifies the administration portal of the delivery status of the application data.
+
+    \item The data exchange platform notifies the institution of a new application and enables it to download the corresponding data.
+
+    \item The institution can send messages to the inbox of a user profile to for example request additional documents.
+
+    \item The user can send messages to the institution which for example asked for additional documents.
 
@@
 \subsubsection{Data Objects}
-The system architecture processes the following data objects which are associated to certain system components:
-
-\subsection{Basic Use Case Sequence Diagram}
-
-\includegraphics[width=15cm]{Basic Use Case.png}
+This section describes what data each component processes.
+The property value describes a certain type of data.
+The source describes which component stores the value.
+This distinguishes the access of a property by reference and by copy.
+If the source of a property is another component, the property is accessed by reference.
+The description gives further detail on how the property is processed by the component.
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{Administration Portal: Service Web Page} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    Name & Web Page & FIM & Name of an administrative service \\
+    \hline
+    URL & Portal & Portal & The URL of the Web Page \\
+    \hline
+    Description & Web Page & FIM & Description of an administrative service \\
+    \hline
+    FIM-ID & Web Page & FIM & FIM-ID of a data field schemata which describes attributes required from the user when applying for the service \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{Administration Portal: User} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    Attributes & User Profile & User Profile & The portal can manage attributes of user profiles \\
+    \hline
+    JWT & Portal & User Profile & The portal can retrieve a JSON Web Token from the profile after successful authentication by a user \\
+    \hline
+    URL Form & Portal & Form Server & The portal stores the URL where the form server hosts the interactive form \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{Administration Portal: Application} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    FMS-ID & Portal & Form Server & The portal receives the ID of applications from the form server \\
+    \hline
+    Status & Portal & Form Server & The portal receives status updates for each application \\
+    \hline
+    XML Form Data & Portal & Form Server & The portal can retrieve the data which was filled into a form \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{User Profile: Personal Information} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    Attributes & User Profile & FIM & The list of attributes the user can fill in at his profile are based on FIM data fields managed in the FIM repository. \\
+    \hline
+    Attribute Values & User Profile & User & The user can manually add values to a list of predetermined attributes in his profile \\
+    \hline
+    Credentials & User Profile & User & The User Profile stores encrypted credentials of the user to authenticate him \\
+    \hline
+    User Profile ID & User Profile & User Profile & The User Profile creates and stores a unique ID for the user \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{User Profile: Authorisatiozation} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    JWT & Other Component & User Profile & The user profile can create and transfer JSON Web Tokens which authorise other components to access resources of the user profile \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{User Profile: Inbox} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    Received Messages & User Profile & User & The user profile stores messages which were addressed to the user \\
+    \hline
+    Sent Messages & User Profile & User & The user profile stores messages which were sent by the user \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{User Profile: Data Wallet} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    Documents & User Profile & User & The user profile stores documents which were uploaded by the user \\
+    \hline
+    \end{tabularx}
+\end{table}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{Form Server} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    FMS-ID & Form Server & Form Server & The form server creates a unique ID for each application \\
+    \hline
+    JWT & Form Server & User Profile & The form server uses a JSON Web Token to verify that the entity issuing the request is authorised \\
+    \hline
+    User Profile ID & Form Server & User Profile & The ID of the user who is associated to the application \\
+    \hline
+    FIM-ID & Form Server & FIM & The FIM ID of a data field schemata is used to determine how to construct the form \\
+    \hline
+    Form & Form Server & FIM & The list of attributes the user can fill in at the form are based on the FIM data field schemata.
+The form server maps the FIM data fields of the FIM data field schemata to attributes the form server understands \\
+    \hline
+    Status & Form Server & Form Server & The status describes which actions were performed on the application \\
+    \hline
+    Application Data & Form Server & User & The form server stores the data which the user filled in to the form as an XML file \\
+    \hline
+    Web Page & Form Server & Form Server & The form server hosts a web page with the interactive form  \\
+    \hline 
+    Web Page URL & Form Server & Form Server & The form server hosts the web page of the form at an individual URL \\
+    \hline 
+    \end{tabularx}
+\end{table}
+
+\subsubsection{Sequence Diagram}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=17cm]{Diagrams/Basic Use Case Sequence Diagram.png}
+\end{figure}
 
@@
 
-\subsection{IMP Functionalities}
-
-The IMP solution aims to replace existing user profiles by enabling users to manage their identity through IMP clients and by integration with service providers.
-
-\subsection{Basic Use Case}
-
-The following diagram describes the concept of how IMP fits within the basic use case of the OZG.
-It contains some of the previously explained OZG components and an additional component: the IMP client.
-The IMP client is part of the system architecture and is responsible for identity management.
-Components related to integration and implementation of IMP are left out in this diagram and are focus of the Integration chapter.
-
-\includegraphics[width=15cm]{Basic Use Case IMP.png}
-
-The selection of an administrative service is online self-service which is not part of identity management an is therefore left to be done through the websites of the administration portal.
-
-One focus of IMP is to enable the user to be in full control of his identity.
-It therefore is the goal to execute the basic use case while sharing as little personal information as necessary and sharing personal information only with the components which require it.
-The main issue of the official execution of the basic use case in this regard is, that the administration portal collects personal information with the purpose of forwarding it to responsible institutions.
-It is not in the best interest of the user to share all information of an application with the administration portal of a member state when the application is eventually processed by an institution.
-It would be in the interest of the user to share personal information regarding the application with the institution directly.
-This way, the user has more differentiated control of which institutions access which personal information.
-The IMP client in the proposed solution therefore shares personal information directly with the institutions instead of the administration portal.
-
-The result of the application is sent to the IMP client as it contributes to personal information of his identity.
+This section describes a solution for an IMP system considering the previously mentioned requirements.
+
+\subsection{Components}
+
+\subsubsection{IMP Client}
+
+The IMP client is a smartphone application which enables the user to manage his IMP identity. The client provides the following functionalities:
+\begin{itemize}
+    \item Create an identity
+    \item Manage attributes of the identity
+    \item Manage documents
+    \item Send and receive messages
+    \item Send and receive relationship requests
+    \item Send and receive requests
+\end{itemize}
+
+\subsubsection{IMP Server}
+The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
+\begin{itemize}
+    \item Create and store relationship template
+    \item Create and store request template
+    \item Deliver relationship requests
+    \item Deliver requests
+    \item Deliver messages
+\end{itemize}
+
+\subsection{Functionalities}
+
+\subsubsection{Relationships}
+
+\subsubsection{Requests}
+
+\subsection{Data Objects}
+
+\begin{table}[!h]
+    \begin{tabularx}{\textwidth}{|l|l|l|C|}
+    \rowcolor{LightCyan}
+    \hline
+    \multicolumn{4}{|l|}{Form Server} \\
+    \hline
+    Property & Storage & Origin & Description  \\
+    \hline
+    \hline
+    \hline
+    \end{tabularx}
+\end{table}
 
@@
 
-\paragraph{Data Mapping}
-If multiple SPs and the user are able to add new attributes, there is the possibility of duplicate attributes with the same meaning but different name.
-It is also possible for SPs to utilize the same attribute but interpreting its meaning differently.
-
-\paragraph{Identity Attributes}
-Service providers are able to add attributes to an identity.
-It, however, is not clear which information should be added to an IMP system as part of an identity and which information should be stored by the individual SPs.
-One reason is, that service providers exist for which creation and utilization of personal information is a business model.
-For those SPs, the secrecy of certain types of personal information is important.
-One example would be information about product preferences of customers acquired by online retailers for usage with recommender systems.
-A guideline could be, to only add attributes to the IMP system, which should be directly managed by users.
-
-\paragraph{Online Self-Service}
-SPs might add attributes to the identity of an IMP system which have very special meanings which are not self-explanatory.
-The attribute might also adhere to a special data format or be conditioned by other attributes of the identity.
-The modification of the attributes might also require interaction with the system architecture of an SP.
-In order for the attributes to stay valid, management through online self-service tools which are provided by the system architecture of an SP might be required.
-
-In this case, the self-service tools should be accessible through the IMP systems in a user friendly way.
-
-\paragraph{Attribute Access}
-Attributes which were added by a SP might require restrictions towards the user.
-If for example a subscription status is saved as an attribute, the user should not be able to modify it without permission of the SP.
-
 \subsection{Basic Use Case}
@@
 
-\section{Basic Use Case}
-
-\subsection{Sequence Diagrams}
-
-Hier der Anfang einer detaillierteren Beschreibung des Basis Anwendungsfalls basierend auf dem Klassen Diagramm weiter unten.
-
-\includegraphics[width=15cm]{Diagrams/out/Sequence Diagram/Sequence Diagram.png}
-
-\subsection{Class Diagram}
-
-\includegraphics[width=15cm]{Diagrams/out/Class Diagram/Class Diagram.png}
-
-\subsection{Messaging Diagram}
+\section{Integration}
+
+Multiple integration scenarios are presented with increasing complexity and functionality.
+
+\subsection{Scenario 1}
+
+In this scenario, the IMP system integrates only with the administration portal to enable the usage of its identity related functionalities through the IMP client.
+The integration architecture contains one connector which interacts with the administration portal.
+The integration should provide an additional optional way for users to manage their OZG identity.
+
+\subsubsection{Overview}
+
+\begin{center}
+    \includegraphics[width=8cm]{Diagrams/Integration 1 Overview.png}
+\end{center}
+
+\subsubsection{Functionalities}
+
+The IMP client should be able to:
+\begin{itemize}
+    \item manage personal information stored in the user profile
+    \item receive and send messages through the inbox of the user profile
+    \item upload and download documents through the data wallet of the user profile
+    \item manage active applications
+\end{itemize}
+
+The IMP client should however not be used to search for administrative services, as this is a service of the portal which is not related to the management of an identity.
+
+\subsubsection{Integration}
+
+\paragraph{Association IMP ID and OZG ID}
+
+Before the IMP client can access services of the administration portal, it has to be possible to connect the IMP identity with a user profile.
+The user should be able to connect and disconnect the identity with an existing user profile.
+As in this scenario the IMP systems only integrate with the administration portal, the user profile should not be modified to include information about an IMP identity.
+
+\begin{center}
+    \includegraphics[width=8cm]{Diagrams/Integration 1 Connection Overview.png}
+\end{center}
+
+The administration portal can provide an additional web page where a logged in user can connect an IMP identity with his user profile.
+In order for the web page to initiate a connection process, administration portal and IMP identity require some way to identify each other.
+Either the IMP identity identifies itself to the administration portal or the administration portal identifies itself to the IMP identity.
+
+The IMP identity could identify itself to the administration portal through manual entering of an IMP ID on the web page.
+This could enable the administration portal to interact with the identity through a connector.
+Another option is for the administration portal to identify itself to the IMP identity.
+As the IMP system provides a functionality for this, it is the better option.
+Through the connector, the administration portal can create a relationship template.
+The template is stored on the IMP server but can be accessed by any client which has the correlating template ID.
+The template contains information for identification of the connector, a encrypted session ID, a reason why the relationship is requested and a list of attributes the IMP client is required to share.
+
+Based on the resulting template ID, the connector creates a QR code which the administration portal includes in web page before sending it to the user.
+The user can now scan the QR code with the IMP client which retrieves the template corresponding to the template ID from the IMP server.
+The IMP client displays the request and if the user accepts, the connector is notified of an incoming relationship request.
+The request contains the template ID, information about the IMP identity of the user, the shared attributes and the encrypted session ID.
+
+The connector transfers the relationship request to the administration portal which based on the decrypted session ID sends a confirmation request to the web page.
+The confirmation request contains information about the IMP identity which requested to connect to the user profile.
+If the user accepts the confirmation, the association of the IMP relation and the user ID is stored in a database.
+
+The connection of the user profile and the IMP identity would therefore be an IMP relationship.
+
+\paragraph{Authorisation}
+
+If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token, which enables it to start actions in the name of the user.
+The user might want to manage which actions an IMP client is authorised for.
+
+On the web page where the user can connect user profile and IMP identity, authorisation of a connection can be managed too.
+After a success full connection, the web page presents a UI where the user can determine which actions the IMP client should be able to perform.
+If the user finishes, the administration portal can request the authorisation from the user profile which requests authentication from a user.
+The resulting JSON Web Token is then transmitted to the administration portal.
+
+The JSON Web Token contains information to identify the user profile and the authorisations for the entity which possesses this token.
+It also includes a signature with a private key of the user profile component.
+This allows the component to check if the token is valid.
+
+This token can be stored in the database where IMP relations are mapped to profile IDs.
+
+\paragraph{Improved Association of IMP ID and OZG ID}
+
+JSON Web Tokens can also function as a connection between user profile and IMP identity because they includes the ID of a user profile.
+If the IMP client is in possession of this token and requests the administration portal to perform an action, the administration portal can read the profile ID stored inside the token along with the authorisation information.
+The portal can then verify the validity of the token through the user profile component.
+If the validation was successful, the portal knows, that whoever sent the request has the authorisation stored in the token for the user profile ID stored in the token.
+
+The JSON Web Token can be saved as attribute of the IMP identity which the administration portal was granted access to.
+Whenever the portal receives a request from a relation to for example modify an attribute in the user profile, the portal can read the JSON Web Token of the corresponding IMP identity determine the connected user profile ID and verify the authorisation.
+
+\paragraph{Personal Information}
+
+One of the goals of an IMP system is to enable the user to only manage his identity in one place while all other service providers rely on the attributes of the identity.
+As in this scenario however, the OZG system does not rely on attributes of the IMP system but enables it to manage personal information stored in the user profile.
+Some synchronisation mechanism can therefore operate.
+
+When the user profile is connected with the IMP identity, an attribute request is issued at least for the JWT issued by the user profile component.
+In case the JWT authorizes the IMP client to manage personal information of user profile, the administration portal can request access to attributes of the IMP identity which are also stored in the user profile.
+
+As the attributes stored in the user profile might be named differently than the attributes stored in the user profile, some mapping has to take place.
+
+The access of the administration portal to attributes of the IMP identity is stored as part of the relationship.
+
+There are multiple ways to synchronize the attributes.
+One way would require the administration portal to compare the attributes of the IMP identity with those of the user profile.
+Another option would be for the IMP client to notify the administration portal of a change in the shared attributes.
+The second option would be beneficial, as iterative requests to the IMP Client and user profile are resource intensive, especially for a large number of users.
+
+\paragraph{Attribute Mapping}
+
+\paragraph{Inbox}
+
+Both IMP Client and the administration portal provide an inbox functionality.
+If an IMP identity is connected with a user profile, it can send and receive messages as part of the relation it has with the administration portal.
+As the administration portal does not store any information on which user profile is connected with which IMP identity, it cannot forward messages of the inbox to the IMP identity of a relation.
+The IMP client will have to request for new messages from time to time or the previously removed database which maps IMP relations to user profiles is added again.
 

### 2021-01-17 msc-thesis.tex
first integration iteration started

@@
 \begin{center}
-    \includegraphics[width=8cm]{Diagrams/Integration 1 Overview.png}
+    \includegraphics[width=8cm]{Diagrams/Integration 1/Overview.png}
 \end{center}
@@
 The user should be able to connect and disconnect the identity with an existing user profile.
-As in this scenario the IMP systems only integrate with the administration portal, the user profile should not be modified to include information about an IMP identity.
-
-\begin{center}
-    \includegraphics[width=8cm]{Diagrams/Integration 1 Connection Overview.png}
-\end{center}
-
-The administration portal can provide an additional web page where a logged in user can connect an IMP identity with his user profile.
-In order for the web page to initiate a connection process, administration portal and IMP identity require some way to identify each other.
-Either the IMP identity identifies itself to the administration portal or the administration portal identifies itself to the IMP identity.
-
-The IMP identity could identify itself to the administration portal through manual entering of an IMP ID on the web page.
-This could enable the administration portal to interact with the identity through a connector.
-Another option is for the administration portal to identify itself to the IMP identity.
-As the IMP system provides a functionality for this, it is the better option.
-Through the connector, the administration portal can create a relationship template.
+
+\begin{center}
+    \includegraphics[width=10cm]{Diagrams/Integration 1/Connection/Overview.png}
+\end{center}
+
+The administration portal provides an additional web page where a logged in user can connect an IMP identity with his user profile.
+When the user requests the web page from the server, the portal requests the connector to create a relationship template.
 The template is stored on the IMP server but can be accessed by any client which has the correlating template ID.
-The template contains information for identification of the connector, a encrypted session ID, a reason why the relationship is requested and a list of attributes the IMP client is required to share.
-
-Based on the resulting template ID, the connector creates a QR code which the administration portal includes in web page before sending it to the user.
-The user can now scan the QR code with the IMP client which retrieves the template corresponding to the template ID from the IMP server.
-The IMP client displays the request and if the user accepts, the connector is notified of an incoming relationship request.
-The request contains the template ID, information about the IMP identity of the user, the shared attributes and the encrypted session ID.
-
-The connector transfers the relationship request to the administration portal which based on the decrypted session ID sends a confirmation request to the web page.
+The administration portal fills the template with information for identification of the connector, the ID of the user, a reason why the relationship is requested and a list of attributes the IMP client is required to share.
+After creation of the template, the connector submits the template ID to the administration portal in form of a QR code.
+
+The portal now transmits the web page including the QR code to the web browser of the user.
+The user can now scan the QR code with the IMP client.
+The client retrieves the template corresponding to the template ID from the IMP server and displays the request.
+
+If the user accepts, the connector is notified of an incoming relationship request trough the IMP server.
+The request contains the template ID, information about the IMP identity of the user, the shared attributes and the user ID.
+
+The connector transfers the request to the administration portal which, based on the user ID, updates the web page to display a confirmation request.
 The confirmation request contains information about the IMP identity which requested to connect to the user profile.
-If the user accepts the confirmation, the association of the IMP relation and the user ID is stored in a database.
-
-The connection of the user profile and the IMP identity would therefore be an IMP relationship.
+If the user accepts the confirmation, the administration portal requests the connector to accept the relationship which results in a relationship ID.
+The association of the relationship ID and the user ID is stored in a database.
+
+The connection of the user profile and the IMP identity is an IMP relationship.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging Overview.png}
+\end{center}
+
+The newly created web page uses messages to communicate with the administration portal using a request-reply pattern.
+The request-reply pattern enables the requestor - the web page in this case - to send a message to the replier - the connector in this case - and receive an answer which correlates to the request.
+The purpose of the communication in this case is for the web page to receive the QR code containing the relationship template.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 1.png}
+\end{center}
+
+In order for the web page to send and receive messages, it includes a messaging gateway.
+As the web page is added as part of the integration architecture, the gateway can be included in the web page.
+It provides domain specific functions to the web page and hides much of the complexity of interacting with the messaging system.
+In combination with the request-reply pattern, the local functions provided by the gateway can be used synchronously and asynchronously.
+The web page requires the user to be logged in to his user profile and therefore expects the web browser to contain a JSON Web Token.
+The web page uses the messaging gateway to send a message, requesting a QR code for connecting an IMP identity.
+The message consists of a JSON Web Token and is placed in a datatype channel called "QR Request Channel".
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 2.png}
+\end{center}
+
+In order to implement a request-reply pattern, a stateful smart proxy is used.
+The web page sends a message which contains a JSON Web Token in the body to the "QR Request" channel.
+Besides the body, the message contains a message ID in the header which uniquely identifies it.
+The message also contains a return address which specifies a channel to which the reply should be sent.
+The messaging gateway specifies a reply channel unique to the web browser instance.
+The temporary channel is deleted eventually.
+The smart proxy stores message ID and reply channel in order to correlate replies in the "QR Reply Service" channel with the request and send it to the specified reply channel.
+If eventually, the integration architecture is ready to send a QR code as reply, the corresponding message can be put on the "QR Reply Service" channel, where, based on the message ID, the smart proxy can correlate it to the request message and send the reply to the corresponding reply channel.
+The messaging gateway included in the web browser can retrieve the reply from its reply channel in multiple ways.
+One example would be iterative polling.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 3.png}
+\end{center}
+
+The message from the "QR Request Channel" are processed by a filter.
+All messages which are invalid through for example an expired JSON Web Token are deleted.
+Valid messages are then routed by a stateful content-based router.
+The router keeps track from which users a message was received.
+In case a message was received previously, the current message is routed to the "Existing Request" channel.
+Otherwise the message is routed to the "New Request Template" channel.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 4.png}
+\end{center}
+
+The messages from the "Existing Request Template" channel are consumed by a QR code management system, which stores all valid QR codes in a database.
+The system adds the QR code corresponding to the user to the message and sends it to the "QR Reply Service" channel, where it is delivered to the web page by the smart proxy.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 5.png}
+\end{center}
+
+Messages on the "New Relationship Template" channel are modified by a content enricher to contain parameters which are required by the connector to create a relationship template.
+The message is then send to the connector using a request-reply pattern.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 6.png}
+\end{center}
+
+As there is only one possible channel to receive the reply from the connector, no smart proxy is required for this request-reply pattern.
+The message is send to the "Relationship Template Request" channel, trough which the portal connector receives it.
+As the connector is designed with integration in mind, he is capable of receiving and sending messages through an included messaging gateway.
+The connector also contains a sophisticated process manager for implementing the provided IMP functionalities through interaction with an IMP server.
+In this case, the process manager interacts with the IMP server to create a relationship template, store it on the IMP server, retrieve a template ID and export it as a QR code.
+Through a content enricher, the QR code is attached to the message and placed on the "Relationship Template Reply" channel.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 7.png}
+\end{center}
+
+The message from the "Relationship Template Reply" channel is consumed by the QR code management system.
+The system stores the new QR code for the user and sends the message unchanged to the "QR Reply Service" channel, where the smart proxy delivers it to the web page.
 
@@
 
-If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token, which enables it to start actions in the name of the user.
-The user might want to manage which actions an IMP client is authorised for.
-
-On the web page where the user can connect user profile and IMP identity, authorisation of a connection can be managed too.
-After a success full connection, the web page presents a UI where the user can determine which actions the IMP client should be able to perform.
-If the user finishes, the administration portal can request the authorisation from the user profile which requests authentication from a user.
-The resulting JSON Web Token is then transmitted to the administration portal.
-
-The JSON Web Token contains information to identify the user profile and the authorisations for the entity which possesses this token.
-It also includes a signature with a private key of the user profile component.
-This allows the component to check if the token is valid.
-
-This token can be stored in the database where IMP relations are mapped to profile IDs.
-
-\paragraph{Improved Association of IMP ID and OZG ID}
-
-JSON Web Tokens can also function as a connection between user profile and IMP identity because they includes the ID of a user profile.
-If the IMP client is in possession of this token and requests the administration portal to perform an action, the administration portal can read the profile ID stored inside the token along with the authorisation information.
-The portal can then verify the validity of the token through the user profile component.
-If the validation was successful, the portal knows, that whoever sent the request has the authorisation stored in the token for the user profile ID stored in the token.
-
-The JSON Web Token can be saved as attribute of the IMP identity which the administration portal was granted access to.
-Whenever the portal receives a request from a relation to for example modify an attribute in the user profile, the portal can read the JSON Web Token of the corresponding IMP identity determine the connected user profile ID and verify the authorisation.
+If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token which enables it to perform actions for the user.
+The user might want to manage which actions an IMP client is authorised to perform without having to approve each of them trough the website of the portal.
+
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Authorisation/Overview.png}
+\end{center}
+
+After successful connection of an IMP identity with the user profile through the introduced web page, the website can display a user interface for specifying which actions the IMP identity is authorized for.
+After the user finishes, the web page submits the configuration to the administration portal.
+The portal then creates a suitable authorisation request to the user profile which requires the token to include the relationship ID associated to the user profile.
+After successful authentication by the user, the user profile transmits a JSON Web Token to the portal.
+
+It contains the user profile ID, the relationship ID and information about the authorisations that are granted when attaching this tokens to a request.
+It also includes a signature with the private key of the user profile component.
+This enables components to verify if the token is valid by transmitting it to the user profile component.
+
+The JSON Web Token is stored as attribute of the IMP identity.
+Upon receiving the token form the user profile component, the administration portal initiates two requests through the connector to the IMP identity of the relation corresponding to the relation ID.
+The first requests to add the token as attribute.
+The second requests to share the attribute.
+
+If the user approves both requests, every time the connector requests the portal to perform an action coming from a relationship, the portal can use the JSON Web Token shared through this relation.
 
@@
 
-When the user profile is connected with the IMP identity, an attribute request is issued at least for the JWT issued by the user profile component.
-In case the JWT authorizes the IMP client to manage personal information of user profile, the administration portal can request access to attributes of the IMP identity which are also stored in the user profile.
-
-As the attributes stored in the user profile might be named differently than the attributes stored in the user profile, some mapping has to take place.
-
-The access of the administration portal to attributes of the IMP identity is stored as part of the relationship.
-
-There are multiple ways to synchronize the attributes.
-One way would require the administration portal to compare the attributes of the IMP identity with those of the user profile.
-Another option would be for the IMP client to notify the administration portal of a change in the shared attributes.
-The second option would be beneficial, as iterative requests to the IMP Client and user profile are resource intensive, especially for a large number of users.
-
-\paragraph{Attribute Mapping}
+\begin{center}
+    \includegraphics[width=15cm]{Diagrams/Integration 1/Personal Information/Overview.png}
+\end{center}
+
+While configuring the authorisation of the IMP identity on the previously described website, the user can determine if the IMP identity is allowed to manage personal information stored in the user profile.
+If the user approves, the JSON web Token stored as attribute of the identity is authorized to update, delete and read attributes of the user profile.
+As the user profile determines which attributes exist, no attributes can be added.
+
+If an attribute of an identity changes, the IMP client notifies all relationships.
+When the connector receives this notification, he reads all shared attributes and requests the administration portal to update the same attributes in the user profile.
+As the naming and meaning of attributes can differentiate between IMP systems and OZG systems, the attributes have to be mapped to each other.
+A simple solution would be a table, created by an administrator, which maps each attribute from the IMP system to an attribute of the OZG system.
 
@@
 Both IMP Client and the administration portal provide an inbox functionality.
-If an IMP identity is connected with a user profile, it can send and receive messages as part of the relation it has with the administration portal.
-As the administration portal does not store any information on which user profile is connected with which IMP identity, it cannot forward messages of the inbox to the IMP identity of a relation.
-The IMP client will have to request for new messages from time to time or the previously removed database which maps IMP relations to user profiles is added again.
+If an IMP identity has established a relationship with the administration portal, they can exchange messages through the connector as part of this relationship.
+
+In order to notify the user of a new message to the user profile, the administration portal can send the same message through the relationship associated with this user.
+The user can, however, only send messages to the administration portal and not to for example institutions.
+
+\paragraph{Data Wallet}
+
+\subsubsection{Messaging Architecture}
+
+\subsection{Integration 2}
+
+Option for user to use IMP identity INSTEAD of user profile
 

### 2021-01-19 msc-thesis.tex
changed stuff

@@
 
-In this scenario, the IMP system integrates only with the administration portal to enable the usage of its identity related functionalities through the IMP client.
-The integration architecture contains one connector which interacts with the administration portal.
-The integration should provide an additional optional way for users to manage their OZG identity.
-
-\subsubsection{Overview}
-
-\begin{center}
-    \includegraphics[width=8cm]{Diagrams/Integration 1/Overview.png}
-\end{center}
-
-\subsubsection{Functionalities}
-
-The IMP client should be able to:
-\begin{itemize}
-    \item manage personal information stored in the user profile
-    \item receive and send messages through the inbox of the user profile
-    \item upload and download documents through the data wallet of the user profile
-    \item manage active applications
-\end{itemize}
-
-The IMP client should however not be used to search for administrative services, as this is a service of the portal which is not related to the management of an identity.
-
-\subsubsection{Integration}
-
-\paragraph{Association IMP ID and OZG ID}
-
-Before the IMP client can access services of the administration portal, it has to be possible to connect the IMP identity with a user profile.
-The user should be able to connect and disconnect the identity with an existing user profile.
-
-\begin{center}
-    \includegraphics[width=10cm]{Diagrams/Integration 1/Connection/Overview.png}
-\end{center}
-
-The administration portal provides an additional web page where a logged in user can connect an IMP identity with his user profile.
-When the user requests the web page from the server, the portal requests the connector to create a relationship template.
-The template is stored on the IMP server but can be accessed by any client which has the correlating template ID.
-The administration portal fills the template with information for identification of the connector, the ID of the user, a reason why the relationship is requested and a list of attributes the IMP client is required to share.
-After creation of the template, the connector submits the template ID to the administration portal in form of a QR code.
-
-The portal now transmits the web page including the QR code to the web browser of the user.
-The user can now scan the QR code with the IMP client.
-The client retrieves the template corresponding to the template ID from the IMP server and displays the request.
-
-If the user accepts, the connector is notified of an incoming relationship request trough the IMP server.
-The request contains the template ID, information about the IMP identity of the user, the shared attributes and the user ID.
-
-The connector transfers the request to the administration portal which, based on the user ID, updates the web page to display a confirmation request.
-The confirmation request contains information about the IMP identity which requested to connect to the user profile.
-If the user accepts the confirmation, the administration portal requests the connector to accept the relationship which results in a relationship ID.
-The association of the relationship ID and the user ID is stored in a database.
-
-The connection of the user profile and the IMP identity is an IMP relationship.
-
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging Overview.png}
-\end{center}
+\begin{figure}[h]
+\caption{Overview Integration Scenario 1}
+    \centering
+    \includegraphics[scale=0.2]{Diagrams/Integration 1/Overview.png}
+\end{figure}
+
+In this scenario, the IMP system integrates only with the administration portal to extend the usage of identity related functionalities through the IMP client.
+The integration architecture contains one connector which integrates with the administration portal and communicates with IMP server and IMP client.
+
+Through the integration, the user will be able to connect his OZG user profile with an IMP identity.
+As a result of this connection, the personal information of the user profile will be synchronized with the attributes of the IMP identity.
+The user will only be able to change personal information of his user profile through the IMP client.
+If the user has connected an IMP identity, starting an application will require authorization through the IMP client.
+However, starting and filling in the application will still be done through the web page of the administration portal and form server.
+After the user submitted the application through the form server, the user will be able to manage active applications through the IMP client.
+The user will be able to send and receive messages of the user profile inbox through the inbox of the IMP client and combine the data wallet of the IMP client and user profile.
+
+The integration provides an improved experience of the basic OZG use case through the IMP systems by making existing functionalities of the administration portal available through the IMP client.
+Especially the fact that the user wont have to manage the OZG user profile separately is an advantage for the user.
+Communicating with governmental institutions through the smartphone instead of a web page is also more convenient.
+
+This integration scenario can be a first step by service providers to adopt an IMP system.
+
+\paragraph{Linking IMP ID and OZG ID}
+
+Before the IMP client can access services of the administration portal, the user has to be able to connect his IMP identity with the user profile.
+This is necessary for the integration architecture to enable bidirectional communication between OZG systems and IMP client regarding a user.
+
+The administration portal hosts an additional web page where a logged in user can connect one IMP identity to his user profile.
+The IMP identity can be connected with the user profile through an IMP relationship between the administration portal and the IMP identity.
+The relationship includes the ID of the user profile as metadata in order for the relationship to be associated to a user profile.
+For a relationship to be established, a relationship template has to be created.
+This template is created by the IMP connector and stored on the IMP server.
+The template can be referenced through a template ID, created by the IMP server.
+The relationship template contains information about the administration portal and its connector, the reason for the relationship, attributes the IMP client is required to share as part of the relationship and the ID of the user profile.
+Based on the template ID, the connector creates a QR code which gets displayed on the web page for any IMP client to scan, retrieve the relationship template and issue a relationship request.
+The request contains information about the IMP identity and values for the requested attributes.
+The user gets notified of the connection request through an E-Mail which includes an URL.
+Visiting this URL will confirm the relationship request.
+
+After confirmation, the IMP identity is connected with the administration portal through an IMP relationship which contains the ID of a user profile.
+The administration portal stores the IMP identity ID, the relationship ID and the user profile ID as an entry in a database.
+
+The relationship can be cancelled through the IMP client or through the web page of the administration portal.
+
+\begin{figure}[h]
+\caption{Overview Connection}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Overview.png}
+\end{figure}
+
+The web server of the administration portal hosts an additional web page where a user can connect an IMP identity with his user profile.
+When a user tries to visit the web page, the browser sends a GET request to the server and attaches a session ID as cookie.
+Based on the session ID, the web server can determine the user ID and the authentication state of the session.
+If the user is not authenticated, the server responds with a redirection to the login page.
+If the user is authenticated, the web server requests a QR code from the messaging system for connecting an IMP identity to the user ID of the session.
+
+A messaging gateway is integrated into the run-time of the web server.
+It provides an API for the server code to send and receive messages while hiding most complexities of messaging.
+After the authentication of the session is validated, the web server calls the API of the gateway to request the QR code for connecting an IMP identity to the user ID which corresponds to the session.
+The messaging gateway places a message on the "Connection QR Request" channel.
+The message contains the ID of the user (UID).
+Based on the request-reply pattern, the messaging gateway will receive a reply through the "Connection QR Reply" channel.
+In order for the gateway to match replies to requests, request and reply message contain a request ID (RID) with the same value.
+
+As the name suggests, the relationship template is the basis for creating a relationship request.
+One template can therefore be used multiple times.
+Therefore, in order to save resources, QR codes for connecting IMP identities and user profiles should be reused.
+However, it still has to be possible to use new relationship templates, as the required content of future relationships might change.
+It could for example happen, that additional attributes are required to be shared by the IMP identity or that a user agreement attached to the relationship metadata changed.
+
+The messaging architecture contains a QR code management system which is responsible for storing all QR codes and the corresponding user IDs.
+Messages sent to the "Connection QR Request" channel are consumed by a content-based router who checks if the QR code database contains an entry for the UID of the message.
+If this is the case, the message is sent through a content enricher and a content filter where the QR code is added, the UID is removed and the message is placed on the "Connection QR Reply" channel.
+Content-based router and content enricher have access to the QR code database but do not necessarily communicate through messaging.
+
+If the content-based router does not find a QR code for the UID in the database, the message is sent to a different content enricher which adds a configuration to the message.
+This configuration contains information for the connector on how to create the relationship template.
+The message is then sent to the "Create Relationship Template" channel, where the connector is able to read it.
+The connector uses the configuration stored in the message to create the relationship template and store it on the IMP server.
+The connector exports the corresponding template ID as a QR code and publishes a message containing the user ID, the request ID and the QR code on the "Publish New Relationship QR" channel.
+Any application can subscribe to this channel and process the contained messages.
+In this case, two content filters are subscribed.
+One of the content filters was already described earlier where a QR code for the user ID was already stored in the database.
+This content filter does the same as described previously, it removes the user ID from the message and sends it to the "Connection QR Reply" channel.
+The other content filter prepares the message to be added to the QR code database by removing the Response ID.
+Through a messaging gateway, the database is able to receive the message and store the QR code.
+
+The messages on the "Connection QR Reply" channel are read by the messaging gateway of the web server and received by the code of the server through a return statement of an API function call.
+The QR code is now added to the web page and sent back to the web browser of the user.
+
+\begin{figure}[h]
+\caption{Overview Connection Messaging}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging Overview.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 1.png}
-\end{center}
+\begin{figure}[h]
+\caption{Web Page Messaging Adapter}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 1.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 2.png}
-\end{center}
+\begin{figure}[h]
+\caption{Request Reply Smart Proxy}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 2.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 3.png}
-\end{center}
+\begin{figure}[h]
+\caption{Filtering and Routing Request}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 3.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 4.png}
-\end{center}
+\begin{figure}[h]
+\caption{Retrieving Existing QR Code}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 4.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 5.png}
-\end{center}
+\begin{figure}[h]
+\caption{Requesting New Template}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 5.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 6.png}
-\end{center}
+\begin{figure}[h]
+\caption{Creating New Template}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 6.png}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Connection/Messaging 7.png}
-\end{center}
+\begin{figure}[h]
+\caption{Storing New Template}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 7.png}
+\end{figure}
 
@@
 \begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Authorisation/Overview.png}
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Authorisation/Overview.png}
 \end{center}
@@
 \begin{center}
-    \includegraphics[width=15cm]{Diagrams/Integration 1/Personal Information/Overview.png}
+    \includegraphics[scale=0.3]{Diagrams/Integration 1/Personal Information/Overview.png}
 \end{center}

### 2021-01-28 msc-thesis.tex
integration overview

--- 2021-01-13 msc-thesis.tex
@@
 
-\paragraph{1. Selection of Administrative Service}
+\paragraph{1. Create User Profile}
+The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.
+
+\paragraph{2. Login to User Profile}
+Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
+The user has to finish authentication steps, which can consist for example of a username and password.
+Depending on the authentication method, a trust level of the current session is determined.
+With approval from the user, personal information from his profile is provided towards the form-server.
+
+\paragraph{3. Selection of Administrative Service}
 The user visits any administration portal of the portal network and types a search term in the corresponding search field.
@@
 
-\paragraph{2. Login to User Profile}
-Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
-The user has to finish authentication steps, which can consist for example of a username and password.
-Depending on the authentication method, a trust level of the current session is determined.
-With approval from the user, personal information from his profile is provided towards the form-server.
-
-\paragraph{3. Filling in Application}
+\paragraph{4. Filling in Application}
 Personal information from the user profile is used by the form-server to fill as many fields of the form as possible.
@@
 
-\paragraph{4. Uploading Attachments}
-The user can upload documents to his user profile and reference them in the form.
-
 \paragraph{5. Submission of Application}
@@
 
-\paragraph{8. Sending of Acknowledgment}
-The data-exchange platform notifies the user through the inbox functionality of the user profile if the application was submitted successfully.
+\paragraph{8. Management of Applications}
+The administration portal stores active applications and enables the user to manage them.
+
+\paragraph{9. Communication}
+As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.
+Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.
 
@@
 Components are defined based on strongly connected categories of services \cite{NRW:Umsetzung}:
+
+\begin{figure}[h]
+\caption{Overview IMP System}
+    \centering
+    \includegraphics[scale=0.25]{Diagrams/OZG System Overview.png}
+\end{figure}
+
+\paragraph{Administration Portal}
+The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components.
+Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server.
+Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
+The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components.
+The most important components, the service facade provides an interface for are:
+
+\begin{itemize}
+    \item \textbf{Responsibility Finder}
+
+    This service component is used to find administrative institutions which are responsible for an application.
+Depending on the type of application and on the home address of the user, different institutions might be responsible.
+
+    \item \textbf{Process Management}
+
+    This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.
+
+    \item \textbf{Search}
+
+    This service component creates a list of URLs of administrative services relevant for a specified search term.
+This enables the portal to provide a search functionality of administrative services for the user.
+
+    \item \textbf{User Profile Management}
+
+    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and sent messages to an institution.
+
+    \item \textbf{Application Management}
+
+    This service component manages applications issued through the administration portal through communication with the form server.
+The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server.
+Form server and portal communicate about the status and content of the application.
+The user is able to keep track about the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.
+
+\end{itemize}
 
@@
     The user can be notified of a new message through E-Mail.
-
-\end{itemize}
-
-\paragraph{Administration Portal}
-The administration portal provides the user access to various OZG services of other system components:
-
-\begin{itemize}
-
-    \item \textbf{Application for administrative service}
-    The administration portal provides access to services for creation and submission of applications for administration services.
-The portal hosts a web page for each administration service which enables the user to get information about the service and start the application process.
-After starting the process, the portal interacts with multiple system components to guide the user through the application.
-
-    \item \textbf{Management of user profile}
-    The administration portal provides access to the personal information stored in the user profile by interacting with the user profile system component.
-It enables the user to add, remove and update a set of attributes.
-
-    \item \textbf{Management of inbox}
-    The administration portal provides access to the inbox of the user profile. It enables the user to send new messages and display received messages.
-
-    \item \textbf{Management of data wallet}
-    The administration portal provides access to the data wallet of the user profile. It enables the user to upload and download documents and to attach copies of documents to applications.
-
-\end{itemize}
-
-The administration portal provides additional services:
-
-\begin{itemize}
-    \item \textbf{Determination of responsible institution}
-
-    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender.
-It is the responsibility of the administration portal to determine which institution receives which application.
-
-    \item \textbf{Search and find Administrative Service}
-
-    The administration portal provides a search and find service which enables the user to find the web page of all administrative services which relate to the entered search term.
 
@@
 
-\section{IMP Solution Proposal}
-
-This section describes a solution for an IMP system considering the previously mentioned requirements.
+\section{IMP System Proposal}
+There exist many ways to realize an IMP system. Based on the previously analyzed requirements of users and OZG systems, a possible solution for an IMP system is presented.
 
 \subsection{Components}
+The IMP system operates on three domains and consists 3 system components.
+The user domain contains systems, a user directly interacts with.
+As for the system architecture of the OZG, can be a web browser.
+The solution for the IMP system provides an IMP client as an app for smartphones.
+The IMP domain contains systems hosted by the IMP provider.
+The IMP server is part of this domain.
+The Service Provider domain contains the system architecture of the service provider and integration components of the IMP solution.
+In the following sections, IMP client and IMP server are explained in more detail, the integration system will be the focus of the next chapter.
+
+\begin{figure}[h]
+\caption{Overview IMP System}
+    \centering
+    \includegraphics[scale=0.25]{Diagrams/IMP System Overview.png}
+\end{figure}
 
@@
 
-The IMP client is a smartphone application which enables the user to manage his IMP identity. The client provides the following functionalities:
-\begin{itemize}
-    \item Create an identity
-    \item Manage attributes of the identity
-    \item Manage documents
-    \item Send and receive messages
-    \item Send and receive relationship requests
-    \item Send and receive requests
-\end{itemize}
+The IMP client is a smartphone application which enables the user to manage his IMP identity. It enables the user to:
+
+\paragraph{Create an IMP identity}
+
+After the user installs the application on his smartphone, he is able to create an IMP identity.
+The identity consists of a public and private key-pair.
+The private key will never leave the smartphone.
+The public key is shared with the IMP server along with information on how to communicate with the client.
+
+\paragraph{Manage Attributes}
+
+The user is able to add, remove, update and read any key-value pair as an attribute of his identity. Attributes are encrypted with the
+
+\paragraph{Documents}
+
+The user is able to add, remove, update and read any document as an attribute of his identity. All documents are stored on the smartphone.
+
+\paragraph{Send and Receive Messages}
+\paragraph{Send and Receive Relationship Requests}
+\paragraph{Send and Receive Share Requests}
+\paragraph{Display Forms}
 
@@
 \begin{itemize}
+    \item Store identities
     \item Create and store relationship template
@@
 \subsection{Functionalities}
-
-\subsubsection{Relationships}
-
-\subsubsection{Requests}
+As already introduced, the IMP solution provides the user with multiple functionalities. In this section, important features are described in more detail.
+
+\subsubsection{Relationship}
+
+IMP identities can establish an IMP relationship. Through this relationship, both identities can securely share attributes and communicate.
+
+To establish a relationship, a relationship template is required.
+The template is created by an identity which wants to receive relationship requests and is shared with the identity which wants to request a relationship.
+The relationship template is stored on the IMP server and can be retrieved trough template ID.
+Besides technical information, the template usually contains:
+\begin{enumerate}
+    \item Information which the templator would like to share about itself 
+    \item Information which the templator would like the requestor to share
+    \item Requested additional information about the requestor 
+    \item Meta information 
+\end{enumerate}
+
+\subsubsection{Share Attribute}
+
+\subsubsection{Change Attribute}
 
@@
 
+The goal of the integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. The main OZG functionalities are:
+\begin{enumerate}
+    \item{Create User Profile}
+    \item{Login to User Profile}
+    \item{Selection of Administrative Service}
+    \item{Filling in Application}
+    \item{Submission of Application}
+    \item{Reception of Application by Administration Portal}
+    \item{Submission of Application to Data-Exchange Platform}
+    \item{Management of Applications}
+    \item{Communication}
+\end{enumerate}
+
 \section{Requirement Analysis}
@@
 
-\section{Integration}
-
-Multiple integration scenarios are presented with increasing complexity and functionality.
-
-\subsection{Scenario 1}
-
-In this scenario, the IMP system integrates only with the administration portal to enable the usage of its identity related functionalities through the IMP client.
-The integration architecture contains one connector which interacts with the administration portal.
-The integration should provide an additional optional way for users to manage their OZG identity.
-
-\subsubsection{Overview}
-
-\begin{center}
-    \includegraphics[width=8cm]{Diagrams/Integration 1 Overview.png}
-\end{center}
-
-\subsubsection{Functionalities}
-
-The IMP client should be able to:
-\begin{itemize}
-    \item manage personal information stored in the user profile
-    \item receive and send messages through the inbox of the user profile
-    \item upload and download documents through the data wallet of the user profile
-    \item manage active applications
-\end{itemize}
-
-The IMP client should however not be used to search for administrative services, as this is a service of the portal which is not related to the management of an identity.
-
-\subsubsection{Integration}
-
-\paragraph{Association IMP ID and OZG ID}
-
-Before the IMP client can access services of the administration portal, it has to be possible to connect the IMP identity with a user profile.
-The user should be able to connect and disconnect the identity with an existing user profile.
-As in this scenario the IMP systems only integrate with the administration portal, the user profile should not be modified to include information about an IMP identity.
-
-\begin{center}
-    \includegraphics[width=8cm]{Diagrams/Integration 1 Connection Overview.png}
-\end{center}
-
-The administration portal can provide an additional web page where a logged in user can connect an IMP identity with his user profile.
-In order for the web page to initiate a connection process, administration portal and IMP identity require some way to identify each other.
-Either the IMP identity identifies itself to the administration portal or the administration portal identifies itself to the IMP identity.
-
-The IMP identity could identify itself to the administration portal through manual entering of an IMP ID on the web page.
-This could enable the administration portal to interact with the identity through a connector.
-Another option is for the administration portal to identify itself to the IMP identity.
-As the IMP system provides a functionality for this, it is the better option.
-Through the connector, the administration portal can create a relationship template.
-The template is stored on the IMP server but can be accessed by any client which has the correlating template ID.
-The template contains information for identification of the connector, a encrypted session ID, a reason why the relationship is requested and a list of attributes the IMP client is required to share.
-
-Based on the resulting template ID, the connector creates a QR code which the administration portal includes in web page before sending it to the user.
-The user can now scan the QR code with the IMP client which retrieves the template corresponding to the template ID from the IMP server.
-The IMP client displays the request and if the user accepts, the connector is notified of an incoming relationship request.
-The request contains the template ID, information about the IMP identity of the user, the shared attributes and the encrypted session ID.
-
-The connector transfers the relationship request to the administration portal which based on the decrypted session ID sends a confirmation request to the web page.
-The confirmation request contains information about the IMP identity which requested to connect to the user profile.
-If the user accepts the confirmation, the association of the IMP relation and the user ID is stored in a database.
-
-The connection of the user profile and the IMP identity would therefore be an IMP relationship.
-
-\paragraph{Authorisation}
-
-If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token, which enables it to start actions in the name of the user.
-The user might want to manage which actions an IMP client is authorised for.
-
-On the web page where the user can connect user profile and IMP identity, authorisation of a connection can be managed too.
-After a success full connection, the web page presents a UI where the user can determine which actions the IMP client should be able to perform.
-If the user finishes, the administration portal can request the authorisation from the user profile which requests authentication from a user.
-The resulting JSON Web Token is then transmitted to the administration portal.
-
-The JSON Web Token contains information to identify the user profile and the authorisations for the entity which possesses this token.
-It also includes a signature with a private key of the user profile component.
-This allows the component to check if the token is valid.
-
-This token can be stored in the database where IMP relations are mapped to profile IDs.
-
-\paragraph{Improved Association of IMP ID and OZG ID}
-
-JSON Web Tokens can also function as a connection between user profile and IMP identity because they includes the ID of a user profile.
-If the IMP client is in possession of this token and requests the administration portal to perform an action, the administration portal can read the profile ID stored inside the token along with the authorisation information.
-The portal can then verify the validity of the token through the user profile component.
-If the validation was successful, the portal knows, that whoever sent the request has the authorisation stored in the token for the user profile ID stored in the token.
-
-The JSON Web Token can be saved as attribute of the IMP identity which the administration portal was granted access to.
-Whenever the portal receives a request from a relation to for example modify an attribute in the user profile, the portal can read the JSON Web Token of the corresponding IMP identity determine the connected user profile ID and verify the authorisation.
-
-\paragraph{Personal Information}
-
-One of the goals of an IMP system is to enable the user to only manage his identity in one place while all other service providers rely on the attributes of the identity.
-As in this scenario however, the OZG system does not rely on attributes of the IMP system but enables it to manage personal information stored in the user profile.
-Some synchronisation mechanism can therefore operate.
-
-When the user profile is connected with the IMP identity, an attribute request is issued at least for the JWT issued by the user profile component.
-In case the JWT authorizes the IMP client to manage personal information of user profile, the administration portal can request access to attributes of the IMP identity which are also stored in the user profile.
-
-As the attributes stored in the user profile might be named differently than the attributes stored in the user profile, some mapping has to take place.
-
-The access of the administration portal to attributes of the IMP identity is stored as part of the relationship.
-
-There are multiple ways to synchronize the attributes.
-One way would require the administration portal to compare the attributes of the IMP identity with those of the user profile.
-Another option would be for the IMP client to notify the administration portal of a change in the shared attributes.
-The second option would be beneficial, as iterative requests to the IMP Client and user profile are resource intensive, especially for a large number of users.
-
-\paragraph{Attribute Mapping}
-
-\paragraph{Inbox}
-
-Both IMP Client and the administration portal provide an inbox functionality.
-If an IMP identity is connected with a user profile, it can send and receive messages as part of the relation it has with the administration portal.
-As the administration portal does not store any information on which user profile is connected with which IMP identity, it cannot forward messages of the inbox to the IMP identity of a relation.
-The IMP client will have to request for new messages from time to time or the previously removed database which maps IMP relations to user profiles is added again.
-
-\section{Extension: Inbox}
-
-\section{Extension: Collaboration}
+\section{Integration Architecture 1}
+
+Integrating an IMP solution for management of customer identities is no simple task.
+To make the introduction of IMP systems easier for service providers, this first integration architecture describes a non invasive integration.
+After applying this integration, all OZG services are still usable as before but can be enhanced by IMP solutions.
+For this integration not to be invasive, only one connector exists and integrates only with the administration portal.
+No other OZG system component is modified or directly accessed.
+
+The goal of the integration is to enhance each step of the basic OZG use case through integration with IMP solutions.
+Therefore in the overview section, for each step, possible integration's of OZG systems are evaluated.
+The following sections contain more detailed descriptions of the selected integration strategies.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
+\end{figure}
+
+\subsection{Overview}
+
+This section gives an overview of integration possibilities for each step of the basic OZG use case.
+For each step, multiple integration strategies are evaluated and one strategy is selected for more detailed description in following sections.
+
+\paragraph{Create User Profile}
+
+The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
+
+Creation and management of multiple user profiles quickly becomes a burden for users.
+If all service providers would switch to using only identities provided by an IMP solution, users would only have to manage one digital identity.
+However performing this change is no simple task for a service provider.
+An abrupt change of the system architecture can lead to many problems like extended periods of down times.
+This integration architecture therefore focuses on a simplified initial integration of IMP identities where OZG user profiles can still be used to access OZG services.
+
+It would be possible to integrate the IMP identity as an alternative to the user profile.
+The user could then use OZG services either by creating a user profile or by providing an IMP identity.
+Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile.
+The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management.
+The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution.
+OZG systems would have to request personal information from the IMP identity while providing a reason for doing so.
+After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity.
+However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile.
+As the focus of this integration architecture is simplicity and non incisiveness, the connection of IMP identity and user profile is preferred.
+
+The IMP solution provides a service for establishing a connection between entities.
+It is called an IMP relationship.
+Through a relationship, two entities can identify each other, assume authentication of the other party and can securely communicate and share attributes of their IMP identities.
+To utilize an IMP relationship between the administration portal and the IMP identity as connection between user profile and IMP identity, the relationship has to contain identification of the user profile in form of for example a user ID.
+The administration portal would then be able to map relationships along with the IMP identity ID to user profiles.
+
+In order for an IMP identity to request a relationship with the administration portal, the portal has to provide a relationship template to the IMP client of the user.
+The template can be made accessible to the IMP client trough a new web page which displays the template ID as QR code if the user is logged in.
+Each time a logged in user requests the web page, the web server requests the IMP connector to create a relationship template.
+
+The IMP connector provides an API for creation of relationship templates as part of its REST interface.
+Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response.
+The web page can then render the template as a QR code on the web page.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template REST.png}
+\end{figure}
+
+This is one example, where the OZG system could use the REST interface for integration with the IMP system.
+However, messaging can improve the integration solution to be more maintainable, stable and scalable and will be the preferred option in following scenarios.
+Using messaging, the web server can publish a message containing the request for a new relationship template on a "Relationship Template Request" channel, where the connector receives it, creates the template and publishes a reply message containing the template ID on the "Relationship Template Reply" channel.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging.png}
+\end{figure}
+
+It could happen, that in future, the API of the connector changes.
+If the web server integrated the connector through its REST interface, this would require the request code of the web server to be changed.
+If messaging is used, messages leaving the "Relationship Template Request" channel could be mapped to the new API signature through an additional messaging component called message translator.
+This is an example for how a messaging can improve maintainability of an integration architecture.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging Improved.png}
+\end{figure}
+
+When the user is presented with the web page containing the QR code, the user can scan it with its IMP client.
+Based on the template ID, the client retrieves the template from the IMP server and displays it for the user.
+If the user accepts the template, the client sends a relationship request to the IMP server, who forwards it to the corresponding connector.
+
+Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request.
+If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request.
+The server would have to regularly request a status update which is not efficient.
+Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified.
+The administration portal can process the relationship request and publish a message containing a response on the "Relationship Request Response" channel, where the connector will be notified.
+Through the IMP server, the connector sends the response to the IMP client and the relationship is established.
+In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Request.png}
+\end{figure}
+
+Neues Kapitel/Überschrift: Attribute Synchronization
+
+The goal of the connection of IMP identity and OZG user profile is to enable management of personal information through the IMP client.
+Attributes stored as part of the IMP identity and attributes stored as part of the user profile have to be manageable through the IMP client.
+
+One option would be for the IMP client to overwrite all attributes of the OZG user profile with those stored in the IMP identity and update values in the user profile as soon as an attribute of the IMP identity changes.
+This would require the user profile management web page of the administration portal to be locked for profiles with a connected IMP identity.
+Another option would be to enable the user to manage attributes of IMP identity and user profile separately through the IMP client.
+
+The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically.
+However, this would require the user to always share the most current personal information with the OZG systems.
+Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider.
+If the user for example changes the home address of its IMP identity, the OZG system might not want to approve this change immediately.
+If the user manages IMP identity and user profile separately, changes of the OZG user profile can happen on a request reply basis.
+The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there.
+The disadvantage of this option is, that the management of personal information is more complicated than the first option.
+Through attribute management tools on the IMP client, the experience can be improved.
+
+As the second option provides necessary features, which the first option does not have, it is preferred.
+
+The management of both IMP identity attributes and attributes of the OZG user profile can be done as part of the relationship established for their connection.
+As part of the connection, IMP identity and administration portal share attributes.
+The user profile can be determined to store the exact same values as shared by the IMP identity as part of this relationship.
+Therefore, in order to change attributes of the user profile, the value of the shared attributes has to change.
+This can be done through a request-reply process.
+One party requests the change of a shared attribute, which will only be done if the other party accepts.
+This enables the user to manage the OZG user profile through the IMP client by requesting a change for attributes shared as part of a relationship.
+The user could also manage his user profile through the web page of the administration portal, resulting in a request form the administration portal to change shared attributes of the relationship.
+
+As administration portal and IMP identity established a relationship, the connector can be excluded from the diagram for better visualisation.
+Behind the scenes, all interactions between administration portal and IMP client still go through connector and IMP server.
+
+If the user requests the change of a shared attribute through the IMP client, it sends an attribute change request to the administration portal by publishing a message on the "Inbound Attribute Change Request" channel.
+After the administration portal decides to accept the request, it can publish a message to the "Outbound Attribute Change Response" channel.
+This message will on one hand be received by the IMP client and on the other hand result in an update of the user profile.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change IMP Client.png}
+\end{figure}
+
+If the user requests the change of a shared attribute through the web page of the administration portal, the web server sends an attribute change request to the "Outbound Attribute Change Request" channel which is received by the IMP client.
+If the user accepts the request, the client publishes a message on the "Inbound Attribute Change Response" channel where it results in an update of the user profile.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change Web Page.png}
+\end{figure}
+
+\paragraph{Login to a User Profile}
+
+The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
+As the integration solution for connection of user profile and IMP identity was chosen, the user is still able to login to his user profile on the administration portal and take advantage of all OZG services.
+The IMP system can however provide an additional way to access OZG services through the IMP client.
+One possibility was already introduced: the management of personal information.
+
+In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid.
+Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session.
+When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components.
+This process is necessary because any person can send requests to the web server and possibly pretend to be a different user.
+In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user.
+Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity.
+As the IMP client is an app installed on the smartphone of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Login.png}
+\end{figure}
+
+\paragraph{Application for Administrative Service}
+The third step is selection of an administrative service through the web page of the administration portal.
+This service is not directly related to identity management and will therefore not be provided by the IMP client.
+The steps four to eight are not integrated by the IMP solution as this would require invasive interaction with components other than the administration portal.
+
+As a result of that, most of the steps necessary for applying for an administrative service remain to be done through the web page of the administration portal with a logged in user profile.
+The next integration architecture will present a solution where most of the steps will be done through the IMP systems.
+
+\paragraph{Communication}
+
+The ninth step of the basic OZG use case is to communicate with responsible institutions.
+As both the user profile and the IMP identity provide an inbox, the IMP client can be used to send and receive messages through the inbox of the OZG user profile.
+
+The messages related to a OZG user profile can be exchanged as part of the relationship between the administration portal and the IMP identity.
+Messages received by the user profile can be forwarded by the administration portal to the inbox of the IMP identity.
+Sending messages from the IMP client to institutions however is not possible, as the IMP client does not know the address of the institution responsible for an application.
+However, if the IMP client already received a message from an institution, it can enable the user to respond.
+
+\subsection{Connection}
+
+\subsection{Personal Information}
+
+\subsection{Authentication}
+
+\subsection{Communication}
+
+\section{Integration Architecture 2}
+
+The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client.
+Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 2/Overview.png}
+\end{figure}
+
+\subsection{Overview}
+
+The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
+This is not necessary any more, as user profiles are replaced by IMP identities.
+The user will only have to create an IMP identity.
+
+The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
+As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services.
+The IMP client does not require authentication, as it is installed on the smart phone of the user.
+The user can secure his smartphone through for example biometric authentication.
+
+The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.
+
+The fourth step of the basic OZG use case is to fill in the application.
+The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.
+
+The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more.
+Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.
+
+For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template.
+The connector responds to the institution with the template IDs.
+
+In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address.
+After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.
+
+If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it.
+The relationship template contains a description of the selected administrative service as reason for the relationship.
+The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application.
+This replaces the functionalities of the form server.
+
+The fifth step of the basic OZG use case is to submit the application.
+After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes.
+The institution can accept the request and start processing the application.
+The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.
+
+The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.
+
+The eighth step of the basic OZG use case is the management of active applications.
+As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution.
+Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.
+
+The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications.
+As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.
 

### 2021-01-28 msc-thesis.tex
Corrections

@@
 
-The goal of the integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. The main OZG functionalities are:
+The goal of the integration architecture is to make as many functionalities required for the basic OZG use case available through the IMP client as possible.
+As described in chapter 2.3, the steps of the basic OZG use case are:
 \begin{enumerate}
@@
 
-\section{Integration Architecture 1}
-
-Integrating an IMP solution for management of customer identities is no simple task.
-To make the introduction of IMP systems easier for service providers, this first integration architecture describes a non invasive integration.
-After applying this integration, all OZG services are still usable as before but can be enhanced by IMP solutions.
-For this integration not to be invasive, only one connector exists and integrates only with the administration portal.
+\section{Minimal Integration Architecture}
+To enable service providers a quick introduction of IMP systems into their system architecture, this first integration architecture describes a minimally invasive integration.
+After deployment of this integration architecture, all OZG services are still usable as before but can be enhanced by IMP solutions.
+For this integration to be minimally invasive, only one connector exists and integrates only with the administration portal.
 No other OZG system component is modified or directly accessed.
@@
 It would be possible to integrate the IMP identity as an alternative to the user profile.
-The user could then use OZG services either by creating a user profile or by providing an IMP identity.
+The user could then use OZG services either by creating an OZG user profile or by providing an IMP identity.
 Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile.
@@
 However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile.
-As the focus of this integration architecture is simplicity and non incisiveness, the connection of IMP identity and user profile is preferred.
+As the focus of this integration architecture is non invasiveness, the connection of IMP identity and user profile is preferred.
 
@@
 Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response.
-The web page can then render the template as a QR code on the web page.
+The web page of the administration portal can then render the template as a QR code on the web page.
 
@@
 Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified.
-The administration portal can process the relationship request and publish a message containing a response on the "Relationship Request Response" channel, where the connector will be notified.
-Through the IMP server, the connector sends the response to the IMP client and the relationship is established.
+The administration portal can process the relationship request and publish a message containing a response on the "Relationship Response" channel, where the connector will be notified.
+Through the IMP server, the response server is routed to the IMP client and the relationship is established.
 In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.
@@
 
-Neues Kapitel/Überschrift: Attribute Synchronization
+\paragraph{Attribute Synchronization}
 
@@
 Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider.
-If the user for example changes the home address of its IMP identity, the OZG system might not want to approve this change immediately.
-If the user manages IMP identity and user profile separately, changes of the OZG user profile can happen on a request reply basis.
+If the user for example changes the birth date of its IMP identity, the OZG system might not want to approve this change immediately.
+Another option would be for the user to manage IMP identity and user profile separately.
+Changes of the OZG user profile can then happen on a request reply basis.
 The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there.
@@
 
-The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
-As the integration solution for connection of user profile and IMP identity was chosen, the user is still able to login to his user profile on the administration portal and take advantage of all OZG services.
+The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal to access OZG services.
+As previously described, the integration architecture does not replace the OZG user profile.
+The user is therefore still able to login to his user profile on the administration portal and take advantage of all OZG services.
 The IMP system can however provide an additional way to access OZG services through the IMP client.
@@
 Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity.
-As the IMP client is an app installed on the smartphone of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.
+As the IMP client is an app installed on the device of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.
 

### 2021-01-28 msc-thesis.tex
split sections into files

--- 2021-01-19 msc-thesis.tex
@@
 \usepackage{float}
+
+\usepackage{subfiles} % Best loaded last in the preamble
 
@@
 \section{Context}
-Since invention of the World Wide Web, the number of its users increased rapidly.
-Today, more than 90 percent of the German population use the internet \cite{Onlinestudie}.
-Enterprises and organizations, recognised this potential to provide their services to a large number of people as Service Providers (SP).
-A frequently used method of SPs is "online self-service" (OSS).
-Specialized software tools enable customers to use services through the internet without direct human interaction.
 
-Many tools require identification of a user in case interactions or initiated business processes have to be associated with him.
-A system for management of identities of users therefore is part of numerous system architectures.
-Service Providers usually enable users to manage their partial identities using online self-service through so called User Profiles.
-Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP
-
-The result is variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
-\begin{itemize}
-    \item Multiple SPs collect, use and share parts of identities which leads to distributed and fragmented identities.
-    \item As a result of the distributed identities, risk of data breaches increases.
-    \item Managing multiple use profiles is very inconvenient for users.
-    \item It is often unclear who stores which data and for what purpose.
-    \item SPs have an incentive to collect and share more user data than they need.
-\end{itemize}
-
-An improved model for identity management is necessary.
-In recent years, multiple new models have been invented.
-One model called Social Login became popular.
-It enables customers to create User Profiles for SPs through existing User Profile of Social Networks like Facebook.
-This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes.
-Users can therefore manage identity related information through their Social Profile which is accessed by the SP.
-
-This approach, however, still leaves the requirement of User Profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
-SPs also might require additional online self-service tools the social network does not provide.
-
-The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles.
-The system itself is provided and hosted by a SP for consumption by other SPs.
-To replace existing User Profiles, the IMP can not only rely on systems for registration, authentication, authorisation and provisioning.
-Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
-
-In order for an SP to use identities and services of an IMP, an integration into the system architecture of the SP has to take place.
-Due to the complex nature of system architectures and identity management, this is a difficult task.
-
-A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG).
-It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
-The current plan is to make the profiles only available for usage in context of the OZG.
-From a user perspective, this would be yet another partial identity and user profile to manage.
+\subfile{sections/1-context}
 
 \section{Objective}
-Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management Provider.
-In order to make the integration architecture suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
-The integration architecture is however not only applicable in cases relevant for OZG but also for other Service Providers with similar requirements.
-As requirements of SPs are not guaranteed to be similar to those of the OZG, the integration architecture is built to be expendable.
 
-The \textbf{integration architecture} for the OZG enables \textbf{IMP functionalities} to be usable for selected \textbf{OZG scenarios} by integrating a \textbf{connector} in the \textbf{system architecture} of a member state.
-
-\begin{itemize}
-    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example the application for an administrative service or the communication with a governmental institution.
-    \item The system architecture is based on documentation about architecture plans of member states.
-    \item The functionalities of the IMP are based on a requirements analysis of OZG scenarios and additional research.
-    \item The connector is defined based on functionalities the integration architecture requires from the IMP.
-    \item The integration architecture is the main scientific contribution of this bachelor thesis.
-It is based on messaging patterns in order to utilize a combination of established and tested messaging solutions.
-In order to save investments it also reuses as many system components as possible and modifies as few system components as necessary.
-\end{itemize}
-
-The integration architecture ...
+\subfile{sections/2-objective}
 
 \section{Structure of Work}
-The "Fundamentals" chapter explains terminology and basic concepts.
 
-In the following chapter called "Identity Management System" the thesis analyzes requirements for identity management through the perspective of the user and through the perspective of service providers for the OZG.
-It is presented, how an identity management provider could solve current identity management problems and which challenges for an integration exist.
-
-The chapter "Integration Proposal" first documents a possible IMP system and connector, based on the requirement analysis of the previous chapter.
-It then presents the integration architecture with iteratively increasing requirements through textual description, multiple flow diagrams and messaging architectures.
-
-A "Solution Evaluation" analyzes benefits and problems of the proposed solution.
-
-The "Outlook" will conclude the thesis by presenting possibilities for advanced integration architectures.
+\subfile{sections/3-structure_of_work}
 
@@
 
-\paragraph{Service Provider}
-Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.
-
-\paragraph{Online Self-Service}
-Online self-service (OSS) describes a method used by Service Providers to make their services available to the user.
-The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way.
-The user is usually supported by a variety of software solutions.
-
-\paragraph{Self-Service Tools}
-Self-service tools are software solutions for customers to enable a online self-service experience.
-Depending on the use case, the tools can be transactional or informing.
-Informing tools help users to retrieve relevant information, often replacing human customer support.
-Transactional tools help users to interact with services in a persistent way to for example save personal data or trigger business processes.
-
-Information tools can be for example so called "WiKi" pages or search fields which assist the user in his process of finding information.
-Transactional tools can be for example online forms which assist the user in his process of triggering an order placement business process.
-
-In contrast to information tools, transactional tools often require identification of users in order to associate them with changes they made to the system: If a user triggers the business process of ordering a product, the SP requires identification of the user.
-
-\paragraph{Digital Identity}
-The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information.
-Each piece of personal information is an attribute.
-Attributes can be identifiers which are able uniquely identify an entity.
-It is also possible to use an aggregation of attributes as identifier.
-
-Identifiers which are commonly used by SPs are the phone number and E-Mail address.
-Attributes are for example nicknames, hobbies, interests or education.
-The full name of a person is often not sufficient unique identification, the aggregation of name, age and home address can therefore be used as identifier.
-
-\paragraph{Partial Digital Identity}
-A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.
-
-\paragraph{Identity Management}
-Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities.
-The possible utilization of identities depends on the system for management of identities.
-It could be for example authorization for a service or communication through an inbox.
-
-\paragraph{Identity Management System}
-Identity management systems are solutions which enable SPs and customers to manage identities or partial identities.
-They usually provide the following functionalities an properties:
-\begin{itemize}
-    \item 
-\end{itemize}
-
-\paragraph{User Profile}
-User profiles are one method for identity management.
-They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.
-
-\section{Identity Management Provisioning (IMP)}
-Identity management provisioning (IMP) is a method for identity management which is characterized by an identity management provider hosting an identity management system for "non-partial" identities.
-The identity management system provides one-stop online self-service for users and manages the storage of identities.
-SPs are provided access to the identities of the identity management system.
-
-The following are functionalities of an IMP system in addition to those of conventional identity management systems:
-
-\paragraph{Attribute Management}
-It is common for identity management systems to enable users to manage a predetermined set of attributes.
-IMP systems however do not just manage partial identities and therefore enable users to manage any possible attribute of their identity.
-Users therefore can add, remove and modify any attribute.
-
-As often, attributes of a digital identity are defined by service providers, they are also able to create new attributes or delete and modify existing ones, if approved by the user.
-
-\paragraph{Online Self-Service}
-Many attributes, especially those created by SPs, do not make sense to the user without context and my be heavily dependant on systems of a SP.
-Therefore, the IMP provides solutions for online self-service which supports the management of attributes.
-
-\paragraph{Integration}
-Service providers which use IMP systems as solution for identity management require access to its services and have to make their existing systems work with them.
-The IMP solution therefore provides interfaces which enable the SP to access services.
-As it is in the best interest of the IMP solution to integrate SPs, advanced integration methods reducing the integration effort for SPs can be provided.
+\subfile{sections/4-terminology}
 
 \section{Online Access Law (OZG)}
-In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
-\begin{enumerate}
-    \item \textbf{Digital availability of administrative services} \\
-    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.
-As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
-The OZG requires these services to be digitally available.
-As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
-    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
-    Federal republic, each member state and each commune must provide an administration portal.
-Portals of communes must be linked to the portal of the corresponding member state.
-Portals of federal republic and member states must be connected through a portal network.
-\cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.
-    \item \textbf{Interoperable user profiles for accessing administrative services} \\
-    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
-The user profiles must be interoperable for every administration portal of the portal network.
-\end{enumerate}
 
-Execution of the OZG can be separated into two projects:
-
-\paragraph{Digitalization}
-Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions.
-The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:
-
-A digitized administrative service can be accessed by a user through a website.
-The website is hosted either by the federal republic or a member state and is called "Administration Portal".
-Access is usually provided through an application form.
-The administrative service can be managed through a user profile which is provided by the federal republic or the member state.
-Management of an administrative service usually includes starting the service by sending in a form, communicating with responsible institutions through the inbox of the profile and receiving a result.
-The user profile can also enable users to upload documents to a data wallet and to save personal information for automatically filling in forms.
-
-Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal.
-In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and yet other by the communes \cite{BMI:Onlinezugangsgesetz}.
-
-\paragraph{Networking}
-The networking focuses on connecting governmental systems to make all digitized administrative services available for every user.
-This includes most importantly the connection of administration portals to a portal network through an online gateway and the interoperability of user profiles.
-
-In order to save investments a method called "one for all" is used when hosting administrative services.
-One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood".
-As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal.
-Interoperable user profiles enable usage of each profile for management of administrative services on all portals.
-
-\subsection{Basic Use Case}
-The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}.
-Each process consists of multiple sub-processes.
-When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements.
-Those arrangements can be called the basic use case of OZG services.
-
-The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:
-
-\paragraph{1. Selection of Administrative Service}
-The user visits any administration portal of the portal network and types a search term in the corresponding search field.
-The user is then presented with a list of search results consisting of administrative services.
-If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service.
-This page provides information about the administration service along with instructions on how to access the form for application.
-The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.
-
-\paragraph{2. Login to User Profile}
-Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
-The user has to finish authentication steps, which can consist for example of a username and password.
-Depending on the authentication method, a trust level of the current session is determined.
-With approval from the user, personal information from his profile is provided towards the form-server.
-
-\paragraph{3. Filling in Application}
-Personal information from the user profile is used by the form-server to fill as many fields of the form as possible.
-The form with prefilled information is then presented to the user.
-The interactive form can then be modified by the user.
-Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.
-
-\paragraph{4. Uploading Attachments}
-The user can upload documents to his user profile and reference them in the form.
-
-\paragraph{5. Submission of Application}
-The user again authenticates for his user profile and authorises the form-server to submit the application.
-The form-server saves the application until he is notified to delete it.
-The form-server submits the application to the administration portal which hosts the administrative service.
-
-\paragraph{6. Reception of Application by Administration Portal}
-The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.
-
-\paragraph{7. Submission of Application to Data-Exchange Platform}
-The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.
-
-\paragraph{8. Sending of Acknowledgment}
-The data-exchange platform notifies the user through the inbox functionality of the user profile if the application was submitted successfully.
-
-\subsection{System Architecture}
-This subsection describes the system architecture of a member state relevant for the execution the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen.
-Systems, which are responsible for coordination of OZG execution between member states and the federal republic are not the focus.
-
-\subsubsection{System Components}
-The system architecture consists of the following system components.
-Each component consists of a list of services it provides either to the user or to other components.
-Components are defined based on strongly connected categories of services \cite{NRW:Umsetzung}:
-
-\paragraph{Form-Server}
-The from-server provides digital forms associated to administrative services.
-They can be accessed by a user profile through online self-service and submitted as applications to administrative institutions.
-The main services are \cite{dNRW:Standardisierungskonzeptzur}
-
-\begin{itemize}
-    \item \textbf{Retrieval of a digital form}
-
-    There exist many administrative services and depending on the member state or commune, the required layout of the application can be different.
-Therefore, a system called federal information management (Föderales Informationsmanagement: FIM) is used to standardize administrative services.
-FIM consists of three categories of building blocks.
-
-    \textit{Service blocks} contain human readable descriptions about a administrative service.
-
-    \textit{Data field blocks} contain the standardized description of data fields required for the application of administrative services.
-
-    \textit{Process blocks} contain standardized descriptions about the process of an administrative service.
-
-    Relevant for the form-server are data field blocks. A data field block can contain one element of five categories.
-
-    \textit{Data fields} are the "smallest entity" of a data field block and describes one standardized piece of information.
-Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.
-
-    \textit{Data field groups} consist of multiple data fields and other data field groups, relating to a category of information. A data field group can for example be "person" or "company".
-
-    \textit{Rules} describe all kinds of logical conditions of and between data fields.
-This includes for example the automatic validation of the correctness of an entered value or the activation and deactivation of data fields depending on an entered value.
-
-    \textit{Code lists} are lists of predefined values the user can select. This can for example be a list of all countries.
-
-    \textit{Data field schemata} is the combination of entities from all previously described categories and describes the structure of a form.
-
-    The building blocks are centrally managed by federal republic, member states and communes.
-This simplifies the creation of for example a new form by reusing existing data schema blocks and adding additional required data fields to a new data field schema.
-
-    Each data field block can be uniquely identified through an ID.
-Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data filed block from the central storage.
-
-    \item \textbf{Initiation of application}
-
-    The from-server can be requested to initiate an application using a certain form based on a FIM ID of a data field schemata.
-Along with the request, an identification and authorisation of a user profile has to be passed.
-Additional personal information of the user profile can be passed for automated filling in of the form.
-
-    \item \textbf{Status update}
-
-    The form-server sends updates regarding the current status of the application.
-
-    \item \textbf{Automatic filling in of form}
-
-    If the form server was provided with personal information during the initiation request for an application, it can automatically fill in the form.
-
-    \item \textbf{Presentation of form}
-
-    The form server can host a website where it displays an interactive form. The user can access this website either through an URL or through a web component.
-
-    \item \textbf{Application interruption}
-
-    The application can be interrupted or aborted.
-Interruption may occur if the user stays inactive for a certain period of time while filling in the form.
-The user can also manually interrupt the editing process.
-If the application is interrupted, the form-server stores the unfinished application for a certain amount of time.
-The user can then access the application at a later time.
-
-    If the user decides to cancel editing the form, the application is deleted from the from-server.
-
-    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.
-
-    \item \textbf{Storage of application}
-    The form-server stores applications for a specified period of time if they were interrupted or submitted.
-
-    \item \textbf{Provisioning stored applications}
-
-    If the form server is provided an identification and authorisation of a user, it searches all stored applications which belong to the user and sends back a list of URLs, through which the user can access them.
-
-    \item \textbf{Deletion of stored application}
-
-    If the form server is provided an identification and authorisation of a user and an identification of an application, it can delete the stored application.
-
-    \item \textbf{Manually filling in data fields}
-
-    When the form is presented to the user, it can happen, that not all information could be automatically filled in. In this case, the form can be interactively filled in by the user.
-
-    \item \textbf{Uploading documents}
-
-    The user can add documents as attachments to an application. The documents can either be uploaded from the local machine or the data wallet of the user profile.
-
-    \item \textbf{Submission of application}
-
-    When the user submits the application by for example pressing a "submit" button, the form-server sends a status update. The finished application can now be transmitted to a requesting system.
-
-\end{itemize}
-
-\paragraph{User Profile}
-Each member state provides its own user profile for identity management. The main services are \cite{NRW:Umsetzung}:
-
-\begin{itemize}
-    \item \textbf{Identification and Authentification} \cite{dNRW:Anbindungsleitfaden}
-
-    The user profile can be used for identification by transmitting personal information like name and address after successfully authentification.
-Authentification is the verification of an authentication.
-Users can authenticate for the user profile for example through a username / password combination.
-
-    \item \textbf{Determination Trust Level} \cite{dNRW:Anbindungsleitfaden}
-
-    The trust level of a logged in user profile is determined while registration and usage.
-The user can register and login to the user profile using a username / password combination or the German ID card.
-The trust level "High" is only granted, if the user registered using the German ID card \textbf{AND} logs in using the German ID card.
-All other combinations of registration and login result in a "normal" trust level.
-
-    \item \textbf{Management Personal Information} \cite{dNRW:Anbindungsleitfaden}
-
-    Personal information of the user profile can be modified.
-This requires the user to authenticate.
-In case the user profile is connected with an online identity card, some attributes like name and age can not be changed.
-
-    \item \textbf{Provisioning Personal Information} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}
-
-    The user profile can be requested to send personal information to a specified URL. This requires the user to authenticate.
-
-\end{itemize}
-
-\paragraph{Institution}
-Institutions are the entities which eventually process the incoming applications and provide the users with solutions.
-They receive a digital application through the data-exchange platform and send back the result as a message through the inbox.
-
-\paragraph{Data-Exchange Platform}
-The data-exchange platform delivers applications from the administration portal to the correct administrative institution.
-
-\paragraph{Data Wallet}
-The data wallet is a sub-component of the user profile and enables the user to manage documents for his user profile. The main services are:
-
-\begin{itemize}
-
-    \item \textbf{Upload of document}
-
-    The user can upload a document from his local machine to the data wallet.
-
-    \item \textbf{Show documents}
-
-    The user can list all documents which are stored in the data wallet.
-
-    \item \textbf{Delete documents}
-
-    The user can delete documents from the data wallet.
-
-    \item \textbf{Attach documents to application}
-
-    The user can attach a copy of a document stored in his data wallet to an application on a from server.
-
-\end{itemize}
-
-\paragraph{Inbox}
-The inbox is a sub-component of the user profile and enables the user to send messages through his user profile. The main services are:
-
-\begin{itemize}
-
-    \item \textbf{Send a message}
-
-    The user can send a message to authorities. This can be for example an institution which processes an application.
-
-    \item \textbf{Receive a message}
-
-    The user can receive messages from authorities for example to update the status of an application.
-
-    \item \textbf{List messages}
-
-    The user can see the messages he received by logging in to his user profile on the administration portal.
-
-    \item \textbf{Notification through E-Mail}
-
-    The user can be notified of a new message through E-Mail.
-
-\end{itemize}
-
-\paragraph{Administration Portal}
-The administration portal provides the user access to various OZG services of other system components:
-
-\begin{itemize}
-
-    \item \textbf{Application for administrative service}
-    The administration portal provides access to services for creation and submission of applications for administration services.
-The portal hosts a web page for each administration service which enables the user to get information about the service and start the application process.
-After starting the process, the portal interacts with multiple system components to guide the user through the application.
-
-    \item \textbf{Management of user profile}
-    The administration portal provides access to the personal information stored in the user profile by interacting with the user profile system component.
-It enables the user to add, remove and update a set of attributes.
-
-    \item \textbf{Management of inbox}
-    The administration portal provides access to the inbox of the user profile. It enables the user to send new messages and display received messages.
-
-    \item \textbf{Management of data wallet}
-    The administration portal provides access to the data wallet of the user profile. It enables the user to upload and download documents and to attach copies of documents to applications.
-
-\end{itemize}
-
-The administration portal provides additional services:
-
-\begin{itemize}
-    \item \textbf{Determination of responsible institution}
-
-    Administrative services can be processed by a variety of administrative institutions, depending on the content of the application or the sender.
-It is the responsibility of the administration portal to determine which institution receives which application.
-
-    \item \textbf{Search and find Administrative Service}
-
-    The administration portal provides a search and find service which enables the user to find the web page of all administrative services which relate to the entered search term.
-
-\end{itemize}
-
-\subsubsection{Interfaces}
-In order to implement the basic use case, the components have to interact with each.
-The following diagram visualizes, which components interact.
-Each interaction is described afterwards.
-The arrows describe the main direction of information flow in an interaction.
-
-\begin{center}
-    \includegraphics[width=8cm]{Diagrams/Interaction Diagram.png}
-\end{center}
-
-\begin{enumerate}
-
-    \item The web browser of the user displays the web pages hosted by the administration portal.
-
-    \item The form-server can initiate the application if requested by the administration portal.
-The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID.
-In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata.
-In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.
-
-    \item The form server provides the user a web page which displays an interactive form.
-
-    \item The form server notifies the administration portal of changes in the status of applications.
-If the administration portal is notified of a submitted application, it requests the form server to transmit the application data.
-
-    \item The administration portal requests the user profile for identification and authentication to login a user on the web page of the portal.
-The portal also requests authorisation from the user profile to for example access certain personal information.
-
-    \item The administration portal enables the user to manage services of the user profile.
-It provides OSS tools for managing attributes stored in the user profile, to send new messages and to manage documents in the data wallet.
-
-    \item The administration platform submits application data to the data exchange platform for delivery to the responsible institution.
-
-    \item The data exchange platform notifies the administration portal of the delivery status of the application data.
-
-    \item The data exchange platform notifies the institution of a new application and enables it to download the corresponding data.
-
-    \item The institution can send messages to the inbox of a user profile to for example request additional documents.
-
-    \item The user can send messages to the institution which for example asked for additional documents.
-
-\end{enumerate}
-
-\subsubsection{Data Objects}
-This section describes what data each component processes.
-The property value describes a certain type of data.
-The source describes which component stores the value.
-This distinguishes the access of a property by reference and by copy.
-If the source of a property is another component, the property is accessed by reference.
-The description gives further detail on how the property is processed by the component.
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: Service Web Page} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Name & Web Page & FIM & Name of an administrative service \\
-    \hline
-    URL & Portal & Portal & The URL of the Web Page \\
-    \hline
-    Description & Web Page & FIM & Description of an administrative service \\
-    \hline
-    FIM-ID & Web Page & FIM & FIM-ID of a data field schemata which describes attributes required from the user when applying for the service \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: User} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Attributes & User Profile & User Profile & The portal can manage attributes of user profiles \\
-    \hline
-    JWT & Portal & User Profile & The portal can retrieve a JSON Web Token from the profile after successful authentication by a user \\
-    \hline
-    URL Form & Portal & Form Server & The portal stores the URL where the form server hosts the interactive form \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: Application} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    FMS-ID & Portal & Form Server & The portal receives the ID of applications from the form server \\
-    \hline
-    Status & Portal & Form Server & The portal receives status updates for each application \\
-    \hline
-    XML Form Data & Portal & Form Server & The portal can retrieve the data which was filled into a form \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Personal Information} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Attributes & User Profile & FIM & The list of attributes the user can fill in at his profile are based on FIM data fields managed in the FIM repository. \\
-    \hline
-    Attribute Values & User Profile & User & The user can manually add values to a list of predetermined attributes in his profile \\
-    \hline
-    Credentials & User Profile & User & The User Profile stores encrypted credentials of the user to authenticate him \\
-    \hline
-    User Profile ID & User Profile & User Profile & The User Profile creates and stores a unique ID for the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Authorisatiozation} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    JWT & Other Component & User Profile & The user profile can create and transfer JSON Web Tokens which authorise other components to access resources of the user profile \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Inbox} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Received Messages & User Profile & User & The user profile stores messages which were addressed to the user \\
-    \hline
-    Sent Messages & User Profile & User & The user profile stores messages which were sent by the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Data Wallet} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Documents & User Profile & User & The user profile stores documents which were uploaded by the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Form Server} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    FMS-ID & Form Server & Form Server & The form server creates a unique ID for each application \\
-    \hline
-    JWT & Form Server & User Profile & The form server uses a JSON Web Token to verify that the entity issuing the request is authorised \\
-    \hline
-    User Profile ID & Form Server & User Profile & The ID of the user who is associated to the application \\
-    \hline
-    FIM-ID & Form Server & FIM & The FIM ID of a data field schemata is used to determine how to construct the form \\
-    \hline
-    Form & Form Server & FIM & The list of attributes the user can fill in at the form are based on the FIM data field schemata.
-The form server maps the FIM data fields of the FIM data field schemata to attributes the form server understands \\
-    \hline
-    Status & Form Server & Form Server & The status describes which actions were performed on the application \\
-    \hline
-    Application Data & Form Server & User & The form server stores the data which the user filled in to the form as an XML file \\
-    \hline
-    Web Page & Form Server & Form Server & The form server hosts a web page with the interactive form  \\
-    \hline 
-    Web Page URL & Form Server & Form Server & The form server hosts the web page of the form at an individual URL \\
-    \hline 
-    \end{tabularx}
-\end{table}
-
-\subsubsection{Sequence Diagram}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=17cm]{Diagrams/Basic Use Case Sequence Diagram.png}
-\end{figure}
+\subfile{sections/5-online_access_law}
 
@@
 
-\subsection{User Perspective}
+\subfile{sections/6-requirement_analysis}
 
-\begin{itemize}
-    \item The user wants to manage his personal information in one place
-    \begin{itemize}
-        \item The user wants to CRUD attributes
-        \item The user wants SPs to CRUD his attributes
-        \item The user wants a user friendly interface where he can CRUD his attributes
-        \item In case the user cannot understand an attribute or its possible values, he needs OSS tools which enables him to enter the correct value
-        \item The user wants to enter personal information only once (=> SPs should reuse existing attributes)
-        \item The user wants a new or modified attributes to be instantly used everywhere
-        \item The user wants a deleted attribute to be instantly deleted everywhere
-        \item The user wants to have a list of often used attributes, in order to prefill them
-    \end{itemize}
-    \item The user wants to manage authentication in one place
-    \begin{itemize}
-        \item The user does not want to authenticate
-        \item The user wants that only he has access to the identity
-    \end{itemize}
-    \item The user wants to manage authorisation in one place
-    \begin{itemize}
-        \item The user wants to manage who can perform which actions in his name (f.e CRUD attributes, place order, cancel subscription)
-        \item The user wants an authorisation to only be granted if he manually approves
-        \item The user wants an authorisation to be associated with a single entity, a reason, which actions can be performed and duration of the authorisation
-        \item The user wants to communicate with the authorised entity
-        \item The user wants to have much information about the authorised entity
-        \item The user wants to be able to revoke an authorisation
-        \item The user wants to save the history of authorisations
-    \end{itemize}
-    \item The user wants to use all OSS tools in one place
-    \begin{itemize}
-        \item Communication through inbox
-        \item Subscribe for a service of an SP
-        \item Place order in a shop of an SP
-        \item ...
-    \end{itemize}
-    \item The user wants
+\section{IMP System Proposal}
 
-\end{itemize}
+\subfile{sections/7-imp_system_proposal}
 
-\subsection{Service Provider Perspective}
+\chapter{Minimal Integration Architecture}
 
-\begin{itemize}
-    \item SPs want to manage personal information of users
-    \begin{itemize}
-        \item SPs want to CRUD attributes of the user
-        \item In case modification of an attribute has strong implications on the operation of a system, the modification of an attribute needs to be limited
-        \item SPs want to access personal information already collected by other SPs
-        \item SPs want 
-    \end{itemize}
-    \item identification
-    \item authentication
-    \item authorisation
-    \item 
-\end{itemize}
+The goal of the integration architecture is to make as many functionalities required for the basic OZG use case available through the IMP client as possible.
+As described in chapter 2.3, the steps of the basic OZG use case are:
+\begin{enumerate}
+    \item{Create User Profile}
+    \item{Login to User Profile}
+    \item{Selection of Administrative Service}
+    \item{Filling in Application}
+    \item{Submission of Application}
+    \item{Reception of Application by Administration Portal}
+    \item{Submission of Application to Data-Exchange Platform}
+    \item{Management of Applications}
+    \item{Communication}
+\end{enumerate}
 
-\subsection{OZG Perspective}
+To enable service providers a quick introduction of IMP systems into their system architecture, this integration architecture describes a minimally invasive integration.
+After deployment of this integration architecture, all OZG services are still usable as before but can be enhanced by IMP solutions.
+For this integration to be minimally invasive, only one connector exists and integrates only with the administration portal.
+No other OZG system component is modified or directly accessed.
 
-\section{IMP Solution Proposal}
-
-This section describes a solution for an IMP system considering the previously mentioned requirements.
-
-\subsection{Components}
-
-\subsubsection{IMP Client}
-
-The IMP client is a smartphone application which enables the user to manage his IMP identity. The client provides the following functionalities:
-\begin{itemize}
-    \item Create an identity
-    \item Manage attributes of the identity
-    \item Manage documents
-    \item Send and receive messages
-    \item Send and receive relationship requests
-    \item Send and receive requests
-\end{itemize}
-
-\subsubsection{IMP Server}
-The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
-\begin{itemize}
-    \item Create and store relationship template
-    \item Create and store request template
-    \item Deliver relationship requests
-    \item Deliver requests
-    \item Deliver messages
-\end{itemize}
-
-\subsection{Functionalities}
-
-\subsubsection{Relationships}
-
-\subsubsection{Requests}
-
-\subsection{Data Objects}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Form Server} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    \hline
-    \end{tabularx}
-\end{table}
-
-\chapter{IMP Integration Architecture}
-
-\section{Requirement Analysis}
-
-\subsection{Integration Challenges}
-
-The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems.
-The origin of the challenges is the interoperability of the IMP identity with multiple SPs.
-It is the purpose of the integration architecture to solve as many of these challenges as possible.
-
-\subsection{Basic Use Case}
-
-\subsection{Extensions}
-
-\section{Integration Proposal}
-
-\subsection{IMP Connector}
-
-\subsection{Messaging}
-
-\section{Integration}
-
-Multiple integration scenarios are presented with increasing complexity and functionality.
-
-\subsection{Scenario 1}
+The goal of the integration is to enhance each step of the basic OZG use case through integration with IMP solutions.
+Therefore in the overview section, for each step, possible integration's of OZG systems are evaluated.
+The following sections contain more detailed descriptions of the selected integration strategies.
 
 \begin{figure}[h]
-\caption{Overview Integration Scenario 1}
     \centering
-    \includegraphics[scale=0.2]{Diagrams/Integration 1/Overview.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
 \end{figure}
 
-In this scenario, the IMP system integrates only with the administration portal to extend the usage of identity related functionalities through the IMP client.
-The integration architecture contains one connector which integrates with the administration portal and communicates with IMP server and IMP client.
+\section{IMP Solution Integration}
 
-Through the integration, the user will be able to connect his OZG user profile with an IMP identity.
-As a result of this connection, the personal information of the user profile will be synchronized with the attributes of the IMP identity.
-The user will only be able to change personal information of his user profile through the IMP client.
-If the user has connected an IMP identity, starting an application will require authorization through the IMP client.
-However, starting and filling in the application will still be done through the web page of the administration portal and form server.
-After the user submitted the application through the form server, the user will be able to manage active applications through the IMP client.
-The user will be able to send and receive messages of the user profile inbox through the inbox of the IMP client and combine the data wallet of the IMP client and user profile.
+\subfile{sections/8-imp_solution_integration}
 
-The integration provides an improved experience of the basic OZG use case through the IMP systems by making existing functionalities of the administration portal available through the IMP client.
-Especially the fact that the user wont have to manage the OZG user profile separately is an advantage for the user.
-Communicating with governmental institutions through the smartphone instead of a web page is also more convenient.
+\section{Technological Integration}
 
-This integration scenario can be a first step by service providers to adopt an IMP system.
+\subfile{sections/9-technological_integration}
 
-\paragraph{Linking IMP ID and OZG ID}
+\chapter{Advanced Integration Architecture}
 
-Before the IMP client can access services of the administration portal, the user has to be able to connect his IMP identity with the user profile.
-This is necessary for the integration architecture to enable bidirectional communication between OZG systems and IMP client regarding a user.
-
-The administration portal hosts an additional web page where a logged in user can connect one IMP identity to his user profile.
-The IMP identity can be connected with the user profile through an IMP relationship between the administration portal and the IMP identity.
-The relationship includes the ID of the user profile as metadata in order for the relationship to be associated to a user profile.
-For a relationship to be established, a relationship template has to be created.
-This template is created by the IMP connector and stored on the IMP server.
-The template can be referenced through a template ID, created by the IMP server.
-The relationship template contains information about the administration portal and its connector, the reason for the relationship, attributes the IMP client is required to share as part of the relationship and the ID of the user profile.
-Based on the template ID, the connector creates a QR code which gets displayed on the web page for any IMP client to scan, retrieve the relationship template and issue a relationship request.
-The request contains information about the IMP identity and values for the requested attributes.
-The user gets notified of the connection request through an E-Mail which includes an URL.
-Visiting this URL will confirm the relationship request.
-
-After confirmation, the IMP identity is connected with the administration portal through an IMP relationship which contains the ID of a user profile.
-The administration portal stores the IMP identity ID, the relationship ID and the user profile ID as an entry in a database.
-
-The relationship can be cancelled through the IMP client or through the web page of the administration portal.
+The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client.
+Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.
 
 \begin{figure}[h]
-\caption{Overview Connection}
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Overview.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 2/Overview.png}
 \end{figure}
 
-The web server of the administration portal hosts an additional web page where a user can connect an IMP identity with his user profile.
-When a user tries to visit the web page, the browser sends a GET request to the server and attaches a session ID as cookie.
-Based on the session ID, the web server can determine the user ID and the authentication state of the session.
-If the user is not authenticated, the server responds with a redirection to the login page.
-If the user is authenticated, the web server requests a QR code from the messaging system for connecting an IMP identity to the user ID of the session.
-
-A messaging gateway is integrated into the run-time of the web server.
-It provides an API for the server code to send and receive messages while hiding most complexities of messaging.
-After the authentication of the session is validated, the web server calls the API of the gateway to request the QR code for connecting an IMP identity to the user ID which corresponds to the session.
-The messaging gateway places a message on the "Connection QR Request" channel.
-The message contains the ID of the user (UID).
-Based on the request-reply pattern, the messaging gateway will receive a reply through the "Connection QR Reply" channel.
-In order for the gateway to match replies to requests, request and reply message contain a request ID (RID) with the same value.
-
-As the name suggests, the relationship template is the basis for creating a relationship request.
-One template can therefore be used multiple times.
-Therefore, in order to save resources, QR codes for connecting IMP identities and user profiles should be reused.
-However, it still has to be possible to use new relationship templates, as the required content of future relationships might change.
-It could for example happen, that additional attributes are required to be shared by the IMP identity or that a user agreement attached to the relationship metadata changed.
-
-The messaging architecture contains a QR code management system which is responsible for storing all QR codes and the corresponding user IDs.
-Messages sent to the "Connection QR Request" channel are consumed by a content-based router who checks if the QR code database contains an entry for the UID of the message.
-If this is the case, the message is sent through a content enricher and a content filter where the QR code is added, the UID is removed and the message is placed on the "Connection QR Reply" channel.
-Content-based router and content enricher have access to the QR code database but do not necessarily communicate through messaging.
-
-If the content-based router does not find a QR code for the UID in the database, the message is sent to a different content enricher which adds a configuration to the message.
-This configuration contains information for the connector on how to create the relationship template.
-The message is then sent to the "Create Relationship Template" channel, where the connector is able to read it.
-The connector uses the configuration stored in the message to create the relationship template and store it on the IMP server.
-The connector exports the corresponding template ID as a QR code and publishes a message containing the user ID, the request ID and the QR code on the "Publish New Relationship QR" channel.
-Any application can subscribe to this channel and process the contained messages.
-In this case, two content filters are subscribed.
-One of the content filters was already described earlier where a QR code for the user ID was already stored in the database.
-This content filter does the same as described previously, it removes the user ID from the message and sends it to the "Connection QR Reply" channel.
-The other content filter prepares the message to be added to the QR code database by removing the Response ID.
-Through a messaging gateway, the database is able to receive the message and store the QR code.
-
-The messages on the "Connection QR Reply" channel are read by the messaging gateway of the web server and received by the code of the server through a return statement of an API function call.
-The QR code is now added to the web page and sent back to the web browser of the user.
-
-\begin{figure}[h]
-\caption{Overview Connection Messaging}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging Overview.png}
-\end{figure}
-
-The newly created web page uses messages to communicate with the administration portal using a request-reply pattern.
-The request-reply pattern enables the requestor - the web page in this case - to send a message to the replier - the connector in this case - and receive an answer which correlates to the request.
-The purpose of the communication in this case is for the web page to receive the QR code containing the relationship template.
-
-\begin{figure}[h]
-\caption{Web Page Messaging Adapter}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 1.png}
-\end{figure}
-
-In order for the web page to send and receive messages, it includes a messaging gateway.
-As the web page is added as part of the integration architecture, the gateway can be included in the web page.
-It provides domain specific functions to the web page and hides much of the complexity of interacting with the messaging system.
-In combination with the request-reply pattern, the local functions provided by the gateway can be used synchronously and asynchronously.
-The web page requires the user to be logged in to his user profile and therefore expects the web browser to contain a JSON Web Token.
-The web page uses the messaging gateway to send a message, requesting a QR code for connecting an IMP identity.
-The message consists of a JSON Web Token and is placed in a datatype channel called "QR Request Channel".
-
-\begin{figure}[h]
-\caption{Request Reply Smart Proxy}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 2.png}
-\end{figure}
-
-In order to implement a request-reply pattern, a stateful smart proxy is used.
-The web page sends a message which contains a JSON Web Token in the body to the "QR Request" channel.
-Besides the body, the message contains a message ID in the header which uniquely identifies it.
-The message also contains a return address which specifies a channel to which the reply should be sent.
-The messaging gateway specifies a reply channel unique to the web browser instance.
-The temporary channel is deleted eventually.
-The smart proxy stores message ID and reply channel in order to correlate replies in the "QR Reply Service" channel with the request and send it to the specified reply channel.
-If eventually, the integration architecture is ready to send a QR code as reply, the corresponding message can be put on the "QR Reply Service" channel, where, based on the message ID, the smart proxy can correlate it to the request message and send the reply to the corresponding reply channel.
-The messaging gateway included in the web browser can retrieve the reply from its reply channel in multiple ways.
-One example would be iterative polling.
-
-\begin{figure}[h]
-\caption{Filtering and Routing Request}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 3.png}
-\end{figure}
-
-The message from the "QR Request Channel" are processed by a filter.
-All messages which are invalid through for example an expired JSON Web Token are deleted.
-Valid messages are then routed by a stateful content-based router.
-The router keeps track from which users a message was received.
-In case a message was received previously, the current message is routed to the "Existing Request" channel.
-Otherwise the message is routed to the "New Request Template" channel.
-
-\begin{figure}[h]
-\caption{Retrieving Existing QR Code}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 4.png}
-\end{figure}
-
-The messages from the "Existing Request Template" channel are consumed by a QR code management system, which stores all valid QR codes in a database.
-The system adds the QR code corresponding to the user to the message and sends it to the "QR Reply Service" channel, where it is delivered to the web page by the smart proxy.
-
-\begin{figure}[h]
-\caption{Requesting New Template}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 5.png}
-\end{figure}
-
-Messages on the "New Relationship Template" channel are modified by a content enricher to contain parameters which are required by the connector to create a relationship template.
-The message is then send to the connector using a request-reply pattern.
-
-\begin{figure}[h]
-\caption{Creating New Template}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 6.png}
-\end{figure}
-
-As there is only one possible channel to receive the reply from the connector, no smart proxy is required for this request-reply pattern.
-The message is send to the "Relationship Template Request" channel, trough which the portal connector receives it.
-As the connector is designed with integration in mind, he is capable of receiving and sending messages through an included messaging gateway.
-The connector also contains a sophisticated process manager for implementing the provided IMP functionalities through interaction with an IMP server.
-In this case, the process manager interacts with the IMP server to create a relationship template, store it on the IMP server, retrieve a template ID and export it as a QR code.
-Through a content enricher, the QR code is attached to the message and placed on the "Relationship Template Reply" channel.
-
-\begin{figure}[h]
-\caption{Storing New Template}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Connection/Messaging 7.png}
-\end{figure}
-
-The message from the "Relationship Template Reply" channel is consumed by the QR code management system.
-The system stores the new QR code for the user and sends the message unchanged to the "QR Reply Service" channel, where the smart proxy delivers it to the web page.
-
-\paragraph{Authorisation}
-
-If the user successfully authenticated for a user profile, the administration portal receives a JSON Web Token which enables it to perform actions for the user.
-The user might want to manage which actions an IMP client is authorised to perform without having to approve each of them trough the website of the portal.
-
-\begin{center}
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Authorisation/Overview.png}
-\end{center}
-
-After successful connection of an IMP identity with the user profile through the introduced web page, the website can display a user interface for specifying which actions the IMP identity is authorized for.
-After the user finishes, the web page submits the configuration to the administration portal.
-The portal then creates a suitable authorisation request to the user profile which requires the token to include the relationship ID associated to the user profile.
-After successful authentication by the user, the user profile transmits a JSON Web Token to the portal.
-
-It contains the user profile ID, the relationship ID and information about the authorisations that are granted when attaching this tokens to a request.
-It also includes a signature with the private key of the user profile component.
-This enables components to verify if the token is valid by transmitting it to the user profile component.
-
-The JSON Web Token is stored as attribute of the IMP identity.
-Upon receiving the token form the user profile component, the administration portal initiates two requests through the connector to the IMP identity of the relation corresponding to the relation ID.
-The first requests to add the token as attribute.
-The second requests to share the attribute.
-
-If the user approves both requests, every time the connector requests the portal to perform an action coming from a relationship, the portal can use the JSON Web Token shared through this relation.
-
-\paragraph{Personal Information}
-
-One of the goals of an IMP system is to enable the user to only manage his identity in one place while all other service providers rely on the attributes of the identity.
-As in this scenario however, the OZG system does not rely on attributes of the IMP system but enables it to manage personal information stored in the user profile.
-Some synchronisation mechanism can therefore operate.
-
-\begin{center}
-    \includegraphics[scale=0.3]{Diagrams/Integration 1/Personal Information/Overview.png}
-\end{center}
-
-While configuring the authorisation of the IMP identity on the previously described website, the user can determine if the IMP identity is allowed to manage personal information stored in the user profile.
-If the user approves, the JSON web Token stored as attribute of the identity is authorized to update, delete and read attributes of the user profile.
-As the user profile determines which attributes exist, no attributes can be added.
-
-If an attribute of an identity changes, the IMP client notifies all relationships.
-When the connector receives this notification, he reads all shared attributes and requests the administration portal to update the same attributes in the user profile.
-As the naming and meaning of attributes can differentiate between IMP systems and OZG systems, the attributes have to be mapped to each other.
-A simple solution would be a table, created by an administrator, which maps each attribute from the IMP system to an attribute of the OZG system.
-
-\paragraph{Inbox}
-
-Both IMP Client and the administration portal provide an inbox functionality.
-If an IMP identity has established a relationship with the administration portal, they can exchange messages through the connector as part of this relationship.
-
-In order to notify the user of a new message to the user profile, the administration portal can send the same message through the relationship associated with this user.
-The user can, however, only send messages to the administration portal and not to for example institutions.
-
-\paragraph{Data Wallet}
-
-\subsubsection{Messaging Architecture}
-
-\subsection{Integration 2}
-
-Option for user to use IMP identity INSTEAD of user profile
-
-\section{Extension: Inbox}
-
-\section{Extension: Collaboration}
+\section{IMP Solution Integration}
 
@@
 
-\chapter{Tables}
-
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            JSON Web Token & The portal received this JWT as a result of the login process with the user profile component.
-This token enables the form-server to verify the authentication of the user.
-& User Profile \\
-
-            \hline
-
-            User Profile ID & This ID is a unique identifier of a user profile and is used by the form server to associate the initiated application with a user profile. & User Profile \\
-
-            \hline
-
-            Personal Data & If the user approves, the administration portal submits personal data, the form-server can use to automatically fill in the form. & User Profile \\
-
-            \hline
-
-            FIM Schema ID & The administration portal stores a hard coded FIM-ID for every administration service.
-This FIM-ID corresponds to the correct data field schemata, the form-server can display & Hard Coded in Portal \\
-
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Output} \\
-            \hline
-
-            Status & The form-server answers with the status of the initiated application. & From Server \\
-
-            \hline
-
-            FMS-ID & While initializing the application, the form-server creates an ID, which uniquely identifies the application.
-This FMS-ID is sent back to the portal so that it can request information about the application at a later time.
-& Form Server \\
-
-            \hline
-            \end{tabularx}
-            \caption{Interface of the form-server for initialization of an application}
-            \label{table:interface_form_initialization}
-        \end{table}
-
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal.
-Each status update includes this ID in order for the portal to associate the update with an application.
-& Form Server \\
-
-            \hline
-
-            Status & The status provides information about interactions of the user or the form-server with the application. The possible states are:
-
-            \begin{itemize}
-                \item \textbf{null}: This application has this status right after initialisation.
-                \item \textbf{submitted}: The application has this status after the user triggered the submit functionality of the form-server.
-Usually the form is now locked for further modification by the user.
-                \item \textbf{filed}: The form-server submitted the application to the portal but did not yet receive a confirmation.
-                \item \textbf{confirmed}: The form-server received a confirmation from the portal.
-                \item \textbf{deleted}: The form-server deleted the application.
-            \end{itemize}
-
-            & Form Server \\
-            \hline
-            \end{tabularx}
-            \caption{Interface of the administration portal for receiving status updates by the form-server}
-            \label{table:interface_status}
-        \end{table}
-
-        \begin{table}[!h]
-            \begin{tabularx}{\textwidth}{|l|C|l|}
-            \hline
-            Property & Description & Data Source \\
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Input} \\
-            \hline
-
-            FMS-ID & The FMS-ID was created by the form-server during the initialisation of the application and sent to the administration portal along with the status update of the submission.
-The administration portal sends this ID in order for the form-server to know which application data to transfer.
-& Form Server \\
-
-            \hline
-            \rowcolor{LightCyan}
-            \multicolumn{3}{|l|}{Output} \\
-            \hline
-
-            FMS-ID & The FMS-ID is transmitted in order for the portal to associate the response with an application. & Form Server \\
-
-            \hline
-
-            JSON Web Token & The JWT which was initially sent from the portal to the form-server is now transmitted back again, in order for the portal to verify, that the form-server is authorized to submit an application for the user.
-& User Profile \\
-
-            \hline
-
-            User Profile ID & The user profile ID was initially transmitted to the form-server by the portal and is now transmitted back in order for the portal to associate the application with a user profile.
-& User Profile \\
-
-            \hline
-
-            XML File & The XML file contains the personal data retrieved through the form. & Form Server \\
-
-            \hline
-            \end{tabularx}
-            \caption{Interface of the form-server for requesting application data by the administration portal.}
-            \label{table:interface_application_data}
-        \end{table}
-
 \printbibliography

### 2021-01-28 sections/1-context.tex
split sections into files

Since invention of the World Wide Web, the number of its users increased rapidly. Today, more than 90 percent of the German population use the internet \cite{Onlinestudie}. Enterprises and organizations, recognised this potential to provide their services to a large number of people as Service Providers (SP). A frequently used method of SPs is "online self-service" (OSS). Specialized software tools enable customers to use services through the internet without direct human interaction.

Many tools require identification of a user in case interactions or initiated business processes have to be associated with him. A system for management of identities of users therefore is part of numerous system architectures. Service Providers usually enable users to manage their partial identities using online self-service through so called User Profiles. Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP

The result is variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
\begin{itemize}
    \item Multiple SPs collect, use and share parts of identities which leads to distributed and fragmented identities.
    \item As a result of the distributed identities, risk of data breaches increases.
    \item Managing multiple use profiles is very inconvenient for users.
    \item It is often unclear who stores which data and for what purpose.
    \item SPs have an incentive to collect and share more user data than they need.
\end{itemize}

An improved model for identity management is necessary. In recent years, multiple new models have been invented. One model called Social Login became popular. It enables customers to create User Profiles for SPs through existing User Profile of Social Networks like Facebook. This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes. Users can therefore manage identity related information through their Social Profile which is accessed by the SP.

This approach, however, still leaves the requirement of User Profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user. SPs also might require additional online self-service tools the social network does not provide.

The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles. The system itself is provided and hosted by a SP for consumption by other SPs. To replace existing User Profiles, the IMP can not only rely on systems for registration, authentication, authorisation and provisioning. Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.

In order for an SP to use identities and services of an IMP, an integration into the system architecture of the SP has to take place. Due to the complex nature of system architectures and identity management, this is a difficult task.

A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG). It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles. The current plan is to make the profiles only available for usage in context of the OZG. From a user perspective, this would be yet another partial identity and user profile to manage.

### 2021-01-28 sections/10-imp_solution_integration.tex
split sections into files

The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal. This is not necessary any more, as user profiles are replaced by IMP identities. The user will only have to create an IMP identity.

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal. As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services. The IMP client does not require authentication, as it is installed on the smart phone of the user. The user can secure his smartphone through for example biometric authentication.

The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.

The fourth step of the basic OZG use case is to fill in the application. The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.

The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more. Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.

For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template. The connector responds to the institution with the template IDs.

In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address. After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.

If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it. The relationship template contains a description of the selected administrative service as reason for the relationship. The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application. This replaces the functionalities of the form server.

The fifth step of the basic OZG use case is to submit the application. After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes. The institution can accept the request and start processing the application. The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.

The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.

The eighth step of the basic OZG use case is the management of active applications. As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution. Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.

The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications. As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.

### 2021-01-28 sections/2-objective.tex
split sections into files

Based on the prominent example of the OZG, the bachelor thesis will construct a message based integration architecture which enables system architectures of service providers with existing user profiles to make their services usable with an Identity Management Provider. In order to make the integration architecture suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management. The integration architecture is however not only applicable in cases relevant for OZG but also for other Service Providers with similar requirements. As requirements of SPs are not guaranteed to be similar to those of the OZG, the integration architecture is built to be expendable.

The \textbf{integration architecture} for the OZG enables \textbf{IMP functionalities} to be usable for selected \textbf{OZG scenarios} by integrating a \textbf{connector} in the \textbf{system architecture} of a member state.

\begin{itemize}
    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example the application for an administrative service or the communication with a governmental institution.
    \item The system architecture is based on documentation about architecture plans of member states.
    \item The functionalities of the IMP are based on a requirements analysis of OZG scenarios and additional research.
    \item The connector is defined based on functionalities the integration architecture requires from the IMP.
    \item The integration architecture is the main scientific contribution of this bachelor thesis. It is based on messaging patterns in order to utilize a combination of established and tested messaging solutions. In order to save investments it also reuses as many system components as possible and modifies as few system components as necessary.
\end{itemize}

The integration architecture ...

### 2021-01-28 sections/3-structure_of_work.tex
split sections into files

The "Fundamentals" chapter explains terminology and basic concepts.

In the following chapter called "Identity Management System" the thesis analyzes requirements for identity management through the perspective of the user and through the perspective of service providers for the OZG. It is presented, how an identity management provider could solve current identity management problems and which challenges for an integration exist.

The chapter "Integration Proposal" first documents a possible IMP system and connector, based on the requirement analysis of the previous chapter. It then presents the integration architecture with iteratively increasing requirements through textual description, multiple flow diagrams and messaging architectures.

A "Solution Evaluation" analyzes benefits and problems of the proposed solution.

The "Outlook" will conclude the thesis by presenting possibilities for advanced integration architectures.

### 2021-01-28 sections/4-terminology.tex
split sections into files

\paragraph{Service Provider}
Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.

\paragraph{Online Self-Service}
Online self-service (OSS) describes a method used by Service Providers to make their services available to the user. The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way. The user is usually supported by a variety of software solutions.

\paragraph{Self-Service Tools}
Self-service tools are software solutions for customers to enable a online self-service experience. Depending on the use case, the tools can be transactional or informing. Informing tools help users to retrieve relevant information, often replacing human customer support. Transactional tools help users to interact with services in a persistent way to for example save personal data or trigger business processes.

Information tools can be for example so called "WiKi" pages or search fields which assist the user in his process of finding information. Transactional tools can be for example online forms which assist the user in his process of triggering an order placement business process.

In contrast to information tools, transactional tools often require identification of users in order to associate them with changes they made to the system: If a user triggers the business process of ordering a product, the SP requires identification of the user.

\paragraph{Digital Identity}
The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information. Each piece of personal information is an attribute. Attributes can be identifiers which are able uniquely identify an entity. It is also possible to use an aggregation of attributes as identifier.

Identifiers which are commonly used by SPs are the phone number and E-Mail address. Attributes are for example nicknames, hobbies, interests or education. The full name of a person is often not sufficient unique identification, the aggregation of name, age and home address can therefore be used as identifier.

\paragraph{Partial Digital Identity}
A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.

\paragraph{Identity Management}
Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities. The possible utilization of identities depends on the system for management of identities. It could be for example authorization for a service or communication through an inbox.

\paragraph{Identity Management System}
Identity management systems are solutions which enable SPs and customers to manage identities or partial identities.
They usually provide the following functionalities an properties:
\begin{itemize}
    \item 
\end{itemize}

\paragraph{User Profile}
User profiles are one method for identity management. They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.

\section{Identity Management Provisioning (IMP)}
Identity management provisioning (IMP) is a method for identity management which is characterized by an identity management provider hosting an identity management system for "non-partial" identities. The identity management system provides one-stop online self-service for users and manages the storage of identities. SPs are provided access to the identities of the identity management system.

The following are functionalities of an IMP system in addition to those of conventional identity management systems:

\paragraph{Attribute Management}
It is common for identity management systems to enable users to manage a predetermined set of attributes. IMP systems however do not just manage partial identities and therefore enable users to manage any possible attribute of their identity. Users therefore can add, remove and modify any attribute.

As often, attributes of a digital identity are defined by service providers, they are also able to create new attributes or delete and modify existing ones, if approved by the user.

\paragraph{Online Self-Service}
Many attributes, especially those created by SPs, do not make sense to the user without context and my be heavily dependant on systems of a SP. Therefore, the IMP provides solutions for online self-service which supports the management of attributes.

\paragraph{Integration}
Service providers which use IMP systems as solution for identity management require access to its services and have to make their existing systems work with them. The IMP solution therefore provides interfaces which enable the SP to access services. As it is in the best interest of the IMP solution to integrate SPs, advanced integration methods reducing the integration effort for SPs can be provided.

### 2021-01-28 sections/5-online_access_law.tex
split sections into files

In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
\begin{enumerate}
    \item \textbf{Digital availability of administrative services} \\
    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.  As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
    Federal republic, each member state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}. 
    \item \textbf{Interoperable user profiles for accessing administrative services} \\
    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.
\end{enumerate}

Execution of the OZG can be separated into two projects:

\paragraph{Digitalization}
Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions. The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:

A digitized administrative service can be accessed by a user through a website. The website is hosted either by the federal republic or a member state and is called "Administration Portal". Access is usually provided through an application form. The administrative service can be managed through a user profile which is provided by the federal republic or the member state. Management of an administrative service usually includes starting the service by sending in a form, communicating with responsible institutions through the inbox of the profile and receiving a result. The user profile can also enable users to upload documents to a data wallet and to save personal information for automatically filling in forms.

Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal. In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and yet other by the communes \cite{BMI:Onlinezugangsgesetz}.

\paragraph{Networking}
The networking focuses on connecting governmental systems to make all digitized administrative services available for every user. This includes most importantly the connection of administration portals to a portal network through an online gateway and the interoperability of user profiles.

In order to save investments a method called "one for all" is used when hosting administrative services. One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood". As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal. Interoperable user profiles enable usage of each profile for management of administrative services on all portals.

\subsection{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services.

The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:

\paragraph{1. Create User Profile}
The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.

\paragraph{2. Login to User Profile}
Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal. The user has to finish authentication steps, which can consist for example of a username and password. Depending on the authentication method, a trust level of the current session is determined. With approval from the user, personal information from his profile is provided towards the form-server.

\paragraph{3. Selection of Administrative Service}
The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

\paragraph{4. Filling in Application}
Personal information from the user profile is used by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

\paragraph{5. Submission of Application}
The user again authenticates for his user profile and authorises the form-server to submit the application. The form-server saves the application until he is notified to delete it. The form-server submits the application to the administration portal which hosts the administrative service.

\paragraph{6. Reception of Application by Administration Portal}
The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.

\paragraph{7. Submission of Application to Data-Exchange Platform}
The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.

\paragraph{8. Management of Applications}
The administration portal stores active applications and enables the user to manage them.

\paragraph{9. Communication}
As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.  Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.

\subsection{System Architecture}
This subsection describes the system architecture of a member state relevant for the execution the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen. Systems, which are responsible for coordination of OZG execution between member states and the federal republic are not the focus.

\subsubsection{System Components}
The system architecture consists of the following system components. Each component consists of a list of services it provides either to the user or to other components. Components are defined based on strongly connected categories of services \cite{NRW:Umsetzung}:

\begin{figure}[h]
\caption{Overview IMP System}
    \centering
    \includegraphics[scale=0.25]{Diagrams/OZG System Overview.png}
\end{figure}

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components. The most important components, the service facade provides an interface for are:

\begin{itemize}
    \item \textbf{Responsibility Finder}

    This service component is used to find administrative institutions which are responsible for an application. Depending on the type of application and on the home address of the user, different institutions might be responsible.

    \item \textbf{Process Management}

    This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.

    \item \textbf{Search}

    This service component creates a list of URLs of administrative services relevant for a specified search term. This enables the portal to provide a search functionality of administrative services for the user.

    \item \textbf{User Profile Management}

    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and sent messages to an institution.

    \item \textbf{Application Management}

    This service component manages applications issued through the administration portal through communication with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track about the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

\end{itemize}

\paragraph{Form-Server}
The from-server provides digital forms associated to administrative services. They can be accessed by a user profile through online self-service and submitted as applications to administrative institutions. The main services are \cite{dNRW:Standardisierungskonzeptzur}

\begin{itemize}
    \item \textbf{Retrieval of a digital form}

    There exist many administrative services and depending on the member state or commune, the required layout of the application can be different. Therefore, a system called federal information management (Föderales Informationsmanagement: FIM) is used to standardize administrative services. FIM consists of three categories of building blocks.

    \textit{Service blocks} contain human readable descriptions about a administrative service.

    \textit{Data field blocks} contain the standardized description of data fields required for the application of administrative services.

    \textit{Process blocks} contain standardized descriptions about the process of an administrative service.

    Relevant for the form-server are data field blocks. A data field block can contain one element of five categories.

    \textit{Data fields} are the "smallest entity" of a data field block and describes one standardized piece of information. Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.

    \textit{Data field groups} consist of multiple data fields and other data field groups, relating to a category of information. A data field group can for example be "person" or "company".

    \textit{Rules} describe all kinds of logical conditions of and between data fields. This includes for example the automatic validation of the correctness of an entered value or the activation and deactivation of data fields depending on an entered value.

    \textit{Code lists} are lists of predefined values the user can select. This can for example be a list of all countries.

    \textit{Data field schemata} is the combination of entities from all previously described categories and describes the structure of a form.

    The building blocks are centrally managed by federal republic, member states and communes. This simplifies the creation of for example a new form by reusing existing data schema blocks and adding additional required data fields to a new data field schema.

    Each data field block can be uniquely identified through an ID. Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data filed block from the central storage.

    \item \textbf{Initiation of application}

    The from-server can be requested to initiate an application using a certain form based on a FIM ID of a data field schemata. Along with the request, an identification and authorisation of a user profile has to be passed. Additional personal information of the user profile can be passed for automated filling in of the form.

    \item \textbf{Status update}

    The form-server sends updates regarding the current status of the application.

    \item \textbf{Automatic filling in of form}

    If the form server was provided with personal information during the initiation request for an application, it can automatically fill in the form.

    \item \textbf{Presentation of form}

    The form server can host a website where it displays an interactive form. The user can access this website either through an URL or through a web component.

    \item \textbf{Application interruption}

    The application can be interrupted or aborted. Interruption may occur if the user stays inactive for a certain period of time while filling in the form. The user can also manually interrupt the editing process. If the application is interrupted, the form-server stores the unfinished application for a certain amount of time. The user can then access the application at a later time.

    If the user decides to cancel editing the form, the application is deleted from the from-server.

    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.

    \item \textbf{Storage of application}
    The form-server stores applications for a specified period of time if they were interrupted or submitted.

    \item \textbf{Provisioning stored applications}

    If the form server is provided an identification and authorisation of a user, it searches all stored applications which belong to the user and sends back a list of URLs, through which the user can access them.

    \item \textbf{Deletion of stored application}

    If the form server is provided an identification and authorisation of a user and an identification of an application, it can delete the stored application.

    \item \textbf{Manually filling in data fields}

    When the form is presented to the user, it can happen, that not all information could be automatically filled in. In this case, the form can be interactively filled in by the user.

    \item \textbf{Uploading documents}

    The user can add documents as attachments to an application. The documents can either be uploaded from the local machine or the data wallet of the user profile.

    \item \textbf{Submission of application}

    When the user submits the application by for example pressing a "submit" button, the form-server sends a status update. The finished application can now be transmitted to a requesting system.

\end{itemize}

\paragraph{User Profile}
Each member state provides its own user profile for identity management. The main services are \cite{NRW:Umsetzung}:

\begin{itemize}
    \item \textbf{Identification and Authentification} \cite{dNRW:Anbindungsleitfaden}

    The user profile can be used for identification by transmitting personal information like name and address after successfully authentification. Authentification is the verification of an authentication. Users can authenticate for the user profile for example through a username / password combination.

    \item \textbf{Determination Trust Level} \cite{dNRW:Anbindungsleitfaden}

    The trust level of a logged in user profile is determined while registration and usage. The user can register and login to the user profile using a username / password combination or the German ID card. The trust level "High" is only granted, if the user registered using the German ID card \textbf{AND} logs in using the German ID card. All other combinations of registration and login result in a "normal" trust level.

    \item \textbf{Management Personal Information} \cite{dNRW:Anbindungsleitfaden}

    Personal information of the user profile can be modified. This requires the user to authenticate. In case the user profile is connected with an online identity card, some attributes like name and age can not be changed.

    \item \textbf{Provisioning Personal Information} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}

    The user profile can be requested to send personal information to a specified URL. This requires the user to authenticate.

\end{itemize}

\paragraph{Institution}
Institutions are the entities which eventually process the incoming applications and provide the users with solutions. They receive a digital application through the data-exchange platform and send back the result as a message through the inbox.

\paragraph{Data-Exchange Platform}
The data-exchange platform delivers applications from the administration portal to the correct administrative institution.

\paragraph{Data Wallet}
The data wallet is a sub-component of the user profile and enables the user to manage documents for his user profile. The main services are:

\begin{itemize}

    \item \textbf{Upload of document}

    The user can upload a document from his local machine to the data wallet.

    \item \textbf{Show documents}

    The user can list all documents which are stored in the data wallet.

    \item \textbf{Delete documents}

    The user can delete documents from the data wallet.

    \item \textbf{Attach documents to application}

    The user can attach a copy of a document stored in his data wallet to an application on a from server.

\end{itemize}

\paragraph{Inbox}
The inbox is a sub-component of the user profile and enables the user to send messages through his user profile. The main services are:

\begin{itemize}

    \item \textbf{Send a message}

    The user can send a message to authorities. This can be for example an institution which processes an application.

    \item \textbf{Receive a message}

    The user can receive messages from authorities for example to update the status of an application.

    \item \textbf{List messages}

    The user can see the messages he received by logging in to his user profile on the administration portal.

    \item \textbf{Notification through E-Mail}

    The user can be notified of a new message through E-Mail.

\end{itemize}

\subsubsection{Interfaces}
In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards. The arrows describe the main direction of information flow in an interaction.

\begin{center}
    \includegraphics[width=8cm]{Diagrams/Interaction Diagram.png}
\end{center}

\begin{enumerate}

    \item The web browser of the user displays the web pages hosted by the administration portal.

    \item The form-server can initiate the application if requested by the administration portal. The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID. In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata. In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.

    \item The form server provides the user a web page which displays an interactive form.

    \item The form server notifies the administration portal of changes in the status of applications. If the administration portal is notified of a submitted application, it requests the form server to transmit the application data.

    \item The administration portal requests the user profile for identification and authentication to login a user on the web page of the portal. The portal also requests authorisation from the user profile to for example access certain personal information.

    \item The administration portal enables the user to manage services of the user profile. It provides OSS tools for managing attributes stored in the user profile, to send new messages and to manage documents in the data wallet.

    \item The administration platform submits application data to the data exchange platform for delivery to the responsible institution.

    \item The data exchange platform notifies the administration portal of the delivery status of the application data.

    \item The data exchange platform notifies the institution of a new application and enables it to download the corresponding data.

    \item The institution can send messages to the inbox of a user profile to for example request additional documents.

    \item The user can send messages to the institution which for example asked for additional documents.

\end{enumerate}

\subsubsection{Data Objects}
This section describes what data each component processes. The property value describes a certain type of data. The source describes which component stores the value. This distinguishes the access of a property by reference and by copy. If the source of a property is another component, the property is accessed by reference. The description gives further detail on how the property is processed by the component.

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{Administration Portal: Service Web Page} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    Name & Web Page & FIM & Name of an administrative service \\
    \hline
    URL & Portal & Portal & The URL of the Web Page \\
    \hline
    Description & Web Page & FIM & Description of an administrative service \\
    \hline
    FIM-ID & Web Page & FIM & FIM-ID of a data field schemata which describes attributes required from the user when applying for the service \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{Administration Portal: User} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    Attributes & User Profile & User Profile & The portal can manage attributes of user profiles \\
    \hline
    JWT & Portal & User Profile & The portal can retrieve a JSON Web Token from the profile after successful authentication by a user \\
    \hline
    URL Form & Portal & Form Server & The portal stores the URL where the form server hosts the interactive form \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{Administration Portal: Application} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    FMS-ID & Portal & Form Server & The portal receives the ID of applications from the form server \\
    \hline
    Status & Portal & Form Server & The portal receives status updates for each application \\
    \hline
    XML Form Data & Portal & Form Server & The portal can retrieve the data which was filled into a form \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{User Profile: Personal Information} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    Attributes & User Profile & FIM & The list of attributes the user can fill in at his profile are based on FIM data fields managed in the FIM repository. \\
    \hline
    Attribute Values & User Profile & User & The user can manually add values to a list of predetermined attributes in his profile \\
    \hline
    Credentials & User Profile & User & The User Profile stores encrypted credentials of the user to authenticate him \\
    \hline
    User Profile ID & User Profile & User Profile & The User Profile creates and stores a unique ID for the user \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{User Profile: Authorisatiozation} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    JWT & Other Component & User Profile & The user profile can create and transfer JSON Web Tokens which authorise other components to access resources of the user profile \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{User Profile: Inbox} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    Received Messages & User Profile & User & The user profile stores messages which were addressed to the user \\
    \hline
    Sent Messages & User Profile & User & The user profile stores messages which were sent by the user \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{User Profile: Data Wallet} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    Documents & User Profile & User & The user profile stores documents which were uploaded by the user \\
    \hline
    \end{tabularx}
\end{table}

\begin{table}[!h]
    \begin{tabularx}{\textwidth}{|l|l|l|C|}
    \rowcolor{LightCyan}
    \hline
    \multicolumn{4}{|l|}{Form Server} \\
    \hline
    Property & Storage & Origin & Description  \\
    \hline
    \hline
    FMS-ID & Form Server & Form Server & The form server creates a unique ID for each application \\
    \hline
    JWT & Form Server & User Profile & The form server uses a JSON Web Token to verify that the entity issuing the request is authorised \\
    \hline
    User Profile ID & Form Server & User Profile & The ID of the user who is associated to the application \\
    \hline
    FIM-ID & Form Server & FIM & The FIM ID of a data field schemata is used to determine how to construct the form \\
    \hline
    Form & Form Server & FIM & The list of attributes the user can fill in at the form are based on the FIM data field schemata. The form server maps the FIM data fields of the FIM data field schemata to attributes the form server understands \\
    \hline
    Status & Form Server & Form Server & The status describes which actions were performed on the application \\
    \hline
    Application Data & Form Server & User & The form server stores the data which the user filled in to the form as an XML file \\
    \hline
    Web Page & Form Server & Form Server & The form server hosts a web page with the interactive form  \\
    \hline 
    Web Page URL & Form Server & Form Server & The form server hosts the web page of the form at an individual URL \\
    \hline 
    \end{tabularx}
\end{table}

\subsubsection{Sequence Diagram}

\begin{figure}[!h]
    \centering
    \includegraphics[width=17cm]{Diagrams/Basic Use Case Sequence Diagram.png}
\end{figure}

### 2021-01-28 sections/6-requirement_analysis.tex
split sections into files

\subsection{User Perspective}

\begin{itemize}
    \item The user wants to manage his personal information in one place
    \begin{itemize}
        \item The user wants to CRUD attributes
        \item The user wants SPs to CRUD his attributes
        \item The user wants a user friendly interface where he can CRUD his attributes
        \item In case the user cannot understand an attribute or its possible values, he needs OSS tools which enables him to enter the correct value
        \item The user wants to enter personal information only once (=> SPs should reuse existing attributes)
        \item The user wants a new or modified attributes to be instantly used everywhere
        \item The user wants a deleted attribute to be instantly deleted everywhere
        \item The user wants to have a list of often used attributes, in order to prefill them
    \end{itemize}
    \item The user wants to manage authentication in one place
    \begin{itemize}
        \item The user does not want to authenticate
        \item The user wants that only he has access to the identity
    \end{itemize}
    \item The user wants to manage authorisation in one place
    \begin{itemize}
        \item The user wants to manage who can perform which actions in his name (f.e CRUD attributes, place order, cancel subscription)
        \item The user wants an authorisation to only be granted if he manually approves
        \item The user wants an authorisation to be associated with a single entity, a reason, which actions can be performed and duration of the authorisation
        \item The user wants to communicate with the authorised entity
        \item The user wants to have much information about the authorised entity
        \item The user wants to be able to revoke an authorisation
        \item The user wants to save the history of authorisations
    \end{itemize}
    \item The user wants to use all OSS tools in one place
    \begin{itemize}
        \item Communication through inbox
        \item Subscribe for a service of an SP
        \item Place order in a shop of an SP
        \item ...
    \end{itemize}
    \item The user wants

\end{itemize}

\subsection{Service Provider Perspective}

\begin{itemize}
    \item SPs want to manage personal information of users
    \begin{itemize}
        \item SPs want to CRUD attributes of the user
        \item In case modification of an attribute has strong implications on the operation of a system, the modification of an attribute needs to be limited
        \item SPs want to access personal information already collected by other SPs
        \item SPs want 
    \end{itemize}
    \item identification
    \item authentication
    \item authorisation
    \item 
\end{itemize}

\subsection{OZG Perspective}

### 2021-01-28 sections/7-imp_system_proposal.tex
split sections into files

There exist many ways to realize an IMP system. Based on the previously analyzed requirements of users and OZG systems, a possible solution for an IMP system is presented.

\subsection{Components}
The IMP system operates on three domains and consists 3 system components. The user domain contains systems, a user directly interacts with. As for the system architecture of the OZG, can be a web browser. The solution for the IMP system provides an IMP client as an app for smartphones. The IMP domain contains systems hosted by the IMP provider. The IMP server is part of this domain. The Service Provider domain contains the system architecture of the service provider and integration components of the IMP solution.
In the following sections, IMP client and IMP server are explained in more detail, the integration system will be the focus of the next chapter.

\begin{figure}[h]
\caption{Overview IMP System}
    \centering
    \includegraphics[scale=0.25]{Diagrams/IMP System Overview.png}
\end{figure}

\subsubsection{IMP Client}

The IMP client is a smartphone application which enables the user to manage his IMP identity. It enables the user to:

\paragraph{Create an IMP identity}

After the user installs the application on his smartphone, he is able to create an IMP identity. The identity consists of a public and private key-pair. The private key will never leave the smartphone. The public key is shared with the IMP server along with information on how to communicate with the client.

\paragraph{Manage Attributes}

The user is able to add, remove, update and read any key-value pair as an attribute of his identity. Attributes are encrypted with the

\paragraph{Documents}

The user is able to add, remove, update and read any document as an attribute of his identity. All documents are stored on the smartphone.

\paragraph{Send and Receive Messages}
\paragraph{Send and Receive Relationship Requests}
\paragraph{Send and Receive Share Requests}
\paragraph{Display Forms}

\subsubsection{IMP Server}
The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
\begin{itemize}
    \item Store identities
    \item Create and store relationship template
    \item Create and store request template
    \item Deliver relationship requests
    \item Deliver requests
    \item Deliver messages
\end{itemize}

\subsection{Functionalities}
As already introduced, the IMP solution provides the user with multiple functionalities. In this section, important features are described in more detail.

\subsubsection{Relationship}

IMP identities can establish an IMP relationship. Through this relationship, both identities can securely share attributes and communicate.

To establish a relationship, a relationship template is required. The template is created by an identity which wants to receive relationship requests and is shared with the identity which wants to request a relationship. The relationship template is stored on the IMP server and can be retrieved trough template ID. Besides technical information, the template usually contains:
\begin{enumerate}
    \item Information which the templator would like to share about itself 
    \item Information which the templator would like the requestor to share
    \item Requested additional information about the requestor 
    \item Meta information 
\end{enumerate}

\subsubsection{Share Attribute}

\subsubsection{Change Attribute}

### 2021-01-28 sections/8-imp_solution_integration.tex
split sections into files

\subsection{Create User Profile}

The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.

Creation and management of multiple user profiles quickly becomes a burden for users. If all service providers would switch to using only identities provided by an IMP solution, users would only have to manage one digital identity. However performing this change is no simple task for a service provider. An abrupt change of the system architecture can lead to many problems like extended periods of down times. This integration architecture therefore focuses on a simplified initial integration of IMP identities where OZG user profiles can still be used to access OZG services.

It would be possible to integrate the IMP identity as an alternative to the user profile. The user could then use OZG services either by creating an OZG user profile or by providing an IMP identity. Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile. The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management. The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution. OZG systems would have to request personal information from the IMP identity while providing a reason for doing so. After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity. However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile. As the focus of this integration architecture is non invasiveness, the connection of IMP identity and user profile is preferred.

The IMP solution provides a service for establishing a connection between entities. It is called an IMP relationship. Through a relationship, two entities can identify each other, assume authentication of the other party and can securely communicate and share attributes of their IMP identities. To utilize an IMP relationship between the administration portal and the IMP identity as connection between user profile and IMP identity, the relationship has to contain identification of the user profile in form of for example a user ID. The administration portal would then be able to map relationships along with the IMP identity ID to user profiles.

\subsection{Attribute Synchronization}

The goal of the connection of IMP identity and OZG user profile is to enable management of personal information through the IMP client. Attributes stored as part of the IMP identity and attributes stored as part of the user profile have to be manageable through the IMP client.

One option would be for the IMP client to overwrite all attributes of the OZG user profile with those stored in the IMP identity and update values in the user profile as soon as an attribute of the IMP identity changes. This would require the user profile management web page of the administration portal to be locked for profiles with a connected IMP identity. Another option would be to enable the user to manage attributes of IMP identity and user profile separately through the IMP client.

The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically. However, this would require the user to always share the most current personal information with the OZG systems. Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider. If the user for example changes the birth date of its IMP identity, the OZG system might not want to approve this change immediately. Another option would be for the user to manage IMP identity and user profile separately. Changes of the OZG user profile can then happen on a request reply basis. The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there. The disadvantage of this option is, that the management of personal information is more complicated than the first option. Through attribute management tools on the IMP client, the experience can be improved.

As the second option provides necessary features, which the first option does not have, it is preferred.

The management of both IMP identity attributes and attributes of the OZG user profile can be done as part of the relationship established for their connection. As part of the connection, IMP identity and administration portal share attributes. The user profile can be determined to store the exact same values as shared by the IMP identity as part of this relationship. Therefore, in order to change attributes of the user profile, the value of the shared attributes has to change. This can be done through a request-reply process. One party requests the change of a shared attribute, which will only be done if the other party accepts. This enables the user to manage the OZG user profile through the IMP client by requesting a change for attributes shared as part of a relationship. The user could also manage his user profile through the web page of the administration portal, resulting in a request form the administration portal to change shared attributes of the relationship.

\subsection{Login to a User Profile}

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal to access OZG services. As previously described, the integration architecture does not replace the OZG user profile. The user is therefore still able to login to his user profile on the administration portal and take advantage of all OZG services. The IMP system can however provide an additional way to access OZG services through the IMP client. One possibility was already introduced: the management of personal information.

In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid. Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session. When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components. This process is necessary because any person can send requests to the web server and possibly pretend to be a different user. In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user. Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity. As the IMP client is an app installed on the device of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.

\subsection{Application for Administrative Service}
The third step is selection of an administrative service through the web page of the administration portal. This service is not directly related to identity management and will therefore not be provided by the IMP client.
The steps four to eight are not integrated by the IMP solution as this would require invasive interaction with components other than the administration portal.

As a result of that, most of the steps necessary for applying for an administrative service remain to be done through the web page of the administration portal with a logged in user profile. The next integration architecture will present a solution where most of the steps will be done through the IMP systems.

\subsection{Communication}

The ninth step of the basic OZG use case is to communicate with responsible institutions. As both the user profile and the IMP identity provide an inbox, the IMP client can be used to send and receive messages through the inbox of the OZG user profile.

The messages related to a OZG user profile can be exchanged as part of the relationship between the administration portal and the IMP identity. Messages received by the user profile can be forwarded by the administration portal to the inbox of the IMP identity. Sending messages from the IMP client to institutions however is not possible, as the IMP client does not know the address of the institution responsible for an application. However, if the IMP client already received a message from an institution, it can enable the user to respond.

### 2021-01-28 sections/9-technological_integration.tex
split sections into files

\subsection{Messaging}

\subsection{Create User Profile}

In order for an IMP identity to request a relationship with the administration portal, the portal has to provide a relationship template to the IMP client of the user. The template can be made accessible to the IMP client trough a new web page which displays the template ID as QR code if the user is logged in. Each time a logged in user requests the web page, the web server requests the IMP connector to create a relationship template.

The IMP connector provides an API for creation of relationship templates as part of its REST interface. Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response. The web page of the administration portal can then render the template as a QR code on the web page.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template REST.png}
\end{figure}

This is one example, where the OZG system could use the REST interface for integration with the IMP system. However, messaging can improve the integration solution to be more maintainable, stable and scalable and will be the preferred option in following scenarios. Using messaging, the web server can publish a message containing the request for a new relationship template on a "Relationship Template Request" channel, where the connector receives it, creates the template and publishes a reply message containing the template ID on the "Relationship Template Reply" channel.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging.png}
\end{figure}

It could happen, that in future, the API of the connector changes. If the web server integrated the connector through its REST interface, this would require the request code of the web server to be changed. If messaging is used, messages leaving the "Relationship Template Request" channel could be mapped to the new API signature through an additional messaging component called message translator. This is an example for how a messaging can improve maintainability of an integration architecture.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging Improved.png}
\end{figure}

When the user is presented with the web page containing the QR code, the user can scan it with its IMP client. Based on the template ID, the client retrieves the template from the IMP server and displays it for the user. If the user accepts the template, the client sends a relationship request to the IMP server, who forwards it to the corresponding connector.

Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request. If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request. The server would have to regularly request a status update which is not efficient. Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified. The administration portal can process the relationship request and publish a message containing a response on the "Relationship Response" channel, where the connector will be notified. Through the IMP server, the response server is routed to the IMP client and the relationship is established.
In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Request.png}
\end{figure}

\subsection{Attribute Synchronization}

As administration portal and IMP identity established a relationship, the connector can be excluded from the diagram for better visualisation. Behind the scenes, all interactions between administration portal and IMP client still go through connector and IMP server.

If the user requests the change of a shared attribute through the IMP client, it sends an attribute change request to the administration portal by publishing a message on the "Inbound Attribute Change Request" channel. After the administration portal decides to accept the request, it can publish a message to the "Outbound Attribute Change Response" channel. This message will on one hand be received by the IMP client and on the other hand result in an update of the user profile.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change IMP Client.png}
\end{figure}

If the user requests the change of a shared attribute through the web page of the administration portal, the web server sends an attribute change request to the "Outbound Attribute Change Request" channel which is received by the IMP client. If the user accepts the request, the client publishes a message on the "Inbound Attribute Change Response" channel where it results in an update of the user profile.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change Web Page.png}
\end{figure}

\subsection{Login to a User Profile}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Login.png}
\end{figure}

\subsection{Communication}

### 2021-02-06 msc-thesis.tex
chapter 3 finished

@@
 %     idxtotoc,     % index in toc
-%     parskip       % paragraph skip instad of paragraph indent
+%     parskip       % paragraph skip instead of paragraph indent
      ]{scrreprt}
@@
 \usepackage{float}
-
+\usepackage{wrapfig}
 \usepackage{subfiles} % Best loaded last in the preamble
@@
 
+\section{Messaging}
+
+This section describes possibilities of constructing a message based integration architecture
+
+\subsection{Messaging Patterns}
+
 \chapter{Identity Management}
@@
 
-\section{IMP System Proposal}
+\section{IMP System Solution}
 
@@
 
-\chapter{Minimal Integration Architecture}
+\chapter{Integration Challenges}
 
-The goal of the integration architecture is to make as many functionalities required for the basic OZG use case available through the IMP client as possible.
-As described in chapter 2.3, the steps of the basic OZG use case are:
-\begin{enumerate}
-    \item{Create User Profile}
-    \item{Login to User Profile}
-    \item{Selection of Administrative Service}
-    \item{Filling in Application}
-    \item{Submission of Application}
-    \item{Reception of Application by Administration Portal}
-    \item{Submission of Application to Data-Exchange Platform}
-    \item{Management of Applications}
-    \item{Communication}
-\end{enumerate}
+This chapter describes challenges for integrating the IMP system described in chapter 3 into the OZG system architecture.
+The quality of the presented integration can be determined based on the number of the following challenges it solves.
 
-To enable service providers a quick introduction of IMP systems into their system architecture, this integration architecture describes a minimally invasive integration.
-After deployment of this integration architecture, all OZG services are still usable as before but can be enhanced by IMP solutions.
-For this integration to be minimally invasive, only one connector exists and integrates only with the administration portal.
-No other OZG system component is modified or directly accessed.
+\section{IMP Challenges}
+This section describes challenges which arise from the operation of the IMP system
 
-The goal of the integration is to enhance each step of the basic OZG use case through integration with IMP solutions.
-Therefore in the overview section, for each step, possible integration's of OZG systems are evaluated.
-The following sections contain more detailed descriptions of the selected integration strategies.
+\begin{itemize}
+    \item Connector has REST interface and cannot notify system architecture
+    \item Connector does not understand messages
+    \item Messages can have different versions
+    \item API of connector can change
+    \item New types of messages can be added by the client and the system provider might need to understand them
+\end{itemize}
+
+\section{SP Challenges}
+
+This section describes challenges which arise from service provider integration requirements.
+
+\begin{itemize}
+    \item Minimal modification of existing systems
+    \item Maintainability
+    \item Scalability
+    \item Failure Handling
+    \item Administration
+    \item Extendability
+    \item Modularity
+
+\end{itemize}
+
+\subsection{OZG Challenges}
+
+This section describes challenges which arise from OZG integration requirements.
+
+\begin{itemize}
+    \item Administration portal has access to all personal information
+    \item Once an application is submitted, its attributes cannot be changed
+    \item Mapping of IMP attributes and FIM data blocks
+    \item Messages can have a correlation (request-reply) which the system architecture might want to keep track of
+\end{itemize}
+
+\chapter{Initial Solution Proposal}
+
+The goal of the initial integration solution is to introduce features of the IMP system into the OZG system architecture.
+All existing services should be accessible the same way as before but with additional options for using IMP.
+The focus of this initial integration is to avoid disruption of existing system operation through non-invasive integration, to enable a fast and simple entrance into the IMP system and to provide future upgrade capabilities.
+The integration takes place on three layers:
 
 \begin{figure}[h]
+\caption{IMP Layer Diagram}
     \centering
-    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
+    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.png}
 \end{figure}
+
+\paragraph{IMP Solution Integration Layer} 
+The purpose of the integration on the IMP solution layer is to take advantage of new interaction capabilities with the user through the IMP system.
+Chapter 3 gives some examples on how the IMP client can enable the user to interact with the IMP system.
+The integration evaluates possibilities of using relationships and IMP messages to improve OZG services, defines what the purpose of each message and relationship type is and how they should be handled by client and service provider.
+For example relationship templates can be defined and new message types can be created with corresponding new user interfaces in the IMP client.
+
+\paragraph{Relationship Integration Layer} The purpose of the integration on the relationship layer is to enable the technological utilization of relationships as described by the integration on the solution integration layer.
+
+\paragraph{Communication Integration Layer} The purpose of the integration on the communication layer is to enable the technological utilization of messages as described by the integration on the solution integration layer.
 
@@
 
+This section evaluates possibilities of a technological integration architecture for realizing the integration solution described in the previous section.
+
 \subfile{sections/9-technological_integration}
 
-\chapter{Advanced Integration Architecture}
+\chapter{Advanced Solution Proposal}
 
@@
 
+\subfile{sections/10-imp_solution_integration}
+
 \chapter{Solution Evaluation}

### 2021-02-06 sections/6-requirement_analysis.tex
chapter 3 finished

@@
 \begin{itemize}
-    \item The user wants to manage his personal information in one place
-    \begin{itemize}
-        \item The user wants to CRUD attributes
-        \item The user wants SPs to CRUD his attributes
-        \item The user wants a user friendly interface where he can CRUD his attributes
-        \item In case the user cannot understand an attribute or its possible values, he needs OSS tools which enables him to enter the correct value
-        \item The user wants to enter personal information only once (=> SPs should reuse existing attributes)
-        \item The user wants a new or modified attributes to be instantly used everywhere
-        \item The user wants a deleted attribute to be instantly deleted everywhere
-        \item The user wants to have a list of often used attributes, in order to prefill them
-    \end{itemize}
-    \item The user wants to manage authentication in one place
-    \begin{itemize}
-        \item The user does not want to authenticate
-        \item The user wants that only he has access to the identity
-    \end{itemize}
-    \item The user wants to manage authorisation in one place
-    \begin{itemize}
-        \item The user wants to manage who can perform which actions in his name (f.e CRUD attributes, place order, cancel subscription)
-        \item The user wants an authorisation to only be granted if he manually approves
-        \item The user wants an authorisation to be associated with a single entity, a reason, which actions can be performed and duration of the authorisation
-        \item The user wants to communicate with the authorised entity
-        \item The user wants to have much information about the authorised entity
-        \item The user wants to be able to revoke an authorisation
-        \item The user wants to save the history of authorisations
-    \end{itemize}
-    \item The user wants to use all OSS tools in one place
-    \begin{itemize}
-        \item Communication through inbox
-        \item Subscribe for a service of an SP
-        \item Place order in a shop of an SP
-        \item ...
-    \end{itemize}
-    \item The user wants
+    \item The user wants one service where he can manage all personal information
+
+    \item The user does not want to manage multiple user profiles
+
+    \item The user wants all service providers to be able to use the personal information of the service
+
+    \item The user wants service providers to always use the most recent state of his personal information
+
+    \item The user wants to be able to share and retract personal information, service providers have access to
+
+    \item The user wants to restrict access to personal information as much as possible
+
+    \item The user wants information about the service provider he is about to share information with
+
+    \item The user wants to know the reason each time a service provider wants to process his personal information
 
@@
 
+The service provider is assumed to have an existing system architecture containing systems for management of user profiles.
+This section describes requirements of a service provider regarding the service for managing user data.
+
 \begin{itemize}
-    \item SPs want to manage personal information of users
-    \begin{itemize}
-        \item SPs want to CRUD attributes of the user
-        \item In case modification of an attribute has strong implications on the operation of a system, the modification of an attribute needs to be limited
-        \item SPs want to access personal information already collected by other SPs
-        \item SPs want 
+
+    \item The service provider wants a good user experience -> see all user requirements above
+
+    \item The service provider wants to access personal information necessary for processing user requests
+
+    \item The service provider wants to change, add or delete personal information
+
+    \item The service provider wants to communicate with users
+
+    \item The service provider wants to the service to guarantee secure interaction with users
+
+    \item The service provider wants the system to keep a record of interactions with users and be able to verify the validity of the record
+
+    \item The service provider wants to inform users about legal regulations like privacy protection measurements
+
+    \item The service provider wants minimal integration effort and cost
+
+    \item The service provider wants to be able to quickly integrate parts of the service with optional future upgrades
+
+    \item The service provider wants the integrated solution to be scalable, maintainable and stable
+
 \end{itemize}
-    \item identification
-    \item authentication
-    \item authorisation
-    \item 
-\end{itemize}
-
-\subsection{OZG Perspective}

### 2021-02-06 sections/7-imp_system_proposal.tex
chapter 3 finished

@@
-There exist many ways to realize an IMP system. Based on the previously analyzed requirements of users and OZG systems, a possible solution for an IMP system is presented.
+There exist many ways to realize an IMP system.
+Based on the previously analyzed requirements of users and service providers, a possible solution for an IMP system is presented.
+The purpose of this chapter is not to give a detailed explanation of the presented IMP system but to deliver a brought understanding of the concepts, features and components involved.
+
+\subsection{Features}
+
+\paragraph{Provisioning} The IMP system is hosted on the system architecture of the identity management provider and provides identity management as a service for users and SPs.
+Users and service providers can manage identities by accessing features of the IMP system.
+The IMP system stores all personal information and data necessary for the operation of identity management.
+The user only manages one identity which can be accessed by multiple service providers.
+
+\paragraph{Tooling} The IMP system provides users and service providers with software tools for accessing its features.
+The user is provided with a user friendly application while the enterprise is provided with tools for integration.
+
+\paragraph{Personal Information Management} One feature of the IMP system is management of personal information.
+Through the application, the user can create an identity and add, remove and update any kind of key-value pairs.
+These are IMP identity attributes.
+
+\paragraph{Relationship}
+
+Users and service providers can establish relationships which enables them to share information and interact.
+The initial form of a relationship is a relationship template.
+The template is created by the service provider and describes which relationships he is willing to establish.
+Relationship templates are distributed to interested users which can use it to request relationships.
+A service provider has to fill a relationship template with some minimal required and some optional information:
+
+\begin{itemize}
+    \item \textbf{Title}
+
+    The title describes the purpose of the relationship in a short way.
+
+    \item \textbf{Requested Attributes} (optional)
+
+    Requested Attributes is a list of attribute keys, the user will have to submit as part of the relationship request.
+
+    \item \textbf{Shared Attributes}
+
+    Shared Attributes is a list of attribute keys and values, the service provider wakes available to any user interested in requesting this relationship.
+The service provider has to share a minimal amount of attributes which enable the user to identify it.
+
+    \item \textbf{Purpose}
+
+    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested by the user are necessary for it.
+
+    \item \textbf{Attachments}
+
+    Attachments are documents attached to the relationship template by the service provider. The documents can for example contain legal information.
+
+    \item \textbf{Metadata}
+
+    Metadata can be any type of information which should not be displayed to the user but is necessary for the user application or the service provider to process the resulting relationship request.
+
+\end{itemize}
+
+When the user receives the template through his IMP tooling, the requested attributes are automatically filled in if he previously added them to his IMP identity.
+Otherwise he can fill in the correct values now and automatically add them as attributes of his identity.
+
+It is important to differentiate identity attributes from the attributes shared as part of the relationship.
+Identity attributes are managed by the user to reflect the most up to date information.
+Attributes shared as part of a relationship can be automatically filled with values from the same attributes of the IMP identity but can also be manually entered.
+This means, shared attributes and IMP identity attributes are not necessarily the same.
+
+Based on the information about the service provider and the purpose of the relationship, the user can decide to send a relationship request or not.
+If the user decides to request the relationship, the request is sent to the service provider along with a copy of the requested attributes.
+If the service provider approves the request, the relationship is established and both parties get notified.
+
+\paragraph{Messages} As part of a relationship, user and service provider can interact with each other by asynchronously exchanging structured data (IMP messages).
+Messages with any content can be exchanged, however, the tools used by the user and the service provider should be able to understand the messages.
+
+The integration tool for the service provider does not understand the content of messages but simply makes the accessible by the system architecture of the service provider.
+Without additional integration solutions, the service provider has to implement his own solutions for processing the different types of messages.
+The application provided to the user has a set of messages it understands.
+The list of messages the application is able to process can be expanded by the identity management provider who develops it.
+
+Some important messages the user application understands and the service provider should be able to process too are:
+
+\begin{itemize}
+    \item \textbf{Mails}
+
+    Mails are messages which contain a human readable title, and body.
+
+    \item \textbf{Attribute Change}
+
+    After a relationship is established, service provider or user might want to change attributes they shared. This can be done by exchanging request-reply messages.
+\end{itemize}
+
+\paragraph{Security}
+The IMP system guarantees, that all information is encrypted and can only be decrypted by identities which are allowed to read it.
+Only the owner of an identity can manage attributes of his identity.
+A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared.
+Interactions as part of a relationship are only possible between the identities of the relationship.
+
+\subsection{Evaluation of Features}
+
+This section evaluates the advantages and disadvantages of the described features of the IMP system based on the requirements of users and service providers.
+
+\subsubsection{User}
+The IMP system enables users to manage one identity and share attributes with multiple service providers.
+This replaces the need of a user profile for all service providers which take advantage of the IMP service.
+The user wont have to access multiple websites for managing user profiles but update his identity only through the IMP service.
+As attributes can only be shared with service providers as part of a relationship, the user has control of his personal information.
+Before accepting the relationship, he can see information about the identity of the service provider, like his name, address, phone number and more.
+The user is also provided with information on why the relationship and request attributes are necessary which helps the user in deciding if he agrees with the necessity of sharing the information.
+As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relation for each business process which requires access to personal information.
+The information therefore can not only be shared with a single service provider but also for an individual process.
+User and service provider can interact through relationships.
+Therefore messages can be exchanged and associated to a certain business process.
+
+\subsubsection{Service Provider}
+
+The IMP system enables the service provider to access personal information of users without the need of hosting a system for identity management.
+Depending on the price of the IMP solution, this can reduce the cost for operating and maintaining the system architecture.
+The service provider has to hire less personal, does not have to buy expensive hardware and can more easily scale the performance of his system.
+As previously described, the user experience can also increase and lead to more customers.
+Relationships enable service providers to request users to share attributes while specifying the legal reasons for processing the information and to directly interact with them.
+The IMP system takes over the responsibility for securing personal information of users and interactions with the service provider.
+As the relationship cannot be deleted without approval of both identities, it can be used as proof of for example contracts or order placements.
+The IMP system provides tools for integration which minimizes the effort for system providers to start using the IMP system.
+
+As the IMP system focuses on improved data protection for users, the service provider might lose access to valuable but not necessary personal information.
+The determination of a reason for processing personal information also requires increased system complexity for making sure, that personal information is only used for the specified reason.
+The integration of a new solution for identity management is an expensive and time consuming task and might in short term increase instead of reduce cost.
+Using an external service for identity management makes the service provider dependent on the identity management provider.
+This can be a problem, if in the future, the service costs increase or the IMP solution stops being supported.
 
 \subsection{Components}
-The IMP system operates on three domains and consists 3 system components.
-The user domain contains systems, a user directly interacts with.
-As for the system architecture of the OZG, can be a web browser.
-The solution for the IMP system provides an IMP client as an app for smartphones.
-The IMP domain contains systems hosted by the IMP provider.
-The IMP server is part of this domain.
-The Service Provider domain contains the system architecture of the service provider and integration components of the IMP solution.
-In the following sections, IMP client and IMP server are explained in more detail, the integration system will be the focus of the next chapter.
 
 \begin{figure}[h]
-\caption{Overview IMP System}
+\caption{IMP System Overview}
     \centering
@@
 
-\subsubsection{IMP Client}
+The IMP system operates on three domains.
+The user domain contains systems, the user directly interacts with.
+This typically are applications on PC or smartphone and websites.
+The IMP system provides an application for PC and smartphone to the user for accessing IMP services.
+For simplification, the user is assumed to use only one device which eliminates the need for synchronization of devices.
+The client enables the user to manage attributes of his identity, to establish relationships, to manage relationships and to interact through relationships.
 
-The IMP client is a smartphone application which enables the user to manage his IMP identity. It enables the user to:
+The IMP domain contains all systems hosted by the identity management provider.
+In this case, the domain contains only the IMP server.
+The IMP server is able to communicate with IMP client and IMP connector.
 
-\paragraph{Create an IMP identity}
+The service provider domain contains the system architecture of the service provider and the IMP connector.
+The IMP connector contains a REST API which enables the system architecture to access IMP services.
 
-After the user installs the application on his smartphone, he is able to create an IMP identity.
-The identity consists of a public and private key-pair.
-The private key will never leave the smartphone.
-The public key is shared with the IMP server along with information on how to communicate with the client.
+\begin{figure}[h]
+\caption{IMP System Operation Layers}
+    \centering
+    \includegraphics[scale=0.3]{Diagrams/IMP Layer Diagram.png}
+\end{figure}
 
-\paragraph{Manage Attributes}
+The operation of IMP systems can be separated in multiple layers.
+The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.
 
-The user is able to add, remove, update and read any key-value pair as an attribute of his identity. Attributes are encrypted with the
+\paragraph{Transport Layer}
 
-\paragraph{Documents}
+The "transport layer" is responsible for securely routing data between IMP client, IMP server and IMP connector.
+Depending on the use case, the transport layer encrypts data so that it is only visible for client and connector.
+In this layer, IMP client and IMP connector are endpoints where data can be encrypted, decrypted, sent and received.
+In this layer, the IMP server is the routing component which forwards sent data to its correct destination while checking validity of messages.
 
-The user is able to add, remove, update and read any document as an attribute of his identity. All documents are stored on the smartphone.
+\paragraph{Relationship Layer}
 
-\paragraph{Send and Receive Messages}
-\paragraph{Send and Receive Relationship Requests}
-\paragraph{Send and Receive Share Requests}
-\paragraph{Display Forms}
+The "relationship layer" is responsible for establishing a relationship between IMP client and IMP connector.
+IMP client and IMP connector send relationship requests and responses and store relationships.
+The IMP server creates, stores and updates relationships and synchronizes their status with client and connector.
 
-\subsubsection{IMP Server}
-The IMP server interacts with the clients in order to deliver information from one client to the other. The server has the following functionalities:
+\paragraph{Communication Layer}
+
+The "communication layer" is responsible for exchanging IMP messages as part of an active relationship between IMP client and IMP connector.
+The client can create, send, receive, process and display a list of IMP messages he is able to understand.
+The IMP connector is able to send and receive IMP messages through a relationship without being aware of its content.
+The IMP server stores an encrypted backup of all messages.
+
+\paragraph{IMP Solution Layer}
+
+The "IMP solution layer" is responsible for providing user interaction capabilities for construction of IMP solutions.
+A service provider can interact with the user in multiple ways through user interfaces of the IMP client.
+Depending on the use case of the service provider, interactions through the UIs can have different purposes.
+
+For example, a service provider can decide to use relationships as a way to receive product or subscription orders.
+Another possibility would be to use relationships for filling in a form as part of a survey.
+
+The user interface described in the following are a minimal example which fulfill basic requirements for establishing relationships and displaying IMP messages.
+An identity management provider can add multiple more specialized UIs to the application.
+
+\begin{figure}[h]
+\caption{User Application Interfaces}
+    \centering
+    \includegraphics[scale=0.2]{Diagrams/UI.png}
+\end{figure}
+
+\paragraph{Personal Information} The attributes interface enables the user to manage attributes for his identity by adding, updating or removing values for common keys like name, surname, birth date and more.
+Here, the user can also create, update or delete new key-value pairs.
+
+\paragraph{Relationship Request} On the relationship request interface, the user can scan a QR code containing a relationship template and request a corresponding relationship.
+The attributes required for the relationship are automatically filled in if they exist for the identity.
+Otherwise the user can manually enter the correct values.
+If all requested attributes are filled in, the user can request the relationship
+
+\paragraph{Relationship Overview} On the relationship overview interface, the user can see all active relationships
+
+\paragraph{Relationship Details} On the relationship details interface, the user can view the content of a relationship and change shared attributes.
+However, an attribute will only be changed after the service provider accepted.
+The user can also send a mail to the other party of the relationship.
+
+\paragraph{Notifications} On the notifications interface, the user sees all received mails and the corresponding relationship. The user is able to reply to the mails.
+
+\subsection{IMP Use Cases}
+
+In this section the most important use cases of the IMP system are described in more detail.
+
+\subsubsection{Establish Relationship}
+
+The first step towards a relationship usually is the interest of a user.
+A user for example wants to subscribe to the newsletter of a service provider.
+The service provider needs personal information of the user to be able to send him personalized mails.
+To obtain the necessary attributes and receive the approval of the user, the service provider requires an established relationship.
+
+\begin{figure}[h]
+    \centering
+    \caption{IMP Use Case Establish Relationship Sequence Diagram}
+    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Establish Relationship Sequence Diagram 1.png}
+\end{figure}
+
+To enable users to request a relationship with the purpose of subscribing for a newsletter, the service provider has to create a relationship template.
+Through the REST interface of the connector, he sends a request for a new relationship template.
+The request contains parameters specifying the content of the relationship template.
+In this case, the relationship template could be configured as follows:
+
 \begin{itemize}
-    \item Store identities
-    \item Create and store relationship template
-    \item Create and store request template
-    \item Deliver relationship requests
-    \item Deliver requests
-    \item Deliver messages
+    \item Title: Subscribe to the newsletter
+    \item Requested Attributes: Name, Surname, E-Mail address, Interests
+    \item Shared Attributes: SP Name, SP address, SP phone number, SP E-Mail address
+    \item Purpose: By accepting this relationship, you agree to receive personalized mails to the shared address. Name, surname and interests are required to personalize the content of the mails.
+    \item Attachments: Some legal document
 \end{itemize}
 
-\subsection{Functionalities}
-As already introduced, the IMP solution provides the user with multiple functionalities. In this section, important features are described in more detail.
+\begin{wrapfigure}{r}{0.5\textwidth}
+    \centering
+    \caption{Relationship Request Example}
+    \includegraphics[scale=0.25]{Diagrams/Relationship Request Example.png}
+\end{wrapfigure}
 
-\subsubsection{Relationship}
+Based on the parameters of the request, the connector creates a relationship template and sends it to the IMP server.
+The server stores the template and returns a relationship template ID.
+Through this ID, the corresponding template can be retrieved from the IMP server.
+The service provider can transmit the template ID to any user who wishes to subscribe for a newsletter. This can be done by for example rendering the template ID as a QR code on a website.
+If the QR code is displayed to the user, he can scan it using the IMP client.
+The client understands that the content of the QR code contains a relationship template ID and retrieves the corresponding template from the IMP server.
 
-IMP identities can establish an IMP relationship. Through this relationship, both identities can securely share attributes and communicate.
+The IMP client displays the relationship template to the user and automatically fills in as many requested attributes as possible.
 
-To establish a relationship, a relationship template is required.
-The template is created by an identity which wants to receive relationship requests and is shared with the identity which wants to request a relationship.
-The relationship template is stored on the IMP server and can be retrieved trough template ID.
-Besides technical information, the template usually contains:
-\begin{enumerate}
-    \item Information which the templator would like to share about itself 
-    \item Information which the templator would like the requestor to share
-    \item Requested additional information about the requestor 
-    \item Meta information 
-\end{enumerate}
+The user can now decide if he wants to accept the relationship and share the requested attributes.
+If he accepts, IMP client sends a relationship request to the IMP server.
+The request contains all information of the relationship template in addition to the shared attributes of the user.
 
-\subsubsection{Share Attribute}
+\begin{figure}[h]
+    \centering
+    \caption{IMP Use Case Establish Relationship Sequence Diagram}
+    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Establish Relationship Sequence Diagram 2.png}
+\end{figure}
 
-\subsubsection{Change Attribute}
+Based on the relationship request, the IMP server creates a relationship with the status "pending".
+A unique relationship ID is attached.
+The server then forwards the relationship request to the connector of the service provider.
+
+As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector trough its REST interface.
+The connector responds with the received relationship request.
+The system architecture of the service provider processes the request in order to decide if it should be accepted.
+The service provider could for example verify if a relationship with the identity already exists or if the E-mail address is already registered.
+
+The system architecture sends a relationship response to the REST interface of the connector.
+The response contains all information of the received relationship request with optional additional information the service provider might want to share now.
+This could for example be the name of the newsletter the service provider decided to select for the user based on his specified interests.
+
+The connector sends the relationship response to the IMP server which updates the content and status of the corresponding relationship.
+It might be possible, that the user retracted the relationship request in the meantime.
+In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
+If however, the IMP server updates the status of the relationship to "established", both IMP client and connector are notified with the final content of the relationship.
+
+After receiving the final relationship established notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.
+
+\subsubsection{Send Message}
+
+Through an established message, user and service provider can exchange messages with any structure and content.
+However, this only makes sense if both IMP client and system architecture of the service provider can understand the messages.
+IMP server and IMP connector only take care of the correct routing.
+The list of messages an IMP client understands can be expanded by the identity management provider.
+It can therefore be assumed, that the IMP client understands any message service providers often want to exchange.
+For simplicity, in the following sections, behaviour of the IMP client for newly defined message can be defined at will.
+Two important types of messages were already defined: Mail Messages and Attribute Change Request-Reply Messages.
+
+\subsubsection{Request Attribute Change}
+
+It is possible, that in the future, the user wants to change the mail address where he receives the newsletter.
+As the established relationship remains to be valid, it should not be terminated, but shared attributes should be changed instead.
+
+Through the IMP client, the user can view the corresponding relationship and edit the attributes.
+After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends a attribute change request message to the connector.
+The connector does not understand the content of the message but from which relationship it originated from.
+As the connector cannot notify the system architecture of the service provider, polling for new messages is required.
+After the system architecture receives the message, it understands the structure of the message and that the purpose of the message is an attribute change request.
+
+The system architecture evaluates if it accepts the changes and sends a response trough the REST interface of the connector.
+The system architecture might execute additional processes.
+In this case, the mail address stored in the database would be updated.
+
+The IMP server receives the response message through the connector and routs it to the IMP client.
+The IMP client understands the message, updates the value stored as part of the relationship and displays a notification to the user.
+
+\begin{figure}[h]
+    \centering
+    \caption{IMP Use Case Change Relationship Attribute Sequence Diagram}
+    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Change Realtionship Attribute Sequence Diagram.png}
+\end{figure}
+
+\subsubsection{Send Mail}
+
+If a user has questions about the newsletter, he can send messages to the service provider as part of the relationship.
+Client sends the mail message to the IMP server which routes it to the connector.
+The system architecture polls for incoming messages.
+When the system architecture receives the message, it understands the content and purpose and for example notifies an employee.
+An employee could be notified through E-Mail and a response from the employee to the mail could automatically sent to the relationship through the REST API of the connector.
+Connector and IMP server route the message to the IMP client, who understands the message and displays it to the user.
+
+\begin{figure}[h]
+    \centering
+    \caption{IMP Use Case Communication Sequence Diagram}
+    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Communication Sequence Diagram.png}
+\end{figure}

### 2021-02-06 sections/8-imp_solution_integration.tex
chapter 3 finished

@@
+This section describes integration possibilities on the solution layer.
+For each step of the basic OZG use case described in chapter 2, it is evaluated how the IMP system described in chapter 3 can be utilized to improve it.
+
+\begin{enumerate}
+    \item{Create User Profile}
+    \item{Login to User Profile}
+    \item{Selection of Administrative Service}
+    \item{Filling in Application}
+    \item{Submission of Application}
+    \item{Reception of Application by Administration Portal}
+    \item{Submission of Application to Data-Exchange Platform}
+    \item{Management of Applications}
+    \item{Communication}
+\end{enumerate}
+
 \subsection{Create User Profile}

### 2021-02-06 sections/9-technological_integration.tex
chapter 3 finished

@@
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
+\end{figure}
+
 \subsection{Messaging}
 
+This section describes the advantages of using a message based integration approach.
+
+...
+
 \subsection{Create User Profile}
+
+\begin{figure}[h]
+    \centering
+    \caption{Overview Connection}
+    \includegraphics[scale=0.2]{Diagrams/Integration Architecture 1/Messaging/Connection/Technological Integration Connection.png}
+\end{figure}
 
@@
     \centering
+    \caption{Relationship Template}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template REST.png}
@@
     \centering
+    \caption{Relationship Template Messaging}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging.png}
@@
     \centering
+    \caption{Relationship Template Improved Messaging}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging Improved.png}
@@
     \centering
+    \caption{Relationship Request}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Request.png}
@@
     \centering
+    \caption{Attribute Change Inbound}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change IMP Client.png}
@@
     \centering
+    \caption{Attribute Change Outbound}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change Web Page.png}
@@
 
+The administration portal receives a request from the IMP client through a "Request" channel.
+Through the connection database created in 4.2.2, the administration portal finds the corresponding user ID.
+Through a JWT database, where all JWT tokens are stored for the user profiles, the administration portal retrieves the JWT corresponding to the user ID.
+The administration portal can then route the request on the "Request" channel and attach the JWT.
+
 \begin{figure}[h]
     \centering
+    \caption{Authentication}
     \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Login.png}

### 2021-02-09 sections/8-imp_solution_integration.tex
integration solution notes

@@
 \subsection{Create User Profile}
+\begin{itemize}
+    \item User profile should not be replaced by IMP identity in order for OZG services to be accessible the same way
+    \item Connector can establish relationships and provides messaging capabilities
+    \item Option 1: Use an established relationship as alternative for a user profile
+    \begin{itemize}
+        \item Advantages: 
+        \item Disadvantages: All components of the system architecture would have to be able to separate between user profile and IMP identity processing and be able to interact with the IMP system.
+This would require modification of each system component and is too invasive.
+Users which already have a user profile cannot use it with their IMP identity.
+    \end{itemize}
+    \item Option 2: Use a relationship to create a user profile and connect it to the IMP identity
+    \begin{itemize}
+        \item Advantages: A connection between user profile and IMP system enables all components to still use the user profile.
+The connection of a user profile to an IMP identity enables the system architecture to translate user profile interactions to IMP interactions.
+Users with existing user profiles can connect their IMP identity.
+        \item Disadvantages: 
+    \end{itemize}
+    \item Option 2 is chosen because it is less invasive
+    \item On the web page where users can create their user profiles, a relationship template can be displayed as QR code:
+    \begin{itemize}
+        \item Title: Create an OZG user profile
+        \item Attributes: Name, Surname, ... (all optional)
+        \item Shared Attributes: Administration Portal of the German state ...,
+        \item Reason: Create a user profile and connect your IMP identity.
+    \end{itemize}
+    \item If the system architecture receives the request, it checks the validity of the attributes, sends a response back and if the relationship is established, creates a new user profile and stores the mapping of the user profile and the IMP identity.
+    \item The attributes from the IMP identity to the user profile have to be mapped (maybe mention it here or just in the technology chapter)
+    \item Synchronize attributes of imp identity and user profile using attribute change request messages
+\end{itemize}
 
-The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
+\subsection{Login to User Profile}
+\begin{itemize}
+    \item Previously, the option 2 was chosen for creating a user profile.
+    \item Option 1: User can send messages through the relationship to the administration portal to interact with the system architecture.
+As the IP system guarantees secure communication, the requests can be assumed to originate from the correct user and be processed without further validation.
+    \item Option 2: The user can access OZG services through the web page.
+The web page can contain an additional QR code, which the IMP client can scan and interpret as login request.
+Through messaging over the relationship, the system architecture can be notified that the login request of the user connected to the IMP identity through the web page is valid.
+The system architecture can then send the appropriate cookie to the web browser of the user.
+    \item Both options can be used
+\end{itemize}
 
-Creation and management of multiple user profiles quickly becomes a burden for users.
-If all service providers would switch to using only identities provided by an IMP solution, users would only have to manage one digital identity.
-However performing this change is no simple task for a service provider.
-An abrupt change of the system architecture can lead to many problems like extended periods of down times.
-This integration architecture therefore focuses on a simplified initial integration of IMP identities where OZG user profiles can still be used to access OZG services.
+\subsection{Selection of Administrative Service}
+\begin{itemize}
+    \item This is no service directly related to identity management and remains to be accessible through the web page
+\end{itemize}
 
-It would be possible to integrate the IMP identity as an alternative to the user profile.
-The user could then use OZG services either by creating an OZG user profile or by providing an IMP identity.
-Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile.
-The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management.
-The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution.
-OZG systems would have to request personal information from the IMP identity while providing a reason for doing so.
-After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity.
-However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile.
-As the focus of this integration architecture is non invasiveness, the connection of IMP identity and user profile is preferred.
+\subsection{Filling in Application}
+\begin{itemize}
+    \item Option 1: Add option for using a relationship between IMP identity and administration portal for starting applications.
+    \item Option 2: Add option for using a relationship between IMP identity and institution for starting applications.
+    \item Option 3: Use the IMP client to send application requests as a IMP message
+    \item Option 3: Do not add IMP to this service.
+    \item Use Option 1 as it enables to fill in applications with IMP client and allows to track the sharing of personal information. Also simplifies the removal of user profiles later on.
+    \item Option 2 will be focus of advanced integration in chapter 6
+    \item On administrative service website add relationship template with QR code.
+    \begin{itemize}
+        \item Title: Apply for the administrative service XYZ
+        \item Attributes: Name, Surname, ... (all required)
+        \item Shared Attributes: Administration Portal of the German state ... or information about the institution which processes the application
+        \item Reason: Description of the administrative service
+    \end{itemize}
+    \item When receiving the request, the system architecture checks for validity of the request and accepts.
+After the relationship is established, it constructs the "old" application object and submits it to the data exchange platform
+    \item Mapping between FIM attributes and IMP attributes is very important here!!
+    \item The application can still be done as usual through the form server => those applications cannot be managed by the IMP client
+\end{itemize}
 
-The IMP solution provides a service for establishing a connection between entities.
-It is called an IMP relationship.
-Through a relationship, two entities can identify each other, assume authentication of the other party and can securely communicate and share attributes of their IMP identities.
-To utilize an IMP relationship between the administration portal and the IMP identity as connection between user profile and IMP identity, the relationship has to contain identification of the user profile in form of for example a user ID.
-The administration portal would then be able to map relationships along with the IMP identity ID to user profiles.
+\subsection{Submission of Application}
+\begin{itemize}
+    \item Is done by sending the relationship request
+\end{itemize}
 
-\subsection{Attribute Synchronization}
+\subsection{Reception of Application by Administration Portal}
+\subsection{Submission of Application to Data-Exchange Platform}
 
-The goal of the connection of IMP identity and OZG user profile is to enable management of personal information through the IMP client.
-Attributes stored as part of the IMP identity and attributes stored as part of the user profile have to be manageable through the IMP client.
-
-One option would be for the IMP client to overwrite all attributes of the OZG user profile with those stored in the IMP identity and update values in the user profile as soon as an attribute of the IMP identity changes.
-This would require the user profile management web page of the administration portal to be locked for profiles with a connected IMP identity.
-Another option would be to enable the user to manage attributes of IMP identity and user profile separately through the IMP client.
-
-The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically.
-However, this would require the user to always share the most current personal information with the OZG systems.
-Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider.
-If the user for example changes the birth date of its IMP identity, the OZG system might not want to approve this change immediately.
-Another option would be for the user to manage IMP identity and user profile separately.
-Changes of the OZG user profile can then happen on a request reply basis.
-The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there.
-The disadvantage of this option is, that the management of personal information is more complicated than the first option.
-Through attribute management tools on the IMP client, the experience can be improved.
-
-As the second option provides necessary features, which the first option does not have, it is preferred.
-
-The management of both IMP identity attributes and attributes of the OZG user profile can be done as part of the relationship established for their connection.
-As part of the connection, IMP identity and administration portal share attributes.
-The user profile can be determined to store the exact same values as shared by the IMP identity as part of this relationship.
-Therefore, in order to change attributes of the user profile, the value of the shared attributes has to change.
-This can be done through a request-reply process.
-One party requests the change of a shared attribute, which will only be done if the other party accepts.
-This enables the user to manage the OZG user profile through the IMP client by requesting a change for attributes shared as part of a relationship.
-The user could also manage his user profile through the web page of the administration portal, resulting in a request form the administration portal to change shared attributes of the relationship.
-
-\subsection{Login to a User Profile}
-
-The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal to access OZG services.
-As previously described, the integration architecture does not replace the OZG user profile.
-The user is therefore still able to login to his user profile on the administration portal and take advantage of all OZG services.
-The IMP system can however provide an additional way to access OZG services through the IMP client.
-One possibility was already introduced: the management of personal information.
-
-In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid.
-Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session.
-When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components.
-This process is necessary because any person can send requests to the web server and possibly pretend to be a different user.
-In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user.
-Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity.
-As the IMP client is an app installed on the device of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.
-
-\subsection{Application for Administrative Service}
-The third step is selection of an administrative service through the web page of the administration portal.
-This service is not directly related to identity management and will therefore not be provided by the IMP client.
-The steps four to eight are not integrated by the IMP solution as this would require invasive interaction with components other than the administration portal.
-
-As a result of that, most of the steps necessary for applying for an administrative service remain to be done through the web page of the administration portal with a logged in user profile.
-The next integration architecture will present a solution where most of the steps will be done through the IMP systems.
+\subsection{Management of Applications}
+\begin{itemize}
+    \item User can manage application through relationship: change attributes, cancel relationship
+\end{itemize}
 
 \subsection{Communication}
-
-The ninth step of the basic OZG use case is to communicate with responsible institutions.
-As both the user profile and the IMP identity provide an inbox, the IMP client can be used to send and receive messages through the inbox of the OZG user profile.
-
-The messages related to a OZG user profile can be exchanged as part of the relationship between the administration portal and the IMP identity.
-Messages received by the user profile can be forwarded by the administration portal to the inbox of the IMP identity.
-Sending messages from the IMP client to institutions however is not possible, as the IMP client does not know the address of the institution responsible for an application.
-However, if the IMP client already received a message from an institution, it can enable the user to respond.
+\begin{itemize}
+    \item User and institution can communicate through relationship.
+OZG system architecture knows which institution is processing which application and can forwards messages between IMP and OZG inbox.
+\end{itemize}

### 2021-02-09 sections/9-technological_integration.tex
integration solution notes

--- 2021-01-28 sections/9-technological_integration.tex
@@
-\subsection{Messaging}
-
-\subsection{Create User Profile}
-
-In order for an IMP identity to request a relationship with the administration portal, the portal has to provide a relationship template to the IMP client of the user.
-The template can be made accessible to the IMP client trough a new web page which displays the template ID as QR code if the user is logged in.
-Each time a logged in user requests the web page, the web server requests the IMP connector to create a relationship template.
-
-The IMP connector provides an API for creation of relationship templates as part of its REST interface.
-Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response.
-The web page of the administration portal can then render the template as a QR code on the web page.
+\begin{itemize}
+    \item Integration only with administration portal to be non invasive
+    \item Only one connector for the administration portal
+\end{itemize}
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template REST.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
 \end{figure}
 
-This is one example, where the OZG system could use the REST interface for integration with the IMP system.
-However, messaging can improve the integration solution to be more maintainable, stable and scalable and will be the preferred option in following scenarios.
-Using messaging, the web server can publish a message containing the request for a new relationship template on a "Relationship Template Request" channel, where the connector receives it, creates the template and publishes a reply message containing the template ID on the "Relationship Template Reply" channel.
+\subsection{Messaging}
+
+This section describes the advantages of using a message based integration approach.
+
+...
+
+\subsection{Modularity}
+
+\begin{itemize}
+    \item Use the Request-Reply methodology of the REST interface (only system sends requests, only connector sends replies) and expand it by a notification feature where only the connector sends notifications.
+    \item Make Request-Reply functionality accessible to the messaging system through system request and connector reply modules.
+    \item Make notification functionalities accessible to the messaging system through system notification and connector notification modules
+    \item Solutions presented in the previous chapter rely on relationships and messages therefore make relationships and messages accessible to the messaging system through system relationship and system message modules.
+Those modules both rely on request and notification modules.
+    \item To finally implement the features described in the previous chapter, multiple feature modules exist.
+    \item All modules besides those for the connector can exist in multiple configurations: A feature module for example requires a system relationship module which is configured to only send and receive special types of relationships
+    \item Examples
+    \begin{itemize}
+        \item Feature Module
+        \begin{itemize}
+            \item Attribute Change
+            \item IMP Identity Connection
+            \item Exchange mail
+        \end{itemize}
+        \item System Relationship Module
+        \begin{itemize}
+            \item Connection Relationship
+            \item Administrative Service Application Relationship
+        \end{itemize}
+        \item System Request Module
+        \begin{itemize}
+            \item Create Template
+            \item Send Relationship Response
+        \end{itemize}
+        \item System Message Module
+        \begin{itemize}
+            \item attribute change request
+            \item incoming mail
+        \end{itemize}
+        \item System notification module
+        \begin{itemize}
+            \item new message
+            \item relationship request
+        \end{itemize}
+    \end{itemize}
+\end{itemize}
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/0. Modules Overview.png}
 \end{figure}
 
-It could happen, that in future, the API of the connector changes.
-If the web server integrated the connector through its REST interface, this would require the request code of the web server to be changed.
-If messaging is used, messages leaving the "Relationship Template Request" channel could be mapped to the new API signature through an additional messaging component called message translator.
-This is an example for how a messaging can improve maintainability of an integration architecture.
+\subsection{Connector Integration}
+
+\begin{itemize}
+    \item 
+\end{itemize}
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Template Messaging Improved.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/1. Request-Reply.png}
 \end{figure}
-
-When the user is presented with the web page containing the QR code, the user can scan it with its IMP client.
-Based on the template ID, the client retrieves the template from the IMP server and displays it for the user.
-If the user accepts the template, the client sends a relationship request to the IMP server, who forwards it to the corresponding connector.
-
-Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request.
-If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request.
-The server would have to regularly request a status update which is not efficient.
-Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified.
-The administration portal can process the relationship request and publish a message containing a response on the "Relationship Response" channel, where the connector will be notified.
-Through the IMP server, the response server is routed to the IMP client and the relationship is established.
-In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Relationship Request.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/2. Multiple Systems.png}
 \end{figure}
-
-\subsection{Attribute Synchronization}
-
-As administration portal and IMP identity established a relationship, the connector can be excluded from the diagram for better visualisation.
-Behind the scenes, all interactions between administration portal and IMP client still go through connector and IMP server.
-
-If the user requests the change of a shared attribute through the IMP client, it sends an attribute change request to the administration portal by publishing a message on the "Inbound Attribute Change Request" channel.
-After the administration portal decides to accept the request, it can publish a message to the "Outbound Attribute Change Response" channel.
-This message will on one hand be received by the IMP client and on the other hand result in an update of the user profile.
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change IMP Client.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/3. Routing.png}
 \end{figure}
-
-If the user requests the change of a shared attribute through the web page of the administration portal, the web server sends an attribute change request to the "Outbound Attribute Change Request" channel which is received by the IMP client.
-If the user accepts the request, the client publishes a message on the "Inbound Attribute Change Response" channel where it results in an update of the user profile.
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Attribute Change Web Page.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/4. Routing Detail.png}
 \end{figure}
-
-\subsection{Login to a User Profile}
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/Overview/Login.png}
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/5. Proxy.png}
 \end{figure}
 
-\subsection{Communication}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/6. Integration Modules.png}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Technological Integration/Connector/7. Buffer Modularity.png}
+\end{figure}
+
+\subsection{Relationship Integration}
+
+\subsection{Message Integration}
+
+\subsection{Attribute Mapping}

### 2021-02-21 msc-thesis.tex
added second integration

--- 2021-01-28 msc-thesis.tex
@@
 \usepackage{float}
-
+\usepackage{wrapfig}
 \usepackage{subfiles} % Best loaded last in the preamble
+\usepackage{pdfpages}
 
@@
           {
-               \Large University of Heidelberg\\
+               \Large Universität Heidelberg\\
                \smallskip
@@
 
+\section{Identity Management Provisioning (IMP)}
+
+\subfile{sections/5-imp}
+
 \section{Online Access Law (OZG)}
 
-\subfile{sections/5-online_access_law}
+\subfile{sections/6-online_access_law}
+
+\section{Messaging}
+
+\subfile{sections/7-messaging}
 
@@
 
-\section{Functional Requirement Analysis}
+\subfile{sections/8-identity_management}
 
-\subfile{sections/6-requirement_analysis}
+\chapter{IMP Utilization in OZG}
 
-\section{IMP System Proposal}
+\subfile{sections/9-imp_utilization_in_ozg}
 
-\subfile{sections/7-imp_system_proposal}
+\chapter{Advanced Utilization}
 
-\chapter{Minimal Integration Architecture}
-
-The goal of the integration architecture is to make as many functionalities required for the basic OZG use case available through the IMP client as possible.
-As described in chapter 2.3, the steps of the basic OZG use case are:
-\begin{enumerate}
-    \item{Create User Profile}
-    \item{Login to User Profile}
-    \item{Selection of Administrative Service}
-    \item{Filling in Application}
-    \item{Submission of Application}
-    \item{Reception of Application by Administration Portal}
-    \item{Submission of Application to Data-Exchange Platform}
-    \item{Management of Applications}
-    \item{Communication}
-\end{enumerate}
-
-To enable service providers a quick introduction of IMP systems into their system architecture, this integration architecture describes a minimally invasive integration.
-After deployment of this integration architecture, all OZG services are still usable as before but can be enhanced by IMP solutions.
-For this integration to be minimally invasive, only one connector exists and integrates only with the administration portal.
-No other OZG system component is modified or directly accessed.
-
-The goal of the integration is to enhance each step of the basic OZG use case through integration with IMP solutions.
-Therefore in the overview section, for each step, possible integration's of OZG systems are evaluated.
-The following sections contain more detailed descriptions of the selected integration strategies.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 1/Overview.png}
-\end{figure}
-
-\section{IMP Solution Integration}
-
-\subfile{sections/8-imp_solution_integration}
-
-\section{Technological Integration}
-
-\subfile{sections/9-technological_integration}
-
-\chapter{Advanced Integration Architecture}
-
-The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client.
-Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.15]{Diagrams/Integration Architecture 2/Overview.png}
-\end{figure}
-
-\section{IMP Solution Integration}
+\subfile{sections/12-advanced_utilization}
 

### 2021-02-21 sections/10-imp_solution_integration.tex
added second integration

@@
-The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
-This is not necessary any more, as user profiles are replaced by IMP identities.
-The user will only have to create an IMP identity.
+This section describes integration possibilities on the solution layer.
+For each step of the basic OZG use case described in chapter 2, it is evaluated how the IMP system described in chapter 3 can be utilized to improve it.
 
-The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
-As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services.
-The IMP client does not require authentication, as it is installed on the smart phone of the user.
-The user can secure his smartphone through for example biometric authentication.
+\begin{enumerate}
+    \item{Create User Profile}
+    \item{Login to User Profile}
+    \item{Selection of Administrative Service}
+    \item{Filling in Application}
+    \item{Submission of Application}
+    \item{Reception of Application by Administration Portal}
+    \item{Submission of Application to Data-Exchange Platform}
+    \item{Management of Applications}
+    \item{Communication}
+\end{enumerate}
 
-The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.
+\subsection{Create User Profile}
+\begin{itemize}
+    \item User profile should not be replaced by IMP identity in order for OZG services to be accessible the same way
+    \item Connector can establish relationships and provides messaging capabilities
+    \item Option 1: Use an established relationship as alternative for a user profile
+    \begin{itemize}
+        \item Advantages: 
+        \item Disadvantages: All components of the system architecture would have to be able to separate between user profile and IMP identity processing and be able to interact with the IMP system.
+This would require modification of each system component and is too invasive.
+Users which already have a user profile cannot use it with their IMP identity.
+    \end{itemize}
+    \item Option 2: Use a relationship to create a user profile and connect it to the IMP identity
+    \begin{itemize}
+        \item Advantages: A connection between user profile and IMP system enables all components to still use the user profile.
+The connection of a user profile to an IMP identity enables the system architecture to translate user profile interactions to IMP interactions.
+Users with existing user profiles can connect their IMP identity.
+        \item Disadvantages: 
+    \end{itemize}
+    \item Option 2 is chosen because it is less invasive
+    \item On the web page where users can create their user profiles, a relationship template can be displayed as QR code:
+    \begin{itemize}
+        \item Title: Create an OZG user profile
+        \item Attributes: Name, Surname, ... (all optional)
+        \item Shared Attributes: Administration Portal of the German state ...,
+        \item Reason: Create a user profile and connect your IMP identity.
+    \end{itemize}
+    \item If the system architecture receives the request, it checks the validity of the attributes, sends a response back and if the relationship is established, creates a new user profile and stores the mapping of the user profile and the IMP identity.
+    \item The attributes from the IMP identity to the user profile have to be mapped (maybe mention it here or just in the technology chapter)
+    \item Synchronize attributes of imp identity and user profile using attribute change request messages
+\end{itemize}
 
-The fourth step of the basic OZG use case is to fill in the application.
-The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.
+\subsection{Login to User Profile}
+\begin{itemize}
+    \item Previously, the option 2 was chosen for creating a user profile.
+    \item Option 1: User can send messages through the relationship to the administration portal to interact with the system architecture.
+As the IP system guarantees secure communication, the requests can be assumed to originate from the correct user and be processed without further validation.
+    \item Option 2: The user can access OZG services through the web page.
+The web page can contain an additional QR code, which the IMP client can scan and interpret as login request.
+Through messaging over the relationship, the system architecture can be notified that the login request of the user connected to the IMP identity through the web page is valid.
+The system architecture can then send the appropriate cookie to the web browser of the user.
+    \item Both options can be used
+\end{itemize}
 
-The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more.
-Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.
+\subsection{Selection of Administrative Service}
+\begin{itemize}
+    \item This is no service directly related to identity management and remains to be accessible through the web page
+\end{itemize}
 
-For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template.
-The connector responds to the institution with the template IDs.
+\subsection{Filling in Application}
+\begin{itemize}
+    \item Option 1: Add option for using a relationship between IMP identity and administration portal for starting applications.
+    \item Option 2: Add option for using a relationship between IMP identity and institution for starting applications.
+    \item Option 3: Use the IMP client to send application requests as a IMP message
+    \item Option 3: Do not add IMP to this service.
+    \item Use Option 1 as it enables to fill in applications with IMP client and allows to track the sharing of personal information. Also simplifies the removal of user profiles later on.
+    \item Option 2 will be focus of advanced integration in chapter 6
+    \item On administrative service website add relationship template with QR code.
+    \begin{itemize}
+        \item Title: Apply for the administrative service XYZ
+        \item Attributes: Name, Surname, ... (all required)
+        \item Shared Attributes: Administration Portal of the German state ... or information about the institution which processes the application
+        \item Reason: Description of the administrative service
+    \end{itemize}
+    \item When receiving the request, the system architecture checks for validity of the request and accepts.
+After the relationship is established, it constructs the "old" application object and submits it to the data exchange platform
+    \item Mapping between FIM attributes and IMP attributes is very important here!!
+    \item The application can still be done as usual through the form server => those applications cannot be managed by the IMP client
+\end{itemize}
 
-In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address.
-After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.
+\subsection{Submission of Application}
+\begin{itemize}
+    \item Is done by sending the relationship request
+\end{itemize}
 
-If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it.
-The relationship template contains a description of the selected administrative service as reason for the relationship.
-The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application.
-This replaces the functionalities of the form server.
+\subsection{Reception of Application by Administration Portal}
+\subsection{Submission of Application to Data-Exchange Platform}
 
-The fifth step of the basic OZG use case is to submit the application.
-After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes.
-The institution can accept the request and start processing the application.
-The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.
+\subsection{Management of Applications}
+\begin{itemize}
+    \item User can manage application through relationship: change attributes, cancel relationship
+\end{itemize}
 
-The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.
-
-The eighth step of the basic OZG use case is the management of active applications.
-As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution.
-Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.
-
-The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications.
-As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.
+\subsection{Communication}
+\begin{itemize}
+    \item User and institution can communicate through relationship.
+OZG system architecture knows which institution is processing which application and can forwards messages between IMP and OZG inbox.
+\end{itemize}

### 2021-02-21 sections/11-technological_integration.tex
added second integration

\begin{itemize}
    \item Integration only with administration portal to be non invasive
    \item Only one connector for the administration portal
\end{itemize}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Overview.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
\end{center}

System architecture of the SP and IMP system consist of multiple components. The administration portal component of the system architecture is the component which will interact with the integration system. The administration portal contains a web server and a service facade. The service facade enables the administration portal amongst other things to access the user profile component.

On the side of the IMP system, the connector will interact with the integration system.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Overview.pdf}
\end{center}

The integration is constructed as a messaging system. The messaging system consists of modules which exchange messages with connector and administration portal. As administration portal and connector are not able to send, receive or understand messages, a messaging adapter is attached to both systems. A messaging adapter is software which provides an API to the system hiding the operation of the messaging system. Depending on the system the messaging adapter should be attached to, different integration methods can be used. In most cases however, manual modification of the programming of the system is necessary to utilize the API of the adapter.

The integration system consists of messaging modules, each of them solving a different integration task. The modular approach enables the integration system to be easily expandable by new features trough new modules. Assigning integration tasks to modules also improves maintenance. System administrators can update a feature by modifying and expanding the corresponding component.
Modules can be designed to be reusable by other components which reduces the development time for new features and the size of the integration system. If the modules supports it, the performance of the integration system can be dynamically scaled by adding multiple module instances.

Modules have the purpose of solving integration tasks by providing access to features presented in section 5.1 while hiding the complexity of the operation of the IMP system. Modules therefore exchange messages through three types of publish-subscribe channels. Between administration portal and modules, feature channels are used. On these channels, messages strongly related to the operation of the system architecture of the service provider are exchanged. This are for example messages for requesting services like the transmission of a mail.

Between modules and connector, connector channels are used. These are a predetermined and limited set of channels which are used by the messaging adapter to map the functionalities of the connector to the messaging system. Messages exchanged on these channels are strongly related to the operation of the IMP system. This are for example requests and replies for relationships and templates.

Between modules, intermodule channels are used to exchange messages. Modules can exchange messages in order to access distributed functionalities of other modules.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
\end{center}

As described in section 5.1, the user should be able to create a new user profile for the OZG system through an existing IMP identity.

On the existing website of the administration portal, where users can create a user profile, the relationship template for onboarding should be displayed. When the web server receives a GET request for the profile creation website, it issues a request to the messaging system for a new onboarding template. The messaging system interacts with the IMP connector to construct the template and send it back to the web server. The web server renders the template as a QR code. The QR code is displayed on the device of the user who can use the IMP client to scan it and initiate a relationship request. The messaging system interacts with the connector to establish the relationship and eventually issues the service facade to create a new user profile based on the attributes shared as part of the IMP relationship. After successful creation of the user profile, the messaging system stores the relationship ID and the user profile ID in a database. In the future, each request containing either a user profile ID or relationship ID can be mapped to the correct OZG and IMP identities. The messaging system notifies the web server of the successful creation of the user profile and the web server displays a corresponding notification to the user.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
\end{center}

\begin{itemize}
    \item Web Server has messaging adapter with API for retrieving onboarding template

    \item Connector has messaging adapter with API for creating templates

    \item Onboarding Template Module exists, which manages the exchange of request and reply messages

    \item Module exchanges messages with web server adapter through request and reply channel. Only this module and the adapter of the web server use the channels.

    \item Module exchanges messages with connector adapter through request reply channel. Multiple different modules can use the channels.

    \item Config Enricher adds suitable configuration as new entry to request

    \item Configuration is stored in a database or file. An administrator maintains the configuration

    \item The configuration creates a relationship template used to create a user profile. The configuration has to define the template to require attributes necessary for creating a user profiles.

    \item Attribute names and meaning can differ between OZG user profile and IMP identity, the configuration has to use the attribute definition of the IMP system.

    \item Config Message Translator incorporates the metadata entry to the template configuration

    \item Adapter Message Translator incorporates mapping of possible future changes of adapters in for example attribute naming or attribute data types (this type of message translator can be added to every channel connected to an adapter and is therefore excluded in future visualizations)

    \item Module filters for templates of the onboarding type as the channel could contain responses with templates of different type for other modules.

\end{itemize}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/6. Onboarding Template Module.pdf}
\end{center}

Eventually, the user sends a relationship request which will be processed by the "Onboarding Request Module"

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/7. Onboarding Request Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Attribute Change Message Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Request Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Onboarding Relationship Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. User Profile Attribute Sync Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Mail Message Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. Mail Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Authenticatin Message Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Authentication.pdf}
\end{center}

### 2021-02-21 sections/12-advanced_utilization.tex
added second integration

The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.

\section{IMP Solution Integration}

\subfile{13-imp_solution_integration}

\section{Technological Integration}

\subfile{14-technological_integration}

### 2021-02-21 sections/13-imp_solution_integration.tex
added second integration

\begin{itemize}
    \item The goal of this advanced integration is to take full advantage of IMP features

    \item The integration now focuses not only in the system architecture of the administration portal but also of the institutions

    \item A disadvantage of the previous integration solution is, that the administration portal maintains user profiles. This results in a duplication of user data management systems (IMP system and user profile system). In addition, trough the user profiles, the administration portal has access to personal information without the need for processing but routing it. This is a data protection issue.

    \item As institutions are the entities which eventually need to process personal information, personal information should only be shared with them.

    \item Using a IMP connector, institutions can establish relationships with users while the relationship represents the application for an administrative service.

    \item The institution does not maintain a identity management system in addition to the IMP system: An application is started being processed after the relationship is established and further communication regarding the application is done through the relationship. If the application is finished, the relationship is terminated, removing access to personal information for the institution.

    \item Institutions are capable of processing multiple administrative services. Each service has its own purpose, description and personal information required by the user. For each service, the institution processes, individual relationship templates can be created.

    \item In order for users to determine which institution is responsible for processing their request and for accessing the correct relationship template, the administration portal can be used as a "search-engine"

    \item The user searches for a administration service on the website of the administration portal and specifies the location he lives in. The administration portal determines the responsible institution and retrieves the correct relationship template from it.

    \item Based on the template, the user now interact only with the institution to apply for a service. The administration portal does not receive any further personal information.

    \item By requesting to change attributes of established relationships the institutions can process modifications of the request and decide if they accept or deny the request.

    \item As there is no standard for how the system of an institution operates, the integration can follow the integration of the administration portal by constructing a "form" from the shared personal information and enabling to deliver it in all kinds of formats through an adapter

    \item However, to further demonstrate the integration capabilities, the integration presents a possible integration for enabling application management through an E-Mail server on the institution side.

    \item Incoming applications can be sent as an E-Mail to employees assigned to a certain type of request. The relationship ID can be used as a reference ID in the title of the relationship or as a "spoofed" email sender. Further communication like attribute change requests can follow the same style and be aggregates by any email client to display all messages with the same reference ID.

    \item This method of applying for administrative services completely removes the need for administration portal and institution to maintain user profiles. It also enables users to share personal information only with entities which really need to process it. By enabling institution and user to directly interact, changes of the request content, status updates and exchange of mails can be done easily.

    \item Integration aufbauend auf erster oder ersetzend??

    \item Messaging architektur aus 1 genau so applizierbar in advanced integration

    \item im stil der overview der integrationen auch das connection diagram des OZG systems beschreiben. User Domain, Portal Domain, FIM Domain, Institution Domain, Data Exchange Domain

    \item basic use case umsetzen durch IMP trotz ablösen von 3 vorher existierenden domänen

    \item in diagrammen aufzeigen wo persönliche daten verarbeitet werden

    \item datenverabeitung vergleich zwischen diagrammen

    \item offen ob man andere domänen abschaltet (übergangszeit anlassen)

\end{itemize}

### 2021-02-21 sections/14-technological_integration.tex
added second integration

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Integration Overview.pdf}
\end{center}

### 2021-02-21 sections/4-terminology.tex
added second integration

@@
 They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.
-
-\section{Identity Management Provisioning (IMP)}
-Identity management provisioning (IMP) is a method for identity management which is characterized by an identity management provider hosting an identity management system for "non-partial" identities.
-The identity management system provides one-stop online self-service for users and manages the storage of identities.
-SPs are provided access to the identities of the identity management system.
-
-The following are functionalities of an IMP system in addition to those of conventional identity management systems:
-
-\paragraph{Attribute Management}
-It is common for identity management systems to enable users to manage a predetermined set of attributes.
-IMP systems however do not just manage partial identities and therefore enable users to manage any possible attribute of their identity.
-Users therefore can add, remove and modify any attribute.
-
-As often, attributes of a digital identity are defined by service providers, they are also able to create new attributes or delete and modify existing ones, if approved by the user.
-
-\paragraph{Online Self-Service}
-Many attributes, especially those created by SPs, do not make sense to the user without context and my be heavily dependant on systems of a SP.
-Therefore, the IMP provides solutions for online self-service which supports the management of attributes.
-
-\paragraph{Integration}
-Service providers which use IMP systems as solution for identity management require access to its services and have to make their existing systems work with them.
-The IMP solution therefore provides interfaces which enable the SP to access services.
-As it is in the best interest of the IMP solution to integrate SPs, advanced integration methods reducing the integration effort for SPs can be provided.

### 2021-02-21 sections/5-imp.tex
added second integration

--- 2021-02-06 sections/7-imp_system_proposal.tex
@@
-There exist many ways to realize an IMP system.
-Based on the previously analyzed requirements of users and service providers, a possible solution for an IMP system is presented.
-The purpose of this chapter is not to give a detailed explanation of the presented IMP system but to deliver a brought understanding of the concepts, features and components involved.
+\begin{itemize}
+    \item IMP hosts systems for identity management and provides access to users with an application and to service providers with integration tools
+    \item Users can create an identity and manage attributes (key-value pairs)
+    \item Users and service providers can establish relationships and use them to securely share personal information and exchange structured data
+\end{itemize}
+
+\begin{itemize}
+    \item Ease of Use: Users only need to manage one online identity which can be accessed by multiple service providers
+    \item Data protection: Users can control which service providers get access to which attributes
+    \item Bidirectional Communication: Service providers and users can directly communicate with each other by exchanging structured data their tools have a common understanding of.
+    \item User Interaction: The user application can display various user interfaces based on the content of exchanged structured data.
+    \item Data Abuse Protection: Service providers are only supplied with necessary personal information which minimizes the possibilities of abuse by the service provider or in case of a data breach.
+    \item Communication Security: Attributes communicated structured data are securely exchanged.
+User and service provider can therefore also directly exchange sensible information.
+This is not possible for example through e-mail
+\end{itemize}
+
+The purpose of the following sections is not to give a detailed explanation of the presented IMP system but to deliver a brought understanding of the concepts, features and components involved.
 
@@
 
-\paragraph{Tooling} The IMP system provides users and service providers with software tools for accessing its features.
+\paragraph{Applications} The IMP system provides users and service providers with software tools for accessing its features.
 The user is provided with a user friendly application while the enterprise is provided with tools for integration.
@@
 \end{figure}
+
+\section{}

### 2021-02-21 sections/8-identity_management.tex
added second integration

\section{Identity Management in OZG}
Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities. In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles. Each member state has to provide its own user profile system which can be utilized through every administration portal. This solution is expensive to develop and maintain, as cooperation of multiple member states and institutions is required.

If every member state integrated IMP, users could access all administrative services through on IMP identity. Member states would not need to coordinate the operation of their user profile systems but independently access personal information through the IMP system.

Users are required to create and maintain multiple user profile, the user profile of the OZG being yet another one. Changing personal information is a time consuming task with with an increasing number of user profiles and login credentials.

Multiple service providers accessing personal information through the IMP identity of a user would enable the management of personal information in one place.

Possibilities of interaction with the user to for example notify him about the status of an application are limited as no information which requires a high authentication level can be transmitted via E-Mail.

Through the IMP client, direct interaction with the user is possible. The user can not only receive notifications but directly respond without the need for visiting a website and logging in.

With a large number of user profiles the risk of forgetting passwords and the possibility of users using the same password multiple times increases.
Using the IMP client to access services, no authentication through a username and password combination is required as the application is installed on a secured smartphone.

\section{Integration Challenges}

This chapter describes challenges for integrating the IMP system described in chapter 3 into the OZG system architecture. The quality of the presented integration can be determined based on the number of the following challenges it solves.

\subsection{IMP Challenges}
This section describes challenges which arise from the operation of the IMP system

\begin{itemize}
    \item Connector has REST interface and cannot notify system architecture
    \item Connector does not understand messages
    \item Messages can have different versions
    \item API of connector can change
    \item New types of messages can be added by the client and the system provider might need to understand them
\end{itemize}

\subsection{SP Challenges}

This section describes challenges which arise from service provider integration requirements.

\begin{itemize}
    \item Minimal modification of existing systems
    \item Maintainability
    \item Scalability
    \item Failure Handling
    \item Administration
    \item Extendability
    \item Modularity

\end{itemize}

\subsection{OZG Challenges}

This section describes challenges which arise from OZG integration requirements.

\begin{itemize}
    \item Administration portal has access to all personal information
    \item Once an application is submitted, its attributes cannot be changed
    \item Mapping of IMP attributes and FIM data blocks
\end{itemize}

### 2021-02-21 sections/9-imp_utilization_in_ozg.tex
added second integration

Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities. In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles. Each member state has to provide its own user profile system which can be utilized through every administration portal. This solution is expensive to develop and maintain, as communication between multiple member states and institutions is required.

Goal of the integration solution is to introduce features of the IMP system into the OZG system architecture. All existing services should be accessible the same way as before but with additional options for using IMP. The focus of this initial integration is to avoid disruption of existing system operation through non-invasive integration, to enable a fast and simple introduction of IMP features and to provide future upgrade capabilities. The integration takes place on three layers:

\begin{figure}[h]
\caption{IMP Layer Diagram}
    \centering
    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.png}
\end{figure}

\paragraph{IMP Solution Integration Layer} 
The purpose of the integration on the IMP solution layer is to take advantage of new interaction capabilities with the user through the IMP system. The integration evaluates possibilities of using relationships and IMP messages to improve OZG services, defines what the purpose of each message and relationship type is and how they should be handled by client and service provider. For example relationship templates can be defined and new message types can be created with corresponding new user interfaces in the IMP client.

\paragraph{Relationship Integration Layer} The purpose of the integration on the relationship layer is to enable the technological utilization of relationships as described by the integration on the solution integration layer.

\paragraph{Communication Integration Layer} The purpose of the integration on the communication layer is to enable the technological utilization of messages as described by the integration on the solution integration layer.

\section{IMP Solution Integration}

\subfile{10-imp_solution_integration}

\section{Technological Integration}

This section evaluates possibilities of a technological integration architecture for realizing the integration solution described in the previous section.

\subfile{11-technological_integration}

### 2021-02-26 msc-thesis.tex
added textual descriptions

@@
           {
-               \Large Universität Heidelberg\\
+               \Large Ruprecht-Karls-Universität Heidelberg\\
                \smallskip
-               \Large Institute for Computer Science\\
+               \Large Institut für Informatik\\
                \smallskip
-               \Large Working group database systems\\
+               \Large Lehrstuhl für Datenbanksysteme\\
                \smallskip
@@
 
-          \textbf{\large Bachelor thesis}
+          \textbf{\large Bachelor Arbeit}
 
@@
                Name:                 & Jonas Gann              \\
-               Matriculation number: & 3367576                 \\
-               Supervisor:           & Prof. Dr. Michael Gertz \\
-               Date of submission:   & \today
+               Matrikelnummer: & 3367576                 \\
+               Betreuer:           & Prof. Dr. Michael Gertz \\
+               Datum der Abgabe:   & \today
           \end{tabular}
@@
 \noindent
-I assure that I have written this bachelor thesis on my own and only used the specified sources and resources and that I followed the principles and recommendations "Responsibility in Science" of the University of Heidelberg.
+Ich versichere, dass ich diese Bachelorarbeit selbstständig verfasst und nur die angegebenen Quellen und Hilfsmittel verwendet habe.
 
@@
 
-\chapter{Identity Management}
+\chapter{OZG Identity Management}
 

### 2021-02-26 sections/10-imp_solution_integration.tex
added textual descriptions

--- 2021-01-28 sections/10-imp_solution_integration.tex
@@
-The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
-This is not necessary any more, as user profiles are replaced by IMP identities.
-The user will only have to create an IMP identity.
+This section describes integration possibilities on the solution layer.
+Although the eventual goal of an IMP integration is to replace user profiles, in this case, IMP identity and user profiles will be used together to solve issues described in chapter 3 without disrupting the operation of the existing system architecture.
+The advanced integration in chapter 5 will present a more invasive solution.
 
-The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
-As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services.
-The IMP client does not require authentication, as it is installed on the smart phone of the user.
-The user can secure his smartphone through for example biometric authentication.
+The presented solution enables users to access OZG services by connecting user profiles to existing IMP identities.
+Operations performed on the IMP identity will then be synchronized with the connected user profile.
 
-The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.
+\subsection{Create User Profile}
+One way to connect user profile and IMP identity is by creating a new user profile based on an existing IMP identity.
+The web page of the administration portal responsible for guiding the user through the user profile creation steps can present an additional option of creating a user profile called "Login using IMP Identity".
+A relationship template can be displayed in form of a QR code with the following content:
 
-The fourth step of the basic OZG use case is to fill in the application.
-The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.
+\begin{itemize}
+    \item Title: Create OZG User Profile
+    \item Attributes: Name, Surname, ... 
+    \item Shared Attributes: Administration Portal of the member state ...
+    \item Reason: Create an OZG user profile and connect your IMP identity.
+\end{itemize}
 
-The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more.
-Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.
+The user can scan the QR code using his IMP client and is presented with the relationship template.
+As part of the template, the user is requested to share attributes which thee IMP client can automatically fill in if they already exist.
+The attributes requested as part of the template have to be sufficient for creating an OZG user profile.
+The user is also presented with an explanation for what the purpose of the relationship is and why the specified attributes are required.
+If the user accepts, a relationship request can be sent to the administration portal, where the attributes can be analyzed.
+Depending on the result of the analysis, the relationship can be accepted and therefore established or rejected.
+Once the relationship is established, the OZG system architecture can create a new user profile based on the shared attributes and store the connection of user profile and IMP identity.
 
-For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template.
-The connector responds to the institution with the template IDs.
+\subsection{Authentication}
+Communication between IMP system and administration portal can assumed to be secure: Messages originating from an IMP identity for an IMP relationship can not be accessed or modified by a third party and are authorized by the corresponding user.
+Therefore messages exchanged as part of the established relationship can be used to provide the IMP identity access to OZG services.
+Some examples for this are shown in the following sections.
 
-In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address.
-After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.
+\subsection{Login to User Profile}
+Messages trough the established IMP relationship can be used to enable the user to access OZG services through the existing web page, by using the IMP client for authentication.
+After receiving a login request for a user profile on the web page of the administration portal, an authentication request containing the session ID can be sent to the IMP relationship corresponding to the user profile.
+The IMP client can display an appropriate notification with options for the user to accept or reject the request.
+The IMP client sends the result back to the administration portal which according to the response authenticates the browser session or not.
 
-If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it.
-The relationship template contains a description of the selected administrative service as reason for the relationship.
-The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application.
-This replaces the functionalities of the form server.
+\subsection{Attribute Synchronization}
+Modifications of the personal information stored in the user profile can be done by exchanging messages trough the established IMP relationship.
+Through the IMP client, the user can send an attribute change request regarding the relationship.
+The system architecture can map the relationship to the connected user profile, evaluate the request and if accepted, perform the modification of personal information.
+It is possible to enable the user to update attributes of his user profile trough the web page which would require the OZG system to send attribute change requests to the IMP client.
+For simplicity, this option is left out and the profile management web page is expected to be inaccessible for user profiles connected to IMP.
 
-The fifth step of the basic OZG use case is to submit the application.
-After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes.
-The institution can accept the request and start processing the application.
-The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.
+\subsection{Communication}
+Messages sent to the inbox of the user profile can be forwarded to the inbox of the IMP identity.
+As the exchange of messages through the IMP system is secure, also security relevant information can be shared.
 
-The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.
-
-The eighth step of the basic OZG use case is the management of active applications.
-As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution.
-Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.
-
-The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications.
-As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.
+\subsection{Application}
+To minimize the invasiveness of the integration, applications for administrative services remain to be done on the administration portal trough user profiles.

### 2021-02-26 sections/11-technological_integration.tex
added textual descriptions

@@
-\begin{itemize}
-    \item Integration only with administration portal to be non invasive
-    \item Only one connector for the administration portal
-\end{itemize}
-
 \begin{center}
@@
 
+For the existing system architecture to access the IMP system, an IMP connector is added to the portal domain.
+The connector communicates with an IMP client trough the IMP server located in the IMP domain.
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Overview.pdf}
 \end{center}
@@
 System architecture of the SP and IMP system consist of multiple components.
-The administration portal component of the system architecture is the component which will interact with the integration system.
+The administration portal component of the system architecture  will interact with the integration system.
 The administration portal contains a web server and a service facade.
 The service facade enables the administration portal amongst other things to access the user profile component.
-
 On the side of the IMP system, the connector will interact with the integration system.
@@
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
 \end{center}
@@
 Assigning integration tasks to modules also improves maintenance.
-System administrators can update a feature by modifying and expanding the corresponding component.
+System administrators can update a feature by modifying and expanding the corresponding module.
 Modules can be designed to be reusable by other components which reduces the development time for new features and the size of the integration system.
-If the modules supports it, the performance of the integration system can be dynamically scaled by adding multiple module instances.
+If the modules supports it, the performance of the integration system can be dynamically scaled by adding more module instances.
 
 Modules have the purpose of solving integration tasks by providing access to features presented in section 5.1 while hiding the complexity of the operation of the IMP system.
-Modules therefore exchange messages through three types of publish-subscribe channels.
+They exchange messages through three types of publish-subscribe channels.
 Between administration portal and modules, feature channels are used.
@@
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
 \end{center}
@@
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
-\end{center}
-
-\begin{itemize}
-    \item Web Server has messaging adapter with API for retrieving onboarding template
-
-    \item Connector has messaging adapter with API for creating templates
-
-    \item Onboarding Template Module exists, which manages the exchange of request and reply messages
-
-    \item Module exchanges messages with web server adapter through request and reply channel. Only this module and the adapter of the web server use the channels.
-
-    \item Module exchanges messages with connector adapter through request reply channel. Multiple different modules can use the channels.
-
-    \item Config Enricher adds suitable configuration as new entry to request
-
-    \item Configuration is stored in a database or file. An administrator maintains the configuration
-
-    \item The configuration creates a relationship template used to create a user profile. The configuration has to define the template to require attributes necessary for creating a user profiles.
-
-    \item Attribute names and meaning can differ between OZG user profile and IMP identity, the configuration has to use the attribute definition of the IMP system.
-
-    \item Config Message Translator incorporates the metadata entry to the template configuration
-
-    \item Adapter Message Translator incorporates mapping of possible future changes of adapters in for example attribute naming or attribute data types (this type of message translator can be added to every channel connected to an adapter and is therefore excluded in future visualizations)
-
-    \item Module filters for templates of the onboarding type as the channel could contain responses with templates of different type for other modules.
-
-\end{itemize}
-
-\begin{center}
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/6. Onboarding Template Module.pdf}
@@
 
-Eventually, the user sends a relationship request which will be processed by the "Onboarding Request Module"
+To present an onboarding relationship template to the user, the web server first has to retrieve it from the integration system.
+For this purpose, an "Onboarding Template Module" is added to the messaging system.
+Using the API of a messaging adapter provided in addition to the module, the web server can request the creation of new onboarding templates.
+Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template.
+In this case, the web server will want to notify the user about the successful creation of his user profile.
+The web server therefore adds the users current session ID as metadata to the template.
+
+The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests and the "Onboarding Template Response" channel, where it listens for responses.
+In order for the adapter to correlate request and reply messages, it creates a message which besides the Template Metadata contains a request ID.
+This ID is expected to be included in the response message.
+The message ID is a unique identifier and is part of every message.
+The module consumes messages from the "Onboarding Template Request" channel and adds an configuration object stored at a database.
+This configuration contains information on how relationship templates of type onboarding are supposed to look like.
+It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more.
+If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited.
+
+Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity.
+Therefore, all attributes which are required to create a user profile have to be requested by the template.
+As the data model of the OZG systems and IMP systems are different, message translators will have to be used to translate between them.
+Therefore, most modules will contain a component called "Attribute Mapping" which is responsible for translating the attribute definitions of the IMP system to attribute definitions of the OZG system and vice versa.
+In this model however, no message translator is required, as the configuration of the template can be defined to use the IMP data model.
+
+A message translator combines template metadata and configuration to a configuration object, the connector understands and publishes it on the "Template Request" channel.
+
+The messaging adapter of the connector issues the appropriate REST request to the connector and publishes the resulting template along with the request ID on the "Template Response Channel".
+As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.
+
+The messaging adapter returns the template to the web server, which based on the session ID in the template metadata can display the template as QR code to the user.
 
@@
 
+Eventually, the user scans the QR code, fills in the attributes and submits a relationship request.
+The request is received by the connector, forwarded to the messaging adapter and published on the "Relationship Request" channel.
+The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship.
+It also contains the request content with attributes shared by the user and the template the request originated from.
+Messages on the "Relationship Request" channel are consumed by the "Onboarding Request Module".
+A message filter only lets messages trough which contain templates of type onboarding.
+A message translator translates attributes shared by the user from the IMP data model to the OZG data model and publishes the message on the "Onboarding Request" channel.
+
+Based on the attributes the user shares, the OZG system has to decide if the relationship should be established or not.
+As this process heavily depends on the use case of the relationship and on the service provider, the messaging system expects the SP to add a module called "Onboarding Request Processing Module" which consumes the request and responds with either approve or reject on the "Onboarding Response" channel.
+To correlate the response to the request, the message also has to contain the relationship ID.
+The "Onboarding Request Module" forwards the response to the "Relationship Response" channel, where the connector will further interact with the IMP system to either establish or cancel the relationship.
+In between a message translator can, if required, translate the format of the response attribute so that the connector understands it.
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Attribute Change Message Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
 \end{center}
 
+If the user did not retract his relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification which the messaging adapter publishes on the "Relationship Established" channel.
+The message contains the ID of the established relationship along with all attributes shared by the user.
+The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships.
+In this case, the module only processes the establishing of relationships, it could however be expanded to also process terminations of relationships.
+
+The module processes an established relationship by initiating the creation of a new user profile.
+First, a message filter lets trough only messages of the onboarding type.
+Afterwards, each message is stored in a "Relationship Storage" database and published on the "Create User Profile Request" channel.
+However, before publishing the message, attributes are again mapped form the IMP data model to the OZG data model.
+
+To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content.
+After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created Profile ID.
+
+As responses to requests from other modules might be published on this channel, the "Onboarding Relationship" module filters all messages which do not contain a relationship ID stored in the "Relationship Storage".
+The rest of the messages is stored in a "Profile ID / Relationship ID Mapping" database.
+
+This database is used trough intermodule communication to map profile IDs to relationship IDs and vice versa.
+Modules can publish messages on the "Identity Mapping Request" channel either containing a relationship ID or profile ID attribute and receive the message containing both profile ID and relationship ID on the "Identity Mapping Response" channel.
+Using messaging for this form of database access enables modules to stay unaware of the complexities of the underlying data storage mechanisms.
+An alternative would be for modules to use the database as a shared database.
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Request Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Message Module.pdf}
 \end{center}
 
+For the messaging system to process messages being exchanged as part of relationships, message modules can be added.
+Their purpose is to map messages of certain types on the "Message Inbound" channel to individual message type channels so that modules can process them.
+They also map messages of the individual message type channels to the "Message Outbound" channel to so that the connector can submit them.
+
+In this case, an "Attribute Change Message Module" is included, which processes messages related to the attribute change process of onboarding relationships.
+The connector receives a message corresponding to a relationship ID which the messaging adapter publishes on the "Message Inbound" channel.
+The message contains the ID of the relationship it was exchanged trough, an identification of the message type and the content of the message.
+Message type and content can be freely specified by the IMP client, however only certain message types are understood by message modules and only certain message contents can be processed by the integration system.
+The integration architecture will therefore have to adhere to the standard the IMP client specifies and adapt to possible future changes.
+
+The "Attribute Change Message Module" consumes messages on the "Message Inbound" channel and filters all messages with types not related to attribute change.
+A message translator translates incoming message types to types the integration architecture can processes.
+This can be necessary, if for example the IMP client changes definitions of message types.
+A message router routes the messages to different channels depending on their type.
+In this case, two types of incoming messages can be processed on the "Attribute Change Request" channel and on the "Attribute Change Established" channel.
+To expand the list of message types the integration architecture can process, corresponding channel can be added.
+
+Before publishing messages on the channels, a message translator translates the message content to a format, the integration architecture understands.
+This might be possible if in the future, the IMP client changes the format.
+A content filter removes unnecessary content from the message such as the message type, as modules will be able to infer it from the channel a message is published on.
+
+The module is also able to process outbound messages originating from one of the modules.
+In this case, messages can arrive on the "Attribute Change Response" channel.
+A content filter removes unnecessary attributes attached to the message.
+In order to adapt to changes in the response format the IMP client understands, a message translator is attached.
+For the IMP client to understand the message, the implicit message type of the channel has to be added aThe module s an attribute.
+The resulting message is then published on the "Message Outbound" channel, where the messaging adapter instructs the connector to submit it.
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Onboarding Relationship Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Attribute Change Request Module.pdf}
 \end{center}
+
+To process incoming attribute change requests for profiles, a "Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel.
+To retrieve the user profile ID connected to the relationship ID, an incoming message is forwarded to the "Identity Mapping Request" channel.
+To eventually correlate the reply to the request, a content enricher adds a request ID to the message and stores the ID in a "Request ID Store".
+
+Replies on the "Identity Mapping Response" channel which do not contain a request ID stored in the "Request ID Store" are filtered.
+The other messages are consumed by a message translator which, such as in previous modules, maps attributes shared as part of the attribute change request from the IMP data model to the OZG data model an publishes the message on the "Attribute Change Request" channel.
+
+Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the service provider.
+Therefore, the SP is expected to include an "Attribute Change Processor" module, which based on the attribute change request, the relationship ID and the profile ID decides to approve or reject.
+The response is published to the "Attribute Change Response" channel and besides the response content contains the relationship ID.
+
+The "Profile Attribute Change Request" module forwards the message to the "Attribute Change Response" channel, where the message module will further process it for delivery to the connector.
 
@@
 
+If the user did not cancel the attribute change request before the OZG system accepted, the attribute change is established.
+The connector is notified trough a message, which eventually the "Profile Attribute Change Message" module described earlier will process and publish on the "Attribute Change Established" channel.
+
+The "User Profile Attribute Sync" module consumes messages from the "Attribute Change Established" channel and similar to the "Profile Attribute Change Request" module, retrieves the profile ID corresponding to the relationship ID.
+Before publishing the response on the "User Profile Attribute Change" channel, the attributes are again translated from the IMP data model to the OZG data model.
+A channel adapter connected to the service facade consumes the message and updates the specified attributes for the specified user profile.
+
 \begin{center}
@@
 \end{center}
+
+In order for the user to receive messages sent to his user profile trough the IMP client, mail messages are processed by the integration architecture.
+Similar to the "Profile Attribute Change Message" module, a "Mail Message" module is included, which maps messages on the "Mail Outbound" channel to the "Message Outbound" channel.
+
+In this module, incoming mails from the IMP client could also be processed, however this option is not included in the integration.
+
+Trough a content filter, the module removes unimportant attributes from the message.
+A message translator is sued to translate the mail format of the user profile inbox to the format of the IMP client inbox.
+Eventually, a content enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it and publishes it on the "Message Outbound" channel.
 
@@
 
+An messaging adapter attached to the service facade is notified each time, a user profile connected to an IMP identity receives a mail and publishes a message on the "Profile Mail Outbound" channel.
+The message contains the ID of the profile which received the message and the content of the mail.
+A "Mail" module is included which consumes the messages from the "Profile Mail Outbound" channel, retrieves the corresponding relationship ID, similar to previous modules, and publishes them on the "Mail Outbound" channel.
+The messages on the "Mail Outbound" channel are processed by the "Mail Message" module described earlier.
+
 \begin{center}
@@
 
+If the user creates a user profile using his IMP identity, it is possible to replace authentication using a password with authentication trough the IMP client.
+It is also possible to use the IMP client for two factor authentication.
+
+In order to send and receive messages related to authentication, similar to previous message modules, a "Authentication Message" module is included which maps incoming messages on the "Message Inbound" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.
+
 \begin{center}
@@
 \end{center}
+
+When the user visits the web page of the administration portal to apply for an administrative service, he will have to login.
+To utilize the IMP client for authentication, the web server can use a channel adapter to publish a authentication request concerning a user profile ID and a certain session ID.
+The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content.
+Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser.
+Similar to previous modules, the relationship ID connected to the profile ID is retrieved and the response published on the "Authentication Request Message, where the "Authentication Message" module further processes the message and sends it to the connector.
+
+Eventually, the IMP client sends a response as message, which the "Authentication Message" module publishes on the "Authentication Response" channel.
+As the message module already appropriately formatted the response content, the "Authentication" module can simply forward the message to the "Authenticated" channel.
+The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.

### 2021-02-26 sections/12-advanced_utilization.tex
added textual descriptions

@@
-The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client.
-Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.
+The goal of the advanced IMP utilization for OZG is to improve upon the solution presented in chapter 4 while allowing it to be modify and replace large portions of the existing system architecture.
 
@@
 \subfile{14-technological_integration}
+
+\subsection{Solution Evaluation}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Personal Information Existing Architecture.pdf}
+\end{center}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Overview.pdf}
+\end{center}
+
+\begin{itemize}
+
+    \item Integration aufbauend auf erster oder ersetzend??
+
+    \item Messaging architektur aus 1 genau so applizierbar in advanced integration
+
+    \item im stil der overview der integrationen auch das connection diagram des OZG systems beschreiben. User Domain, Portal Domain, FIM Domain, Institution Domain, Data Exchange Domain
+
+    \item basic use case umsetzen durch IMP trotz ablösen von 3 vorher existierenden domänen
+
+    \item in diagrammen aufzeigen wo persönliche daten verarbeitet werden
+
+    \item datenverabeitung vergleich zwischen diagrammen
+
+    \item offen ob man andere domänen abschaltet (übergangszeit anlassen)
+
+    \item benefit of module for each application type is, that the processing of applications with different legitimations is fully seperated and in the future new apllication types can be added without touching exisitng modules
+\end{itemize}

### 2021-02-26 sections/13-imp_solution_integration.tex
added textual descriptions

@@
+The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection.
+The IMP solution described in this chapter puts the individual institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.
+
+Applications submitted to administration portals will eventually be submitted to responsible governmental institutions.
+Using IMP, relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.
+Each institution has a predetermined set of administrative services it can process.
+For each administrative service, the institution can create relationship templates, containing a description of the service along with attributes required by the user:
+
 \begin{itemize}
-    \item The goal of this advanced integration is to take full advantage of IMP features
+    \item Title: Apply for administrative service XYZ
+    \item Attributes: Name, Surname, ... 
+    \item Shared Attributes: Institution Name ...
+    \item Reason: Apply for the administrative service XYZ ...
+\end{itemize}
 
-    \item The integration now focuses not only in the system architecture of the administration portal but also of the institutions
+Based on these relationship templates, users and institutions can establish relationships.
+In contrast to the IMP solution of chapter 4, an established relationship does not result in the creation of a user profile.
+Instead, relationships represent a single application process and the attributes shared as part of the relationship are used by the institution to process the corresponding administrative service.
+After finishing the service, the relationship can be terminated, removing access to the shared attributes from the institution.
 
-    \item A disadvantage of the previous integration solution is, that the administration portal maintains user profiles.
-This results in a duplication of user data management systems (IMP system and user profile system).
-In addition, trough the user profiles, the administration portal has access to personal information without the need for processing but routing it.
-This is a data protection issue.
+While processing the administrative service, institution and user can securely and directly exchange data such as mails trough the IMP system without the need of an administration portal or user profile being involved.
 
-    \item As institutions are the entities which eventually need to process personal information, personal information should only be shared with them.
+Providing an attribute change feature as described in chapter 4, can enable users to request modification of attributes of an active application.
+The institution can then decide whether to accept or reject the request.
 
-    \item Using a IMP connector, institutions can establish relationships with users while the relationship represents the application for an administrative service.
+For users to access the relationship templates, each institution can host its own web page which lists all administration services along with the corresponding QR code containing the template.
 
-    \item The institution does not maintain a identity management system in addition to the IMP system: An application is started being processed after the relationship is established and further communication regarding the application is done through the relationship.
-If the application is finished, the relationship is terminated, removing access to personal information for the institution.
-
-    \item Institutions are capable of processing multiple administrative services.
-Each service has its own purpose, description and personal information required by the user.
-For each service, the institution processes, individual relationship templates can be created.
-
-    \item In order for users to determine which institution is responsible for processing their request and for accessing the correct relationship template, the administration portal can be used as a "search-engine"
-
-    \item The user searches for a administration service on the website of the administration portal and specifies the location he lives in.
-The administration portal determines the responsible institution and retrieves the correct relationship template from it.
-
-    \item Based on the template, the user now interact only with the institution to apply for a service. The administration portal does not receive any further personal information.
-
-    \item By requesting to change attributes of established relationships the institutions can process modifications of the request and decide if they accept or deny the request.
-
-    \item As there is no standard for how the system of an institution operates, the integration can follow the integration of the administration portal by constructing a "form" from the shared personal information and enabling to deliver it in all kinds of formats through an adapter
-
-    \item However, to further demonstrate the integration capabilities, the integration presents a possible integration for enabling application management through an E-Mail server on the institution side.
-
-    \item Incoming applications can be sent as an E-Mail to employees assigned to a certain type of request.
-The relationship ID can be used as a reference ID in the title of the relationship or as a "spoofed" email sender.
-Further communication like attribute change requests can follow the same style and be aggregates by any email client to display all messages with the same reference ID.
-
-    \item This method of applying for administrative services completely removes the need for administration portal and institution to maintain user profiles.
-It also enables users to share personal information only with entities which really need to process it.
-By enabling institution and user to directly interact, changes of the request content, status updates and exchange of mails can be done easily.
-
-    \item Integration aufbauend auf erster oder ersetzend??
-
-    \item Messaging architektur aus 1 genau so applizierbar in advanced integration
-
-    \item im stil der overview der integrationen auch das connection diagram des OZG systems beschreiben. User Domain, Portal Domain, FIM Domain, Institution Domain, Data Exchange Domain
-
-    \item basic use case umsetzen durch IMP trotz ablösen von 3 vorher existierenden domänen
-
-    \item in diagrammen aufzeigen wo persönliche daten verarbeitet werden
-
-    \item datenverabeitung vergleich zwischen diagrammen
-
-    \item offen ob man andere domänen abschaltet (übergangszeit anlassen)
-
-\end{itemize}
+However, depending on for example the home address of the user, the institution responsible for processing an administrative service can change.
+Therefore the administration portals connected trough the online gateway can be used as a "search-engine" for institutions.
+On any administration portal a user can select an administrative service and specify his home address.
+Based on this information, the portal is able to determine the institution responsible for processing the request.
+However, instead of requiring the user to login to a profile, the portal can redirect him to the web page of the institution where the relationship templates are being displayed.

### 2021-02-26 sections/14-technological_integration.tex
added textual descriptions

@@
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Integration Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Overview.pdf}
 \end{center}
+
+To implement the solution described in the previous section, a connector is included in the existing system architecture of every institution.
+The same messaging system described in chapter 4 can be used to integrate the IMP solution described in the previous section.
+Many of the messaging modules can be reused with minor modifications.
+Similar to the messaging system in chapter 4, two system components are connected: A web server and a institution system.
+
+As described in the previous section, for each administrative service, the institution is able to process, a relationship template is created and stored on a web page displayed by the web server.
+This can be done, as no personalized relationship templates will have to be created.
+
+Therefore, the messaging system wont need modules for creating templates. However, modules for processing incoming relationship requests are required.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Request Module.pdf}
+\end{center}
+
+For each administrative service, separate types of relationship templates and therefore relationship requests exist.
+Each relationship request type is processed by its custom "Application Request" module and "Application Request Processing" module.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Relationship Module.pdf}
+\end{center}
+
+Application Relationship Modules consume messages from the "Relationship Established" and filter all requests not concerning the application type of the module.
+After that, attributes shared as part of the relationship are mapped from the IMP data model to the OZG data model.
+As the existing institution system expects applications to be delivered as a form created by the form server of the administration portal, a message translator is added which translates the shared attributes to a suitable format so that the institution system understands it.
+The message is then published on the "Process Application" channel where a messaging adapter connected to the institution system consumes the message and submits the included form to the institution system the same way as the data exchange platform would.
+
+The institution system can use the unique relationship ID as reference ID for the application process and all further user interactions.
+
+Similar to the "Profile Attribute Change Message" module a "Application Attribute Change Message" module can be included witch performs the same operations.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Attribute Change Request Module.pdf}
+\end{center}
+
+For processing attribute change requests, application attribute change request modules are included for each relationship type.
+They consume messages from the !Attribute Change Request" channel and filter messages which do not concern the application type of the module.
+After mapping the attributes from IMP data model to OZG data model, messages are published on the "Application Attribute Change Request" channel.
+A module of the service provider can, based on the provided relationship ID and shared attributes decide if the attributes of the active application can still be changed.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Attribute Sync Module.pdf}
+\end{center}
+
+In order to process the change of an attribute for an active application, application attribute sync modules are included for each relationship type.
+They first filter all messages not concerning the relationship type of the module, then translate all attributes from the IMP data model to the OZG data model and publish them on the "Application Attribute Change" channel.
+A messaging adapter connected to the service facade consumes the messages and submits it to the institution system.
+In case the institution system has no way of processing an attribute change, a message translator can be included which constructs a form the messaging adapter submits as a new application with the same relationship ID.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Mail Message Module.pdf}
+\end{center}
+
+Using a bidirectional version of the "Mail Message" module, the messaging system can exchange mails from institution to IMP client and vice versa relating to a relationship ID.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Mail Module.pdf}
+\end{center}
+
+For exchanging mails, application mail modules are included for each type of application.

### 2021-02-26 sections/8-identity_management.tex
added textual descriptions

@@
-\section{Identity Management in OZG}
-Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities.
-In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles.
-Each member state has to provide its own user profile system which can be utilized through every administration portal.
-This solution is expensive to develop and maintain, as cooperation of multiple member states and institutions is required.
+\section{OZG Identity Management Issues}
 
-If every member state integrated IMP, users could access all administrative services through on IMP identity.
-Member states would not need to coordinate the operation of their user profile systems but independently access personal information through the IMP system.
+The OZG system architecture utilizes user profiles for identity management.
+This leads to several issues regarding usability, data protection, security and maintenance costs.
+The following sections describe problems of user profiles in general as well as problems arising specifically in context of the OZG system architecture.
 
-Users are required to create and maintain multiple user profile, the user profile of the OZG being yet another one.
-Changing personal information is a time consuming task with with an increasing number of user profiles and login credentials.
+\paragraph{Usability}
+Each service provider has different platform for management of personal information and identity related interactions.
+This can for example be web pages or applications for desktop and smartphone.
+Keeping track of all created user profiles is difficult.
+In case of web pages, users will also have to remember various URLs, usernames and passwords.
+The risk of forgetting login credentials is high.
+To manage personal information stored in each user profile and for example change an E-Mail address, users have to access the individual platforms of each service provider.
+Depending on the amount of created profiles, this can be a time consuming task.
+Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA or Magic-Link.
+Users receiving notifications, messages and mails on multiple platforms can quickly loose the overview and oversee important notifications.
+Each platform is often presented with a different design although the purpose remains similar.
+This makes it difficult for users to orientate themselves.
+Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while E-Mails are only used to notify the user to check his user profile ("You have unread messages!").
+One reason is, that E-Mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content.
+Although service providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.
+Service providers rely on the validity of information stored in the user profile.
+To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show his ID at a local shop.
+As each service provider manages separate user profiles, the user might have to go trough this time consuming process repeatedly.
+Users are not able to automatically share personal information from one user profile with another (except for some Single-Sign-On cases).
+As a result of that, creating new user profiles each time involves entering personal information all over again.
 
-Multiple service providers accessing personal information through the IMP identity of a user would enable the management of personal information in one place.
+In case of the OZG, usability of user profiles across multiple administration portals is limited: Although user profiles are interoperable, administration portals are individually responsible for the application process.
+Applying for different administration services, users might have to visit different administration portals.
+Each of the portals managing the application process separately.
+Active applications are not stored as part of the user profile but remain accessible only trough the respective portals they were created through.
+There does not exist an overview of all active applications amongst all administration portals.
+The user has to go trough each portal to find the application he for example wants to cancel.
+Especially due to the „one for all“ approach, users will have to access dedicated administration portals for certain types of administrative services.
+To mitigate this issue, the inbox of user profiles is used to notify the user of the status of all applications.
 
-Possibilities of interaction with the user to for example notify him about the status of an application are limited as no information which requires a high authentication level can be transmitted via E-Mail.
+\paragraph{Data Protection}
+In the past, service providers established a habit of collecting more personal information than necessary for providing their services.
+As a response, the "Datenschutz Grundverordnung" - DSGVO (General Data Protection Regulation) was passed.
+Amongst other things, it requires service providers to inform the user about which personal information is processed, what the reason for processing the information is and how it is being processed.
+Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage.
+As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which service provider processes which personal information.
+Multiple service providers storing sensible information increases the risk of data being stolen due to a data breach.
 
-Through the IMP client, direct interaction with the user is possible. The user can not only receive notifications but directly respond without the need for visiting a website and logging in.
+In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also multiple systems operated by the member state.
+Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it.
+As a result of that, the administration portal has access to all personal information only the institution will eventually need to process.
+In addition, institutions actually do not require user profiles for processing applications.
+After an application is finished, the institution can delete all data stored as part of this process.
+The only reason user profiles are required is to verify the validity and authorization of incoming applications and to enable the user to comfortably fill in application forms and communicate trough an inbox.
 
-With a large number of user profiles the risk of forgetting passwords and the possibility of users using the same password multiple times increases.
-Using the IMP client to access services, no authentication through a username and password combination is required as the application is installed on a secured smartphone.
+\paragraph{Security}
 
-\section{Integration Challenges}
+User profiles are often secured trough passwords.
+Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of it being stolen and all user profiles being accessible.
+With the amount of different service providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between service providers.
+Users also have to rely on the correct operation of the system architecture of the service provider and might not be able to proof failures in the operation of the system.
+If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proofing to the service provider, that he did cancel the subscription.
 
-This chapter describes challenges for integrating the IMP system described in chapter 3 into the OZG system architecture.
-The quality of the presented integration can be determined based on the number of the following challenges it solves.
+\section{IMP Solution Opportunities}
 
-\subsection{IMP Challenges}
-This section describes challenges which arise from the operation of the IMP system
+Identity management provisioning is capable of solving many of the issues described in the previous section.
+
+\paragraph{Usability}
+
+The goal of IMP solutions is to replace user profiles with a single IMP identity.
+Trough the IMP client a user can manage his IMP identity and all integrated service providers.
+Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider.
+Depending on the use case, the relationship can be utilized differently.
+Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.
+It also enables the user to update personal information shared with service providers trough one application.
+As the IMP client also contains an inbox, all notifications sent by each service provider can be viewed in the same place.
+As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can sent structured data to the IMP client along with the information that it should be displayed as a form.
+Depending on the content of the form and the use case of the service provider, the form can either be a purchase agreement or a survey.
+Assumed, trough a secure identification and validation process, the identity management provider makes sure, attributes users stores as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls.
+Due to the IMP client being able to automatically fill in attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.
+
+In case of the OZG system architecture, IMP can be used by each member state to individually establish relationships with IMP identities of users to access personal information.
+This could replace the requirement for user profiles to be interoperable.
+For the most part, member states would then be able to operate independently from each other.
+This solution is described in detail in chapter 4.
+
+\paragraph{Data Protection}
+
+IMP puts the user back in control of his personal information.
+As part of the process of establishing a relationship, the service provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed.
+With this information, the user can make an informed decision whether to establish the relationship and the service provider performed his duty to inform the user as required by the DSGVO.
+As personal information is only shared as part of a relationship and with a specified purpose, the service provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible trough.
+This helps the service provider in processing personal information according to the DSGVO.
+As every relationship along with shared attributes is manageable trough the IMP client, the user wont loose track of which service provider has access to which personal information.
+The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the service provider processes only a small portion of attributes of IMP identities.
+
+In case of the OZG system architecture, IMP can be used by the individual institutions to establish relationships with IMP identities of users to retrieve applications for administrative services.
+This could eventually eliminate the need of user profiles.
+Personal information could be shared with only the responsible institution.
+This solution is described in detail in chapter 5.
+
+\paragraph{Security}
+
+The IMP client enables users to access their IMP identity and all relationships without the need of remembering a variety of credentials.
+This removes the risk of passwords being stolen.
+The IMP client itself can be secured without the need for a password.
+As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validate at any time.
+This enables both user and service provider to provide proof for interactions.
+
+\section{IMP Integration Challenges}
+
+In order for the system architecture of the OZG and service providers in general to utilize IMP services, the IMP connector has to be integrated.
+Multiple integration challenges are described in the following sections and will be focus of the integration architectures of chapter 4 and 5.
+
+\paragraph{SP Challenges}
+
+\begin{itemize}
+    \item Sp does not understand concepts of the IMP like relationships, the integration has to bridge this gap
+    \item The SP wants the integration to 
+    \item Minimal modification of existing systems
+    \item Maintainability
+    \item Scalability
+    \item Extendability
+    \item Modularity
+    \item
+
+\end{itemize}
+
+\paragraph{OZG Challenges}
+
+\begin{itemize}
+    \item Once an application is submitted, its attributes cannot be changed
+    \item Mapping of IMP attributes and FIM data blocks
+    \item 
+\end{itemize}
+
+\paragraph{IMP Challenges}
 
@@
     \item Connector does not understand messages
-    \item Messages can have different versions
     \item API of connector can change
@@
 \end{itemize}
-
-\subsection{SP Challenges}
-
-This section describes challenges which arise from service provider integration requirements.
-
-\begin{itemize}
-    \item Minimal modification of existing systems
-    \item Maintainability
-    \item Scalability
-    \item Failure Handling
-    \item Administration
-    \item Extendability
-    \item Modularity
-
-\end{itemize}
-
-\subsection{OZG Challenges}
-
-This section describes challenges which arise from OZG integration requirements.
-
-\begin{itemize}
-    \item Administration portal has access to all personal information
-    \item Once an application is submitted, its attributes cannot be changed
-    \item Mapping of IMP attributes and FIM data blocks
-\end{itemize}

### 2021-02-26 sections/9-imp_utilization_in_ozg.tex
added textual descriptions

@@
-Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities.
-In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles.
-Each member state has to provide its own user profile system which can be utilized through every administration portal.
-This solution is expensive to develop and maintain, as communication between multiple member states and institutions is required.
+This chapter presents an IMP solution which solves issues of OZG identity management described in chapter 3 through integration of the IMP system described in section 2.2 into the OZG system architecture described in section 2.4.
+Focus of this solution is to not be invasive into the existing system architecture: Few existing system components should have to be modified and the existing operation of the system should not be disrupted.
+This enables the introduction of IMP as an additional but optional way of accessing OZG services with improved usability.
 
-Goal of the integration solution is to introduce features of the IMP system into the OZG system architecture.
-All existing services should be accessible the same way as before but with additional options for using IMP.
-The focus of this initial integration is to avoid disruption of existing system operation through non-invasive integration, to enable a fast and simple introduction of IMP features and to provide future upgrade capabilities.
-The integration takes place on three layers:
+The integration of the IMP system takes place on three layers:
 
-\begin{figure}[h]
-\caption{IMP Layer Diagram}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.png}
-\end{figure}
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
+\end{center}
 
-\paragraph{IMP Solution Integration Layer} 
+\paragraph{IMP Solution Layer} 
 The purpose of the integration on the IMP solution layer is to take advantage of new interaction capabilities with the user through the IMP system.
@@
 
-\paragraph{Relationship Integration Layer} The purpose of the integration on the relationship layer is to enable the technological utilization of relationships as described by the integration on the solution integration layer.
-
-\paragraph{Communication Integration Layer} The purpose of the integration on the communication layer is to enable the technological utilization of messages as described by the integration on the solution integration layer.
+\paragraph{Technological Integration} The technological integration on the "Communication Integration" layer and the "Relationship To Identity Integration" layer describes how an integration system can enable the existing system architecture to implement the IMP solution described in the "IMP Solution" layer.
 
@@
 
-This section evaluates possibilities of a technological integration architecture for realizing the integration solution described in the previous section.
+\subfile{11-technological_integration}
 
-\subfile{11-technological_integration}
+\section{Solution Evaluation}
+
+The described IMP solution combines the existing identity management solution of the OZG with new IMP services, increasing usability trough a non-invasive integration while compromising on data protection.
+
+The IMP solution enables users to manage their OZG user profile as one of multiple IMP relationships which enables him to keep an overview of shared attributes and how they are being processed.
+The user can update personal information and receive notifications in one place.
+Using the IMP client for authentication, the user wont need to remember user password for his user profile.
+
+For the service provider, the integration architecture is non-invasive, as only two system components are required to connect to a messaging adapter and the existing operation of the system architecture is not disturbed.
+As a result of the modular messaging approach, the integration can easily be expanded with new features by adding new modules.
+
+However, the simplified integration comes at a cost for the user.
+Most of the basic use case as well as most personal information is still being processed by the administration portals.
+This remains to be a data protection issue.
+As the administration portal only establishes one type of relationship for accessing all necessary personal information, differentiation in processing the individual attributes is difficult.
+The user also is required to approve to a very general request for sharing attributes: "Create user profile".
+Further legitimisation for processing personal information e.g the individual administrative services remain to be hidden from the IMP client.
+
+In the future, the described IMP solution can eventually replace interoperable user profiles.
+If every administration portal integrates the IMP solution and establishes its own IMP relationship with users, user profiles will no longer need to be interoperable as the user can easily manage the individual relationships trough one IMP client.
+
+\begin{itemize}
+    \item Can eventually replace interoperable user profiles by each administration portal only using IMP and user profiles "behind the scenes"
+    \item Can eventually replace user profiles by using relationships to apply for services
+\end{itemize}

### 2021-03-01 sections/11-technological_integration.tex
textualizing

--- 2021-02-21 sections/11-technological_integration.tex
@@
-\begin{itemize}
-    \item Integration only with administration portal to be non invasive
-    \item Only one connector for the administration portal
-\end{itemize}
+This section describes a messaging architecture enabling the integration of the IMP solution described in the previous section into the existing OZG system architecture.
 
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Overview.pdf}
-\end{center}
+\subsection{Integration Overview}
 
@@
 
-System architecture of the SP and IMP system consist of multiple components.
-The administration portal component of the system architecture is the component which will interact with the integration system.
-The administration portal contains a web server and a service facade.
-The service facade enables the administration portal amongst other things to access the user profile component.
-
-On the side of the IMP system, the connector will interact with the integration system.
+The IMP solution described in the previous section requires the administration portal to access IMP services.
+For integration, an IMP connector and a messaging system are added to the portal domain.
+Using the messaging system, existing systems of the administration portal can access IMP services trough the IMP connector.
 
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Integration Overview.pdf}
 \end{center}
 
-The integration is constructed as a messaging system.
-The messaging system consists of modules which exchange messages with connector and administration portal.
-As administration portal and connector are not able to send, receive or understand messages, a messaging adapter is attached to both systems.
-A messaging adapter is software which provides an API to the system hiding the operation of the messaging system.
-Depending on the system the messaging adapter should be attached to, different integration methods can be used.
-In most cases however, manual modification of the programming of the system is necessary to utilize the API of the adapter.
+In order for the integration not to be invasive, only the web server and the service facade of the administration portal are connected to the messaging system.
+All other existing system components remain untouched.
 
-The integration system consists of messaging modules, each of them solving a different integration task.
-The modular approach enables the integration system to be easily expandable by new features trough new modules.
-Assigning integration tasks to modules also improves maintenance.
-System administrators can update a feature by modifying and expanding the corresponding component.
-Modules can be designed to be reusable by other components which reduces the development time for new features and the size of the integration system.
-If the modules supports it, the performance of the integration system can be dynamically scaled by adding multiple module instances.
-
-Modules have the purpose of solving integration tasks by providing access to features presented in section 5.1 while hiding the complexity of the operation of the IMP system.
-Modules therefore exchange messages through three types of publish-subscribe channels.
-Between administration portal and modules, feature channels are used.
-On these channels, messages strongly related to the operation of the system architecture of the service provider are exchanged.
-This are for example messages for requesting services like the transmission of a mail.
-
-Between modules and connector, connector channels are used.
-These are a predetermined and limited set of channels which are used by the messaging adapter to map the functionalities of the connector to the messaging system.
-Messages exchanged on these channels are strongly related to the operation of the IMP system.
-This are for example requests and replies for relationships and templates.
-
-Between modules, intermodule channels are used to exchange messages. Modules can exchange messages in order to access distributed functionalities of other modules.
+\subsection{Onboarding Sequence}
 
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
 \end{center}
@@
 
+\subsection{Messaging Overview}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
 \end{center}
 
-\begin{itemize}
-    \item Web Server has messaging adapter with API for retrieving onboarding template
+The main task of the integration system is to translate between the domain of the existing system architecture and the domain of the IMP system.
+None of the existing systems can process IMP relationships but they can process user profiles and vice versa.
 
-    \item Connector has messaging adapter with API for creating templates
+On the side of the administration portal, messaging adapters provide an API to the existing systems providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
+The adapters communicate with the messaging system trough publish-subscribe datatype channels.
+Each datatype channel contains messages with the same datatype and has a defined purpose.
+All systems, consuming messages from the channel are aware of this purpose and process consumed messages accordingly.
+Messages placed on a publish-subscribe channel can be simultaneously accessed by multiple systems which subscribed to the channel.
+Using these channels, message adapters can send requests, receive replies, receive notifications, receive requests and send replies.
 
-    \item Onboarding Template Module exists, which manages the exchange of request and reply messages
+On the side of the connector, messaging adapters translate the REST API of the connector to a set of publish-subscribe datatype channels.
+Using these channels, the messaging system can send REST requests by placing messages on channels corresponding to a certain interface.
+This also enables the messaging system to receive events from by the connector by the messaging adapter placing messages on a notification channels.
 
-    \item Module exchanges messages with web server adapter through request and reply channel. Only this module and the adapter of the web server use the channels.
+Messaging adapters do not communicate directly trough channels, but with messaging modules.
+Messaging modules consist of messaging patterns which are able to modify, delete and route messages.
+Purpose of the modules is to translate messages sent by messaging adapters of either service provider or connector to be understood by the respective recipient.
+Each module is assigned to an individual integration task.
+By adding or removing modules, integration capabilities of the messaging system can be suited to the system architecture of the service provider.
+Modules can be designed to provide services to messaging adapters or other modules.
+Designing modules specifically for the usage by other modules helps in distributing integration responsibilities and avoiding a single monolithic integration component.
 
-    \item Module exchanges messages with connector adapter through request reply channel. Multiple different modules can use the channels.
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
+\end{center}
 
-    \item Config Enricher adds suitable configuration as new entry to request
+The figure gives an overview of the messaging system which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.
 
-    \item Configuration is stored in a database or file. An administrator maintains the configuration
+As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which is built upon it.
+As described in section 2.2, communication between IMP identity and service provider is only possible trough an established relationship.
 
-    \item The configuration creates a relationship template used to create a user profile. The configuration has to define the template to require attributes necessary for creating a user profiles.
+Three messaging modules on the "Relationship to Identity Integration Layer" exist, which directly access services of the connector.
+The onboarding template module provides the feature of creating relationship templates for onboarding.
+The Onboarding request module, provides the feature of processing and responding to relationship requests.
+And the Onboarding relationship module provides the feature of processing established relationships by creating a new user profile.
+The relationship mapping module has the purpose of combining "Relationship to Identity Integration Layer" and "Communication Integration Layer" by enabling the messaging system to map relationships to the corresponding entity of the service provider.
+In this case, the module maps IDs of relationships to IDs of user profiles.
+Each relationship has a one-to-one relationship to a user profile.
 
-    \item Attribute names and meaning can differ between OZG user profile and IMP identity, the configuration has to use the attribute definition of the IMP system.
+The "Communication Integration Layer" consists of modules, which enable the existing systems to exchange structured data with the IMP client.
+Purpose of the modules is to translate between the data models of the service provider and the IMP system.
+Most importantly in this case, none of the existing systems is able to understand relationships or relationship IDs.
+Therefore, the message mapping module has the purpose of translating all incoming relationship IDs to user profile IDs with the help of the previously mentioned relationship mapping module on the underlying layer.
+Three message modules are included.
+Each of them has the purpose of identifying messages of a certain type and separate them on individual channels.
+This enables the construction of various modules processing the same message types in different ways.
+However, in this case, each message type has only a single module processing it.
+Modules which eventually process the messages, have the purpose of translating the message content between the data models of service provider and IMP system.
+For example the mail module consumes messages which contain a mail received by a user profile.
+It is very likely, that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types.
+The mail module therefore has to convert the format of the mail content.
 
-    \item Config Message Translator incorporates the metadata entry to the template configuration
-
-    \item Adapter Message Translator incorporates mapping of possible future changes of adapters in for example attribute naming or attribute data types (this type of message translator can be added to every channel connected to an adapter and is therefore excluded in future visualizations)
-
-    \item Module filters for templates of the onboarding type as the channel could contain responses with templates of different type for other modules.
-
-\end{itemize}
+\subsection{Onboarding Template Module}
 
@@
 
-Eventually, the user sends a relationship request which will be processed by the "Onboarding Request Module"
+To present an onboarding relationship template to the user, the web server first has to retrieve it from the messaging system.
+For this purpose, an "Onboarding Template Module" is added to the messaging system.
+Using the API of a messaging adapter provided in addition to the module, the web server can request the creation of new onboarding templates.
+Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template.
+In this case, the web server will want to notify the user about the successful creation of his user profile.
+The web server therefore adds the users current session ID as metadata to the template.
+
+The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests and the "Onboarding Template Response" channel, where it listens for responses.
+In order for the adapter to correlate request and reply messages, it creates a message which besides the Template Metadata contains a request ID.
+This ID is expected to be included in the response message.
+The message ID is a unique identifier and is part of every message.
+The module consumes messages from the "Onboarding Template Request" channel.
+On each channel connected to a messaging adapter, message translators are attached.
+These translators have the purpose of providing a canonical data model within the module by translating messages on the data representation, data types and data structures layer.
+It might happen, that in the future one of the adapters switches from using for example an XML instead of a JSON data representation.
+Using message translators on each side, enables to adapt to these changes by only appropriately configuring the translator while leaving the rest of the module untouched.
+
+In between the message translators, the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute.
+This configuration contains information on how relationship templates of type onboarding are supposed to look like.
+It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more.
+If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited.
+Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity.
+Therefore, all attributes which are required to create a user profile have to be requested by the template.
+In the template, attributes have to be requested according to the data model of the IMP system in order for the IMP client to understand them.
+When receiving a response later, a module will translate the attributes back to the OZG data model.
+
+After enriching the message with the template configuration, the message is published on the "Template Request" channel.
+The messaging adapter of the connector consumes the message and issues the appropriate REST request to the connector.
+After receiving a response from the connector it publishes the resulting template along with the request ID on the "Template Response Channel".
+As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.
+
+The messaging adapter consumes the message on the response channel and returns the template to the web server, which based on the session ID in the template metadata can display the template as QR code to the user.
+
+\subsection{Onboarding Request Module}
 
@@
 
+Eventually, the user scans the QR code, fills in the attributes and submits a relationship request.
+The request is received by the connector, forwarded to the messaging adapter and published on the "Relationship Request" channel.
+The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship.
+It also contains the request content with attributes shared by the user and the template the request originated from.
+Messages on the "Relationship Request" channel are consumed by the "Onboarding Request Module".
+As in the previous example, message translators are included to construct a canonical data model for the module.
+A message filter only lets messages trough which contain templates of type onboarding.
+The message translator connected to the "Onboarding Request" channel translates attributes shared by the user from the IMP data model to the OZG data model.
+
+Based on the attributes the user shares, the OZG system has to decide if the relationship should be established or not.
+As this process heavily depends on the use case of the relationship and on the service provider, the messaging system expects the SP to add a module called "Onboarding Request Processing Module" which consumes the request and responds with either approve or reject on the "Onboarding Response" channel.
+To correlate the response to the request, the message also has to contain the relationship ID.
+The "Onboarding Request Module" forwards the response to the "Relationship Response" channel, where the connector will further interact with the IMP system to either establish or cancel the relationship.
+
+\subsection{Onboarding Relationship Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Attribute Change Message Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
 \end{center}
 
+If the user did not retract his relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification which the messaging adapter publishes on the "Relationship Established" channel.
+The message contains the ID of the established relationship along with all attributes shared by the user.
+The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships.
+In this case, the module only processes the establishing of relationships, it could however be expanded to also process terminations of relationships.
+
+Message translators are inserted again for creating a canonical data model.
+
+The module processes an established relationship by initiating the creation of a new user profile.
+First, a message filter lets trough only messages of the onboarding type.
+Afterwards, each message is stored in a "Relationship Storage" database and published on the "Create User Profile Request" channel.
+However, before publishing the message, a message translator maps attributes form the IMP data model to the OZG data model.
+
+To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content.
+After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.
+
+As responses to requests from other modules might be published on this channel, the "Onboarding Relationship" module filters all messages which do not contain a relationship ID stored in the "Relationship Storage".
+The module then publishes the response on the "New Relationship Mapping" channel.
+
+\subsection{Relationship Mapping Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Request Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Relationship Mapping.pdf}
 \end{center}
 
+Trough the "New Relationship Mapping" channel, the "Relationship Mapping" module receives the message sent by the previously described module.
+Purpose of the "Relationship Mapping" module is to map relationships to corresponding entities in the existing system architecture.
+In this case, relationships are mapped to user profiles and vice versa using relationship IDs and user profile IDs.
+The message consumed trough the "New Relationship Mapping" channel is stored in a database for enabling future translation between the contained relationship ID and user profile ID.
+Using the "Relationship Mapping Request" channel, modules can request the "Relationship Mapping" module to add a user profile ID for a given relationship ID and vice versa.
+
+Using messaging for this form of database access enables modules to stay unaware of the complexities of the underlying data storage mechanisms.
+An alternative would be for modules to use the database as a shared database.
+
+\subsection{Message Mapping Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Onboarding Relationship Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Message Mapping Module.pdf}
 \end{center}
 
+Using the previously defined "Relationship Mapping" module, the "Message Mapping" module has the purpose of translating the relationship ID of all inbound messages to the corresponding user profile ID and translating the user profile ID of all outbound messages to the corresponding relationship ID.
+As a result of that, on the left side, messages coming from or going to the existing system architecture, messages contain identification of the known user profile entity instead of the unknown relationship entity.
+On the right side, messages coming from or going to the IMP system contain identification of the known relationship instead of the unknown user profile.
+
+Incoming messages on the "Message Inbound" channel are consumed by the module and translated by a message translator to a canonical data model.
+In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a content enricher adds a unique request ID to the message and stores the ID in a database.
+Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let trough by the request ID message filter.
+As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes relationship IDs from the message before publishing it on the "Message Inbound Mapping" channel.
+
+Outbound messages on the "Message Outbound Mapping" channel are processed similar to inbound messages.
+The difference being, that the user profile ID contained in the message is replaced by the corresponding relationship ID.
+
+\subsection{Attribute Change Message Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. User Profile Attribute Sync Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. Attribute Change Message Module.pdf}
 \end{center}
 
+For the messaging system to process messages being exchanged as part of relationships, message modules can be added.
+Their purpose is to map messages of certain types on the "Message Inbound Mapping" channel to individual message type channels so that modules can process them.
+They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.
+
+In this case, an "Attribute Change Message Module" is included, which processes messages related to the attribute change process.
+Messages exchanged trough IMP relationships can have arbitrary content, however, the messages are assumed to contain a message type attribute and a message content attribute.
+Based on the message type attribute, a message filter can let messages trough which contain a message type attribute correlating to an attribute change process.
+Based on the type of a message, a content based message router then copies each message to a datatype channel.
+In this case, messages of type attribute change request and attribute change established are distinguished.
+Corresponding to that, two data type channels exist.
+As based on the channel, a message is placed, its message type can be inferred, content filters remove the message type attributes.
+
+Outbound messages related to the attribute change process are consumed on data type channels.
+In this case, it is only one "Attribute Change Response" channel.
+A content enricher adds a message type attribute correlating to the channel the message was placed on.
+This is required in order for the IMP client to properly interpret the message.
+After that, the message is published on the "Message Outbound Mapping" channel.
+
+\subsection{User Profile Attribute Change Request Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Mail Message Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Attribute Change Request Module.pdf}
 \end{center}
 
+To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel.
+Messages arriving on the "Attribute Change Request" channel were mapped form a relationship ID to a user profile ID in an earlier integration step.
+Depending on the use case of the service provider, not all user profiles should be processed in the same way.
+Therefore, message filters are inserted, which are able to distinguish possible "types" of user profiles based on the user profile ID.
+It would also be possible to include an additional module, which is able to request user profile type information from the existing systems, separating messages on the "Attribute Change Request" channel appropriately.
+For example, user profiles for businesses could exist, where processing of attribute change requests requires a more through and manual verification by employees.
+
+In the example at hand, however, only one module processes attribute change requests.
+To translate the canonical data model into the data model of the OZG, a message translator is included.
+This concerns especially the attributes shared as part of the attribute change request.
+
+Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the service provider.
+Therefore, the SP is expected to include a "Profile Attribute Change Processor" module, which based on the user profile ID and the shared attributes decides to approve or reject the request.
+The response is published to the "Attribute Change Response" channel and besides the response, contains the user profile ID.
+
+\subsection{User Profile Attribute Sync Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. Mail Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. User Profile Attribute Sync Module.pdf}
 \end{center}
 
+If the user did not cancel the attribute change request before the OZG system accepted, the attribute change is established.
+The connector is notified trough a message, which eventually by processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.
+
+The "User Profile Attribute Sync" module consumes messages from the "Attribute Change Established" channel.
+Similar to the "User Profile Attribute Change Request" module, a message filter is inserted for distinguishing possible user profile types based on the user profile ID.
+A message translator is inserted to translate the message content to the OZG data model.
+This concerns especially the attributes shared as part of the attribute change established message.
+
+\subsection{Mail Message module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Authenticatin Message Module.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Mail Message Module.pdf}
 \end{center}
 
+In order for the user to receive messages sent to his user profile trough the IMP client, mail messages are processed by the integration architecture.
+Similar to the "Profile Attribute Change Message" module, a "Mail Message" module is included, which maps messages on the "Mail Outbound" channel to the "Message Outbound Mapping" channel.
+
+In this module, incoming mails from the IMP client could also be processed.
+
+Before publishing messages on the "Message Outbound Mapping" channel, a content enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it.
+
+\subsection{Mail Module}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Authentication.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Mail Module.pdf}
 \end{center}
+
+A messaging adapter attached to the service facade is notified each time, a user profile connected to an IMP identity receives a mail and publishes a message on the "Profile Mail Outbound" channel.
+The message contains the ID of the profile which received the message and the content of the mail.
+
+A "Mail" module is included which consumes the messages from the "Profile Mail Outbound" channel.
+A message translator is inserted, which translates the mails from the OZG data model to the IMP data model and publishes them on the "Mail Outbound" channel.
+
+\subsection{Authentication Message Module}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/16. Authenticatin Message Module.pdf}
+\end{center}
+
+If the user creates a user profile using his IMP identity, it is possible to replace authentication using a password with authentication trough the IMP client.
+It is also possible to use the IMP client for two factor authentication.
+
+In order to send and receive messages related to authentication, similar to previous message modules, an "Authentication Message" module is included which maps incoming messages on the "Message Inbound Mapping" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.
+
+\subsection{Authentication Module}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/17. Authentication.pdf}
+\end{center}
+
+When the user visits the web page of the administration portal to apply for an administrative service, he will have to login.
+To utilize the IMP client for authentication, the web server can use a channel adapter to publish a authentication request concerning a user profile ID and a certain session ID.
+The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content.
+Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser.
+Similar to previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message".
+
+Eventually, the IMP client sends a response as message, which the "Authentication Message" module publishes on the "Authentication Response" channel.
+Similar to previous modules, the service provider can use a message filter to process user profile types differently.
+After translating the message to the OZG data model, it is published on the "Authenticate Profile Response" channel.
+The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.

### 2021-03-01 sections/12-advanced_utilization.tex
textualizing

--- 2021-02-21 sections/12-advanced_utilization.tex
@@
 \subfile{14-technological_integration}
+
+\subsection{Solution Evaluation}
+
+\begin{itemize}
+
+    \item The IMP solution present in this chapter reduces the amount of systems processing personal information to the absolute minimum: only the responsible institution and the user.
+
+    \item The integration architecture described in section 4.2 was able to integrate into two different system architectures.
+This demonstrates, that the presented integration architecture is applicable to a variety of system architectures.
+
+    \item The integration architecture described in section 4.2 was able to integrate a user oriented (persistent) relationship scenario as well as a process oriented (temporary) relationship scenario.
+This demonstrates, that the presented integration architecture can be used for integrating a variety of IMP solutions.
+
+    \item The modular message based approach made it possible to use the integration architecture in a different scenario, by enabling easy configuration of modules for new requirements.
+
+    \item IMP utilization of chapter 5 can be used simultaneously to IMP utilization of chapter 4 or as an incremental step.
+
+    \item Eventually, profile based operation of OZG can be replaced by process based IMP solution.
+
+\end{itemize}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/OZG Personal Information.pdf}
+\end{center}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
+\end{center}

### 2021-03-01 sections/14-technological_integration.tex
textualizing

--- 2021-02-21 sections/14-technological_integration.tex
@@
+This section describes the integration of the IMP solution presented in section 5.1 using the same messaging system as described in section 4.2.
+
+\subsection{Integration Overview}
+
 \begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Integration Overview.pdf}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
 \end{center}
+
+To implement the IMP solution, a connector is included in the existing system architecture of each institution as well as the messaging system described in section 4.2.
+Instead of the web server and service facade in the portal domain, the messaging system is connected to the web server and institution system of the institution domain.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
+\end{center}
+
+Institutions are able to process a predetermined set of administrative services. For each service, the institution can once create a relationship template and store them as QR code on their web page.
+
+Users visiting an administration portal can select an administrative service, specify their home address and be forwarded to the web page of the respective institution.
+After scanning the appropriate QR code with the IMP client, the user can fill in the requested attributes and send the relationship request.
+After the relationship is established, the institution is notified and starts processing the application utilizing the shared attributes.
+
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
+\end{center}
+
+The layout of the messaging system is identical to the one presented in section 4.2. Exactly the same type of messages are exchanged with however, a slightly different purpose and content.
+
+On the "Relationship to Identity Integration Layer", modules exist for establishing the different types of application relationships.
+For simplification, modules only for an "Application A" are shown.
+Besides the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: Each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
+As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately.
+For an established relationship, instead of issuing the existing system architecture to create a user profile, the application relationship module issues the existing system architecture to process an application based on the attributes shared as part of the relationship.
+And instead of a user profile ID, the existing system architecture responds with an application process reference ID.
+This application process reference ID is used in the same way as the user profile ID in section 4.2.
+Trough the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.
+
+On the "Communication Integration Layer", the same types of messages are exchanged.
+However instead of user profile IDs, relationship IDs are mapped to application process reference IDs.
+In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs in order to for example distinguish a enterprise profile from the profile of a private person.
+In this case, modules can distinguish between different application types based on the application process reference ID.
+
+...... Hier muss noch mehr kommen (ausführlicher) .......

### 2021-03-04 sections/1-context.tex
message chapter started

@@
 Since invention of the World Wide Web, the number of its users increased rapidly.
-Today, more than 90 percent of the German population use the internet \cite{Onlinestudie}.
-Enterprises and organizations, recognised this potential to provide their services to a large number of people as Service Providers (SP).
+Today, more than 90 percent of the german population uses the internet \cite{Onlinestudie}.
+Enterprises and organizations recognised this potential to provide their services to a large number of people as Service Providers (SP).
 A frequently used method of SPs is "online self-service" (OSS).
@@
 A system for management of identities of users therefore is part of numerous system architectures.
-Service Providers usually enable users to manage their partial identities using online self-service through so called User Profiles.
-Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP
+Service Providers usually enable users to manage their partial identities using online self-service through user profiles.
+Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP.
 
-The result is variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
+The result is a variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
 \begin{itemize}
@@
     \item As a result of the distributed identities, risk of data breaches increases.
-    \item Managing multiple use profiles is very inconvenient for users.
+    \item Managing multiple user profiles is very inconvenient for users.
     \item It is often unclear who stores which data and for what purpose.
@@
 One model called Social Login became popular.
-It enables customers to create User Profiles for SPs through existing User Profile of Social Networks like Facebook.
+It enables customers to create User Profiles for SPs through existing User Profiles of Social Networks like Facebook.
 This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes.
@@
 
-The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and User Profiles.
+The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and user profiles.
 The system itself is provided and hosted by a SP for consumption by other SPs.
@@
 A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG).
-It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
+It requires all administrative services of the german federal republic, each member state and commune to be digitally available through interoperable user profiles.
 The current plan is to make the profiles only available for usage in context of the OZG.

### 2021-03-04 sections/10-imp_solution_integration.tex
message chapter started

--- 2021-01-28 sections/10-imp_solution_integration.tex
@@
-The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal.
-This is not necessary any more, as user profiles are replaced by IMP identities.
-The user will only have to create an IMP identity.
+The IMP solution presented in this section describes the utilization of IMP relationships with the purpose of creating and maintaining user profiles through the IMP client.
+Message types for attribute synchronization, authentication and communication are defined.
+To not disrupt the operation of the existing system architecture, the IMP solution is designed to not replace user profiles but provide an additional way of accessing them trough IMP.
+To later reduce technological integration efforts, the IMP solution is designed to only require interaction with systems of the portal domain.
 
-The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal.
-As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services.
-The IMP client does not require authentication, as it is installed on the smart phone of the user.
-The user can secure his smartphone through for example biometric authentication.
+\subsection{Relationship Utilization}
+The option of using an existing IMP identity for creation of an OZG user profile is added to the account creation web page of the administration portal.
+An IMP relationship is used for the account creation process.
+The web page renders the ID of the following relationship template as a QR-code:
 
-The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.
+\begin{itemize}
+    \item Title: Create OZG User Profile
+    \item Attributes: Name, Surname, ... 
+    \begin{itemize}
+        \item Name: Max
+        \item Surname: Mustermann
+    \end{itemize}
+    \item Shared Attributes: Administration Portal of the member state ...
+    \item Reason: Create an OZG user profile and connect your IMP identity.
+    \item Metadata: <<data for technological integration>>
+\end{itemize}
 
-The fourth step of the basic OZG use case is to fill in the application.
-The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.
+Users visiting the account creation web page of the administration portal can use the IMP client to scan the QR code.
+The IMP client presents the corresponding relationship template to the user and automatically fills in attributes which the administration portal requests from the user as part of the relationship.
+It is assumed that the IMP system has systems in place for identifying users and validating personal information of corresponding IMP identities.
+As a result of that, service providers could rely on the validity of shared attributes.
 
-The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more.
-Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.
+Based on the presented content of the template, the user can make an informed decision on whether to submit a relationship request.
+If the user submits the request, the administration portal receives it and, based on the attributes shared by the user, decides whether to accept or reject it.
+If it accepts the relationship request and the user did not retract the request in the meantime, the relationship is established.
 
-For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template.
-The connector responds to the institution with the template IDs.
+Using the personal information shared as part of the established relationship, the portal creates a new user profile and connects it to the IMP identity.
 
-In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address.
-After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.
+\subsection{Message Utilization}
+As part of an established relationship, service provider and user can securely exchange structured data in form of asynchronous messages.
+Security in this case means that messages can not be accessed or modified by a third party and are authorized by the corresponding user.
+Based on this secure data exchange capabilities, service providers can define various types of messages, each with different purposes and effects on the IMP client.
+This section contains various message types useful for managing the user profile created as a result of an established relationship.
 
-If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it.
-The relationship template contains a description of the selected administrative service as reason for the relationship.
-The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application.
-This replaces the functionalities of the form server.
+\paragraph{Login to User Profile}
+During the user profile creation process using IMP, the user specified a username but not a password. The IMP client is used for authentication of login requests to the administration portal.
 
-The fifth step of the basic OZG use case is to submit the application.
-After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes.
-The institution can accept the request and start processing the application.
-The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.
+On the login web page of the administration portal, an option is added to login to a user profile using IMP.
+After entering and submitting the username specified during the profile creation process, administration portal and IMP client exchange authentication messages.
+Through the IMP client, the user will be requested to approve a login attempt along with information about the corresponding relationship, IP address, URL and more.
 
-The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.
+If the user accepts the request, the administration portal authenticates the browser session.
 
-The eighth step of the basic OZG use case is the management of active applications.
-As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution.
-Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.
+\paragraph{Attribute Synchronization}
 
-The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications.
-As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.
+The IMP client is used for management of personal information of the user profile.
+Through the IMP client, the user can send requests for adding, updating or deleting shared attributes.
+Administration portal and IMP client exchange attribute change request and reply messages.
+The requests can either be accepted or rejected by the service provider.
+Accepting the request will result in according modification of the user profile connected to the relationship.
+
+For simplification purposes, the web page for management of personal information on the administration portal is expected to be locked.
+However, it would also be possible for the portal to send attribute change requests to the IMP client based on the modifications the user performed on the web page.
+
+\paragraph{Communication}
+
+The IMP client is used for receiving and displaying mails sent to the user profile.
+The administration portal forwards mails sent to a user profile to the inbox of the IMP identity corresponding to the connected relationship.
+
+For simplification purposes, the option of the user to send mails to the administration portal is left out.
+
+\subsection{Evaluation}
+
+The approach of this IMP solution is to map partial identities to IMP relationships.
+This section evaluates the advantages and disadvantages of this approach as well as its application in the OZG context.
+
+\paragraph{Advantages}
+
+User profiles are known to the existing system architecture and are an often used identity management solution.
+Many service providers, especially in the private sector will want to keep using a profile based identity management approach.
+The IMP solution presents an opportunity of leveraging existing user profile systems while simplifying identity management through IMP.
+In addition to that, the IMP solution is designed, so that it can almost effortlessly be turned on and off, giving service providers the freedom of testing the solution.
+Service providers can initially add the IMP solution as an alternative to the conventional user profile identity management solution and after some period of time switch to only using the IMP solution.
+
+Mapping user profiles to IMP relationships has many of the usability advantages described in section 3.2.
+The onboarding process is simplified.
+Users don't have to manually fill in a form for the creation of a user profile but are supported by the IMP client.
+As part of established relationships, service provider and users are able to directly exchange messages with structured content.
+In addition to interaction capabilities of the IMP client, this enables a variety of interaction scenarios not possible through for example common e-mail clients.
+In this case, scenarios for attribute changes, user profile authentication and communication are made possible.
+
+This approach also increases data protection by providing the user with information on exactly which personal information is shared and how it is being processed as part of the profile creation process.
+This helps users in making an informed decision on whether to create the user profile.
+At any time after the onboarding process, users can view the relationship in the IMP client and check which service providers process which personal information and how.
+This enables users to keep an overview of the distribution of personal information.
+
+Security is also increased as a result of this approach.
+Through established relationships, service provider and users have the ability to not only directly exchange messages but also securely.
+As a result of that, authentication through the IMP client can replace password based authentication methods.
+This eliminates the risk of weak or stolen passwords.
+
+In case of the OZG, this IMP solution can eventually replace the need for interoperable user profiles.
+In case each administration portal enables onboarding as described by the IMP solution, regarding usability, the existence of a separation of user profiles can be transparent to the user but regarding data protection, the user profiles are strongly separated:
+
+After an effortless onboarding process on multiple administration portals, users are able to manage each profile through the IMP client.
+This enables users break free access to all user profiles giving the illusion of an interoperable user profile.
+Logging in to a user profile using the IMP client eliminates the need of remembering passwords, furthering the illusion of interoperable user profiles.
+Finally, if for each user profile, the same profile name is selected, the user wont be able to distinguish user profiles most of the time.
+
+However in cases where the user requires distinction between user profiles in regard to data protection, the IMP client enables the user to separately view personal information shared with each portal and information about how each portal processes it.
+
+\paragraph{Disadvantages}
+
+The IMP solution has also several problems regarding usability and data protection.
+
+Most importantly, as a result of integrating the IMP system through user profiles, each administration portal is still required to access personal information.
+
+In addition to that, application and management of administrative services remains accessible only through administration portal and form server which presents a discontinuity in accessing OZG services.

### 2021-03-04 sections/11-technological_integration.tex
message chapter started

@@
-This section describes a messaging architecture enabling the integration of the IMP solution described in the previous section into the existing OZG system architecture.
+In this section an integration architecture is presented for integration of the IMP system presented in section 2.2 into the existing OZG system architecture presented in section 3.3.
+
+\subsection{Integration Requirements}
+Purpose of the integration architecture is to enable the existing OZG system to access IMP services according to the previously described IMP solution.
+It therefore has to enable the creation of onboarding relationship template, the processing of onboarding relationship requests and the processing of established relationships through creation of user profiles.
+
+In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution. This are messages for attribute changes, communication and authentication.
+
+As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless translation between the two entities.
+
+OZG system architecture and IMP systems use different data models, especially in regard to personal information. The integration architecture therefore has to translate between them.
+
+As the IMP connector is not capable of sending asynchronous notifications, the integration architecture has to add this functionality.
+
+Depending on the use case of service providers, multiple types of relationships or in this case multiple types of user profiles might be necessary.
+
+The integration architecture has to enable each type of relationship and user profile to be processed separately, as they might have different processing legitimization.
+
+OZG and the presented IMP solution are only one example of a system architecture and IMP use case.
+The integration architecture should be able to be used in various different scenarios.
+It therefore has to be configurable and expandable in order to meet new requirements.
+
+\subsection{Messaging}
+For the technological integration, a messaging approach is used.
+
+The reasons are ...
 
@@
 For integration, an IMP connector and a messaging system are added to the portal domain.
-Using the messaging system, existing systems of the administration portal can access IMP services trough the IMP connector.
+Using the messaging system, existing systems of the administration portal can access IMP services through the IMP connector.
 
@@
 On the side of the administration portal, messaging adapters provide an API to the existing systems providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
-The adapters communicate with the messaging system trough publish-subscribe datatype channels.
-Each datatype channel contains messages with the same datatype and has a defined purpose.
-All systems, consuming messages from the channel are aware of this purpose and process consumed messages accordingly.
-Messages placed on a publish-subscribe channel can be simultaneously accessed by multiple systems which subscribed to the channel.
+The adapters communicate with the messaging system through channels.
+Messages placed on each channel can be simultaneously accessed by multiple systems.
 Using these channels, message adapters can send requests, receive replies, receive notifications, receive requests and send replies.
@@
 
-Messaging adapters do not communicate directly trough channels, but with messaging modules.
+Messaging adapters do not communicate directly through channels, but with messaging modules.
 Messaging modules consist of messaging patterns which are able to modify, delete and route messages.
@@
 As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which is built upon it.
-As described in section 2.2, communication between IMP identity and service provider is only possible trough an established relationship.
+As described in section 2.2, communication between IMP identity and service provider is only possible through an established relationship.
 
@@
 For example the mail module consumes messages which contain a mail received by a user profile.
-It is very likely, that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types.
+It is very likely that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types.
 The mail module therefore has to convert the format of the mail content.
@@
 The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.
+
+\subsection{Evaluation}
+
+The messaging system and the modular approach make integration architecture expandable and configurable for new integration scenarios.
+
+Message mapping module and relationship mapping module enable the translation between user profile and relationship.
+
+Onboarding template, onboarding request and onboarding relationship module enable the definition and utilization of one or more relationship types.
+
+Message modules enable the definition of message types.
+
+Message processing modules enable the translation between data models.
+
+Messaging system enables asynchronous, event based and direct communication between user and service provider.
+
+Assigning special modules to each type of relationship and message type enables the separation of processing depending on differences in processing legitimization.

### 2021-03-04 sections/13-imp_solution_integration.tex
message chapter started

@@
 The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection.
-The IMP solution described in this chapter puts the individual institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.
+The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.
 
-Applications submitted to administration portals will eventually be submitted to responsible governmental institutions.
+\subsection{Relationship Utilization}
+
+As part of the existing operation of the OZG system architecture, applications submitted to administration portals will eventually be transferred to responsible governmental institutions.
 Using IMP, relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.
+
 Each institution has a predetermined set of administrative services it can process.
-For each administrative service, the institution can create relationship templates, containing a description of the service along with attributes required by the user:
+For each administrative service, the institution can create a relationship template, containing the description of the service, the list of attributes required from the user necessary for processing the application and information on how the personal information will be processed:
 
@@
 
-Based on these relationship templates, users and institutions can establish relationships.
-In contrast to the IMP solution of chapter 4, an established relationship does not result in the creation of a user profile.
-Instead, relationships represent a single application process and the attributes shared as part of the relationship are used by the institution to process the corresponding administrative service.
-After finishing the service, the relationship can be terminated, removing access to the shared attributes from the institution.
+In contrast to relationship templates in the previous IMP solution, these wont have to be dynamically created but only once.
+The reason is, that in the previous IMP solution templates had to contain personalized information like the session ID.
+This is not necessary in this case.
 
-While processing the administrative service, institution and user can securely and directly exchange data such as mails trough the IMP system without the need of an administration portal or user profile being involved.
+Once the templates are created, the corresponding template IDs can be rendered as QR code on the web page of the institution.
+If the content of a template has to be changed, an employee can be manually create a new template and switch the template IDs on the web page.
 
-Providing an attribute change feature as described in chapter 4, can enable users to request modification of attributes of an active application.
-The institution can then decide whether to accept or reject the request.
+Visiting the web page of the institution, the user can scan the QR code and is presented with the relationship template.
+The user can read trough the included description of the corresponding administrative service to determine if it is the correct one.
+Based on the requested attributes and the information of how they are processed, the user can make an informed decision whether to apply for the administrative service.
 
-For users to access the relationship templates, each institution can host its own web page which lists all administration services along with the corresponding QR code containing the template.
+When sending the relationship request, the institution directly receives it without an administration portal being involved.
+Based on the shared attributes, the institution can decide to either accept or reject the application request.
+It might for example verify if the home address of the user lies in the area of its responsibility.
 
-However, depending on for example the home address of the user, the institution responsible for processing an administrative service can change.
-Therefore the administration portals connected trough the online gateway can be used as a "search-engine" for institutions.
-On any administration portal a user can select an administrative service and specify his home address.
-Based on this information, the portal is able to determine the institution responsible for processing the request.
-However, instead of requiring the user to login to a profile, the portal can redirect him to the web page of the institution where the relationship templates are being displayed.
+When accepting the relationship and therefore the application request, and the user did not retract his request in the meantime, the relationship is established and the institution gets notified of a new application.
+
+After the administrative service is finished, the relationship can be terminated and the institution loose access to all shared personal information.
+
+However, the administration portal cannot be completely replaced.
+It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address.
+Therefore, users visit any administration portal, search for an administrative service and specify their home address.
+The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.
+
+\subsection{Message Utilization}
+
+This IMP solution utilizes the same message types as the previous IMP solution however with a different purpose.
+
+\paragraph{Attribute Synchronization}
+
+Trough the IMP client users can request attribute changes for established relationships.
+The purpose of these messages is to enable uses to change the content of an application even after it was submitted.
+
+\paragraph{Communication}
+
+As in the previous IMP solution, users should be able to receive mails from every institution trough the IMP client.
+Each mail is associated to a relationship, enabling the user to easily correlate mails to active applications.
+
+\paragraph{Authentication}
+
+As no user profiles are necessary in this IMP solution, users wont have to use the IMP client for logging into a user profile.
+However, authentication messages can still be used as an accept / reject based communication method.
+
+\subsection{Evaluation}
+The approach of this IMP solution is to map temporary business processes to IMP relationships.
+This section evaluates the advantages and disadvantages of this approach as well as its application in the OZG context in comparison to the previous IMP solution.
+
+\paragraph{Advantages}
+
+As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information.
+Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes.
+The user can better control whether he agrees to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved.
+In case of the OZG, the user profile component did require authentication prior to sharing attributes with institutions, but this might not be the case for all service providers.
+
+Using relationships for execution of business processes eliminates the need for service providers to operate identity management systems.
+It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution.
+This leaves the service provider with the main task of executing the business processes.
+
+The IMP solution enables users to share personal information directly with responsible institution, restricting access to for example administration portals.
+It also enables direct and secure exchange of messages.
+As a result of the direct mapping of relationships to applications, users can request the modification of application content even after submission.
+
+The IMP solution can also operate alongside the previous IMP solution and eventually replace it.
+
+\paragraph{Disadvantages}
+
+The disadvantage of this IMP solution is, the invasive integration, which does not only provide an alternative way of accessing existing systems but for the most part replaces them.

### 2021-03-04 sections/14-technological_integration.tex
message chapter started

@@
-This section describes the integration of the IMP solution presented in section 5.1 using the same messaging system as described in section 4.2.
+This section describes how the messaging system described as part of the previous chapter can be reused for the IMP solution described in this chapter.
+
+\subsection{Integration Requirements}
+
+Focus of the technological integration in this case is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
+The layout of the messaging system should not change and the purpose of each module should stay the same.
+In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.
 
@@
 
-The layout of the messaging system is identical to the one presented in section 4.2. Exactly the same type of messages are exchanged with however, a slightly different purpose and content.
+The layout of the messaging system is identical to the one presented in section 4.2.
+Exactly the same type of messages are exchanged with however, a slightly different purpose and content.
+Therefore, in this and the following sections, only important differences between the operation of the messaging system will be described.
 
@@
 For an established relationship, instead of issuing the existing system architecture to create a user profile, the application relationship module issues the existing system architecture to process an application based on the attributes shared as part of the relationship.
-And instead of a user profile ID, the existing system architecture responds with an application process reference ID.
-This application process reference ID is used in the same way as the user profile ID in section 4.2.
+And instead of a user profile ID, the existing system architecture responds with an application process ID.
+This application process ID is used in the same way as the user profile ID in section 4.2.
 Trough the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.
@@
 On the "Communication Integration Layer", the same types of messages are exchanged.
-However instead of user profile IDs, relationship IDs are mapped to application process reference IDs.
+However instead of user profile IDs, relationship IDs are mapped to application process IDs.
 In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs in order to for example distinguish a enterprise profile from the profile of a private person.
-In this case, modules can distinguish between different application types based on the application process reference ID.
+In this case, modules can distinguish between different application types based on the application process ID.
 
-...... Hier muss noch mehr kommen (ausführlicher) .......
+\subsection{Application Template Module}
+
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/4. Application Template Module.pdf}
+\end{center}
+
+Relationship templates are created manually and stored as a QR-code image on the web page of the institution.
+Fore each application type, a separate application template module can be included which stores the configuration for the template type and issues the connector to create new relationship templates.
+Instead of the web page, the institution system is connected, as application templates are not dynamically created for user requests but once by an employee of the institution.
+Each time, the content of an application template has to be changed, the institution creates a new one trough this module.
+
+\subsection{Application Request Module}
+
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/5. Application Request Module.pdf}
+\end{center}
+
+For each type of application relationship, a different application request module is used to separate the processing of requests for different application types into application request processing modules.
+Depending on the type of application, different requirements regarding the acceptance of application requests exist.
+A request processing module might for example check if the home address of the user lies in the are of responsibility of the institution.
+Only after the relationship and therefore the application request is accepted will the application be processed.
+
+\subsection{Application Relationship Module}
+
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/6. Application Relationship Module.pdf}
+\end{center}
+
+For each type of application relationship a different application relationship module is used for processing established relationships.
+The institution system is notified of an accepted application trough the "Process Application Request" channel.
+As part of the existing system architecture, institution systems received applications trough the data exchange platform as an application document.
+In order to adhere to this standard, the message translator connected to the "Process Application Request" channel translates the relationship content into the application format of documents delivered trough the data exchange platform.
+As explained in section 2.3.2, form servers create the application documents based on a standard defined by FIM.
+
+Institution systems are assumed to uniquely reference active applications with process IDs.
+After starting the application process, the institution responds trough the messaging adapter with the process ID on the "Application Process Reference Response" channel.
+This process ID is then published on the "New Relationship Mapping" channel.
+The result is, that in contrast to the messaging system of chapter 4, relationships are not mapped to user profiles but to application processes.
+
+\subsection{Application Attribute Change Request Module}
+
+\begin{center}
+    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/7. Application Attribute Change Request Module.pdf}
+\end{center}
+
+As an example for a message type processed on the "Communication Integration Layer", the application attribute change messages are selected.
+
+In the same way as in chapter 4, attribute change message types are published on individual channels, this time however, instead of a user profile ID, they contain a process ID.
+As described on the example of different user profile ID types in chapter 4, different process ID types may exist in this case too.
+For example, an attribute change request for an application of type "A" might be processed differently to an attribute change request for an application of type "B".
+To process different types of attribute change requests separately, multiple application attribute change request modules can be included, each of them filtering for different types of process IDs.
+If it is possible to retrieve the application type from the process ID, processing of each application type could be separated into multiple application change request modules.
+In case, application types are not retrievable from process IDs, an additional module can be included, which requests the application type from the institution system based on the process ID.
+An alternative would be for the application relationship module to not only publish the process ID corresponding to a relationship ID on the "New Relationship Mapping" channel but also the application type.
+
+Only after the attribute change request is accepted, will the institution system be notified of the attribute change.
+
+\subsection{Application Attribute Sync Module}
+
+Continuing the example of how application attribute change messages are processed on the "Communication Integration Layer", the application attribute sync module processes messages on the "Attribute Change Established" channel.
+With the same reasoning as in the previous section, the message filter attached to the channel enables to include multiple application attribute sync modules, processing different application types.
+
+The institution system receives the notification of a modification of the application trough the messaging adapter.
+Depending on the capabilities of the institution system, this could result in either an automated update of the referenced application process or an automated E-Mail to the assigned employee.
+
+\subsection{Application Mail}
+
+Similar to the attribute change messages, mail messages can be fitted to the process based scenario, enabling institutions to send mails to a process ID which the messaging system translates to a relationship ID in order for the correct IMP identity to receive it.
+In addition to the one directional message transfer from the institution to the IMP identity, the application mail module and the mail message module could be expanded to be able to receive mails from an IMP identity trough an established relationship.
+The relationship ID of the message would be mapped to the corresponding process ID and submitted it to the institution system.
+The institution system could then send the mail to the responsible employee.
+
+\subsection{Application Authentication}
+
+Authentication messages and modules are not required for this IMP solution, as no user profile and therefore no login process exists.
+However, depending on the use case, authentication messages could be included as an additional accept / reject communication method between institution and user.
+
+\subsection{Evaluation}
+The integration architecture enables users to directly interact with the system architecture of the service provider for submitting applications.
+This eliminates the need for administration portals to process personal information.
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/OZG Personal Information.pdf}
+\end{center}
+
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
+\end{center}
+
+Comparing the existing system architecture of the OZG with the system architecture utilizing IMP, the amount of systems processing personal information is reduced.
+Using this IMP solution, only the user and the responsible institution have access to personal information.
+
+The integration architecture described in section 4.2 was able to integrate into two different system architectures.
+This demonstrates, that the presented integration architecture is applicable to a variety of system architectures.
+
+It was also able to integrate a user oriented (persistent) relationship scenario as well as a process oriented (temporary) relationship scenario.
+This demonstrates, that the presented integration architecture can be used for integrating a variety of IMP solutions.
+
+The modular message based approach made it possible to use the integration architecture in a different scenarios, by enabling easy configuration of modules for new requirements.

### 2021-03-04 sections/4-terminology.tex
message chapter started

@@
 
-Identifiers which are commonly used by SPs are the phone number and E-Mail address.
+Identifiers which are commonly used by SPs are the phone number and e-mail address.
 Attributes are for example nicknames, hobbies, interests or education.
@@
 Identity management systems are solutions which enable SPs and customers to manage identities or partial identities.
-They usually provide the following functionalities an properties:
+They usually provide the following functionalities and properties:
 \begin{itemize}
@@
 User profiles are one method for identity management.
-They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.
+They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management (CRM) system for accessing identities internally and a website with online self-service tools for providing access to customers.

### 2021-03-04 sections/5-imp.tex
added textual descriptions
message chapter started

@@
 
-    Requested Attributes is a list of attribute keys, the user will have to submit as part of the relationship request.
+    Requested Attributes is a list of attribute keys the user will have to submit as part of the relationship request.
 
@@
 
-    Shared Attributes is a list of attribute keys and values, the service provider wakes available to any user interested in requesting this relationship.
+    Shared Attributes is a list of attribute keys and values the service provider makes available to any user interested in requesting a relationship.
 The service provider has to share a minimal amount of attributes which enable the user to identify it.
@@
 
-    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested by the user are necessary for it.
+    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested from the user are necessary for it.
 
@@
 
-The integration tool for the service provider does not understand the content of messages but simply makes the accessible by the system architecture of the service provider.
+The integration tool for the service provider does not understand the content of messages but simply makes them accessible by the system architecture of the service provider.
 Without additional integration solutions, the service provider has to implement his own solutions for processing the different types of messages.
@@
 \paragraph{Security}
-The IMP system guarantees, that all information is encrypted and can only be decrypted by identities which are allowed to read it.
+The IMP system guarantees that all information is encrypted and can only be decrypted by identities which are allowed to read it.
 Only the owner of an identity can manage attributes of his identity.
@@
 The user is also provided with information on why the relationship and request attributes are necessary which helps the user in deciding if he agrees with the necessity of sharing the information.
-As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relation for each business process which requires access to personal information.
+As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relationship for each business process which requires access to personal information.
 The information therefore can not only be shared with a single service provider but also for an individual process.
@@
 Depending on the price of the IMP solution, this can reduce the cost for operating and maintaining the system architecture.
-The service provider has to hire less personal, does not have to buy expensive hardware and can more easily scale the performance of his system.
+The service provider has to hire less staff, does not have to buy expensive hardware and can more easily scale the performance of his system.
 As previously described, the user experience can also increase and lead to more customers.
@@
 The IMP system operates on three domains.
-The user domain contains systems, the user directly interacts with.
-This typically are applications on PC or smartphone and websites.
+The user domain contains systems the user directly interacts with.
+These typically are applications on PC or smartphone and websites.
 The IMP system provides an application for PC and smartphone to the user for accessing IMP services.
@@
 
-The operation of IMP systems can be separated in multiple layers.
+The operation of IMP systems can be separated into multiple layers.
 The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.
@@
 
-As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector trough its REST interface.
+As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector through its REST interface.
 The connector responds with the received relationship request.
 The system architecture of the service provider processes the request in order to decide if it should be accepted.
-The service provider could for example verify if a relationship with the identity already exists or if the E-mail address is already registered.
+The service provider could for example verify if a relationship with the identity already exists or if the e-mail address is already registered.
 
@@
 The connector sends the relationship response to the IMP server which updates the content and status of the corresponding relationship.
-It might be possible, that the user retracted the relationship request in the meantime.
+It might be possible that the user retracted the relationship request in the meantime.
 In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
@@
 
-After receiving the final relationship established notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.
+After receiving the final "relationship established" notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.
 
@@
 The list of messages an IMP client understands can be expanded by the identity management provider.
-It can therefore be assumed, that the IMP client understands any message service providers often want to exchange.
+It can therefore be assumed that the IMP client understands any message service providers often want to exchange.
 For simplicity, in the following sections, behaviour of the IMP client for newly defined message can be defined at will.
@@
 
-It is possible, that in the future, the user wants to change the mail address where he receives the newsletter.
+It is possible that in the future, the user wants to change the mail address where he receives the newsletter.
 As the established relationship remains to be valid, it should not be terminated, but shared attributes should be changed instead.
@@
 Through the IMP client, the user can view the corresponding relationship and edit the attributes.
-After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends a attribute change request message to the connector.
+After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends an attribute change request message to the connector.
 The connector does not understand the content of the message but from which relationship it originated from.
@@
 
-The system architecture evaluates if it accepts the changes and sends a response trough the REST interface of the connector.
+The system architecture evaluates if it accepts the changes and sends a response through the REST interface of the connector.
 The system architecture might execute additional processes.
@@
 
-The IMP server receives the response message through the connector and routs it to the IMP client.
+The IMP server receives the response message through the connector and routes it to the IMP client.
 The IMP client understands the message, updates the value stored as part of the relationship and displays a notification to the user.
@@
 If a user has questions about the newsletter, he can send messages to the service provider as part of the relationship.
-Client sends the mail message to the IMP server which routes it to the connector.
+The client sends the mail message to the IMP server which routes it to the connector.
 The system architecture polls for incoming messages.
 When the system architecture receives the message, it understands the content and purpose and for example notifies an employee.
-An employee could be notified through E-Mail and a response from the employee to the mail could automatically sent to the relationship through the REST API of the connector.
+An employee could be notified via e-mail and a response from the employee to the mail could automatically be sent to the relationship through the REST API of the connector.
 Connector and IMP server route the message to the IMP client, who understands the message and displays it to the user.
@@
 \end{figure}
-
-\section{}

### 2021-03-04 sections/6-online_access_law.tex
added second integration
message chapter started

--- 2021-01-28 sections/5-online_access_law.tex
@@
 In order to save investments a method called "one for all" is used when hosting administrative services.
-One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood".
+One member state or the federal republic provides access to a service on their administration portal and distributes the requests to the responsible institutions "under the hood".
 As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal.
@@
 Each process consists of multiple sub-processes.
-When comparing the processes, one can see, that some sub-processes occur very often and in similar arrangements.
+When comparing the processes, one can see that some sub-processes occur very often and in similar arrangements.
 Those arrangements can be called the basic use case of OZG services.
@@
 \subsection{System Architecture}
-This subsection describes the system architecture of a member state relevant for the execution the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen.
-Systems, which are responsible for coordination of OZG execution between member states and the federal republic are not the focus.
+This subsection describes the system architecture of a member state relevant for the execution of the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen.
+Systems responsible for coordination of OZG execution between member states and the federal republic are not the focus.
 
@@
 
-\begin{figure}[h]
-\caption{Overview IMP System}
-    \centering
-    \includegraphics[scale=0.25]{Diagrams/OZG System Overview.png}
-\end{figure}
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/OZG System Overview.pdf}
+\end{center}
 
@@
 The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components.
-The most important components, the service facade provides an interface for are:
+The most important components the service facade provides an interface for are:
 
@@
 
-    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and sent messages to an institution.
+    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.
 
@@
 Form server and portal communicate about the status and content of the application.
-The user is able to keep track about the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.
+The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.
 
@@
 
-    \textit{Service blocks} contain human readable descriptions about a administrative service.
+    \textit{Service blocks} contain human readable descriptions about an administrative service.
 
@@
 
-    \textit{Data fields} are the "smallest entity" of a data field block and describes one standardized piece of information.
+    \textit{Data fields} are the "smallest entity" of a data field block and describe one standardized piece of information.
 Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.
@@
     Each data field block can be uniquely identified through an ID.
-Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data filed block from the central storage.
+Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data field block from the central storage.
 
@@
 
-    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.
+    Depending on the actions of the user, the status of the application changes accordingly and the form server sends a status update.
 
@@
 The user can register and login to the user profile using a username / password combination or the German ID card.
-The trust level "High" is only granted, if the user registered using the German ID card \textbf{AND} logs in using the German ID card.
+The trust level "High" is only granted if the user registered using the German ID card \textbf{AND} logs in using the German ID card.
 All other combinations of registration and login result in a "normal" trust level.
@@
 
-    The user can attach a copy of a document stored in his data wallet to an application on a from server.
+    The user can attach a copy of a document stored in his data wallet to an application on a form server.
 
@@
 
-    The user can be notified of a new message through E-Mail.
+    The user can be notified of a new message through e-mail.
 
@@
 \subsubsection{Interfaces}
-In order to implement the basic use case, the components have to interact with each.
+In order to implement the basic use case, the components have to interact with each other.
 The following diagram visualizes, which components interact.
@@
 \begin{center}
-    \includegraphics[width=8cm]{Diagrams/Interaction Diagram.png}
+    \includegraphics[scale=0.6]{Diagrams/Interaction Diagram.pdf}
 \end{center}
@@
     \item The form-server can initiate the application if requested by the administration portal.
-The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID.
+The portal submits information for identification, authentication and authorisation of a user through a JSON Web Token and a user profile ID.
 In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata.

### 2021-03-04 sections/7-messaging.tex
message chapter started

This chapter gives a brief overview of what messaging is and how it can be used for system integration purposes. It introduces various messaging patterns which will be used by the technological integration of chapter 4 and 5.
The content of this chapter is based on the book \textit{Enterprise Integration Patterns} by \textcite{EIP}.

\section{Messaging}

Messaging is an asynchronous system-to-system communication, delivering packages of data called messages trough channels. Messages can contain any structured data like strings, arrays or objects. It is up to the sender and receiver to determine and understand its content.

Channels can be seen as a collection or array of messages, accessible to interested systems. Channels have a direction in a sense, that no system simultaneously writes to and reads from a channel. Therefore, by one system writing messages to a channel and another system reading them, a message and data flow can be established.

Depending on the use case, the flow and destination of messages might have to be determined during operation. Therefore, various message routing components exist. Their purpose is to transfer messages from an inbound channel to one or more outbound channels, depending on predefined or dynamic rules.

During the routing of messages between systems, the content of messages might have to be modified. Therefore various message transformation components exist. Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message on a outbound channel.

"\textit{A messaging system manages messaging the way a database system manages data persistence}" \cite[p. 31]{EIP}. Configuring a messaging system involves definition of available channels, the type of messages they exchange, their connection between systems, the message flow and where necessary the insertion of routing and transformation components.

Depending on the messaging system solution, additional features can be configured to increase performance, stability, failure safety and more. If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently store messages in case of a system crash.

\section{Messaging Integration}

One use case for a messaging system is integration.

The main benefit of messaging for integration is, that it enables systems to share services and data in a decoupled way. Neither system, whether sending or receiving messages, needs to be aware of each other.

During configuration of the messaging system, datatype channels can be defined. On these channels, only messages with the same content are exchanged. Using message transformation components, messages placed on a datatype channel can be translated to follow a canonical data model.

Systems consuming messages from datatype channels can individually assign a purpose to channels independent from the sending system. As a result of the canonical data model, receiving systems can also choose a data structure independent from the sending system.

As channels are able to function as a message buffer, sender and receiver of messages do not even have to be running at the same time.

\section{Messaging Patterns}

In the book "\textit{Enterprise Integration Patterns}" by \cite{EIP} multiple patterns for designing messaging systems are presented. This section gives a brief overview of patterns relevant for the thesis.

\paragraph{Message}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/1. Message.pdf}
\end{center}

\paragraph{Channel}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/2. Channel.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/3. Channel.pdf}
\end{center}

\paragraph{Messaging Adapter}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/4. Messaging Adapter.pdf}
\end{center}

\paragraph{Message Router}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/5. Message Router.pdf}
\end{center}

\paragraph{Message Translator}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/6. Message Translator.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/7. Message Translator.pdf}
\end{center}

\paragraph{Message Filter}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/8. Message Filter.pdf}
\end{center}

\paragraph{Content Enricher}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/9. Content Enricher.pdf}
\end{center}

\paragraph{Content Filter}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/10. Content Filter.pdf}
\end{center}

\paragraph{Message Store}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Messaging/11. Message Store.pdf}
\end{center}

### 2021-03-04 sections/9-imp_utilization_in_ozg.tex
textualizing
message chapter started

--- 2021-02-21 sections/9-imp_utilization_in_ozg.tex
@@
-Like many online self-service platforms, the system architecture responsible for implementing the OZG relies on user profiles for managing identities.
-In case of the OZG, identity management is especially complicated due to the federated model of interoperable user profiles.
-Each member state has to provide its own user profile system which can be utilized through every administration portal.
-This solution is expensive to develop and maintain, as communication between multiple member states and institutions is required.
+This chapter presents an IMP solution which solves issues of OZG identity management described in chapter 3.
+For utilization of IMP services as described by the IMP solution, an integration architecture is presented which enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.
 
-Goal of the integration solution is to introduce features of the IMP system into the OZG system architecture.
-All existing services should be accessible the same way as before but with additional options for using IMP.
-The focus of this initial integration is to avoid disruption of existing system operation through non-invasive integration, to enable a fast and simple introduction of IMP features and to provide future upgrade capabilities.
+Focus of the IMP solution and the integration architecture is to require minimal invasion into the existing system architecture: Few existing system components should have to be modified and the existing operation of the system should not be disrupted.
+The IMP solution should provide an additional but optional way for users to access OZG services.
+
 The integration takes place on three layers:
 
-\begin{figure}[h]
-\caption{IMP Layer Diagram}
-    \centering
-    \includegraphics[scale=0.3]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.png}
-\end{figure}
+\begin{center}
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
+\end{center}
 
-\paragraph{IMP Solution Integration Layer} 
-The purpose of the integration on the IMP solution layer is to take advantage of new interaction capabilities with the user through the IMP system.
-The integration evaluates possibilities of using relationships and IMP messages to improve OZG services, defines what the purpose of each message and relationship type is and how they should be handled by client and service provider.
-For example relationship templates can be defined and new message types can be created with corresponding new user interfaces in the IMP client.
+\paragraph{IMP Solution Layer} 
+The IMP solution is integration on the use case level.
+It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the service provider for improvement of usability, data protection and security.
+It describes which types of relationships the service provider can use in his business scenario, how relationships can be processed, which types of messages can be exchanged trough the relationships, what the purpose of each message can be and how the IMP client can react to different message types.
 
-\paragraph{Relationship Integration Layer} The purpose of the integration on the relationship layer is to enable the technological utilization of relationships as described by the integration on the solution integration layer.
+The IMP solution focuses on utilizing IMP capabilities in a way which affects the existing operation of the system architecture the least while solving as many identity management issues described in section 3.1 as possible.
 
-\paragraph{Communication Integration Layer} The purpose of the integration on the communication layer is to enable the technological utilization of messages as described by the integration on the solution integration layer.
+\paragraph{Technological Integration} 
+The technological integration is integration on the system level.
+It consists of an integration architecture enabling the existing systems of the service provider to utilize the IMP system as described by the IMP solution.
+It is separated into a "Communication Integration Layer" and a "Relationship to Identity Integration Layer".
+On the "Relationship to Identity Integration Layer" the integration architecture enables the existing systems to create relationship templates and establish relationships.
+On the "Communication Integration Layer" it enables the existing systems to send and receive different types of IMP messages.
+
+Focus of the technological integration is to connect with as few existing systems as possible while solving as many integration issues described in section 3.3 as possible.
 
@@
 
-This section evaluates possibilities of a technological integration architecture for realizing the integration solution described in the previous section.
-
 \subfile{11-technological_integration}

### 2021-03-04 sections/11-technological_integration.tex
messaging chapter done

@@
 For the technological integration, a messaging approach is used.
+As described in section 2.4, messaging enables system to access each others services in a decoupled way.
+This is a useful feature as the integration architecture should reusable for different system architectures.
 
-The reasons are ...
+The messaging patterns described in 2.4 also enable the integration architecture to be configured according to changes in the operation of the existing systems.
+
+The asynchronous nature of messaging systems translates nicely to the asynchronous and message based operation of the IMP system and IMP solution.
 

### 2021-03-04 sections/7-messaging.tex
messaging chapter done

@@
 In the book "\textit{Enterprise Integration Patterns}" by \cite{EIP} multiple patterns for designing messaging systems are presented.
-This section gives a brief overview of patterns relevant for the thesis.
+This section gives a brief overview of patterns relevant for the thesis and their visual notation.
 
@@
 
-\begin{center}
+Figure \ref{messaging:message} shows the visual notation of a message with two attributes.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/1. Message.pdf}
-\end{center}
+    \caption{Message}
+    \label{messaging:message}
+\end{figure}
 
@@
 
-\begin{center}
+Figure \ref{messaging:channel1} shows the visual notation of an unnamed channel. Arrows to a message symbol are not a notation for channels but for message flow.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Messaging/3. Channel.pdf}
+    \caption{Unnamed Channel}
+    \label{messaging:channel1}
+\end{figure}
+
+Figure \ref{messaging:channel2} shows the visual notation of a named channel.
+Arrows to and from named channels are no notation for channels but for message flow.
+Channels are named if they have a special importance.
+
+There exist different types of channels.
+In the thesis, named channels are publish-subscribe datatype channels.
+Unnamed channels are point-to-point channels.
+Publish-subscribe channels can be accessed by every system.
+In contrast to that, point-to-point channels can only be accessed by two systems - one writing and one reading system.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/2. Channel.pdf}
-\end{center}
-
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Messaging/3. Channel.pdf}
-\end{center}
+    \caption{Named Channel}
+    \label{messaging:channel2}
+\end{figure}
 
@@
 
-\begin{center}
+Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system trough an API.
+The messaging adapter usually has to be developed for each system individually, and manually integrated into the code of the system trough asynchronous function calls of the adapter API.
+
+Figure \ref{messaging:adapter} shows the visual notation of a messaging adapter connected to a system.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/4. Messaging Adapter.pdf}
-\end{center}
+    \caption{Messaging Adapter}
+    \label{messaging:adapter}
+\end{figure}
 
-\paragraph{Message Router}
+\paragraph{Content-Based Router}
 
-\begin{center}
+Content based routers contain a preconfigured set of routing rules, which instruct the router to place inbound messages on different outbound channels, depending on their content.
+The definition of the rules does not change during operation of the system.
+
+Figure \ref{messaging:router} shows the visual notation of a message router.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/5. Message Router.pdf}
-\end{center}
+    \caption{Message Router}
+    \label{messaging:router}
+\end{figure}
 
@@
 
-\begin{center}
+Message translators have the purpose of translating message content on data representation and data type layer.
+On the data representation layer, message translators for example translate message content from an XML format to a JSON format.
+On the data type layer, message translators can for example concatenate first name and last name fields to a single name field.
+
+Figure \ref{messaging:translator1} shows the visual notation of a message translator.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/6. Message Translator.pdf}
-\end{center}
+    \caption{Message Translator}
+    \label{messaging:translator1}
+\end{figure}
 
-\begin{center}
+As shown in figure \ref{messaging:translator2}, if using two message translators on both sides of a channel, a canonical data model can be created in between.
+For more information, read \textcite[p.
+355]{EIP}
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/7. Message Translator.pdf}
-\end{center}
+    \caption{Message Translator creating Canonical Data Model}
+    \label{messaging:translator2}
+\end{figure}
 
@@
 
-\begin{center}
+Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages, based on their content.
+The definition of the rules does not change during operation of the system.
+
+Figure \ref{messaging:filter} shows the visual notation of a message filter.
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Messaging/8. Message Filter.pdf}
-\end{center}
+    \caption{Message Filter}
+    \label{messaging:filter1}
+\end{figure}
+
+As shown in figure \ref{messaging:filter2}, message filters can, in combination with publish-subscribe channels, be used to separate messages onto individual datatype channels.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Messaging/9. Message Filter.pdf}
+    \caption{Message Filter Separating Message Types}
+    \label{messaging:filter2}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Messaging/9. Content Enricher.pdf}
-\end{center}
+Content enricher have the purpose of adding new attributes to messages. The content which is added usually is a predetermined set of attributes but with dynamically created values.
+
+Figure \ref{messaging:enricher} shows the visual notation of a content enricher.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Messaging/10. Content Enricher.pdf}
+    \caption{Content Enricher}
+    \label{messaging:enricher}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Messaging/10. Content Filter.pdf}
-\end{center}
+Content filters have the purpose of removing a predetermined set of attributes from messages.
+
+Figure \ref{messaging:filter3} shows the visual notation of a content filter.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Messaging/11. Content Filter.pdf}
+    \caption{Content Filter}
+    \label{messaging:filter3}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Messaging/11. Message Store.pdf}
-\end{center}
+Message stores have the purpose of storing consumed messages in a database.
+They are also capable of communicating with other messaging patterns for providing access to stored messages.
+Communication between message patterns and message stores is indicated by a dotted arrows.
+
+Figure \ref{messaging:store} shows the visual notation of a message store. It also shows the example of a content enricher accessing the message store.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Messaging/12. Message Store.pdf}
+    \caption{Message Store}
+    \label{messaging:store}
+\end{figure}

### 2021-03-06 chapters/2-background_and_related_work.tex
überarbeitung

This chapter covers three important topics, following chapters rely on.

Identity Management Provisioning is introduced as a new identity management method. Its features along with system components and important use cases are described.

The Online Access Law is introduced as a currently relevant regulation with special requirements for identity management. The most important regulations as well as resulting system architectures for its implementation are described.

Messaging is introduced as a way of designing integration architectures. Multiple messaging patterns as well as their visual notation are described.

\section{Identity Management Provisioning (IMP)}
\subfile{sections/5-imp}

\section{Online Access Law (OZG)}
\subfile{sections/6-online_access_law}

\section{Messaging}
\subfile{sections/7-messaging}

### 2021-03-06 chapters/sections/1-context.tex
überarbeitung

--- 2021-03-04 sections/1-context.tex
@@
 Since invention of the World Wide Web, the number of its users increased rapidly.
-Today, more than 90 percent of the german population uses the internet \cite{Onlinestudie}.
+Today, more than 90 percent of the German population uses the internet \cite{Onlinestudie}.
 Enterprises and organizations recognised this potential to provide their services to a large number of people as Service Providers (SP).
@@
 
-Many tools require identification of a user in case interactions or initiated business processes have to be associated with him.
+Many tools require identification of users in case interactions or initiated business processes have to be associated with them.
 A system for management of identities of users therefore is part of numerous system architectures.
-Service Providers usually enable users to manage their partial identities using online self-service through user profiles.
+Service Providers often enable users to manage their partial identities using online self-service through user profiles.
 Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP.
@@
     \item As a result of the distributed identities, risk of data breaches increases.
-    \item Managing multiple user profiles is very inconvenient for users.
-    \item It is often unclear who stores which data and for what purpose.
+    \item Managing multiple user profiles is very inconvenient. Users have to login to various websites to change attributes of each user profile.
+    \item It is often unclear which SP stores which data and for what purpose.
     \item SPs have an incentive to collect and share more user data than they need.
@@
 
-An improved model for identity management is necessary.
+An improved identity management is necessary.
 In recent years, multiple new models have been invented.
 One model called Social Login became popular.
-It enables customers to create User Profiles for SPs through existing User Profiles of Social Networks like Facebook.
+It enables customers to create user profiles for SPs through existing user profiles of Social Networks like Facebook.
 This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes.
@@
 
-This approach, however, still leaves the requirement of User Profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
-SPs also might require additional online self-service tools the social network does not provide.
+This approach, however, still leaves the requirement of user profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
 
-The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and user profiles.
-The system itself is provided and hosted by a SP for consumption by other SPs.
-To replace existing User Profiles, the IMP can not only rely on systems for registration, authentication, authorisation and provisioning.
-Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
+A possible solution to this problem is Identity Management Provisioning (IMP) which enables users to manage their whole online identity instead of partial identities and user profiles.
+Trough IMP relationships, users can share personal information of their IMP identity with service providers and exchange data in form of messages.
+Users remain in control of their identity.
+They share personal information when needed, retract access for service providers when no longer necessary, securely exchange messages, all trough the same service.
 
-In order for an SP to use identities and services of an IMP, an integration into the system architecture of the SP has to take place.
+An Identity Management Host (IMH) hosts an Identity Management Provisioning System (IMPS) to make IMP accessible to service providers.
+In order for a SP to use IMP for identity management, an integration of IMPS into its existing system architecture is necessary.
 Due to the complex nature of system architectures and identity management, this is a difficult task.
 
-A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG).
-It requires all administrative services of the german federal republic, each member state and commune to be digitally available through interoperable user profiles.
-The current plan is to make the profiles only available for usage in context of the OZG.
+A currently relevant example for usage of online self-service with particular interesting requirements for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG).
+It requires all administrative services of the German federal republic, each member state and commune to be digitally available through interoperable user profiles.
+The current plan is to make user profiles only available for usage in context of the OZG.
 From a user perspective, this would be yet another partial identity and user profile to manage.

### 2021-03-06 chapters/sections/11-technological_integration.tex
überarbeitung

--- 2021-03-04 sections/11-technological_integration.tex
@@
 In this case, the web server will want to notify the user about the successful creation of his user profile.
-The web server therefore adds the users current session ID as metadata to the template.
+The web server therefore adds the user's current session ID as metadata to the template.
 
@@
 It might happen, that in the future one of the adapters switches from using for example an XML instead of a JSON data representation.
-Using message translators on each side, enables to adapt to these changes by only appropriately configuring the translator while leaving the rest of the module untouched.
+Using message translators on each side enables to adapt to these changes by only appropriately configuring the translator while leaving the rest of the module untouched.
 
@@
 The module processes an established relationship by initiating the creation of a new user profile.
-First, a message filter lets trough only messages of the onboarding type.
+First, a message filter lets through only messages of type "onboarding".
 Afterwards, each message is stored in a "Relationship Storage" database and published on the "Create User Profile Request" channel.
-However, before publishing the message, a message translator maps attributes form the IMP data model to the OZG data model.
+However, before publishing the message, a message translator maps attributes from the IMP data model to the OZG data model.
 
@@
 
-Trough the "New Relationship Mapping" channel, the "Relationship Mapping" module receives the message sent by the previously described module.
+Through the "New Relationship Mapping" channel, the "Relationship Mapping" module receives the message sent by the previously described module.
 Purpose of the "Relationship Mapping" module is to map relationships to corresponding entities in the existing system architecture.
 In this case, relationships are mapped to user profiles and vice versa using relationship IDs and user profile IDs.
-The message consumed trough the "New Relationship Mapping" channel is stored in a database for enabling future translation between the contained relationship ID and user profile ID.
+The message consumed through the "New Relationship Mapping" channel is stored in a database for enabling future translation between the contained relationship ID and user profile ID.
 Using the "Relationship Mapping Request" channel, modules can request the "Relationship Mapping" module to add a user profile ID for a given relationship ID and vice versa.
@@
 In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a content enricher adds a unique request ID to the message and stores the ID in a database.
-Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let trough by the request ID message filter.
+Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let through by the request ID message filter.
 As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes relationship IDs from the message before publishing it on the "Message Inbound Mapping" channel.
 
-Outbound messages on the "Message Outbound Mapping" channel are processed similar to inbound messages.
-The difference being, that the user profile ID contained in the message is replaced by the corresponding relationship ID.
+Outbound messages on the "Message Outbound Mapping" channel are processed similarly to inbound messages.
+The difference is that the user profile ID contained in the message is replaced by the corresponding relationship ID.
 
@@
 In this case, an "Attribute Change Message Module" is included, which processes messages related to the attribute change process.
-Messages exchanged trough IMP relationships can have arbitrary content, however, the messages are assumed to contain a message type attribute and a message content attribute.
-Based on the message type attribute, a message filter can let messages trough which contain a message type attribute correlating to an attribute change process.
+Messages exchanged through IMP relationships can have arbitrary content.
+However, the messages are assumed to contain a message type attribute and a message content attribute.
+Based on the message type attribute, a message filter can let messages through which contain a message type attribute correlating to an attribute change process.
 Based on the type of a message, a content based message router then copies each message to a datatype channel.
-In this case, messages of type attribute change request and attribute change established are distinguished.
+In this example, messages of type attribute change request and attribute change established are distinguished.
 Corresponding to that, two data type channels exist.
@@
 To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel.
-Messages arriving on the "Attribute Change Request" channel were mapped form a relationship ID to a user profile ID in an earlier integration step.
+Messages arriving on the "Attribute Change Request" channel were mapped from a relationship ID to a user profile ID in an earlier integration step.
 Depending on the use case of the service provider, not all user profiles should be processed in the same way.
@@
 If the user did not cancel the attribute change request before the OZG system accepted, the attribute change is established.
-The connector is notified trough a message, which eventually by processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.
+The connector is notified through a message, which eventually is processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.
 
@@
 
-In order for the user to receive messages sent to his user profile trough the IMP client, mail messages are processed by the integration architecture.
+In order for the user to receive messages sent to his user profile through the IMP client, mail messages are processed by the integration architecture.
 Similar to the "Profile Attribute Change Message" module, a "Mail Message" module is included, which maps messages on the "Mail Outbound" channel to the "Message Outbound Mapping" channel.
@@
 
-A messaging adapter attached to the service facade is notified each time, a user profile connected to an IMP identity receives a mail and publishes a message on the "Profile Mail Outbound" channel.
+A messaging adapter attached to the service facade is notified each time a user profile connected to an IMP identity receives a mail and publishes a message on the "Profile Mail Outbound" channel.
 The message contains the ID of the profile which received the message and the content of the mail.
@@
 
-If the user creates a user profile using his IMP identity, it is possible to replace authentication using a password with authentication trough the IMP client.
+If the user creates a user profile using his IMP identity, it is possible to replace password authentication with authentication through the IMP client.
 It is also possible to use the IMP client for two factor authentication.
@@
 When the user visits the web page of the administration portal to apply for an administrative service, he will have to login.
-To utilize the IMP client for authentication, the web server can use a channel adapter to publish a authentication request concerning a user profile ID and a certain session ID.
+To utilize the IMP client for authentication, the web server can use a channel adapter to publish an authentication request concerning a user profile ID and a certain session ID.
 The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content.

### 2021-03-06 chapters/sections/13-imp_solution_integration.tex
überarbeitung

--- 2021-03-04 sections/13-imp_solution_integration.tex
@@
 In contrast to relationship templates in the previous IMP solution, these wont have to be dynamically created but only once.
-The reason is, that in the previous IMP solution templates had to contain personalized information like the session ID.
+The reason is that in the previous IMP solution templates had to contain personalized information like the session ID.
 This is not necessary in this case.
@@
 Once the templates are created, the corresponding template IDs can be rendered as QR code on the web page of the institution.
-If the content of a template has to be changed, an employee can be manually create a new template and switch the template IDs on the web page.
+If the content of a template has to be changed, an employee can manually create a new template and switch the template IDs on the web page.
 
 Visiting the web page of the institution, the user can scan the QR code and is presented with the relationship template.
-The user can read trough the included description of the corresponding administrative service to determine if it is the correct one.
-Based on the requested attributes and the information of how they are processed, the user can make an informed decision whether to apply for the administrative service.
+The user can read through the included description of the corresponding administrative service to determine if it is the correct one.
+Based on the requested attributes and the information on how they are processed, the user can make an informed decision whether to apply for the administrative service.
 
@@
 
-When accepting the relationship and therefore the application request, and the user did not retract his request in the meantime, the relationship is established and the institution gets notified of a new application.
+When accepting the relationship and therefore the application request, and the user did not retract his request in the meantime, the relationship is established and the institution gets notified about a new application.
 
-After the administrative service is finished, the relationship can be terminated and the institution loose access to all shared personal information.
+After the administrative service is finished, the relationship can be terminated and the institution looses access to all shared personal information.
 
@@
 
-This IMP solution utilizes the same message types as the previous IMP solution however with a different purpose.
+This IMP solution utilizes the same message types as the previous IMP solution, however with a different purpose.
 
@@
 
-Trough the IMP client users can request attribute changes for established relationships.
-The purpose of these messages is to enable uses to change the content of an application even after it was submitted.
+Through the IMP, client users can request attribute changes for established relationships.
+The purpose of these messages is to enable users to change the content of an application even after it was submitted.
 
@@
 
-As in the previous IMP solution, users should be able to receive mails from every institution trough the IMP client.
-Each mail is associated to a relationship, enabling the user to easily correlate mails to active applications.
+As in the previous IMP solution, users should be able to receive mails from every institution through the IMP client.
+Each mail is associated with a relationship, enabling the user to easily correlate mails to active applications.
 
@@
 
-The IMP solution enables users to share personal information directly with responsible institution, restricting access to for example administration portals.
+The IMP solution enables users to share personal information directly with responsible institutions, restricting access to for example administration portals.
 It also enables direct and secure exchange of messages.

### 2021-03-06 chapters/sections/14-technological_integration.tex
überarbeitung

--- 2021-03-04 sections/14-technological_integration.tex
@@
 
-Institutions are able to process a predetermined set of administrative services. For each service, the institution can once create a relationship template and store them as QR code on their web page.
+Institutions are able to process a predetermined set of administrative services. For each service, the institution can create a relationship template once and store it as QR code on their web page.
 
@@
 The layout of the messaging system is identical to the one presented in section 4.2.
-Exactly the same type of messages are exchanged with however, a slightly different purpose and content.
+Exactly the same type of messages are exchanged with however a slightly different purpose and content.
 Therefore, in this and the following sections, only important differences between the operation of the messaging system will be described.
@@
 For simplification, modules only for an "Application A" are shown.
-Besides the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: Each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
+Besides the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
 As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately.
@@
 This application process ID is used in the same way as the user profile ID in section 4.2.
-Trough the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.
+Through the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.
 
@@
 However instead of user profile IDs, relationship IDs are mapped to application process IDs.
-In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs in order to for example distinguish a enterprise profile from the profile of a private person.
+In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs in order to for example distinguish an enterprise profile from the profile of a private person.
 In this case, modules can distinguish between different application types based on the application process ID.
@@
 Relationship templates are created manually and stored as a QR-code image on the web page of the institution.
-Fore each application type, a separate application template module can be included which stores the configuration for the template type and issues the connector to create new relationship templates.
+For each application type, a separate application template module can be included which stores the configuration for the template type and issues the connector to create new relationship templates.
 Instead of the web page, the institution system is connected, as application templates are not dynamically created for user requests but once by an employee of the institution.
-Each time, the content of an application template has to be changed, the institution creates a new one trough this module.
+Each time the content of an application template has to be changed, the institution creates a new one through this module.
 
@@
 Depending on the type of application, different requirements regarding the acceptance of application requests exist.
-A request processing module might for example check if the home address of the user lies in the are of responsibility of the institution.
-Only after the relationship and therefore the application request is accepted will the application be processed.
+A request processing module might for example check if the home address of the user is within the are of responsibility of the institution.
+Only after the relationship and therefore the application request is accepted the application will be processed.
 
@@
 For each type of application relationship a different application relationship module is used for processing established relationships.
-The institution system is notified of an accepted application trough the "Process Application Request" channel.
-As part of the existing system architecture, institution systems received applications trough the data exchange platform as an application document.
-In order to adhere to this standard, the message translator connected to the "Process Application Request" channel translates the relationship content into the application format of documents delivered trough the data exchange platform.
+The institution system is notified of an accepted application through the "Process Application Request" channel.
+As part of the existing system architecture, institution systems received applications through the data exchange platform as an application document.
+In order to adhere to this standard, the message translator connected to the "Process Application Request" channel translates the relationship content into the application format of documents delivered through the data exchange platform.
 As explained in section 2.3.2, form servers create the application documents based on a standard defined by FIM.
@@
 Institution systems are assumed to uniquely reference active applications with process IDs.
-After starting the application process, the institution responds trough the messaging adapter with the process ID on the "Application Process Reference Response" channel.
+After starting the application process, the institution responds through the messaging adapter with the process ID on the "Application Process Reference Response" channel.
 This process ID is then published on the "New Relationship Mapping" channel.
@@
 If it is possible to retrieve the application type from the process ID, processing of each application type could be separated into multiple application change request modules.
-In case, application types are not retrievable from process IDs, an additional module can be included, which requests the application type from the institution system based on the process ID.
+In case application types are not retrievable from process IDs, an additional module can be included, which requests the application type from the institution system based on the process ID.
 An alternative would be for the application relationship module to not only publish the process ID corresponding to a relationship ID on the "New Relationship Mapping" channel but also the application type.
 
-Only after the attribute change request is accepted, will the institution system be notified of the attribute change.
+Only after the attribute change request is accepted, the institution system will be notified about the attribute change.
 
@@
 
-The institution system receives the notification of a modification of the application trough the messaging adapter.
-Depending on the capabilities of the institution system, this could result in either an automated update of the referenced application process or an automated E-Mail to the assigned employee.
+The institution system receives the notification from the application through the messaging adapter.
+Depending on the capabilities of the institution system, this could result in either an automated update of the referenced application process or an automated e-mail to the assigned employee.
 
@@
 Similar to the attribute change messages, mail messages can be fitted to the process based scenario, enabling institutions to send mails to a process ID which the messaging system translates to a relationship ID in order for the correct IMP identity to receive it.
-In addition to the one directional message transfer from the institution to the IMP identity, the application mail module and the mail message module could be expanded to be able to receive mails from an IMP identity trough an established relationship.
-The relationship ID of the message would be mapped to the corresponding process ID and submitted it to the institution system.
+In addition to the one directional message transfer from the institution to the IMP identity, the application mail module and the mail message module could be expanded to be able to receive mails from an IMP identity through an established relationship.
+The relationship ID of the message would be mapped to the corresponding process ID and submitted to the institution system.
 The institution system could then send the mail to the responsible employee.
@@
 It was also able to integrate a user oriented (persistent) relationship scenario as well as a process oriented (temporary) relationship scenario.
-This demonstrates, that the presented integration architecture can be used for integrating a variety of IMP solutions.
+This demonstrates that the presented integration architecture can be used for integrating a variety of IMP solutions.
 

### 2021-03-06 chapters/sections/15-conclusion.tex
überarbeitung

Finally, this chapter aims to summarize the most important results of the thesis and give an outlook on possible future developments and contributions.

\section{Summary}

\begin{itemize}
    \item Purpose of the thesis is to design integration solutions for identity management provisioning systems on the example of OZG.
    \item The integration is separated into a business scenario integration trough an IMP solution and a system integration trough a messaging system.
    \item Trough two IMP solutions, it was shown, how IMP can be utilized in different identity management scenarios
    \item In the first scenario, an IMP solution was presented which focused on enhancing usability of 
    \item The thesis introduced identity management provisioning as an identity management service capable of replacing conventional user profiles
    \item On the example of the OZG, the thesis showed 
\end{itemize}

\section{Outlook}

\begin{itemize}
    \item experimental evaluation
    \item 
\end{itemize}

### 2021-03-06 chapters/sections/2-objective.tex
überarbeitung

Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.

In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.

Two solutions for IMP integration and one message based IMPS integration architecture are presented.

The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management. In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them. This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.

In the second solution, IMP is used as an alternative way for identity management without user profiles. This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.

The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers. This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.

### 2021-03-06 chapters/sections/3-structure_of_work.tex
überarbeitung

In the chapter "Background and Related Work" important topics, following chapters rely on are covered.
In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well ass possible solutions trough IMP.
In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Replacing IMP Utilization" the second IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Conclusion" the most important results of the thesis are summarized and possible future developments and contributions are discussed.

### 2021-03-06 chapters/sections/5-imp.tex
überarbeitung

--- 2021-03-04 sections/5-imp.tex
@@
-\begin{itemize}
-    \item IMP hosts systems for identity management and provides access to users with an application and to service providers with integration tools
-    \item Users can create an identity and manage attributes (key-value pairs)
-    \item Users and service providers can establish relationships and use them to securely share personal information and exchange structured data
-\end{itemize}
+The purpose of the following sections is not to give a detailed explanation but to deliver a brought understanding of what identity management provisioning is and how identity management provisioning systems operate.
 
-\begin{itemize}
-    \item Ease of Use: Users only need to manage one online identity which can be accessed by multiple service providers
-    \item Data protection: Users can control which service providers get access to which attributes
-    \item Bidirectional Communication: Service providers and users can directly communicate with each other by exchanging structured data their tools have a common understanding of.
-    \item User Interaction: The user application can display various user interfaces based on the content of exchanged structured data.
-    \item Data Abuse Protection: Service providers are only supplied with necessary personal information which minimizes the possibilities of abuse by the service provider or in case of a data breach.
-    \item Communication Security: Attributes communicated structured data are securely exchanged.
-User and service provider can therefore also directly exchange sensible information.
-This is not possible for example through e-mail
-\end{itemize}
+Identity management provisioning (IMP) is a service which enables users to manage a digital identity and use it to share personal information and interact with service providers.
 
-The purpose of the following sections is not to give a detailed explanation of the presented IMP system but to deliver a brought understanding of the concepts, features and components involved.
+Any user can create an IMP identity and similar to user profiles, add any personal information as attributes.
+In contrast to existing user profile based identity management systems, however, only one IMP identity and only one identity management provisioning system (IMPS) are necessary.
+The IMPS is hosted by an identity management provisioning host (IMPH) to enable every service provider to access its service.
 
-\subsection{Features}
+Service providers can use the service for identity management by requesting access to personal information of IMP identities.
+The user has the option of accepting or rejecting to share personal information.
+As part of the service, users and service provider are also enabled to exchange messages to interact with each other.
 
-\paragraph{Provisioning} The IMP system is hosted on the system architecture of the identity management provider and provides identity management as a service for users and SPs.
-Users and service providers can manage identities by accessing features of the IMP system.
-The IMP system stores all personal information and data necessary for the operation of identity management.
-The user only manages one identity which can be accessed by multiple service providers.
+\subsection{IMP Example}
 
-\paragraph{Applications} The IMP system provides users and service providers with software tools for accessing its features.
+This section describes what an identity management provisioning service can look like and is based on the identity management provisioning system called IDAS.
+
+\paragraph{Applications} Users and service providers can access  software tools for accessing its features.
 The user is provided with a user friendly application while the enterprise is provided with tools for integration.
@@
 
-\subsection{Evaluation of Features}
-
-This section evaluates the advantages and disadvantages of the described features of the IMP system based on the requirements of users and service providers.
-
-\subsubsection{User}
-The IMP system enables users to manage one identity and share attributes with multiple service providers.
-This replaces the need of a user profile for all service providers which take advantage of the IMP service.
-The user wont have to access multiple websites for managing user profiles but update his identity only through the IMP service.
-As attributes can only be shared with service providers as part of a relationship, the user has control of his personal information.
-Before accepting the relationship, he can see information about the identity of the service provider, like his name, address, phone number and more.
-The user is also provided with information on why the relationship and request attributes are necessary which helps the user in deciding if he agrees with the necessity of sharing the information.
-As it is possible to establish multiple relationships with a service provider, each with a different specified reason and list of shared attributes, it is possible for user and service provider to establish a relationship for each business process which requires access to personal information.
-The information therefore can not only be shared with a single service provider but also for an individual process.
-User and service provider can interact through relationships.
-Therefore messages can be exchanged and associated to a certain business process.
-
-\subsubsection{Service Provider}
-
-The IMP system enables the service provider to access personal information of users without the need of hosting a system for identity management.
-Depending on the price of the IMP solution, this can reduce the cost for operating and maintaining the system architecture.
-The service provider has to hire less staff, does not have to buy expensive hardware and can more easily scale the performance of his system.
-As previously described, the user experience can also increase and lead to more customers.
-Relationships enable service providers to request users to share attributes while specifying the legal reasons for processing the information and to directly interact with them.
-The IMP system takes over the responsibility for securing personal information of users and interactions with the service provider.
-As the relationship cannot be deleted without approval of both identities, it can be used as proof of for example contracts or order placements.
-The IMP system provides tools for integration which minimizes the effort for system providers to start using the IMP system.
-
-As the IMP system focuses on improved data protection for users, the service provider might lose access to valuable but not necessary personal information.
-The determination of a reason for processing personal information also requires increased system complexity for making sure, that personal information is only used for the specified reason.
-The integration of a new solution for identity management is an expensive and time consuming task and might in short term increase instead of reduce cost.
-Using an external service for identity management makes the service provider dependent on the identity management provider.
-This can be a problem, if in the future, the service costs increase or the IMP solution stops being supported.
-
-\subsection{Components}
+\subsection{IMPS Example}
 
@@
     \centering
-    \includegraphics[scale=0.3]{Diagrams/IMP Layer Diagram.png}
+    \includegraphics[scale=0.6]{Diagrams/IMP Layer Diagram.pdf}
 \end{figure}

### 2021-03-06 chapters/sections/6-online_access_law.tex
überarbeitung

--- 2021-03-04 sections/6-online_access_law.tex
@@
+This chapter gives an overview of regulations, execution and system architecture regarding the online access law.
+
+\subsection{Regulations}
+
 In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
-\begin{enumerate}
-    \item \textbf{Digital availability of administrative services} \\
-    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.
+
+\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.
 As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
@@
 As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
-    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
-    Federal republic, each member state and each commune must provide an administration portal.
+
+\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each member state and each commune must provide an administration portal.
 Portals of communes must be linked to the portal of the corresponding member state.
@@
 \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.
-    \item \textbf{Interoperable user profiles for accessing administrative services} \\
-    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
+
+\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
 The user profiles must be interoperable for every administration portal of the portal network.
-\end{enumerate}
+
+\subsection{Execution}
 
@@
 
-\subsection{Basic Use Case}
+\subsection{System Architecture}
+This subsection first describes the basic use case of the OZG. It then presents the OZG system architecture of a member state capable of executing the basic OZG use case.
+Systems responsible for coordination of OZG execution between member states and the federal republic such as the online gateway are not included.
+
+This section combines references from OZG system architectures from Baden-Würrtemberg \cite{ozg:bw} and Nordrhein-Westfalen \cite{ozg:nrw}.
+
+\paragraph{Basic Use Case}
 The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}.
@@
 Those arrangements can be called the basic use case of OZG services.
-
 The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:
 
-\paragraph{1. Create User Profile}
+\begin{enumerate}
+    \item \textbf{Create User Profile}
+
     The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.
 
-\paragraph{2. Login to User Profile}
+    \item \textbf{Login to User Profile}
+
     Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
@@
 
-\paragraph{3. Selection of Administrative Service}
+    \item \textbf{Selection of Administrative Service}
+
     The user visits any administration portal of the portal network and types a search term in the corresponding search field.
@@
 
-\paragraph{4. Filling in Application}
+    \item \textbf{Filling in Application}
+
     Personal information from the user profile is used by the form-server to fill as many fields of the form as possible.
@@
 
-\paragraph{5. Submission of Application}
+    \item \textbf{Submission of Application}
+
     The user again authenticates for his user profile and authorises the form-server to submit the application.
@@
 
-\paragraph{6. Reception of Application by Administration Portal}
+    \item \textbf{Reception of Application by Administration Portal}
+
     The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.
 
-\paragraph{7. Submission of Application to Data-Exchange Platform}
+    \item \textbf{Submission of Application to Data-Exchange Platform}
+
     The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.
 
-\paragraph{8. Management of Applications}
+    \item \textbf{Management of Applications}
+
     The administration portal stores active applications and enables the user to manage them.
 
-\paragraph{9. Communication}
+    \item \textbf{Communication}
+
     As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.
@@
 
-\subsection{System Architecture}
-This subsection describes the system architecture of a member state relevant for the execution of the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen.
-Systems responsible for coordination of OZG execution between member states and the federal republic are not the focus.
+\end{enumerate}
 
@@
 The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components.
-The most important components the service facade provides an interface for are:
 
-\begin{itemize}
-    \item \textbf{Responsibility Finder}
-
+The service facade provides an interface to the \textbf{responsibility finder}.
 This service component is used to find administrative institutions which are responsible for an application.
@@
 
-    \item \textbf{Process Management}
-
+The service facade provides an interface to the \textbf{process manager}.
 This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.
 
-    \item \textbf{Search}
+The service facade provides an interface to the \textbf{search service}.
+This service component creates a list of URLs of administrative services relevant for a specified search term.
+It enables the portal to provide a search functionality of administrative services for the user.
 
-    This service component creates a list of URLs of administrative services relevant for a specified search term.
-This enables the portal to provide a search functionality of administrative services for the user.
-
-    \item \textbf{User Profile Management}
-
+The service facade provides an interface to \textbf{user profile management}.
 This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.
 
-    \item \textbf{Application Management}
-
-    This service component manages applications issued through the administration portal through communication with the form server.
+The service facade provides an interface to \textbf{application management}.
+This service component manages applications issued through the administration portal by communicating with the form server.
 The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server.
@@
 The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.
-
-\end{itemize}
 

### 2021-03-06 chapters/sections/7-messaging.tex
überarbeitung

--- 2021-03-04 sections/7-messaging.tex
@@
 
-\section{Messaging}
+\subsection{Messaging}
 
-Messaging is an asynchronous system-to-system communication, delivering packages of data called messages trough channels.
+Messaging is an asynchronous system-to-system communication, delivering packages of data called messages through channels.
 Messages can contain any structured data like strings, arrays or objects.
@@
 Therefore various message transformation components exist.
-Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message on a outbound channel.
+Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message to an outbound channel.
 
@@
 Depending on the messaging system solution, additional features can be configured to increase performance, stability, failure safety and more.
-If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently store messages in case of a system crash.
+If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently stores messages in case of a system crash.
 
-\section{Messaging Integration}
+\subsection{Messaging Integration}
 
@@
 
-The main benefit of messaging for integration is, that it enables systems to share services and data in a decoupled way.
+The main benefit of messaging for integration is that it enables systems to share services and data in a decoupled way.
 Neither system, whether sending or receiving messages, needs to be aware of each other.
@@
 
-\section{Messaging Patterns}
+\subsection{Messaging Patterns}
 
@@
 
-There exist different types of channels.
-In the thesis, named channels are publish-subscribe datatype channels.
+There are different types of channels.
+In this thesis, named channels are publish-subscribe datatype channels.
 Unnamed channels are point-to-point channels.
@@
 
-Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system trough an API.
+Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API.
 The messaging adapter usually has to be developed for each system individually, and manually integrated into the code of the system trough asynchronous function calls of the adapter API.
@@
 Message translators have the purpose of translating message content on data representation and data type layer.
-On the data representation layer, message translators for example translate message content from an XML format to a JSON format.
+On the data representation layer, message translators translate message content for example from an XML format to a JSON format.
 On the data type layer, message translators can for example concatenate first name and last name fields to a single name field.
@@
 
-Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages, based on their content.
+Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages based on their content.
 The definition of the rules does not change during operation of the system.
 
-Figure \ref{messaging:filter} shows the visual notation of a message filter.
+Figure \ref{messaging:filter1} shows the visual notation of a message filter.
 
@@
 
-Content enricher have the purpose of adding new attributes to messages. The content which is added usually is a predetermined set of attributes but with dynamically created values.
+Content enricher have the purpose of adding new attributes to messages. The content which is usually added is a predetermined set of attributes but with dynamically created values.
 
@@
 They are also capable of communicating with other messaging patterns for providing access to stored messages.
-Communication between message patterns and message stores is indicated by a dotted arrows.
+Communication between message patterns and message stores is indicated by a dotted arrow.
 

### 2021-03-06 chapters/sections/8-identity_management.tex
überarbeitung

--- 2021-02-26 sections/8-identity_management.tex
@@
+This chapter describes issues of user based identity management in general and for the use case of the OZG. It also presents possibilities of how IMP can be utilized to solve mentioned issues.
+
 \section{OZG Identity Management Issues}
@@
 \paragraph{Usability}
-Each service provider has different platform for management of personal information and identity related interactions.
+Each service provider has a different platform for management of personal information and identity related interactions.
 This can for example be web pages or applications for desktop and smartphone.
 Keeping track of all created user profiles is difficult.
-In case of web pages, users will also have to remember various URLs, usernames and passwords.
-The risk of forgetting login credentials is high.
-To manage personal information stored in each user profile and for example change an E-Mail address, users have to access the individual platforms of each service provider.
+
+In case of web pages, users will also have to remember various URLs, usernames and passwords. The risk of forgetting login credentials is high.
+
+To manage personal information stored in each user profile and for example change an e-mail address, users have to access the individual platforms of each service provider.
 Depending on the amount of created profiles, this can be a time consuming task.
 Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA or Magic-Link.
-Users receiving notifications, messages and mails on multiple platforms can quickly loose the overview and oversee important notifications.
-Each platform is often presented with a different design although the purpose remains similar.
-This makes it difficult for users to orientate themselves.
-Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while E-Mails are only used to notify the user to check his user profile ("You have unread messages!").
-One reason is, that E-Mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content.
+Users receiving notifications, messages and mails on multiple platforms can quickly loose track and oversee important notifications.
+
+Each platform is often presented with a different design although the purpose remains similar. This makes it difficult for users to orientate themselves.
+
+Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while e-mails are only used to notify the user to check his user profile ("You have unread messages!").
+This is because e-mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content.
 Although service providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.
+
 Service providers rely on the validity of information stored in the user profile.
@@
 As each service provider manages separate user profiles, the user might have to go trough this time consuming process repeatedly.
+
 Users are not able to automatically share personal information from one user profile with another (except for some Single-Sign-On cases).
-As a result of that, creating new user profiles each time involves entering personal information all over again.
+As a result of that, creating new user profile each time involves entering personal information all over again.
 
@@
 Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage.
+
 As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which service provider processes which personal information.
-Multiple service providers storing sensible information increases the risk of data being stolen due to a data breach.
+Multiple service providers storing sensible information increases the risk of personal information being stolen due to a data breach.
 
-In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also multiple systems operated by the member state.
+In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also with multiple systems operated by the member state.
 Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it.
@@
 After an application is finished, the institution can delete all data stored as part of this process.
-The only reason user profiles are required is to verify the validity and authorization of incoming applications and to enable the user to comfortably fill in application forms and communicate trough an inbox.
+The only reason user profiles are required is to verify the validity and authorization of incoming applications and to enable the user to comfortably fill in application forms and communicate through an inbox.
 
@@
 
-User profiles are often secured trough passwords.
+User profiles are often secured through passwords.
 Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of it being stolen and all user profiles being accessible.
 With the amount of different service providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between service providers.
+
 Users also have to rely on the correct operation of the system architecture of the service provider and might not be able to proof failures in the operation of the system.
@@
 
-The goal of IMP solutions is to replace user profiles with a single IMP identity.
-Trough the IMP client a user can manage his IMP identity and all integrated service providers.
-Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider.
-Depending on the use case, the relationship can be utilized differently.
+The goal of IMP solutions is to replace user profiles with a single IMP identity. Through the IMP client a user can manage his IMP identity and all integrated service providers.
+
+Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider. Depending on the use case, the relationship can be utilized differently.
+
 Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.
+
 It also enables the user to update personal information shared with service providers trough one application.
+
 As the IMP client also contains an inbox, all notifications sent by each service provider can be viewed in the same place.
-As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can sent structured data to the IMP client along with the information that it should be displayed as a form.
+
+As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can send structured data to the IMP client along with the information that it should be displayed as a form.
 Depending on the content of the form and the use case of the service provider, the form can either be a purchase agreement or a survey.
-Assumed, trough a secure identification and validation process, the identity management provider makes sure, attributes users stores as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls.
+
+Assumed, through a secure identification and validation process, the identity management provider makes sure, attributes users store as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls.
+
 Due to the IMP client being able to automatically fill in attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.
@@
 With this information, the user can make an informed decision whether to establish the relationship and the service provider performed his duty to inform the user as required by the DSGVO.
+
 As personal information is only shared as part of a relationship and with a specified purpose, the service provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible trough.
 This helps the service provider in processing personal information according to the DSGVO.
+
 As every relationship along with shared attributes is manageable trough the IMP client, the user wont loose track of which service provider has access to which personal information.
+
 The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the service provider processes only a small portion of attributes of IMP identities.
@@
 The IMP client itself can be secured without the need for a password.
-As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validate at any time.
+As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validated at any time.
 This enables both user and service provider to provide proof for interactions.
-
-\section{IMP Integration Challenges}
-
-In order for the system architecture of the OZG and service providers in general to utilize IMP services, the IMP connector has to be integrated.
-Multiple integration challenges are described in the following sections and will be focus of the integration architectures of chapter 4 and 5.
-
-\paragraph{SP Challenges}
-
-\begin{itemize}
-    \item Sp does not understand concepts of the IMP like relationships, the integration has to bridge this gap
-    \item The SP wants the integration to 
-    \item Minimal modification of existing systems
-    \item Maintainability
-    \item Scalability
-    \item Extendability
-    \item Modularity
-    \item
-
-\end{itemize}
-
-\paragraph{OZG Challenges}
-
-\begin{itemize}
-    \item Once an application is submitted, its attributes cannot be changed
-    \item Mapping of IMP attributes and FIM data blocks
-    \item 
-\end{itemize}
-
-\paragraph{IMP Challenges}
-
-\begin{itemize}
-    \item Connector has REST interface and cannot notify system architecture
-    \item Connector does not understand messages
-    \item API of connector can change
-    \item New types of messages can be added by the client and the system provider might need to understand them
-\end{itemize}

### 2021-03-07 chapters/sections/5-imp.tex
überarbeitungen

@@
-The purpose of the following sections is not to give a detailed explanation but to deliver a brought understanding of what identity management provisioning is and how identity management provisioning systems operate.
+The purpose of this section is not to give a detailed explanation but to deliver a broad understanding of what identity management provisioning is, what an IMP service can look like and how identity management provisioning systems can operate.
 
-Identity management provisioning (IMP) is a service which enables users to manage a digital identity and use it to share personal information and interact with service providers.
+\subsection{IMP}
+Identity management provisioning (IMP) is a method of identity management where identity management is provided as a service to users and service providers.
+The service enables users to manage a digital identity and use it to share personal information and interact with service providers.
 
-Any user can create an IMP identity and similar to user profiles, add any personal information as attributes.
-In contrast to existing user profile based identity management systems, however, only one IMP identity and only one identity management provisioning system (IMPS) are necessary.
-The IMPS is hosted by an identity management provisioning host (IMPH) to enable every service provider to access its service.
+Many identity management systems currently in use by service providers each require the user to create a user profile, specify login credentials and maintain personal information.
+Each service provider operates his own identity management system and users have to access each system individually trough multiple websites to access their user profiles.
+This approach to identity management leads to several problems which are discussed in section \ref{section:identity_management_issues}.
 
-Service providers can use the service for identity management by requesting access to personal information of IMP identities.
-The user has the option of accepting or rejecting to share personal information.
-As part of the service, users and service provider are also enabled to exchange messages to interact with each other.
+In contrast to a user profile based identity management approach, IMP provides identity management as a service.
+Only one identity management provisioning system is hosted and accessed by user and service providers.
+Users therefore only need one IMP identity, which is accessed by multiple service providers.
+This approach to identity management is capable of solving various issues of user profile based identity management which is discussed in section \ref{section:imp_solution_opportunities}
 
-\subsection{IMP Example}
+To access the IMP service, users can use applications or websites.
+Service providers however often require integration into their existing system architecture to enable existing system components to use the new identity management method.
 
-This section describes what an identity management provisioning service can look like and is based on the identity management provisioning system called IDAS.
+\subsection{IMP Service}
 
-\paragraph{Applications} Users and service providers can access  software tools for accessing its features.
-The user is provided with a user friendly application while the enterprise is provided with tools for integration.
+There are many ways to design a service for identity management provisioning.
+This section describes what an identity management provisioning service can look like.
+It is based on the IMP service called IDAS.
 
-\paragraph{Personal Information Management} One feature of the IMP system is management of personal information.
-Through the application, the user can create an identity and add, remove and update any kind of key-value pairs.
-These are IMP identity attributes.
+For users and service provider to access the IMP service, software tools exist.
+For the user, this is a smartphone application.
+For the service provider this is an integration component.
+The smartphone application provides a user friendly graphical interface which enables the user to receive notifications, maintain personal information, share personal information, and more.
+The integration component for the service provider is a software solution with similar capabilities as the smartphone app but designed towards enterprise use.
+It therefore has no graphical user interface but additional business relevant features and integration capabilities.
+IMP application and integration component are described in section \ref{section:imp_system} in more detail.
 
-\paragraph{Relationship}
+One important part of the IMP service is management of personal information by users.
+After installation of the smartphone application, a new identity (IMP identity) can be created.
+As part of this identity, the user can add any amount of key-value pairs as attributes.
+The list of all attributes makes up the personal information of the IMP identity.
+Despite being able to add any key-value pair, there exist some commonly used keys like name, age, home address and so on.
+Depending on the use case of service providers, multiple more keys and their meaning have to be agreed upon.
+This means, the IMP service has to define a canonical data model.
+Each service provider then translates it to their individual data models.
 
-Users and service providers can establish relationships which enables them to share information and interact.
+Many service providers require users to manually verify their identity and personal information by for example visiting a store and showing their ID card.
+Similar verification processes are expected to be used by the IMP service to verify IMP identities and their personal information.
+However, for simplification reasons, the details of this verification process are left out.
+
+Users and service providers can establish relationships and use them to share personal information and interact.
 The initial form of a relationship is a relationship template.
-The template is created by the service provider and describes which relationships he is willing to establish.
-Relationship templates are distributed to interested users which can use it to request relationships.
-A service provider has to fill a relationship template with some minimal required and some optional information:
+The template is created by the service provider and describes which types relationships he is willing to establish.
+The templates are made available to interested users, which can use them to request relationships.
 
-\begin{itemize}
-    \item \textbf{Title}
+A service provider fill a relationship template with optional and mandatory information:
 
-    The title describes the purpose of the relationship in a short way.
+\paragraph{Title} The title describes the purpose of the relationship in a short way.
 
-    \item \textbf{Requested Attributes} (optional)
+\paragraph{Requested Attributes} The service provider can list keys of attributes he requires the user to share in order to send a relationship request.
+When the user submits a relationship request based on this relationship template, the values filled in for the requested attributes are copied and sent as part of the request.
+The recipient of the request can use the personal information to decide whether to accept or reject the relationship.
 
-    Requested Attributes is a list of attribute keys the user will have to submit as part of the relationship request.
-
-    \item \textbf{Shared Attributes}
-
-    Shared Attributes is a list of attribute keys and values the service provider makes available to any user interested in requesting a relationship.
+\paragraph{Shared Attributes} Shared Attributes is a list of key-values pairs, the service provider makes available to any user interested in requesting a relationship.
 The service provider has to share a minimal amount of attributes which enable the user to identify it.
 
-    \item \textbf{Purpose}
+\paragraph{Purpose} This is a text field where the service provider can give a detailed explanation of what the purpose of the relationship is, e.g what effects a relationship request and an established relationship will have.
+Here, the reason for why the requested attributes are necessary for the relationship has to be explained as well as how each shared attribute is going to be processed.
+This helps the user in making an informed decision on whether to submit the relationship request or not.
 
-    The purpose describes why the user and the service provider want to establish the relationship and why the attributes requested from the user are necessary for it.
+\paragraph{Attachments} Attachments can be all kinds of documents and files.
+Here, for example legal information can be included but also for example product flyers corresponding to the relationship template.
 
-    \item \textbf{Attachments}
+\paragraph{Metadata} Metadata can be any type of information which should not be displayed to the user but is necessary for the user application or the service provider to process the relationship process.
 
-    Attachments are documents attached to the relationship template by the service provider. The documents can for example contain legal information.
+When the user receives the template through his IMP application, the requested attributes are automatically filled in if they exist for his IMP identity.
+Otherwise they can be filled in manually and added as new attributes of the IMP identity.
 
-    \item \textbf{Metadata}
-
-    Metadata can be any type of information which should not be displayed to the user but is necessary for the user application or the service provider to process the resulting relationship request.
-
-\end{itemize}
-
-When the user receives the template through his IMP tooling, the requested attributes are automatically filled in if he previously added them to his IMP identity.
-Otherwise he can fill in the correct values now and automatically add them as attributes of his identity.
-
-It is important to differentiate identity attributes from the attributes shared as part of the relationship.
-Identity attributes are managed by the user to reflect the most up to date information.
-Attributes shared as part of a relationship can be automatically filled with values from the same attributes of the IMP identity but can also be manually entered.
+At this point it is important to take a look at how IMP identity attributes and shared attributes are separated.
+IMP identity attributes are managed by the user to reflect the most up to date information.
+Attributes shared as part of a relationship can be automatically filled with values from the IMP identity but can also be manually entered.
 This means, shared attributes and IMP identity attributes are not necessarily the same.
@@
 Based on the information about the service provider and the purpose of the relationship, the user can decide to send a relationship request or not.
-If the user decides to request the relationship, the request is sent to the service provider along with a copy of the requested attributes.
+If the user decides to request the relationship, the request is sent to the service provider.
 If the service provider approves the request, the relationship is established and both parties get notified.
+Trough the IMP application, the user can see all relationships as well as their status, the content of the underlying relationship template and a list of shared attributes and their values.
 
-\paragraph{Messages} As part of a relationship, user and service provider can interact with each other by asynchronously exchanging structured data (IMP messages).
-Messages with any content can be exchanged, however, the tools used by the user and the service provider should be able to understand the messages.
-
-The integration tool for the service provider does not understand the content of messages but simply makes them accessible by the system architecture of the service provider.
-Without additional integration solutions, the service provider has to implement his own solutions for processing the different types of messages.
-The application provided to the user has a set of messages it understands.
+As part of an established relationship, user and service provider can interact with each other by asynchronously exchanging structured data packages as IMP messages.
+IMP messages can contain any content, however, both IMP application and service provider systems should be able to understand the messages.
+For this purpose, besides content, messages are expected to contain some identification value like a message type.
+The integration component provided to the SP does not process the content of messages but simply makes the messages accessible to the system architecture of the service provider.
+Without additional integration systems, the service provider has to implement his own solutions for understanding and processing messages.
+The IMP application however, has a set of messages it understands.
 The list of messages the application is able to process can be expanded by the identity management provider who develops it.
 
-Some important messages the user application understands and the service provider should be able to process too are:
+Some important messages the IMP application understands and the service provider should be able to process too are:
 
-\begin{itemize}
-    \item \textbf{Mails}
+\paragraph{Mail} Messages of the mail type can be used by service provider and user to exchange human readable text.
+Mails sent to an IMP identity are displayed by the IMP application trough for example a notification.
+The IMP application defines a format, for the content of the mail.
 
-    Mails are messages which contain a human readable title, and body.
+\paragraph{Attribute Change} Messages of the attribute change type can be used by the user to request the modification of shared attributes.
+The user can modify, add or delete attributes shared as part of a relationship and submit a attribute change request to the service provider which contains the changes.
+The service provider can decide to either accept or reject the request and respond with a corresponding attribute change response message.
+The IMP application defines a format, for the content of the attribute change request and response messages.
 
-    \item \textbf{Attribute Change}
+\paragraph{Authentication} Messages of the authentication type can be used by the service provider to request confirmation from the IMP identity for some business process.
+The service provider sends a initial request message to the IMP identity which contains a description of what confirmation is requested by the user.
+Through the IMP application the user is notified and can accept or reject.
+Depending on the interaction by the user, the IMP application sends a response message to the service provider.
+The IMP application defines a format, for the content of the authentication request and response messages.
 
-    After a relationship is established, service provider or user might want to change attributes they shared. This can be done by exchanging request-reply messages.
-\end{itemize}
-
-\paragraph{Security}
 The IMP system guarantees that all information is encrypted and can only be decrypted by identities which are allowed to read it.
+This usually does not include the systems hosting the IMP service.
 Only the owner of an identity can manage attributes of his identity.
 A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared.
-Interactions as part of a relationship are only possible between the identities of the relationship.
+Interactions as part of a relationship are only possible between the two parties of the relationship and cannot be intercepted or modified others.
 
-\subsection{IMPS Example}
+\subsection{IMP System} \label{section:imp_system}
 
-\begin{figure}[h]
+There are many ways to design a system for identity management provisioning.
+This section describes what an identity management provisioning systems can look like.
+It is based on the IMP system for IDAS.
+An IMP system is the combination of all system components required for providing IMP services.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/IMP System Overview.pdf}
     \caption{IMP System Overview}
-    \centering
-    \includegraphics[scale=0.25]{Diagrams/IMP System Overview.png}
+    \label{imp:imp_system_overview}
 \end{figure}
 
-The IMP system operates on three domains.
+As shown in figure \ref{imp:imp_system_overview}, the IMP system can be separated into three domains.
 The user domain contains systems the user directly interacts with.
 These typically are applications on PC or smartphone and websites.
-The IMP system provides an application for PC and smartphone to the user for accessing IMP services.
-For simplification, the user is assumed to use only one device which eliminates the need for synchronization of devices.
-The client enables the user to manage attributes of his identity, to establish relationships, to manage relationships and to interact through relationships.
-
-The IMP domain contains all systems hosted by the identity management provider.
-In this case, the domain contains only the IMP server.
-The IMP server is able to communicate with IMP client and IMP connector.
+IMP application on smartphones are provided to users for accessing IMP services.
+For simplification, each user is assumed to use access the IMP service trough one device which eliminates the need for device synchronization.
+As previously described, the IMP application enables the user to manage attributes of his identity, to establish relationships, to manage relationships and interact with messages through relationships.
 
@@
 
+The IMP domain contains all identity management provisioning systems required to be hosted by the identity management provider.
+In this case, the domain contains only the IMP server.
+The IMP server is able to communicate with each IMP application and IMP connector.
+It has the purpose of maintaining a - where necessary encrypted - list of all identities, relationships, relationship templates and IMP messages.
+As the IMP server does not know the private key corresponding to the IMP identity, it is unable to decrypt the data.
+The IMP server is also capable of creating relationship templates, processing and routing relationship requests and responses and IMP messages.
+The exact details of how the IMP server operates is out of the scope of this thesis.
+
 \begin{figure}[h]
-\caption{IMP System Operation Layers}
     \centering
     \includegraphics[scale=0.6]{Diagrams/IMP Layer Diagram.pdf}
+    \caption{IMP System Operation Layers}
+    \label{imp:layer_diagram}
 \end{figure}
 
-The operation of IMP systems can be separated into multiple layers.
+As shown in figure \ref{imp:layer_diagram}, the operation of IMP systems can be separated into multiple layers.
 The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.
 
-\paragraph{Transport Layer}
+The vertical bars in the figure represent all previously described components of the IMP system and one additional component called "Integration Module".
+The "Integration Module" is not important for the moment and fill be the focus of following chapters.
+The horizontal bars in the figure represent layers of IMP system operation.
+From bottom to top, the layers describe the operation of the IMP system in a way increasingly abstracted from the underlying technology.
+In addition to that, each bar is split up into two sides, however, in this section only the left side is relevant.
 
-The "transport layer" is responsible for securely routing data between IMP client, IMP server and IMP connector.
-Depending on the use case, the transport layer encrypts data so that it is only visible for client and connector.
-In this layer, IMP client and IMP connector are endpoints where data can be encrypted, decrypted, sent and received.
-In this layer, the IMP server is the routing component which forwards sent data to its correct destination while checking validity of messages.
+The lowest layer is called "Relationship Layer".
+On this layer, the IMP system operates by establishing relationships.
+IMP application and IMP connector exchange relationship requests and responses trough the IMP server in order to establish new relationships.
+The IMP server maintains a list of all relationships and their status.
 
-\paragraph{Relationship Layer}
-
-The "relationship layer" is responsible for establishing a relationship between IMP client and IMP connector.
-IMP client and IMP connector send relationship requests and responses and store relationships.
-The IMP server creates, stores and updates relationships and synchronizes their status with client and connector.
-
-\paragraph{Communication Layer}
-
-The "communication layer" is responsible for exchanging IMP messages as part of an active relationship between IMP client and IMP connector.
-The client can create, send, receive, process and display a list of IMP messages he is able to understand.
+Once a relationship is established, the IMP system operates on the "Communication Layer".
+On this layer, IMP messages are exchanged as part of an active IMP relationship between IMP application and IMP connector.
+The application can create, send, receive, process and display a list of IMP messages he is able to understand.
 The IMP connector is able to send and receive IMP messages through a relationship without being aware of its content.
@@
 
-\paragraph{IMP Solution Layer}
-
-The "IMP solution layer" is responsible for providing user interaction capabilities for construction of IMP solutions.
-A service provider can interact with the user in multiple ways through user interfaces of the IMP client.
-Depending on the use case of the service provider, interactions through the UIs can have different purposes.
-
+Using IMP relationships and IMP messages, the service provider can interact with the user on the "IMP Interaction Layer".
+On this layer, depending on the use case, different purposes can be assigned to interaction possibilities.
 For example, a service provider can decide to use relationships as a way to receive product or subscription orders.
@@
 
-The user interface described in the following are a minimal example which fulfill basic requirements for establishing relationships and displaying IMP messages.
-An identity management provider can add multiple more specialized UIs to the application.
-
-\begin{figure}[h]
-\caption{User Application Interfaces}
-    \centering
-    \includegraphics[scale=0.2]{Diagrams/UI.png}
-\end{figure}
-
-\paragraph{Personal Information} The attributes interface enables the user to manage attributes for his identity by adding, updating or removing values for common keys like name, surname, birth date and more.
-Here, the user can also create, update or delete new key-value pairs.
-
-\paragraph{Relationship Request} On the relationship request interface, the user can scan a QR code containing a relationship template and request a corresponding relationship.
-The attributes required for the relationship are automatically filled in if they exist for the identity.
-Otherwise the user can manually enter the correct values.
-If all requested attributes are filled in, the user can request the relationship
-
-\paragraph{Relationship Overview} On the relationship overview interface, the user can see all active relationships
-
-\paragraph{Relationship Details} On the relationship details interface, the user can view the content of a relationship and change shared attributes.
-However, an attribute will only be changed after the service provider accepted.
-The user can also send a mail to the other party of the relationship.
-
-\paragraph{Notifications} On the notifications interface, the user sees all received mails and the corresponding relationship. The user is able to reply to the mails.
-
 \subsection{IMP Use Cases}
 
-In this section the most important use cases of the IMP system are described in more detail.
+In this section the IMP system operation for most important use cases of the IMP service are described in more detail.
 
@@
 
-The first step towards a relationship usually is the interest of a user.
+This section elaborates the sequence of establishing an IMP relationship as shown in figure \ref{imp:establish_relationship}.
+The first step towards a relationship is the interest of a user.
 A user for example wants to subscribe to the newsletter of a service provider.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \caption{IMP Use Case Establish Relationship Sequence Diagram}
-    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Establish Relationship Sequence Diagram 1.png}
+    \includegraphics[scale=0.6]{Diagrams/IMP Use Case Establish Relationship Sequence Diagram.pdf}
+    \caption{Establish Relationship Sequence Diagram}
+    \label{imp:establish_relationship}
 \end{figure}
@@
 To enable users to request a relationship with the purpose of subscribing for a newsletter, the service provider has to create a relationship template.
-Through the REST interface of the connector, he sends a request for a new relationship template.
+Through the REST interface of the connector, the SP sends a request for a new relationship template.
 The request contains parameters specifying the content of the relationship template.
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-    \centering
-    \caption{Relationship Request Example}
-    \includegraphics[scale=0.25]{Diagrams/Relationship Request Example.png}
-\end{wrapfigure}
-
 Based on the parameters of the request, the connector creates a relationship template and sends it to the IMP server.
@@
 The service provider can transmit the template ID to any user who wishes to subscribe for a newsletter. This can be done by for example rendering the template ID as a QR code on a website.
-If the QR code is displayed to the user, he can scan it using the IMP client.
-The client understands that the content of the QR code contains a relationship template ID and retrieves the corresponding template from the IMP server.
+If the QR code is displayed to the user, he can scan it using the IMP application.
+The application understands that the content of the QR code contains a relationship template ID and retrieves the corresponding template from the IMP server.
 
-The IMP client displays the relationship template to the user and automatically fills in as many requested attributes as possible.
+The IMP application displays the relationship template to the user and automatically fills in as many requested attributes as possible.
 
 The user can now decide if he wants to accept the relationship and share the requested attributes.
-If he accepts, IMP client sends a relationship request to the IMP server.
+If he accepts, IMP application sends a relationship request to the IMP server.
 The request contains all information of the relationship template in addition to the shared attributes of the user.
-
-\begin{figure}[h]
-    \centering
-    \caption{IMP Use Case Establish Relationship Sequence Diagram}
-    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Establish Relationship Sequence Diagram 2.png}
-\end{figure}
 
@@
 In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
-If however, the IMP server updates the status of the relationship to "established", both IMP client and connector are notified with the final content of the relationship.
+If however, the IMP server updates the status of the relationship to "established", both IMP application and connector are notified with the final content of the relationship.
 
-After receiving the final "relationship established" notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID for the newsletter system to access.
+After receiving the final "relationship established" notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID.
 
-\subsubsection{Send Message}
+\subsubsection{Attribute Change}
+This section elaborates the sequence of changing an attribute shared as part of an IMP relationship as shown in figure \ref{imp:attribute_change}.
+If the user switches to a new e-mail provider, he will need to change the corresponding e-mail attribute shared as part of the relationship to receive the newsletter on his new e-mail address.
 
-Through an established message, user and service provider can exchange messages with any structure and content.
-However, this only makes sense if both IMP client and system architecture of the service provider can understand the messages.
-IMP server and IMP connector only take care of the correct routing.
-The list of messages an IMP client understands can be expanded by the identity management provider.
-It can therefore be assumed that the IMP client understands any message service providers often want to exchange.
-For simplicity, in the following sections, behaviour of the IMP client for newly defined message can be defined at will.
-Two important types of messages were already defined: Mail Messages and Attribute Change Request-Reply Messages.
-
-\subsubsection{Request Attribute Change}
-
-It is possible that in the future, the user wants to change the mail address where he receives the newsletter.
-As the established relationship remains to be valid, it should not be terminated, but shared attributes should be changed instead.
-
-Through the IMP client, the user can view the corresponding relationship and edit the attributes.
-After he changed the mail attribute he shares, through routing by the IMP server, the IMP client sends an attribute change request message to the connector.
-The connector does not understand the content of the message but from which relationship it originated from.
-As the connector cannot notify the system architecture of the service provider, polling for new messages is required.
-After the system architecture receives the message, it understands the structure of the message and that the purpose of the message is an attribute change request.
-
-The system architecture evaluates if it accepts the changes and sends a response through the REST interface of the connector.
-The system architecture might execute additional processes.
-In this case, the mail address stored in the database would be updated.
-
-The IMP server receives the response message through the connector and routes it to the IMP client.
-The IMP client understands the message, updates the value stored as part of the relationship and displays a notification to the user.
-
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \caption{IMP Use Case Change Relationship Attribute Sequence Diagram}
-    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Change Realtionship Attribute Sequence Diagram.png}
+    \includegraphics[scale=0.6]{Diagrams/IMP Use Case Change Realtionship Attribute Sequence Diagram.pdf}
+    \caption{Change Relationship Attributes Sequence Diagram}
+    \label{imp:attribute_change}
 \end{figure}
 
-\subsubsection{Send Mail}
+Through the IMP application, the user can view relationships and edit shared attributes.
+After changing an attribute, like for example the e-mail address, the IMP application sends an attribute change request to the IMP server, which forwards it to the IMP connector corresponding to the IMP relationship.
+Trough the REST interface of the IMP connector, the service provider iteratively polls for new messages and eventually receives the attribute change request as response.
+The service provider evaluates whether to accept or reject the request and uses the REST interface of the IMP connector to submit the response.
+The IMP connector sends the response to the IMP server which - if the service provider accepted the request - notifies IMP connector and IMP application of the successful change of attributes.
+The service provider again polls for new messages and eventually receives the attribute change established notification based on which it now updates the stored attributes associated to the relationship.
+When the IMP application receives the attribute change established message, it displays a notification to the user.
 
-If a user has questions about the newsletter, he can send messages to the service provider as part of the relationship.
-The client sends the mail message to the IMP server which routes it to the connector.
-The system architecture polls for incoming messages.
-When the system architecture receives the message, it understands the content and purpose and for example notifies an employee.
-An employee could be notified via e-mail and a response from the employee to the mail could automatically be sent to the relationship through the REST API of the connector.
-Connector and IMP server route the message to the IMP client, who understands the message and displays it to the user.
+\subsubsection{Mail}
+This section elaborates the sequence of sending a mail as part of an IMP relationship as shown in figure \ref{imp:mail}.
+If a user for example has questions about the newsletter, he can send a mail to the service provider as part of the established relationship.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
-    \caption{IMP Use Case Communication Sequence Diagram}
-    \includegraphics[scale=0.3]{Diagrams/IMP Use Case Communication Sequence Diagram.png}
+    \includegraphics[scale=0.6]{Diagrams/IMP Use Case Mail Sequence Diagram.pdf}
+    \caption{Mail Sequence Diagram}
+    \label{imp:mail}
 \end{figure}
+
+Trough the IMP application the user can view relationships and submit mails.
+Once submitted, the IMP application sends the mail to the IMP server which forwards it to the IMP connector corresponding to the relationship.
+The service provider polls for new messages and eventually receives the mail as response.
+An employee of the service provider can process the email and use the REST interface of the IMP connector to send a response mail to the same relationship.
+The IMP connector sends the mail to the IMP server which forwards it to the IMP application of the IMP identity corresponding to the IMP relationship.
+The application then notifies the user of the received mail.
+
+\subsubsection{Authenticate}
+This section elaborates the sequence of authenticating as part of an IMP relationship as shown in figure \ref{imp:authenticate}.
+If the service provider wants to request confirmation from the user, it can send an authentication request to the corresponding relationship.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/IMP Use Case Authenticate Sequence Diagram.pdf}
+    \caption{Authenticate Sequence Diagram}
+    \label{imp:authenticate}
+\end{figure}
+
+The SP uses the REST interface of the IMP connector to send an authentication request as part of an IMP relationship.
+The IMP connector sends the request to the IMP server which forwards it to the IMP application of the IMP identity corresponding to the IMP relationship.
+The application displays the authentication request to the user.
+The user can accept or reject the request which will result in the corresponding authentication response by the IMP application.
+The response is send to the IMP server which forwards it to the IMP connector corresponding to the IMP relationship.
+The service provider polls for new messages and eventually receives the authentication response.

### 2021-03-07 chapters/sections/6-online_access_law.tex
überarbeitungen

@@
 
-In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
+In 2017, the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
 
@@
 
-\begin{center}
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/OZG System Overview.pdf}
-\end{center}
+    \caption{OZG System Overview}
+    \label{ozg:system_overview}
+\end{figure}
 
@@
 
-\subsubsection{Data Objects}
-This section describes what data each component processes.
-The property value describes a certain type of data.
-The source describes which component stores the value.
-This distinguishes the access of a property by reference and by copy.
-If the source of a property is another component, the property is accessed by reference.
-The description gives further detail on how the property is processed by the component.
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: Service Web Page} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Name & Web Page & FIM & Name of an administrative service \\
-    \hline
-    URL & Portal & Portal & The URL of the Web Page \\
-    \hline
-    Description & Web Page & FIM & Description of an administrative service \\
-    \hline
-    FIM-ID & Web Page & FIM & FIM-ID of a data field schemata which describes attributes required from the user when applying for the service \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: User} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Attributes & User Profile & User Profile & The portal can manage attributes of user profiles \\
-    \hline
-    JWT & Portal & User Profile & The portal can retrieve a JSON Web Token from the profile after successful authentication by a user \\
-    \hline
-    URL Form & Portal & Form Server & The portal stores the URL where the form server hosts the interactive form \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Administration Portal: Application} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    FMS-ID & Portal & Form Server & The portal receives the ID of applications from the form server \\
-    \hline
-    Status & Portal & Form Server & The portal receives status updates for each application \\
-    \hline
-    XML Form Data & Portal & Form Server & The portal can retrieve the data which was filled into a form \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Personal Information} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Attributes & User Profile & FIM & The list of attributes the user can fill in at his profile are based on FIM data fields managed in the FIM repository. \\
-    \hline
-    Attribute Values & User Profile & User & The user can manually add values to a list of predetermined attributes in his profile \\
-    \hline
-    Credentials & User Profile & User & The User Profile stores encrypted credentials of the user to authenticate him \\
-    \hline
-    User Profile ID & User Profile & User Profile & The User Profile creates and stores a unique ID for the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Authorisatiozation} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    JWT & Other Component & User Profile & The user profile can create and transfer JSON Web Tokens which authorise other components to access resources of the user profile \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Inbox} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Received Messages & User Profile & User & The user profile stores messages which were addressed to the user \\
-    \hline
-    Sent Messages & User Profile & User & The user profile stores messages which were sent by the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{User Profile: Data Wallet} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    Documents & User Profile & User & The user profile stores documents which were uploaded by the user \\
-    \hline
-    \end{tabularx}
-\end{table}
-
-\begin{table}[!h]
-    \begin{tabularx}{\textwidth}{|l|l|l|C|}
-    \rowcolor{LightCyan}
-    \hline
-    \multicolumn{4}{|l|}{Form Server} \\
-    \hline
-    Property & Storage & Origin & Description  \\
-    \hline
-    \hline
-    FMS-ID & Form Server & Form Server & The form server creates a unique ID for each application \\
-    \hline
-    JWT & Form Server & User Profile & The form server uses a JSON Web Token to verify that the entity issuing the request is authorised \\
-    \hline
-    User Profile ID & Form Server & User Profile & The ID of the user who is associated to the application \\
-    \hline
-    FIM-ID & Form Server & FIM & The FIM ID of a data field schemata is used to determine how to construct the form \\
-    \hline
-    Form & Form Server & FIM & The list of attributes the user can fill in at the form are based on the FIM data field schemata.
-The form server maps the FIM data fields of the FIM data field schemata to attributes the form server understands \\
-    \hline
-    Status & Form Server & Form Server & The status describes which actions were performed on the application \\
-    \hline
-    Application Data & Form Server & User & The form server stores the data which the user filled in to the form as an XML file \\
-    \hline
-    Web Page & Form Server & Form Server & The form server hosts a web page with the interactive form  \\
-    \hline 
-    Web Page URL & Form Server & Form Server & The form server hosts the web page of the form at an individual URL \\
-    \hline 
-    \end{tabularx}
-\end{table}
-
 \subsubsection{Sequence Diagram}

### 2021-03-13 chapters/sections/1-context.tex
Anfang und ende fertig

--- 2021-03-04 sections/1-context.tex
@@
-Since invention of the World Wide Web, the number of its users increased rapidly.
-Today, more than 90 percent of the german population uses the internet \cite{Onlinestudie}.
-Enterprises and organizations recognised this potential to provide their services to a large number of people as Service Providers (SP).
-A frequently used method of SPs is "online self-service" (OSS).
-Specialized software tools enable customers to use services through the internet without direct human interaction.
+Many services, are accessible through the internet.
+Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns.
+Online Service Providers (SP) often require customers to create user profiles in order to access their services.
+Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail.
+It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.
 
-Many tools require identification of a user in case interactions or initiated business processes have to be associated with him.
-A system for management of identities of users therefore is part of numerous system architectures.
-Service Providers usually enable users to manage their partial identities using online self-service through user profiles.
-Today, customers of SPs are associated with multiple partial identities and user profiles - one for each SP.
+In some cases, user profiles are required by Service Providers even if their service could be provided without them.
+Especially in case of small stores, running their individual online shop, user profiles are not necessary for customers to place an order.
+Personal information can be shared temporarily until processing of the order is completed and the package delivered.
+Some online shops allow users to place orders by temporarily sharing personal information, which however, limits interaction and communication possibilities to insecure e-mail exchange.
 
-The result is a variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
-\begin{itemize}
-    \item Multiple SPs collect, use and share parts of identities which leads to distributed and fragmented identities.
-    \item As a result of the distributed identities, risk of data breaches increases.
-    \item Managing multiple user profiles is very inconvenient for users.
-    \item It is often unclear who stores which data and for what purpose.
-    \item SPs have an incentive to collect and share more user data than they need.
-\end{itemize}
-
-An improved model for identity management is necessary.
-In recent years, multiple new models have been invented.
-One model called Social Login became popular.
-It enables customers to create User Profiles for SPs through existing User Profiles of Social Networks like Facebook.
-This improves identity management by enabling SPs to rely on the external profile for unique identification, authorisation and personal attributes.
-Users can therefore manage identity related information through their Social Profile which is accessed by the SP.
-
-This approach, however, still leaves the requirement of User Profiles for each SP because, depending on the provided service, additional attributes which are not part of the Social Profile, have to be manageable by the user.
-SPs also might require additional online self-service tools the social network does not provide.
-
-The solution to this problem is an Identity Management Provider (IMP) which manages the whole online identity of a person and can replace the individual partial identities and user profiles.
-The system itself is provided and hosted by a SP for consumption by other SPs.
-To replace existing User Profiles, the IMP can not only rely on systems for registration, authentication, authorisation and provisioning.
-Additional requirements of SPs like communication, data wallet and management of additional attributes have to be satisfied.
-
-In order for an SP to use identities and services of an IMP, an integration into the system architecture of the SP has to take place.
-Due to the complex nature of system architectures and identity management, this is a difficult task.
-
-A currently relevant example for usage of online self-service with particular interesting requirements for identities is the German "Online Access Law" (Online Zugangs Gesetz: OZG).
-It requires all administrative services of the german federal republic, each member state and commune to be digitally available through interoperable user profiles.
-The current plan is to make the profiles only available for usage in context of the OZG.
-From a user perspective, this would be yet another partial identity and user profile to manage.
+A method for identity management called Identity Management Provisioning (IMP) is introduced.
+IMP provides identity management as a service to users and Service Providers.
+It enables users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages".
+Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be used in different ways.
+It can be used to create and manage a persistent user profile or to temporarily share personal information for a business process.
+IMP messages enable user and Service Provider to securely exchange structured data and depending on the client application which receives and displays the data, design rich user interactions.

### 2021-03-13 chapters/sections/10-imp_solution_integration.tex
Anfang und ende fertig

--- 2021-03-04 sections/10-imp_solution_integration.tex
@@
 Message types for attribute synchronization, authentication and communication are defined.
-To not disrupt the operation of the existing system architecture, the IMP solution is designed to not replace user profiles but provide an additional way of accessing them trough IMP.
+To not disrupt the operation of the existing system architecture, the IMP solution is designed to not replace user profiles but to provide an additional way of accessing them through IMP.
 To later reduce technological integration efforts, the IMP solution is designed to only require interaction with systems of the portal domain.
@@
 
+\begin{figure}[H]
 \begin{itemize}
@@
     \item Attributes: Name, Surname, ... 
-    \begin{itemize}
-        \item Name: Max
-        \item Surname: Mustermann
-    \end{itemize}
     \item Shared Attributes: Administration Portal of the member state ...
-    \item Reason: Create an OZG user profile and connect your IMP identity.
+    \item Reason: Create an OZG user profile and connect the IMP identity.
     \item Metadata: <<data for technological integration>>
 \end{itemize}
+\end{figure}
 
 Users visiting the account creation web page of the administration portal can use the IMP client to scan the QR code.
-The IMP client presents the corresponding relationship template to the user and automatically fills in attributes which the administration portal requests from the user as part of the relationship.
+The IMP client presents the corresponding relationship template to the user and automatically fills in attributes that the administration portal requests from the user as part of the relationship.
 It is assumed that the IMP system has systems in place for identifying users and validating personal information of corresponding IMP identities.
-As a result of that, service providers could rely on the validity of shared attributes.
+As a result of that, Service Providers can rely on the validity of shared attributes.
 
@@
 \subsection{Message Utilization}
-As part of an established relationship, service provider and user can securely exchange structured data in form of asynchronous messages.
-Security in this case means that messages can not be accessed or modified by a third party and are authorized by the corresponding user.
-Based on this secure data exchange capabilities, service providers can define various types of messages, each with different purposes and effects on the IMP client.
+As part of an established relationship, Service Providers and users can securely exchange structured data in form of asynchronous messages.
+Security in this case is defined as that a messages can not be accessed or modified by a third party and are authorized by the corresponding user.
+Based on this secure data exchange capabilities, Service Providers can define various types of messages, each with different purposes and effects on the IMP client.
 This section contains various message types useful for managing the user profile created as a result of an established relationship.
@@
 \paragraph{Login to User Profile}
-During the user profile creation process using IMP, the user specified a username but not a password. The IMP client is used for authentication of login requests to the administration portal.
+During the user profile creation process using IMP, the user specifies a username but not a password. The IMP client is used for authentication of login requests to the administration portal.
 
@@
 Administration portal and IMP client exchange attribute change request and reply messages.
-The requests can either be accepted or rejected by the service provider.
+The requests can either be accepted or rejected by the Service Provider.
 Accepting the request will result in according modification of the user profile connected to the relationship.
 
-For simplification purposes, the web page for management of personal information on the administration portal is expected to be locked.
+For simplification purposes, the web page for the management of personal information on the administration portal is expected to be read-only.
 However, it would also be possible for the portal to send attribute change requests to the IMP client based on the modifications the user performed on the web page.
@@
 User profiles are known to the existing system architecture and are an often used identity management solution.
-Many service providers, especially in the private sector will want to keep using a profile based identity management approach.
+Many Service Providers, especially in the private sector will want to keep using a profile based identity management approach.
 The IMP solution presents an opportunity of leveraging existing user profile systems while simplifying identity management through IMP.
-In addition to that, the IMP solution is designed, so that it can almost effortlessly be turned on and off, giving service providers the freedom of testing the solution.
-Service providers can initially add the IMP solution as an alternative to the conventional user profile identity management solution and after some period of time switch to only using the IMP solution.
+In addition to that, the IMP solution is designed, so that it can almost effortlessly be turned on and off, giving Service Providers the freedom of testing the solution.
+Service Providers can initially add the IMP solution as an alternative to the conventional user profile identity management solution and after a certain period of time switch to only using the IMP solution.
 
@@
 Users don't have to manually fill in a form for the creation of a user profile but are supported by the IMP client.
-As part of established relationships, service provider and users are able to directly exchange messages with structured content.
+As part of established relationships, Service Provider and users are able to directly exchange messages with structured content.
 In addition to interaction capabilities of the IMP client, this enables a variety of interaction scenarios not possible through for example common e-mail clients.
@@
 This helps users in making an informed decision on whether to create the user profile.
-At any time after the onboarding process, users can view the relationship in the IMP client and check which service providers process which personal information and how.
-This enables users to keep an overview of the distribution of personal information.
+At any time after the onboarding process, users can view the relationship in the IMP client and check which Service Providers process which personal information, why and how.
+This enables users to keep an overview of the distribution of their personal information.
 
 Security is also increased as a result of this approach.
-Through established relationships, service provider and users have the ability to not only directly exchange messages but also securely.
+Through established relationships, Service Provider and users have the ability to not only directly exchange messages but also to do this securely.
 As a result of that, authentication through the IMP client can replace password based authentication methods.
@@
 After an effortless onboarding process on multiple administration portals, users are able to manage each profile through the IMP client.
-This enables users break free access to all user profiles giving the illusion of an interoperable user profile.
+This enables users to break free access from all user profiles giving the illusion of an interoperable user profile.
 Logging in to a user profile using the IMP client eliminates the need of remembering passwords, furthering the illusion of interoperable user profiles.
@@
 The IMP solution has also several problems regarding usability and data protection.
-
 Most importantly, as a result of integrating the IMP system through user profiles, each administration portal is still required to access personal information.
-
-In addition to that, application and management of administrative services remains accessible only through administration portal and form server which presents a discontinuity in accessing OZG services.
+In addition to that, application and management of administrative services remains accessible only through the administration portal and form server which presents a discontinuity in accessing OZG services.

### 2021-03-13 chapters/sections/11-technological_integration.tex
Anfang und ende fertig

@@
 Purpose of the integration architecture is to enable the existing OZG system to access IMP services according to the previously described IMP solution.
-It therefore has to enable the creation of onboarding relationship template, the processing of onboarding relationship requests and the processing of established relationships through creation of user profiles.
-
-In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution. This are messages for attribute changes, communication and authentication.
-
+It therefore has to enable the creation of an onboarding relationship template, the processing of onboarding relationship requests and the processing of established relationships through creation of user profiles.
+\\
+In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution.
+This are messages for attribute changes, communication and authentication.
 As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless translation between the two entities.
-
-OZG system architecture and IMP systems use different data models, especially in regard to personal information. The integration architecture therefore has to translate between them.
-
+OZG system architecture and IMP systems use different data models, especially in regard to personal information.
+The integration architecture therefore has to translate between them.
 As the IMP connector is not capable of sending asynchronous notifications, the integration architecture has to add this functionality.
-
-Depending on the use case of service providers, multiple types of relationships or in this case multiple types of user profiles might be necessary.
-
+Depending on the use case of Service Providers, multiple types of relationships or in this case multiple types of user profiles might be necessary.
 The integration architecture has to enable each type of relationship and user profile to be processed separately, as they might have different processing legitimization.
-
 OZG and the presented IMP solution are only one example of a system architecture and IMP use case.
@@
 \subsection{Messaging}
-For the technological integration, a messaging approach is used.
-As described in section 2.4, messaging enables system to access each others services in a decoupled way.
-This is a useful feature as the integration architecture should reusable for different system architectures.
-
+A messaging approach is used for the technological integration.
+As described in section 2.4, messaging enables the systems to access each others services in a decoupled way.
+This is a useful feature as the integration architecture should be reusable for different system architectures.
 The messaging patterns described in 2.4 also enable the integration architecture to be configured according to changes in the operation of the existing systems.
-
-The asynchronous nature of messaging systems translates nicely to the asynchronous and message based operation of the IMP system and IMP solution.
+The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.
 
@@
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
-\end{center}
+    \caption{Insertion of Integration Systems into OZG System Architecture}
+    \label{integration1:integration_overview}
+\end{figure}
 
 The IMP solution described in the previous section requires the administration portal to access IMP services.
-For integration, an IMP connector and a messaging system are added to the portal domain.
-Using the messaging system, existing systems of the administration portal can access IMP services through the IMP connector.
-
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/2. System Integration Overview.pdf}
-\end{center}
+As shown in figure \ref{integration1:integration_overview}, an IMP connector and a messaging system are added to the administration portal for integration.
+Using the messaging system, existing systems of the administration portal and IMP connector can access each others services.
+IMP server and IMP client of the IMP system as described in section \ref{section:imp_system} are also displayed in figure \ref{integration1:integration_overview}.
 
@@
 All other existing system components remain untouched.
+Through the service facade, the messaging system can integrate services of all connected service components.
 
 \subsection{Onboarding Sequence}
+This section describes the sequence of an application process as visualized in figure \ref{integration1:onboarding_overview}.
 
-\begin{center}
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
-\end{center}
+    \caption{Onboarding Overview}
+    \label{integration1:onboarding_overview}
+\end{figure}
 
-As described in section 5.1, the user should be able to create a new user profile for the OZG system through an existing IMP identity.
+The user should be able to create a new user profile for the OZG system through an existing IMP identity.
 
@@
 The messaging system interacts with the connector to establish the relationship and eventually issues the service facade to create a new user profile based on the attributes shared as part of the IMP relationship.
+\\
 After successful creation of the user profile, the messaging system stores the relationship ID and the user profile ID in a database.
@@
 
-\begin{center}
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
-\end{center}
+    \caption{Messaging Integration}
+    \label{integration1:messaging_integration}
+\end{figure}
 
@@
 
-On the side of the administration portal, messaging adapters provide an API to the existing systems providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
+On the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
 The adapters communicate with the messaging system through channels.
 Messages placed on each channel can be simultaneously accessed by multiple systems.
-Using these channels, message adapters can send requests, receive replies, receive notifications, receive requests and send replies.
+Using these channels, message adapters can send requests and replies, and receive replies, notifications and requests
 
@@
 Using these channels, the messaging system can send REST requests by placing messages on channels corresponding to a certain interface.
-This also enables the messaging system to receive events from by the connector by the messaging adapter placing messages on a notification channels.
+This also enables the messaging system to receive events from the connector.
 
@@
 Messaging modules consist of messaging patterns which are able to modify, delete and route messages.
-Purpose of the modules is to translate messages sent by messaging adapters of either service provider or connector to be understood by the respective recipient.
+Purpose of the modules is to translate messages sent by messaging adapters of either Service Provider or connector to be understood by the respective recipient.
 Each module is assigned to an individual integration task.
-By adding or removing modules, integration capabilities of the messaging system can be suited to the system architecture of the service provider.
+By adding or removing modules, integration capabilities of the messaging system can be suited to the system architecture of the Service Provider.
 Modules can be designed to provide services to messaging adapters or other modules.
@@
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
-\end{center}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
+    \caption{Messaging System Overview}
+    \label{integration1:messaging_system_overview}
+\end{figure}
 
@@
 
-As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which is built upon it.
-As described in section 2.2, communication between IMP identity and service provider is only possible through an established relationship.
+As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which it is built upon.
+As described in section 2.2, communication between IMP identity and Service Provider is only possible through an established relationship.
 
-Three messaging modules on the "Relationship to Identity Integration Layer" exist, which directly access services of the connector.
+Three messaging modules exist on the "Relationship to Identity Integration Layer", which directly access services of the connector.
 The onboarding template module provides the feature of creating relationship templates for onboarding.
-The Onboarding request module, provides the feature of processing and responding to relationship requests.
-And the Onboarding relationship module provides the feature of processing established relationships by creating a new user profile.
-The relationship mapping module has the purpose of combining "Relationship to Identity Integration Layer" and "Communication Integration Layer" by enabling the messaging system to map relationships to the corresponding entity of the service provider.
+The onboarding request module, provides the feature of processing and responding to relationship requests.
+And the onboarding relationship module provides the feature of processing established relationships by creating a new user profile.
+The relationship mapping module has the purpose of combining "Relationship to Identity Integration Layer" and "Communication Integration Layer" by enabling the messaging system to map relationships to the corresponding entity of the Service Provider.
 In this case, the module maps IDs of relationships to IDs of user profiles.
@@
 
-The "Communication Integration Layer" consists of modules, which enable the existing systems to exchange structured data with the IMP client.
-Purpose of the modules is to translate between the data models of the service provider and the IMP system.
+The "Communication Integration Layer" consists of modules, that enable the existing systems to exchange structured data with the IMP client.
+Purpose of the modules is to translate between the data models of the Service Provider and the IMP system.
 Most importantly in this case, none of the existing systems is able to understand relationships or relationship IDs.
 Therefore, the message mapping module has the purpose of translating all incoming relationship IDs to user profile IDs with the help of the previously mentioned relationship mapping module on the underlying layer.
+\\
 Three message modules are included.
-Each of them has the purpose of identifying messages of a certain type and separate them on individual channels.
+Each of them has the purpose of identifying messages of a certain type and separate them onto individual channels.
 This enables the construction of various modules processing the same message types in different ways.
 However, in this case, each message type has only a single module processing it.
-Modules which eventually process the messages, have the purpose of translating the message content between the data models of service provider and IMP system.
+Modules, that eventually process the messages, have the purpose of translating the message content between the data models of Service Provider and IMP system.
 For example the mail module consumes messages which contain a mail received by a user profile.
@@
 
-\subsection{Onboarding Template Module}
+\subsection{Messaging Modules}
 
-\begin{center}
+In this section each messaging module mentioned in the overview of the message architecture is described.
+
+\paragraph{Onboarding Template Module}
+
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/6. Onboarding Template Module.pdf}
-\end{center}
+    \caption{Onboarding Template Module}
+    \label{integration1:onboarding_template_module}
+\end{figure}
 
@@
 Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template.
-In this case, the web server will want to notify the user about the successful creation of his user profile.
+In this case, the web server will need to notify the user about the successful creation of his user profile.
 The web server therefore adds the user's current session ID as metadata to the template.
 
-The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests and the "Onboarding Template Response" channel, where it listens for responses.
-In order for the adapter to correlate request and reply messages, it creates a message which besides the Template Metadata contains a request ID.
+The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests, and the "Onboarding Template Response" channel, where it listens for responses.
+In order for the adapter to correlate request and reply messages, it creates a message that contains a request ID additionally to the Template Metadata.
 This ID is expected to be included in the response message.
@@
 
-In between the message translators, the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute.
-This configuration contains information on how relationship templates of type onboarding are supposed to look like.
+In between the message translators the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute.
+This configuration contains information on how the relationship templates of type onboarding are supposed to look like.
 It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more.
@@
 Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity.
-Therefore, all attributes which are required to create a user profile have to be requested by the template.
+\\
+Therefore all attributes that are required to create a user profile have to be requested by the template.
 In the template, attributes have to be requested according to the data model of the IMP system in order for the IMP client to understand them.
@@
 
-The messaging adapter consumes the message on the response channel and returns the template to the web server, which based on the session ID in the template metadata can display the template as QR code to the user.
+The messaging adapter consumes the message on the response channel and returns the template to the web server which based on the session ID in the template metadata can display the template as QR code to the user.
 
-\subsection{Onboarding Request Module}
+\paragraph{Onboarding Request Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/7. Onboarding Request Module.pdf}
-\end{center}
+    \caption{Onboarding Request Module}
+    \label{integration1:onboarding_request_module}
+\end{figure}
 
 Eventually, the user scans the QR code, fills in the attributes and submits a relationship request.
-The request is received by the connector, forwarded to the messaging adapter and published on the "Relationship Request" channel.
+The request is received by the connector, then forwarded to the messaging adapter and published on the "Relationship Request" channel.
 The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship.
@@
 As in the previous example, message translators are included to construct a canonical data model for the module.
-A message filter only lets messages trough which contain templates of type onboarding.
+A message filter only lets messages through that contain templates of type onboarding.
 The message translator connected to the "Onboarding Request" channel translates attributes shared by the user from the IMP data model to the OZG data model.
@@
 Based on the attributes the user shares, the OZG system has to decide if the relationship should be established or not.
-As this process heavily depends on the use case of the relationship and on the service provider, the messaging system expects the SP to add a module called "Onboarding Request Processing Module" which consumes the request and responds with either approve or reject on the "Onboarding Response" channel.
+As this process heavily depends on the use case of the relationship and on the Service Provider, the messaging system expects the SP to add a module called "Onboarding Request Processing Module" which consumes the request and responds with either approve or reject on the "Onboarding Response" channel.
 To correlate the response to the request, the message also has to contain the relationship ID.
@@
 
-\subsection{Onboarding Relationship Module}
+\paragraph{Onboarding Relationship Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
-\end{center}
+    \caption{Onboarding Relationship Module}
+    \label{integration1:onboarding_relationship_module}
+\end{figure}
 
-If the user did not retract his relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification which the messaging adapter publishes on the "Relationship Established" channel.
+If the user did not retract their relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification that the messaging adapter publishes on the "Relationship Established" channel.
 The message contains the ID of the established relationship along with all attributes shared by the user.
@@
 To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content.
-After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.
+After successful creation of the user profile the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.
 
@@
 
-\subsection{Relationship Mapping Module}
+\paragraph{Relationship Mapping Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Relationship Mapping.pdf}
-\end{center}
+    \caption{Relationship Mapping Module}
+    \label{integration1:relationship_mapping_module}
+\end{figure}
 
-Through the "New Relationship Mapping" channel, the "Relationship Mapping" module receives the message sent by the previously described module.
+Through the "New Relationship Mapping" channel the "Relationship Mapping" module receives the messages sent by the previously described module.
 Purpose of the "Relationship Mapping" module is to map relationships to corresponding entities in the existing system architecture.
@@
 The message consumed through the "New Relationship Mapping" channel is stored in a database for enabling future translation between the contained relationship ID and user profile ID.
-Using the "Relationship Mapping Request" channel, modules can request the "Relationship Mapping" module to add a user profile ID for a given relationship ID and vice versa.
+Using the "Relationship Mapping Request" channel modules can request the "Relationship Mapping" module to add a user profile ID for a given relationship ID and vice versa.
 
@@
 
-\subsection{Message Mapping Module}
+\paragraph{Message Mapping Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Message Mapping Module.pdf}
-\end{center}
+    \caption{Message Mapping Module}
+    \label{integration1:message_mapping_module}
+\end{figure}
 
 Using the previously defined "Relationship Mapping" module, the "Message Mapping" module has the purpose of translating the relationship ID of all inbound messages to the corresponding user profile ID and translating the user profile ID of all outbound messages to the corresponding relationship ID.
-As a result of that, on the left side, messages coming from or going to the existing system architecture, messages contain identification of the known user profile entity instead of the unknown relationship entity.
+As a result of that, on the left side of the figure \ref{integration1:message_mapping_module}, messages coming from or going to the existing system architecture contain identification of the known user profile entity instead of the unknown relationship entity.
 On the right side, messages coming from or going to the IMP system contain identification of the known relationship instead of the unknown user profile.
@@
 Incoming messages on the "Message Inbound" channel are consumed by the module and translated by a message translator to a canonical data model.
-In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a content enricher adds a unique request ID to the message and stores the ID in a database.
+In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a Content Enricher adds a unique request ID to the message and stores the ID in a database.
 Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let through by the request ID message filter.
@@
 
-\subsection{Attribute Change Message Module}
+\paragraph{Attribute Change Message Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/11. Attribute Change Message Module.pdf}
-\end{center}
+    \caption{Attribute Change Message Module}
+    \label{integration1:attribute_change_message_module}
+\end{figure}
 
 For the messaging system to process messages being exchanged as part of relationships, message modules can be added.
-Their purpose is to map messages of certain types on the "Message Inbound Mapping" channel to individual message type channels so that modules can process them.
+Their purpose is to map messages of certain types onto the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them.
 They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.
 
-In this case, an "Attribute Change Message Module" is included, which processes messages related to the attribute change process.
+In this case an "Attribute Change Message Module" is included, which processes messages related to the attribute change process.
 Messages exchanged through IMP relationships can have arbitrary content.
 However, the messages are assumed to contain a message type attribute and a message content attribute.
-Based on the message type attribute, a message filter can let messages through which contain a message type attribute correlating to an attribute change process.
+Based on the message type attribute a message filter can let messages through that contain a message type attribute correlating to an attribute change process.
 Based on the type of a message, a content based message router then copies each message to a datatype channel.
@@
 
-Outbound messages related to the attribute change process are consumed on data type channels.
-In this case, it is only one "Attribute Change Response" channel.
-A content enricher adds a message type attribute correlating to the channel the message was placed on.
+Outbound messages related to the attribute change process are consumed in data type channels.
+In this case it is only one "Attribute Change Response" channel.
+A Content Enricher adds a message type attribute correlating to the channel the message was placed on.
 This is required in order for the IMP client to properly interpret the message.
-After that, the message is published on the "Message Outbound Mapping" channel.
+After that the message is published on the "Message Outbound Mapping" channel.
 
-\subsection{User Profile Attribute Change Request Module}
+\paragraph{User Profile Attribute Change Request Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/12. Attribute Change Request Module.pdf}
-\end{center}
+    \caption{Attribute Change Request Module}
+    \label{integration1:attribute_change_request_module}
+\end{figure}
 
@@
 Messages arriving on the "Attribute Change Request" channel were mapped from a relationship ID to a user profile ID in an earlier integration step.
-Depending on the use case of the service provider, not all user profiles should be processed in the same way.
-Therefore, message filters are inserted, which are able to distinguish possible "types" of user profiles based on the user profile ID.
-It would also be possible to include an additional module, which is able to request user profile type information from the existing systems, separating messages on the "Attribute Change Request" channel appropriately.
-For example, user profiles for businesses could exist, where processing of attribute change requests requires a more through and manual verification by employees.
+Depending on the use case of the Service Provider, not all attribute change requests for user profiles should be processed in the same way.
+Therefore, message filters are inserted which are able to distinguish possible "types" of user profiles based on the user profile ID.
+It would also be possible to include an additional module that is able to request user profile type information from the existing systems, separating messages on the "Attribute Change Request" channel appropriately.
+For example, user profiles for businesses could exist, where processing of attribute change requests requires a more thorough and manual verification by employees.
 
@@
 
-Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the service provider.
-Therefore, the SP is expected to include a "Profile Attribute Change Processor" module, which based on the user profile ID and the shared attributes decides to approve or reject the request.
-The response is published to the "Attribute Change Response" channel and besides the response, contains the user profile ID.
+Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the Service Provider.
+Therefore the SP is expected to include a "Profile Attribute Change Processor" module, which decides to approve or reject the request based on the user profile ID and the shared attributes.
+The response is published to the "Attribute Change Response" channel and contains the user profile ID additionally to the response.
 
-\subsection{User Profile Attribute Sync Module}
+\paragraph{User Profile Attribute Sync Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/13. User Profile Attribute Sync Module.pdf}
-\end{center}
+    \caption{User Profile Attribute Sync Module}
+    \label{integration1:user_profile_attribute_sync_module}
+\end{figure}
 
-If the user did not cancel the attribute change request before the OZG system accepted, the attribute change is established.
+If the user did not cancel the attribute change request before the OZG system accepted it, the attribute change is established.
 The connector is notified through a message, which eventually is processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.
@@
 
-\subsection{Mail Message module}
+\paragraph{Mail Message module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/14. Mail Message Module.pdf}
-\end{center}
+    \caption{Mail Message Module}
+    \label{integration1:mail_message_module}
+\end{figure}
 
-In order for the user to receive messages sent to his user profile through the IMP client, mail messages are processed by the integration architecture.
+In order for the user to receive messages sent to their user profile through the IMP client, mail messages are processed by the integration architecture.
 Similar to the "Profile Attribute Change Message" module, a "Mail Message" module is included, which maps messages on the "Mail Outbound" channel to the "Message Outbound Mapping" channel.
@@
 
-Before publishing messages on the "Message Outbound Mapping" channel, a content enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it.
+Before publishing messages on the "Message Outbound Mapping" channel, a Content Enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it.
 
-\subsection{Mail Module}
+\paragraph{Mail Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/15. Mail Module.pdf}
-\end{center}
+    \caption{Mail Module}
+    \label{integration1:mail_module}
+\end{figure}
 
@@
 
-\subsection{Authentication Message Module}
+\paragraph{Authentication Message Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/16. Authenticatin Message Module.pdf}
-\end{center}
+    \caption{Authentication Message Module}
+    \label{integration1:authentication_message_module}
+\end{figure}
 
-If the user creates a user profile using his IMP identity, it is possible to replace password authentication with authentication through the IMP client.
+If the user creates a user profile using their IMP identity, it is possible to replace password authentication with an authentication through the IMP client.
 It is also possible to use the IMP client for two factor authentication.
@@
 
-\subsection{Authentication Module}
+\paragraph{Authentication Module}
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/17. Authentication.pdf}
-\end{center}
+    \caption{Authentication Module}
+    \label{integration1:authentication_module}
+\end{figure}
 
-When the user visits the web page of the administration portal to apply for an administrative service, he will have to login.
+When the users visit the web page of the administration portal to apply for an administrative service, they will have to login.
 To utilize the IMP client for authentication, the web server can use a channel adapter to publish an authentication request concerning a user profile ID and a certain session ID.
@@
 Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser.
-Similar to previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message".
+Similar to previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message" channel.
 
-Eventually, the IMP client sends a response as message, which the "Authentication Message" module publishes on the "Authentication Response" channel.
-Similar to previous modules, the service provider can use a message filter to process user profile types differently.
+Eventually, the IMP client sends a response as a message, which the "Authentication Message" module publishes on the "Authentication Response" channel.
+Similar to previous modules the Service Provider can use a message filter to process user profile types differently.
 After translating the message to the OZG data model, it is published on the "Authenticate Profile Response" channel.
@@
 The messaging system and the modular approach make integration architecture expandable and configurable for new integration scenarios.
-
 Message mapping module and relationship mapping module enable the translation between user profile and relationship.
-
 Onboarding template, onboarding request and onboarding relationship module enable the definition and utilization of one or more relationship types.
-
 Message modules enable the definition of message types.
-
 Message processing modules enable the translation between data models.
-
-Messaging system enables asynchronous, event based and direct communication between user and service provider.
-
+Messaging system enables asynchronous, event based and direct communication between user and Service Provider.
 Assigning special modules to each type of relationship and message type enables the separation of processing depending on differences in processing legitimization.

### 2021-03-13 chapters/sections/13-imp_solution_integration.tex
Anfang und ende fertig

@@
 The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection.
-The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.
+The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and administration portals to process personal information.
 
@@
 As part of the existing operation of the OZG system architecture, applications submitted to administration portals will eventually be transferred to responsible governmental institutions.
-Using IMP, relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.
+Using IMP relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.
 
@@
 \end{itemize}
+\end{figure}
 
-In contrast to relationship templates in the previous IMP solution, these wont have to be dynamically created but only once.
+In contrast to relationship templates in the previous IMP solution, these will not have to be dynamically created but only once.
 The reason is that in the previous IMP solution templates had to contain personalized information like the session ID.
@@
 
-Visiting the web page of the institution, the user can scan the QR code and is presented with the relationship template.
+Visiting the web page of the institution, the user can scan the QR code and the corresponding relationship template for an application is shown.
 The user can read through the included description of the corresponding administrative service to determine if it is the correct one.
@@
 Based on the shared attributes, the institution can decide to either accept or reject the application request.
-It might for example verify if the home address of the user lies in the area of its responsibility.
+It might for example verify whether the home address of the user is within the area that it is responsible for.
 
-When accepting the relationship and therefore the application request, and the user did not retract his request in the meantime, the relationship is established and the institution gets notified about a new application.
+When accepting the application request and therefore the whole relationship, and if the user did not retract his request in the meantime, the relationship is established and the institution gets notified about a new application.
 
@@
 It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address.
-Therefore, users visit any administration portal, search for an administrative service and specify their home address.
+Therefore users visiting any administration portal search for an administrative service and specify their home address.
 The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.
@@
 
-This IMP solution utilizes the same message types as the previous IMP solution, however with a different purpose.
+This IMP solution utilizes the same message types as the previous IMP solution, however for a different purpose.
 
@@
 
-Through the IMP, client users can request attribute changes for established relationships.
+Through the IMP client, users can request attribute changes for established relationships.
 The purpose of these messages is to enable users to change the content of an application even after it was submitted.
@@
 
-As no user profiles are necessary in this IMP solution, users wont have to use the IMP client for logging into a user profile.
+As no user profiles are necessary in this IMP solution, users will not have to use the IMP client for logging into a user profile.
 However, authentication messages can still be used as an accept / reject based communication method.
@@
 Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes.
-The user can better control whether he agrees to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved.
-In case of the OZG, the user profile component did require authentication prior to sharing attributes with institutions, but this might not be the case for all service providers.
+The users can better control whether they agree to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved.
+In case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.
 
-Using relationships for execution of business processes eliminates the need for service providers to operate identity management systems.
+Using relationships for execution of business processes eliminates the need for Service Providers to operate identity management systems.
 It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution.
-This leaves the service provider with the main task of executing the business processes.
+This leaves the Service Provider with the main task of executing the business processes.
 
@@
 
-The disadvantage of this IMP solution is, the invasive integration, which does not only provide an alternative way of accessing existing systems but for the most part replaces them.
+The disadvantage of this IMP solution is the invasive integration which does not only provide an alternative way of accessing existing systems but for the most part completely replaces them.

### 2021-03-13 chapters/sections/14-technological_integration.tex
Anfang und ende fertig

@@
 
-Focus of the technological integration in this case is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
+Focus of the technological integration is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
 The layout of the messaging system should not change and the purpose of each module should stay the same.
@@
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
-\end{center}
+    \caption{Integration Overview}
+    \label{integration2:integration_overview}
+\end{figure}
 
@@
 
-\begin{center}
+\begin{figure}[H]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
-\end{center}
+    \caption{Service Application Overview}
+    \label{integration2:application_overview}
+\end{figure}
 
@@
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
-\end{center}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
+    \caption{Messaging Overview}
+    \label{integration2:messaging_overview}
+\end{figure}
 
@@
 
-\subsection{Application Template Module}
+\subsection{Messaging Modules}
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/4. Application Template Module.pdf}
-\end{center}
+\paragraph{Application Template Module}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/4. Application Template Module.pdf}
+    \caption{Application Template Module}
+    \label{integration2:application_template_module}
+\end{figure}
 
@@
 
-\subsection{Application Request Module}
+\paragraph{Application Request Module}
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/5. Application Request Module.pdf}
-\end{center}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/5. Application Request Module.pdf}
+    \caption{Application Request Module}
+    \label{integration2:application_request_module}
+\end{figure}
 
@@
 
-\subsection{Application Relationship Module}
+\paragraph{Application Relationship Module}
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/6. Application Relationship Module.pdf}
-\end{center}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/6. Application Relationship Module.pdf}
+    \caption{Application Relationship Module}
+    \label{integration2:application_relationship_module}
+\end{figure}
 
@@
 
-\subsection{Application Attribute Change Request Module}
+\paragraph{Application Attribute Change Request Module}
 
-\begin{center}
-    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/7. Application Attribute Change Request Module.pdf}
-\end{center}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/7. Application Attribute Change Request Module.pdf}
+    \caption{Application Attribute Change Request Module}
+    \label{integration2:application_attribute_change_request_module}
+\end{figure}
 
@@
 
-\subsection{Application Attribute Sync Module}
+\paragraph{Application Attribute Sync Module}
 
@@
 
-\subsection{Application Mail}
+\paragraph{Application Mail Module}
 
@@
 
-\subsection{Application Authentication}
+\paragraph{Application Authentication Module}
 
@@
 \subsection{Evaluation}
-The integration architecture enables users to directly interact with the system architecture of the service provider for submitting applications.
+The integration architecture enables users to directly interact with the system architecture of the Service Provider for submitting applications.
 This eliminates the need for administration portals to process personal information.
 
-\begin{center}
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/OZG Personal Information.pdf}
-\end{center}
+    \caption{OZG System Architecture Personal Information}
+    \label{integration2:ozg_personal_information}
+\end{figure}
 
-\begin{center}
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
-\end{center}
+    \caption{IMP System Architecture Personal Information}
+    \label{integration2:imp_personal_information}
+\end{figure}
 

### 2021-03-13 chapters/sections/15-conclusion.tex
Anfang und ende fertig

@@
 
-\begin{itemize}
-    \item Purpose of the thesis is to design integration solutions for identity management provisioning systems on the example of OZG.
-    \item The integration is separated into a business scenario integration trough an IMP solution and a system integration trough a messaging system.
-    \item Trough two IMP solutions, it was shown, how IMP can be utilized in different identity management scenarios
-    \item In the first scenario, an IMP solution was presented which focused on enhancing usability of 
-    \item The thesis introduced identity management provisioning as an identity management service capable of replacing conventional user profiles
-    \item On the example of the OZG, the thesis showed 
-\end{itemize}
+The thesis describes an identity management method called IMP, which provides identity management to Service Providers and users as a service.
+To share personal information, users and Service Providers can establish IMP relationships and exchange IMP messages to interact with each other.
+On the example of the system architecture for the Online Access Law, problems of user profile based identity management are described as well as possibilities of how IMP could be used to solve them.
+
+User profile based identity management systems lack usability as they lead to a fragmentation of partial identities, accessible only through separate applications and web pages.
+Data protection is reduced due to the lack of oversight for the user about existing user profiles and shared personal information.
+Due to the distribution of personal information to various Service Providers, the risk of data being stolen increases.
+
+Especially in case of the OZG, issues regarding data protection exist: As a result of the "one-for-all" method, access to administrative services is distributed across multiple administration portals.
+Users applying for services therefore have to share large quantities of personal information with administration portals of multiple federal states.
+As institutions and not administration portals eventually process the personal information, sharing personal information directly with institutions would be favourable in regard to data minimisation.
+
+Using the OZG as an example, the thesis presents two solutions for IMP utilization for Service Providers with existing user profile based identity management.
+The first solution utilizes IMP in addition to existing user profiles.
+It provides an optional way for users to create and manage OZG user profiles through an IMP client.
+This is done by enabling users to create new user profiles through existing IMP identities by establishing an IMP relationship.
+By exchanging IMP messages users are able to access and manage their user profile.
+The IMP solution especially improves usability as OZG user profiles can be managed along with many other user profiles of other Service Providers through the same IMP client.
+The solution requires integration only with the administration portal component and can operate without disrupting the existing operation of the system architecture.
+However, this IMP solution does not solve many of the data protection issues, as the user profile based identity management system remains in operation.
+
+The second solution utilizes IMP to replace user profiles.
+Instead of persistently sharing personal information with administration portals in form of user profiles, IMP is used to temporarily share personal information with institutions, for the period of time where an application is being processed.
+This is done by enabling users to establish different types of IMP relationships, each corresponding to a different application type.
+This IMP solution especially improves data protection, as only the institution responsible for processing the application receives personal information.
+In addition to that, sharing personal information only for a short period of time decreases the risk of personal information being misused or stolen.
+
+Service Providers which want to use IMP solutions have to integrate the IMP system into their existing system architecture.
+The IMP system provides an IMP connector with a REST interface for integration purposes.
+However, as the functionality of the connector is limited to establishing communication between user and Service Provider and exchanging messages, additional integration systems are necessary.
+
+The thesis presents a modular messaging system, which enables the integration of IMP solutions into existing system architectures of Service Providers.
+Through the messaging system, the system architecture of the Service Provider can
+establish multiple types of IMP relationships and define, exchange and process different message types.
+The messaging system maps relationships to entities the SP systems understand.
+This can be for example the mapping of an IMP relationship to a user profile or to an application process.
+It also translates between data models of IMP and Service Provider.
+As a result of using messaging and messaging modules, the integration system can be configured and extended to fit requirements of different system architectures of Service Providers.
+
+The messaging system is shown, integrating both previously descried IMP solutions into different system architectures.
+The first IMP solution was integrated into the administration portal component, the second IMP solution was integrated into the institution domain.
+This demonstrates, that the messaging system is capable of integrating different IMP solutions into different system architectures.
+
+\section{Solution to Objectives}
 
@@
 
-\begin{itemize}
-    \item experimental evaluation
-    \item 
-\end{itemize}
+The bachelor thesis describes integration of IMP on a theoretical level.
+Developing a prototype of the messaging system as part of an experimental evaluations can give further information about its feasibility, performance and stability.
+The prototype can furthermore be used to test integration of the first IMP solution into the OZG system architecture of a federal state to validate the functionality of IMP solution and messaging system and find out about possible missing features.
+Due to the modular design of the messaging system, new messaging modules implementing missing features can be added.
+
+The thesis presents OZG as a Service Provider relevant for integration of IMP.
+IMP, however, is relevant for many other Service Providers.
+For example, in the scope of the National Education Platform, "a digital portal is being created that in the future will support universities as well as national and international students who are seeking a stay abroad, a course of study, or a change of study location in Germany along their educational career through a digital offering that is interoperable across institutions" \cite{digitale_bildung}.
+In accordance to IMP solutions in the thesis, an IMP solution for this new use case can be designed and the presented messaging system can be configured and expanded to suit new requirements and be used for system integration.

### 2021-03-13 chapters/sections/2-objective.tex
Anfang und ende fertig

@@
-Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.
+Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to for example access personal information and perform authentication.
+They also play an important role in the design of business processes.
+Therefore, for Service Providers to utilize IMP, integration into existing business processes and existing system architectures is necessary.
 
-In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
+A currently relevant topic with challenging requirements regarding identity management is the German Online Access Law (Online Zugangs Gesetz - OZG).
+It requires all administrative services of the German federal republic, each federal state and commune to be digitally available through interoperable user profiles.
+The current plan is to make user profiles only available for usage in context of the OZG.
+From a user perspective, this is yet another partial identity and user profile to manage.
 
-Two solutions for IMP integration and one message based IMPS integration architecture are presented.
+One objective of the bachelor thesis is to design IMP solutions which enable utilization of IMP on the example of - but not limited to - the OZG use case.
+IMP solutions describe how IMP relationships and IMP messages can be utilized by users and Service Providers to share personal information and interact in order to improve, simplify, eliminate or replace existing business process.
+Besides usability and system complexity concerns, IMP solutions also make design decisions in regard to data protection and security.
 
-The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management.
-In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them.
-This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.
-
-In the second solution, IMP is used as an alternative way for identity management without user profiles.
-This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.
-
-The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers.
-This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.
+Using OZG as an example, another objective of the bachelor thesis is to design a technological integration architecture for integration of IMP solutions into existing system architectures of Service Providers.
+Its integration capabilities should, however, not be limited to one IMP solution and one system architecture.
+On the contrary, it should be capable of integrating various IMP solutions into different system architectures.
+The integration system therefore should be configurable and expandable according to requirements of new IMP solutions and system architectures.
+To demonstrate the capabilities of the integration architecture, IMP solutions presented as part of the thesis, should be integrated into different system architectures in context of the OZG.

### 2021-03-13 chapters/sections/3-structure_of_work.tex
Anfang und ende fertig

@@
-In the chapter "Background and Related Work" important topics, following chapters rely on are covered.
-In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well ass possible solutions trough IMP.
+In the chapter "Background and Related Work" important topics that following chapters rely on are covered.
+In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well as possible solutions through IMP.
 In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.

### 2021-03-13 chapters/sections/5-imp.tex
Anfang und ende fertig

@@
-The purpose of this section is not to give a detailed explanation but to deliver a broad understanding of what identity management provisioning is, what an IMP service can look like and how identity management provisioning systems can operate.
+The purpose of this section is to deliver a broad understanding of what Identity Management Provisioning (IMP) is, what an IMP service can look like and how identity management provisioning systems can operate.
 
 \subsection{IMP}
-Identity management provisioning (IMP) is a method of identity management where identity management is provided as a service to users and service providers.
-The service enables users to manage a digital identity and use it to share personal information and interact with service providers.
+Identity Management Provisioning is a method where identity management is provided as a service to users and Service Providers.
+The service enables users to create and manage a digital identity and use it to share personal information and interact with Service Providers.
 
-Many identity management systems currently in use by service providers each require the user to create a user profile, specify login credentials and maintain personal information.
-Each service provider operates his own identity management system and users have to access each system individually trough multiple websites to access their user profiles.
+Many identity management systems currently in use by Service Providers require the user to create a new user profile, specify login credentials and keep the personal Information up to date.
+Every Service Provider operates their own identity management system and users have to access each system individually through multiple websites to use their user profiles.
 This approach to identity management leads to several problems which are discussed in section \ref{section:identity_management_issues}.
@@
 In contrast to a user profile based identity management approach, IMP provides identity management as a service.
-Only one identity management provisioning system is hosted and accessed by user and service providers.
-Users therefore only need one IMP identity, which is accessed by multiple service providers.
-This approach to identity management is capable of solving various issues of user profile based identity management which is discussed in section \ref{section:imp_solution_opportunities}
+Only one identity management provisioning system is hosted and accessed by users and Service Providers.
+Users therefore only need one IMP identity, which is accessed by multiple Service Providers.
+This approach to identity management is capable of solving various issues of user profile based identity management that are discussed in section \ref{section:imp_solution_opportunities}
 
 To access the IMP service, users can use applications or websites.
-Service providers however often require integration into their existing system architecture to enable existing system components to use the new identity management method.
+Service Providers however often require integration into their existing system architecture to enable existing system components to use the new identity management method.
 
@@
 This section describes what an identity management provisioning service can look like.
-It is based on the IMP service called IDAS.
+The content of this section is based on the IMP service provided by IDAS \cite{idas}.
 
-For users and service provider to access the IMP service, software tools exist.
+Software tools exist for users and Service Provider to access the IMP service. 
 For the user, this is a smartphone application.
-For the service provider this is an integration component.
+For the Service Provider this is an integration component.
 The smartphone application provides a user friendly graphical interface which enables the user to receive notifications, maintain personal information, share personal information, and more.
-The integration component for the service provider is a software solution with similar capabilities as the smartphone app but designed towards enterprise use.
+The integration component for the Service Provider is a software solution with similar capabilities as the smartphone app but designed towards enterprise use.
 It therefore has no graphical user interface but additional business relevant features and integration capabilities.
@@
 After installation of the smartphone application, a new identity (IMP identity) can be created.
-As part of this identity, the user can add any amount of key-value pairs as attributes.
-The list of all attributes makes up the personal information of the IMP identity.
-Despite being able to add any key-value pair, there exist some commonly used keys like name, age, home address and so on.
-Depending on the use case of service providers, multiple more keys and their meaning have to be agreed upon.
-This means, the IMP service has to define a canonical data model.
-Each service provider then translates it to their individual data models.
+As part of this identity, the user can add any amount of key-value pairs as attributes, the list of all attributes making up the personal information of the IMP identity.
+Despite being able to add any key-value pair, there are some commonly used keys like name, age, home address etc.
+Depending on the use case of Service Providers, multiple more keys and their meaning have to be agreed upon.
+This means the IMP service has to define a canonical data model.
+Each Service Provider then translates it to their individual data models.
 
-Many service providers require users to manually verify their identity and personal information by for example visiting a store and showing their ID card.
+Many Service Providers require users to manually verify their identity and personal information by for example visiting a store and showing their ID card.
 Similar verification processes are expected to be used by the IMP service to verify IMP identities and their personal information.
-However, for simplification reasons, the details of this verification process are left out.
+However, for simplification reasons, the details of this verification process are left out .
 
-Users and service providers can establish relationships and use them to share personal information and interact.
-The initial form of a relationship is a relationship template.
-The template is created by the service provider and describes which types relationships he is willing to establish.
+Users and Service Providers can establish relationships and use them to share personal information and interact.
+The initial form of a relationship is a relationship template, which is created by the Service Provider and describes what types of relationships they are willing to establish.
 The templates are made available to interested users, which can use them to request relationships.
 
-A service provider fill a relationship template with optional and mandatory information:
+A Service Provider fill a relationship template with optional and mandatory information:
 
@@
 
-\paragraph{Requested Attributes} The service provider can list keys of attributes he requires the user to share in order to send a relationship request.
+\paragraph{Requested Attributes} The Service Provider can list keys of attributes he requires the user to share in order to send a relationship request.
 When the user submits a relationship request based on this relationship template, the values filled in for the requested attributes are copied and sent as part of the request.
@@
 
-\paragraph{Shared Attributes} Shared Attributes is a list of key-values pairs, the service provider makes available to any user interested in requesting a relationship.
-The service provider has to share a minimal amount of attributes which enable the user to identify it.
+\paragraph{Shared Attributes} Shared Attributes is a list of key-values pairs that the Service Provider makes available to any user interested in requesting a relationship.
+The Service Provider has to share a minimal amount of attributes that enable the user to identify it.
 
-\paragraph{Purpose} This is a text field where the service provider can give a detailed explanation of what the purpose of the relationship is, e.g what effects a relationship request and an established relationship will have.
-Here, the reason for why the requested attributes are necessary for the relationship has to be explained as well as how each shared attribute is going to be processed.
+\paragraph{Purpose} This is a text field where the Service Provider can give a detailed explanation of what the purpose of the relationship is, e.g what effects a relationship request and an established relationship will have.
+The reason for why the requested attributes are necessary for the relationship have to be explained here as well as how each shared attribute is going to be processed.
 This helps the user in making an informed decision on whether to submit the relationship request or not.
 
-\paragraph{Attachments} Attachments can be all kinds of documents and files.
-Here, for example legal information can be included but also for example product flyers corresponding to the relationship template.
+\paragraph{Attachments} Attachments can be all kinds of documents and files. For example legal information can be included but also product flyers corresponding to the relationship template, etc.
 
-\paragraph{Metadata} Metadata can be any type of information which should not be displayed to the user but is necessary for the user application or the service provider to process the relationship process.
+\paragraph{Metadata} Metadata can be any type of information which should not be displayed to the user but is necessary for the user application or the Service Provider to process the relationship process.
 
@@
 
-Based on the information about the service provider and the purpose of the relationship, the user can decide to send a relationship request or not.
-If the user decides to request the relationship, the request is sent to the service provider.
-If the service provider approves the request, the relationship is established and both parties get notified.
-Trough the IMP application, the user can see all relationships as well as their status, the content of the underlying relationship template and a list of shared attributes and their values.
+Based on the information about the Service Provider and the purpose of the relationship, the user can decide to send a relationship request or not.
+If the user decides to request the relationship, the request is sent to the Service Provider.
+If the Service Provider approves the request, the relationship is established and both parties get notified.
+Through the IMP application, the user can see all relationships as well as their status, the content of the underlying relationship template and a list of shared attributes and their values.
 
-As part of an established relationship, user and service provider can interact with each other by asynchronously exchanging structured data packages as IMP messages.
-IMP messages can contain any content, however, both IMP application and service provider systems should be able to understand the messages.
+As part of an established relationship, user and Service Provider can interact with each other by asynchronously exchanging structured data packages as IMP messages.
+IMP messages can contain any content, however, both IMP application and Service Provider systems should be able to understand the messages.
 For this purpose, besides content, messages are expected to contain some identification value like a message type.
-The integration component provided to the SP does not process the content of messages but simply makes the messages accessible to the system architecture of the service provider.
-Without additional integration systems, the service provider has to implement his own solutions for understanding and processing messages.
+The integration component provided to the SP does not process the content of messages but simply makes the messages accessible to the system architecture of the Service Provider.
+Without additional integration systems, the Service Provider has to implement his own solutions for understanding and processing messages.
 The IMP application however, has a set of messages it understands.
@@
 
-Some important messages the IMP application understands and the service provider should be able to process too are:
+Some important messages the IMP application understands and the Service Provider should be able to process are:
 
-\paragraph{Mail} Messages of the mail type can be used by service provider and user to exchange human readable text.
-Mails sent to an IMP identity are displayed by the IMP application trough for example a notification.
-The IMP application defines a format, for the content of the mail.
+\paragraph{Mail} Messages of the mail type can be used by Service Provider and user to exchange human readable text.
+Mails sent to an IMP identity are displayed by the IMP application through for example a notification.
+The IMP application defines a format for the content of the mail. The term "mail" is used as an alternative to the term "message", as messages will later be used in context of a messaging system.
 
 \paragraph{Attribute Change} Messages of the attribute change type can be used by the user to request the modification of shared attributes.
-The user can modify, add or delete attributes shared as part of a relationship and submit a attribute change request to the service provider which contains the changes.
-The service provider can decide to either accept or reject the request and respond with a corresponding attribute change response message.
-The IMP application defines a format, for the content of the attribute change request and response messages.
+The user can modify, add or delete attributes shared as part of a relationship and submit an attribute change request to the Service Provider which contains the changes.
+The Service Provider can decide to either accept or reject the request and respond with a corresponding attribute change response message.
+The IMP application defines a format for the content of the attribute change request and response messages.
 
-\paragraph{Authentication} Messages of the authentication type can be used by the service provider to request confirmation from the IMP identity for some business process.
-The service provider sends a initial request message to the IMP identity which contains a description of what confirmation is requested by the user.
+\paragraph{Authentication} Messages of the authentication type can be used by the Service Provider to request confirmation from the IMP identity for specific business process.
+The Service Provider sends an initial request message to the IMP identity which contains a description of what confirmation is requested by the user.
 Through the IMP application the user is notified and can accept or reject.
-Depending on the interaction by the user, the IMP application sends a response message to the service provider.
-The IMP application defines a format, for the content of the authentication request and response messages.
+Depending on the interaction by the user, the IMP application sends a response message to the Service Provider.
+The IMP application defines a format for the content of the authentication request and response messages.
 
-The IMP system guarantees that all information is encrypted and can only be decrypted by identities which are allowed to read it.
+The IMP system guarantees that all information is encrypted and can only be deciphered by identities that are allowed to read it.
 This usually does not include the systems hosting the IMP service.
-Only the owner of an identity can manage attributes of his identity.
+Only the owner of an identity can manage attributes of their identity.
 A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared.
-Interactions as part of a relationship are only possible between the two parties of the relationship and cannot be intercepted or modified others.
+Interactions as part of a relationship are only possible between the two parties of the relationship and cannot be intercepted or modified by others.
 
 \subsection{IMP System} \label{section:imp_system}
-
-There are many ways to design a system for identity management provisioning.
-This section describes what an identity management provisioning systems can look like.
-It is based on the IMP system for IDAS.
-An IMP system is the combination of all system components required for providing IMP services.
+This section describes the IMP system which is the system architecture required for providing the IMP service described in the previous section.
+The content of this section is based on the IMP system used by IDAS \cite{idas}.
 
@@
 
-As shown in figure \ref{imp:imp_system_overview}, the IMP system can be separated into three domains.
-The user domain contains systems the user directly interacts with.
+As shown in figure \ref{imp:imp_system_overview}, the IMP system can be separated into three domains. \\
+The user domain contains systems that the user directly interacts with.
 These typically are applications on PC or smartphone and websites.
 IMP application on smartphones are provided to users for accessing IMP services.
-For simplification, each user is assumed to use access the IMP service trough one device which eliminates the need for device synchronization.
-As previously described, the IMP application enables the user to manage attributes of his identity, to establish relationships, to manage relationships and interact with messages through relationships.
+For simplification, each user is assumed to access the IMP service through one device which eliminates the need for device synchronization.
+As previously described, the IMP application enables the user to manage attributes of their identity, to establish relationships, to manage relationships and to interact with messages through relationships.
 
-The service provider domain contains the system architecture of the service provider and the IMP connector.
+The Service Provider domain contains the system architecture of the Service Provider and the IMP connector.
 The IMP connector contains a REST API which enables the system architecture to access IMP services.
@@
 The IMP server is able to communicate with each IMP application and IMP connector.
-It has the purpose of maintaining a - where necessary encrypted - list of all identities, relationships, relationship templates and IMP messages.
-As the IMP server does not know the private key corresponding to the IMP identity, it is unable to decrypt the data.
+It has the purpose of maintaining a - when necessary encrypted - list of all identities, relationships, relationship templates and IMP messages.
+As the IMP server does not know the private key corresponding to the IMP identity, it is unable to decipher the data.
 The IMP server is also capable of creating relationship templates, processing and routing relationship requests and responses and IMP messages.
-The exact details of how the IMP server operates is out of the scope of this thesis.
+The exact details of how the IMP server operates is too broad to be covered in this thesis.
 
@@
 The vertical bars in the figure represent all previously described components of the IMP system and one additional component called "Integration Module".
-The "Integration Module" is not important for the moment and fill be the focus of following chapters.
+The "Integration Module" is not important at the moment and will be the focus of following chapters.
 The horizontal bars in the figure represent layers of IMP system operation.
-From bottom to top, the layers describe the operation of the IMP system in a way increasingly abstracted from the underlying technology.
+From bottom to top, the layers describe the operation of the IMP system increasingly more abstract from the underlying technology.
 In addition to that, each bar is split up into two sides, however, in this section only the left side is relevant.
@@
 On this layer, the IMP system operates by establishing relationships.
-IMP application and IMP connector exchange relationship requests and responses trough the IMP server in order to establish new relationships.
+IMP application and IMP connector exchange relationship requests and responses through the IMP server in order to establish new relationships.
 The IMP server maintains a list of all relationships and their status.
@@
 On this layer, IMP messages are exchanged as part of an active IMP relationship between IMP application and IMP connector.
-The application can create, send, receive, process and display a list of IMP messages he is able to understand.
-The IMP connector is able to send and receive IMP messages through a relationship without being aware of its content.
+The application can create, send, receive, process and display a list of IMP messages that it is able to understand.
+The IMP connector is able to send and receive IMP messages through a relationship without requiring to know details about the content.
 The IMP server stores an encrypted backup of all messages.
 
-Using IMP relationships and IMP messages, the service provider can interact with the user on the "IMP Interaction Layer".
+Using IMP relationships and IMP messages, the Service Provider can interact with the user on the "IMP Interaction Layer".
 On this layer, depending on the use case, different purposes can be assigned to interaction possibilities.
-For example, a service provider can decide to use relationships as a way to receive product or subscription orders.
+For example, a Service Provider can decide to use relationships as a way to receive product or subscription orders.
 Another possibility would be to use relationships for filling in a form as part of a survey.
@@
 
-In this section the IMP system operation for most important use cases of the IMP service are described in more detail.
+In this section the IMP system operation for the most important use cases of the IMP service are described in more detail.
 
@@
 The first step towards a relationship is the interest of a user.
-A user for example wants to subscribe to the newsletter of a service provider.
-The service provider needs personal information of the user to be able to send him personalized mails.
-To obtain the necessary attributes and receive the approval of the user, the service provider requires an established relationship.
+A user for example wants to subscribe to the newsletter of a Service Provider.
+The Service Provider needs personal information of the users to be able to send them personalized mails.
+To obtain the necessary attributes and receive the approval of the users, the Service Provider requires  established relationships.
 
@@
 
-To enable users to request a relationship with the purpose of subscribing for a newsletter, the service provider has to create a relationship template.
+To enable users to request a relationship with the purpose of subscribing to a newsletter, the Service Provider has to create a relationship template.
 Through the REST interface of the connector, the SP sends a request for a new relationship template.
@@
 In this case, the relationship template could be configured as follows:
-
+\begin{figure}[H]
     \begin{itemize}
@@
     \item Shared Attributes: SP Name, SP address, SP phone number, SP E-Mail address
-    \item Purpose: By accepting this relationship, you agree to receive personalized mails to the shared address. Name, surname and interests are required to personalize the content of the mails.
-    \item Attachments: Some legal document
+    \item Purpose: By accepting this relationship, you agree to receive personalized emails to the shared address. Name, surname and interests are required to personalize the content of the emails.
+    \item Attachments: required legal document
 \end{itemize}
+\end{figure}
 
@@
 Through this ID, the corresponding template can be retrieved from the IMP server.
-The service provider can transmit the template ID to any user who wishes to subscribe for a newsletter. This can be done by for example rendering the template ID as a QR code on a website.
+The Service Provider can transmit the template ID to any user who wishes to subscribe to a newsletter. This can be done by for example rendering the template ID as a QR code on a website.
 If the QR code is displayed to the user, he can scan it using the IMP application.
@@
 A unique relationship ID is attached.
-The server then forwards the relationship request to the connector of the service provider.
+The server then forwards the relationship request to the connector of the Service Provider.
 
-As the system architecture of the service provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector through its REST interface.
-The connector responds with the received relationship request.
-The system architecture of the service provider processes the request in order to decide if it should be accepted.
-The service provider could for example verify if a relationship with the identity already exists or if the e-mail address is already registered.
+As the system architecture of the Service Provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector through its REST interface.
+The connector responds with the received relationship request, provided a request was submitted.
+The system architecture of the Service Provider processes the request in order to decide if it should be accepted.
+The Service Provider could for example verify if a relationship with the identity already exists or if the e-mail address is already registered.
 
 The system architecture sends a relationship response to the REST interface of the connector.
-The response contains all information of the received relationship request with optional additional information the service provider might want to share now.
-This could for example be the name of the newsletter the service provider decided to select for the user based on his specified interests.
+The response contains all information of the received relationship request with optional additional information the Service Provider might want to share now.
+This could for example be the name of the newsletter the Service Provider decided to select for the user based on his specified interests.
 
@@
 
-After receiving the final "relationship established" notification, the system architecture of the service provider can store the shared attributes in a database along with the corresponding relationship ID.
+After receiving the final "relationship established" notification, the system architecture of the Service Provider can store the shared attributes in a database along with the corresponding relationship ID.
 
 \subsubsection{Attribute Change}
-This section elaborates the sequence of changing an attribute shared as part of an IMP relationship as shown in figure \ref{imp:attribute_change}.
+This section describes the sequence of changing an attribute shared as part of an IMP relationship as shown in figure \ref{imp:attribute_change}.
 If the user switches to a new e-mail provider, he will need to change the corresponding e-mail attribute shared as part of the relationship to receive the newsletter on his new e-mail address.
@@
 Through the IMP application, the user can view relationships and edit shared attributes.
-After changing an attribute, like for example the e-mail address, the IMP application sends an attribute change request to the IMP server, which forwards it to the IMP connector corresponding to the IMP relationship.
-Trough the REST interface of the IMP connector, the service provider iteratively polls for new messages and eventually receives the attribute change request as response.
-The service provider evaluates whether to accept or reject the request and uses the REST interface of the IMP connector to submit the response.
-The IMP connector sends the response to the IMP server which - if the service provider accepted the request - notifies IMP connector and IMP application of the successful change of attributes.
-The service provider again polls for new messages and eventually receives the attribute change established notification based on which it now updates the stored attributes associated to the relationship.
+After changing an attribute, for example the e-mail address, the IMP application sends an attribute change request to the IMP server, which forwards it to the IMP connector corresponding to the IMP relationship.
+Through the REST interface of the IMP connector, the Service Provider regularly polls for new messages and eventually receives the attribute change request.
+The Service Provider evaluates whether to accept or reject the request and uses the REST interface of the IMP connector to submit the response.
+The IMP connector sends the response to the IMP server which - if the Service Provider accepted the request - notifies IMP connector and IMP application of the successful change of attributes.
+The Service Provider again polls for new messages and eventually receives the attribute change established notification based on which it now updates the stored attributes associated to the relationship.
 When the IMP application receives the attribute change established message, it displays a notification to the user.
@@
 This section elaborates the sequence of sending a mail as part of an IMP relationship as shown in figure \ref{imp:mail}.
-If a user for example has questions about the newsletter, he can send a mail to the service provider as part of the established relationship.
+If a user for example has questions about the newsletter, he can send a mail to the Service Provider as part of the established relationship.
 
@@
 
-Trough the IMP application the user can view relationships and submit mails.
+Through the IMP application the user can view relationships and submit mails.
 Once submitted, the IMP application sends the mail to the IMP server which forwards it to the IMP connector corresponding to the relationship.
-The service provider polls for new messages and eventually receives the mail as response.
-An employee of the service provider can process the email and use the REST interface of the IMP connector to send a response mail to the same relationship.
+The Service Provider polls for new messages and eventually receives the mail as response.
+An employee of the Service Provider can process the email and use the REST interface of the IMP connector to send a response mail to the same relationship.
 The IMP connector sends the mail to the IMP server which forwards it to the IMP application of the IMP identity corresponding to the IMP relationship.
@@
 This section elaborates the sequence of authenticating as part of an IMP relationship as shown in figure \ref{imp:authenticate}.
-If the service provider wants to request confirmation from the user, it can send an authentication request to the corresponding relationship.
+If the Service Provider wants to request confirmation from the user, they can send an authentication request to the corresponding relationship.
 
@@
 The user can accept or reject the request which will result in the corresponding authentication response by the IMP application.
-The response is send to the IMP server which forwards it to the IMP connector corresponding to the IMP relationship.
-The service provider polls for new messages and eventually receives the authentication response.
+The response is sent to the IMP server which forwards it to the IMP connector corresponding to the IMP relationship.
+The Service Provider polls for new messages and eventually receives the authentication response.

### 2021-03-13 chapters/sections/6-online_access_law.tex
Anfang und ende fertig

@@
-This chapter gives an overview of regulations, execution and system architecture regarding the online access law.
+This chapter gives an overview about the Online Access Law regarding its regulations, their implementation and the underlying system architecture.
 
@@
 
-In 2017, the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
+In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
 
-\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.
-As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
+\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.
+As it is not clear which administrative services exactly are included by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
 The OZG requires these services to be digitally available.
@@
 
-\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each member state and each commune must provide an administration portal.
+\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each federal state and each commune must provide an administration portal.
 Portals of communes must be linked to the portal of the corresponding member state.
@@
 
-\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
+\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
 The user profiles must be interoperable for every administration portal of the portal network.
 
-\subsection{Execution}
+\subsection{Implementation of Regulations}
 
-Execution of the OZG can be separated into two projects:
+The implementation of OZG regulations can be separated into two projects: The digitalization and the networking project.
 
-\paragraph{Digitalization}
 Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions.
@@
 A digitized administrative service can be accessed by a user through a website.
-The website is hosted either by the federal republic or a member state and is called "Administration Portal".
+The website is hosted either by the federal republic or a federal state and is called "Administration Portal".
 Access is usually provided through an application form.
 The administrative service can be managed through a user profile which is provided by the federal republic or the member state.
-Management of an administrative service usually includes starting the service by sending in a form, communicating with responsible institutions through the inbox of the profile and receiving a result.
-The user profile can also enable users to upload documents to a data wallet and to save personal information for automatically filling in forms.
+Management of an administrative service usually includes starting the service by sending in a form, communicating with the responsible institutions through the inbox of the profile and receiving a result.
+The user profile can also enable users to upload documents to a datawallet and to save personal information for automatically filling in forms.
 
 Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal.
-In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and yet other by the communes \cite{BMI:Onlinezugangsgesetz}.
+In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and some by the communes \cite{BMI:Onlinezugangsgesetz}.
 
-\paragraph{Networking}
 The networking focuses on connecting governmental systems to make all digitized administrative services available for every user.
@@
 In order to save investments a method called "one for all" is used when hosting administrative services.
-One member state or the federal republic provides access to a service on their administration portal and distributes the requests to the responsible institutions "under the hood".
+One federal state or the federal republic provides access to a service on their administration portal and distributes the requests to the responsible institutions "under the hood".
 As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal.
@@
 
+\subsection{Basic Use Case}
+Each time users apply for administrative services, they have to go through an application process, in the following section summarized as the basic OZG use case.
+
+A user wants to apply for two administrative services: funding under the Federal Training Assistance Act (BAföG) and a drivers license.
+Both administrative services are provided through the "one-for-all" method.
+The federal state Sachsen-Anhalt is responsible for processing BAföG applications on its administration portal and the federal state Hessen is responsible for processing drivers license applications on its administration portal.
+The user has never access OZG services before.
+
+\paragraph{Create User Profile} The user wants to apply for BAföG first and therefore visits an administration portal which informs them, that in order to apply for administrative services, a user profile is required.
+As user profiles are designed to be interoperable, it does not matter through which administration portal the user profile is created.
+
+The user is requested to enter personal information and to specify an authentication method. For authentication for example a username and password combination can be used.
+
+\paragraph{Selection of Administrative Service} Using the search feature of the administration portal, the user enters the search term "bafög" and is presented with a list of administrative services as result.
+The user selects the correct administrative service from the search result and is forwarded to the web page of the service on the administration portal of Sachsen-Anhalt .
+It contains information about the administrative service along with instructions on how to access an interactive application form which is can be hosted on a separate web page.
+
+\paragraph{Login to User Profile} Before being able to apply for administrative services, the user has to login into the user profile on the administration portal.
+Depending on the authentication method used for logging in, a trust level of the current session is determined.
+Only with a high trust level users can apply for a broad selection of administrative services.
+The user has selected an authentication method which results in a high trust level.
+
+\paragraph{Application} On the web page of the administrative portal the user clicks on a "bring me to the application" button and is forwarded to a web page with an interactive form.
+Before the user is forwarded, he has the option to transfer personal information for automatic filling of the form.
+The user decides to accept and is presented with a filled in form.
+After pressing the "submit" button the application is transferred to the responsible institution.
+
+\paragraph{Management of Applications} The user is forwarded back to the administration portal and selects to view all active applications created through the portal.
+Here the user can see the application they just submitted and is able manage it by for example requesting cancellation.
+
+\paragraph{Communication} Through the inbox of the user profile the user is notified about a message regarding the application.
+The institution responsible for processing the application informs the user about receiving the application.
+Eventually the institution finishes processing the application and sends a message to the inbox of the user to inform them about the result.
+This marks the end of the basic OZG use case, however, the user wants to apply for a second administrative service.
+
+\paragraph{Selection of Administrative Service} Using the search feature of the administration portal, the user now enters the search term "drivers license", selects the correct search result and is forwarded to the corresponding web page on the administration portal of Hessen.
+
+\paragraph{Login to User Profile} The same interoperable user profile can be used as on the administration portal of Sachsen-Anhalt, but the user is required to login again.
+
+\paragraph{Application} The application process is designed to be similar for each administration portal, however, as Sachsen-Anhalt and Hessen operate their application processes independently, minor differences exist in for example the design and text of the web pages.
+
+\paragraph{Management of Applications} The user is, again, forwarded back to the administration portal and selects to view all active applications created through the portal.
+The user is only able to see and manage the application for a drivers license.
+As the application for BAföG was created through a the administration portal of Sachsen-Anhalt, it is not accessible through the administration portal of Hessen.
+
+\paragraph{Communication} Through the inbox of the user profile, the responsible institution again sends notifications about the current status and results of the application.
+
 \subsection{System Architecture}
-This subsection first describes the basic use case of the OZG. It then presents the OZG system architecture of a member state capable of executing the basic OZG use case.
-Systems responsible for coordination of OZG execution between member states and the federal republic such as the online gateway are not included.
+This section describes the OZG system architecture of a federal state capable of executing the basic OZG use case.
+References about OZG system architectures of Baden-Württemberg \cite{ozg:bw} and Nordrhein-Westfalen \cite{ozg:nrw} are used.
+The presentation document regarding the administration portal of Baden-Württemberg \cite{ozg:bw_administration_portal} is used as basis for describing the administration portal.
 
-This section combines references from OZG system architectures from Baden-Würrtemberg \cite{ozg:bw} and Nordrhein-Westfalen \cite{ozg:nrw}.
+As shown in figure \ref{ozg:system_overview}, the OZG system architecture is separated into three components and two domains.
+Domains in this context describe the operation of systems they contain in separate physical locations.
+Components in this context describe functionally correlated systems of a system architecture.
 
-\paragraph{Basic Use Case}
-The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}.
-Each process consists of multiple sub-processes.
-When comparing the processes, one can see that some sub-processes occur very often and in similar arrangements.
-Those arrangements can be called the basic use case of OZG services.
-The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:
-
-\begin{enumerate}
-    \item \textbf{Create User Profile}
-
-    The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.
-
-    \item \textbf{Login to User Profile}
-
-    Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal.
-The user has to finish authentication steps, which can consist for example of a username and password.
-Depending on the authentication method, a trust level of the current session is determined.
-With approval from the user, personal information from his profile is provided towards the form-server.
-
-    \item \textbf{Selection of Administrative Service}
-
-    The user visits any administration portal of the portal network and types a search term in the corresponding search field.
-The user is then presented with a list of search results consisting of administrative services.
-If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service.
-This page provides information about the administration service along with instructions on how to access the form for application.
-The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.
-
-    \item \textbf{Filling in Application}
-
-    Personal information from the user profile is used by the form-server to fill as many fields of the form as possible.
-The form with prefilled information is then presented to the user.
-The interactive form can then be modified by the user.
-Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.
-
-    \item \textbf{Submission of Application}
-
-    The user again authenticates for his user profile and authorises the form-server to submit the application.
-The form-server saves the application until he is notified to delete it.
-The form-server submits the application to the administration portal which hosts the administrative service.
-
-    \item \textbf{Reception of Application by Administration Portal}
-
-    The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.
-
-    \item \textbf{Submission of Application to Data-Exchange Platform}
-
-    The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.
-
-    \item \textbf{Management of Applications}
-
-    The administration portal stores active applications and enables the user to manage them.
-
-    \item \textbf{Communication}
-
-    As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.
-Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.
-
-\end{enumerate}
-
-\subsubsection{System Components}
-The system architecture consists of the following system components.
-Each component consists of a list of services it provides either to the user or to other components.
-Components are defined based on strongly connected categories of services \cite{NRW:Umsetzung}:
+The "User Component" directly interacts with users to enable access to administration portals.
+This can be desktop or mobile applications or as in this specific case a web browser.
+The "Administration Portal Component" hosts the administration portal.
+The "User Profile Component" provides interoperable user profiles.
+The "Integration Component" transfers filled in applications to responsible institutions.
+And finally, the "Institution Component" receives and processes applications.
 
@@
 
-\paragraph{Administration Portal}
-The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components.
-Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server.
-Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
-The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components.
+The administration portal directly interacts with the "User Component" through a web page and provides access to the basic OZG use case by interacting with other components.
+It consists of a web server that is responsible for hosting web pages and a service facade connected to multiple service components.
+Through the service facade, the web server accesses each service component and makes its service available to the "User Component".
+The "User Profile Management" component is capable of interacting with the "User Profile Component" to create new user profiles, retrieve personal information from existing user profiles and process login requests.
+The "User Profile Component" provides conventional user profile based identity management. 
+Through the Federated Identity Management of Interoperable User Accounts in Germany (Föderiertes Identitätsmanagement interoperabler Nutzerkonten in Deutschland - FINK) the "User Profile" component of each federal state is made interoperable.
+The "Search" component can be used to retrieve a list of URLs of administrative services corresponding to a search term.
+It can retrieve URLs of administrative services from all administration portals through the "Online-Gateway".
 
-The service facade provides an interface to the \textbf{responsibility finder}.
-This service component is used to find administrative institutions which are responsible for an application.
-Depending on the type of application and on the home address of the user, different institutions might be responsible.
+The "Online-Gateway" is a system connecting all administration portals and enabling them to exchange information.
+The "Formula Engine" component is accessed by the web server to display interactive forms to the user when applying for selected administrative services.
+The interactive form can be either integrated into the web page of the administrative service or hosted on a separate web page.
+The user can opt in to automatically fill in forms with personal information.
+In that case, after authentication of the user, the "Administration Portal" component retrieves personal information from the "User Profile" component and sends it to the "Formula Engine" before displaying a filled in form to the user.
 
-The service facade provides an interface to the \textbf{process manager}.
-This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.
+The "Application Management" component receives submitted applications by the "Formula Engine" component for further processing.
+Depending on the administration portal and type of application, additional processing steps, that are not part of the use case can take place.
+This includes for example payment processes.
+The component tracks the current status of the application which the user can view through the web page of the administration portal.
+It is also capable of terminating the application process if the user requests it.
 
-The service facade provides an interface to the \textbf{search service}.
-This service component creates a list of URLs of administrative services relevant for a specified search term.
-It enables the portal to provide a search functionality of administrative services for the user.
-
-The service facade provides an interface to \textbf{user profile management}.
-This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.
-
-The service facade provides an interface to \textbf{application management}.
-This service component manages applications issued through the administration portal by communicating with the form server.
-The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server.
-Form server and portal communicate about the status and content of the application.
-The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.
-
-\paragraph{Form-Server}
-The from-server provides digital forms associated to administrative services.
-They can be accessed by a user profile through online self-service and submitted as applications to administrative institutions.
-The main services are \cite{dNRW:Standardisierungskonzeptzur}
-
-\begin{itemize}
-    \item \textbf{Retrieval of a digital form}
-
-    There exist many administrative services and depending on the member state or commune, the required layout of the application can be different.
-Therefore, a system called federal information management (Föderales Informationsmanagement: FIM) is used to standardize administrative services.
-FIM consists of three categories of building blocks.
-
-    \textit{Service blocks} contain human readable descriptions about an administrative service.
-
-    \textit{Data field blocks} contain the standardized description of data fields required for the application of administrative services.
-
-    \textit{Process blocks} contain standardized descriptions about the process of an administrative service.
-
-    Relevant for the form-server are data field blocks. A data field block can contain one element of five categories.
-
-    \textit{Data fields} are the "smallest entity" of a data field block and describe one standardized piece of information.
-Depending on the type of information - if it is for example a checkbox or input field - additional metadata is included.
-
-    \textit{Data field groups} consist of multiple data fields and other data field groups, relating to a category of information. A data field group can for example be "person" or "company".
-
-    \textit{Rules} describe all kinds of logical conditions of and between data fields.
-This includes for example the automatic validation of the correctness of an entered value or the activation and deactivation of data fields depending on an entered value.
-
-    \textit{Code lists} are lists of predefined values the user can select. This can for example be a list of all countries.
-
-    \textit{Data field schemata} is the combination of entities from all previously described categories and describes the structure of a form.
-
-    The building blocks are centrally managed by federal republic, member states and communes.
-This simplifies the creation of for example a new form by reusing existing data schema blocks and adding additional required data fields to a new data field schema.
-
-    Each data field block can be uniquely identified through an ID.
-Therefore, if the form-server is provided with a FIM-ID, he can retrieve the corresponding data field block from the central storage.
-
-    \item \textbf{Initiation of application}
-
-    The from-server can be requested to initiate an application using a certain form based on a FIM ID of a data field schemata.
-Along with the request, an identification and authorisation of a user profile has to be passed.
-Additional personal information of the user profile can be passed for automated filling in of the form.
-
-    \item \textbf{Status update}
-
-    The form-server sends updates regarding the current status of the application.
-
-    \item \textbf{Automatic filling in of form}
-
-    If the form server was provided with personal information during the initiation request for an application, it can automatically fill in the form.
-
-    \item \textbf{Presentation of form}
-
-    The form server can host a website where it displays an interactive form. The user can access this website either through an URL or through a web component.
-
-    \item \textbf{Application interruption}
-
-    The application can be interrupted or aborted.
-Interruption may occur if the user stays inactive for a certain period of time while filling in the form.
-The user can also manually interrupt the editing process.
-If the application is interrupted, the form-server stores the unfinished application for a certain amount of time.
-The user can then access the application at a later time.
-
-    If the user decides to cancel editing the form, the application is deleted from the from-server.
-
-    Depending on the actions of the user, the status of the application changes accordingly and the form server sends a status update.
-
-    \item \textbf{Storage of application}
-    The form-server stores applications for a specified period of time if they were interrupted or submitted.
-
-    \item \textbf{Provisioning stored applications}
-
-    If the form server is provided an identification and authorisation of a user, it searches all stored applications which belong to the user and sends back a list of URLs, through which the user can access them.
-
-    \item \textbf{Deletion of stored application}
-
-    If the form server is provided an identification and authorisation of a user and an identification of an application, it can delete the stored application.
-
-    \item \textbf{Manually filling in data fields}
-
-    When the form is presented to the user, it can happen, that not all information could be automatically filled in. In this case, the form can be interactively filled in by the user.
-
-    \item \textbf{Uploading documents}
-
-    The user can add documents as attachments to an application. The documents can either be uploaded from the local machine or the data wallet of the user profile.
-
-    \item \textbf{Submission of application}
-
-    When the user submits the application by for example pressing a "submit" button, the form-server sends a status update. The finished application can now be transmitted to a requesting system.
-
-\end{itemize}
-
-\paragraph{User Profile}
-Each member state provides its own user profile for identity management. The main services are \cite{NRW:Umsetzung}:
-
-\begin{itemize}
-    \item \textbf{Identification and Authentification} \cite{dNRW:Anbindungsleitfaden}
-
-    The user profile can be used for identification by transmitting personal information like name and address after successfully authentification.
-Authentification is the verification of an authentication.
-Users can authenticate for the user profile for example through a username / password combination.
-
-    \item \textbf{Determination Trust Level} \cite{dNRW:Anbindungsleitfaden}
-
-    The trust level of a logged in user profile is determined while registration and usage.
-The user can register and login to the user profile using a username / password combination or the German ID card.
-The trust level "High" is only granted if the user registered using the German ID card \textbf{AND} logs in using the German ID card.
-All other combinations of registration and login result in a "normal" trust level.
-
-    \item \textbf{Management Personal Information} \cite{dNRW:Anbindungsleitfaden}
-
-    Personal information of the user profile can be modified.
-This requires the user to authenticate.
-In case the user profile is connected with an online identity card, some attributes like name and age can not be changed.
-
-    \item \textbf{Provisioning Personal Information} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}
-
-    The user profile can be requested to send personal information to a specified URL. This requires the user to authenticate.
-
-\end{itemize}
-
-\paragraph{Institution}
-Institutions are the entities which eventually process the incoming applications and provide the users with solutions.
-They receive a digital application through the data-exchange platform and send back the result as a message through the inbox.
-
-\paragraph{Data-Exchange Platform}
-The data-exchange platform delivers applications from the administration portal to the correct administrative institution.
-
-\paragraph{Data Wallet}
-The data wallet is a sub-component of the user profile and enables the user to manage documents for his user profile. The main services are:
-
-\begin{itemize}
-
-    \item \textbf{Upload of document}
-
-    The user can upload a document from his local machine to the data wallet.
-
-    \item \textbf{Show documents}
-
-    The user can list all documents which are stored in the data wallet.
-
-    \item \textbf{Delete documents}
-
-    The user can delete documents from the data wallet.
-
-    \item \textbf{Attach documents to application}
-
-    The user can attach a copy of a document stored in his data wallet to an application on a form server.
-
-\end{itemize}
-
-\paragraph{Inbox}
-The inbox is a sub-component of the user profile and enables the user to send messages through his user profile. The main services are:
-
-\begin{itemize}
-
-    \item \textbf{Send a message}
-
-    The user can send a message to authorities. This can be for example an institution which processes an application.
-
-    \item \textbf{Receive a message}
-
-    The user can receive messages from authorities for example to update the status of an application.
-
-    \item \textbf{List messages}
-
-    The user can see the messages he received by logging in to his user profile on the administration portal.
-
-    \item \textbf{Notification through E-Mail}
-
-    The user can be notified of a new message through e-mail.
-
-\end{itemize}
-
-\subsubsection{Interfaces}
-In order to implement the basic use case, the components have to interact with each other.
-The following diagram visualizes, which components interact.
-Each interaction is described afterwards.
-The arrows describe the main direction of information flow in an interaction.
-
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Interaction Diagram.pdf}
-\end{center}
-
-\begin{enumerate}
-
-    \item The web browser of the user displays the web pages hosted by the administration portal.
-
-    \item The form-server can initiate the application if requested by the administration portal.
-The portal submits information for identification, authentication and authorisation of a user through a JSON Web Token and a user profile ID.
-In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata.
-In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.
-
-    \item The form server provides the user a web page which displays an interactive form.
-
-    \item The form server notifies the administration portal of changes in the status of applications.
-If the administration portal is notified of a submitted application, it requests the form server to transmit the application data.
-
-    \item The administration portal requests the user profile for identification and authentication to login a user on the web page of the portal.
-The portal also requests authorisation from the user profile to for example access certain personal information.
-
-    \item The administration portal enables the user to manage services of the user profile.
-It provides OSS tools for managing attributes stored in the user profile, to send new messages and to manage documents in the data wallet.
-
-    \item The administration platform submits application data to the data exchange platform for delivery to the responsible institution.
-
-    \item The data exchange platform notifies the administration portal of the delivery status of the application data.
-
-    \item The data exchange platform notifies the institution of a new application and enables it to download the corresponding data.
-
-    \item The institution can send messages to the inbox of a user profile to for example request additional documents.
-
-    \item The user can send messages to the institution which for example asked for additional documents.
-
-\end{enumerate}
-
-\subsubsection{Sequence Diagram}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=17cm]{Diagrams/Basic Use Case Sequence Diagram.png}
-\end{figure}
+The "Application Management" component sends information about the application to the "Responsibility Finder" component which returns an identification of the institution responsible for processing the application.
+Along with the institution ID, the "Application Management" component submits the application to the "Data Exchange Platform".
+This component transfers the application data to the institution corresponding to the specified institution ID.
+The institution can register their "Institution System" to automatically receive the application from the "Data Exchange Platform" where it will be processed.
+In addition to that, the "Institution Component" hosts a web page with information about the institution.

### 2021-03-13 chapters/sections/7-messaging.tex
überarbeitungen
Anfang und ende fertig

@@
 This chapter gives a brief overview of what messaging is and how it can be used for system integration purposes.
-It introduces various messaging patterns which will be used by the technological integration of chapter 4 and 5.
+It introduces various messaging patterns which will be used by the technological integration in chapter 4 and 5.
 The content of this chapter is based on the book \textit{Enterprise Integration Patterns} by \textcite{EIP}.
-
-\subsection{Messaging}
 
@@
 
-Channels can be seen as a collection or array of messages, accessible to interested systems.
-Channels have a direction in a sense, that no system simultaneously writes to and reads from a channel.
+Channels can be seen as a queue of messages, accessible to interested systems.
+Channels have a direction in a sense so that no system simultaneously writes to and reads from a channel.
 Therefore, by one system writing messages to a channel and another system reading them, a message and data flow can be established.
@@
 31]{EIP}.
-Configuring a messaging system involves definition of available channels, the type of messages they exchange, their connection between systems, the message flow and where necessary the insertion of routing and transformation components.
+Configuring a messaging system involves definition of available channels, the type of messages they exchange, their connection between systems, the message flow and when necessary the insertion of routing and transformation components.
 
@@
 This section gives a brief overview of patterns relevant for the thesis and their visual notation.
+Lucidchart \cite{lucid} was used for drawing messaging figures.
 
@@
 Figure \ref{messaging:channel2} shows the visual notation of a named channel.
-Arrows to and from named channels are no notation for channels but for message flow.
-Channels are named if they have a special importance.
+Arrows to and from named channels are not a notation for channels but for message flow.
+Channels are named if they have special importance.
 
@@
 
-Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API.
-The messaging adapter usually has to be developed for each system individually, and manually integrated into the code of the system trough asynchronous function calls of the adapter API.
+Systems that do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API.
+The messaging adapter usually has to be developed individually for each system, and manually integrated into the code of the system through asynchronous function calls of the adapter API.
 
-Figure \ref{messaging:adapter} shows the visual notation of a messaging adapter connected to a system.
+Figure \ref{messaging:adapter} shows the visual notation of a Messaging Adapter connected to a system.
 
@@
 
-Content based routers contain a preconfigured set of routing rules, which instruct the router to place inbound messages on different outbound channels, depending on their content.
-The definition of the rules does not change during operation of the system.
+Content-Based Routers contain a preconfigured set of routing rules, that instruct the router to place inbound messages on different outbound channels depending on their content.
+These rules do not change during operation of the system.
 
-Figure \ref{messaging:router} shows the visual notation of a message router.
+Figure \ref{messaging:router} shows the visual notation of a Message Router.
 
@@
 
-Message translators have the purpose of translating message content on data representation and data type layer.
+Message Translators have the purpose of translating message content on data representation and data type layer. 
 On the data representation layer, message translators translate message content for example from an XML format to a JSON format.
@@
 
-Figure \ref{messaging:translator1} shows the visual notation of a message translator.
+Figure \ref{messaging:translator1} shows the visual notation of a Message Translator.
 
@@
 For more information, read \textcite[p.
-355]{EIP}
+355]{EIP}.
 
@@
 
-Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages based on their content.
-The definition of the rules does not change during operation of the system.
+Message Filters contain a preconfigured set of filtering rules that instruct the filter to delete messages based on their content. These rules do not change during operation of the system.
 
-Figure \ref{messaging:filter1} shows the visual notation of a message filter.
+Figure \ref{messaging:filter1} shows the visual notation of a Message Filter.
 
@@
 
-As shown in figure \ref{messaging:filter2}, message filters can, in combination with publish-subscribe channels, be used to separate messages onto individual datatype channels.
+As shown in figure \ref{messaging:filter2}, Message Filters can, in combination with publish-subscribe channels, be used to separate messages onto individual datatype channels.
 
@@
     \includegraphics[scale=0.6]{Diagrams/Messaging/9. Message Filter.pdf}
-    \caption{Message Filter Separating Message Types}
+    \caption{Message Filter separating Message Types}
     \label{messaging:filter2}
@@
 
-Content enricher have the purpose of adding new attributes to messages. The content which is usually added is a predetermined set of attributes but with dynamically created values.
+Content Enricher have the purpose of adding new attributes to messages. The content which is usually added is a predetermined set of attributes but with dynamically created values.
 
-Figure \ref{messaging:enricher} shows the visual notation of a content enricher.
+Figure \ref{messaging:enricher} shows the visual notation of a Content Enricher.
 
@@
 
-Figure \ref{messaging:filter3} shows the visual notation of a content filter.
+Figure \ref{messaging:filter3} shows the visual notation of a Content Filter.
 
@@
 
-Message stores have the purpose of storing consumed messages in a database.
+Message Stores have the purpose of storing consumed messages in a database.
 They are also capable of communicating with other messaging patterns for providing access to stored messages.
-Communication between message patterns and message stores is indicated by a dotted arrow.
+Communication between message patterns and Message Stores is indicated by a dotted arrow.
 
-Figure \ref{messaging:store} shows the visual notation of a message store. It also shows the example of a content enricher accessing the message store.
+Figure \ref{messaging:store} shows the visual notation of a Message Store. It also shows the example of a Content Enricher accessing the message store.
 

### 2021-03-13 chapters/sections/8-identity_management.tex
überarbeitungen
Anfang und ende fertig

@@
-This chapter describes issues of user based identity management in general and for the use case of the OZG. It also presents possibilities of how IMP can be utilized to solve mentioned issues.
+This chapter describes issues of user based identity management in general and for the specific use case of the OZG.
+It also presents possibilities of how IMP can be utilized to solve mentioned issues.
 
-\section{OZG Identity Management Issues}
+\section{Identity Management Issues} \label{section:identity_management_issues}
 
@@
 \paragraph{Usability}
-Each service provider has a different platform for management of personal information and identity related interactions.
+Each Service Provider has a different platform for the management of personal information and identity related interactions.
 This can for example be web pages or applications for desktop and smartphone.
@@
 
-To manage personal information stored in each user profile and for example change an e-mail address, users have to access the individual platforms of each service provider.
+To manage personal information stored in each user profile and for example change an e-mail address, users have to access the individual platforms of each Service Provider.
 Depending on the amount of created profiles, this can be a time consuming task.
@@
 
-Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while e-mails are only used to notify the user to check his user profile ("You have unread messages!").
-This is because e-mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content.
-Although service providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.
+Bidirectional identity related interactions like subscribing to a service, canceling a subscription, sending or receiving a security relevant mail often only takes place through a web page where e-mails are only used to notify the user to check his user profile ("You have unread messages!").
+This is because e-mails do not provide a secure way of exchanging information and do not enable advanced interaction capabilities or exchange of structured content.
+Although Service Providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.
 
-Service providers rely on the validity of information stored in the user profile.
-To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show his ID at a local shop.
-As each service provider manages separate user profiles, the user might have to go trough this time consuming process repeatedly.
+Service Providers rely on the validity of information stored in the user profile.
+To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show their ID at a local shop.
+As each Service Provider manages separate user profiles, the user might have to go through this time consuming process repeatedly.
 
-Users are not able to automatically share personal information from one user profile with another (except for some Single-Sign-On cases).
-As a result of that, creating new user profile each time involves entering personal information all over again.
+Users are not able to automatically share personal information from one user profile to another (except for some Single-Sign-On cases).
+As a result of that, creating a new user profile each time involves entering personal information all over again.
 
 In case of the OZG, usability of user profiles across multiple administration portals is limited: Although user profiles are interoperable, administration portals are individually responsible for the application process.
-Applying for different administration services, users might have to visit different administration portals.
-Each of the portals managing the application process separately.
-Active applications are not stored as part of the user profile but remain accessible only trough the respective portals they were created through.
-There does not exist an overview of all active applications amongst all administration portals.
-The user has to go trough each portal to find the application he for example wants to cancel.
+Applying for different administration services, users might have to visit separate administration portals.
+Each of the portals manage the application process differently.
+Active applications are not stored as part of the user profile but remain accessible only through the respective portals they were created through.\\ An overview of all active applications amongst all administration portals does not exist.
+The user has to go through each portal to find the application they for example want to cancel.
 Especially due to the „one for all“ approach, users will have to access dedicated administration portals for certain types of administrative services.
@@
 \paragraph{Data Protection}
-In the past, service providers established a habit of collecting more personal information than necessary for providing their services.
+Before, Service Providers established a habit of collecting more personal information than necessary to provide their services.
 As a response, the "Datenschutz Grundverordnung" - DSGVO (General Data Protection Regulation) was passed.
-Amongst other things, it requires service providers to inform the user about which personal information is processed, what the reason for processing the information is and how it is being processed.
+Amongst other things, it requires Service Providers to inform the user about which personal information is processed, the reason for processing the information and how it is being processed.
 Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage.
 
-As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which service provider processes which personal information.
-Multiple service providers storing sensible information increases the risk of personal information being stolen due to a data breach.
+As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which Service Provider processes which personal information.
+Multiple Service Providers storing sensible information increases the risk of personal information being stolen due to a data breach.
 
@@
 Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it.
-As a result of that, the administration portal has access to all personal information only the institution will eventually need to process.
+As a result of that, the administration portal has access to all personal information that in reality only the institution will eventually need to process.
 In addition, institutions actually do not require user profiles for processing applications.
@@
 
-User profiles are often secured through passwords.
-Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of it being stolen and all user profiles being accessible.
-With the amount of different service providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between service providers.
+User profiles are most commonly secured through passwords.
+Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of them being stolen and all user profiles being accessible.
+With the amount of different Service Providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between Service Providers.
 
-Users also have to rely on the correct operation of the system architecture of the service provider and might not be able to proof failures in the operation of the system.
-If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proofing to the service provider, that he did cancel the subscription.
+Users also have to rely on the correct operation of the system architecture of the Service Provider and might not be able to prove failures in the operation of the system.
+If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proving to the Service Provider, that they did cancel the subscription.
 
-\section{IMP Solution Opportunities}
+\section{IMP Solution Opportunities} \label{section:imp_solution_opportunities}
 
-Identity management provisioning is capable of solving many of the issues described in the previous section.
+Identity Management provisioning is capable of solving many of the issues described in the previous section.
 
@@
 
-The goal of IMP solutions is to replace user profiles with a single IMP identity. Through the IMP client a user can manage his IMP identity and all integrated service providers.
+The goal of IMP solutions is to replace user profiles with a single IMP identity.
+Through the IMP client a user can manage their IMP identity and all connected integrated Service Providers.
+Instead of creating user profiles, the user can establish a relationship between their IMP identity and the Service Provider.
+Depending on the use case, the relationship can be utilized differently.
+Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.
+It also enables the user to update personal information shared with Service Providers through one application.
+As the IMP client also contains an inbox, all notifications sent by each Service Provider can be accessed in the same place.
 
-Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider. Depending on the use case, the relationship can be utilized differently.
+As part of established relationships, IMP client and Service Provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service Providers can send structured data to the IMP client along with the information that it should display as a form.
+Depending on the content of the form and the use case of the Service Provider, the form can for example be a purchase agreement or a survey.
 
-Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.
-
-It also enables the user to update personal information shared with service providers trough one application.
-
-As the IMP client also contains an inbox, all notifications sent by each service provider can be viewed in the same place.
-
-As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can send structured data to the IMP client along with the information that it should be displayed as a form.
-Depending on the content of the form and the use case of the service provider, the form can either be a purchase agreement or a survey.
-
-Assumed, through a secure identification and validation process, the identity management provider makes sure, attributes users store as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls.
+Assuming that, through a secure identification and validation process, the identity management provider has made sure that attributes users store as part of their IMP identity are correct, Service Providers wont require any additional identification steps through for example video calls.
 
@@
 
-IMP puts the user back in control of his personal information.
-As part of the process of establishing a relationship, the service provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed.
-With this information, the user can make an informed decision whether to establish the relationship and the service provider performed his duty to inform the user as required by the DSGVO.
+IMP puts the users back in control of their personal information. \\
+As part of the process of establishing a relationship, the Service Provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed.
+With this information, the user can make an informed decision whether to establish the relationship and the Service Provider performed their duty to inform the user as required by the DSGVO.
 
-As personal information is only shared as part of a relationship and with a specified purpose, the service provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible trough.
-This helps the service provider in processing personal information according to the DSGVO.
+As personal information is only shared as part of a relationship and with a specified purpose, the Service Provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible through.
+This helps the Service Provider in processing personal information according to the DSGVO.
 
-As every relationship along with shared attributes is manageable trough the IMP client, the user wont loose track of which service provider has access to which personal information.
+As every relationship along with shared attributes is manageable through the IMP client, the user wont loose track of which Service Provider has access to what personal information.
 
-The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the service provider processes only a small portion of attributes of IMP identities.
+The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the Service Provider processes only a small portion of attributes of IMP identities.
 
 In case of the OZG system architecture, IMP can be used by the individual institutions to establish relationships with IMP identities of users to retrieve applications for administrative services.
-This could eventually eliminate the need of user profiles.
+This could eventually eliminate the need for user profiles.
 Personal information could be shared with only the responsible institution.
@@
 The IMP client enables users to access their IMP identity and all relationships without the need of remembering a variety of credentials.
-This removes the risk of passwords being stolen.
+This removes the risk of credentials being stolen.
 The IMP client itself can be secured without the need for a password.
-As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validated at any time.
-This enables both user and service provider to provide proof for interactions.
+As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and Service Provider can be validated at any time.
+This enables both user and Service Provider to provide proof for every interactions.
+
+\section{Outcome}

### 2021-03-13 chapters/sections/9-imp_utilization_in_ozg.tex
Anfang und ende fertig

--- 2021-03-04 sections/9-imp_utilization_in_ozg.tex
@@
-This chapter presents an IMP solution which solves issues of OZG identity management described in chapter 3.
-For utilization of IMP services as described by the IMP solution, an integration architecture is presented which enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.
+This chapter presents an IMP solution which solves issues that OZG identity management has, as described in chapter 3.
+For utilization of IMP services as described by the IMP solution, an integration architecture will be presented that enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.
 
@@
 
-The integration takes place on three layers:
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
+    \caption{IMP Layer Diagram}
+    \label{integration1:layer_diagram}
+\end{figure}
 
-\begin{center}
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
-\end{center}
+As shown in figure \ref{integration1:layer_diagram}, the integration takes place on three layers:
 
@@
 The IMP solution is integration on the use case level.
-It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the service provider for improvement of usability, data protection and security.
-It describes which types of relationships the service provider can use in his business scenario, how relationships can be processed, which types of messages can be exchanged trough the relationships, what the purpose of each message can be and how the IMP client can react to different message types.
+It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the Service Provider for improvement of usability, data protection and security.
+Furthermore it describes which types of relationships the Service Provider can use in their business scenario, how relationships can be processed, which types of messages can be exchanged through the relationships, what the purpose of each message can be and how the IMP client can react to different message types.
 
@@
 \paragraph{Technological Integration} 
-The technological integration is integration on the system level.
-It consists of an integration architecture enabling the existing systems of the service provider to utilize the IMP system as described by the IMP solution.
-It is separated into a "Communication Integration Layer" and a "Relationship to Identity Integration Layer".
+The Technological Integration is integration on the system level.
+It consists of an integration architecture enabling the existing systems of the Service Provider to utilize the IMP system as described by the IMP solution.
+The Technological Integration is separated into a "Communication Integration Layer" and a "Relationship to Identity Integration Layer".
 On the "Relationship to Identity Integration Layer" the integration architecture enables the existing systems to create relationship templates and establish relationships.
@@
 
-Focus of the technological integration is to connect with as few existing systems as possible while solving as many integration issues described in section 3.3 as possible.
+Focus of the Technological Integration is to connect with the minimal number systems possibly while solving as many integration issues described in section 3.3 as possible.
 

### 2021-03-13 msc-thesis.tex
textualizing
message chapter started
messaging chapter done
überarbeitung
überarbeitungen
Anfang und ende fertig

@@
                \huge
-               \textbf{Integrating Identity Management Providers based on Online Zugangs Gesetz}
+               \textbf{Integrating Identity Management Providers based on Online Access Law}
           }
@@
 
-\newpage
+Diese Bachelorarbeit stellt Identity Management Provisioning (IMP) als mögliche Lösung von Problemen Benutzerprofil basierter Identitätsmanagementsysteme vor.
+IMP bietet Identitätsmanagement als Service für Benutzer und Dienstanbieter.
+Es ermöglicht Benutzern eine IMP-Identität zu erstellen und diese zu nutzen, um persönliche Informationen und Nachrichten mit mehreren Dienstanbietern auszutauschen.
+
+Damit Dienstanbieter mit bestehenden, auf Benutzerprofilen basierenden, Identitätsmanagementsystemen, IMP nutzen können, ist eine Integration in bestehende Geschäftsprozesse und bestehende Systemarchitekturen erforderlich.
+Es werden zwei IMP-Lösungen vorgestellt, die beschreiben, wie Service-Provider IMP verwenden können.
+Außerdem wird ein Messaging-System für die technologische Integration präsentiert.
+
+Ziel der IMP-Lösungen ist es, Möglichkeiten zu beschreiben, die Benutzerfreundlichkeit, Datenschutz und Sicherheit des Identitätsmanagements durch die Nutzung des IMP-Dienstes erhöhen.
+Basierend auf dem aktuell relevanten Anwendungsfall des Online-Zugangs-Gesetzes (OZG) werden zwei IMP-Lösungen vorgestellt.
+Die erste IMP-Lösung beschreibt eine Möglichkeit, welche Benutzern die Erstellung von Benutzerprofilen, Pflege persönlicher Informationen und Interaktion über eine IMP-Anwendung ermöglicht.
+Dieser Integrationsansatz soll die Benutzerfreundlichkeit erhöhen und gleichzeitig das Risiko, die Komplexität und die Kosten der Integration minimieren.
+Dadurch, dass das auf Benutzerprofilen basierende Identitätsmanagement in Betrieb gelassen wird, bleiben Probleme hinsichtlich des Datenschutzes bestehen.
+Eine zweite IMP-Lösung wird vorgestellt, die den Datenschutz erhöht, indem Benutzerprofile ersetzt werden.
+Stattdessen geben Benutzer persönliche Informationen für einzelne Geschäftsprozesse temporär frei.
+
+Zur Integration von IMP-Lösungen wird ein Messaging-System vorgestellt, das in der Lage ist, IMP in bestehende Systemarchitekturen von Dienstanbietern zu integrieren.
+Neben messaging ermöglicht ein modularer Ansatz, dass die Integrationsarchitektur konfigurierbar und erweiterbar ist, um verschiedene IMP-Lösungen in unterschiedliche Systemarchitekturen zu integrieren.
+Die Fähigkeiten des Messaging-Systems werden durch die Integration der zuvor beschriebenen, grundsätzlich unterschiedlichen, IMP-Lösungen in verschiedene Systemarchitekturen im Kontext des OZG demonstriert.
 
 \chapter*{Abstract}
+
+This bachelor thesis presents Identity Management Provisioning (IMP) as possibility for solving problems of user profile based identity management systems.
+IMP provides identity management as a service to users and Service Providers.
+It enables users to create an IMP identity and use it to share personal information and exchange messages with multiple Service Providers.
+
+In order for Service Providers with existing user profile based identity management systems to utilize IMP, integration into their existing business processes and existing system architectures is necessary.
+Two IMP solutions which describe how Service Providers can utilize IMP and one messaging system for technological integration are presented.
+
+Purpose of IMP solutions is to describe possibilities to increase usability, data protection and security of identity management trough utilization of the IMP service.
+Based on the currently relevant use case of the Online Access Law (Online Zugangs Gesetz - OZG), two IMP solutions are presented.
+
+The first IMP solution describes the possibility of enabling users to create user profiles, maintain personal information and interact trough an IMP application.
+This integration approach is designed to increase usability while minimizing risk, complexity and cost of integration.
+
+As a result of leaving user profile based identity management in operation, problems regarding data protection remain.
+A second IMP solution is presented to increase data protection by replacing user profiles.
+Instead users temporarily share personal information for individual business processes.
+
+For integration of IMP solutions, a messaging system is presented which is capable of integrating IMP into existing system architectures of Service Providers.
+In addition to messaging, a modular approach enables the integration architecture to be configurable and expandable to integrate various IMP solutions into different system architectures.
+
+The capabilities of the messaging system are demonstrated by integrating the previously described, fundamentally different, IMP solutions into different system architectures in the context of the OZG.
 
@@
 \chapter{Introduction}
-
-\section{Context}
-
-\subfile{sections/1-context}
-
-\section{Objective}
-
-\subfile{sections/2-objective}
-
-\section{Structure of Work}
-
-\subfile{sections/3-structure_of_work}
+\subfile{chapters/1-introduction}
 
 \chapter{Background and Related Work}
+\subfile{chapters/2-background_and_related_work}
 
-\section{Terminology}
+\chapter{User Profile Identity Management} \label{chapter:user_profile_identity_management}
+\subfile{chapters/3-ozg_identity_management}
 
-\subfile{sections/4-terminology}
+\chapter{IMP Utilization as Extension}
+\subfile{chapters/4-imp_utilization_in_ozg}
 
-\section{Identity Management Provisioning (IMP)}
+\chapter{IMP Utilization as Replacement}
+\subfile{chapters/5-advanced_utilization}
 
-\subfile{sections/5-imp}
-
-\section{Online Access Law (OZG)}
-
-\subfile{sections/6-online_access_law}
-
-\section{Messaging}
-
-\subfile{sections/7-messaging}
-
-\chapter{OZG Identity Management}
-
-\subfile{sections/8-identity_management}
-
-\chapter{IMP Utilization in OZG}
-
-\subfile{sections/9-imp_utilization_in_ozg}
-
-\chapter{Advanced Utilization}
-
-\subfile{sections/12-advanced_utilization}
-
-\chapter{Solution Evaluation}
-
-\section{Conclusion}
-
-\chapter{Outlook: Advanced IMP Integration}
+\chapter{Conclusion}
+\subfile{chapters/6-conclusion}
 

### 2021-03-13 chapters/2-background_and_related_work.tex
überarbeitungen
Anfang und ende fertig
Einleitung überarbeitet

@@
-This chapter covers three important topics, following chapters rely on.
+This chapter covers three important topics that the following chapters rely on.
+Identity Management Provisioning as approach to solve problems of distributed partial identities is described along with possible services and systems.
+The most important regulations of the Online Access Law as well as its basic use case and resulting system architecture of a federal state are described.
+Messaging is presented as a way of designing technological integration architectures.
+Multiple messaging patterns as well as their visual notation are explained.
 
-Identity Management Provisioning is introduced as a new identity management method. Its features along with system components and important use cases are described.
-
-The Online Access Law is introduced as a currently relevant regulation with special requirements for identity management.
-The most important regulations as well as resulting system architectures for its implementation are described.
-
-Messaging is introduced as a way of designing integration architectures. Multiple messaging patterns as well as their visual notation are described.
-
-\section{Identity Management Provisioning (IMP)}
+\section{Identity Management Provisioning (IMP)} \label{imp}
 \subfile{sections/5-imp}
 
-\section{Online Access Law (OZG)}
+\section{Online Access Law (OZG)} \label{ozg}
 \subfile{sections/6-online_access_law}
 
-\section{Messaging}
+\section{Messaging} \label{messaging}
 \subfile{sections/7-messaging}

### 2021-03-13 chapters/sections/1-context.tex
Einleitung überarbeitet

@@
-Many services, are accessible through the internet.
+Today, many services are accessible through the internet.
 Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns.
@@
 
-In some cases, user profiles are required by Service Providers even if their service could be provided without them.
-Especially in case of small stores, running their individual online shop, user profiles are not necessary for customers to place an order.
+In some cases, user profiles are required by Service Providers even if they are not necessary.
+Especially in case of small stores, running their individual online shops, user profiles are not necessary for customers to place an order.
 Personal information can be shared temporarily until processing of the order is completed and the package delivered.
@@
 
-A method for identity management called Identity Management Provisioning (IMP) is introduced.
-IMP provides identity management as a service to users and Service Providers.
-It enables users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages".
-Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be used in different ways.
-It can be used to create and manage a persistent user profile or to temporarily share personal information for a business process.
+A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG).
+It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services.
+Federal republic and each member state operate their individual user profile systems accessible through their administration portals.
+
+The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals.
+To solve this problem, a solution for making OZG user profiles "interoperable" is in development.
+However, interoperable user profiles can not be accessed by the private sector.
+
+Identity Management Provisioning (IMP) is an approach to identity management which aims to solve problems of distributed partial identities by enabling users to bring their online identities with them, when accessing systems of Service providers.
+It provides identity management as a service to users and Service Providers by enabling users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages".
+Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be utilized in different ways.
+It can for example be used to create and manage a persistent SP user profile or to temporarily share personal information for a business process of a SP.
 IMP messages enable user and Service Provider to securely exchange structured data and depending on the client application which receives and displays the data, design rich user interactions.
+This approach to identity management could be an alternative to user profiles in the private sector and in context of the OZG.
+
+Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to for example access personal information and perform authentication.
+They also play an important role in the design of business processes.
+Therefore, for Service Providers to utilize IMP, integration into existing business processes and existing system architectures is necessary.

### 2021-03-13 chapters/sections/11-technological_integration.tex
Einleitung überarbeitet

@@
-In this section an integration architecture is presented for integration of the IMP system presented in section 2.2 into the existing OZG system architecture presented in section 3.3.
+In this section an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.
 
@@
 
-\subsection{Messaging}
-A messaging approach is used for the technological integration.
-As described in section 2.4, messaging enables the systems to access each others services in a decoupled way.
-This is a useful feature as the integration architecture should be reusable for different system architectures.
-The messaging patterns described in 2.4 also enable the integration architecture to be configured according to changes in the operation of the existing systems.
-The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.
-
 \subsection{Integration Overview}
 
-\begin{figure}[H]
+\begin{figure}[h!]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
     \centering
@@
 
-\begin{figure}[h]
+A messaging approach is used for the technological integration.
+As described in section \ref{messaging}, messaging enables the systems to access each others services in a decoupled way.
+This is a useful feature as the integration architecture should be reusable for different system architectures.
+The messaging patterns described in section \ref{messaging} also enable the integration architecture to be configured according to changes in the operation of the existing systems.
+The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.
+
+\begin{figure}[h!]
     \centering
@@
 
-On the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
+As shown in figure \ref{integration1:messaging_integration}, on the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
 The adapters communicate with the messaging system through channels.
@@
 
-The figure gives an overview of the messaging system which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.
+Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system which will be discussed in detail in the following sections.
+The figure contains all channels and messaging modules along with their connectivity.
 
 As introduced in the beginning of this chapter, the technological integration can be separated into two layers: The "Relationship to Identity Integration Layer" and the "Communication Integration Layer" which it is built upon.
-As described in section 2.2, communication between IMP identity and Service Provider is only possible through an established relationship.
+As described in section \ref{imp}, communication between IMP identity and Service Provider is only possible through an established relationship.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
     \centering
@@
 For the messaging system to process messages being exchanged as part of relationships, message modules can be added.
-Their purpose is to map messages of certain types onto the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them.
+Their purpose is to map messages of certain types from the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them.
 They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.
@@
 Corresponding to that, two data type channels exist.
-As based on the channel, a message is placed, its message type can be inferred, content filters remove the message type attributes.
+As the type of a message can be inferred from the channel it is placed on, content filters can remove the message type attributes.
 

### 2021-03-13 chapters/sections/14-technological_integration.tex
Einleitung überarbeitet

@@
 
-Focus of the technological integration is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
+Focus of the technological integration is to use the messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
 The layout of the messaging system should not change and the purpose of each module should stay the same.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 
-To implement the IMP solution, a connector is included in the existing system architecture of each institution as well as the messaging system described in section 4.2.
+As shown in figure \ref{integration2:integration_overview}, to implement the IMP solution, a connector as well as the messaging system described in section 4.2 is included in the existing system architecture of each institution.
 Instead of the web server and service facade in the portal domain, the messaging system is connected to the web server and institution system of the institution domain.
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 On the "Relationship to Identity Integration Layer", modules exist for establishing the different types of application relationships.
-For simplification, modules only for an "Application A" are shown.
-Besides the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
+For simplification, modules only for an exemplary application process "Application A" are shown.
+Although the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
 As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately.

### 2021-03-13 chapters/sections/2-objective.tex
Einleitung überarbeitet

--- 2021-03-06 chapters/sections/2-objective.tex
@@
-Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.
+The bachelor thesis uses the scenario of the OZG as a small scale model for the general problem of distributed partial identities.
+Focus is the utilization and system integration of IMP for Service Providers with existing user profile based system architectures.
+A federal state, in context of the OZG, is used as an example for a Service Provider.
 
-In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
+One objective of the bachelor thesis is to examine problems of user profile based identity management and interoperable OZG user profiles and describe to what extend IMP as an approach can be a solution.
 
-Two solutions for IMP integration and one message based IMPS integration architecture are presented.
+Another objective of the bachelor thesis is to design "IMP solutions" which describe possibilities of how IMP services and tools can be concretely utilized on the example of - but not limited to - the OZG use case.
+IMP solutions demonstrate how IMP relationships and IMP messages can be utilized by users and Service Providers to share personal information and interact in order to solve problems of distributed partial identities related to usability, data protection and security.
 
-The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management.
-In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them.
-This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.
+Using OZG as an example, another objective of the bachelor thesis is to design a technological integration architecture for integration of IMP solutions into existing system architectures of Service Providers.
+Its integration capabilities, however, can not be limited to one IMP solution and one system architecture.
+On the contrary, it has to be capable of integrating various IMP solutions into different system architectures.
+The integration system therefore has to be configurable and expandable according to requirements of new IMP solutions and system architectures.
+To demonstrate the capabilities of the integration architecture in theory, IMP solutions presented as part of the thesis, have to be integrated into different system architectures in the context of the OZG.
 
-In the second solution, IMP is used as an alternative way for identity management without user profiles.
-This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.
-
-The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers.
-This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.
+IMP solutions and integration architecture presented in the bachelor thesis must not be tightly fitted to the scenario of the OZG but have to also be utilizable by Service Providers in other contexts.

### 2021-03-13 chapters/sections/3-structure_of_work.tex
Einleitung überarbeitet

--- 2021-03-06 chapters/sections/3-structure_of_work.tex
@@
-In the chapter "Background and Related Work" important topics, following chapters rely on are covered.
-In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well ass possible solutions trough IMP.
-In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.
-In the chapter "Replacing IMP Utilization" the second IMP solution is presented as well as its integration through the IMPS integration architecture.
-In the chapter "Conclusion" the most important results of the thesis are summarized and possible future developments and contributions are discussed.
+The chapter "Background and Related Work" covers important topics that following chapters rely on. 
+The chapter "User Profile Identity Management" describes disadvantages of user profile based identity management in general as well as in context of the OZG.
+Possible solutions through IMP are described.
+The chapter "IMP Utilization as Extension" presents the first IMP solution as well as its integration through the technological integration architecture.
+The chapter "IMP Utilization as Replacement" presents the second IMP solution as well as its integration through the technological integration architecture.
+The chapter "Conclusion" summarizes the most important results of the thesis and mentions possible future developments and contributions.

### 2021-03-13 chapters/sections/6-online_access_law.tex
Einleitung überarbeitet

@@
-This chapter gives an overview about the Online Access Law regarding its regulations, their implementation and the underlying system architecture.
+This chapter gives an overview about the Online Access Law regarding its regulations, their implementation, the basic OZG use case and the underlying system architecture.
 
@@
 \paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.
-As it is not clear which administrative services exactly are included by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}.
+As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{BMI:Verwaltungsleistungen}.
 The OZG requires these services to be digitally available.
@@
 
-Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions.
-The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:
-
-A digitized administrative service can be accessed by a user through a website.
+The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way: A digitized administrative service can be accessed by a user through a website.
 The website is hosted either by the federal republic or a federal state and is called "Administration Portal".
@@
 As shown in figure \ref{ozg:system_overview}, the OZG system architecture is separated into three components and two domains.
-Domains in this context describe the operation of systems they contain in separate physical locations.
-Components in this context describe functionally correlated systems of a system architecture.
+Domains in this case separate systems in regard to the physical location where they operate.
+Components in this case describe functionally correlated systems of a system architecture.
 

### 2021-03-14 chapters/sections/1-context.tex
backup

@@
 Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns.
+Even after lockdowns, customers might continue to favour e-commerce \cite{9076858}.
 Online Service Providers (SP) often require customers to create user profiles in order to access their services.
@@
 A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG).
-It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services.
-Federal republic and each member state operate their individual user profile systems accessible through their administration portals.
+It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services \cite{ozg:general}.
+Federal republic and each member state operate their individual user profile systems accessible through their administration portals \cite{ozg:user_profiles_general}.
 
 The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals.
-To solve this problem, a solution for making OZG user profiles "interoperable" is in development.
+To solve this problem, a solution for making OZG user profiles "interoperable" is in development \cite{ozg:user_profiles_general}.
 However, interoperable user profiles can not be accessed by the private sector.

### 2021-03-14 chapters/sections/6-online_access_law.tex
backup

@@
 
-In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
+In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{ozg:regulations}:
 
 \paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.
-As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{BMI:Verwaltungsleistungen}.
+As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{ozg:informationsplattform}.
 The OZG requires these services to be digitally available.
-As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
+As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{ozg:maturity_model}.
 
@@
 Portals of federal republic and member states must be connected through a portal network.
-\cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.
+\cite{ozg:onlinegateway_general} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{ozg:onlinegateway_architecture}.
 
-\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}.
-The user profiles must be interoperable for every administration portal of the portal network.
+\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services.
+The user profiles must be interoperable for every administration portal of the portal network \cite{ozg:user_profiles_general}.
 

### 2021-03-26 chapters/2-background_and_related_work.tex
finished

@@
 This chapter covers three important topics that the following chapters rely on.
-Identity Management Provisioning as approach to solve problems of distributed partial identities is described along with possible services and systems.
-The most important regulations of the Online Access Law as well as its basic use case and resulting system architecture of a federal state are described.
+Identity Management Provisioning as an approach to solve problems of distributed partial identities is described along with possible services and systems.
+The most important regulations of the Online Access Law as well as its basic use case and the resulting system architecture of a federal state are described.
 Messaging is presented as a way of designing technological integration architectures.

### 2021-03-26 chapters/sections/1-context.tex
finished

--- 2021-03-13 chapters/sections/1-context.tex
@@
 Especially during the COVID-19 pandemic, stores had to switch to online trade due to lockdowns.
-Online Service Providers (SP) often require customers to create user profiles in order to access their services.
-Management of personal information as well as interaction and communication between Service Provider and customer are often only possible through a web page or e-mail.
-It is time consuming to maintain even a small amount of user profiles: To change personal information, like an e-mail address, the web page of each Service Provider has to be accessed the correct credentials have to be submitted and the information has to be manually filled in each time.
+Even after lockdowns, customers might continue to favour e-commerce \cite{9076858}.
+Online Service Providers (SP) often require customers to create user profiles to access their services.
+Management of personal information as well as interaction and communication between Service Providers and customers are often only possible through a web page or e-mail.
+It is time consuming to maintain even a small number of user profiles: To change personal information, for example, an e-mail address, the web page of each Service Provider has to be accessed, the correct credentials have to be submitted, and the information has to be manually filled in each time.
 
 In some cases, user profiles are required by Service Providers even if they are not necessary.
-Especially in case of small stores, running their individual online shops, user profiles are not necessary for customers to place an order.
-Personal information can be shared temporarily until processing of the order is completed and the package delivered.
-Some online shops allow users to place orders by temporarily sharing personal information, which however, limits interaction and communication possibilities to insecure e-mail exchange.
+Especially in the case of small stores, running their individual online shops, user profiles are not necessary for customers to place an order.
+Personal information can be shared temporarily until processing of the order is completed and the package is delivered.
+Some online shops allow users to place orders by temporarily sharing personal information, however this limits interaction and communication possibilities to insecure e-mail exchanges.
 
 A currently relevant topic with an interesting approach for identity management is the German Online Access Law (Online Zugangs Gesetz - OZG).
-It requires German federal republic, each federal state and commune to provide administration portals for digital access to administrative services.
-Federal republic and each member state operate their individual user profile systems accessible through their administration portals.
+It requires the German federal republic, each federal state and each commune to provide administration portals for digital access to administrative services \cite{ozg:general}.
+The federal republic and each member state operate their individual user profile systems accessible through their administration portals \cite{ozg:user_profiles_general}.
 
-The Online Access Law therefore constructs a system landscape which demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain and login into multiple user profiles to access administrative services distributed across administration portals.
-To solve this problem, a solution for making OZG user profiles "interoperable" is in development.
+The Online Access Law therefore constructs a system landscape that demonstrates the scenario of distributed partial identities on a small scale while maintaining the same problems as the private sector: Users have to create, maintain, and login into multiple user profiles to access administrative services distributed across administration portals.
+To solve this problem, a new solution for making OZG user profiles "interoperable" is in development \cite{ozg:user_profiles_general}.
 However, interoperable user profiles can not be accessed by the private sector.
 
-Identity Management Provisioning (IMP) is an approach to identity management which aims to solve problems of distributed partial identities by enabling users to bring their online identities with them, when accessing systems of Service providers.
+Identity Management Provisioning (IMP) is an approach to identity management which aims to solve the problems of distributed partial identities by enabling users to bring their online identities with them when accessing the systems of Service Providers.
 It provides identity management as a service to users and Service Providers by enabling users to create and manage a single digital identity and use it to share personal information and interact with multiple Service Providers through "IMP relationships" and "IMP messages".
-Through IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case can be utilized in different ways.
-It can for example be used to create and manage a persistent SP user profile or to temporarily share personal information for a business process of a SP.
-IMP messages enable user and Service Provider to securely exchange structured data and depending on the client application which receives and displays the data, design rich user interactions.
-This approach to identity management could be an alternative to user profiles in the private sector and in context of the OZG.
+With IMP relationships, users and Service Providers have a tool to securely share personal information which, depending on the use case, can be utilized in different ways.
+It can, for example, be used to create and manage a persistent SP user profile or to temporarily share personal information for the business process of a SP.
+IMP messages enable the user and Service Provider to securely exchange structured data and depending on the client application that receives and displays the data, design rich user interactions.
+This approach to identity management could be an alternative to user profiles in the private sector and in the context of the OZG.
 
-Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to for example access personal information and perform authentication.
+Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to, for example, access personal information and perform authentication.
 They also play an important role in the design of business processes.

### 2021-03-26 chapters/sections/10-imp_solution_integration.tex
finished

@@
-The IMP solution presented in this section describes the utilization of IMP relationships with the purpose of creating and maintaining user profiles through the IMP client.
-Message types for attribute synchronization, authentication and communication are defined.
+The IMP solution presented in this section describes the utilization of IMP relationships with the purpose of creating and maintaining OZG user profiles through the IMP client.
+Message types for attribute synchronization, authentication, and communication are defined.
 To not disrupt the operation of the existing system architecture, the IMP solution is designed to not replace user profiles but to provide an additional way of accessing them through IMP.
@@
 \subsection{Relationship Utilization}
-The option of using an existing IMP identity for creation of an OZG user profile is added to the account creation web page of the administration portal.
+The option of using an existing IMP identity for the creation of an OZG user profile is added to the account creation web page of the administration portal.
 An IMP relationship is used for the account creation process.
@@
 The IMP client presents the corresponding relationship template to the user and automatically fills in attributes that the administration portal requests from the user as part of the relationship.
-It is assumed that the IMP system has systems in place for identifying users and validating personal information of corresponding IMP identities.
+It is assumed that the IMP system has systems in place for identifying users and validating the personal information of corresponding IMP identities.
 As a result of that, Service Providers can rely on the validity of shared attributes.
@@
 \subsection{Message Utilization}
-As part of an established relationship, Service Providers and users can securely exchange structured data in form of asynchronous messages.
-Security in this case is defined as that a messages can not be accessed or modified by a third party and are authorized by the corresponding user.
-Based on this secure data exchange capabilities, Service Providers can define various types of messages, each with different purposes and effects on the IMP client.
+As part of an established relationship, Service Providers and users can securely exchange structured data in the form of asynchronous messages.
+Security in this case is defined as that a message can not be accessed or modified by a third party and are authorized by the corresponding user.
+Based on this secure data exchange capability, Service Providers can define various types of messages, each with different purposes and effects on the IMP client.
 This section contains various message types useful for managing the user profile created as a result of an established relationship.
@@
 On the login web page of the administration portal, an option is added to login to a user profile using IMP.
-After entering and submitting the username specified during the profile creation process, administration portal and IMP client exchange authentication messages.
-Through the IMP client, the user will be requested to approve a login attempt along with information about the corresponding relationship, IP address, URL and more.
+After entering and submitting the username specified during the profile creation process, the administration portal and IMP client exchange authentication messages.
+Through the IMP client, the user will be requested to approve a login attempt along with information about the corresponding relationship, IP address, URL, and more.
 
@@
 
-The IMP client is used for management of personal information of the user profile.
-Through the IMP client, the user can send requests for adding, updating or deleting shared attributes.
+The IMP client is used for the management of personal information of the user profile.
+Through the IMP client, the user can send requests for adding, updating, or deleting shared attributes.
 Administration portal and IMP client exchange attribute change request and reply messages.
@@
 
-For simplification purposes, the web page for the management of personal information on the administration portal is expected to be read-only.
+For simplification purposes, the web page for the management of personal information on the administration portal is expected to be read only.
 However, it would also be possible for the portal to send attribute change requests to the IMP client based on the modifications the user performed on the web page.
@@
 
-User profiles are known to the existing system architecture and are an often used identity management solution.
-Many Service Providers, especially in the private sector will want to keep using a profile based identity management approach.
+User profiles are known to the existing system architecture and are often used as an identity management solution.
+Many Service Providers, especially in the private sector, will want to keep using a profile-based identity management approach.
 The IMP solution presents an opportunity of leveraging existing user profile systems while simplifying identity management through IMP.
-In addition to that, the IMP solution is designed, so that it can almost effortlessly be turned on and off, giving Service Providers the freedom of testing the solution.
+In addition to that, the IMP solution is designed so that it can almost effortlessly be turned on and off, giving Service Providers the freedom of testing the solution.
 Service Providers can initially add the IMP solution as an alternative to the conventional user profile identity management solution and after a certain period of time switch to only using the IMP solution.
@@
 The onboarding process is simplified.
-Users don't have to manually fill in a form for the creation of a user profile but are supported by the IMP client.
-As part of established relationships, Service Provider and users are able to directly exchange messages with structured content.
-In addition to interaction capabilities of the IMP client, this enables a variety of interaction scenarios not possible through for example common e-mail clients.
-In this case, scenarios for attribute changes, user profile authentication and communication are made possible.
+Users do not have to manually fill in a form for the creation of a user profile but are supported by the IMP client.
+As part of established relationships, Service Providers and users are able to directly exchange messages with structured content.
+In addition to the interaction capabilities of the IMP client, this enables a variety of interaction scenarios not possible through, for example, common e-mail clients.
+In this case, scenarios for attribute changes, user profile authentication, and communication are made possible.
 
@@
 This helps users in making an informed decision on whether to create the user profile.
-At any time after the onboarding process, users can view the relationship in the IMP client and check which Service Providers process which personal information, why and how.
+At any time after the onboarding process, users can view the relationship with the IMP client and check which Service Providers process which personal information, why, and how.
 This enables users to keep an overview of the distribution of their personal information.
@@
 Security is also increased as a result of this approach.
-Through established relationships, Service Provider and users have the ability to not only directly exchange messages but also to do this securely.
-As a result of that, authentication through the IMP client can replace password based authentication methods.
+Through established relationships, Service Providers and users have the ability to not only directly exchange messages but also to do this securely.
+As a result of that, authentication through the IMP client can replace password-based authentication methods.
 This eliminates the risk of weak or stolen passwords.
 
-In case of the OZG, this IMP solution can eventually replace the need for interoperable user profiles.
-In case each administration portal enables onboarding as described by the IMP solution, regarding usability, the existence of a separation of user profiles can be transparent to the user but regarding data protection, the user profiles are strongly separated:
+In the case of the OZG, this IMP solution can eventually replace the need for interoperable user profiles.
+In case each administration portal enables onboarding as described by the IMP solution, regarding usability, the existence of a separation of user profiles can be transparent to the user, but regarding data protection, the user profiles are strongly separated:
 
 After an effortless onboarding process on multiple administration portals, users are able to manage each profile through the IMP client.
-This enables users to break free access from all user profiles giving the illusion of an interoperable user profile.
-Logging in to a user profile using the IMP client eliminates the need of remembering passwords, furthering the illusion of interoperable user profiles.
-Finally, if for each user profile, the same profile name is selected, the user wont be able to distinguish user profiles most of the time.
+Logging in to a user profile using the IMP client eliminates the need of remembering passwords, giving the illusion of interoperable user profiles.
+Finally, if for each user profile, the same profile name is selected, the user wont be able to distinguish OZG user profiles most of the time.
 
-However in cases where the user requires distinction between user profiles in regard to data protection, the IMP client enables the user to separately view personal information shared with each portal and information about how each portal processes it.
+However, in cases where the user requires a distinction between OZG user profiles regarding data protection, the IMP client enables the user to separately view the personal information shared with each portal and information about how each portal processes it.
 
@@
 Most importantly, as a result of integrating the IMP system through user profiles, each administration portal is still required to access personal information.
-In addition to that, application and management of administrative services remains accessible only through the administration portal and form server which presents a discontinuity in accessing OZG services.
+Therefore, the data protection issues described in section \ref{chapter:user_profile_identity_management} remain.
+In addition to that, application and management of administrative services remains accessible only through the administration portal and form server, which presents a discontinuity in accessing OZG services.

### 2021-03-26 chapters/sections/11-technological_integration.tex
finished

@@
-In this section an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.
+In this section, an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.
 
@@
 Purpose of the integration architecture is to enable the existing OZG system to access IMP services according to the previously described IMP solution.
-It therefore has to enable the creation of an onboarding relationship template, the processing of onboarding relationship requests and the processing of established relationships through creation of user profiles.
+It therefore has to enable the creation of an onboarding relationship template, the processing of onboarding relationship requests, and the processing of established relationships through the creation of user profiles.
 \\
 In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution.
-This are messages for attribute changes, communication and authentication.
-As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless translation between the two entities.
-OZG system architecture and IMP systems use different data models, especially in regard to personal information.
+This are messages for attribute change, communication and authentication.
+As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless transition between the two entities.
+OZG system architecture and IMP systems use different data models, especially regarding personal information.
 The integration architecture therefore has to translate between them.
@@
 OZG and the presented IMP solution are only one example of a system architecture and IMP use case.
-The integration architecture should be able to be used in various different scenarios.
-It therefore has to be configurable and expandable in order to meet new requirements.
+The integration architecture should usable in various scenarios.
+It therefore has to be configurable and expandable to meet new requirements.
 
@@
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
-    \caption{Insertion of Integration Systems into OZG System Architecture}
+    \caption{IMP Integration for OZG System Architecture}
     \label{integration1:integration_overview}
@@
 As shown in figure \ref{integration1:integration_overview}, an IMP connector and a messaging system are added to the administration portal for integration.
-Using the messaging system, existing systems of the administration portal and IMP connector can access each others services.
+Using the messaging system, the existing systems of the administration portal and IMP connector can access each others services.
 IMP server and IMP client of the IMP system as described in section \ref{section:imp_system} are also displayed in figure \ref{integration1:integration_overview}.
@@
 All other existing system components remain untouched.
-Through the service facade, the messaging system can integrate services of all connected service components.
+Through the service facade, the messaging system can integrate the services of all connected service components.
 
-\subsection{Onboarding Sequence}
-This section describes the sequence of an application process as visualized in figure \ref{integration1:onboarding_overview}.
+\subsection{Onboarding Process}
+This section describes the process of an application for an administrative service as visualized in figure \ref{integration1:onboarding_overview}.
 
@@
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
-    \caption{Onboarding Overview}
+    \caption{User Profile Onboarding Process}
     \label{integration1:onboarding_overview}
@@
 
-The user should be able to create a new user profile for the OZG system through an existing IMP identity.
+As stated by the IMP solution, the user has to be able to create a new user profile for the OZG system through an existing IMP identity.
 
@@
 The messaging patterns described in section \ref{messaging} also enable the integration architecture to be configured according to changes in the operation of the existing systems.
-The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.
+The asynchronous nature of messaging systems translates well to the asynchronous and message-based operation of the IMP system and IMP solution.
 
@@
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
-    \caption{Messaging Integration}
+    \caption{Messaging System Layout}
     \label{integration1:messaging_integration}
@@
 The main task of the integration system is to translate between the domain of the existing system architecture and the domain of the IMP system.
-None of the existing systems can process IMP relationships but they can process user profiles and vice versa.
+None of the existing systems can process IMP relationships, but they can process user profiles and vice versa.
 
-As shown in figure \ref{integration1:messaging_integration}, on the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
+As shown in figure \ref{integration1:messaging_integration} on the side of the administration portal, messaging adapters provide an API to the existing systems.
+They give access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system.
 The adapters communicate with the messaging system through channels.
 Messages placed on each channel can be simultaneously accessed by multiple systems.
-Using these channels, message adapters can send requests and replies, and receive replies, notifications and requests
+Using these channels, message adapters can send requests and replies, and receive replies, notifications, and requests
 
@@
 Messaging adapters do not communicate directly through channels, but with messaging modules.
-Messaging modules consist of messaging patterns which are able to modify, delete and route messages.
+Messaging modules consist of messaging patterns which are able to modify, delete, and route messages.
 Purpose of the modules is to translate messages sent by messaging adapters of either Service Provider or connector to be understood by the respective recipient.
 Each module is assigned to an individual integration task.
-By adding or removing modules, integration capabilities of the messaging system can be suited to the system architecture of the Service Provider.
+By adding or removing modules, the integration capabilities of the messaging system can be suited to the system architecture of the Service Provider.
 Modules can be designed to provide services to messaging adapters or other modules.
-Designing modules specifically for the usage by other modules helps in distributing integration responsibilities and avoiding a single monolithic integration component.
+Designing modules specifically for usage by other modules helps in distributing integration responsibilities and avoiding a single monolithic integration component.
 
@@
     \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
-    \caption{Messaging System Overview}
+    \caption{Messaging System Detailed Layout}
     \label{integration1:messaging_system_overview}
@@
 
-Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system which will be discussed in detail in the following sections.
+Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system, which will be discussed in detail in the following sections.
 The figure contains all channels and messaging modules along with their connectivity.
@@
 The onboarding template module provides the feature of creating relationship templates for onboarding.
-The onboarding request module, provides the feature of processing and responding to relationship requests.
+The onboarding request module provides the feature of processing and responding to relationship requests.
 And the onboarding relationship module provides the feature of processing established relationships by creating a new user profile.
@@
 In this case, the module maps IDs of relationships to IDs of user profiles.
-Each relationship has a one-to-one relationship to a user profile.
 
-The "Communication Integration Layer" consists of modules, that enable the existing systems to exchange structured data with the IMP client.
+The "Communication Integration Layer" consists of modules that enable the existing systems to exchange structured data with the IMP client.
 Purpose of the modules is to translate between the data models of the Service Provider and the IMP system.
-Most importantly in this case, none of the existing systems is able to understand relationships or relationship IDs.
+Most importantly, in this case, none of the existing systems is able to understand relationships or relationship IDs.
 Therefore, the message mapping module has the purpose of translating all incoming relationship IDs to user profile IDs with the help of the previously mentioned relationship mapping module on the underlying layer.
@@
 Three message modules are included.
-Each of them has the purpose of identifying messages of a certain type and separate them onto individual channels.
+Each of them has the purpose of identifying messages of a certain type and separating them into individual channels.
 This enables the construction of various modules processing the same message types in different ways.
-However, in this case, each message type has only a single module processing it.
-Modules, that eventually process the messages, have the purpose of translating the message content between the data models of Service Provider and IMP system.
-For example the mail module consumes messages which contain a mail received by a user profile.
+Modules that eventually process the messages have the purpose of translating the message content between the data models of Service Provider and IMP system.
+For example, the mail module consumes messages which contain a mail received by a user profile.
 It is very likely that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types.
@@
 
-In this section each messaging module mentioned in the overview of the message architecture is described.
+In this section, each messaging module mentioned in the overview of the message architecture is described.
 
@@
 Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template.
-In this case, the web server will need to notify the user about the successful creation of his user profile.
-The web server therefore adds the user's current session ID as metadata to the template.
+The web server will need to notify the user about the successful creation of his user profile and therefore adds the session ID of the user as metadata to the template.
 
@@
 On each channel connected to a messaging adapter, message translators are attached.
-These translators have the purpose of providing a canonical data model within the module by translating messages on the data representation, data types and data structures layer.
-It might happen, that in the future one of the adapters switches from using for example an XML instead of a JSON data representation.
-Using message translators on each side enables to adapt to these changes by only appropriately configuring the translator while leaving the rest of the module untouched.
+These translators have the purpose of providing a canonical data model within the module by translating messages on the data representation, data type, and data structure layers.
+It might happen that in the future one of the adapters switches from using, for example, an XML instead of a JSON data representation.
+Using message translators on each side enables to adapt to these changes by only configuring the translator while leaving the rest of the module untouched.
 
-In between the message translators the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute.
-This configuration contains information on how the relationship templates of type onboarding are supposed to look like.
-It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more.
+In between the message translators, the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute.
+This configuration contains information on how the relationship templates with type onboarding are supposed to look like.
+It specifies the title of the template, which attributes will be requested from the user, the reason the attributes are requested, and more.
 If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited.
@@
 \\
-Therefore all attributes that are required to create a user profile have to be requested by the template.
+Therefore, all attributes that are required to create a user profile have to be requested by the template.
 In the template, attributes have to be requested according to the data model of the IMP system in order for the IMP client to understand them.
@@
 The messaging adapter of the connector consumes the message and issues the appropriate REST request to the connector.
-After receiving a response from the connector it publishes the resulting template along with the request ID on the "Template Response Channel".
+After receiving a response from the connector, it publishes the resulting template along with the request ID on the "Template Response Channel".
 As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.
@@
 
-Eventually, the user scans the QR code, fills in the attributes and submits a relationship request.
+Eventually, the user scans the QR code, fills in the attributes, and submits a relationship request.
 The request is received by the connector, then forwarded to the messaging adapter and published on the "Relationship Request" channel.
@@
 A message filter only lets messages through that contain templates of type onboarding.
-The message translator connected to the "Onboarding Request" channel translates attributes shared by the user from the IMP data model to the OZG data model.
+The message translator connected to the "Onboarding Request" channel translates the attributes shared by the user from the IMP data model to the OZG data model.
 
@@
 The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships.
-In this case, the module only processes the establishing of relationships, it could however be expanded to also process terminations of relationships.
+In this case, the module only processes the establishing of relationships, it could however be expanded to process the termination of relationships.
 
@@
 To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content.
-After successful creation of the user profile the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.
+After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.
 
@@
 
-Using messaging for this form of database access enables modules to stay unaware of the complexities of the underlying data storage mechanisms.
+Using messaging for this form of database access enables modules to stay unaware of the complexity of the underlying data storage mechanisms.
 An alternative would be for modules to use the database as a shared database.
@@
 Using the previously defined "Relationship Mapping" module, the "Message Mapping" module has the purpose of translating the relationship ID of all inbound messages to the corresponding user profile ID and translating the user profile ID of all outbound messages to the corresponding relationship ID.
-As a result of that, on the left side of the figure \ref{integration1:message_mapping_module}, messages coming from or going to the existing system architecture contain identification of the known user profile entity instead of the unknown relationship entity.
-On the right side, messages coming from or going to the IMP system contain identification of the known relationship instead of the unknown user profile.
+As a result of that, on the left side of the figure \ref{integration1:message_mapping_module}, messages coming from or going to the existing system architecture contain the identification of the known user profile entity instead of the unknown relationship entity.
+On the right side, messages coming from or going to the IMP system contain the identification of the known relationship instead of the unknown user profile.
 
@@
 Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let through by the request ID message filter.
-As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes relationship IDs from the message before publishing it on the "Message Inbound Mapping" channel.
+As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes the relationship IDs from the message before publishing it to the "Message Inbound Mapping" channel.
 
@@
 
-For the messaging system to process messages being exchanged as part of relationships, message modules can be added.
+For the messaging system, to process messages being exchanged as part of relationships, message modules can be added.
 Their purpose is to map messages of certain types from the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them.
-They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.
+They also map messages from the individual message type channels to the "Message Outbound Mapping" channel so that the connector can submit them.
 
@@
 However, the messages are assumed to contain a message type attribute and a message content attribute.
-Based on the message type attribute a message filter can let messages through that contain a message type attribute correlating to an attribute change process.
-Based on the type of a message, a content based message router then copies each message to a datatype channel.
-In this example, messages of type attribute change request and attribute change established are distinguished.
+Based on the message type attribute, a message filter can let messages through that contain a message type attribute correlating to an attribute change process.
+Based on the type of a message, a content-based message router then copies each message to a datatype channel.
+In this example, messages with the type "attribute change request" and "attribute change established" are distinguished.
 Corresponding to that, two data type channels exist.
@@
 Outbound messages related to the attribute change process are consumed in data type channels.
-In this case it is only one "Attribute Change Response" channel.
+In this case, it is only one "Attribute Change Response" channel.
 A Content Enricher adds a message type attribute correlating to the channel the message was placed on.
 This is required in order for the IMP client to properly interpret the message.
-After that the message is published on the "Message Outbound Mapping" channel.
+After that, the message is published on the "Message Outbound Mapping" channel.
 
@@
 
-To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel.
+To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included, which consumes messages from the "Attribute Change Request" channel.
 Messages arriving on the "Attribute Change Request" channel were mapped from a relationship ID to a user profile ID in an earlier integration step.
@@
 Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the Service Provider.
-Therefore the SP is expected to include a "Profile Attribute Change Processor" module, which decides to approve or reject the request based on the user profile ID and the shared attributes.
-The response is published to the "Attribute Change Response" channel and contains the user profile ID additionally to the response.
+Therefore, the SP is expected to include a "Profile Attribute Change Processor" module, which decides to approve or reject the request based on the user profile ID and the shared attributes.
+The response is published on the "Attribute Change Response" channel and contains the user profile ID additionally to the response.
 
@@
 
-If the user did not cancel the attribute change request before the OZG system accepted it, the attribute change is established.
+If the user does not cancel the attribute change request before the OZG system accepts it, the attribute change is established.
 The connector is notified through a message, which eventually is processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.
@@
 A message translator is inserted to translate the message content to the OZG data model.
-This concerns especially the attributes shared as part of the attribute change established message.
+This concerns especially the attributes shared as part of the "attribute change established" message.
 
@@
 
-Before publishing messages on the "Message Outbound Mapping" channel, a Content Enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it.
+Before publishing messages on the "Message Outbound Mapping" channel, a Content Enricher adds the implicit message type of the channel as an attribute in order for the IMP client to understand it.
 
@@
 If the user creates a user profile using their IMP identity, it is possible to replace password authentication with an authentication through the IMP client.
-It is also possible to use the IMP client for two factor authentication.
+It is also possible to use the IMP client for two-factor authentication.
 
-In order to send and receive messages related to authentication, similar to previous message modules, an "Authentication Message" module is included which maps incoming messages on the "Message Inbound Mapping" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.
+To send and receive messages related to authentication, similar to previous message modules, an "Authentication Message" module is included, which maps incoming messages on the "Message Inbound Mapping" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.
 
@@
 Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser.
-Similar to previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message" channel.
+Similar to the previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message" channel.
 
 Eventually, the IMP client sends a response as a message, which the "Authentication Message" module publishes on the "Authentication Response" channel.
-Similar to previous modules the Service Provider can use a message filter to process user profile types differently.
+Similar to previous modules, the Service Provider can use a message filter to process user profile types differently.
 After translating the message to the OZG data model, it is published on the "Authenticate Profile Response" channel.
@@
 
-The messaging system and the modular approach make integration architecture expandable and configurable for new integration scenarios.
+The messaging system and the modular approach make the integration architecture expandable and configurable for new integration scenarios.
 Message mapping module and relationship mapping module enable the translation between user profile and relationship.
-Onboarding template, onboarding request and onboarding relationship module enable the definition and utilization of one or more relationship types.
+Onboarding template, onboarding request, and onboarding relationship module enable the definition and utilization of one or more relationship types.
 Message modules enable the definition of message types.
 Message processing modules enable the translation between data models.
-Messaging system enables asynchronous, event based and direct communication between user and Service Provider.
+Messaging system enables asynchronous, event-based, and direct communication between users and Service Providers.
 Assigning special modules to each type of relationship and message type enables the separation of processing depending on differences in processing legitimization.

### 2021-03-26 chapters/sections/13-imp_solution_integration.tex
finished

@@
 The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection.
-The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and administration portals to process personal information.
+The IMP solution described in this chapter puts the institutions in the center of integration to eliminate the need for user profiles and administration portals to process personal information.
 
@@
 Each institution has a predetermined set of administrative services it can process.
-For each administrative service, the institution can create a relationship template, containing the description of the service, the list of attributes required from the user necessary for processing the application and information on how the personal information will be processed:
+For each administrative service, the institution can create a relationship template, containing the description of the service, the list of attributes required from the user necessary for processing the application, and information on how the personal information will be processed:
 
@@
 
-In contrast to relationship templates in the previous IMP solution, these will not have to be dynamically created but only once.
+In contrast to the relationship templates in the previous IMP solution, these will not have to be dynamically created but only once.
 The reason is that in the previous IMP solution templates had to contain personalized information like the session ID.
@@
 Based on the shared attributes, the institution can decide to either accept or reject the application request.
-It might for example verify whether the home address of the user is within the area that it is responsible for.
+It might, for example, verify whether the home address of the user is within the area that it is responsible for.
 
@@
 
-After the administrative service is finished, the relationship can be terminated and the institution looses access to all shared personal information.
+After the administrative service is finished, the relationship can be terminated and the institution loses access to all shared personal information.
 
 However, the administration portal cannot be completely replaced.
-It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address.
-Therefore users visiting any administration portal search for an administrative service and specify their home address.
+It is still required by users for directing them to the correct institution based on the selected administrative service and, for example, their home address.
+Therefore, users visiting any administration portal search for an administrative service and specify their home address.
 The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.
@@
 
-This IMP solution utilizes the same message types as the previous IMP solution, however for a different purpose.
+This IMP solution utilizes the same message types as the previous IMP solution, however, for a different purpose.
 
@@
 As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information.
-Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes.
+Compared to the previous IMP solution, the user does not give general access to personal information for creating a user profile but for individual processes.
 The users can better control whether they agree to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved.
-In case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.
+In the case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.
 
-Using relationships for execution of business processes eliminates the need for Service Providers to operate identity management systems.
+Using relationships for the execution of business processes eliminates the need for Service Providers to operate identity management systems.
 It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution.
@@
 
-The IMP solution enables users to share personal information directly with responsible institutions, restricting access to for example administration portals.
+The IMP solution enables users to share personal information directly with responsible institutions, restricting access to, for example, administration portals.
 It also enables direct and secure exchange of messages.

### 2021-03-26 chapters/sections/14-technological_integration.tex
finished

@@
-This section describes how the messaging system described as part of the previous chapter can be reused for the IMP solution described in this chapter.
+This section presents how the messaging system described as part of the previous chapter can be reused for the IMP solution of this chapter.
 
@@
 
-Focus of the technological integration is to use the messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
+The focus of the technological integration is to use the messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions.
 The layout of the messaging system should not change and the purpose of each module should stay the same.
-In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.
+To adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \centering
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
-    \caption{Service Application Overview}
-    \label{integration2:application_overview}
-\end{figure}
-
-Institutions are able to process a predetermined set of administrative services. For each service, the institution can create a relationship template once and store it as QR code on their web page.
-
-Users visiting an administration portal can select an administrative service, specify their home address and be forwarded to the web page of the respective institution.
-After scanning the appropriate QR code with the IMP client, the user can fill in the requested attributes and send the relationship request.
-After the relationship is established, the institution is notified and starts processing the application utilizing the shared attributes.
-
-\begin{figure}[h]
-    \centering
     \includegraphics[scale=0.45]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
@@
 
-The layout of the messaging system is identical to the one presented in section 4.2.
-Exactly the same type of messages are exchanged with however a slightly different purpose and content.
-Therefore, in this and the following sections, only important differences between the operation of the messaging system will be described.
+As shown in figure \ref{integration2:messaging_overview}, the layout of the messaging system is identical to the one presented in section 4.2.
+The same type of messages are exchanged with a slightly different purpose and content.
+Therefore, in this and the following sections, only the important differences between the operation of the messaging system will be detailed.
 
-On the "Relationship to Identity Integration Layer", modules exist for establishing the different types of application relationships.
-For simplification, modules only for an exemplary application process "Application A" are shown.
-Although the content and purpose of relationships in this case are different to the relationships of chapter 4, they are processed exactly the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
+On the "Relationship to Identity Integration Layer" modules exist for establishing different types of application relationships.
+For simplification, only modules for an exemplary application process "Application A" are shown.
+Although the content and purpose of the relationships in this case are different to the relationships of chapter 4, they are processed the same: each type of relationship request is processed by an individual application request module and each type of established relationship is processed by an individual application relationship module.
 As the purpose of relationships in this case are applications for administrative services, each module has to be configured appropriately.
 For an established relationship, instead of issuing the existing system architecture to create a user profile, the application relationship module issues the existing system architecture to process an application based on the attributes shared as part of the relationship.
-And instead of a user profile ID, the existing system architecture responds with an application process ID.
-This application process ID is used in the same way as the user profile ID in section 4.2.
+Moreover, instead of a user profile ID, the existing system architecture responds with an application process ID.
+This application process ID is used in the same way the user profile ID is utilized in section 4.2.
 Through the "New Relationship Mapping" channel, it is sent to the relationship mapping module, which maps each relationship to an application process and vice versa.
 
-On the "Communication Integration Layer", the same types of messages are exchanged.
-However instead of user profile IDs, relationship IDs are mapped to application process IDs.
-In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs in order to for example distinguish an enterprise profile from the profile of a private person.
+On the "Communication Integration Layer" the same types of messages are exchanged.
+However, instead of user profile IDs, relationship IDs are mapped to application process IDs.
+In chapter 4, each module connected to the messaging adapter of the institution system was designed to be able to distinguish between different types of user profile IDs to, for example, distinguish an enterprise profile from the profile of a private person.
+\\
 In this case, modules can distinguish between different application types based on the application process ID.
 
+\subsection{Application Process}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
+    \caption{Administrative Service Application Overview}
+    \label{integration2:application_overview}
+\end{figure}
+This section describes the process of applying for an administrative service as shown in figure \ref{integration2:application_overview}.
+Institutions are able to process a predetermined set of administrative services. For each service, the institution can create a relationship template once and store it as QR code on their web page. 
+Users visiting an administration portal can select an administrative service, specify their home address, and be forwarded to the web page of the respective institution.
+After scanning the appropriate QR code with the IMP client, the user can fill in the requested attributes and send the relationship request.
+After the relationship is established, the institution is notified and starts processing the application utilizing the shared attributes.
+
 \subsection{Messaging Modules}
+
+In this section, each messaging module mentioned in the overview of the message architecture is described.
 
@@
 
-Relationship templates are created manually and stored as a QR-code image on the web page of the institution.
-For each application type, a separate application template module can be included which stores the configuration for the template type and issues the connector to create new relationship templates.
-Instead of the web page, the institution system is connected, as application templates are not dynamically created for user requests but once by an employee of the institution.
-Each time the content of an application template has to be changed, the institution creates a new one through this module.
+Relationship templates are created manually and stored as a QR-code on the web page of the institution.
+For each application type, a separate application template module can be included, which stores the configuration for the template type and issues the connector to create new relationship templates.
+Instead of the web page, the institution system itself is connected, as application templates are not dynamically created for user requests but only once by an employee of the institution.
+Each time the content of an application template has to be changed, the institution creates a new one with this module.
 
@@
 Depending on the type of application, different requirements regarding the acceptance of application requests exist.
-A request processing module might for example check if the home address of the user is within the are of responsibility of the institution.
-Only after the relationship and therefore the application request is accepted the application will be processed.
+A request processing module might, for example, check if the home address of the user is within the area of responsibility of the institution.
+Only after the relationship and therefore the application request is accepted, the application will be processed.
 
@@
 
-For each type of application relationship a different application relationship module is used for processing established relationships.
+For each type of application relationship, a different application relationship module is used for processing the established relationships.
 The institution system is notified of an accepted application through the "Process Application Request" channel.
-As part of the existing system architecture, institution systems received applications through the data exchange platform as an application document.
-In order to adhere to this standard, the message translator connected to the "Process Application Request" channel translates the relationship content into the application format of documents delivered through the data exchange platform.
-As explained in section 2.3.2, form servers create the application documents based on a standard defined by FIM.
+As part of the existing system architecture, institution systems receive applications through the data exchange platform as an application document.
+To adhere to this standard, the message translator connected to the "Process Application Request" channel translates the relationship content into the application format of documents delivered through the data exchange platform.
 
@@
 After starting the application process, the institution responds through the messaging adapter with the process ID on the "Application Process Reference Response" channel.
-This process ID is then published on the "New Relationship Mapping" channel.
-The result is, that in contrast to the messaging system of chapter 4, relationships are not mapped to user profiles but to application processes.
+This process ID is then published to the "New Relationship Mapping" channel.
+In contrast to the messaging system of chapter 4, the relationships in this case are not mapped to user profiles but to application processes.
 
@@
 
-As an example for a message type processed on the "Communication Integration Layer", the application attribute change messages are selected.
+As an example, for a message type processed on the "Communication Integration Layer", the application attribute change messages are selected.
 
-In the same way as in chapter 4, attribute change message types are published on individual channels, this time however, instead of a user profile ID, they contain a process ID.
-As described on the example of different user profile ID types in chapter 4, different process ID types may exist in this case too.
+Similar to the process in chapter 4, attribute change message types are published on individual channels, this time however, instead of a user profile ID, they contain a process ID.
+As described in the example of different user profile ID types in chapter 4, different process ID types may exist in this case too.
 For example, an attribute change request for an application of type "A" might be processed differently to an attribute change request for an application of type "B".
 To process different types of attribute change requests separately, multiple application attribute change request modules can be included, each of them filtering for different types of process IDs.
-If it is possible to retrieve the application type from the process ID, processing of each application type could be separated into multiple application change request modules.
-In case application types are not retrievable from process IDs, an additional module can be included, which requests the application type from the institution system based on the process ID.
-An alternative would be for the application relationship module to not only publish the process ID corresponding to a relationship ID on the "New Relationship Mapping" channel but also the application type.
+If it is possible to retrieve the application type from the process ID, the processing of each application type could be separated into multiple application change request modules.
+For the case that application types are not retrievable from process IDs, an additional module can be included, which requests the application type from the institution system based on the process ID.
+An alternative way would be for the application relationship module to not only publish the process ID corresponding to a relationship ID on the "New Relationship Mapping" channel but also the application type.
 
-Only after the attribute change request is accepted, the institution system will be notified about the attribute change.
+Only when the attribute change request is accepted, the institution system will be notified about the attribute change.
 
@@
 Continuing the example of how application attribute change messages are processed on the "Communication Integration Layer", the application attribute sync module processes messages on the "Attribute Change Established" channel.
-With the same reasoning as in the previous section, the message filter attached to the channel enables to include multiple application attribute sync modules, processing different application types.
+With the same reasoning as in the previous section, the message filter attached to the channel enables to include multiple application attribute sync modules, each processing different application types.
 
@@
 
-Similar to the attribute change messages, mail messages can be fitted to the process based scenario, enabling institutions to send mails to a process ID which the messaging system translates to a relationship ID in order for the correct IMP identity to receive it.
-In addition to the one directional message transfer from the institution to the IMP identity, the application mail module and the mail message module could be expanded to be able to receive mails from an IMP identity through an established relationship.
+Similar to attribute change messages, mail messages can be fitted to the process-based scenario, enabling institutions to send mails to a process ID which the messaging system translates to a relationship ID in order for the correct IMP identity to receive it.
+In addition to the one-directional message transfer from the institution to the IMP identity, the application mail module and the mail message module could be expanded to be able to receive mails from an IMP identity through an established relationship.
 The relationship ID of the message would be mapped to the corresponding process ID and submitted to the institution system.
@@
 Authentication messages and modules are not required for this IMP solution, as no user profile and therefore no login process exists.
-However, depending on the use case, authentication messages could be included as an additional accept / reject communication method between institution and user.
+However, depending on the use case, authentication messages could be included as an additional accept / reject communication method between the institution and user.
 
 \subsection{Evaluation}
-The integration architecture enables users to directly interact with the system architecture of the Service Provider for submitting applications.
-This eliminates the need for administration portals to process personal information.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
-    \caption{IMP System Architecture Personal Information}
-    \label{integration2:imp_personal_information}
-\end{figure}
-
-Comparing the existing system architecture of the OZG with the system architecture utilizing IMP, the amount of systems processing personal information is reduced.
-Using this IMP solution, only the user and the responsible institution have access to personal information.
+The integration architecture enables users to directly interact with the system architecture of the Service Provider for submitting applications.
+This eliminates the need for administration portals to process personal information.
+As shown in figure \ref{integration2:ozg_personal_information}, every component and every domain of the existing OZG system architecture processes personal information.
+Using the IMP solution presented in this chapter, only the user and the responsible institution have access to personal information, which improves data protection.
 
 The integration architecture described in section 4.2 was able to integrate into two different system architectures.
-This demonstrates, that the presented integration architecture is applicable to a variety of system architectures.
-
-It was also able to integrate a user oriented (persistent) relationship scenario as well as a process oriented (temporary) relationship scenario.
+This demonstrates that the presented integration architecture is applicable to a variety of system architectures.
+In addition, it was able to integrate a user-oriented (persistent) relationship scenario as well as a process-oriented (temporary) relationship scenario.
 This demonstrates that the presented integration architecture can be used for integrating a variety of IMP solutions.
-
-The modular message based approach made it possible to use the integration architecture in a different scenarios, by enabling easy configuration of modules for new requirements.
+The modular message-based approach makes it possible to use the integration architecture in different scenarios by enabling easy configuration of modules for new requirements.

### 2021-03-26 chapters/sections/15-conclusion.tex
Einleitung überarbeitet
finished

--- 2021-03-06 chapters/sections/15-conclusion.tex
@@
-Finally, this chapter aims to summarize the most important results of the thesis and give an outlook on possible future developments and contributions.
+Finally, this chapter summarizes the most important results of this thesis and gives an outlook on possible future developments and contributions.
 
@@
 
-\begin{itemize}
-    \item Purpose of the thesis is to design integration solutions for identity management provisioning systems on the example of OZG.
-    \item The integration is separated into a business scenario integration trough an IMP solution and a system integration trough a messaging system.
-    \item Trough two IMP solutions, it was shown, how IMP can be utilized in different identity management scenarios
-    \item In the first scenario, an IMP solution was presented which focused on enhancing usability of 
-    \item The thesis introduced identity management provisioning as an identity management service capable of replacing conventional user profiles
-    \item On the example of the OZG, the thesis showed 
-\end{itemize}
+The bachelor thesis uses the scenario of the OZG as a small-scale model for the general problem of distributed partial identities.
+Focus is the utilization and system integration of IMP for Service Providers with existing user profile-based system architectures.
+
+The first objective of the bachelor thesis is to examine the problems of user profile-based identity management and interoperable OZG user profiles and to describe to what extent IMP can be a solution.
+In chapter \ref{chapter:user_profile_identity_management} the thesis describes multiple problems of user profile-based identity management regarding usability, data protection and security.
+They lack usability as they lead to fragmentation into partial identities, accessible only through separate applications and web pages.
+Data protection is reduced due to the lack of oversight for the user about existing user profiles and shared personal information.
+The distribution of personal information to various Service Providers increases the risk of data being stolen.
+Especially in the case of the OZG, issues regarding data protection exist: \\
+As a result of the "one-for-all" method, access to administrative services is distributed across multiple administration portals.
+Users applying for services therefore have to share large quantities of personal information with the administration portals of multiple federal states.
+As it is the institutions and not the administration portals that eventually process the personal information, sharing personal information directly with institutions would be favourable regarding data minimisation.
+\\
+Possibilities for solving the mentioned problems through IMP are presented.
+IMP enables to increase usability by enabling users to interact, manage, and share personal information with Service Providers through only one application.
+Data protection is increased, as users can keep an overview of shared personal information.
+Security is improved, as IMP provides secure communication channels.
+In the case of the OZG, IMP is a possibility to increase usability and even eliminate the need for administration portals to process personal information, favouring data minimization.
+Based on the mentioned problems and solutions, the chapter concludes that IMP can be taken into consideration for solving problems of fragmented partial identities.
+
+The bachelor thesis therefore moves to the second objective to design "IMP solutions" which describe the possibilities of how IMP services and tools can be specifically utilized on the example of - but not limited to - the OZG use case.
+The thesis presents two solutions for IMP utilization for Service Providers with existing user profile-based identity management.
+The first solution utilizes IMP in addition to existing user profiles.
+It provides an optional way for users to create and manage OZG user profiles through an IMP client.
+\\
+This is done by enabling users to create new user profiles through existing IMP identities by establishing an IMP relationship.
+By exchanging IMP messages, users are able to access and manage their user profile.
+The IMP solution especially improves usability as OZG user profiles can be managed along with many other user profiles of other Service Providers through the same IMP client.
+The solution requires integration only with the administration portal component and can operate without disrupting the existing operation of the system architecture.
+
+The approach of enhancing accessibility to existing user profiles through an IMP client can be used to replace the need for OZG user profiles to be interoperable.
+Users can effortlessly create, manage, and login to user profiles for each federal state and administration portal.
+In addition to that, not only user profiles in the context of the OZG can be managed through IMP but user profiles of any integrated Service Provider.
+This IMP utilization therefore is a possibility to solve the usability problems of partial identities.
+
+However, this IMP solution does not solve many of the data protection issues, as the user profile-based identity management system remains in operation.
+Therefore, the bachelor thesis presents a second IMP solution, with a focus on data protection.
+
+The second solution utilizes IMP to replace user profiles.
+Instead of persistently sharing personal information with administration portals in the form of user profiles, IMP is used to temporarily share personal information with institutions for the period of time where an application is being processed.
+This is done by enabling users to establish different types of IMP relationships, each corresponding to a different application type.
+This IMP solution especially improves data protection, as only the institution responsible for processing the application receives personal information.
+In addition to that, sharing personal information only for a short period of time decreases the risk of personal information being misused or stolen.
+
+The approach of replacing user profiles with temporary sharing of personal information for individual business processes can be used to eliminate partial identities while increasing data protection.
+However, while this approach might be usable in the context of the OZG, Service Providers in the private sector might not be interested in switching to this fundamentally different approach of identity management.
+Not as a result of technological problems but due to corporate policy reasons ("Never change a running system").
+The advantage of IMP is: users can access Service Providers utilizing either IMP solutions through their IMP application.
+
+The third objective of the bachelor thesis is to design a technological integration architecture for the integration of IMP solutions into existing system architectures of Service Providers.
+The thesis presents a modular messaging system, which enables the integration of IMP solutions into existing system architectures of Service Providers.
+Through the messaging system, the system architecture of the Service Provider can establish multiple types of IMP relationships and define, exchange, and process different message types.
+The messaging system maps relationships to entities that the SP systems understand.
+This can be, for example, the mapping of an IMP relationship to a user profile or to an application process.
+It also translates between the data models of IMP and Service Provider.
+As a result of using messaging and messaging modules, the integration system can be configured and extended to fit the requirements of different IMP solutions and system architectures of Service Providers.
+
+The messaging system is shown, integrating both previously described IMP solutions into different system architectures.
+The first IMP solution was integrated into the administration portal component, the second IMP solution was integrated into the institution domain.
+This demonstrates that the messaging system is capable of integrating different IMP solutions into different system architectures.
 
@@
 
-\begin{itemize}
-    \item experimental evaluation
-    \item 
-\end{itemize}
+The bachelor thesis describes the integration of IMP on a theoretical level.
+Developing a prototype of the messaging system as part of an experimental evaluation can give further information about its feasibility, performance, and stability.
+The prototype can furthermore be used to test integration of the first IMP solution into the OZG system architecture of a federal state, to validate the functionality of the IMP solution and the messaging system, and to find missing features.
+Due to the modular design of the messaging system, new messaging modules implementing missing features can be added.
+
+To make the modular approach of the integration architecture more utilizable for Service Providers, a "Module Store" can be hosted, where enterprises can publish messaging modules for integration of enterprise systems they sell.
+Through an IMP tool, Service Providers could be enabled to generate a custom messaging system with messaging modules for selected systems.
+With "only" configuration of the messaging modules remaining, this could reduce the time required for implementing and deploying the integration architecture.
+
+The thesis presents OZG as a Service Provider relevant for the integration of IMP.
+Identity Management Provisioning, however, is relevant for many other Service Providers.
+For example, in the scope of the National Education Platform, "a digital portal is being created that in the future will support universities as well as national and international students who are seeking a stay abroad, a course of study, or a change of study location in Germany along their educational career through a digital offering that is interoperable across institutions" \cite{digitale_bildung}.
+In accordance with IMP solutions in the thesis, an IMP solution for this new use case can be designed and the presented messaging system can be configured and expanded to suit new requirements and to be used for system integration.

### 2021-03-26 chapters/sections/2-objective.tex
finished

--- 2021-03-06 chapters/sections/2-objective.tex
@@
-Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.
+The bachelor thesis uses the scenario of the OZG as a small-scale model for the general problem of distributed partial identities.
+Focus is the utilization and system integration of IMP for Service Providers with existing user profile-based system architectures.
+A federal state, in the context of the OZG, is used as an example for a Service Provider.
 
-In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.
+One objective of the bachelor thesis is to examine the problems of user profile-based identity management and interoperable OZG user profiles and to describe to what extend IMP as an approach can be a solution.
 
-Two solutions for IMP integration and one message based IMPS integration architecture are presented.
+Another objective of the bachelor thesis is to design "IMP solutions" which describe the possibilities of how IMP services and tools can be concretely utilized on the example of - but not limited to - the OZG use case.
+IMP solutions demonstrate how IMP relationships and IMP messages can be utilized by users and Service Providers to share personal information and interact to solve the problems of distributed partial identities related to usability, data protection, and security.
 
-The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management.
-In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them.
-This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.
+Using OZG as an example, another objective of the bachelor thesis is to design a technological integration architecture for the integration of IMP solutions into existing system architectures of Service Providers.
+Its integration capabilities, however, can not be limited to one IMP solution and one system architecture.
+On the contrary, it has to be capable of integrating various IMP solutions into different system architectures.
+The integration system therefore has to be configurable and expandable according to the requirements of new IMP solutions and system architectures.
+To demonstrate the capabilities of the integration architecture in theory, IMP solutions presented as part of the thesis have to be integrated into different system architectures in the context of the OZG.
 
-In the second solution, IMP is used as an alternative way for identity management without user profiles.
-This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.
-
-The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers.
-This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.
+IMP solutions and integration architecture presented in the bachelor thesis should not be perfectly fitted to the scenario of the OZG but have to also be utilizable by Service Providers in other contexts.

### 2021-03-26 chapters/sections/3-structure_of_work.tex
finished

@@
-The chapter "Background and Related Work" covers important topics that following chapters rely on. 
-The chapter "User Profile Identity Management" describes disadvantages of user profile based identity management in general as well as in context of the OZG.
+The chapter "Background and Related Work" covers important topics that the following chapters rely on. 
+The chapter "User Profile Identity Management" describes the disadvantages of user profile-based identity management in general as well as in the context of the OZG.
 Possible solutions through IMP are described.

### 2021-03-26 chapters/sections/5-imp.tex
Einleitung überarbeitet
finished

@@
-The purpose of this section is to deliver a broad understanding of what Identity Management Provisioning (IMP) is, what an IMP service can look like and how identity management provisioning systems can operate.
+The purpose of this section is to deliver a broad understanding of what Identity Management Provisioning (IMP) is, what an IMP service can look like and how Identity Management Provisioning systems can operate.
 
@@
 Identity Management Provisioning is a method where identity management is provided as a service to users and Service Providers.
-The service enables users to create and manage a digital identity and use it to share personal information and interact with Service Providers.
+This service enables users to create and manage a digital identity and to use it to share personal information and interact with Service Providers.
 
-Many identity management systems currently in use by Service Providers require the user to create a new user profile, specify login credentials and keep the personal Information up to date.
+Many identity management systems currently in use by Service Providers require the user to create a new user profile, specify login credentials, and keep the personal information up to date.
 Every Service Provider operates their own identity management system and users have to access each system individually through multiple websites to use their user profiles.
@@
 
-In contrast to a user profile based identity management approach, IMP provides identity management as a service.
+In contrast to a user profile-based identity management approach, IMP provides identity management as a service.
 Only one identity management provisioning system is hosted and accessed by users and Service Providers.
-Users therefore only need one IMP identity, which is accessed by multiple Service Providers.
-This approach to identity management is capable of solving various issues of user profile based identity management that are discussed in section \ref{section:imp_solution_opportunities}
+Users therefore only need one IMP identity that is accessed by multiple Service Providers.
+This approach to identity management is capable of solving various issues of user profile-based identity management that are discussed in section \ref{section:imp_solution_opportunities}
 
 To access the IMP service, users can use applications or websites.
-Service Providers however often require integration into their existing system architecture to enable existing system components to use the new identity management method.
+Service Providers, however, often require integration into their existing system architecture to enable existing system components to use the new identity management method.
 
@@
 
-Software tools exist for users and Service Provider to access the IMP service. 
+Software tools exist for users and Service Providers to access the IMP service.
 For the user, this is a smartphone application.
-For the Service Provider this is an integration component.
-The smartphone application provides a user friendly graphical interface which enables the user to receive notifications, maintain personal information, share personal information, and more.
+For the Service Provider, this is an integration component.
+The smartphone application provides a user-friendly graphical interface which enables the user to receive notifications, maintain personal information, share personal information, and more.
 The integration component for the Service Provider is a software solution with similar capabilities as the smartphone app but designed towards enterprise use.
@@
 
-One important part of the IMP service is management of personal information by users.
+One important part of the IMP service is the management of personal information by users.
 After installation of the smartphone application, a new identity (IMP identity) can be created.
-As part of this identity, the user can add any amount of key-value pairs as attributes, the list of all attributes making up the personal information of the IMP identity.
-Despite being able to add any key-value pair, there are some commonly used keys like name, age, home address etc.
-Depending on the use case of Service Providers, multiple more keys and their meaning have to be agreed upon.
+As part of this identity, the user can add any number of key-value pairs as attributes, the list of all attributes making up the personal information of the IMP identity.
+Despite being able to add any key-value pair, there are some commonly used keys like name, age, home address, etc.
+Depending on the use case of Service Providers, different keys and their meaning have to be agreed upon.
 This means the IMP service has to define a canonical data model.
@@
 
-Many Service Providers require users to manually verify their identity and personal information by for example visiting a store and showing their ID card.
+Many Service Providers require users to manually verify their identity and personal information by, for example, visiting a store and showing their ID card.
 Similar verification processes are expected to be used by the IMP service to verify IMP identities and their personal information.
-However, for simplification reasons, the details of this verification process are left out .
+However, for simplification reasons, the details of this verification process are left out in this thesis.
 
 Users and Service Providers can establish relationships and use them to share personal information and interact.
-The initial form of a relationship is a relationship template, which is created by the Service Provider and describes what types of relationships they are willing to establish.
+The initial form of a relationship is a relationship template, which is created by the Service Provider and describes what type of relationships they are willing to establish.
 The templates are made available to interested users, which can use them to request relationships.
 
-A Service Provider fill a relationship template with optional and mandatory information:
+A Service Provider can fill a relationship template with optional and mandatory information:
 
@@
 
-\paragraph{Requested Attributes} The Service Provider can list keys of attributes he requires the user to share in order to send a relationship request.
+\paragraph{Requested Attributes} The Service Provider can list the keys of the attributes he requires the user to share to send a relationship request.
 When the user submits a relationship request based on this relationship template, the values filled in for the requested attributes are copied and sent as part of the request.
@@
 
-\paragraph{Shared Attributes} Shared Attributes is a list of key-values pairs that the Service Provider makes available to any user interested in requesting a relationship.
-The Service Provider has to share a minimal amount of attributes that enable the user to identify it.
+\paragraph{Shared Attributes} Shared Attributes is a list of key-value pairs that the Service Provider makes available to any user interested in requesting a relationship.
+The Service Provider has to share a minimal number of attributes that enable the user to identify it.
 
-\paragraph{Purpose} This is a text field where the Service Provider can give a detailed explanation of what the purpose of the relationship is, e.g what effects a relationship request and an established relationship will have.
-The reason for why the requested attributes are necessary for the relationship have to be explained here as well as how each shared attribute is going to be processed.
+\paragraph{Purpose} This is a text field where the Service Provider can give a detailed explanation of what the purpose of the relationship is, e.g, what effects a relationship request and an established relationship will have.
+The reasons for why the requested attributes are necessary for the relationship have to be explained here as well as how each shared attribute is going to be processed.
 This helps the user in making an informed decision on whether to submit the relationship request or not.
 
-\paragraph{Attachments} Attachments can be all kinds of documents and files. For example legal information can be included but also product flyers corresponding to the relationship template, etc.
+\paragraph{Attachments} Attachments can be all kinds of documents and files. For example, legal information can be included but also product flyers corresponding to the relationship template, etc.
 
@@
 
-When the user receives the template through his IMP application, the requested attributes are automatically filled in if they exist for his IMP identity.
-Otherwise they can be filled in manually and added as new attributes of the IMP identity.
+When the user receives the template through his IMP application, the requested attributes are automatically filled in if they exist in his IMP identity.
+Otherwise, they can be filled in manually and added as new attributes of the IMP identity.
 
-At this point it is important to take a look at how IMP identity attributes and shared attributes are separated.
+At this point, it is important to take a look at how IMP identity attributes and shared attributes are separated.
 IMP identity attributes are managed by the user to reflect the most up to date information.
 Attributes shared as part of a relationship can be automatically filled with values from the IMP identity but can also be manually entered.
-This means, shared attributes and IMP identity attributes are not necessarily the same.
+This means shared attributes and IMP identity attributes are not necessarily the same.
 
@@
 If the Service Provider approves the request, the relationship is established and both parties get notified.
-Through the IMP application, the user can see all relationships as well as their status, the content of the underlying relationship template and a list of shared attributes and their values.
+Through the IMP application, the user can see all relationships as well as their status, the content of the underlying relationship template, and a list of shared attributes and their values.
 
-As part of an established relationship, user and Service Provider can interact with each other by asynchronously exchanging structured data packages as IMP messages.
+As part of an established relationship, the user and Service Provider can interact with each other by asynchronously exchanging structured data packages as IMP messages.
 IMP messages can contain any content, however, both IMP application and Service Provider systems should be able to understand the messages.
@@
 Without additional integration systems, the Service Provider has to implement his own solutions for understanding and processing messages.
-The IMP application however, has a set of messages it understands.
+The IMP application, however, has a set of messages it understands.
 The list of messages the application is able to process can be expanded by the identity management provider who develops it.
@@
 
-\paragraph{Mail} Messages of the mail type can be used by Service Provider and user to exchange human readable text.
-Mails sent to an IMP identity are displayed by the IMP application through for example a notification.
-The IMP application defines a format for the content of the mail. The term "mail" is used as an alternative to the term "message", as messages will later be used in context of a messaging system.
+\paragraph{Mail} Messages of the mail type can be used by Service Providers and users to exchange human readable text.
+Mails sent to an IMP identity are displayed by the IMP application through, for example, a notification.
+The IMP application defines a format for the content of the mail. The term "mail" is used as an alternative to the term "message", as messages will later be used in the context of a messaging system.
 
 \paragraph{Attribute Change} Messages of the attribute change type can be used by the user to request the modification of shared attributes.
-The user can modify, add or delete attributes shared as part of a relationship and submit an attribute change request to the Service Provider which contains the changes.
+The user can modify, add, or delete the attributes shared as part of a relationship and submit an attribute change request to the Service Provider which contains the changes.
 The Service Provider can decide to either accept or reject the request and respond with a corresponding attribute change response message.
@@
 
-\paragraph{Authentication} Messages of the authentication type can be used by the Service Provider to request confirmation from the IMP identity for specific business process.
+\paragraph{Authentication} Messages of the authentication type can be used by the Service Provider to request confirmation of the IMP identity for a specific business process.
 The Service Provider sends an initial request message to the IMP identity which contains a description of what confirmation is requested by the user.
@@
 This usually does not include the systems hosting the IMP service.
-Only the owner of an identity can manage attributes of their identity.
+Only the owner of an identity can manage the attributes of their identity.
 A relationship is established only with the identity presented as part of the relationship request and only the specified attributes are shared.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
     \includegraphics[scale=0.6]{Diagrams/IMP System Overview.pdf}
-    \caption{IMP System Overview}
+    \caption{IMP System Domains}
     \label{imp:imp_system_overview}
@@
 The user domain contains systems that the user directly interacts with.
-These typically are applications on PC or smartphone and websites.
-IMP application on smartphones are provided to users for accessing IMP services.
-For simplification, each user is assumed to access the IMP service through one device which eliminates the need for device synchronization.
-As previously described, the IMP application enables the user to manage attributes of their identity, to establish relationships, to manage relationships and to interact with messages through relationships.
+These typically are applications on personal computers, smartphones, and websites.
+IMP applications on smartphones are provided to users for accessing IMP services.
+For simplification, each user is assumed to access the IMP service through one device, which eliminates the need for device synchronization.
+As previously described, the IMP application enables users to manage the attributes of their identity, to establish relationships, to manage relationships, and to exchange messages for interaction.
 
@@
 The IMP server is able to communicate with each IMP application and IMP connector.
-It has the purpose of maintaining a - when necessary encrypted - list of all identities, relationships, relationship templates and IMP messages.
+It has the purpose of maintaining a - when necessary, encrypted - list of all identities, relationships, relationship templates, and IMP messages.
 As the IMP server does not know the private key corresponding to the IMP identity, it is unable to decipher the data.
 The IMP server is also capable of creating relationship templates, processing and routing relationship requests and responses and IMP messages.
-The exact details of how the IMP server operates is too broad to be covered in this thesis.
+The exact details of how the IMP server operates are too complex to be covered in this thesis.
 
@@
     \includegraphics[scale=0.6]{Diagrams/IMP Layer Diagram.pdf}
-    \caption{IMP System Operation Layers}
+    \caption{IMP System Layers}
     \label{imp:layer_diagram}
@@
 
-As shown in figure \ref{imp:layer_diagram}, the operation of IMP systems can be separated into multiple layers.
-The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionalities of each component.
+As shown in figure \ref{imp:layer_diagram}, the operation of the IMP system can be separated into multiple layers.
+The layers build upon each other (from bottom to top) and provide an increasingly abstract perspective on the functionality of each component.
 
 The vertical bars in the figure represent all previously described components of the IMP system and one additional component called "Integration Module".
-The "Integration Module" is not important at the moment and will be the focus of following chapters.
-The horizontal bars in the figure represent layers of IMP system operation.
+The "Integration Module" is not important at the moment and will be the focus of the following chapters.
+The horizontal bars in the figure represent the layers of IMP system operation.
 From bottom to top, the layers describe the operation of the IMP system increasingly more abstract from the underlying technology.
@@
 The lowest layer is called "Relationship Layer".
-On this layer, the IMP system operates by establishing relationships.
-IMP application and IMP connector exchange relationship requests and responses through the IMP server in order to establish new relationships.
+In this layer, the IMP system operates by establishing relationships.
+IMP application and IMP connector exchange relationship requests and responses through the IMP server to establish new relationships.
 The IMP server maintains a list of all relationships and their status.
@@
 Once a relationship is established, the IMP system operates on the "Communication Layer".
-On this layer, IMP messages are exchanged as part of an active IMP relationship between IMP application and IMP connector.
-The application can create, send, receive, process and display a list of IMP messages that it is able to understand.
+In this layer, IMP messages are exchanged as part of an active IMP relationship between IMP application and IMP connector.
+The application can create, send, receive, process, and display a list of IMP messages that it is able to understand.
 The IMP connector is able to send and receive IMP messages through a relationship without requiring to know details about the content.
@@
 Using IMP relationships and IMP messages, the Service Provider can interact with the user on the "IMP Interaction Layer".
-On this layer, depending on the use case, different purposes can be assigned to interaction possibilities.
+On this layer, depending on the use case, different purposes can be assigned to the interaction capabilities of IMP.
 For example, a Service Provider can decide to use relationships as a way to receive product or subscription orders.
@@
 
-In this section the IMP system operation for the most important use cases of the IMP service are described in more detail.
+In this section, the IMP system operation for the most important use cases of the IMP service are described in more detail.
 
@@
 The first step towards a relationship is the interest of a user.
-A user for example wants to subscribe to the newsletter of a Service Provider.
-The Service Provider needs personal information of the users to be able to send them personalized mails.
-To obtain the necessary attributes and receive the approval of the users, the Service Provider requires  established relationships.
+A user, for example, wants to subscribe to the newsletter of a Service Provider.
+The Service Provider needs the personal information of the user to be able to send personalized mails.
+To obtain the necessary attributes and receive the approval of the user, the Service Provider requires an established relationship.
 
@@
 
-To enable users to request a relationship with the purpose of subscribing to a newsletter, the Service Provider has to create a relationship template.
+To enable the user to request a relationship with the purpose of subscribing to a newsletter, the Service Provider has to create a relationship template.
 Through the REST interface of the connector, the SP sends a request for a new relationship template.
@@
 In this case, the relationship template could be configured as follows:
+
 \begin{figure}[H]
@@
     \item Requested Attributes: Name, Surname, E-Mail address, Interests
-    \item Shared Attributes: SP Name, SP address, SP phone number, SP E-Mail address
+    \item Shared Attributes: SP Name, SP address, SP phone number, SP e-mail address
     \item Purpose: By accepting this relationship, you agree to receive personalized emails to the shared address. Name, surname and interests are required to personalize the content of the emails.
@@
 Through this ID, the corresponding template can be retrieved from the IMP server.
-The Service Provider can transmit the template ID to any user who wishes to subscribe to a newsletter. This can be done by for example rendering the template ID as a QR code on a website.
-If the QR code is displayed to the user, he can scan it using the IMP application.
+The Service Provider can transmit the template ID to any user who wishes to subscribe to a newsletter. This can be done by, for example, rendering the template ID as a QR code on a website.
+If the QR code is displayed, the user can scan it using the IMP application.
 The application understands that the content of the QR code contains a relationship template ID and retrieves the corresponding template from the IMP server.
@@
 
-The user can now decide if he wants to accept the relationship and share the requested attributes.
-If he accepts, IMP application sends a relationship request to the IMP server.
+The user can now decide whether to accept the relationship and share the requested attributes.
+If the user accepts, IMP application sends a relationship request to the IMP server.
 The request contains all information of the relationship template in addition to the shared attributes of the user.
@@
 
-As the system architecture of the Service Provider has no way of knowing when the connector receives a relationship request, he iteratively requests an update from the connector through its REST interface.
-The connector responds with the received relationship request, provided a request was submitted.
-The system architecture of the Service Provider processes the request in order to decide if it should be accepted.
-The Service Provider could for example verify if a relationship with the identity already exists or if the e-mail address is already registered.
+As the system architecture of the Service Provider has no way of knowing when the connector receives a relationship request, it regularly requests an update from the connector through its REST interface.
+The connector eventually responds with the received relationship request.
+The system architecture of the Service Provider processes the request to decide if it should be accepted.
+The Service Provider could, for example, verify if a relationship with the identity already exists or if the e-mail address is already registered.
 
@@
 The response contains all information of the received relationship request with optional additional information the Service Provider might want to share now.
-This could for example be the name of the newsletter the Service Provider decided to select for the user based on his specified interests.
+This could, for example, be the name of the newsletter the Service Provider decided to select for the user based on his specified interests.
 
-The connector sends the relationship response to the IMP server which updates the content and status of the corresponding relationship.
+The connector sends the relationship response to the IMP server, which updates the content and status of the corresponding relationship.
 It might be possible that the user retracted the relationship request in the meantime.
-In this case, the relationship response would be dropped by the IMP server and the connector would be notified.
-If however, the IMP server updates the status of the relationship to "established", both IMP application and connector are notified with the final content of the relationship.
+In that case, the relationship response would be dropped by the IMP server and the connector would be notified.
+If, however, the IMP server updates the status of the relationship to "established", both IMP application and connector are notified about the final content of the relationship.
 
@@
 Through the IMP application, the user can view relationships and edit shared attributes.
-After changing an attribute, for example the e-mail address, the IMP application sends an attribute change request to the IMP server, which forwards it to the IMP connector corresponding to the IMP relationship.
+After changing an attribute, for example, the e-mail address, the IMP application sends an attribute change request to the IMP server, which forwards it to the IMP connector corresponding to the IMP relationship.
 Through the REST interface of the IMP connector, the Service Provider regularly polls for new messages and eventually receives the attribute change request.
 The Service Provider evaluates whether to accept or reject the request and uses the REST interface of the IMP connector to submit the response.
-The IMP connector sends the response to the IMP server which - if the Service Provider accepted the request - notifies IMP connector and IMP application of the successful change of attributes.
-The Service Provider again polls for new messages and eventually receives the attribute change established notification based on which it now updates the stored attributes associated to the relationship.
+The IMP connector sends the response to the IMP server which - if the Service Provider accepted the request - notifies the IMP connector and IMP application of the successful change of attributes.
+The Service Provider again polls for new messages and eventually receives the "attribute change established" notification, based on which it now updates the stored attributes associated with the relationship.
 When the IMP application receives the attribute change established message, it displays a notification to the user.
@@
 \subsubsection{Mail}
-This section elaborates the sequence of sending a mail as part of an IMP relationship as shown in figure \ref{imp:mail}.
-If a user for example has questions about the newsletter, he can send a mail to the Service Provider as part of the established relationship.
+This section describes the sequence of sending a mail as part of an IMP relationship as shown in figure \ref{imp:mail}.
+If a user, for example, has questions about the newsletter, he can send a mail to the Service Provider as part of the established relationship.
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 
-Through the IMP application the user can view relationships and submit mails.
-Once submitted, the IMP application sends the mail to the IMP server which forwards it to the IMP connector corresponding to the relationship.
+With the IMP application the user can view relationships and submit mails.
+Once submitted, the IMP application sends the mail to the IMP server, which forwards it to the IMP connector corresponding to the relationship.
 The Service Provider polls for new messages and eventually receives the mail as response.
 An employee of the Service Provider can process the email and use the REST interface of the IMP connector to send a response mail to the same relationship.
-The IMP connector sends the mail to the IMP server which forwards it to the IMP application of the IMP identity corresponding to the IMP relationship.
+The IMP connector sends the mail to the IMP server, which forwards it to the IMP application of the IMP identity corresponding to the IMP relationship.
 The application then notifies the user of the received mail.
@@
 \subsubsection{Authenticate}
-This section elaborates the sequence of authenticating as part of an IMP relationship as shown in figure \ref{imp:authenticate}.
+This section describes the sequence of authenticating as part of an IMP relationship as shown in figure \ref{imp:authenticate}.
 If the Service Provider wants to request confirmation from the user, they can send an authentication request to the corresponding relationship.
 
-\begin{figure}[H]
+\begin{figure}[h!]
     \centering

### 2021-03-26 chapters/sections/6-online_access_law.tex
finished

@@
-This chapter gives an overview about the Online Access Law regarding its regulations, their implementation, the basic OZG use case and the underlying system architecture.
+This chapter gives an overview about the Online Access Law regarding its regulations, their implementation, the basic OZG use case, and the underlying system architecture.
 
@@
 
-In 2017, the German government passed the Online Access Law (OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{ozg:regulations}:
+In 2017, the German government passed the Online Access Law (OZG), which requires the federal republic and federal states to execute the following regulations until 2022 \cite{ozg:regulations}:
 
 \paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures that are available from outside the governmental institution.
-As it is not clear which administrative services exactly are included by the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{ozg:informationsplattform}.
+As it is not clear which administrative services exactly are included in the definition of the OZG, the Federal Ministry of the Interior Building and Community (Bundesministerium des Innern, für Bau und Heimat - BMI) created a catalogue \cite{ozg:informationsplattform}.
 The OZG requires these services to be digitally available.
-As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{ozg:maturity_model}.
+As a guideline on what is considered sufficient availability, the BMI defined a maturity model \cite{ozg:maturity_model}.
 
 \paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each federal state and each commune must provide an administration portal.
-Portals of communes must be linked to the portal of the corresponding member state.
-Portals of federal republic and member states must be connected through a portal network.
+Portals of communes must be linked to the portal of the corresponding federal state.
+Portals of federal republic and federal states must be connected through a portal network.
 \cite{ozg:onlinegateway_general} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{ozg:onlinegateway_architecture}.
 
-\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services.
+\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and federal states must provide user profiles that can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services.
 The user profiles must be interoperable for every administration portal of the portal network \cite{ozg:user_profiles_general}.
@@
 
-The implementation of OZG regulations can be separated into two projects: The digitalization and the networking project.
+The implementation of OZG regulations can be separated into two projects: The digitalization and networking project.
 
-The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way: A digitized administrative service can be accessed by a user through a website.
+The goal of digitalization in this case is to make administrative services available towards a user in a digitized way: A digitized administrative service can be accessed by a user through a website.
 The website is hosted either by the federal republic or a federal state and is called "Administration Portal".
 Access is usually provided through an application form.
-The administrative service can be managed through a user profile which is provided by the federal republic or the member state.
-Management of an administrative service usually includes starting the service by sending in a form, communicating with the responsible institutions through the inbox of the profile and receiving a result.
+The administrative service can be managed through a user profile which is provided by the federal republic or the federal state.
+Management of an administrative service usually includes starting the service by sending in a form, communicating with the responsible institutions through the inbox of the profile, and receiving a result.
 The user profile can also enable users to upload documents to a datawallet and to save personal information for automatically filling in forms.
@@
 Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal.
-In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and some by the communes \cite{BMI:Onlinezugangsgesetz}.
+In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the federal states, and some by the communes \cite{BMI:Onlinezugangsgesetz}.
 
@@
 
-In order to save investments a method called "one for all" is used when hosting administrative services.
+To save investment, a method called "one for all" is used when hosting administrative services.
 One federal state or the federal republic provides access to a service on their administration portal and distributes the requests to the responsible institutions "under the hood".
 As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal.
-Interoperable user profiles enable usage of each profile for management of administrative services on all portals.
+Interoperable user profiles enable the usage of each profile for the management of administrative services on all portals.
 
@@
 The federal state Sachsen-Anhalt is responsible for processing BAföG applications on its administration portal and the federal state Hessen is responsible for processing drivers license applications on its administration portal.
-The user has never access OZG services before.
+The user has never accessed OZG services before.
 
-\paragraph{Create User Profile} The user wants to apply for BAföG first and therefore visits an administration portal which informs them, that in order to apply for administrative services, a user profile is required.
+\paragraph{Create User Profile} The user wants to apply for BAföG first and therefore visits an administration portal which informs that to apply for administrative services, a user profile is required.
 As user profiles are designed to be interoperable, it does not matter through which administration portal the user profile is created.
 
-The user is requested to enter personal information and to specify an authentication method. For authentication for example a username and password combination can be used.
+The user is requested to enter personal information and to specify an authentication method. For authentication, for example, a username and password combination can be used.
 
@@
 \paragraph{Login to User Profile} Before being able to apply for administrative services, the user has to login into the user profile on the administration portal.
-Depending on the authentication method used for logging in, a trust level of the current session is determined.
-Only with a high trust level users can apply for a broad selection of administrative services.
+Depending on the authentication method used for logging in, the trust level of the current session is determined.
+Only with a high trust level, users can apply for a broad selection of administrative services.
 The user has selected an authentication method which results in a high trust level.
 
-\paragraph{Application} On the web page of the administrative portal the user clicks on a "bring me to the application" button and is forwarded to a web page with an interactive form.
+\paragraph{Application} On the web page of the administration portal, the user clicks on a "bring me to the application" button and is forwarded to a web page with an interactive form.
 Before the user is forwarded, he has the option to transfer personal information for automatic filling of the form.
-The user decides to accept and is presented with a filled in form.
-After pressing the "submit" button the application is transferred to the responsible institution.
+The user decides to accept and is presented with a filled-in form.
+After pressing the "submit" button, the application is transferred to the responsible institution.
 
 \paragraph{Management of Applications} The user is forwarded back to the administration portal and selects to view all active applications created through the portal.
-Here the user can see the application they just submitted and is able manage it by for example requesting cancellation.
+Here the user can see the application and is able to manage it by, for example, requesting cancellation.
 
-\paragraph{Communication} Through the inbox of the user profile the user is notified about a message regarding the application.
+\paragraph{Communication} Through the inbox of the user profile, the user is notified about a message regarding the application.
 The institution responsible for processing the application informs the user about receiving the application.
-Eventually the institution finishes processing the application and sends a message to the inbox of the user to inform them about the result.
+Eventually, the institution finishes processing the application and sends a message to the inbox of the user to inform them about the result.
 This marks the end of the basic OZG use case, however, the user wants to apply for a second administrative service.
 
-\paragraph{Selection of Administrative Service} Using the search feature of the administration portal, the user now enters the search term "drivers license", selects the correct search result and is forwarded to the corresponding web page on the administration portal of Hessen.
+\paragraph{Selection of Administrative Service} Using the search feature of the administration portal, the user now enters the search term "drivers license", selects the correct search result, and is forwarded to the corresponding web page on the administration portal of Hessen.
 
@@
 
-\paragraph{Application} The application process is designed to be similar for each administration portal, however, as Sachsen-Anhalt and Hessen operate their application processes independently, minor differences exist in for example the design and text of the web pages.
+\paragraph{Application} The application process is designed to be similar for each administration portal, however, as Sachsen-Anhalt and Hessen operate their application processes independently, minor differences exist in, for example, the design and text of the web pages.
 
-\paragraph{Management of Applications} The user is, again, forwarded back to the administration portal and selects to view all active applications created through the portal.
-The user is only able to see and manage the application for a drivers license.
+\paragraph{Management of Applications} The user is again forwarded back to the administration portal and selects to view all active applications created through the portal.
+The user is only able to see and manage the application for a driving license.
 As the application for BAföG was created through a the administration portal of Sachsen-Anhalt, it is not accessible through the administration portal of Hessen.
@@
 References about OZG system architectures of Baden-Württemberg \cite{ozg:bw} and Nordrhein-Westfalen \cite{ozg:nrw} are used.
-The presentation document regarding the administration portal of Baden-Württemberg \cite{ozg:bw_administration_portal} is used as basis for describing the administration portal.
+The presentation document regarding the administration portal of Baden-Württemberg \cite{ozg:bw_administration_portal} is used as the basis for describing the administration portal.
 
 As shown in figure \ref{ozg:system_overview}, the OZG system architecture is separated into three components and two domains.
-Domains in this case separate systems in regard to the physical location where they operate.
+Domains in this case separate systems regarding the physical location where they operate.
 Components in this case describe functionally correlated systems of a system architecture.
@@
 The "User Component" directly interacts with users to enable access to administration portals.
-This can be desktop or mobile applications or as in this specific case a web browser.
+This can be desktop or mobile applications or as in this specific case, a web browser.
 The "Administration Portal Component" hosts the administration portal.
@@
     \includegraphics[scale=0.6]{Diagrams/OZG System Overview.pdf}
-    \caption{OZG System Overview}
+    \caption{OZG System Architecture of Federal State}
     \label{ozg:system_overview}
@@
 Through the service facade, the web server accesses each service component and makes its service available to the "User Component".
-The "User Profile Management" component is capable of interacting with the "User Profile Component" to create new user profiles, retrieve personal information from existing user profiles and process login requests.
-The "User Profile Component" provides conventional user profile based identity management. 
+The "User Profile Management" component is capable of interacting with the "User Profile Component" to create new user profiles, retrieve personal information from existing user profiles, and process login requests.
+The "User Profile Component" provides conventional user profile-based identity management. 
 Through the Federated Identity Management of Interoperable User Accounts in Germany (Föderiertes Identitätsmanagement interoperabler Nutzerkonten in Deutschland - FINK) the "User Profile" component of each federal state is made interoperable.
@@
 The user can opt in to automatically fill in forms with personal information.
-In that case, after authentication of the user, the "Administration Portal" component retrieves personal information from the "User Profile" component and sends it to the "Formula Engine" before displaying a filled in form to the user.
+In that case, after authentication of the user, the "Administration Portal" component retrieves personal information from the "User Profile" component and sends it to the "Formula Engine" before displaying a filled-in form to the user.
 
 The "Application Management" component receives submitted applications by the "Formula Engine" component for further processing.
-Depending on the administration portal and type of application, additional processing steps, that are not part of the use case can take place.
-This includes for example payment processes.
-The component tracks the current status of the application which the user can view through the web page of the administration portal.
+Depending on the administration portal and the type of application, additional processing steps that are not part of the use case can occur.
+This includes, for example, payment processes.
+The component tracks the current status of the application, which the user can view through the web page of the administration portal.
 It is also capable of terminating the application process if the user requests it.

### 2021-03-26 chapters/sections/7-messaging.tex
finished

@@
 This chapter gives a brief overview of what messaging is and how it can be used for system integration purposes.
-It introduces various messaging patterns which will be used by the technological integration in chapter 4 and 5.
+It introduces various messaging patterns which will be used by the technological integration in chapters 4 and 5.
 The content of this chapter is based on the book \textit{Enterprise Integration Patterns} by \textcite{EIP}.
@@
 Messaging is an asynchronous system-to-system communication, delivering packages of data called messages through channels.
-Messages can contain any structured data like strings, arrays or objects.
+Messages can contain any structured data like strings, arrays, or objects.
 It is up to the sender and receiver to determine and understand its content.
 
-Channels can be seen as a queue of messages, accessible to interested systems.
+Channels can be seen as a queue of messages accessible to interested systems.
 Channels have a direction in a sense so that no system simultaneously writes to and reads from a channel.
-Therefore, by one system writing messages to a channel and another system reading them, a message and data flow can be established.
+Therefore, by one system writing messages on a channel and another system reading them, a message and data flow can be established.
 
@@
 During the routing of messages between systems, the content of messages might have to be modified.
-Therefore various message transformation components exist.
-Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message to an outbound channel.
+Therefore, various message transformation components exist.
+Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules, and publish the modified message to an outbound channel.
 
-"\textit{A messaging system manages messaging the way a database system manages data persistence}" \cite[p.
+A messaging system manages messaging the way a database system manages data persistence \cite[p.
 31]{EIP}.
-Configuring a messaging system involves definition of available channels, the type of messages they exchange, their connection between systems, the message flow and when necessary the insertion of routing and transformation components.
+Configuring a messaging system involves the definition of available channels, the type of messages they exchange, their connection between systems, the message flow, and, when necessary, the insertion of routing and transformation components.
 
 Depending on the messaging system solution, additional features can be configured to increase performance, stability, failure safety and more.
-If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently stores messages in case of a system crash.
+If properly configured, the messaging system operates reliably, handles unreliable network connections, and persistently stores messages in case of a system crash.
 
@@
 
-As channels are able to function as a message buffer, sender and receiver of messages do not even have to be running at the same time.
+As channels are able to function as a message buffer, the sender and receiver of messages do not even have to be running at the same time.
 
@@
 
-In the book "\textit{Enterprise Integration Patterns}" by \cite{EIP} multiple patterns for designing messaging systems are presented.
+In the book "\textit{Enterprise Integration Patterns}" by \textcite{EIP} multiple patterns for designing messaging systems are presented.
 This section gives a brief overview of patterns relevant for the thesis and their visual notation.
@@
 There are different types of channels.
-In this thesis, named channels are publish-subscribe datatype channels.
+In this thesis, the named channels are publish-subscribe datatype channels.
 Unnamed channels are point-to-point channels.
@@
 
-Systems that do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API.
+Systems that do not natively support message-based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API.
 The messaging adapter usually has to be developed individually for each system, and manually integrated into the code of the system through asynchronous function calls of the adapter API.
@@
 
-Content-Based Routers contain a preconfigured set of routing rules, that instruct the router to place inbound messages on different outbound channels depending on their content.
+Content-Based Routers contain a preconfigured set of routing rules that instruct the router to place inbound messages on different outbound channels depending on their content.
 These rules do not change during operation of the system.
@@
 Message Translators have the purpose of translating message content on data representation and data type layer. 
-On the data representation layer, message translators translate message content for example from an XML format to a JSON format.
-On the data type layer, message translators can for example concatenate first name and last name fields to a single name field.
+On the data representation layer, message translators translate message content, for example, from an XML format to a JSON format.
+On the data type layer, message translators can, for example, concatenate first name and last name fields to a single name field.
 
@@
 
-As shown in figure \ref{messaging:filter2}, Message Filters can, in combination with publish-subscribe channels, be used to separate messages onto individual datatype channels.
+As shown in figure \ref{messaging:filter2}, Message Filters can, in combination with publish-subscribe channels, be used to separate messages to individual datatype channels.
 
@@
 Message Stores have the purpose of storing consumed messages in a database.
-They are also capable of communicating with other messaging patterns for providing access to stored messages.
+They are also capable of communicating with other messaging patterns to provide access to stored messages.
 Communication between message patterns and Message Stores is indicated by a dotted arrow.
 
-Figure \ref{messaging:store} shows the visual notation of a Message Store. It also shows the example of a Content Enricher accessing the message store.
+Figure \ref{messaging:store} shows the visual notation of a Message Store. It also shows an example of a Content Enricher accessing the message store.
 

### 2021-03-26 chapters/sections/8-identity_management.tex
Einleitung überarbeitet
finished

@@
-This chapter describes issues of user based identity management in general and for the specific use case of the OZG.
-It also presents possibilities of how IMP can be utilized to solve mentioned issues.
+This chapter describes the issues of user-based identity management in general and for the specific use case of the OZG.
+It also presents possibilities of how IMP can be utilized to solve the mentioned issues.
+At the end, the conclusion briefly states whether IMP can be considered for solving the problems of user profile-based identity management.
 
@@
 The OZG system architecture utilizes user profiles for identity management.
-This leads to several issues regarding usability, data protection, security and maintenance costs.
-The following sections describe problems of user profiles in general as well as problems arising specifically in context of the OZG system architecture.
+This leads to several issues regarding usability, data protection, security, and maintenance costs.
+The following sections describe problems of user profiles in general as well as problems arising specifically in the context of the OZG.
 
 \paragraph{Usability}
-Each Service Provider has a different platform for the management of personal information and identity related interactions.
-This can for example be web pages or applications for desktop and smartphone.
+Each Service Provider has a different platform for the management of personal information and identity-related interactions.
+This can, for example, be web pages or applications for personal computers and smartphones.
 Keeping track of all created user profiles is difficult.
 
-In case of web pages, users will also have to remember various URLs, usernames and passwords. The risk of forgetting login credentials is high.
+In the case of web pages, users will also have to remember various URLs, usernames, and passwords. The risk of forgetting login credentials is high.
 
-To manage personal information stored in each user profile and for example change an e-mail address, users have to access the individual platforms of each Service Provider.
-Depending on the amount of created profiles, this can be a time consuming task.
-Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA or Magic-Link.
-Users receiving notifications, messages and mails on multiple platforms can quickly loose track and oversee important notifications.
+To manage the personal information stored in each user profile and, for example, change an e-mail address, users have to access the individual platforms of each Service Provider.
+Depending on the amount of created profiles, this can be a time-consuming task.
+Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA, or Magic-Link.
+Users receiving notifications on multiple platforms can quickly lose track and oversee important notifications.
 
-Each platform is often presented with a different design although the purpose remains similar. This makes it difficult for users to orientate themselves.
+Each platform is often presented with a different design, although the purpose remains similar. This makes it difficult for users to orientate themselves.
 
-Bidirectional identity related interactions like subscribing to a service, canceling a subscription, sending or receiving a security relevant mail often only takes place through a web page where e-mails are only used to notify the user to check his user profile ("You have unread messages!").
+Bidirectional identity-related interactions like subscribing to a service, canceling a subscription, sending or receiving a security relevant mail often only takes place through a web page where e-mails are only used to notify the user to check his user profile ("You have unread messages!").
 This is because e-mails do not provide a secure way of exchanging information and do not enable advanced interaction capabilities or exchange of structured content.
-Although Service Providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.
+Although Service Providers could develop mobile applications as an alternative for web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments, smaller SPs might decide not to.
 
-Service Providers rely on the validity of information stored in the user profile.
-To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show their ID at a local shop.
-As each Service Provider manages separate user profiles, the user might have to go through this time consuming process repeatedly.
+Service Providers rely on the validity of the information stored in the user profile.
+To guarantee that the information is correct, some SPs require users to take extra identification steps by, for example, performing a video call or requesting the user to show their ID at a local shop.
+As each Service Provider manages separate user profiles, the user might have to go through this time-consuming process repeatedly.
 
@@
 
-In case of the OZG, usability of user profiles across multiple administration portals is limited: Although user profiles are interoperable, administration portals are individually responsible for the application process.
+In the case of the OZG, the usability of user profiles across multiple administration portals is limited: Although user profiles are interoperable, the administration portals are individually responsible for the application process.
 Applying for different administration services, users might have to visit separate administration portals.
-Each of the portals manage the application process differently.
+Each of the portals manages the application process differently.
 Active applications are not stored as part of the user profile but remain accessible only through the respective portals they were created through.\\ An overview of all active applications amongst all administration portals does not exist.
-The user has to go through each portal to find the application they for example want to cancel.
-Especially due to the „one for all“ approach, users will have to access dedicated administration portals for certain types of administrative services.
+The user has to go through each portal to find the application they, for example, want to cancel.
+Especially due to the „one-for-all“ approach users will have to access dedicated administration portals for certain types of administrative services.
 To mitigate this issue, the inbox of user profiles is used to notify the user of the status of all applications.
@@
 \paragraph{Data Protection}
-Before, Service Providers established a habit of collecting more personal information than necessary to provide their services.
+Service Providers established a habit of collecting more personal information than necessary to provide their services.
 As a response, the "Datenschutz Grundverordnung" - DSGVO (General Data Protection Regulation) was passed.
-Amongst other things, it requires Service Providers to inform the user about which personal information is processed, the reason for processing the information and how it is being processed.
+Amongst other things, it requires Service Providers to inform the user about which personal information is processed, the reason for processing the information, and how it is being processed.
 Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage.
@@
 
-In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also with multiple systems operated by the member state.
-Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it.
+In the case of the OZG, the user shares personal information not only with the institutions responsible for processing an application but also with multiple systems operated by the member state.
+Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled-in form and stores it.
 As a result of that, the administration portal has access to all personal information that in reality only the institution will eventually need to process.
@@
 
-User profiles are most commonly secured through passwords.
-Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of them being stolen and all user profiles being accessible.
-With the amount of different Service Providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between Service Providers.
+User profiles are often secured through passwords.
+Especially for a large number of profiles, users are tempted to use identical passwords, increasing the risk of them being stolen and all user profiles being accessible.
+With the number of different Service Providers storing personal information and passwords, the risk of it being stolen increases as the security of system architectures differs between Service Providers.
 
 Users also have to rely on the correct operation of the system architecture of the Service Provider and might not be able to prove failures in the operation of the system.
-If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proving to the Service Provider, that they did cancel the subscription.
+If, for example, the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues to provide proof.
 
@@
 The goal of IMP solutions is to replace user profiles with a single IMP identity.
-Through the IMP client a user can manage their IMP identity and all connected integrated Service Providers.
+Through the IMP client, a user can manage their IMP identity and all connected integrated Service Providers.
 Instead of creating user profiles, the user can establish a relationship between their IMP identity and the Service Provider.
 Depending on the use case, the relationship can be utilized differently.
-Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.
+Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames, or passwords.
 It also enables the user to update personal information shared with Service Providers through one application.
@@
 
-As part of established relationships, IMP client and Service Provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service Providers can send structured data to the IMP client along with the information that it should display as a form.
-Depending on the content of the form and the use case of the Service Provider, the form can for example be a purchase agreement or a survey.
+As part of established relationships, IMP clients and Service Providers can securely exchange bidirectional structured data, which along with the advanced interaction capabilities of the IMP client, can be used to create custom interaction scenarios: Service Providers can send structured data to the IMP client along with the information that it should display as a form.
+Depending on the content of the form and the use case of the Service Provider, the form can, for example, be a purchase agreement or a survey.
 
-Assuming that, through a secure identification and validation process, the identity management provider has made sure that attributes users store as part of their IMP identity are correct, Service Providers wont require any additional identification steps through for example video calls.
+Assuming that, through a secure identification and validation process, the identity management provider has made sure that the attributes users store as part of their IMP identity are correct, Service Providers wont require any additional identification steps through for example video calls.
 
-Due to the IMP client being able to automatically fill in attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.
+Due to the IMP client being able to automatically fill in the attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.
 
-In case of the OZG system architecture, IMP can be used by each member state to individually establish relationships with IMP identities of users to access personal information.
+In the case of the OZG system architecture, IMP can be used by each member state to individually establish relationships with IMP identities of users to access personal information.
 This could replace the requirement for user profiles to be interoperable.
-For the most part, member states would then be able to operate independently from each other.
+For the most part, the member states would then be able to operate independently from each other.
 This solution is described in detail in chapter 4.
@@
 As part of the process of establishing a relationship, the Service Provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed.
-With this information, the user can make an informed decision whether to establish the relationship and the Service Provider performed their duty to inform the user as required by the DSGVO.
+The user can make an informed decision whether to establish the relationship and the Service Provider performs its duty to inform the user as required by the DSGVO.
 
@@
 
-As every relationship along with shared attributes is manageable through the IMP client, the user wont loose track of which Service Provider has access to what personal information.
+As every relationship is manageable through the IMP client, the user wont loose track of which Service Provider has access to which personal information.
 
-The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the Service Provider processes only a small portion of attributes of IMP identities.
+The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the Service Provider processes only a small portion of the attributes of IMP identities.
 
-In case of the OZG system architecture, IMP can be used by the individual institutions to establish relationships with IMP identities of users to retrieve applications for administrative services.
+In the case of the OZG system architecture, IMP can be used by individual institutions to establish relationships with IMP identities of users to retrieve applications for administrative services.
 This could eventually eliminate the need for user profiles.
@@
 The IMP client itself can be secured without the need for a password.
-As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and Service Provider can be validated at any time.
-This enables both user and Service Provider to provide proof for every interactions.
+As the IMP system is capable of signing relationships and exchanged data, the interactions between IMP identity and Service Provider can be validated at any time.
+This enables both the user and Service Provider to provide proof for every interaction.
 
-\section{Outcome}
+\section{Conclusion}
+
+User profile based identity management especially in case of the OZG has several problems in regard to usability, data protection and security.
+As described, in many cases, IMP has the possibility of solving these issues and eliminating or at least enabling better control over fragmented partial identities.
+This is the case for interoperable OZG user profiles as well as user profiles in general.
+Therefore it makes sense to further investigate possibilities of utilizing IMP as a solution to partial identities.
+Using the small scale model of fragmented partial identities in context of the OZG, the following chapters 4 and 5 present different possibilities of utilizing IMP.

### 2021-03-26 chapters/sections/9-imp_utilization_in_ozg.tex
finished

@@
-This chapter presents an IMP solution which solves issues that OZG identity management has, as described in chapter 3.
-For utilization of IMP services as described by the IMP solution, an integration architecture will be presented that enables the OZG system architecture described in section 2.3 to access the IMP system described in section 2.2.
-
-Focus of the IMP solution and the integration architecture is to require minimal invasion into the existing system architecture: Few existing system components should have to be modified and the existing operation of the system should not be disrupted.
-The IMP solution should provide an additional but optional way for users to access OZG services.
+This chapter presents an IMP solution which solves issues of user profile-based identity management by enabling users to create, manage, and access user profiles through IMP.
+For the utilization of IMP services as described by the IMP solution, an integration architecture is presented that enables the OZG system architecture described in section 2.2 to access the IMP system described in section 2.1.
 
@@
     \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/IMP Layer Diagram Integration.pdf}
-    \caption{IMP Layer Diagram}
+    \caption{IMP System Layers}
     \label{integration1:layer_diagram}
@@
 The IMP solution is integration on the use case level.
-It presents possibilities of leveraging interaction capabilities of the IMP system in the context of the Service Provider for improvement of usability, data protection and security.
-Furthermore it describes which types of relationships the Service Provider can use in their business scenario, how relationships can be processed, which types of messages can be exchanged through the relationships, what the purpose of each message can be and how the IMP client can react to different message types.
-
-The IMP solution focuses on utilizing IMP capabilities in a way which affects the existing operation of the system architecture the least while solving as many identity management issues described in section 3.1 as possible.
+It presents possibilities of leveraging the interaction capabilities of the IMP system in the context of the Service Provider for the improvement of usability, data protection and security.
+Furthermore, it describes which types of relationships the Service Provider can use in their business scenario, how relationships can be processed, which types of messages can be exchanged through the relationships, what the purpose of each message can be and how the IMP client can react to different message types.
 
@@
 
-Focus of the Technological Integration is to connect with the minimal number systems possibly while solving as many integration issues described in section 3.3 as possible.
-
 \section{IMP Solution Integration}

### 2021-03-26 msc-thesis.tex
finished

--- 2021-02-26 msc-thesis.tex
@@
 
-\newpage
+Diese Bachelorarbeit stellt Identity Management Provisioning (IMP) als mögliche Lösung von Problemen Benutzerprofil basierter Identitätsmanagementsysteme vor.
+IMP bietet Identitätsmanagement als Service für Benutzer und Dienstanbieter.
+Es ermöglicht Nutzern eine IMP Identität zu erstellen, um persönliche Informationen und Nachrichten mit mehreren Dienstanbietern auszutauschen.
+
+Damit Dienstanbieter mit bestehenden, auf Benutzerprofilen basierenden Identitätsmanagementsystemen IMP nutzen können, ist eine Integration in bestehende Geschäftsprozesse und bestehende Systemarchitekturen erforderlich.
+Es werden zwei IMP Lösungen vorgestellt, die beschreiben, wie Service Provider IMP verwenden können.
+Außerdem wird ein Messaging System für die technologische Integration präsentiert.
+
+Ziel der IMP Lösungen ist es, Möglichkeiten zu beschreiben, die Benutzerfreundlichkeit, Datenschutz und Sicherheit des Identitätsmanagements durch die Nutzung des IMP Dienstes erhöhen.
+Die IMP-Lösungen werden, basierend auf dem aktuell relevanten Anwendungsfall des Online-Zugangs-Gesetzes (OZG), konzipiert.
+
+Die erste IMP Lösung beschreibt eine Möglichkeit, welche Benutzern die Erstellung von Benutzerprofilen, Pflege persönlicher Informationen und Interaktion über eine IMP Anwendung ermöglicht.
+Dieser Integrationsansatz soll die Benutzerfreundlichkeit erhöhen und gleichzeitig das Risiko, die Komplexität und die Kosten der Integration minimieren.
+Dadurch, dass auf Benutzerprofilen basierende Identitätsmanagementsysteme in Betrieb gelassen werden, bleiben Probleme hinsichtlich des Datenschutzes bestehen.
+Eine zweite IMP Lösung wird vorgestellt, die den Datenschutz erhöht, indem Benutzerprofile ersetzt werden.
+Stattdessen geben Nutzer persönliche Informationen nur für einzelne Geschäftsprozesse temporär frei.
+
+Zur Integration von IMP Lösungen wird ein Messaging System vorgestellt, das in der Lage ist, IMP in bestehende Systemarchitekturen von Dienstanbietern zu integrieren.
+Neben messaging ermöglicht ein modularer Ansatz, dass die Integrationsarchitektur konfigurierbar und erweiterbar ist, um verschiedene IMP Lösungen in unterschiedliche Systemarchitekturen zu integrieren.
+Die Fähigkeiten des Messaging Systems werden durch die Integration der zuvor beschriebenen, grundsätzlich unterschiedlichen, IMP Lösungen in verschiedene Systemarchitekturen im Kontext des OZG demonstriert.
 
 \chapter*{Abstract}
+
+This bachelor thesis presents Identity Management Provisioning (IMP) as a possibility for solving problems of user profile-based identity management systems.
+IMP provides identity management as a service to users and Service Providers.
+It enables users to create an IMP identity and use it to share personal information and exchange messages with multiple Service Providers.
+
+In order for Service Providers with existing user profile-based identity management systems to utilize IMP, integration into their existing business processes and existing system architectures is necessary.
+Two IMP solutions which describe how Service Providers can utilize IMP and one messaging system for technological integration are presented.
+
+The purpose of IMP solutions is to describe possibilities to increase usability, data protection and security of identity management through the utilization of the IMP service.
+The IMP solutions are designed, based on the currently relevant use case of the Online Access Law (Online Zugangs Gesetz - OZG).
+
+The first IMP solution describes the possibility of enabling users to create user profiles, maintain personal information, and interact through an IMP application.
+This integration approach is designed to increase usability while minimizing the risk, complexity, and cost of integration.
+As a result of leaving user profile-based identity management in operation, problems regarding data protection remain.
+A second IMP solution is presented to increase data protection by replacing user profiles.
+Instead, users temporarily share personal information for individual business processes.
+
+For the integration of IMP solutions, a messaging system is presented which is capable of integrating IMP into existing system architectures of Service Providers.
+In addition to messaging, a modular approach enables the integration architecture to be configurable and expandable to integrate various IMP solutions into different system architectures.
+
+The capabilities of the messaging system are demonstrated by integrating the previously described, fundamentally different IMP solutions into different system architectures in the context of the OZG.
 
@@
 \chapter{Introduction}
+\subfile{chapters/1-introduction}
 
-\section{Context}
+\chapter{Background and Related Work} \label{chapter:background}
+\subfile{chapters/2-background_and_related_work}
 
-\subfile{sections/1-context}
+\chapter{User Profile Identity Management} \label{chapter:user_profile_identity_management}
+\subfile{chapters/3-ozg_identity_management}
 
-\section{Objective}
+\chapter{IMP Utilization as Extension}
+\subfile{chapters/4-imp_utilization_in_ozg}
 
-\subfile{sections/2-objective}
+\chapter{IMP Utilization as Replacement}
+\subfile{chapters/5-advanced_utilization}
 
-\section{Structure of Work}
-
-\subfile{sections/3-structure_of_work}
-
-\chapter{Background and Related Work}
-
-\section{Terminology}
-
-\subfile{sections/4-terminology}
-
-\section{Identity Management Provisioning (IMP)}
-
-\subfile{sections/5-imp}
-
-\section{Online Access Law (OZG)}
-
-\subfile{sections/6-online_access_law}
-
-\section{Messaging}
-
-\subfile{sections/7-messaging}
-
-\chapter{OZG Identity Management}
-
-\subfile{sections/8-identity_management}
-
-\chapter{IMP Utilization in OZG}
-
-\subfile{sections/9-imp_utilization_in_ozg}
-
-\chapter{Advanced Utilization}
-
-\subfile{sections/12-advanced_utilization}
-
-\chapter{Solution Evaluation}
-
-\section{Conclusion}
-
-\chapter{Outlook: Advanced IMP Integration}
+\chapter{Conclusion}
+\subfile{chapters/6-conclusion}
 
